### 2016-05-09 newpaper.tex
change to work office

\documentclass[10pt,journal,compsoc]{IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.
%
% Note that some packages require special options to format as the Computer
% Society requires. In particular, Computer Society  papers do not use
% compressed citation ranges as is done in typical IEEE papers
% (e.g., [1]-[4]). Instead, they list every citation separately in order
% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
% package with the nocompress option which is supported by cite.sty v4.0
% and later. Note also the use of a CLASSOPTION conditional provided by
% IEEEtran.cls V1.7 and later.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
    \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
    \graphicspath{{./pics/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  %  \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/tex-archive/info/epslatex/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
\ifCLASSOPTIONcompsoc
  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
\else
  \usepackage[caption=false,font=footnotesize]{subfig}
\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a sans serif font rather
% than the serif font used in traditional IEEE formatting and thus the need
% to invoke different subfig.sty package options depending on whether
% compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/

% *** FLOAT PACKAGES ***
%
\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Do not use the stfloats baselinefloat ability as IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and
% Axel Sommerfeldt. This package may be useful when used in conjunction with
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

\usepackage{enumitem}
\usepackage{algorithm}
\usepackage{multirow}
\usepackage{slashbox}
%\usepackage{ulem}
%\usepackage[numbers,sort&compress]{natbib}
\renewcommand{\arraystretch}{1.3}

\usepackage{color}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}
\floatname{algorithm}{Procedure}

\begin{document}
\title{Efficient Non-incremental Constructive Solid Geometry Evaluation for Triangular Meshes}
\author{Rui~Wang,~
        Xudong~Jiang,~
        Hongbo~Fu,~
        Bin~Sheng,~and
        Enhua~Wu
\IEEEcompsocitemizethanks{

\IEEEcompsocthanksitem R. Wang and B. Sheng are with the Department of Computer Science and Engineering, Shanghai Jiao Tong University. Email:\{jhcz,shengbin\}@sjtu.edu.cn

\IEEEcompsocthanksitem X. Jiang is with Autodesk China Research \& Development Center. Email: xudong.jiang@autodesk.com

\IEEEcompsocthanksitem H. Fu is with the School of Creative Media, City University of Hong Kong. Email: hongbofu@cityu.edu.hk

\IEEEcompsocthanksitem E. Wu is currently a research professor at State Key Lab. of Computer Science, Institute of Software, Chinese Academy of Sciences. Email: ehwu@umac.mo}
}

%\markboth{Journal of \LaTeX\ Class Files,~Vol.~13, No.~9, September~2014}%
%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}

\IEEEtitleabstractindextext{
\begin{abstract}
\end{abstract}

\begin{IEEEkeywords}
Boolean operations, triangle mesh, CSG evaluation, plane-based geometry.
\end{IEEEkeywords}

}

\maketitle

\IEEEdisplaynontitleabstractindextext
\IEEEpeerreviewmaketitle

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{C}{onstructive} solid geometry (CSG) has long been a popular modeling tool of computer-aided design and computer-aided manufacturing (CAD/CAM). It constructs complex models by combining primitives using a series of regularized Boolean operations \cite{requicha1977mathematical}: union, intersection and difference. CSG is often represented by a binary tree, called a CSG tree, whose leaves are primitives and whose internal nodes are Boolean operations.
\newline

{\color{red}{
Main Contribution:

1. We develop a united representation of intersection lines between CSG primitives. Under this representation, Face re-tessellation and classification can be done robustly in any degenerate cases by our pipeline, while keeping good performance.

2. Unlike any of the previous method, during the algorithm, we conduct point-in-polyhedron tests only on single seed vertex. We develop a propagating to spread the classification information from the seed vertex into the whole CSG. In addition, because of this, we do not need to build a full space division to accelerate point-in-polyhedron tests, which is usually time-consuming.
}}

\section{Related Work}

\begin{figure*}[!t]
\centering
\includegraphics[width=7.1in]{flowchart}
\caption{An overview of the proposed method for CSG evaluation. In this toy example, the CSG tree represents a solid constructed by (Cube $\cup$ Sphere - Cylinder). (d) shows how to classify faces step by step using a flood filling algorithm. Faces of the same primitive are grouped as the inter-primitive group. Then faces of the same inter-primitive group are further divided into intra-primitive groups according to their conditions of intersection (c). The unvisited faces are black. Different colors of other faces indicate that they are accepted and belong to different intra-primitive groups. Rejected faces are rendered with wire-frame. The seed face of flood filling in each primitive is highlighted in red.}
\label{fig_overview}
\end{figure*}

CSG evaluation has had notorious problems with robustness since its inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}. The non-robustness is inherited from the building blocks of CSG: Boolean operations on solids. Many researchers have attempted to solve such an issue using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}. However, these methods are often too expensive in computation time and memory to be practical for evaluation of CSG with massive faces. For example, in the Computational Geometry Algorithms Library (CGAL) \cite{cgal:hk-bonp3-15a}, the state-of-the-art robust Boolean operation algorithm \cite{hachenberger2005boolean} (implemented with arbitrary precision arithmetic) is more than 20 times slower than its non-robust version.

Sugihara and Iri \cite{sugihara1990solid} introduced a plane-based representation of polyhedra. They found that Boolean operations are fundamentally robust using the plane equation as the primary geometry representation. In this condition, the evaluation of Boolean operations can be performed with no `constructions' \cite{shewchuk1999lecture}, thereby avoiding the introduction of any numerical errors.

Berstein and Fussell \cite{bernstein2009fast} noted that a binary space partitioning (BSP) merging algorithm in Boolean operations \cite{thibault1987set, naylor1990merging} is actually a plane-based technique. Therefore, they combined the two conceptions---plane-based geometry and BSP merging---to develop an unconditionally robust method for Boolean operations of polyhedra. Using Shewchuk's adaptive geometry predicate technique \cite{shewchuk1997adaptive}, this method can be only twice slower than non-robust methods. Our approach adopts this technique in the stage of face classification to ensure the robustness.

Berstein and Fussell's method does not alleviate the problem of high memory consumption of BSP-based algorithms. Thus, it remains unprepared for polyhedra with massive faces. However, it inspired Campen and Kobbelt to develop a more delicate approach  \cite{campen2010exact}. This approach solves the problem of exact and efficient conversion of polyhedra between vertex-based and plane-based representations. Moreover, by leveraging the adaptive octree, BSP structures are nested into octree cells where the intersection between primitives occurs. For efficiency, face classification is performed using cells as the basic classification units. This localized scheme saves considerable computing resources and retains the topology of non-intersected areas.

Such localized scheme is widely used in different methods of CSG boundary evaluation \cite{pavic2010hybrid, wang2011approximate, feito2013fast, campen2010exact}. These methods are usually based on intersection computation and face membership classification. The success of such localized scheme is enabled by two facts. First, the intersections between primitives are locally distributed. Second, space labels of a face are often coherent with those of its neighborhood. The former makes it possible to reduce the space that requires an intersection test. The latter enables sharing of space labels between adjacent faces to accelerate face classification.

However, most of these methods use the cube (e.g., voxels, octree cells) as the unit of the face group, which is often the natural result of reusing space-division data structures constructed for intersection computation. In this way, connected faces that share the same labels might be distributed in different cubes. Thus, repetitive classifications may be required for each cube. Furthermore, faces of different classifications may coexist within a small space, forming a ‘mixed’ area (e.g., the red areas in Figs. \ref{fig:cluster}(a) and (b)). Because the size of the cubes cannot be illimitably small, special cubes that contain faces with different space labels typically must be constructed in these mixed areas. Processing these special cubes is often complex and time-consuming. To more efficiently share space labels, we therefore use faces, rather than cubes, as the basic grouping units. Grouping is efficiently performed by utilizing geometry connectivity with a flood-filling algorithm.

Recently, Feito et al. \cite{feito2013fast} proposed a method for Boolean evaluation. This method also uses a face-based grouping scheme. To share classification results, faces that do not intersect with other primitives are grouped together according to geometry connectivity. This method and the proposed method have similar stages for single Boolean operation evaluation. One of the major differences is that our method supports non-incremental evaluation of CSG. For this purpose, we designed a series of dedicated stages. Additionally, our face grouping scheme is intended for both non-intersected faces and faces that intersect with other primitives. It thus provides a uniform treatment for all faces and further accelerates the face classification stage. Moreover, the similarity between adjacent groups is omitted by Feito et al.'s method. Although different groups have different space labels, we observe that they may still share some of these labels if they are neighboring. We utilize this kind of space label coherence between groups for better performance.

On the other hand, with the development of general-purpose computing on graphics processing units (GPGPUs), many researchers  \cite{wang2011approximate, zhao2011parallel, museth2002level, chen1999volumetic, eisemann2008single} have tried to utilize the grand computation power of graphics hardware for Boolean operations. These methods often have good performance and are suitable for interactive applications, such as digital sculpting. However, owing to the paralleled features of graphics hardware, these methods are usually voxel-based and support only approximate evaluation that inevitably suffers from geometric detail loss, especially at the intersection areas of primitives.

\section{Overview}

\label{sec:overview}

As in most previous works \cite{feito2013fast, bernstein2009fast}, we require the input primitives of the CSG tree to be watertight Nef polyhedra with manifold surfaces. We assume there is no self-intersection. Because we adopt a flood-filling strategy, we additionally assume that the connectivity of adjacent faces is available. Our current implementation is dedicated to primitives of triangular meshes for simplicity. Our approach efficiently and robustly computes the boundary of CSG solids in three steps, as illustrated in Fig. \ref{fig_overview}. Our main contributions exist in Steps 2 and 3.

\subsection{Adaptive Octree Construction}

As a typical routine of localization, our method uses the adaptive octree to frequently accelerate the used spatial query afterwards. Our octree construction implementation is akin to the implementation in Feito et al.'s method \cite{feito2013fast}. The major difference is that, because our method is for non-incremental CSG evaluation, the octree is constructed on the bounding box that contains all input primitives (Fig. \ref{fig_overview}(b)). To avoid presentation ambiguity between a CSG leaf and an octree leaf, the latter is called a cell. Intersection detection between triangle faces and cells can be efficiently performed by using the separating axis theorem \cite{gottschalk1996obbtree}. Cells are classified into two types: if all triangles that intersect a cell belong to the same primitive, we call it a \emph{non-critical} cell. Otherwise, it is a \emph{critical} cell. This classification is needed for intersection computation in the next step.

\subsection{United Representation of Intersection Construction}
\label{sec:overview:isect}

\subsection{Multilevel Flood-filling Classification}

\section{United Representation of Primitive Intersection}
{\color{red}{
Primitive intersects primitive, generating intersection line segments (Fig. \ref{fig_raw1}).

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=3.5in]{raw1}\\
  \caption{triangle contains intersection lines, two-primitive case}\label{fig_raw1}
\end{figure}

Considering degenerate cases in n-primitives CSG can be very complex (Fig. \ref{fig_raw2}).

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=3.5in]{raw2}\\
  \caption{triangle contains intersection lines, n-primitives degenerate cases}\label{fig_raw2}
\end{figure}

We converted it into a united representation, making it clear and easy to process by the following process (Fig. \ref{fig_raw3}).

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=3.5in]{raw3}\\
  \caption{triangle contains intersection lines, n-primitives degenerate cases, using united representation}\label{fig_raw3}
\end{figure}
}}

\subsection{Plane-based Triangle Intersection}

{\color{red}{why using triangle intersection, rather than edge-face based, etc. --- for coplanar test.}}
\newline\newline

\begin{figure}[t]
\centering
\includegraphics[width=3.0in]{projection}
\caption{$Seg_1$ is the intersection between $S_2$ and $F_1$. $Seg_2$ is the intersection between $S_1$ and $F_2$. The intersection between $F_1$ and $F_2$, which is the line segment in red, is the overlap of $Seg_1$ and $Seg_2$.}
\label{fig_projection}
\end{figure}

M\"{o}ller's algorithm computes the intersection between two triangles $F_1$ and $F_2$ in three steps, as illustrated in Fig. \ref{fig_projection}. First, an early rejection is performed by testing whether $F_1$ intersects the plane where $F_2$ lies, which is denoted as $S_2$. This is a necessary condition of intersection between $F_1$ and $F_2$. If this test is passed, then the same is performed for $F_2$ and $S_1$, where $S_1$ is the plane of $F_1$. Second, the intersection between $F_1$ and $S_2$, denoted as $Seg_1$, and the intersection between $F_2$ and $S_1$, denoted as $Seg_2$, are separately computed . At last, the intersection between $F_1$ and $F_2$ is determined by computing the overlap area of $Seg_1$ and $Seg_2$ .

\begin{figure}[t]
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=3.0in]{nonrobust}\\
  \caption{The left edges of A and B (\emph{left}) are nearly but not exactly collinear. However, under usual float point arithmetic, they might be judged as collinear causing discontinuous edges in the final result (\emph{right}).}\label{fig:precision}
\end{figure}

Conventional implementations of M\"{o}ller's algorithm use vertex-based representation and usual float point arithmetic. However, this is neither exact nor robust. In Fig. \ref{fig:precision}, we illustrate a non-robust 2D case of the Boolean operation. Although implementing M\"{o}ller's algorithm with arbitrary precision arithmetic could make it robust, it is too costly for a large CSG evaluation. Actually, the non-robustness of this algorithm is from \emph{constructions} \cite{bernstein2009fast}, which compute new coordinates of geometry objects based on the known coordinates of existing ones. In M\"{o}ller's algorithm, the coordinates of $Seg_1$ and $Seg_2$ (Fig. \ref{fig_projection}) are computed as intermediate results. On the other hand, if the computation can be restricted to \emph{predicates}, which make a two or three-way decision based on known coordinates, we could quickly and robustly implement this algorithm.

Fortunately, according to Sugihara and Iri \cite{sugihara1990solid}, geometry computation of Boolean operations can be restricted to predicates using plane-based representation of polyhedra. This motivated us to integrate plane-based representation into M\"{o}ller's algorithm. Exact and efficient predicate computation is performed using precise geometry predicate techniques \cite{shewchuk1997adaptive}. Details of our implementation are shown below.

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=1.7in]{p-reps}\\
  \caption{Plane-based representation of triangles. The yellow triangle is represented by three bounding planes (green) and the supporting plane where the triangle lies.}\label{fig:p-reps}
\end{figure}

We first convert $F_1$ and $F_2$ into their respective plane-based representations: a supporting plane surrounded by three bounding planes (Fig. \ref{fig:p-reps}). We implement this conversion using the exact conversion method by Campen and Kobbelt \cite{campen2010exact}. Then, in our implementation, the relative position of a point and a plane can be determined by computing the sign of the multiplication of determinants \cite{sugihara1990solid}. To avoid introducing errors, we represent the end points of $Seg_1$ and $Seg_2$  by intersections of plane triples, rather than by directly computing their coordinates. As illustrated in Fig. \ref{fig:isect}(a), these points are the intersection between an edge line of a face and the supporting plane of the other face. Because the edge line of $F_1$ can be represented as $[S_1, S_X]$ (or $[S_2, S_X]$ for an edge line of $F_2$), where $S_X$ is the corresponding bounding plane of the edge, the end points of $Seg_1$ or $Seg_2$ can be represented in the form of $[S_1,S_2,S_X]$. In Fig. \ref{fig:isect}, we list all intersection situations between a triangle and a plane, and the $S_X$  in each situation.

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{sign}
\caption{We denote the signed distance from point $X$ to plane $S_2$ as $d_X$. All the four conditions of intersection between $F_1$ and $S_2$ (denoted as $Seg_1$) are:  (a) $d_A\cdot d_C<0$, $d_B\cdot d_C<0$; (b) $d_A=0$, $d_B=0$, $d_C\neq 0$; (c) $d_A=0$, $d_B\cdot d_C<0$; (d) $d_A=0$, $d_B\cdot d_C>0$. End points of $Seg_1$ are intersections between $S_2$ and related edge lines of $F_1$ (bold edges).}
\label{fig:isect}
\end{figure}

The intersection between $F_1$ and $F_2$ is the overlap area of $Seg_1$ and $Seg_2$. It can be easily computed by comparing the end points of $Seg_1$ and $Seg_2$ along $L$ (Fig. \ref{fig_projection}), where $L$ is the intersection between $S_1$ and $S_2$. Unlike M\"{o}ller's implementation, our approach uses no projection, which requires the exact point coordinates. We call the direction of vector $\vec{N}_1\times \vec{N}_2$ the positive direction, where $\vec{N}_1$ and $\vec{N}_2$ are normals of $S_1$ and $S_2$ respectively. Given two points $A$ and $B$ on $L$,  we compute the sign of the multiplication of determinants:
\begin{equation}
\label{eq:sign}
  K(A, B)=
  \left|
  \begin{array}{c}   %该矩阵一共3列，每一列都居中放置
  \vec{S}_1 \\ \vec{S}_2 \\ \vec{S}_A \\ \vec{S}_B
  \end{array}
  \right|
  \left|                 %左括号
  \begin{array}{c}   %该矩阵一共3列，每一列都居中放置
  \vec{N}_1 \\\vec{N}_2 \\\vec{N}_A
  \end{array}
  \right|
  \left|                 %左括号
  \begin{array}{c}   %该矩阵一共3列，每一列都居中放置
  \vec{N}_1 \\\vec{N}_2 \\\vec{N}_B
  \end{array}
  \right|,
\end{equation}
where $\vec{S}_X$ is the coefficient vector of plane equation $[a_X,b_X,c_X,d_X]$,  and $ \vec{N}_X$ is the normal vector $[a_X,b_X,c_X]$. If $K(A, B)$ is positive (negative), this means that $A$ lies in the positive (negative) direction of $B$. Otherwise, $A$ and $B$ are concident.

If $F_1$ and $F_2$ are coplanar, we check whether they overlap within the common plane using the algorithm by M\"{o}ller\cite{moller1997fast}. The substrate of this algorithm is to verify on which side of an edge $E$ a point $V$ lies. We implement it using plane-based geometry by substituting $E$ with its corresponding bounding plane $S_E$ and then computing the sign of distance from $V$ to $S_E$.

\subsection{Generating United Representation}

{\color{red}{Mainly deal with intersection between intersection line segments.}}

\section{Multi-level Flood-filling Classification}
\label{section:floodfill}

{\color{red}{Flood-filling is all about giving a seed and propagation. In this chapter, from down to top, we introduce this process and explain how it can save computation time.}}

In this step, we classify faces one by one to generate the final mesh. The intersection information computed in the previous section is used for re-tessellation and space label computation. To better explain our approach, we firstly introduce the background knowledge. Then the framework of this step is outlined. Afterwards, several important techniques in this step are detailed.

\subsection{Background}
\label{sec:intuitive}

We firstly introduce the space labels, which comprise the basis of face membership classification. The space label of face $F$ with respect to primitive $M$, denoted as $L_F(M)$, is the relative location of $F$ with respect to $M$. Also, we use $L(M)$ to denote the space label with respect to $M$ which does not specify a face. In general, space label has four conditions: completely inside (\emph{In}), completely outside (\emph{Out}), on the boundary (\emph{On}) or not available (\emph{N/A}). In the last condition, $F$  crosses the boundary of $M$. Accordingly, it does not have a uniform label. In addition, if the normal direction of $F$ is considered, there are two derived conditions of \emph{On}: the normal points to the outside (\emph{Same}) and those to the inside (\emph{Oppo}) of $M$.

The evaluation of Boolean operations between B-reps primitives $A$ and $B$ can be converted to the problem of surface selection according to the labels \cite{kuratowski1968set}:
\begin{equation}
\label{eq:select}
\begin{split}
&A\cup^*B:\{F_A~Out~B\}\cup\{F_B~Out~A\}\cup\{F_A~Same~B\},\\
&A\cap^*B:\{F_A~In~B\}\cup\{F_B~In~A\}\cup\{F_A~Same~B\},\\
&A-^*B:\{F_A~Out~B\}\cup\{(F_B~In~A)'\}\cup\{F_A~Oppo~B\},
\end{split}
\end{equation}

\noindent where $F_X$ is the faces of $X$, and $F'$ means $F$ with an inverted normal. The stars ($^*$) after the operation notations ($\cup, \cap, -$) mean that the Boolean operations are regularized.

Now, consider computing $L_F(T)$, where $T$ is a CSG solid $T$ with $n$ primitives $\{M_i~| ~i = 1,2,3,...,n\}$.  Then there are a total of $n$ space labels for $F$: \{$L_F(M_i)~|~i = 1,2,3,...,n\}$ (or in vector form $\vec{L}_F$). If all elements in $\vec{L}_F$ are known and none of them is \emph{N/A}, $L_F(T)$ can be easily computed by traversing the whole CSG tree from bottom to top and progressively combining the space labels of the CSG nodes according to combination rules \cite{requicha1985boolean}:
\begin{equation}
\label{eq:comb}
\begin{split}
X\cup Out\Rightarrow X, ~~&X\cap Out\Rightarrow Out, \\
X\cap In~~\Rightarrow X, ~~&X\cup In\Rightarrow In, \\
X \cup X \Rightarrow X, ~~&X \cap X \Rightarrow X,\\
Same \cup Oppo\Rightarrow In, ~~&Same \cap Oppo\Rightarrow Out,
\end{split}
\end{equation}
where $X$ is an arbitrary label value. Note that the combination rules for difference operation are not shown here, because the difference operation can be converted into the intersection operation using De Morgan's transformations:
\begin{equation}
\label{eq:demo}
\begin{split}
A-B\Rightarrow A\cap B^c, ~~~~~~~&(A^c)^c\Rightarrow A,\\
(A\cap B)^c\Rightarrow A^c\cup B^c, ~~&(A\cup B)^c\Rightarrow A^c\cap B^c,
\end{split}
\end{equation}
where $X^c$ denotes the complement of $X$. If and only if $L_F(T) = Same$, $F$ lies on the boundary of the final model and has the correct normal; accordingly, $F$ belongs to the final result.

If some elements in $\vec{L}_F$ are \emph{N/A} or cannot be computed, we may be unable to compute $L_F(T)$. However, the CSG tree $T$ can be trimmed into a smaller one with fewer primitives to reduce the complexity of further evaluation. For example, assume we have a CSG with its Boolean expression $M_1\cup (M_2\cap M_3-M_4)$. Given the values of two labels $L(M_1)=Out$, $L(M_2)=In$, the expression can be rewritten as $Out\cup (In\cap M_3-M_4)$. Using the combination rules we can simplify the expression as $M_3-M_4$. Thus, any face that shares the same two labels $L(M_1)$ and $L(M_2)$ can be classified based on the trimmed CSG tree $M_3-M_4$, which has only two primitives.

\subsection{Face Classification Framework}
\label{sec:framework}

\begin{figure}
\centering
\includegraphics[width=3.5in]{multilvl}
\caption{Illustration of multi-level face grouping framework. Faces are grouped into smaller groups in each level. The trimmed CSG tree of a specific group is obtained by trimming the tree of its parent according to common labels of this group. When the group is not further subdivided, faces in this group are respectively classified based on the trimmed CSG tree of this group.}
\label{fig:hierachy}
\end{figure}

Space labels of neighboring faces are often coherent. That is, given two neighboring faces $F_1$ and $F_2$, $L_{F_1}(M)$ and $L_{F_2}(M)$ are often the same. Therefore, we can group together neighboring faces and evaluate them based on the smaller CSG tree, which is trimmed by the common labels. The trimmed tree contains fewer leaves, thus enabling faster computation. If face grouping can be efficiently performed, this strategy will greatly accelerate the process of face membership classification. Moreover, a multi-level grouping scheme (Fig. \ref{fig:hierachy}) may provide even greater capability to shared labels. By using such a scheme, faces are first grouped into first-level groups; then, faces of the same first-level groups are further divided into second-level groups, and so on. Labels are shared in each level and the original CSG tree is trimmed step by step according to common labels in each level. We developed this idea into a novel classification algorithm that uses a two-level grouping scheme. The first level is the \emph{inter-primitive} level; the second is the \emph{intra-primitive} level.

Before we begin face classification, pre-computation is conducted to make the subsequent analysis easier. The original CSG tree is converted into a \emph{positive} tree using the method by Rossignac and Voelcker \cite{rossignac1988active}. `Positive' means that the CSG tree contains no difference (-) operation. According to Equation \ref{eq:demo}, there may be some primitives with complement notation. The benefit is that we are not required to consider the difference operations in the following computation.

The classification starts from face grouping in the inter-primitive level. In this level, faces of the same primitives are simply grouped together. Then, we give a rough estimation of the common labels of the group. Suppose the group is primitive $M$. Its face labels with respect to primitives whose bounding boxes are totally outside of $M$'s bounding box must be $Out$ (for primitives with complement notations, $In$). The original CSG tree is trimmed into the first trimmed CSG tree (as short as the \emph{the first trimmed tree}) according to these common labels plus an extra label $L(M)$ whose value is obviously $Same$.

After that, the inter-primitive groups are further divided into smaller intra-primitive groups. To explain how to perform intra-primitive grouping, we firstly introduce an essential concept---intersection primitive (IP). The IPs of a face $F$ is defined as the primitives that $F$ intersects, excluding the primitive to which $F$ belongs (denoted as $M$). Primitives (excluding $M$) that do not intersect $F$ are called non-IPs. The set that contains all IPs of $F$ is the IP-set of $F$. That set can be computed by enumerating all the primitives in the cross list and coplanar list of $F$.

Now, we require that the faces of the same intra-primitive group meet two requirements: they should be connected together and have the same IP-set. These two requirements give these faces very good properties, as discussed in Proposition 1. The labels referenced in Proposition 1 are used to trim the first trimmed tree into the second trimmed CSG tree (as short as \emph{the second trimmed tree}). For a specific intra-primitive group, the primitives of its second trimmed tree is a subset of the common IP-set of that group. This is because all space labels with respect to non-IPs are shared within the intra-primitive group and all these labels are either $In$ or $Out$. Therefore, all non-IPs must have been trimmed from the CSG tree (to be explained in Section \ref{sec:trim}).

\vspace{0.8em}
\noindent \textbf{Proposition 1.}~~~~If a group of faces are connected together and they have the same IP-set, they must share the same labels with respect to all non-IPs. These labels are either \emph{In} or \emph{Out}.

\vspace{0.6em}
\noindent \textbf{Proof.}~~~~We only prove that the conclusion stands for adjacent faces, which is a special case of connected faces. Promoting the conclusion to the general situation is obvious. Assume $M$ is a non-IP and label $L(M)$ is different for the two adjacent faces $A$ and $B$ . Then there must be faces from $M$ between $A$ and $B$ to cause the different space labels. Additionally,  because $A$ and $B$ are adjacent, at least one of $A$ and $B$ intersects the faces from primitive $M$. This contradicts the assumption that $M$ is non-IP. Therefore, $L(M)$ must be the same for $A$ and $B$. Moreover, because $M$  is non-IP, $L(M)$ is either \emph{In} or \emph{Out}.

\begin{figure}
  \centering
  \includegraphics[width=3.5in]{mesh}\\
  \caption{A snapshot during flood filling (\emph{left}), and the final grouping result (\emph{right}). Different intra-primitive groups are distinguished by different colors. From the final grouping result, the whole mesh is divided into 9 intra-primitive groups.}\label{fig:mesh}
\end{figure}

\vspace{1.0em}
Because faces of the same intra-primitive group are connected together, we can efficiently group them using a flood filling algorithm. When visiting a face, its space label vector is instantly computed and its classification is performed. Our intra-level grouping is performed as follows:
\begin{itemize}[leftmargin=0.45cm]
\item[1)]{\textbf{First seed generation.}}~A triangle face $F_{S0}$ is randomly chosen as the first seed (e.g., the red triangle in Fig. \ref{fig:mesh}). Labels of $F_{S0}$ with respect to non-IPs are determined by using $F_{S0}$'s barycenter as the sample point, through a ray-shooting algorithm \cite{havran1999summary} and by employing our octree as a spatial search structure \cite{frisken2002simple} to speed up. Note that because the original CSG tree is trimmed into the first trimmed tree, we only compute labels with respect to primitives within that first trimmed tree.
\item[2)]{\textbf{Label propagation.}}~Once there is a seed $F_S$ with $L_{F_S}$ with respect to all non-IPs, we define the intra-primitive group $G_S$ as follows. All faces that belong to $G_S$ should have the same IP-set as $F_S$. The common labels of $G_S$ are $L_{F_S}$ with respect to all non-IPs. The first trimmed tree is trimmed into the second trimmed tree according to these common labels. Breadth-first flood filling is used to find all faces that belong to $G_S$. When visiting a face, we first check if it has the same IP-set as the seed. If so, set membership classification is performed based on the second trimmed tree of $G_S$ (detailed in Section \ref{section:setmemcls}). Otherwise, it is pushed into a candidate list for Step 3 (e.g., the black faces in Fig. \ref{fig:mesh} (left)).
 \item[3)]{\textbf{Secondary seed generation.}}~When the flood filling ends, which means no more faces belong to the current face group, a new seed is picked from the candidate list (e.g., the stippled faces in Fig. \ref{fig:mesh}). Then a new group is defined by the new seed and the labels with respect to non-IPs of the new seed are computed (details in Section \ref{sec:secondseed}). After that, Step 2 is repeated according to the newly defined group, until that candidate list is empty, indicating all faces of $M$ are classified.
 \end{itemize}

The face membership classification of the whole CSG is accomplished by performing the above process for each primitive. Procedure \ref{code:floodfill} shows the framework as pseudo-code. To avoid repetitive visits during flood filling, we use an extra flag for each face to record its visiting status.

\begin{algorithm}[!ht]
\caption{FaceClassification(PrimitiveList, PosTree)}
\label{code:floodfill}
    \begin{algorithmic}[1]
    \FOR {each $M_i$ in $PrimitiveList$}
    \STATE Get common labels $CL^1$ of $M_i$;
    \STATE Trim $PosTree$ into $TrimTree1$ by $CL^1$;
    \STATE Select the first seed $F_0$ from $M_i$;
    \STATE Put $F_0$ into $CandidateList$;
    \WHILE {$CandidateList$ is not empty}
    	\STATE Pick a seed $F_S$;
        \STATE Define group $G_S$, where $F_S\in G_S$;
        \STATE Compute the common labels of $F_S$, denoted as $CL^2$;
        \STATE Trim $TrimTree1$ into $TrimTree2$ according to $CL^2$;
    	\STATE Put $F_S$ into $FloodFillQueue$;
    	\WHILE {$FloodFillQueue$ is not empty}
    		\STATE Get the next face $F_i$ from $FloodFillQueue$;
    		\STATE Do set membership classification of $F_i$ based on $TrimTree2$;
    		\FOR {each adjacent face $F_{Neighbor}$}
    			\IF {$F_{Neighbor}$ belongs to $G_s$}
    				\STATE Put $F_{Neighbor}$ into $FloodFillQueue$;
    			\ELSE
                    \STATE Put $F_{Neighbor}$ into $CandidateList$;
    			\ENDIF
    		\ENDFOR
    	\ENDWHILE
    \ENDWHILE
    \ENDFOR
    \end{algorithmic}
\end{algorithm}

\subsection{Trimming CSG Tree}
\label{sec:trim}

Trimming a CSG (binary) tree with the $In$ or $Out$ label is relatively simple. According to the first two lines of Equation \ref{eq:comb}, given a primitive $M$, if $L(M)$ is $In$ ($Out$), the label of $M$'s parent node is either $In$ ($Out$) or the value of its sibling. In either condition, the node representing $M$ can be trimmed from the tree.

However, when trimming the original tree into the first trimmed tree for a specific inter-primitive group, a special label, $Same$, exists. This label means that the faces of the group are on the boundary of the primitive to which they belong, which is absolutely correct. This label is not easy to process because we cannot determine the label of its parent node unless we know the label of its sibling. Unfortunately, during tree trimming, the labels we have are incomplete. We may have to leave the $Same$ label unprocessed and wait for further information. This incurs considerable computation burden to check this special condition and makes the trimming algorithm inefficient. To solve the problems, we developed a new representation of the CSG tree, called CSGlist, to minimize the side effect of the special $Same$ label and enable early rejection of face groups that do not belong to the final model of the CSG.

Given a face group from primitive $M$, we construct the CSGlist as follows. We cut the original CSG tree into a set of subtrees along the \emph{critical path}, which is the path from $M$ to the root (e.g., when $M=D$, the construction of CSGlist is shown in Fig. \ref{fig_trim}). Obviously, none of the subtrees contains the primitive $M$. Each subtree of CSGlist is associated with `desired' label values. That is, if the labels with respect to all subtrees meet their corresponding desired values respectively, the labels with respect to the original CSG tree is $Same$. On the contrary, if the labels with respect to any subtree are not desired, the labels with respect to the whole CSG tree is not $Same$; thus the related face group should be dropped. The desired value of a subtree is determined based on how the subtree connects to the critical path. According to the face selection rules (Equation \ref{eq:select}), if the subtree connects to a Union ($\cup$) node, then the desired value is $In$; otherwise, the desired value is $Out$. In addition, suppose the primitive $A$ in Equation \ref{eq:select} is the left child. Then if the subtree is in the left child of its parent node, $Same$ is also desired.

Conversion to CSGlist is performed before the first trimming. After that, all the labels we use for CSG tree trimming are either $In$ or $Out$. Both the first and the second trimmed trees are represented by CSGlists. The subtrees of the CSGlist can be easily trimmed (since there is only $In$ and $Out$ labels) and their desired values are used to enable early rejection.

\begin{figure}[!t]
\centering
\includegraphics[width=3.0in]{csgtree}
\caption{Convert CSG tree into a CSGlist along the critical path (marked by the arrow) from primitive $D$ to the root. The CSGlist contain three subtrees. Each subtree has its desired label value. Subtree 1: $Out$ or $Same$. Subtree 2: $In$ or $Same$. Subtree 3: $Out$.}
\label{fig_trim}
\end{figure}

\subsection{Classifying a Single Face}
\label{section:setmemcls}

If a face is non-intersected, the second trimmed tree will have single value, which can be used to determine whether the face is accepted. However, if it is an intersected face, further processing is needed.

Intersected faces usually cannot be classified as a whole. They have to be tessellated into smaller non-intersected triangles, each of which is classified respectively. Robustness and efficiency are our main consideration. For these purposes, we nest the exact BSP structure \cite{bernstein2009fast, campen2010exact} into the intersected faces. We classify intersected face $F$ as follows.

\vspace{0.5em}
\noindent \textbf{Valid-IPs \& Pseudo-IPs}~~~~
IPs of an intersected face are firstly divided into two types according to whether the IPs are in the second trimmed tree. The IP that is the primitive of the second trimmed tree is called the valid intersection primitive (valid-IP). Otherwise, it is called the pseudo-intersection primitive (pseudo-IP). Pseudo-IPs intersect the face; however, the labels with respect to pseudo-IPs do not affect the classification of $F$. In other words, the intersections of pseudo-IPs are not edges of the final models, as illustrated in Fig. \ref{fig:invalidcross}. Thus, we simply omit these pseudo-intersections during classification. This filtering stage saves computation time by avoiding unnecessary splitting of faces. An extreme instance is that there is no valid-IP. For this condition, the face is processed in the same way as a non-intersected face.

\begin{figure}[!t]
\centering
\includegraphics[width=3.2in]{invalid-cross}
\caption{2D illustration of pseudo-intersection. The vertices in red do not appear in the final model. They are so called pseudo-intersection vertices (line segments in the 3D case).}
\label{fig:invalidcross}
\end{figure}

\vspace{0.5em}
\noindent \textbf{Tessellation}~~~~
In this step, $F$ is divided into a set of sub-triangles using the intersections recorded in Section \ref{section:isect}. Because constrained Delaunay triangulation (CDT) \cite{chew1989constrained} has good topology characteristics, we convert the tessellation into a problem of CDT. The zone of CDT is $F$, and the constraints are all the intersections by valid-IPs. The constraints ensure that no sub-triangles will cross these intersection lines. Because CDT in our method is a vertex-based 2D problem, the 3D coordinates computed by their plane-based representation are projected on a 2D space, which is the axis-aligned plane where the area of $F$ is maximized.

It should be noted that intersections from different valid-IPs may intersect (Fig. \ref{fig:cdt}(c)). Omitting these intersection points may cause false results of CDT. To obtain the correct constraints, intersections from different valid-IPs are tested to determine whether they intersect. We implement this test again using plane-based geometry for robustness. As we know this kind of special intersection is actually the cross point of the three faces: $F$,  and the two associated intersected faces from the valid-IPs (Fig. \ref{fig:cdt}(d)). Therefore, such a point can be represented by the three supporting planes of the three faces. We determine whether the cross point exists by testing if the point is inside all three of these faces. By adopting the routine of the relative position of a point to a plane \cite{sugihara1990solid}, this test is robust and efficient. If the cross point of different intersection lines is detected, these lines are split by the cross point and the constrains of CDT are updated accordingly. Moreover, because the cross point is actually shared by the three faces, it is added to the point lists (Section \ref{sec:isecthandle}) of all three of these faces.

\begin{figure}
\centering
\includegraphics[width=3.5in]{cdt}
\caption{We classify the face $F$ from primitive $M$: (a) faces of $M_1$ (yellow) that intersect $F$. BSP of $M_1$ is constructed according to these. (b) Faces of $M_2$ (green) that intersect $F$. BSP of $M_2$ is constructed according to them. (c) If $M_1$ and $M_2$ are the only valid-IPs of $F$, then triangulation can be performed according to intersection lines recorded in the cross list. The red area shows a possible result of sub-triangle classification. Note that there are intersections between lines from different primitives (marked as red stars), which are (d) intersections of three faces each from different primitives.}
\label{fig:cdt}
\end{figure}

\noindent \textbf{Classification of sub-triangles}~~~~
An intersected face $F$ is divided by faces from each valid-IPs into $In$ cells, $Out$ cells and $On$ cells (Figs. \ref{fig:isect}(a) and (b)). The BSP tree \cite{naylor1990merging} is very suitable for describing such partitions. The labels of sub-triangles can be efficiently computed according to a BSP representation using the BSP-based point-in-polyhedra test \cite{gordon1991front, fuchs80visible, james1999binary}. Details are discussed as follows.

Given a valid-IP, denoted as $M$, we firstly build a BSP tree nested within $F$ according to the intersections between $F$ and $M$. This is a 2D partition problem. Nevertheless, constructing BSP in 2D space of $F$ will introduce errors on account of the involved conversion from plane triples (plane-based representation) into 2D coordinates. Therefore, it is better to construct the BSP tree in 3D space. If we limit the space of the BSP construction zone within the face $F$ with tiny thickness, denoted as $P_F$, it is obvious that all faces from $M$ that intersect $P_F$ are recorded in the cross list and the coplanar list of $F$. These faces give the correct space partition on $P_F$. We construct the 3D BSP tree according to the intersected faces. The construction of the BSP tree is implemented using an exact plane-based algorithm proposed by Berstein and Fussell \cite{bernstein2009fast}. Now, given a sub-triangle $SF$, the label $L_{SF}(M)$ is then computed based on the classification results of the three corners of $SF$ according to the constructed BSP. If all three classification results are $On$, then $L_{SF}(M)$ is either $Same$ or $Oppo$. If any classification of the corners is not $On$, $L_{SF}(M)$  is the same as the non-$On$ classification .

After all space labels of a sub-triangle are computed, we judge whether the sub-triangle belongs to the final model based on the second trimmed tree represented as CSGlist. The subtrees in CSGlist are evaluated using the combination rules of labels. The sub-triangle is accepted if and only if the evaluation results of all subtrees are desired. We might accelerate this step if the coplanar list of $F $is empty or the faces in the coplanar list are all from pseudo-IPs. In this case, the labels with respect to valid-IPs are either $In$ or $Out$, and each subtree of CSGlist can be efficiently evaluated using Blist, which was proposed by Hable and Rossignac \cite{hable2005blister}. For CSG models in which the coplanar cases are rare, this acceleration saves considerable computation time.

\subsection{Secondary Seeds Generation}

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=2.0in]{sgen}\\
  \caption{$F_x$ is the secondary seed, and $F_c$ is its associated face. The labels of $F_x$ with respect to primitives that intersect $F_c$ but do not intersect $F_x$ (e.g., the yellow intersection) can be computed using any point in $E_{x,c}$ as the sample. The labels of $F_x$ with respect to primitives that intersect neither $F_x$ nor $F_c$ are the same for both faces. Line segments of different colors are intersection lines by different primitives.}\label{fig:sgen}
\end{figure}

\label{sec:secondseed}

As discussed in Section \ref{sec:framework}, during flood filling, faces belonging to the group of the current seed are classified according to the second trimmed tree of this group. The rest are added to a candidate list for generating secondary seeds when no more faces belong to the group of the current seed. The main task of secondary seed generation is to compute the space labels with respect to non-IPs of the new seeds.

A straightforward scheme is to use the same approach as the first seed generation in Section \ref{sec:framework}. However, this scheme requires  recalculating all the space labels with respect to non-IPs using the time-consuming ray-shooting method. For complex CSG evaluation, in which secondary seed generation is frequently requested , we need a more efficient solution. Again, we use the information of neighboring faces to accelerate this process. When a face $F_x$ is added to the candidate list, we associate the following data with $F_x$: the face $F_c$ that is currently being visited (therefore $F_x$'s neighbor; see Fig. \ref{fig:sgen}) and the labels of $F_c$ with respect to $F_c$'s non-IPs. Note that the non-IP set of $F_x$, denoted as $C_x$, is different from that of $F_c$, denoted as $C_c$.

Now, if $F_x$ is selected as a new secondary seed, we can compute the labels with respect to non-IPs of $F_x$ in two complementary ways: we can directly inherit from the labels of $F_c$, or represent $F_x$ with a point within $F_c$ and compute the label of this point using the BSP technique presented in Section \ref{section:setmemcls}. The former is used for the computation of the labels with respect to the primitives that are in $C_c\cap C_x$. The labels with respect to these primitives are the same for both $F_x$ and $F_c$. The latter is used for computing the labels with respect to the remaining of primitives (e.g., those in $C_c\setminus C_x$). According to Proposition 2, the sample point of $F_x$ can be chosen as any point in the common edge of $F_x$ and $F_c$, denoted as $E_{x,c}$. For robustness, we use one of the end points of $E_{x,c}$ as the sample point because we have its exact plane-based representation.

\vspace{+1.0em}
\noindent \textbf{Proposition 2.}~~~~Given two adjacent faces $F_c$ and $F_x$, the labels with respect to primitive $M$ for $F_x$ is the same as the classification result of any point on the common edge of $F_x$ and $F_c$ in the BSP tree of $M$ for $F_c$ (constructed in Section \ref{section:setmemcls}), if $M$ is in the IP-set of $F_c$ but not in the IP-set of $F_x$.
\vspace{+0.5em}

\noindent \textbf{Proof.}~~~~We know $M$ is not in the IP-set of $F_x$; therefore, it is obvious that all points on $F_x$ have the same labels with respect to $M$. Because the points on the common edge of $F_x$ and $F_c$ are in $F_x$, they have the same labels.
\vspace{+1.0em}

\section{Experiments and Discussion}

\begin{figure}[!t]
\centering
\includegraphics[width=3.2in]{raster}
\caption{\emph{Cube} $\cup$ \emph{Sphere1} $\cap$ \emph{Sphere2}: our method resulted in simpler mesh connectivity than the method by Campen and Kobbelt \cite{campen2010exact}.}
\label{fig:raster}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{budda}
\caption{Boolean operations on model \emph{Budda}: (a) two \emph{Buddas}, (b) results of \emph{Budda} $\cap$ \emph{Budda}, and (c) the incorrect result of \emph{Budda} $\cap$ \emph{Budda} generated by non-robust implementation of Feito et al.'s method \cite{feito2013fast}.}
\label{fig:budda}
\end{figure}

\begin{figure*}[!t]
\centering
\includegraphics[width=7in]{models2}
\caption{(a) Boolean operations between a \emph{Ring} and a set of \emph{Spheres}. $\langle 1\rangle$ after 200 operations. $\langle 2\rangle$ after 800 operations. (b) Union of \emph{Armadillo} and six \emph{Spoons}. (c) \emph{Head} - \emph{Cuboid} + \emph{LeftBrain} + \emph{RightBrain}. (d) Difference a \emph{BigCylinder} and 28 \emph{SmallCylinders}. (e) \emph{Man} $\cup$ \emph{Horse}. (f) \emph{Dragon} - \emph{Bunny}. (g) \emph{Palate} $\cup$ \emph{Mandible} $\cup$ (20 \emph{Teeth}).}
\label{fig:models}
\end{figure*}

\begin{table*}[ht]
\caption{Computation Time Statistics (Seconds)}
\label{tab:performance}
\centering
\begin{tabular}{*{13}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
\hline
\multirow{2}{*}{No.} & \multirow{2}{*}{Figure} & \multicolumn{3}{c|}{Face Num.$^\nabla$} & \multirow{2}{*}{\tabincell{c}{Primitive\\Num.}} & \multirow{2}{*}{\tabincell{c}{CGAL \\ \cite{cgal:hk-bonp3-15a}}} & \multirow{2}{*}{\tabincell{c}{Maya \\ \cite{Maya2015}}} & \multirow{2}{*}{\tabincell{c}{Campen \\ \cite{campen2010exact}}} & \multirow{2}{*}{\tabincell{c}{Feito \\ \cite{feito2013fast}}}& \multicolumn{4}{c}{Our Approach}\\
\cline{3-5} \cline{11-14}
 & & Total & Min & Max &&&&&& Total$^\circ$ & Step 1 & Step 2 & Step 3\\
\hline \hline
1 & \ref{fig:models}(a) & 37.6K & 180 & 1.6K & 201 & 1350 & 49.9 & TLE$^{\dag}$ & 15.9 & \textbf{3.13}  & 0.328 & 1.69 & 0.922 \\
2 & \ref{fig:models}(a) & 146K & 180 & 1.6K & 801  & TLE & 1400 & TLE & Fail* & \textbf{12.8}  & 1.36 & 6.41 & 4.00 \\
3 & \ref{fig:models}(b) & 377K & 2.56K & 346K & 7 & TLE & 224.5 & 45.7 & 11.7 & \textbf{1.44} & 0.438 & 0.062 & 0.563 \\
4 & \ref{fig:models}(c) & 79.2K & 12 & 38.2K & 4  & 97.6 & Fail & 3.58 & 1.69 & \textbf{0.563}  & 0.187 & 0.141 & 0.172 \\
5 & \ref{fig:models}(d) & 36K & 800 & 2.4K & 29 & 34.1 & 7.03 & 18.7 & 4.05 & \textbf{0.313} & 0.094 & 0.094 & 0.081 \\
6 & \ref{fig:models}(e) & 597K & 96.9K & 500K & 2 & TLE & 38.3 & 26.4 & 5.63 & \textbf{2.13} & 0.563 & 0.031 & 0.984 \\
7 & \ref{fig:models}(f) & 170K & 69.7K & 100K & 2  & 218 & 7.45 & 13.8 & 2.39 & \textbf{0.891} & 0.328 & 0.125 & 0.266 \\
8 & \ref{fig:models}(g) & 362K & 6.91K & 276K & 22 & TLE & 344 & 256 & 19.2 & \textbf{1.80} & 0.766 & 0.172 & 0.593 \\
9 & \ref{fig:budda} & 2.16M & 1.08M & 1.08M & 2 & Fail & Fail & MLE$^\bullet$ & Fail & \textbf{11.3} & 5.55 & 1.36 & 3.01 \\
\hline
\end{tabular}
\begin{flushleft}
$^{\nabla}$~~\emph{Min} (\emph{Max}) means the minimum (maximum) number of faces of a single primitive.

$^{\circ}$~~The total computation time of our method includes the construction of half-edge structure and the three steps in Section \ref{sec:overview}.

* ~~\emph{Fail} means nothing was returned, or we received the wrong evaluation results from the programs.

$^{\dag}$~~\emph{TLE} means the processing time was more than  2,000 s.

$^\bullet$~~\emph{MLE} denotes that the program was out of memory. The memory limit for our implementation of Campen et al.'s approach was around 1.2GB.

\end{flushleft}
\end{table*}

\begin{table}
\caption{Number of Primitives and Computation Time (Seconds)}
\label{tab:linear}
\centering
\begin{tabular}{*{4}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
\hline
Number of Spheres & ~~100~~ & ~~200~~ & ~~300~~ & ~~400~~ \\
\hline
\hline
Our Approach & \textbf{1.38} & \textbf{2.89} & \textbf{4.39 }& \textbf{5.97} \\
Maya \cite{Maya2015} & 17.4 & 53.4 & 124 & 241 \\
CGAL \cite{cgal:hk-bonp3-15a} & 439 & 1350 & - & -\\
Feito \cite{feito2013fast} & 5.20 & 15.9 & 30.4 & -\\
\hline
\hline
Number of Spheres  & 500 & 600 & 700 & 800 \\
\hline
\hline
Our Approach & \textbf{7.90} & \textbf{9.49} & \textbf{11.0} & \textbf{12.8}\\
Maya \cite{Maya2015} & 407 & 628 & 966 & 1400\\
CGAL \cite{cgal:hk-bonp3-15a}& - & - & - & -\\
Feito \cite{feito2013fast}& - & - & - & -\\
\hline
\end{tabular}
\begin{flushleft}
*~~This table was the computation time of the evaluation for Fig. \ref{fig:models} (a).
\end{flushleft}
\end{table}

\iffalse
\begin{table}
\caption{Relations between Number of Operations and Computation Time (Millie Second)}
\label{tab:subdivide}
\centering
\begin{tabular}{*{4}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
\hline
~~Face Number~~ & Step 1 & Step 2 & Step 3 & ~Total~ \\
\hline
\hline
~~1.7K~~ & 6 & 12 & 15 & 37\\
~~16K~~ & 50 & 37 & 51 & 153\\
~~140K~~ & 302 & 121 & 249 & 790\\
~~1300K~~ & 2006 & 372& 1508 & 4902\\
\hline
\end{tabular}
\begin{flushleft}
\end{flushleft}
\end{table}
\fi

We implemented the proposed method in C++ and tested a series of examples with numerous primitives and/or faces on a consumer laptop with an Intel i5-4200D processor at 1.5GHz and with 8 GB of RAM. The OpenMesh library \cite{OpenMesh} is used for storing triangle meshes and supporting the query of neighboring faces. Tessellation of critical triangles is performed by constrained Delaunay triangulation using the Fade2D library \cite{Fade2D}.

We compared four state-of-the-art Boolean evaluation techniques, including CGAL \cite{cgal:hk-bonp3-15a}, Maya 2015 \cite{Maya2015}, the method proposed by Campen and Kobbelt \cite{campen2010exact}, and the approach proposed by Feito et al. \cite{feito2013fast}. The latter two methods used localized schemes. Table \ref{tab:performance} shows the comparison in terms of computing time. It can be easily to seen that our approach was efficient in all these examples. Feito et al.'s method had performance relatively similar to ours for the examples with a  single Boolean operation (Examples 6, 7). This is because both the approaches use a face-based grouping scheme to accelerate face membership classification; thus have similar pipelines for single Boolean operations. However, when the number of primitives grows, the advantage of our non-incremental CSG evaluation approach becomes more obvious. In the examples of more than two primitives, our method is much faster than any other methods. In particular, our method worked out example 2 which consisted of 801 primitives, in 15 s, which was more than 100 times faster than the Boolean evaluation in Maya.

Among the three main steps of our approach, the first step of the octree construction is a typical $O(n~log~n)$ algorithm, where $n$ is the total number of faces in the CSG. The second step of intersection computation is only performed within critical octree cells. The number of critical cells is often linear to the number of intersected faces $k$ (often an $O(\sqrt{n})$ number) in the CSG. Therefore, the computation complexity of the second step is almost $O(k)$. The condition of the third step of face membership classification is more complex. Although the flood filling algorithm used for intra-primitive grouping is $O(n)$ complex, classifying an intersected faces could consume much more time than classifying a non-intersected faces. Therefore, if we assume classifying an intersected faces spends $\theta$ times of computation time to classify a non-intersected face, we may generalize the time complexity of this step as $O(n+\theta\cdot k)$. When $k/n$ is constant, the third step is $O(n)$ complex.

To further validate that our approach is efficient for non-incremental CSG evaluation, we analyzed how the computation time changes with respect to the number of primitives. Table \ref{tab:linear} shows the evaluation time for Fig. \ref{fig:models} (a), which was a CSG consisting of a ring and hundreds of identical spheres. We changed the number of spheres from 100 to 800 and recorded the evaluation times. In this condition, the $k/n$ was relatively constant, and as there are many intersected faces, the bottleneck lies in Step 2 and Step 3. The result shows that the computation time of our algorithm had a linear behavior, which conforms to our previous discussion. The computation time of other incremental approaches rapidly increased when the number of primitives increased, sometimes showing an $O(n^2)$ behavior. This is because for those approaches, as more spheres were added to or subtracted from the ring, the mesh of the ring became more complex, which made it more difficult to perform subsequent Boolean operations.

One possible problem of a non-incremental CSG evaluation approach is memory inefficiency. Unlike incremental ones, non-incremental approaches (including ours) often require loading all the primitives into the memory before the evaluation. Fortunately, our approach does not significantly suffer from such a problem. Our implementation only constructs an octree, which needs typically an $O(n~log~n)$ size data structure, and some auxiliary information of intersected faces, which is usually $O(k)$ size. According to our experiment, our approach performed full evaluations in Table \ref{tab:performance} with less than 600MB. On the contrary, some incremental approaches can be very memory inefficient. For instance, in the evaluation of Example 6, CGAL consumed more than 6 GB of memory. Furthermore, in the evaluation of Example 2, which contained only 146 K faces, Maya 2015 used at least 5 GB of memory.

Our method is robust and could correctly evaluate all the examples in Table \ref{tab:performance}. On the other hand, it is evident that the commercial software Maya could not even correctly evaluate Example 4, which contained only 38.6 k faces and four primitives. CGAL gave warnings when evaluating Example 9 and finally terminated without offering a result. Our implementation of Feito et al's method gave an incorrect result for Example 9 (Fig. \ref{fig:budda}(c)) and a result rife with small holes for Example 2.

Topology simplicity is another significant characteristic of the quality of CSG evaluation. As shown in Fig. \ref{fig:raster}, our method led to less triangles to represent the final model than Campen et al.'s method without stages for surface merging. A simpler topology is preferred because it is easier to process. In fact, we found that it was owing to such inefficient tessellation that Campen et al.'s method took so long time to evaluate Examples 1 and 2. After hundreds of Boolean operations, the resulting surface became so fragmented that it could take tens of seconds to perform a single Boolean operation.

\noindent \textbf{Limitations \& Future work}~~~~
The major limitation of our method is that it is not unconditionally robust. Because the tessellation of intersected faces is performed using vertex-based representation, the computed vertex coordinates may shift from their real location, which may lead to incorrect tessellation in theory. From our tests, we have not found the visible failures caused by this problem, because that the coordinate errors in most cases are small without visible incorrect tessellation,  we will investigate to integrate plane-based geometry computation into intersected face tessellation in the future work.

\section{Conclusion}
In this paper, we proposed a novel method to evaluate CSG with triangular mesh primitives. It is able to efficiently perform non-incremental evaluation of large CSG with massive faces. The key idea of our approach is to use the local coherence of face space labels to accelerate face membership classification. A two-level grouping framework is developed to group neighboring faces together and thus space labels can be shared within each group. This scheme saves much time for space label computation, which is often very time-consuming for conventional Boolean evaluation algorithms. Additionally, in order to be robust, plane-based geometry computation is introduced into the intersection computation step of our approach. Experiments have verified the proposed approach is more efficient than the state-of-the-art techniques while retaining robustness and stability. We will further investigate the robust tessellation in future.

\appendices

%\newpage
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,citation}

%\newpage

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{rui}}]{Rui Wang}
is currently a postgraduate student at the Department of Computer Science and Technology, the Shanghai Jiao Tong University. His main research interests include real-time computer graphics and virtual reality applications.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{xudong}}]{Xudong Jiang}
received his Master degree in Computer Science from Shanghai Jiao Tong University in 2014. He is currently working in Autodesk China Research \& Development Center. His research interest includes computer-aided geometric design and solid modeling.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{hongbo}}]{Hongbu Fu}
is an Associate Professor in the School of Creative Media, City University of Hong Kong. He received the PhD degree in computer science from the Hong Kong University of Science and Technology in 2007 and the BS degree in information sciences from Peking University, China, in 2002. His primary research interests fall in the fields of computer graphics and human computer interaction. He has served as an associate editor of The Visual Computer, Computers \& Graphics, and Computer Graphics Forum.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{sheng}}]{Bin Sheng}
received his BS degree in computer science from Huazhong University of Science and Technology in 2004, MS degree in software engineering from University of Macau in 2007, and PhD Degree in computer science from The Chinese University of Hong Kong in 2011. He is currently an associate professor in the Department of Computer Science and Engineering at Shanghai Jiao Tong University. His research interests include virtual reality, computer graphics, and image-based techniques.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{wu}}]{Enhua Wu}
received the BS degree from Tsinghua University in 1970, and the PhD degree from the University of Manchester (UK) in 1984. He is currently a research professor at the Institute of Software, Chinese Academy of Sciences, and Fellow of China Computer Federation. He has also been teaching at the University of Macau since 1997, where he is currently an Emeritus Professor. His research interests include realistic image synthesis, virtual reality, and scientific visualization. He has served as an associate editor of The Visual Computer, Computer Animation and Virtual Worlds.
\end{IEEEbiography}

\end{document}

### 2016-05-09 paper.tex
change to work office

--- 2016-05-09 newpaper.tex
@@
 
-\usepackage{color}
-
 % correct bad hyphenation here
@@
 \begin{abstract}
+  In this paper, we propose an efficient non-incremental approach to evaluate the boundary of constructive solid geometry (CSG).
+The face membership classification step is a bottleneck in many existing CSG evaluation approaches.
+The key idea of our approach is to use local coherence of space labels to accelerate this step.
+We employ a two-level grouping scheme to group faces that share the same space labels.
+Therefore, these common space labels can be shared within each group to avoid repetitive computation.
+Our method is optimized for a non-incremental evaluation.
+It generates the entire result model at once, rather than performing a step-by-step evaluation of Boolean operations.
+To achieve a robust evaluation, our approach introduces plane-based geometry into the intersection computation step.
+Comparison experiments with state-of-the-art techniques show that our method can more efficiently perform boundary evaluation of both trivial and complicated CSG with massive faces while maintaining robustness.
 \end{abstract}
@@
 It constructs complex models by combining primitives using a series of regularized Boolean operations \cite{requicha1977mathematical}: union, intersection and difference.
-CSG is often represented by a binary tree, called a CSG tree, whose leaves are primitives and whose internal nodes are Boolean operations.
-\newline
-
-{\color{red}{
-Main Contribution:
-
-1.
-We develop a united representation of intersection lines between CSG primitives.
-Under this representation, Face re-tessellation and classification can be done robustly in any degenerate cases by our pipeline, while keeping good performance.
-
-2.
-Unlike any of the previous method, during the algorithm, we conduct point-in-polyhedron tests only on single seed vertex.
-We develop a propagating to spread the classification information from the seed vertex into the whole CSG.
-In addition, because of this, we do not need to build a full space division to accelerate point-in-polyhedron tests, which is usually time-consuming.
-}}
+CSG is often represented by a binary tree, called a CSG tree, whose leaves are primitives and whose internal nodes are Boolean operations..
+
+CSG can be converted into the widely-used  boundary representation (i.e., triangle mesh) through boundary evaluation.
+Most boundary evaluation methods are based first on intersection computation and then on face membership classification.
+Robustness and efficiency are their major issues.
+During the last three decades, many techniques have been developed to solve these problems.
+However, the efficiency of face membership classification still needs improvement.
+
+Computing face space labels is the basis of face classification with respect to CSG.
+For each face, the number of space labels to be computed is equal to the number of primitives.
+For large CSG with massive faces and primitives, computing these space labels can be very time-intensive.
+A common acceleration method is to use localized schemes.
+This method is based on the local coherence of space labels: if a face is inside (or outside) a specific primitive, the face's neighborhoods are likewise often inside (or outside) the primitive.
+Determining whether two adjacent faces share the same space labels is relatively simple (see also Section \ref{sec:framework}); therefore, we can locally group together faces of the same labels and reuse space labels to save computation.
+
+\begin{figure}
+  \centering
+  % Requires \usepackage{graphicx}
+  \includegraphics[width=3.5in]{cluster}\\
+  \caption{2D illustration of grouping schemes.
+The boundaries of polygons are edges.
+Suppose each input mesh consists of hundreds of edges (not shown in the figure).
+Edges are grouped using (a) voxels, (b) octree cells, and (c) edges as the grouping units.
+Different groups in (c) are marked by different colors.} \label{fig:cluster}
+\end{figure}
+
+Several recent studies \cite{campen2010exact, pavic2010hybrid, wang2011approximate} have used such localized schemes.
+These approaches often use the cube (e.g., voxels, octree cells) as the basic grouping unit to reuse the space division data structures constructed during the intersection computation.
+However, using the cube as a basic grouping unit has several disadvantages.
+In general, connected faces with the same space labels should be grouped together.
+Thus, an ideal face group is a union of connected faces and can be of any shape.
+The cube-based grouping scheme can only provide a rough approximation of that shape.
+Therefore, extra computation, which is usually time-consuming, is needed to classify those ungrouped faces.
+For example, in Figs.
+\ref{fig:cluster}(a) and (b), the red cubes contain the intersection of two primitives.
+Thus, the edges (faces in 3D) in these red cubes should belong to different groups (because they have different labels).
+However, the size of cubes cannot be illimitably small to distinguish these different groups.
+Therefore, these edges in the red cubes are left as ungrouped edges.
+In contrast, a face-based grouping scheme can easily handle groups of arbitrary shapes and is potentially more efficient for face classification (Fig.
+\ref{fig:cluster}(c)).
+
+Another limitation of prior exact evaluation algorithms is that most of them are incremental ones \cite{campen2010exact, feito2013fast, bernstein2009fast}.
+This means that they can evaluate only one Boolean operation at a time.
+For a large CSG tree with more than two primitives, incremental algorithms have to decompose the CSG into a series of Boolean operations and then incrementally evaluate each one.
+This strategy is highly inefficient because it unnecessarily computes the CSG intermediate results.
+Incremental algorithms have been more popular for a considerable time because human designers typically construct CSG models by progressively adding primitives.
+However, recent techniques---such as GPU-based approximate evaluation algorithms \cite{pavic2010hybrid, wang2011approximate} and CSG visualization algorithms \cite{hable2007cst, rossignac2011ordered}---are more suitable for such a preview computation.
+Therefore, exact evaluation algorithms are now more likely to be used for final mesh generation (after all the primitives are added), where a non-incremental algorithm has more advantages.
+
+In this paper, we propose a method to perform CSG boundary evaluation with triangular mesh primitives.
+The proposed method uses the face (i.e., a triangle in our implementation) as the basic unit of the grouping and applies a flood-filling algorithm to group faces.
+Our method utilizes the local coherence of space labels.
+It propagates face space labels between adjacent faces and adjacent groups to save computation of space labels.
+The most prominent characteristics of our method are outlined below.
+\vspace{0.0em}
+\begin{itemize}[leftmargin=*]
+  \item{\textbf{Face classification using two-level grouping}}~~~~To efficiently classify faces, we use a two-level grouping scheme to reuse space labels.
+Input faces are firstly grouped into first-level groups at the primitive level; then, the first-level groups are further divided into second-level groups according to their labels (Fig.
+\ref{fig_overview}(d)).
+A flood-filling algorithm is applied to enable efficient grouping and label sharing among adjacent faces.
+This framework makes a balance between the benefit of face label sharing and the cost of grouping faces for the best performance.
+
+  \vspace{0.5em}
+  \item{\textbf{Efficient non-incremental evaluation}}~~~~Unlike many existing Boolean methods \cite{granados2003boolean, bernstein2009fast, campen2010exact, feito2013fast}, the proposed method can perform non-incremental evaluation of CSG, which computes the entire final model directly.
+Our approach is more efficient at evaluating large CSGs because it computes no intermediate results in the internal nodes of CSG trees.
+A non-incremental evaluation is more difficult to perform because the conditions of the intersection and face classification are more complicated.
+We developed a set of techniques, including face-nested binary space partitioning (BSP) and multi-level CSG trimming, to make our method highly efficient for non-incremental evaluation.
+
+  \vspace{0.5em}
+  \item{\textbf{Robustness and exactness}}~~~~In the field of solid modeling, efficiency without robustness is impractical.
+We therefore adopt a series of schemes to make our method robust.
+To avoid the introduction of errors during intersection computation, we combine a triangle-triangle intersection algorithm \cite{moller1997fast} with a plane-based representation \cite{sugihara1990solid}.
+In addition, an exact BSP construction technique \cite{bernstein2009fast, campen2010exact} is adopted to enhance the robustness of face classification.
+\end{itemize}
+\vspace{0.5em}
+
+Experiments performed confirm that our method is more efficient than state-of-the-art techniques \cite{cgal:hk-bonp3-15a, campen2010exact, feito2013fast, Maya2015}.
+It can quickly and robustly perform CSG evaluations not only for trivial CSGs, such as one with single Boolean operation, but also for large CSGs with hundreds of primitives.
 
@@
 
-\subsection{United Representation of Intersection Construction}
+\subsection{Plane-based Intersection Computation}
 \label{sec:overview:isect}
 
-\subsection{Multilevel Flood-filling Classification}
-
-\section{United Representation of Primitive Intersection}
-{\color{red}{
-Primitive intersects primitive, generating intersection line segments (Fig. \ref{fig_raw1}).
-
-\begin{figure}
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=3.5in]{raw1}\\
-  \caption{triangle contains intersection lines, two-primitive case}\label{fig_raw1}
-\end{figure}
-
-Considering degenerate cases in n-primitives CSG can be very complex (Fig. \ref{fig_raw2}).
-
-\begin{figure}
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=3.5in]{raw2}\\
-  \caption{triangle contains intersection lines, n-primitives degenerate cases}\label{fig_raw2}
-\end{figure}
-
-We converted it into a united representation, making it clear and easy to process by the following process (Fig. \ref{fig_raw3}).
-
-\begin{figure}
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=3.5in]{raw3}\\
-  \caption{triangle contains intersection lines, n-primitives degenerate cases, using united representation}\label{fig_raw3}
-\end{figure}
-}}
-
-\subsection{Plane-based Triangle Intersection}
-
-{\color{red}{why using triangle intersection, rather than edge-face based, etc. --- for coplanar test.}}
-\newline\newline
+In this step, we compute all intersections between primitives and record them in intersected faces (e.g., the red triangles in Fig.
+\ref{fig_overview}(c)) for further computation.
+Because we have already constructed the octree and obtained its cell classification, it is instantly known that intersection between faces occurs only within critical cells.
+Thus, we limit the intersection test within these critical cells.
+The intersection test is performed for every pair of faces in each critical cell.
+We assume that primitives are not self-intersected; therefore, tests for faces from the same primitives are unnecessary.
+
+The triangle-triangle intersection test always incurs robustness issues.
+To avoid an unexpected failure caused by numeric errors, we integrate a plane-based representation of polyhedra \cite{sugihara1990solid} into the triangle-triangle intersection test.
+Adaptive precision predicate technique \cite{shewchuk1997adaptive} is applied for efficiency of plane-based geometry computation.
+Details are provided in Section \ref{section:isect}.
+
+\subsection{Face Classification Using Two-level Grouping}
+
+Face classification using two-level grouping is the most novel step of our algorithm.
+For each primitive face, we must determine whether it, or its part (when the face intersects with other faces), belongs to the final model.
+A breadth-first flood-filling algorithm is used to traverse faces of each primitive.
+Starting from a random seed whose space labels are all computed, these labels propagate to neighboring faces and vary according to intersection conditions (Fig.
+\ref{fig_overview}(d)).
+Each face is instantly classified once all of its space labels are computed.
+We use a two-level face grouping scheme to enable the maximum information reuse.
+The first level is the \emph{inter-primitive} level; the second is the \emph{intra-primitive} level.
+When visiting an intersected face, constrained Delaunay triangulation \cite{chew1989constrained} is applied to subdivide the face into smaller triangles, followed by individual classification of the subdivided triangles using BSP techniques.
+The robustness of this step is ensured by the exact BSP computation technique \cite{bernstein2009fast}.
+Details are shown in Section \ref{section:floodfill}.
+
+\section{Plane-based Intersection Computation}
+
+\label{section:isect}
+
+In this step, intersections between faces are computed through the triangle-triangle intersection test within each critical cell.
+We adopt M\"{o}ller's intersection detection algorithm \cite{moller1997fast} for this test on account of the algorithm's efficiency and simplicity.
+However, because collision detection algorithms are often accompanied by non-robustness problems, a conventional implementation of the algorithm may cause unpredictable results.
+Therefore, we integrate plane-based geometry representation \cite{sugihara1990solid} into M\"{o}ller's algorithm to make it unconditionally precise and robust.
+
+\subsection{Intersection Detection}
 
@@
 
-\subsection{Generating United Representation}
-
-{\color{red}{Mainly deal with intersection between intersection line segments.}}
-
-\section{Multi-level Flood-filling Classification}
+\subsection{Intersection Recording}
+\label{sec:isecthandle}
+
+The information of intersection is stored in the intersected faces where the intersection occurs.
+Because the intersection is generated by two (or more) faces, both (all) faces are intersected faces and store the same copy of intersection information.
+
+Each intersected face maintains two important lists for further processing: \emph{cross list} and \emph{coplanar list}.
+The cross list stores the end points of intersections, the associated faces of the intersections, and the primitives to which these associated faces belong.
+The coplanar list is relatively simple.
+It only stores coplanar faces and the primitives to which these coplanar faces belong.
+
+Moreover, in order to reconstruct geometry connectivity and to avoid coincident vertices in the final model, coincident points detected during intersection computation are merged.
+A \emph{point list} for each intersected face $F$ is used for this purpose.
+The list stores all the points inside $F$ or on the boundary of $F$.
+When introducing new vertices into the face (e.g., recording the new intersection line into the cross list, the two end points of the intersection line segment are newly introduced vertices), we determine if there exists a coincident point in the point list.
+Coincident points are merged.
+In addition, because the points on the edges of $F$ are shared by adjacent faces, these points should be added to the corresponding point lists of both two adjacent faces.
+
+There is a degenerate condition for intersection recording: $F_1$ and $F_2$ may intersect on a single point.
+We treat this condition as $F_1$ and $F_2$ being non-intersecting but add the intersected point into the point lists of both faces.
+Another point to notice is that if $F_1$ and $F_2$ are coplanar and overlap, $F_1$ is added to the coplanar list of $F_2$ and vice versa.
+No new point is introduced under this condition.
+
+\section{Face Classification}
 \label{section:floodfill}
-
-{\color{red}{Flood-filling is all about giving a seed and propagation. In this chapter, from down to top, we introduce this process and explain how it can save computation time.}}
 

### 2016-05-09 summary.tex
change to work office

--- 2016-05-09 newpaper.tex
@@
 \IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
-\IEEEPARstart{C}{onstructive} solid geometry (CSG) has long been a popular modeling tool of computer-aided design and computer-aided manufacturing (CAD/CAM).
-It constructs complex models by combining primitives using a series of regularized Boolean operations \cite{requicha1977mathematical}: union, intersection and difference.
-CSG is often represented by a binary tree, called a CSG tree, whose leaves are primitives and whose internal nodes are Boolean operations.
-\newline
 
-{\color{red}{
 Main Contribution:
@@
 In addition, because of this, we do not need to build a full space division to accelerate point-in-polyhedron tests, which is usually time-consuming.
-}}
 
@@
 
+\section{Background}
+
+\subsection{Plane-based geometry}
+
+\subsection{CSG evaluation}
+
+\section{Overview}
+费大幅度发
+\label{sec:overview}
+
+\iffalse
 \begin{figure*}[!t]
@@
 \includegraphics[width=7.1in]{flowchart}
-\caption{An overview of the proposed method for CSG evaluation.
-In this toy example, the CSG tree represents a solid constructed by (Cube $\cup$ Sphere - Cylinder).
-(d) shows how to classify faces step by step using a flood filling algorithm.
-Faces of the same primitive are grouped as the inter-primitive group.
-Then faces of the same inter-primitive group are further divided into intra-primitive groups according to their conditions of intersection (c).
-The unvisited faces are black.
-Different colors of other faces indicate that they are accepted and belong to different intra-primitive groups.
-Rejected faces are rendered with wire-frame.
-The seed face of flood filling in each primitive is highlighted in red.}
+\caption{}
 \label{fig_overview}
 \end{figure*}
+\fi
 
-CSG evaluation has had notorious problems with robustness since its inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}.
-The non-robustness is inherited from the building blocks of CSG: Boolean operations on solids.
-Many researchers have attempted to solve such an issue using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}.
-However, these methods are often too expensive in computation time and memory to be practical for evaluation of CSG with massive faces.
-For example, in the Computational Geometry Algorithms Library (CGAL) \cite{cgal:hk-bonp3-15a}, the state-of-the-art robust Boolean operation algorithm \cite{hachenberger2005boolean} (implemented with arbitrary precision arithmetic) is more than 20 times slower than its non-robust version.
+Our method follows the paradigm of two-step Boolean operation---intersection detection and facet classification, together with an extra step of pre-computation to accelerate the intersection detection.
+The main feature of our method is that we design a unified representation of intersection between primitives (U-rep) to control the complexity of intersection detection result and simplify the facet classification.
+Also, plane-based representation is applied throughout the methods to ensure no error introduced.
+For the same reason, we compute indicator vectors of vertices rather than of the barycenter of facets during classification and deduce the facets' indicator vectors from its vertices'.
 
-Sugihara and Iri \cite{sugihara1990solid} introduced a plane-based representation of polyhedra.
-They found that Boolean operations are fundamentally robust using the plane equation as the primary geometry representation.
-In this condition, the evaluation of Boolean operations can be performed with no `constructions' \cite{shewchuk1999lecture}, thereby avoiding the introduction of any numerical errors.
+\subsection{Space division}
 
-Berstein and Fussell \cite{bernstein2009fast} noted that a binary space partitioning (BSP) merging algorithm in Boolean operations \cite{thibault1987set, naylor1990merging} is actually a plane-based technique.
-Therefore, they combined the two conceptions---plane-based geometry and BSP merging---to develop an unconditionally robust method for Boolean operations of polyhedra.
-Using Shewchuk's adaptive geometry predicate technique \cite{shewchuk1997adaptive}, this method can be only twice slower than non-robust methods.
-Our approach adopts this technique in the stage of face classification to ensure the robustness.
+This step is the mainly the preparation for intersection detection.
+As intersection detection is performed between each pair of faces, localization is necessary for acceleration by filtering invalid pairs.
+In general, any space division data structure can be applied in this stage.
+For simplicity, our method uses the adaptive octree.
+The implementation is akin to the implementation in ??
+et al.'s method \cite{feito2015fast}.
+Intersection between triangle faces and octree leaves can be efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}.
+Octree leaves are classified into two types: if all faces that intersect a leaf belong to the same primitive, we call it a \emph{non-critical cell}.
+Otherwise, it is a \emph{critical cell}.
+The big difference between our construction method and ??'s is the subdivision termination condition.
+In ??'s method,??.
+However, in our method, we do not need subdivide any non-critical cell no matter how many faces it contains.
+This is because subdividing non-critical cells benefits only the polyhedron inclusion test, which is frequently used in ??'s method but rarely in ours.
+This simplification can bring large performance advantage, especially for those cases whose intersection areas are small.
 
-Berstein and Fussell's method does not alleviate the problem of high memory consumption of BSP-based algorithms.
-Thus, it remains unprepared for polyhedra with massive faces.
-However, it inspired Campen and Kobbelt to develop a more delicate approach  \cite{campen2010exact}.
-This approach solves the problem of exact and efficient conversion of polyhedra between vertex-based and plane-based representations.
-Moreover, by leveraging the adaptive octree, BSP structures are nested into octree cells where the intersection between primitives occurs.
-For efficiency, face classification is performed using cells as the basic classification units.
-This localized scheme saves considerable computing resources and retains the topology of non-intersected areas.
+\subsection{Intersection detection}
 
-Such localized scheme is widely used in different methods of CSG boundary evaluation \cite{pavic2010hybrid, wang2011approximate, feito2013fast, campen2010exact}.
-These methods are usually based on intersection computation and face membership classification.
-The success of such localized scheme is enabled by two facts.
-First, the intersections between primitives are locally distributed.
-Second, space labels of a face are often coherent with those of its neighborhood.
-The former makes it possible to reduce the space that requires an intersection test.
-The latter enables sharing of space labels between adjacent faces to accelerate face classification.
+The goal of this step isIntersection detection is performed between pairs of triangle faces within each critical cell.
+For the sake of robustness, all degenerated cases should be classified and well-handled.
 
-However, most of these methods use the cube (e.g., voxels, octree cells) as the unit of the face group, which is often the natural result of reusing space-division data structures constructed for intersection computation.
-In this way, connected faces that share the same labels might be distributed in different cubes.
-Thus, repetitive classifications may be required for each cube.
-Furthermore, faces of different classifications may coexist within a small space, forming a ‘mixed’ area (e.g., the red areas in Figs.
-\ref{fig:cluster}(a) and (b)).
-Because the size of the cubes cannot be illimitably small, special cubes that contain faces with different space labels typically must be constructed in these mixed areas.
-Processing these special cubes is often complex and time-consuming.
-To more efficiently share space labels, we therefore use faces, rather than cubes, as the basic grouping units.
-Grouping is efficiently performed by utilizing geometry connectivity with a flood-filling algorithm.
-
-Recently, Feito et al.
-\cite{feito2013fast} proposed a method for Boolean evaluation.
-This method also uses a face-based grouping scheme.
-To share classification results, faces that do not intersect with other primitives are grouped together according to geometry connectivity.
-This method and the proposed method have similar stages for single Boolean operation evaluation.
-One of the major differences is that our method supports non-incremental evaluation of CSG.
-For this purpose, we designed a series of dedicated stages.
-Additionally, our face grouping scheme is intended for both non-intersected faces and faces that intersect with other primitives.
-It thus provides a uniform treatment for all faces and further accelerates the face classification stage.
-Moreover, the similarity between adjacent groups is omitted by Feito et al.'s method.
-Although different groups have different space labels, we observe that they may still share some of these labels if they are neighboring.
-We utilize this kind of space label coherence between groups for better performance.
-
-On the other hand, with the development of general-purpose computing on graphics processing units (GPGPUs), many researchers  \cite{wang2011approximate, zhao2011parallel, museth2002level, chen1999volumetic, eisemann2008single} have tried to utilize the grand computation power of graphics hardware for Boolean operations.
-These methods often have good performance and are suitable for interactive applications, such as digital sculpting.
-However, owing to the paralleled features of graphics hardware, these methods are usually voxel-based and support only approximate evaluation that inevitably suffers from geometric detail loss, especially at the intersection areas of primitives.
-
-\section{Overview}
-
-\label{sec:overview}
-
-As in most previous works \cite{feito2013fast, bernstein2009fast}, we require the input primitives of the CSG tree to be watertight Nef polyhedra with manifold surfaces.
-We assume there is no self-intersection.
-Because we adopt a flood-filling strategy, we additionally assume that the connectivity of adjacent faces is available.
-Our current implementation is dedicated to primitives of triangular meshes for simplicity.
-Our approach efficiently and robustly computes the boundary of CSG solids in three steps, as illustrated in Fig.
-\ref{fig_overview}.
-Our main contributions exist in Steps 2 and 3.
-
-\subsection{Adaptive Octree Construction}
-
-As a typical routine of localization, our method uses the adaptive octree to frequently accelerate the used spatial query afterwards.
-Our octree construction implementation is akin to the implementation in Feito et al.'s method \cite{feito2013fast}.
-The major difference is that, because our method is for non-incremental CSG evaluation, the octree is constructed on the bounding box that contains all input primitives (Fig.
-\ref{fig_overview}(b)).
-To avoid presentation ambiguity between a CSG leaf and an octree leaf, the latter is called a cell.
-Intersection detection between triangle faces and cells can be efficiently performed by using the separating axis theorem \cite{gottschalk1996obbtree}.
-Cells are classified into two types: if all triangles that intersect a cell belong to the same primitive, we call it a \emph{non-critical} cell.
-Otherwise, it is a \emph{critical} cell.
-This classification is needed for intersection computation in the next step.
-
-\subsection{United Representation of Intersection Construction}
+\subsection{United representation of intersection}
 \label{sec:overview:isect}
 
-\subsection{Multilevel Flood-filling Classification}
+\subsection{Flood-Filling facet classification}
 
-\section{United Representation of Primitive Intersection}
-{\color{red}{
-Primitive intersects primitive, generating intersection line segments (Fig. \ref{fig_raw1}).
+\section{Construction of United Intersection Graph }
+
+The intersection of primitives can be very complex because of so many degenerate cases.
+In order to design a robust algorithm, one have to take into consideration of all the degenerated cases, which often makes the algorithm rather complex and error-prone to implement.
+We observe the important fact that the CSG evaluation is no more than splitting and selecting faces.
+Therefore, the only important thing during intersection test is to find out the potential edges and vertices of the result mesh.
+Therefore, we use a very concise graph model, with only a few extra data for classification on vertices, as the output of this stage.
+
+Another problem is that numerical error introduced by computing coordinates of intersection vertices often leads to fault topology construction in the later stage.
+Using high precision float point is the most common way to alleviate this issue.
+However, only the time-consuming rational number arithmetic can be absolutely precise.
 
@@
   % Requires \usepackage{graphicx}
-  \includegraphics[width=3.5in]{raw1}\\
-  \caption{triangle contains intersection lines, two-primitive case}\label{fig_raw1}
+  \includegraphics[width=1.5in]{p-reps}\\
+  \caption{Plane-based representation of triangles. The yellow triangle is represented by three bounding planes (green) and the supporting plane where the triangle lies. }\label{fig_p-reps}
 \end{figure}
 
-Considering degenerate cases in n-primitives CSG can be very complex (Fig. \ref{fig_raw2}).
+ In order to be both robust and efficient, we choose not to compute the coordinates of intersection vertices until we finally construct the result topology.
+In the early stage, each new vertex is represented by intersection of three planes.
+This method is based on two facts: 1) Douze et al.
+[] observe that every intersected vertex is either the intersection between an edge and a plane, or the intersection of three planes.
+2) Campen et al.
+[] give an efficient method to precisely convert b-reps mesh into its plane-based representation (Fig.
+\ref{fig_p-reps}).
+Details is explained in the following.
+
+\subsection{Definition}
+
+Faces in a certain primitive can be classified into intersected faces and non-intersected ones according to whether they intersect other primitives.
+Our United Intersection Graph (UI-graph) is a graph data structure embedded in each intersected face.
+It is used to split these faces and guide the face classification.
+
+The nodes of UI-graph of an intersected face $F$ are the vertices, include the original three corners of $F$ and all the intersected vertices within $F$.
+Intersected vertices are shared between different UI-graphs.
+For example, the vertex $a$ is generated by intersection between face $F_1$ from primitive $P_i$ and edge $e(G_1, G_2)$ from primitive $P_j$, where $e(G_1, G_2)$  is the shared edge of face $G_1$ and face $G_2$.
+Then face $F_1$, $G_1$, $G_2$ are all intersected faces and each of them contains a UI-graph with one of its node is $a$.
+
+Douze et al.
+[] observed that vertices during a CSG evaluation can be divided into three types.
+The first order vertex is already contained in the input primitives.
+The second order vertex is the intersection between an edge and a face.
+The third vertex results from intersection of three faces from different primitives.
+Considering the degenerate cases, this classification is not complete because different types do overlap.
+But it does not matter because each vertex at least belong to one of these types.
+Then we can use the plane-based representation (Fig.
+\ref{fig_p-reps}) introduced by Campen et al.[], which treats each triangle face by a supporting plane surrounded by three bounding planes, to represent each vertex by intersection of three planes.
+This method has two advantages.
+First, it is universal for all kinds of vertices, thus is easy to handle.
+Second, we can avoid explicitly computing the coordinates of new introduced vertices to avoid introducing numerical error.
+
+Also, each node contains data structure called vertex context.
+It records on which primitives and on which part of primitive the node lies.
+A vertex can lies on the vertex, edge or within the face of a certain primitive.
+For example, the vertex context of $a$ is $\{(F_1, P_i), (e(G_1, G_2), P_j)\}$.
+This information is very important for the classification of the neighborhood.
+In particular, we notice that the vertex context of a certain vertex is invariant in different UI-graphs.
+So we only need to maintain one context for each vertex and shared among UI-graphs.
+
+The edges of UI-graph are simply the intersection line segments between faces of different primitives.
+They are represented by two references of the nodes in the UI-graph.
+No further information is required.
+
+As will explained below, we take two steps to construct UI-graphs for each intersected faces of the whole CSG.
+The first step is to build stand-alone UI-graphs for each pair of primitives, which is built upon our plane-based triangle-triangle intersection test, and the second step is to merge them into a single one for each intersected faces.
 
@@
   % Requires \usepackage{graphicx}
-  \includegraphics[width=3.5in]{raw2}\\
-  \caption{triangle contains intersection lines, n-primitives degenerate cases}\label{fig_raw2}
+  \includegraphics[width=1.7in]{raw3}\\
+  \caption{The UI-graph of a certain face. }\label{fig_raw3}
 \end{figure}
 
-We converted it into a united representation, making it clear and easy to process by the following process (Fig. \ref{fig_raw3}).
-
-\begin{figure}
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=3.5in]{raw3}\\
-  \caption{triangle contains intersection lines, n-primitives degenerate cases, using united representation}\label{fig_raw3}
-\end{figure}
-}}
-
-\subsection{Plane-based Triangle Intersection}
-
-{\color{red}{why using triangle intersection, rather than edge-face based, etc. --- for coplanar test.}}
-\newline\newline
+\subsection{Plane-Based Triangle-Triangle Intersection}
 
@@
 
+The plane-based triangle-triangle intersection (PTTI) test is largely the variant of M\"{o}ller's triangle intersection test [].
 M\"{o}ller's algorithm computes the intersection between two triangles $F_1$ and $F_2$ in three steps, as illustrated in Fig.
@@
 In Fig.
-\ref{fig:isect}, we list all intersection situations between a triangle and a plane, and the $S_X$  in each situation.
+\ref{fig:isect}, we list all non-coplanar intersection situations between a triangle and a plane, and the $S_X$  in each situation.
 
@@
 \caption{We denote the signed distance from point $X$ to plane $S_2$ as $d_X$.
-All the four conditions of intersection between $F_1$ and $S_2$ (denoted as $Seg_1$) are:  (a) $d_A\cdot d_C<0$, $d_B\cdot d_C<0$; (b) $d_A=0$, $d_B=0$, $d_C\neq 0$; (c) $d_A=0$, $d_B\cdot d_C<0$; (d) $d_A=0$, $d_B\cdot d_C>0$.
+All the four non-coplanar conditions of intersection between $F_1$ and $S_2$ (denoted as $Seg_1$) are:  (a) $d_A\cdot d_C<0$, $d_B\cdot d_C<0$; (b) $d_A=0$, $d_B=0$, $d_C\neq 0$; (c) $d_A=0$, $d_B\cdot d_C<0$; (d) $d_A=0$, $d_B\cdot d_C>0$.
 End points of $Seg_1$ are intersections between $S_2$ and related edge lines of $F_1$ (bold edges).}
@@
 If $K(A, B)$ is positive (negative), this means that $A$ lies in the positive (negative) direction of $B$.
-Otherwise, $A$ and $B$ are concident.
+Otherwise, $A$ and $B$ are coincident.
 
-If $F_1$ and $F_2$ are coplanar, we check whether they overlap within the common plane using the algorithm by M\"{o}ller\cite{moller1997fast}.
-The substrate of this algorithm is to verify on which side of an edge $E$ a point $V$ lies.
-We implement it using plane-based geometry by substituting $E$ with its corresponding bounding plane $S_E$ and then computing the sign of distance from $V$ to $S_E$.
+One may find that we do not give the solution of coplanar cases.
+This is deliberate because we find recording coplanar cases is not necessary for the following process.
+This will be discussed further in Section 5.
 
-\subsection{Generating United Representation}
+\subsection{Generating Pairwise UI-Graphs}
 
-{\color{red}{Mainly deal with intersection between intersection line segments.}}
+As a general case, an intersected face intersects with one or more primitives. This means there could be so many different types of degenerate cases, that it is not easy
+
+we choose divide and conquer \cite{ogayar2005point} \cite{douze2015quickcsg}
+
+We first consider constructing UI-graph between each pair of primitives.
+The graph generated by two primitives is much simpler than a n-primitive one: since input primitives are not self-intersected, there is no cross or overlap between intersection line segments.
+
+When PTTI test detects a intersection, it outputs the two end points of intersection line segment, or, in a degenerate case, two coincident points.
+
+\subsection{Merging UI-Graphs}
+
+Mainly deal with intersection between intersection line segments. It is necessary when a face intersects with faces from more than one other primitives.
+
+Atom operation:
+
+1. add an vertex. no need outside a graph
+
+2. remove/add edges.
+
+3. sort along an edge.
+
+4. merge vertices.
+
+comparison:
+
+ If coplanar (collinear), choose a direction as positive. 3-4-2
+ If not, compute intersection, 4-2
 
@@
 
-{\color{red}{Flood-filling is all about giving a seed and propagation. In this chapter, from down to top, we introduce this process and explain how it can save computation time.}}
-
-In this step, we classify faces one by one to generate the final mesh.
-The intersection information computed in the previous section is used for re-tessellation and space label computation.
-To better explain our approach, we firstly introduce the background knowledge.
-Then the framework of this step is outlined.
-Afterwards, several important techniques in this step are detailed.
+Flood-filling is all about giving a seed and propagation. In this chapter, from down to top, we introduce this process and explain how it can save computation time.
 
@@
 
-We firstly introduce the space labels, which comprise the basis of face membership classification.
-The space label of face $F$ with respect to primitive $M$, denoted as $L_F(M)$, is the relative location of $F$ with respect to $M$.
-Also, we use $L(M)$ to denote the space label with respect to $M$ which does not specify a face.
-In general, space label has four conditions: completely inside (\emph{In}), completely outside (\emph{Out}), on the boundary (\emph{On}) or not available (\emph{N/A}).
-In the last condition, $F$  crosses the boundary of $M$.
-Accordingly, it does not have a uniform label.
-In addition, if the normal direction of $F$ is considered, there are two derived conditions of \emph{On}: the normal points to the outside (\emph{Same}) and those to the inside (\emph{Oppo}) of $M$.
+\subsection{Flood-filling Inside a Triangle}
 
-The evaluation of Boolean operations between B-reps primitives $A$ and $B$ can be converted to the problem of surface selection according to the labels \cite{kuratowski1968set}:
-\begin{equation}
-\label{eq:select}
-\begin{split}
-&A\cup^*B:\{F_A~Out~B\}\cup\{F_B~Out~A\}\cup\{F_A~Same~B\},\\
-&A\cap^*B:\{F_A~In~B\}\cup\{F_B~In~A\}\cup\{F_A~Same~B\},\\
-&A-^*B:\{F_A~Out~B\}\cup\{(F_B~In~A)'\}\cup\{F_A~Oppo~B\},
-\end{split}
-\end{equation}
+\subsubsection{Compute indicator vector}
 
-\noindent where $F_X$ is the faces of $X$, and $F'$ means $F$ with an inverted normal.
-The stars ($^*$) after the operation notations ($\cup, \cap, -$) mean that the Boolean operations are regularized.
+How to propagate the indicator vector from the seed vertex to all the vertex in a triangle.
 
-Now, consider computing $L_F(T)$, where $T$ is a CSG solid $T$ with $n$ primitives $\{M_i~| ~i = 1,2,3,...,n\}$.
-Then there are a total of $n$ space labels for $F$: \{$L_F(M_i)~|~i = 1,2,3,...,n\}$ (or in vector form $\vec{L}_F$).
-If all elements in $\vec{L}_F$ are known and none of them is \emph{N/A}, $L_F(T)$ can be easily computed by traversing the whole CSG tree from bottom to top and progressively combining the space labels of the CSG nodes according to combination rules \cite{requicha1985boolean}:
-\begin{equation}
-\label{eq:comb}
-\begin{split}
-X\cup Out\Rightarrow X, ~~&X\cap Out\Rightarrow Out, \\
-X\cap In~~\Rightarrow X, ~~&X\cup In\Rightarrow In, \\
-X \cup X \Rightarrow X, ~~&X \cap X \Rightarrow X,\\
-Same \cup Oppo\Rightarrow In, ~~&Same \cap Oppo\Rightarrow Out,
-\end{split}
-\end{equation}
-where $X$ is an arbitrary label value.
-Note that the combination rules for difference operation are not shown here, because the difference operation can be converted into the intersection operation using De Morgan's transformations:
-\begin{equation}
-\label{eq:demo}
-\begin{split}
-A-B\Rightarrow A\cap B^c, ~~~~~~~&(A^c)^c\Rightarrow A,\\
-(A\cap B)^c\Rightarrow A^c\cup B^c, ~~&(A\cup B)^c\Rightarrow A^c\cap B^c,
-\end{split}
-\end{equation}
-where $X^c$ denotes the complement of $X$. If and only if $L_F(T) = Same$, $F$ lies on the boundary of the final model and has the correct normal; accordingly, $F$ belongs to the final result.
+Start from a full indicator
 
-If some elements in $\vec{L}_F$ are \emph{N/A} or cannot be computed, we may be unable to compute $L_F(T)$.
-However, the CSG tree $T$ can be trimmed into a smaller one with fewer primitives to reduce the complexity of further evaluation.
-For example, assume we have a CSG with its Boolean expression $M_1\cup (M_2\cap M_3-M_4)$.
-Given the values of two labels $L(M_1)=Out$, $L(M_2)=In$, the expression can be rewritten as $Out\cup (In\cap M_3-M_4)$.
-Using the combination rules we can simplify the expression as $M_3-M_4$.
-Thus, any face that shares the same two labels $L(M_1)$ and $L(M_2)$ can be classified based on the trimmed CSG tree $M_3-M_4$, which has only two primitives.
+\subsubsection{Facet classification}
 
-\subsection{Face Classification Framework}
-\label{sec:framework}
+How to generate new face and classify faces using indicator vector.
 
-\begin{figure}
-\centering
-\includegraphics[width=3.5in]{multilvl}
-\caption{Illustration of multi-level face grouping framework.
-Faces are grouped into smaller groups in each level.
-The trimmed CSG tree of a specific group is obtained by trimming the tree of its parent according to common labels of this group.
-When the group is not further subdivided, faces in this group are respectively classified based on the trimmed CSG tree of this group.}
-\label{fig:hierachy}
-\end{figure}
+\subsubsection{Acceleration}
 
-Space labels of neighboring faces are often coherent.
-That is, given two neighboring faces $F_1$ and $F_2$, $L_{F_1}(M)$ and $L_{F_2}(M)$ are often the same.
-Therefore, we can group together neighboring faces and evaluate them based on the smaller CSG tree, which is trimmed by the common labels.
-The trimmed tree contains fewer leaves, thus enabling faster computation.
-If face grouping can be efficiently performed, this strategy will greatly accelerate the process of face membership classification.
-Moreover, a multi-level grouping scheme (Fig.
-\ref{fig:hierachy}) may provide even greater capability to shared labels.
-By using such a scheme, faces are first grouped into first-level groups; then, faces of the same first-level groups are further divided into second-level groups, and so on.
-Labels are shared in each level and the original CSG tree is trimmed step by step according to common labels in each level.
-We developed this idea into a novel classification algorithm that uses a two-level grouping scheme.
-The first level is the \emph{inter-primitive} level; the second is the \emph{intra-primitive} level.
+How to reuse the indicator vector of neighbouring vertex.
 
-Before we begin face classification, pre-computation is conducted to make the subsequent analysis easier.
-The original CSG tree is converted into a \emph{positive} tree using the method by Rossignac and Voelcker \cite{rossignac1988active}.
-`Positive' means that the CSG tree contains no difference (-) operation.
-According to Equation \ref{eq:demo}, there may be some primitives with complement notation.
-The benefit is that we are not required to consider the difference operations in the following computation.
+\subsubsection{Coplanar degenerate case}
 
-The classification starts from face grouping in the inter-primitive level.
-In this level, faces of the same primitives are simply grouped together.
-Then, we give a rough estimation of the common labels of the group.
-Suppose the group is primitive $M$.
-Its face labels with respect to primitives whose bounding boxes are totally outside of $M$'s bounding box must be $Out$ (for primitives with complement notations, $In$).
-The original CSG tree is trimmed into the first trimmed CSG tree (as short as the \emph{the first trimmed tree}) according to these common labels plus an extra label $L(M)$ whose value is obviously $Same$.
+Special case discussion, mainly for coplanar problem.
 
-After that, the inter-primitive groups are further divided into smaller intra-primitive groups.
-To explain how to perform intra-primitive grouping, we firstly introduce an essential concept---intersection primitive (IP).
-The IPs of a face $F$ is defined as the primitives that $F$ intersects, excluding the primitive to which $F$ belongs (denoted as $M$).
-Primitives (excluding $M$) that do not intersect $F$ are called non-IPs.
-The set that contains all IPs of $F$ is the IP-set of $F$.
-That set can be computed by enumerating all the primitives in the cross list and coplanar list of $F$.
+\subsection{Flood-filling Through CSG Primitives}
 
-Now, we require that the faces of the same intra-primitive group meet two requirements: they should be connected together and have the same IP-set.
-These two requirements give these faces very good properties, as discussed in Proposition 1.
-The labels referenced in Proposition 1 are used to trim the first trimmed tree into the second trimmed CSG tree (as short as \emph{the second trimmed tree}).
-For a specific intra-primitive group, the primitives of its second trimmed tree is a subset of the common IP-set of that group.
-This is because all space labels with respect to non-IPs are shared within the intra-primitive group and all these labels are either $In$ or $Out$.
-Therefore, all non-IPs must have been trimmed from the CSG tree (to be explained in Section \ref{sec:trim}).
+\subsubsection{Seed generation}
 
-\vspace{0.8em}
-\noindent \textbf{Proposition 1.}~~~~If a group of faces are connected together and they have the same IP-set, they must share the same labels with respect to all non-IPs.
-These labels are either \emph{In} or \emph{Out}.
+\subsubsection{Flood-filling within primitives}
 
-\vspace{0.6em}
-\noindent \textbf{Proof.}~~~~We only prove that the conclusion stands for adjacent faces, which is a special case of connected faces.
-Promoting the conclusion to the general situation is obvious.
-Assume $M$ is a non-IP and label $L(M)$ is different for the two adjacent faces $A$ and $B$ .
-Then there must be faces from $M$ between $A$ and $B$ to cause the different space labels.
-Additionally,  because $A$ and $B$ are adjacent, at least one of $A$ and $B$ intersects the faces from primitive $M$.
-This contradicts the assumption that $M$ is non-IP.
-Therefore, $L(M)$ must be the same for $A$ and $B$.
-Moreover, because $M$  is non-IP, $L(M)$ is either \emph{In} or \emph{Out}.
+\subsubsection{Flood-filling between primitives}
 
-\begin{figure}
-  \centering
-  \includegraphics[width=3.5in]{mesh}\\
-  \caption{A snapshot during flood filling (\emph{left}), and the final grouping result (\emph{right}).
-Different intra-primitive groups are distinguished by different colors.
-From the final grouping result, the whole mesh is divided into 9 intra-primitive groups.}\label{fig:mesh}
-\end{figure}
-
-\vspace{1.0em}
-Because faces of the same intra-primitive group are connected together, we can efficiently group them using a flood filling algorithm.
-When visiting a face, its space label vector is instantly computed and its classification is performed.
-Our intra-level grouping is performed as follows:
-\begin{itemize}[leftmargin=0.45cm]
-\item[1)]{\textbf{First seed generation.}}~A triangle face $F_{S0}$ is randomly chosen as the first seed (e.g., the red triangle in Fig.
-\ref{fig:mesh}).
-Labels of $F_{S0}$ with respect to non-IPs are determined by using $F_{S0}$'s barycenter as the sample point, through a ray-shooting algorithm \cite{havran1999summary} and by employing our octree as a spatial search structure \cite{frisken2002simple} to speed up.
-Note that because the original CSG tree is trimmed into the first trimmed tree, we only compute labels with respect to primitives within that first trimmed tree.
-\item[2)]{\textbf{Label propagation.}}~Once there is a seed $F_S$ with $L_{F_S}$ with respect to all non-IPs, we define the intra-primitive group $G_S$ as follows.
-All faces that belong to $G_S$ should have the same IP-set as $F_S$.
-The common labels of $G_S$ are $L_{F_S}$ with respect to all non-IPs.
-The first trimmed tree is trimmed into the second trimmed tree according to these common labels.
-Breadth-first flood filling is used to find all faces that belong to $G_S$.
-When visiting a face, we first check if it has the same IP-set as the seed.
-If so, set membership classification is performed based on the second trimmed tree of $G_S$ (detailed in Section \ref{section:setmemcls}).
-Otherwise, it is pushed into a candidate list for Step 3 (e.g., the black faces in Fig.
-\ref{fig:mesh} (left)).
- \item[3)]{\textbf{Secondary seed generation.}}~When the flood filling ends, which means no more faces belong to the current face group, a new seed is picked from the candidate list (e.g., the stippled faces in Fig.
-\ref{fig:mesh}).
-Then a new group is defined by the new seed and the labels with respect to non-IPs of the new seed are computed (details in Section \ref{sec:secondseed}).
-After that, Step 2 is repeated according to the newly defined group, until that candidate list is empty, indicating all faces of $M$ are classified.
- \end{itemize}
-
-The face membership classification of the whole CSG is accomplished by performing the above process for each primitive.
-Procedure \ref{code:floodfill} shows the framework as pseudo-code.
-To avoid repetitive visits during flood filling, we use an extra flag for each face to record its visiting status.
-
-\begin{algorithm}[!ht]
-\caption{FaceClassification(PrimitiveList, PosTree)}
-\label{code:floodfill}
-    \begin{algorithmic}[1]
-    \FOR {each $M_i$ in $PrimitiveList$}
-    \STATE Get common labels $CL^1$ of $M_i$;
-    \STATE Trim $PosTree$ into $TrimTree1$ by $CL^1$;
-    \STATE Select the first seed $F_0$ from $M_i$;
-    \STATE Put $F_0$ into $CandidateList$;
-    \WHILE {$CandidateList$ is not empty}
-    	\STATE Pick a seed $F_S$;
-        \STATE Define group $G_S$, where $F_S\in G_S$;
-        \STATE Compute the common labels of $F_S$, denoted as $CL^2$;
-        \STATE Trim $TrimTree1$ into $TrimTree2$ according to $CL^2$;
-    	\STATE Put $F_S$ into $FloodFillQueue$;
-    	\WHILE {$FloodFillQueue$ is not empty}
-    		\STATE Get the next face $F_i$ from $FloodFillQueue$;
-    		\STATE Do set membership classification of $F_i$ based on $TrimTree2$;
-    		\FOR {each adjacent face $F_{Neighbor}$}
-    			\IF {$F_{Neighbor}$ belongs to $G_s$}
-    				\STATE Put $F_{Neighbor}$ into $FloodFillQueue$;
-    			\ELSE
-                    \STATE Put $F_{Neighbor}$ into $CandidateList$;
-    			\ENDIF
-    		\ENDFOR
-    	\ENDWHILE
-    \ENDWHILE
-    \ENDFOR
-    \end{algorithmic}
-\end{algorithm}
-
-\subsection{Trimming CSG Tree}
-\label{sec:trim}
-
-Trimming a CSG (binary) tree with the $In$ or $Out$ label is relatively simple.
-According to the first two lines of Equation \ref{eq:comb}, given a primitive $M$, if $L(M)$ is $In$ ($Out$), the label of $M$'s parent node is either $In$ ($Out$) or the value of its sibling.
-In either condition, the node representing $M$ can be trimmed from the tree.
-
-However, when trimming the original tree into the first trimmed tree for a specific inter-primitive group, a special label, $Same$, exists.
-This label means that the faces of the group are on the boundary of the primitive to which they belong, which is absolutely correct.
-This label is not easy to process because we cannot determine the label of its parent node unless we know the label of its sibling.
-Unfortunately, during tree trimming, the labels we have are incomplete.
-We may have to leave the $Same$ label unprocessed and wait for further information.
-This incurs considerable computation burden to check this special condition and makes the trimming algorithm inefficient.
-To solve the problems, we developed a new representation of the CSG tree, called CSGlist, to minimize the side effect of the special $Same$ label and enable early rejection of face groups that do not belong to the final model of the CSG.
-
-Given a face group from primitive $M$, we construct the CSGlist as follows.
-We cut the original CSG tree into a set of subtrees along the \emph{critical path}, which is the path from $M$ to the root (e.g., when $M=D$, the construction of CSGlist is shown in Fig.
-\ref{fig_trim}).
-Obviously, none of the subtrees contains the primitive $M$.
-Each subtree of CSGlist is associated with `desired' label values.
-That is, if the labels with respect to all subtrees meet their corresponding desired values respectively, the labels with respect to the original CSG tree is $Same$.
-On the contrary, if the labels with respect to any subtree are not desired, the labels with respect to the whole CSG tree is not $Same$; thus the related face group should be dropped.
-The desired value of a subtree is determined based on how the subtree connects to the critical path.
-According to the face selection rules (Equation \ref{eq:select}), if the subtree connects to a Union ($\cup$) node, then the desired value is $In$; otherwise, the desired value is $Out$.
-In addition, suppose the primitive $A$ in Equation \ref{eq:select} is the left child.
-Then if the subtree is in the left child of its parent node, $Same$ is also desired.
-
-Conversion to CSGlist is performed before the first trimming.
-After that, all the labels we use for CSG tree trimming are either $In$ or $Out$.
-Both the first and the second trimmed trees are represented by CSGlists.
-The subtrees of the CSGlist can be easily trimmed (since there is only $In$ and $Out$ labels) and their desired values are used to enable early rejection.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3.0in]{csgtree}
-\caption{Convert CSG tree into a CSGlist along the critical path (marked by the arrow) from primitive $D$ to the root.
-The CSGlist contain three subtrees.
-Each subtree has its desired label value.
-Subtree 1: $Out$ or $Same$.
-Subtree 2: $In$ or $Same$.
-Subtree 3: $Out$.}
-\label{fig_trim}
-\end{figure}
-
-\subsection{Classifying a Single Face}
-\label{section:setmemcls}
-
-If a face is non-intersected, the second trimmed tree will have single value, which can be used to determine whether the face is accepted.
-However, if it is an intersected face, further processing is needed.
-
-Intersected faces usually cannot be classified as a whole.
-They have to be tessellated into smaller non-intersected triangles, each of which is classified respectively.
-Robustness and efficiency are our main consideration.
-For these purposes, we nest the exact BSP structure \cite{bernstein2009fast, campen2010exact} into the intersected faces.
-We classify intersected face $F$ as follows.
-
-\vspace{0.5em}
-\noindent \textbf{Valid-IPs \& Pseudo-IPs}~~~~
-IPs of an intersected face are firstly divided into two types according to whether the IPs are in the second trimmed tree.
-The IP that is the primitive of the second trimmed tree is called the valid intersection primitive (valid-IP).
-Otherwise, it is called the pseudo-intersection primitive (pseudo-IP).
-Pseudo-IPs intersect the face; however, the labels with respect to pseudo-IPs do not affect the classification of $F$.
-In other words, the intersections of pseudo-IPs are not edges of the final models, as illustrated in Fig.
-\ref{fig:invalidcross}.
-Thus, we simply omit these pseudo-intersections during classification.
-This filtering stage saves computation time by avoiding unnecessary splitting of faces.
-An extreme instance is that there is no valid-IP.
-For this condition, the face is processed in the same way as a non-intersected face.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3.2in]{invalid-cross}
-\caption{2D illustration of pseudo-intersection. The vertices in red do not appear in the final model. They are so called pseudo-intersection vertices (line segments in the 3D case).}
-\label{fig:invalidcross}
-\end{figure}
-
-\vspace{0.5em}
-\noindent \textbf{Tessellation}~~~~
-In this step, $F$ is divided into a set of sub-triangles using the intersections recorded in Section \ref{section:isect}.
-Because constrained Delaunay triangulation (CDT) \cite{chew1989constrained} has good topology characteristics, we convert the tessellation into a problem of CDT.
-The zone of CDT is $F$, and the constraints are all the intersections by valid-IPs.
-The constraints ensure that no sub-triangles will cross these intersection lines.
-Because CDT in our method is a vertex-based 2D problem, the 3D coordinates computed by their plane-based representation are projected on a 2D space, which is the axis-aligned plane where the area of $F$ is maximized.
-
-It should be noted that intersections from different valid-IPs may intersect (Fig.
-\ref{fig:cdt}(c)).
-Omitting these intersection points may cause false results of CDT.
-To obtain the correct constraints, intersections from different valid-IPs are tested to determine whether they intersect.
-We implement this test again using plane-based geometry for robustness.
-As we know this kind of special intersection is actually the cross point of the three faces: $F$,  and the two associated intersected faces from the valid-IPs (Fig.
-\ref{fig:cdt}(d)).
-Therefore, such a point can be represented by the three supporting planes of the three faces.
-We determine whether the cross point exists by testing if the point is inside all three of these faces.
-By adopting the routine of the relative position of a point to a plane \cite{sugihara1990solid}, this test is robust and efficient.
-If the cross point of different intersection lines is detected, these lines are split by the cross point and the constrains of CDT are updated accordingly.
-Moreover, because the cross point is actually shared by the three faces, it is added to the point lists (Section \ref{sec:isecthandle}) of all three of these faces.
-
-\begin{figure}
-\centering
-\includegraphics[width=3.5in]{cdt}
-\caption{We classify the face $F$ from primitive $M$: (a) faces of $M_1$ (yellow) that intersect $F$.
-BSP of $M_1$ is constructed according to these.
-(b) Faces of $M_2$ (green) that intersect $F$.
-BSP of $M_2$ is constructed according to them.
-(c) If $M_1$ and $M_2$ are the only valid-IPs of $F$, then triangulation can be performed according to intersection lines recorded in the cross list.
-The red area shows a possible result of sub-triangle classification.
-Note that there are intersections between lines from different primitives (marked as red stars), which are (d) intersections of three faces each from different primitives.}
-\label{fig:cdt}
-\end{figure}
-
-\noindent \textbf{Classification of sub-triangles}~~~~
-An intersected face $F$ is divided by faces from each valid-IPs into $In$ cells, $Out$ cells and $On$ cells (Figs.
-\ref{fig:isect}(a) and (b)).
-The BSP tree \cite{naylor1990merging} is very suitable for describing such partitions.
-The labels of sub-triangles can be efficiently computed according to a BSP representation using the BSP-based point-in-polyhedra test \cite{gordon1991front, fuchs80visible, james1999binary}.
-Details are discussed as follows.
-
-Given a valid-IP, denoted as $M$, we firstly build a BSP tree nested within $F$ according to the intersections between $F$ and $M$.
-This is a 2D partition problem.
-Nevertheless, constructing BSP in 2D space of $F$ will introduce errors on account of the involved conversion from plane triples (plane-based representation) into 2D coordinates.
-Therefore, it is better to construct the BSP tree in 3D space.
-If we limit the space of the BSP construction zone within the face $F$ with tiny thickness, denoted as $P_F$, it is obvious that all faces from $M$ that intersect $P_F$ are recorded in the cross list and the coplanar list of $F$.
-These faces give the correct space partition on $P_F$.
-We construct the 3D BSP tree according to the intersected faces.
-The construction of the BSP tree is implemented using an exact plane-based algorithm proposed by Berstein and Fussell \cite{bernstein2009fast}.
-Now, given a sub-triangle $SF$, the label $L_{SF}(M)$ is then computed based on the classification results of the three corners of $SF$ according to the constructed BSP.
-If all three classification results are $On$, then $L_{SF}(M)$ is either $Same$ or $Oppo$.
-If any classification of the corners is not $On$, $L_{SF}(M)$  is the same as the non-$On$ classification .
-
-After all space labels of a sub-triangle are computed, we judge whether the sub-triangle belongs to the final model based on the second trimmed tree represented as CSGlist.
-The subtrees in CSGlist are evaluated using the combination rules of labels.
-The sub-triangle is accepted if and only if the evaluation results of all subtrees are desired.
-We might accelerate this step if the coplanar list of $F $is empty or the faces in the coplanar list are all from pseudo-IPs.
-In this case, the labels with respect to valid-IPs are either $In$ or $Out$, and each subtree of CSGlist can be efficiently evaluated using Blist, which was proposed by Hable and Rossignac \cite{hable2005blister}.
-For CSG models in which the coplanar cases are rare, this acceleration saves considerable computation time.
-
-\subsection{Secondary Seeds Generation}
-
-\begin{figure}
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=2.0in]{sgen}\\
-  \caption{$F_x$ is the secondary seed, and $F_c$ is its associated face.
-The labels of $F_x$ with respect to primitives that intersect $F_c$ but do not intersect $F_x$ (e.g., the yellow intersection) can be computed using any point in $E_{x,c}$ as the sample.
-The labels of $F_x$ with respect to primitives that intersect neither $F_x$ nor $F_c$ are the same for both faces.
-Line segments of different colors are intersection lines by different primitives.}\label{fig:sgen}
-\end{figure}
-
-\label{sec:secondseed}
-
-As discussed in Section \ref{sec:framework}, during flood filling, faces belonging to the group of the current seed are classified according to the second trimmed tree of this group.
-The rest are added to a candidate list for generating secondary seeds when no more faces belong to the group of the current seed.
-The main task of secondary seed generation is to compute the space labels with respect to non-IPs of the new seeds.
-
-A straightforward scheme is to use the same approach as the first seed generation in Section \ref{sec:framework}.
-However, this scheme requires  recalculating all the space labels with respect to non-IPs using the time-consuming ray-shooting method.
-For complex CSG evaluation, in which secondary seed generation is frequently requested , we need a more efficient solution.
-Again, we use the information of neighboring faces to accelerate this process.
-When a face $F_x$ is added to the candidate list, we associate the following data with $F_x$: the face $F_c$ that is currently being visited (therefore $F_x$'s neighbor; see Fig.
-\ref{fig:sgen}) and the labels of $F_c$ with respect to $F_c$'s non-IPs.
-Note that the non-IP set of $F_x$, denoted as $C_x$, is different from that of $F_c$, denoted as $C_c$.
-
-Now, if $F_x$ is selected as a new secondary seed, we can compute the labels with respect to non-IPs of $F_x$ in two complementary ways: we can directly inherit from the labels of $F_c$, or represent $F_x$ with a point within $F_c$ and compute the label of this point using the BSP technique presented in Section \ref{section:setmemcls}.
-The former is used for the computation of the labels with respect to the primitives that are in $C_c\cap C_x$.
-The labels with respect to these primitives are the same for both $F_x$ and $F_c$.
-The latter is used for computing the labels with respect to the remaining of primitives (e.g., those in $C_c\setminus C_x$).
-According to Proposition 2, the sample point of $F_x$ can be chosen as any point in the common edge of $F_x$ and $F_c$, denoted as $E_{x,c}$.
-For robustness, we use one of the end points of $E_{x,c}$ as the sample point because we have its exact plane-based representation.
-
-\vspace{+1.0em}
-\noindent \textbf{Proposition 2.}~~~~Given two adjacent faces $F_c$ and $F_x$, the labels with respect to primitive $M$ for $F_x$ is the same as the classification result of any point on the common edge of $F_x$ and $F_c$ in the BSP tree of $M$ for $F_c$ (constructed in Section \ref{section:setmemcls}), if $M$ is in the IP-set of $F_c$ but not in the IP-set of $F_x$.
-\vspace{+0.5em}
-
-\noindent \textbf{Proof.}~~~~We know $M$ is not in the IP-set of $F_x$; therefore, it is obvious that all points on $F_x$ have the same labels with respect to $M$.
-Because the points on the common edge of $F_x$ and $F_c$ are in $F_x$, they have the same labels.
-\vspace{+1.0em}
+\subsubsection{Acceleration}
 
 \section{Experiments and Discussion}
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3.2in]{raster}
-\caption{\emph{Cube} $\cup$ \emph{Sphere1} $\cap$ \emph{Sphere2}: our method resulted in simpler mesh connectivity than the method by Campen and Kobbelt \cite{campen2010exact}.}
-\label{fig:raster}
-\end{figure}
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=3.5in]{budda}
-\caption{Boolean operations on model \emph{Budda}: (a) two \emph{Buddas}, (b) results of \emph{Budda} $\cap$ \emph{Budda}, and (c) the incorrect result of \emph{Budda} $\cap$ \emph{Budda} generated by non-robust implementation of Feito et al.'s method \cite{feito2013fast}.}
-\label{fig:budda}
-\end{figure}
-
-\begin{figure*}[!t]
-\centering
-\includegraphics[width=7in]{models2}
-\caption{(a) Boolean operations between a \emph{Ring} and a set of \emph{Spheres}.
-$\langle 1\rangle$ after 200 operations.
-$\langle 2\rangle$ after 800 operations.
-(b) Union of \emph{Armadillo} and six \emph{Spoons}.
-(c) \emph{Head} - \emph{Cuboid} + \emph{LeftBrain} + \emph{RightBrain}.
-(d) Difference a \emph{BigCylinder} and 28 \emph{SmallCylinders}.
-(e) \emph{Man} $\cup$ \emph{Horse}.
-(f) \emph{Dragon} - \emph{Bunny}.
-(g) \emph{Palate} $\cup$ \emph{Mandible} $\cup$ (20 \emph{Teeth}).}
-\label{fig:models}
-\end{figure*}
-
-\begin{table*}[ht]
-\caption{Computation Time Statistics (Seconds)}
-\label{tab:performance}
-\centering
-\begin{tabular}{*{13}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
-\hline
-\multirow{2}{*}{No.} & \multirow{2}{*}{Figure} & \multicolumn{3}{c|}{Face Num.$^\nabla$} & \multirow{2}{*}{\tabincell{c}{Primitive\\Num.}} & \multirow{2}{*}{\tabincell{c}{CGAL \\ \cite{cgal:hk-bonp3-15a}}} & \multirow{2}{*}{\tabincell{c}{Maya \\ \cite{Maya2015}}} & \multirow{2}{*}{\tabincell{c}{Campen \\ \cite{campen2010exact}}} & \multirow{2}{*}{\tabincell{c}{Feito \\ \cite{feito2013fast}}}& \multicolumn{4}{c}{Our Approach}\\
-\cline{3-5} \cline{11-14}
- & & Total & Min & Max &&&&&& Total$^\circ$ & Step 1 & Step 2 & Step 3\\
-\hline \hline
-1 & \ref{fig:models}(a) & 37.6K & 180 & 1.6K & 201 & 1350 & 49.9 & TLE$^{\dag}$ & 15.9 & \textbf{3.13}  & 0.328 & 1.69 & 0.922 \\
-2 & \ref{fig:models}(a) & 146K & 180 & 1.6K & 801  & TLE & 1400 & TLE & Fail* & \textbf{12.8}  & 1.36 & 6.41 & 4.00 \\
-3 & \ref{fig:models}(b) & 377K & 2.56K & 346K & 7 & TLE & 224.5 & 45.7 & 11.7 & \textbf{1.44} & 0.438 & 0.062 & 0.563 \\
-4 & \ref{fig:models}(c) & 79.2K & 12 & 38.2K & 4  & 97.6 & Fail & 3.58 & 1.69 & \textbf{0.563}  & 0.187 & 0.141 & 0.172 \\
-5 & \ref{fig:models}(d) & 36K & 800 & 2.4K & 29 & 34.1 & 7.03 & 18.7 & 4.05 & \textbf{0.313} & 0.094 & 0.094 & 0.081 \\
-6 & \ref{fig:models}(e) & 597K & 96.9K & 500K & 2 & TLE & 38.3 & 26.4 & 5.63 & \textbf{2.13} & 0.563 & 0.031 & 0.984 \\
-7 & \ref{fig:models}(f) & 170K & 69.7K & 100K & 2  & 218 & 7.45 & 13.8 & 2.39 & \textbf{0.891} & 0.328 & 0.125 & 0.266 \\
-8 & \ref{fig:models}(g) & 362K & 6.91K & 276K & 22 & TLE & 344 & 256 & 19.2 & \textbf{1.80} & 0.766 & 0.172 & 0.593 \\
-9 & \ref{fig:budda} & 2.16M & 1.08M & 1.08M & 2 & Fail & Fail & MLE$^\bullet$ & Fail & \textbf{11.3} & 5.55 & 1.36 & 3.01 \\
-\hline
-\end{tabular}
-\begin{flushleft}
-$^{\nabla}$~~\emph{Min} (\emph{Max}) means the minimum (maximum) number of faces of a single primitive.
-
-$^{\circ}$~~The total computation time of our method includes the construction of half-edge structure and the three steps in Section \ref{sec:overview}.
-
-* ~~\emph{Fail} means nothing was returned, or we received the wrong evaluation results from the programs.
-
-$^{\dag}$~~\emph{TLE} means the processing time was more than  2,000 s.
-
-$^\bullet$~~\emph{MLE} denotes that the program was out of memory. The memory limit for our implementation of Campen et al.'s approach was around 1.2GB.
-
-\end{flushleft}
-\end{table*}
-
-\begin{table}
-\caption{Number of Primitives and Computation Time (Seconds)}
-\label{tab:linear}
-\centering
-\begin{tabular}{*{4}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
-\hline
-Number of Spheres & ~~100~~ & ~~200~~ & ~~300~~ & ~~400~~ \\
-\hline
-\hline
-Our Approach & \textbf{1.38} & \textbf{2.89} & \textbf{4.39 }& \textbf{5.97} \\
-Maya \cite{Maya2015} & 17.4 & 53.4 & 124 & 241 \\
-CGAL \cite{cgal:hk-bonp3-15a} & 439 & 1350 & - & -\\
-Feito \cite{feito2013fast} & 5.20 & 15.9 & 30.4 & -\\
-\hline
-\hline
-Number of Spheres  & 500 & 600 & 700 & 800 \\
-\hline
-\hline
-Our Approach & \textbf{7.90} & \textbf{9.49} & \textbf{11.0} & \textbf{12.8}\\
-Maya \cite{Maya2015} & 407 & 628 & 966 & 1400\\
-CGAL \cite{cgal:hk-bonp3-15a}& - & - & - & -\\
-Feito \cite{feito2013fast}& - & - & - & -\\
-\hline
-\end{tabular}
-\begin{flushleft}
-*~~This table was the computation time of the evaluation for Fig. \ref{fig:models} (a).
-\end{flushleft}
-\end{table}
-
-\iffalse
-\begin{table}
-\caption{Relations between Number of Operations and Computation Time (Millie Second)}
-\label{tab:subdivide}
-\centering
-\begin{tabular}{*{4}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
-\hline
-~~Face Number~~ & Step 1 & Step 2 & Step 3 & ~Total~ \\
-\hline
-\hline
-~~1.7K~~ & 6 & 12 & 15 & 37\\
-~~16K~~ & 50 & 37 & 51 & 153\\
-~~140K~~ & 302 & 121 & 249 & 790\\
-~~1300K~~ & 2006 & 372& 1508 & 4902\\
-\hline
-\end{tabular}
-\begin{flushleft}
-\end{flushleft}
-\end{table}
-\fi
-
-We implemented the proposed method in C++ and tested a series of examples with numerous primitives and/or faces on a consumer laptop with an Intel i5-4200D processor at 1.5GHz and with 8 GB of RAM.
-The OpenMesh library \cite{OpenMesh} is used for storing triangle meshes and supporting the query of neighboring faces.
-Tessellation of critical triangles is performed by constrained Delaunay triangulation using the Fade2D library \cite{Fade2D}.
-
-We compared four state-of-the-art Boolean evaluation techniques, including CGAL \cite{cgal:hk-bonp3-15a}, Maya 2015 \cite{Maya2015}, the method proposed by Campen and Kobbelt \cite{campen2010exact}, and the approach proposed by Feito et al.
-\cite{feito2013fast}.
-The latter two methods used localized schemes.
-Table \ref{tab:performance} shows the comparison in terms of computing time.
-It can be easily to seen that our approach was efficient in all these examples.
-Feito et al.'s method had performance relatively similar to ours for the examples with a  single Boolean operation (Examples 6, 7).
-This is because both the approaches use a face-based grouping scheme to accelerate face membership classification; thus have similar pipelines for single Boolean operations.
-However, when the number of primitives grows, the advantage of our non-incremental CSG evaluation approach becomes more obvious.
-In the examples of more than two primitives, our method is much faster than any other methods.
-In particular, our method worked out example 2 which consisted of 801 primitives, in 15 s, which was more than 100 times faster than the Boolean evaluation in Maya.
-
-Among the three main steps of our approach, the first step of the octree construction is a typical $O(n~log~n)$ algorithm, where $n$ is the total number of faces in the CSG.
-The second step of intersection computation is only performed within critical octree cells.
-The number of critical cells is often linear to the number of intersected faces $k$ (often an $O(\sqrt{n})$ number) in the CSG.
-Therefore, the computation complexity of the second step is almost $O(k)$.
-The condition of the third step of face membership classification is more complex.
-Although the flood filling algorithm used for intra-primitive grouping is $O(n)$ complex, classifying an intersected faces could consume much more time than classifying a non-intersected faces.
-Therefore, if we assume classifying an intersected faces spends $\theta$ times of computation time to classify a non-intersected face, we may generalize the time complexity of this step as $O(n+\theta\cdot k)$.
-When $k/n$ is constant, the third step is $O(n)$ complex.
-
-To further validate that our approach is efficient for non-incremental CSG evaluation, we analyzed how the computation time changes with respect to the number of primitives.
-Table \ref{tab:linear} shows the evaluation time for Fig.
-\ref{fig:models} (a), which was a CSG consisting of a ring and hundreds of identical spheres.
-We changed the number of spheres from 100 to 800 and recorded the evaluation times.
-In this condition, the $k/n$ was relatively constant, and as there are many intersected faces, the bottleneck lies in Step 2 and Step 3.
-The result shows that the computation time of our algorithm had a linear behavior, which conforms to our previous discussion.
-The computation time of other incremental approaches rapidly increased when the number of primitives increased, sometimes showing an $O(n^2)$ behavior.
-This is because for those approaches, as more spheres were added to or subtracted from the ring, the mesh of the ring became more complex, which made it more difficult to perform subsequent Boolean operations.
-
-One possible problem of a non-incremental CSG evaluation approach is memory inefficiency.
-Unlike incremental ones, non-incremental approaches (including ours) often require loading all the primitives into the memory before the evaluation.
-Fortunately, our approach does not significantly suffer from such a problem.
-Our implementation only constructs an octree, which needs typically an $O(n~log~n)$ size data structure, and some auxiliary information of intersected faces, which is usually $O(k)$ size.
-According to our experiment, our approach performed full evaluations in Table \ref{tab:performance} with less than 600MB.
-On the contrary, some incremental approaches can be very memory inefficient.
-For instance, in the evaluation of Example 6, CGAL consumed more than 6 GB of memory.
-Furthermore, in the evaluation of Example 2, which contained only 146 K faces, Maya 2015 used at least 5 GB of memory.
-
-Our method is robust and could correctly evaluate all the examples in Table \ref{tab:performance}.
-On the other hand, it is evident that the commercial software Maya could not even correctly evaluate Example 4, which contained only 38.6 k faces and four primitives.
-CGAL gave warnings when evaluating Example 9 and finally terminated without offering a result.
-Our implementation of Feito et al's method gave an incorrect result for Example 9 (Fig.
-\ref{fig:budda}(c)) and a result rife with small holes for Example 2.
-
-Topology simplicity is another significant characteristic of the quality of CSG evaluation.
-As shown in Fig.
-\ref{fig:raster}, our method led to less triangles to represent the final model than Campen et al.'s method without stages for surface merging.
-A simpler topology is preferred because it is easier to process.
-In fact, we found that it was owing to such inefficient tessellation that Campen et al.'s method took so long time to evaluate Examples 1 and 2.
-After hundreds of Boolean operations, the resulting surface became so fragmented that it could take tens of seconds to perform a single Boolean operation.
-
-\noindent \textbf{Limitations \& Future work}~~~~
-The major limitation of our method is that it is not unconditionally robust.
-Because the tessellation of intersected faces is performed using vertex-based representation, the computed vertex coordinates may shift from their real location, which may lead to incorrect tessellation in theory.
-From our tests, we have not found the visible failures caused by this problem, because that the coordinate errors in most cases are small without visible incorrect tessellation,  we will investigate to integrate plane-based geometry computation into intersected face tessellation in the future work.
 

### 2016-06-11 summary.tex
0611

@@
 \begin{document}
-\title{Efficient Non-incremental Constructive Solid Geometry Evaluation for Triangular Meshes}
+\title{Efficient, Robust and Exact Boolean Operations on N Triangular Mesh Primitives}
 \author{Rui~Wang,~
@@
 \IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
+\IEEEPARstart{C}{onstructive} solid geometry (CSG) has long been a popular modeling tool of computer-aided design and computer-aided manufacturing (CAD/CAM).
+It constructs complex models by combining primitives using a series of regularized Boolean operations \cite{requicha1977mathematical}: union, intersection and difference.
+CSG is often represented by a binary tree, called a CSG tree, whose leaves are primitives and whose internal nodes are Boolean operations.
 
-Main Contribution:
+CSG can be converted into the widely-used  boundary representation (i.e., triangle mesh) through boundary evaluation.
+It is an classical topic with history of over three decades.
+However, one always have to make a bargain between robustness and efficiency of the boundary evaluation.
+One could use rational number arithmetic to avoid errors and thus ensure unconditional robustness, which could be over 20 times slower than a non-robust one [?].
+On the other hand, using an approximate method for boundary evaluation can be very fast, but lack exactness.
 
-1.
-We develop a united representation of intersection lines between CSG primitives.
-Under this representation, Face re-tessellation and classification can be done robustly in any degenerate cases by our pipeline, while keeping good performance.
+Most recent methods [???] try to find a faster way to evaluate boundary of CSG, yet for robustness, the answers are often ambiguous workarounds, like setting a tolerance [?], using higher precision float point number [?] or rotating the primitive with small angle to avoid coplanar cases [?], etc.
+These tricks are often too vague to implement, heavily depend on the experiments, thus not reliable.
+Campen et.
+al.
+[?] gave a good paradigm of a unconditional robust and exact boundary evaluation methods.
+It proved to be fairly efficient, and never crashed with legal inputs.
+Since then, few exact evaluation methods declare themselves as an unconditional robust one.
 
-2.
-Unlike any of the previous method, during the algorithm, we conduct point-in-polyhedron tests only on single seed vertex.
-We develop a propagating to spread the classification information from the seed vertex into the whole CSG.
-In addition, because of this, we do not need to build a full space division to accelerate point-in-polyhedron tests, which is usually time-consuming.
+We prove that exact boundary evaluation of CSG can be even faster, while keeping unconditional robust.
+We adapt the plane-based techniques of Campen et.
+al.'s method for robustness, but use a framework very different from Campen et.
+al.'s, taking advantage of the recent popular idea of using geometry connectivity for face classification acceleration.
+In addition, unlike many other methods, our method can perform boundary evaluation directly for CSG with more than two primitives.
+That is, we do not incrementally generate the intermediate meshes of each Boolean operation.
+In opposite, we generate the final mesh directly.
+In this way, extra complexity of method is introduced, but we can save much computation time.
+The experiment shows that our method is much faster than Campen et.
+al.'s method, while only about twice slower than the state-of-art non-robust methods [??].
 
@@
 
-\section{Background}
+\subsection{Plane-based geometry representation}
 
-\subsection{Plane-based geometry}
+The primary information of commonly used representation of solids are the vertex coordinates.
+In this way, edges and faces are implicitly represented by combination of vertices.
+In contrast, in plane-based representation, the primary elements are planes.
+Vertices and edges are all implicitly represented by plane intersections.
 
-\subsection{CSG evaluation}
+The concept of plane-based representation of polygonal meshes was first described by Sugihara and Iri \cite{sugihara1990solid}. Plane-based representation provides one important advantage
+when it comes to tasks that involve changing the topology of solids represented by meshes like the evaluation of Boolean expressions: no new primary geometry information has to be constructed to obtain the resulting polyhedron – it is composed of a subset of the planes of the input polyhedra.
+Hence, opposed to the case of using vertex coordinates, that inevitably necessitates the construction of new geometry information, only geometric decision predicates are required to compose the output polyhedron from the face planes of the input.
+Since the input is usually given in a numerical representation with finite precision, we can determine an upper bound on the precision that is needed to make correct decisions.
+The a priori knowledge of this upper bound allows us to use fixed precision predicates that are specifically tailored to the precision required in the worst case, resulting in a vastly better performance compared to techniques for arbitrary numerical precision, that are usually required when
+constructions are part of the processing.
+Our processing is rigorously based on this paradigm of plane-based geometry representation that allows us to perform fully robust, exact computations using only fast fixed precision predicates.
+These predicates take planes as arguments and check coincidence and co-orientation of planes, orientation of a plane with respect to a point defined by the intersection of three planes, and whether three planes intersect in a unique point.
+The latter one can also be used in negated form to check if three planes, that are known to intersect in a common point, even intersect in a common line.
+We implement them using filtering techniques proposed by Shewchuk.
 
-\section{Overview}
-费大幅度发
+\subsection{Exact evaluation methods}
+
+CSG evaluation has had notorious problems with robustness since its inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}.
+The non-robustness is inherited from the building blocks of CSG: Boolean operations on solids.
+Many researchers have attempted to solve such an issue using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}.
+However, these methods are often too expensive in computation time and memory to be practical for evaluation of CSG with massive faces.
+For example, in the Computational Geometry Algorithms Library (CGAL) \cite{cgal:hk-bonp3-15a}, the state-of-the-art robust Boolean operation algorithm \cite{hachenberger2005boolean} (implemented with arbitrary precision arithmetic) is more than 20 times slower than its non-robust version.
+
+\subsection{Approximative evaluation methods}
+
+With the development of general-purpose computing on graphics processing units (GPGPUs), many researchers  \cite{wang2011approximate, zhao2011parallel, museth2002level, chen1999volumetic, eisemann2008single} have tried to utilize the grand computation power of graphics hardware for Boolean operations.
+These methods often have good performance and are suitable for interactive applications, such as digital sculpting.
+However, owing to the paralleled features of graphics hardware, these methods are usually voxel-based and support only approximate evaluation that inevitably suffers from geometric detail loss, especially at the intersection areas of primitives.
+
+\section{Motivation and Overview}
+
 \label{sec:overview}
+Our method is designed for boundary evaluation of Boolean operations on arbitrary number of primitives.
+Input primitives should be watertight and non-manifold  triangle meshes, represented by halfedge structures\cite{mcguire2000half}.
+Our method is unconditional robust, exact, while keeping good performance.
+In this section, we first introduce the motivation of our method, then describe where we start to design our boundary evaluation method.
+At last, we give the overview of the method.
 
-\iffalse
-\begin{figure*}[!t]
-\centering
-\includegraphics[width=7.1in]{flowchart}
-\caption{}
-\label{fig_overview}
-\end{figure*}
-\fi
+\subsection{Motivation}
+\label{sec:paradigm}
 
-Our method follows the paradigm of two-step Boolean operation---intersection detection and facet classification, together with an extra step of pre-computation to accelerate the intersection detection.
-The main feature of our method is that we design a unified representation of intersection between primitives (U-rep) to control the complexity of intersection detection result and simplify the facet classification.
-Also, plane-based representation is applied throughout the methods to ensure no error introduced.
-For the same reason, we compute indicator vectors of vertices rather than of the barycenter of facets during classification and deduce the facets' indicator vectors from its vertices'.
+The boundary evaluation is in essence a process of selection.
+In other words, given a Boolean function, it reserves those primitive faces that pass the function and drop the others to generate the final mesh.
+Unfortunately, for B-reps primitives such as triangle mesh, not all the facets from the input primitives can be classified in a whole, since some of them intersect other primitives.
+Therefore, we need an extra step aiming at detecting the intersection between primitives and performing the tessellation.
+In general, most of the boundary evaluation methods follow the two-step paradigm  \cite{wang2011approximate} above, which consists of intersection computation and face classification.
 
-\subsection{Space division}
+During the intersection computation, primitive facets are tested in pairs to compute their intersection.
+Each input primitives are tessellated according to the intersection test results, making every face be either inside, outside or on the boundary of other primitives.
+They are what we called \emph{non-intersected meshes}.
+Every face of non-intersected meshes can be classified in a whole during classification.
+Unfortunately, under common float-point coordinate system, intersection test is error-prone.
+There are mainly two causes: first, there are a large amount of degenerate cases which are hard to be exactly detected; second, when there are intersections, new vertices are introduced into the geometry, whose coordinates usually can not be exactly represented by float-point number.
 
-This step is the mainly the preparation for intersection detection.
-As intersection detection is performed between each pair of faces, localization is necessary for acceleration by filtering invalid pairs.
-In general, any space division data structure can be applied in this stage.
-For simplicity, our method uses the adaptive octree.
-The implementation is akin to the implementation in ??
-et al.'s method \cite{feito2015fast}.
+Face classification is to evaluate whether a given face $x$ belongs to the final geometry according to the n-primitive Boolean function $\Phi$ :
+\begin{equation}
+\lambda_\Phi(x) = \Phi(\lambda_1(x), \lambda_2(x), \cdots, \lambda_n(x)).
+\end{equation}
+The parameter $\lambda_i(x)$ is space indicator with respect to primitive $P_i$.
+This means to classify a face, one has to know the space indicators with respect to all the primitives (or the whole indicator vector $\vec{\lambda}(x)$ for short).
+A space indicator has four conditions: completely inside (\emph{in}), completely outside (\emph{out}), on the boundary with consistent normals (\emph{same}) or opposite normals (\emph{oppo}).
+The rules of Boolean function evaluation by these indicators are described in \cite{douze2015quickcsg}\cite{feito2013fast}.
+
+Face classification also suffers from robustness and exactness problems.
+Many methods classify face according to the indicators of its barycenter, and use point-in-polyhedron test to compute these indicators.
+However, coordinates of barycenters cannot be exactly represented and have the potential to generate false classification.
+In addition, to classify a single face, all the components of its space indicator vector must be figured out.
+Considering the large amount of faces, acceleration is usually necessary.
+Many algorithms take the benefits of the local coherence of indicators, classifying neighboring faces together.
+While this does improve the performance, it can make the exactness problem worse because the false classification can be propagated to neighboring faces.
+
+We want to develop a new boundary evaluation method based on the two-step paradigm, keeping unconditional robust, exact and as fast as possible.
+Combined with the analysis above, we think our method should includes the following features:
+\begin{itemize}
+    \item It has to avoid errors when introducing new vertices during intersection computation. All degenerate cases of intersection have to be well resolved.
+    \item Face classification has to be exact. On the other hand, acceleration using local coherence of indicators may be helpful.
+    \item The exactness and robustness should not rely on arbitrary precision arithmetic, because it is too slow.
+Instead, we choose the plane-based techniques from \cite{bernstein2009fast}\cite{campen2010exact} to ensure good performance.
+\end{itemize}
+
+\subsection{Linked halfedge}
+
+\label{sec:meshes}
+We make an essential observation that the non-intersected meshes, as intermediate result of intersection computation, plays a very important role of the method design.
+It is a bridge that controls the complexity of intersection computation and facilitates the face classification.
+After the non-intersected meshes is determined, all things left are how to construct such a data structure and how to classify according to it.
+
+Our non-intersected mesh, called linked halfedge, is a variance of halfedge, a well-known data structure to represent solids.
+Halfedge has two advantages: first, since halfedge is popular, using it as the intermediate data structure can avoid unnecessary conversion, which has the potential to create simpler algorithm and better performance and result topology; second, the geometry connectivity, by which we accelerate classification using local coherence of space indicators, can be easily retrieved through halfedge.
+
+However, naive halfedge is far from enough.
+The vertex coordinates in halfedge are usually represented by float point number, which cannot exactly represent the newly introduced intersection points.
+Therefore, we utilize plane-based representation to avoid computing new coordinates.
+In addition, we detect all coincident vertices among primitives and linked them together (that is why it is called linked halfedge).
+This information is used for avoiding repetitive vertices, reconstructing geometry connectivity, and ensuring the topology correctness.
+
+Enlightened by Feito et.
+al.
+\cite{feito2013fast}, we found that the the topology near intersection lines between faces can benefit point-in-polyhedron test by dramatically reducing the number of faces needing traversing.
+Therefore, we add extra information into the linked halfedge, called \emph{intersection context}, to facilitate afterwards face classification.
+Intersection context identifies where an intersection lies on the surface of the related primitives.
+An edge of linked halfedge has intersection context only if it is coincident with a certain intersection line segment between primitives.
+We will give the definition and usage of intersection context in details in the following sections.
+
+To give a overall impression of how we design linked halfedge, we summarize the above content and highlight the following features:
+
+\begin{itemize}
+  \item Each input primitive mesh is tessellated into a linked halfedge. Faces in a linked halfedge must not cross any other linked halfedges.
+  \item Coincident vertices between different linked halfedge should be linked, that is, coincident vertices are shared among linked halfedges.
+  \item If a certain edge of linked halfedge is coincident with intersection line segment(s), it should be associated with the corresponding intersection context(s).
+\end{itemize}
+
+\subsection{Method overview}
+
+\subsubsection{Space division}
+
+This step is the preparation of intersection detection.
+As intersection detection is performed between each pair of faces, localization is necessary to filter invalid pairs beforehand.
+In general, any space division data structure can be applied in this step.
+We use the adaptive octree for its simplicity.
+Our implementation is akin to the implementation in \cite{ogayar2015deferred}.
 Intersection between triangle faces and octree leaves can be efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}.
@@
 Otherwise, it is a \emph{critical cell}.
-The big difference between our construction method and ??'s is the subdivision termination condition.
-In ??'s method,??.
-However, in our method, we do not need subdivide any non-critical cell no matter how many faces it contains.
-This is because subdividing non-critical cells benefits only the polyhedron inclusion test, which is frequently used in ??'s method but rarely in ours.
-This simplification can bring large performance advantage, especially for those cases whose intersection areas are small.
 
-\subsection{Intersection detection}
+The difference between our space division and many others \cite{ogayar2015deferred}\cite{feito2013fast} is the octree node subdivision termination criterion.
+In our method, we do not need subdivide any non-critical cell no matter how many faces it contains.
+This is because subdividing non-critical cells benefits only the ray-casting point-in-polyhedron test, which rarely appears in our method.
+This simplification can bring large performance advantage, especially for those cases where intersections between primitives are not complex and limited in small regions.
 
-The goal of this step isIntersection detection is performed between pairs of triangle faces within each critical cell.
-For the sake of robustness, all degenerated cases should be classified and well-handled.
+\subsubsection{Intersection detection}
 
-\subsection{United representation of intersection}
-\label{sec:overview:isect}
+This step is to detect intersections between primitives in a robust and exact way.
+Our algorithm is largely based on vertex-based M\"{o}ller's algorithm \cite{moller1997fast}, which is very efficient to compute intersection between two triangles.
+However, naive implementation of M\"{o}ller's algorithm always incurs robustness issues when computing the coordinates of new vertices.
+To avoid an unexpected failure caused by numeric errors, we integrate plane-based representation of polyhedra \cite{sugihara1990solid} into the implementation of M\"{o}ller's algorithm.
+Adaptive precision predicate technique \cite{shewchuk1997adaptive} is applied for efficiency of plane-based geometry computation.
+Moreover, to make our method robust, we classify all the intersection cases into three major classes and respectively discuss how to each condition.
+Details are provided in Section \ref{section:isect}.
 
-\subsection{Flood-Filling facet classification}
+\subsubsection{Tessellation}
 
-\section{Construction of United Intersection Graph }
+Once all intersections are detected, we need to tessellate the input primitives and construct the linked halfedges..
+In many methods like \cite{ogayar2015deferred}, constraint Delaunay triangulation (CDT) is applied to perform tessellation, since the intersections are naturally the constraints of CDT.
+However, for a CSG with more than two primitives, the intersection vertices may be generated by intersections of three faces from different primitives, which cannot be computed during the previous step.
+Also, intersection line segments may overlap or intersect with each other, and cannot be used for constraints of CDT directly.
+Finally, as our intersection vertices are represented exactly by planes, implementation of CDT could be complex and inefficient, as most CDT methods were not designed to handle planes.
+Therefore, we design a simple structure, called tessellation graph, to guide the tessellation of each single face, and develop a very fast but exact method to construct linked halfedges from tessellation graphs, which is suitable for dealing with plane-based representation of intersections.
+Details are shown in section \ref{sec:tessellation}.
 
-The intersection of primitives can be very complex because of so many degenerate cases.
-In order to design a robust algorithm, one have to take into consideration of all the degenerated cases, which often makes the algorithm rather complex and error-prone to implement.
-We observe the important fact that the CSG evaluation is no more than splitting and selecting faces.
-Therefore, the only important thing during intersection test is to find out the potential edges and vertices of the result mesh.
-Therefore, we use a very concise graph model, with only a few extra data for classification on vertices, as the output of this stage.
+\subsubsection{Face classification}
 
-Another problem is that numerical error introduced by computing coordinates of intersection vertices often leads to fault topology construction in the later stage.
-Using high precision float point is the most common way to alleviate this issue.
-However, only the time-consuming rational number arithmetic can be absolutely precise.
+This step is to choose faces from the linked halfedges to generate the final mesh.
+Literally compute all the space indicators of each face is unacceptable slow for large CSG trees.
+Enlightened by Feito et.
+al.
+\cite{feito2013fast}, we utilize the geometry connectivity to accelerate this process.
+In Feito et.
+al.'s method, the faces of tessellated meshes are first grouped according to whether they have the same indicator vector.
+After the grouping, each group is classified as a whole.
+This is based on the observation that indicators of faces are spatially coherent.
+That is, if a face $f$ is outside of primitive $M_0$, the neighbor of $f$ are likely to be out of $M_0$, too.
+Different from Feito et.
+al.'s method, we also consider the condition when the number of primitives is larger than two.
+In this condition, space vector of a face may be partly the same with its neighborhoods'.
+That is, we allow space indicators not only share within faces of the same group, but also among different groups and even primitives.
+This is useful when the number of primitives is large, or intersections between primitives is complex.
+Details will be shown in section \ref{sec:classification}.
 
-\begin{figure}
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=1.5in]{p-reps}\\
-  \caption{Plane-based representation of triangles. The yellow triangle is represented by three bounding planes (green) and the supporting plane where the triangle lies. }\label{fig_p-reps}
-\end{figure}
+\section{Plane-based geometry}
 
- In order to be both robust and efficient, we choose not to compute the coordinates of intersection vertices until we finally construct the result topology.
-In the early stage, each new vertex is represented by intersection of three planes.
-This method is based on two facts: 1) Douze et al.
-[] observe that every intersected vertex is either the intersection between an edge and a plane, or the intersection of three planes.
-2) Campen et al.
-[] give an efficient method to precisely convert b-reps mesh into its plane-based representation (Fig.
-\ref{fig_p-reps}).
-Details is explained in the following.
+Vertex coordinates are commonly used in geometry computation.
+However, vertex coordinates suffer from inexact representation of intersection point between primitives.
+Therefore, we choose to use planes-based representation of polyhedrons and implicitly represent vertex by plane intersection.
+We start with a quick review of the basic conception of plane-based representation.
+After that, we introduce two substrates related to plane-based representation used in our method, since these two are rarely seen in related researches.
+Other substrates of plane-based representation can be seen in \cite{bernstein2009fast}.
 
-\subsection{Definition}
+\subsection{Conversion}
 
-Faces in a certain primitive can be classified into intersected faces and non-intersected ones according to whether they intersect other primitives.
-Our United Intersection Graph (UI-graph) is a graph data structure embedded in each intersected face.
-It is used to split these faces and guide the face classification.
+\label{sec:convert}
 
-The nodes of UI-graph of an intersected face $F$ are the vertices, include the original three corners of $F$ and all the intersected vertices within $F$.
-Intersected vertices are shared between different UI-graphs.
-For example, the vertex $a$ is generated by intersection between face $F_1$ from primitive $P_i$ and edge $e(G_1, G_2)$ from primitive $P_j$, where $e(G_1, G_2)$  is the shared edge of face $G_1$ and face $G_2$.
-Then face $F_1$, $G_1$, $G_2$ are all intersected faces and each of them contains a UI-graph with one of its node is $a$.
+As we discussed in Section \ref{sec:paradigm}, one of the problem in Boolean evaluation under vertex-based representation is it inevitably introduces new vertices, whose coordinates cannot be exactly represented using standard float-point number.
+On the other hand, if plane-based representation is used, no new geometry information needs to be constructed---the result mesh is composed of the planes of the input primitives.
+Therefore, we can use only geometric decision predicates to perform the Boolean operation.
 
-Douze et al.
-[] observed that vertices during a CSG evaluation can be divided into three types.
-The first order vertex is already contained in the input primitives.
-The second order vertex is the intersection between an edge and a face.
-The third vertex results from intersection of three faces from different primitives.
-Considering the degenerate cases, this classification is not complete because different types do overlap.
-But it does not matter because each vertex at least belong to one of these types.
-Then we can use the plane-based representation (Fig.
-\ref{fig_p-reps}) introduced by Campen et al.[], which treats each triangle face by a supporting plane surrounded by three bounding planes, to represent each vertex by intersection of three planes.
-This method has two advantages.
-First, it is universal for all kinds of vertices, thus is easy to handle.
-Second, we can avoid explicitly computing the coordinates of new introduced vertices to avoid introducing numerical error.
+Using plane-based representation, each face of polyhedron is represented by a supporting plane $S$, where the face lies, and a list bounding planes $\{B_i\}$, each corresponding an edge of the face.
+Edge line is represented by intersection of $S$ and the related $B_i$.
+Corner point is then the intersection of $S$ and two consecutive bounding planes $B_i$ and $B_{i+1}$.
+Efficient and exact conversion from the vertex-based representation to plane-based representation is described in detail in \cite{campen2010exact}.
+If the input vertex coordinates precision is $L$, the maximum precision $P$ required to represent the plane coefficients is:
+\begin{equation}
+\label{eq:precision}
+P = (L-1)+2(K-1)+3+1,
+\end{equation}
+where $K$  is the maximum bits to represent edge vector coordinates.
+If the plane coefficient has $M$ bit precision, $M$ have to greater than $P$ for exact representation.
+We rigorously enforce the criterion to $M \ge P+1$, and we will explain it in section \ref{sec:embed}.
 
-Also, each node contains data structure called vertex context.
-It records on which primitives and on which part of primitive the node lies.
-A vertex can lies on the vertex, edge or within the face of a certain primitive.
-For example, the vertex context of $a$ is $\{(F_1, P_i), (e(G_1, G_2), P_j)\}$.
-This information is very important for the classification of the neighborhood.
-In particular, we notice that the vertex context of a certain vertex is invariant in different UI-graphs.
-So we only need to maintain one context for each vertex and shared among UI-graphs.
+Let $\delta = 2^{K-L-1}$ be the relative length (in max-norm) of the
+longest edge in the mesh (relative to the bounding box).
+If we use IEEE 754 double precision ($M=53$) and assume $\delta \le 2^{-5.5}$, the maximum input precision $L$ can reach to 20, which is enough for most CAD application.
+As the precision of input coordinates is finite, we can determine in advance the upper boundary of precision needed to perform a precise decision, with which we can use fixed precision predicates techniques to gain much performance while keeping exactness.
+We implement the predicates using filtering techniques proposed by Shewchuk \cite{shewchuk1997adaptive}.
 
-The edges of UI-graph are simply the intersection line segments between faces of different primitives.
-They are represented by two references of the nodes in the UI-graph.
-No further information is required.
+\subsection{Substrates}
+\label{sec:substrates}
+Our method rigorously follows the paradigm of plane-based geometry.
+All decision predicates are computed using planes as input.
+These predicates include checking coincidence and co-orientation of planes, orientation of a plane with respect to a point, and whether three planes intersect in a unique point, etc.
+We omit the discussion of the predicates which is already in prior work \cite{bernstein2009fast,banerjee1996topologically}, and focus on specific predicates in our method in the following.
 
-As will explained below, we take two steps to construct UI-graphs for each intersected faces of the whole CSG.
-The first step is to build stand-alone UI-graphs for each pair of primitives, which is built upon our plane-based triangle-triangle intersection test, and the second step is to merge them into a single one for each intersected faces.
+Before we start the discussion, we first introduce several regulations frequently used in the rest of our paper.
+A plane $P_x$ can be represented by plane coefficients $(a_x, b_x, c_x, d_x)$.
+The normal of $P_x$ is denoted as $\vec{N}_x$.
+Under plane-based representation, a line $L$ can be represented by intersection of two planes $(P_m, P_n)$, or in short $L: (P_m, P_n)$.
+The positive direction of $L$ is defined by cross product of the normals of $P_a$ and $P_b$, that is, $\vec{L}=(a_m, b_m, c_m) \times (a_n, b_n, c_n)$.
+A point $p$ is represented by plane triples $(P_a, P_b, P_c)$, or in short $p: (P_a, P_b, P_c)$.
 
-\begin{figure}
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=1.7in]{raw3}\\
-  \caption{The UI-graph of a certain face. }\label{fig_raw3}
-\end{figure}
+Given two points $p$ and $q$ in the same edge line $L: (P_u, P_v)$, the two points can be represented by plane triples $(P_u, P_v, P_p)$ and $(P_u, P_v, P_q)$, sharing the same first two components.
+We want to determine if $q$ is in positive side of $p$ along the $\vec{L}$.
+We call this two-point comparison.
+This predicates can be converted to the problem of orientation of a plane $P_p$ with respect to a point $q$, except that there is an extra request---we have to guarantee cosine between $\vec{L}$ and the normal $\vec{N}_p$ be positive, that is:
+\begin{equation}
+\label{eq:pointcomp}
+   \left|
+  \begin{array}{ccc}   %该矩阵一共3列，每一列都居中放置
+  a_u  & b_u & c_u \\
+  a_v  & b_v & c_v \\
+  a_p  & b_p & c_p
+  \end{array}
+  \right| > 0,
+\end{equation}
+If not, we negate $P_p$ to be the test plane. The computation of this predicates is described in \cite{bernstein2009fast}.
 
-\subsection{Plane-Based Triangle-Triangle Intersection}
+Another predicates is used when tessellating a face (further explanation of its application is shown in Section \ref{}).
+Given two lines $L_a: (P_s, P_a)$ and $L_b: (P_s, P_b)$, which are on the same plane $P_s$, we want decide whether the sign of cross product of $\vec{L}_a$ and $\vec{L}_b$ has the same orientation as the normal $\vec{N}_s$.
+Direct solution requires to explicitly compute the vector of $L_a$ and $L_b$ and then decide the sign by $\vec{N}_s \cdot (\vec{L}_a \times \vec{L}_b)$.
+However, explicit representation of $\vec{L}_a$ and $\vec{L}_b$ requires more bits than standard double precision float point number, bringing extra computation burden.
+
+To solve this, we decompose the normal vectors of $P_a$ and $P_b$: $\vec{N}_a = \vec{N}^\parallel_a + \vec{N}^\perp_a$ and $\vec{N}_b = \vec{N}^\parallel_b + \vec{N}^\perp_b$.
+Here superscript `$\parallel$` means the vector is in the plane $P_s$ and `$\perp$` means it is orthogonal to $P_s$.
+Then $\vec{N}_a \times \vec{N}_b = \vec{N}^\parallel_a \times \vec{N}^\parallel_b + \vec{N}^\perp_a \times \vec{N}^\parallel_b + \vec{N}^\parallel_a \times \vec{N}^\perp_b + \vec{N}^\perp_a \times \vec{N}^\perp_b$.
+As we know $\vec{N}^\perp_a$ and $\vec{N}^\perp_b$ is parallel, $\vec{N}^\perp_a \times \vec{N}^\perp_b = \textbf{0}$.
+Now, we evaluate the expression: $\vec{N}_s \cdot (\vec{N}_a \times \vec{N}_b)$.
+Since $\vec{N}_s$ is orthogonal to both $\vec{N}^\perp_a \times \vec{N}^\parallel_b $ and $\vec{N}^\parallel_a \times \vec{N}^\perp_b $, we deduce $\vec{N}_s \cdot (\vec{N}_a \times \vec{N}_b) = \vec{N}_s \cdot (\vec{N}^\parallel_a \times \vec{N}^\parallel_b)$.
+Here we make an essential observation that $\vec{N}^\parallel_a \times \vec{N}^\parallel_b$ has the same direction as $\vec{L}_a \times \vec{L}_b$, that is:
+\begin{equation}
+\label{eq:cosine}
+sign(\vec{N}_s \cdot (\vec{N}_a \times \vec{N}_b)) = sign(\vec{N}_s \cdot (\vec{L}_a \times \vec{L}_b)),
+\end{equation}
+which means we do not need to explicitly compute $\vec{L}_a$ or $\vec{L}_b$. Instead, we only have to evaluate the left expression of equation \ref{eq:cosine}.
+
+\section{Exact Intersection Detection}
+
+\label{section:isect}
+In this step, intersections between faces are computed through the triangle-triangle intersection test within each critical cell.
+We adopt M\"{o}ller's intersection detection algorithm \cite{moller1997fast} on account of its efficiency and simplicity.
+However, because collision detection algorithms are often accompanied by non-robustness problems, a conventional implementation of this algorithm may cause unpredictable results.
+Therefore, we integrate plane-based geometry representation \cite{sugihara1990solid} into M\"{o}ller's algorithm to make it unconditionally precise and robust.
+In the following, we first make a quick review of M\"{o}ller's algorithm, then discuss the way to make it unconditional robust.
+At last, we talk about how to deal with degenerate cases.
+
+\subsection{Vertex-based method review}
 
@@
 \centering
-\includegraphics[width=3.0in]{projection}
+\includegraphics[width=2.5in]{projection}
 \caption{$Seg_1$ is the intersection between $S_2$ and $F_1$.
@@
 
-The plane-based triangle-triangle intersection (PTTI) test is largely the variant of M\"{o}ller's triangle intersection test [].
-M\"{o}ller's algorithm computes the intersection between two triangles $F_1$ and $F_2$ in three steps, as illustrated in Fig.
-\ref{fig_projection}.
-First, an early rejection is performed by testing whether $F_1$ intersects the plane where $F_2$ lies, which is denoted as $S_2$.
+M\"{o}ller's algorithm computes the intersection between two triangles $F_1$ and $F_2$ in three steps (Fig. \ref{fig_projection}).
+\begin{itemize}[leftmargin=0.45cm]
+\item[1)] An early rejection is performed by testing whether $F_1$ intersects the plane where $F_2$ lies, which is denoted as $S_2$.
 This is a necessary condition of intersection between $F_1$ and $F_2$.
 If this test is passed, then the same is performed for $F_2$ and $S_1$, where $S_1$ is the plane of $F_1$.
-Second, the intersection between $F_1$ and $S_2$, denoted as $Seg_1$, and the intersection between $F_2$ and $S_1$, denoted as $Seg_2$, are separately computed .
-At last, the intersection between $F_1$ and $F_2$ is determined by computing the overlap area of $Seg_1$ and $Seg_2$ .
+\item[2)]The intersection between $F_1$ and $S_2$, denoted as $Seg_1$, and the intersection between $F_2$ and $S_1$, denoted as $Seg_2$, are separately computed .
+ \item[3)]The intersection between $F_1$ and $F_2$ is determined by computing the overlap area of $Seg_1$ and $Seg_2$ .
+\end{itemize}
 
@@
 
-Conventional implementations of M\"{o}ller's algorithm use vertex-based representation and usual float point arithmetic.
-However, this is neither exact nor robust.
+Conventional implementations of M\"{o}ller's algorithm use vertex-based representation and common float point arithmetic, which is neither exact nor robust.
 In Fig.
@@
 Although implementing M\"{o}ller's algorithm with arbitrary precision arithmetic could make it robust, it is too costly for a large CSG evaluation.
-Actually, the non-robustness of this algorithm is from \emph{constructions} \cite{bernstein2009fast}, which compute new coordinates of geometry objects based on the known coordinates of existing ones.
+Actually, the non-robustness of this algorithm is from geometry \emph{constructions} \cite{bernstein2009fast}, which compute new coordinates of geometry objects based on the known coordinates of existing ones.
 In M\"{o}ller's algorithm, the coordinates of $Seg_1$ and $Seg_2$ (Fig.
@@
 
-Fortunately, according to Sugihara and Iri \cite{sugihara1990solid}, geometry computation of Boolean operations can be restricted to predicates using plane-based representation of polyhedra.
-This motivated us to integrate plane-based representation into M\"{o}ller's algorithm.
-Exact and efficient predicate computation is performed using precise geometry predicate techniques \cite{shewchuk1997adaptive}.
-Details of our implementation are shown below.
+\subsection{Plane-based technique embedding}
 
-\begin{figure}
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=1.7in]{p-reps}\\
-  \caption{Plane-based representation of triangles. The yellow triangle is represented by three bounding planes (green) and the supporting plane where the triangle lies.}\label{fig:p-reps}
-\end{figure}
-
-We first convert $F_1$ and $F_2$ into their respective plane-based representations: a supporting plane surrounded by three bounding planes (Fig.
-\ref{fig:p-reps}).
-We implement this conversion using the exact conversion method by Campen and Kobbelt \cite{campen2010exact}.
-Then, in our implementation, the relative position of a point and a plane can be determined by computing the sign of the multiplication of determinants \cite{sugihara1990solid}.
-To avoid introducing errors, we represent the end points of $Seg_1$ and $Seg_2$  by intersections of plane triples, rather than by directly computing their coordinates.
-As illustrated in Fig.
-\ref{fig:isect}(a), these points are the intersection between an edge line of a face and the supporting plane of the other face.
-Because the edge line of $F_1$ can be represented as $[S_1, S_X]$ (or $[S_2, S_X]$ for an edge line of $F_2$), where $S_X$ is the corresponding bounding plane of the edge, the end points of $Seg_1$ or $Seg_2$ can be represented in the form of $[S_1,S_2,S_X]$.
-In Fig.
-\ref{fig:isect}, we list all non-coplanar intersection situations between a triangle and a plane, and the $S_X$  in each situation.
+\label{sec:embed}
+According to the method described in section \ref{sec:convert}, triangle faces $f$ are firstly converted to its plane-based representation: a supporting plane $P_{s,f}$ surrounded by three bounding planes $P^i_{b,f}, i = 1,2,3$.
+We introduce the plane-based implementation of M\"{o}ller's algorithm step by step in the following:
 
@@
 \caption{We denote the signed distance from point $X$ to plane $S_2$ as $d_X$.
-All the four non-coplanar conditions of intersection between $F_1$ and $S_2$ (denoted as $Seg_1$) are:  (a) $d_A\cdot d_C<0$, $d_B\cdot d_C<0$; (b) $d_A=0$, $d_B=0$, $d_C\neq 0$; (c) $d_A=0$, $d_B\cdot d_C<0$; (d) $d_A=0$, $d_B\cdot d_C>0$.
+All the four conditions of intersection between $F_1$ and $S_2$ (denoted as $Seg_1$) are:  (a) $d_A\cdot d_C<0$, $d_B\cdot d_C<0$; (b) $d_A=0$, $d_B=0$, $d_C\neq 0$; (c) $d_A=0$, $d_B\cdot d_C<0$; (d) $d_A=0$, $d_B\cdot d_C>0$.
 End points of $Seg_1$ are intersections between $S_2$ and related edge lines of $F_1$ (bold edges).}
@@
 
-The intersection between $F_1$ and $F_2$ is the overlap area of $Seg_1$ and $Seg_2$.
+\begin{itemize}[leftmargin=0.45cm]
+\item[1)] In this step, we only need to compute the orientation of a plane $(a, b, c, d)$
+with respect to a point $(x, y, z)$, that is to compute:
+\begin{equation}
+sign(ax+by+cz+d).
+\end{equation}
+Using the notation in section \ref{sec:convert},  we know the coordinates of the points are precisely represented by $L$ bits.
+Also, after the conversion, the precisions of four coefficients of the supporting plane are $(P', P', P', P)$, where $P'=P-(L-1)-2$ and $P$ is defined in equation \ref{eq:precision}.
+Using the strengthened criterion $M \ge P+1$, we find that $M$ bits are enough to perform the predicates.
+This observation allow us to perform very efficient early discard on the triangle-triangle intersection test, which is the key idea to stay efficiency while perusing exactness.
+\item[2)]In step 2, constructions are avoid by explicitly represent the end points of $Seg_1$ and $Seg_2$ using plane triples.
+As illustrated in Fig.
+\ref{fig:isect}(a), these points are the intersection between an edge line of a face and the supporting plane of the other face.
+Because the edge line of $f_1$ ($f_2$) can be represented as $[P_{s, f_1}, P^i_{b, f_1}]$ ($[P_{s, f_2}, P^i_{b, f_2}]$), the end points of $Seg_1$ ($Seg_2$) can be represented in the form of $[P_{s, f_1}, P_{s, f_2}, P^i_{b, f_2}]$ ($[P_{s, f_1}, P_{s, f_2}, P^i_{b, f_1}]$).
+In Fig.
+\ref{fig:isect}, we list all intersection situations between a triangle and a plane, and the corresponding bounding plane in each situation.
+Note, coplanar situation will be discussed later in section \ref{sec:degenerate}.
+ \item[3)] The intersection between $f_1$ and $f_2$ is the overlap area of $Seg_1$ and $Seg_2$.
 It can be easily computed by comparing the end points of $Seg_1$ and $Seg_2$ along $L$ (Fig.
-\ref{fig_projection}), where $L$ is the intersection between $S_1$ and $S_2$.
-Unlike M\"{o}ller's implementation, our approach uses no projection, which requires the exact point coordinates.
-We call the direction of vector $\vec{N}_1\times \vec{N}_2$ the positive direction, where $\vec{N}_1$ and $\vec{N}_2$ are normals of $S_1$ and $S_2$ respectively.
-Given two points $A$ and $B$ on $L$,  we compute the sign of the multiplication of determinants:
-\begin{equation}
-\label{eq:sign}
-  K(A, B)=
-  \left|
-  \begin{array}{c}   %该矩阵一共3列，每一列都居中放置
-  \vec{S}_1 \\ \vec{S}_2 \\ \vec{S}_A \\ \vec{S}_B
-  \end{array}
-  \right|
-  \left|                 %左括号
-  \begin{array}{c}   %该矩阵一共3列，每一列都居中放置
-  \vec{N}_1 \\\vec{N}_2 \\\vec{N}_A
-  \end{array}
-  \right|
-  \left|                 %左括号
-  \begin{array}{c}   %该矩阵一共3列，每一列都居中放置
-  \vec{N}_1 \\\vec{N}_2 \\\vec{N}_B
-  \end{array}
-  \right|,
-\end{equation}
-where $\vec{S}_X$ is the coefficient vector of plane equation $[a_X,b_X,c_X,d_X]$,  and $ \vec{N}_X$ is the normal vector $[a_X,b_X,c_X]$.
-If $K(A, B)$ is positive (negative), this means that $A$ lies in the positive (negative) direction of $B$.
-Otherwise, $A$ and $B$ are coincident.
+\ref{fig_projection}), where $L$ is the intersection between $P_{s, f_1}$ and $P_{s, f_2}$.
+Because end points are all represented using plane triples, we can use the technique discussed in section \ref{sec:substrates} to implement the comparison.
+\end{itemize}
 
-One may find that we do not give the solution of coplanar cases.
-This is deliberate because we find recording coplanar cases is not necessary for the following process.
-This will be discussed further in Section 5.
+\subsection{Intersection record}
+\label{sec:ir}
 
-\subsection{Generating Pairwise UI-Graphs}
+The output of this stage, or what we call triangle-triangle intersection record (TTIR), is the data structure which organize the results of triangle-triangle intersection test.
+TTIR is also the input of tessellation, and is in deep couple with the tessellation method.
+It is hard to give full idea of how we design TTIR before we introduce our tessellation algorithm.
+We first give several requirements from tessellation stage, and then discuss the compositions of TTIR.
+To have a comprehensive understanding of TTIR, readers may need to review this section after finish reading section \ref{sec:tessellation}.
 
-As a general case, an intersected face intersects with one or more primitives. This means there could be so many different types of degenerate cases, that it is not easy
+We recall our description of LHEC in section \ref{sec:meshes}, we need to transfer necessary information by TTIR to tessellation stage for LHEC construction. Necessary information includes:
+\begin{itemize}
+  \item The plane-based representation of intersection vertices.
+  \item Intersection line segments, each consisting of references of two end points.
+  \item Intersection context of the intersection line segments.
+\end{itemize}
 
-we choose divide and conquer \cite{ogayar2005point} \cite{douze2015quickcsg}
+For example, assume two triangle faces $f_1$ and $f_2$, from primitive $A$ and $B$, intersect at line segment $(v_1, v_2)$, where $v_1$ and $v_2$ are references of two end points.
+First, $v_1$ and $v_2$ are introduced to $A$ and $B$, then intersection line segment $(v_1, v_2)$ is stored on both $f_1$ and $f_2$.
+At last, intersection context of $(v_1, v_2)$ is attached as an attribute.
+In this case, the intersection context of $(v_1, v_2)$  is $f_1$ for $A$ and $f_2$ for $B$.
 
-We first consider constructing UI-graph between each pair of primitives.
-The graph generated by two primitives is much simpler than a n-primitive one: since input primitives are not self-intersected, there is no cross or overlap between intersection line segments.
+In LHEC, there must not be any repetitive vertices within each LHEC or among LHECs in order to reconstruct the correct topology.
+Therefore, repetitive vertices elimination must be performed.
+Checking whether there are coincident points in a global scope can be quite inefficient.
+Fortunately, it is easy to figure out the location of an intersection vertex---whether it is inside, on a certain edge, or coincident with one of the three corners of intersection faces.
+Therefore, if we store the references of vertices on faces, edges, coincidence detection is localized and repetitive vertices elimination can be very fast.
 
-When PTTI test detects a intersection, it outputs the two end points of intersection line segment, or, in a degenerate case, two coincident points.
+// 区分context and plane representation
 
-\subsection{Merging UI-Graphs}
+\subsection{Degenerate cases}
+\label{sec:degenerate}
 
-Mainly deal with intersection between intersection line segments. It is necessary when a face intersects with faces from more than one other primitives.
+Before we discuss the degenerate cases, we give three principles for handling them.
+First, we want our method be unconditional robust and exact, so all degenerate cases should be well handled (completeness).
+Second, to control the complexity of tessellation, we want degenerate cases to be invisible to tessellation, that is, degenerate cases have the same format of output as non-degenerate cases (invisibility).
+Third, we want the outcome of tessellation be as simple as possible.
+That is, intersection line segments that will not help tessellation, if recognized, are disposed (simplicity).
 
-Atom operation:
+To ensure the completeness, we classify all degenerate cases into three categories by the dimension of intersection:
 
-1. add an vertex. no need outside a graph
+\subsubsection{Intersects on point}
+Point is degenerate case of line segment with zero length.
+The intersection point is potentially a vertex in the LHEC.
+There are two kinds of vertices, depending on whether the vertex is isolated.
+An isolated vertex does not need to participate tessellation.
+On the other side, if the intersection point is not isolated, it is end point of other intersection line segment and will be introduced when that intersection line segment is detected.
+Therefore, we treat the cases of intersection on point as non-intersection cases.
 
-2. remove/add edges.
+\subsubsection{Intersects on line segment}
+This category is often not degenerate cases.
+However, when intersection line segment lies on a edge of one of the two triangle faces (Fig.
+\ref{fig:isect}b), error will occur if not careful.
+In this case, there will be another pair of triangle faces that will have exactly the same intersection line segment (Fig.
+\ref{fig:isect2}).
+This is what we called twin intersections.
+With twin intersections exist, one intersection line segment will be inserted twice, requiring extra effort to eliminate repetitions.
+To make things worse, the intersection will have different intersection contexts.
 
-3. sort along an edge.
+Twin intersection can be treated as union to resolve this.
 
-4. merge vertices.
+\subsubsection{Coplanar}
 
-comparison:
+\begin{figure}[t]
+\centering
+\includegraphics[width=3.5in]{degenerate}
+\caption{}
+\label{fig:isect2}
+\end{figure}
 
- If coplanar (collinear), choose a direction as positive. 3-4-2
- If not, compute intersection, 4-2
+Coplanar cases can also be seen as a special type of twin intersections. One is valid case, another is not.
 
-\section{Multi-level Flood-filling Classification}
-\label{section:floodfill}
+\section{Deferred Tessellation}
 
-Flood-filling is all about giving a seed and propagation. In this chapter, from down to top, we introduce this process and explain how it can save computation time.
+\label{sec:tessellation}
+This is the step to process TTIR and output LHIC, where the tessellation happens.
+We called this process as deferred tessellation because we do not tessellate until we collect all intersection line segments.
+For this problem, Ogayar-Anguita et.
+al.
+\cite{ogayar2015deferred} try to use Constrained Delaunay Triangulation (CDT) to solve, as the recorded intersection is naturally the constraints.
+It works fine for Boolean operation of two primitives.
+However, when there are more than two primitives, simply using CDT covers the complexity of tessellation.
+In such case, the intersection line segments may cross, overlap and even coincident with each other, introducing new vertex, splitting original intersection line segments.
+Naive implementation of CDT may lead to holes, repetitive edges, and other topology errors.
 
-\subsection{Background}
-\label{sec:intuitive}
+To solve these problems, we first refine the TTIR into an intermediate data structure---\emph{tessellation graph}.
+In this process, we resolve any intersection between intersection.
+After this, we tessellation each face according its corresponding tessellation graph.
+To make this process unconditional robust and exact, we utilize plane-based techniques and do not compute explicitly the coordinates of intersection points throughout this step.
 
-\subsection{Flood-filling Inside a Triangle}
+\subsection{Tessellation graph}
 
-\subsubsection{Compute indicator vector}
+TTIRs are only loose data that store the coordinates of intersection line segments.
+To perform tessellation and extract sub-faces, we need to organize TTIRs in a face scope.
+We use a graph-based data structure---tessellation graph---for this purpose.
+For each intersection face which needs tessellation, we construct tessellation graph.
+A tessellation graph is the graph-like description of the tessellated face topology.
+Nodes of tessellation graph represent vertices, and edges represent edges in LHIC.
+To avoid ambiguity, we call original three edges of the face as \emph{face boundaries} in the following.
+An important feature of tessellation graph is that it uses uniform representation for intersection vertices and line segments, and face boundaries and the original three corners.
+This dramatically reduces complexity of extracting sub-faces and allowing the following process simple and fast.
 
-How to propagate the indicator vector from the seed vertex to all the vertex in a triangle.
+\subsubsection{Definition and construction}
 
-Start from a full indicator
+Nodes of tessellation graph represent vertices and store the coordinates of them.
+Edges are nondirectional ones, and store the intersection context if exist.
+We classify graph edges into two types: we call edges on face boundaries as \emph{boundary edges} and edges inside face as \emph{inner edges}.
+They are different in at least two aspects: first, the boundary edges may not have a intersection context since it is not coincident with any TTIR; second, in the view of halfedge, inner edges represent two halfedges but boundary edges represent only one halfedge.
+The same classification is for intersection line segments: if the intersection are inside the face, it is an inner intersection, otherwise a boundary intersection.
+//可以提前到degenreate case
 
-\subsubsection{Facet classification}
+Recall our definition of TTIR in section \ref{sec:ir}, we find most of the work has already been done.
+To construct inner edges, we only need to first collect all vertices on the face (including both inside vertices and boundary vertices) to be the nodes, and then connect nodes by inner intersections.
+However, boundary edge construction is not that easy.
+We cannot simply connect the three face corners to be the boundary edges, since there may be boundary intersections, and face edges have to be splitted.
 
-How to generate new face and classify faces using indicator vector.
+To construct boundary edges of graph, we first need to first sort vertices on each face edge along the edge line.
+This is done by two-point comparison in section \ref{sec:substrates}.
+After the sort, we connect the nodes by their sequence on the edge line to form the boundary edges.
+If any boundary edge is coincident with boundary intersection, we assign the intersection context of the boundary intersection to the boundary edge.
 
-\subsubsection{Acceleration}
+\subsubsection{Intersection refinement}
 
-How to reuse the indicator vector of neighbouring vertex.
+Since tessellation graph is a graph-like description of halfedge, it has extra constraints on its form.
+The most important one is that edges should not intersect each other.
+This can be guaranteed when there are only two primitives,  because the surface of primitives is all watertight, non-manifold, and without self-intersection.
+However, when there are more than two primitives, this constraint can be violated.
+In the view of intersection detection, it is not enough to find all intersection vertices by only triangle-triangle intersection test.
+This is because the new vertex can be formed not only by edge intersects plane, but also by three planes, which involves more than two triangles.
+Therefore, an extra processing--intersection refinement---is necessary to resolve these intersections before constructing tessellation graph.
 
-\subsubsection{Coplanar degenerate case}
+Intersection refinement is performed between every two intersection line segments from different primitives.
+Using plane-based representation, whether two intersection line segments intersect is determined by predicate of orientation of plane against a point.
+For example, we want determine whether $I_v$: $(v_b, v_e, P_v, f_0, C_v)$ and $I_u$: $(u_b, u_e, P_u, f_0, C_u)$ intersects.
+% 需要在IR那一章补充plane rep of intersection这一部分。intersection is describe with 四元组。
+It is done by checking whether $u_b, u_e$ is on different sides of $P_v$ and whether $v_b, v_e$ is on different sides of $P_u$.
+If yes, $I_v$ and $I_u$ intersects and introduced new intersection vertex, which is the intersection of $P_u, P_v$ and the supporting plane $f_0$.
 
-Special case discussion, mainly for coplanar problem.
+Degenerate cases will occur when $I_u$ and $I_v$ intersect on end point(s) or $I_v$ and $I_v$ are collinear.
 
-\subsection{Flood-filling Through CSG Primitives}
+\subsection{Extracting sub-faces}
+The last step of tessellation is to really change the topology of input primitive to construct LHICs.
+We could apply CDT here since the intersection is refined and there is no intersection between the constraints.
+However, we choose to design a new method to extract sub-faces from intersection face for the efficiency:
+\begin{itemize}
+  \item lose topology information
+  \item may not need to triangulate, classify in a whole
+  \item hard to implement with planes
+\end{itemize}
 
-\subsubsection{Seed generation}
+There is yet another problem on this method. Our method of extracting sub-faces assume that the tessellation graph is connected. However, this assumption can be false (Fig.).
 
-\subsubsection{Flood-filling within primitives}
+\section{Face Classification}
 
-\subsubsection{Flood-filling between primitives}
+\label{sec:classification}
+As the final stage, face classification classify all candidate faces in linked halfedges, and decides which faces belong to the final mesh.
+Classification is done by evaluating the indicator vector of each face.
+During this process, we take advantage of plane-based representation to ensure unconditional correct classification.
+Also, as we maintain the geometry intra-primitive connectivity (by halfedge structure) and inter-primitive (by denoting shared vertex), we can utilize the space coherence of indicator vectors to accelerate this process.
 
-\subsubsection{Acceleration}
+In this section, we will first give a overall framework of face classification, then introduce how to classify each individual face.
+At last, we discuss how to accelerate this process by caching intermediate classification result.
 
-\section{Experiments and Discussion}
+\subsection{Basic idea}
 
-\section{Conclusion}
+The space coherence of indicator vectors means neighboring faces often have the same indicator vector, or share most components of indicator vectors.
+This means if we figure out the indicator vector of a face, we may know the indicator vectors of its neighboring faces instantly.
+In other cases, modification must be applied to the indicator vector.
+The necessary and sufficient condition of indicator change is that the two faces lie on different side of the primitive boundary.
+In our method, it means there will be intersection context on the shared edge of the two faces (section ??).
+Because the indicator change can be figured out  by the intersection context efficiently (section ??), we can classify all the faces of linked halfedges using flood-filling method.
+
+The indicator vector of the first face is special.
+We can guarantee that the whole vector can be figured out only by intersection context of the face edges.
+Thus, point-in-polyhedron test is used for compensation.
+This works well under the assumption that the indicator of the sample point is the same with the face.
+For the point inside the face, the answer is absolutely yes, because the whole face must be classified as a whole.
+However, the coordinates of the inner points cannot be exactly represented, thus may lead to wrong predicates.
+Therefore, we choose to the use the face corners for point-in-polyhedron test.
+The test must be guaranteed to be exact, and, on the other hand, efficiency is not so important as we won't need many such tests.
+If ray-trace algorithm is used for the point-in-polyhedron test, the octree built during space division might be useful [].
+
+However, use face corner instead of inner points has another problem.
+The indicator vector of the corner may not be the same as the of the indicator vector of the whole face.
+Figure ?
+shows such condition occurs when any of the face edge is on the boundary of other primitive.
+Nevertheless, we do not to worry about this.
+This is because when such case occurs, one of the edge adjacent to that corner will have intersection context to of that primitive, by which we can figure out the real indicator.
+
+Another thing needs to be noticed is that the neighborhood of a certain face $f$ from primitive $A$ in linked halfedges does not only contain the face in $A$, but also include faces from other primitives which share edges with $f$.
+It can be efficiently found because in linked halfedges, coincident vertices between primitives are shared.
+Therefore, the indicator vector can be transfer not only intra-primitive, but also inter-primitive.
+
+\subsection{Fast and exact face classification}
+
+During flood-filling, we propagate the indicator vector of the current face $f_0$ to its neighboring faces, which have shared edges with the current face.
+If one of shared edges has intersection context $C_{I_v \mapsto A}$, it means the indicator of primitive $A$, denoted as $i_A$, could be different for the corresponding neighboring face $f_i$.
+In this section, we will show that $C_{I_v \mapsto A}$ is enough to compute the new $i_A$ for $f_i$.
+We only discuss the condition that $f_i$ is a triangle in the following.
+However, $f_i$ may not be triangle, not even a convex polygon.
+In these conditions, we can select a triangle subset of $f_i$ to represent $f_i$, since $f_i$ is guaranteed to be classified as a whole.
+
+Feito et.
+al.
+had noticed that intersection neighborhood can be used for fast classification of faces around the intersection.
+According to their method, faces adjacent to intersection line segments must have neighbors from other primitive(s) that define the position and orientation for each other.
+Unfortunately, Feito et.
+al.
+did not give detail description of how to implement a exact classification, nor discuss about degenerate cases such as coplanar faces.
+As Feito et.
+al.
+use geometry connectivity for classification, any incorrect classification can be spread to neighborhoods, which may cause errors in a wide range.
+
+We develop an exact and robust classification method based on the idea of using intersection neighborhood information.
+The intersection neighborhood is abstracted into two situations of intersection context (section ??).
+To make a clear description, we denote the three corners of neighboring face $f$ as $v_0^I$, $v_1^I$, $v_2$, where the superscript means the vertex lies on the intersection line segment $I$ with intersection context $C_{I \mapsto A}$.
+In the first situation, the intersection $I$ lies on the face of primitive $A$.
+That is, $C_{I \mapsto A} = f_x^A$.
+To calculate indicator $i_A$ for $f$, we only need to decide on which side of $f_x^A$ the current  face $f$ lies.
+Any sample point on $f$ except those on $I$ can be used for this predicates.
+As we can get the exact coordinates of corners, we choose $v_2$ to compute $i_A(f)$.
+
+If $I$ lies on edge of primitive $A$,  the intersection context is face pair: $C_{I \mapsto A} = (f_p^A, f_q^A)$.
+This situation is a little more complex that we cannot decide $i_A$ until we check the orientations of both $f_p^A$ and $f_q^A$.
+To correctly classify $f$, we first build BSP structure using $f_p^A$ and $f_q^A$ [?], and then determine the space indicator $i_A(v_2)$ by the BSP.
+As coordinate of $v_2$ and all the planes can be exactly computed, the classification is exact.
+The indicator of the face $i_A(f)$ should be the same as $i_A (v_2)$.
+It is because under a BSP structure with only two division planes, any sample point on $f$ except those on $I$ has the same $\lambda_A$ (Fig.
+??).
+
+\subsection{Caching evaluation results}
+
+If the CSG tree is large, with tens of, or even hundreds of nodes, computing $\lambda_\Phi(f) = \Phi(\vec{\lambda}(f))$ for every face can be costly.
+Considering the space coherence of indicator, we use cache techniques --- by storing the evaluation result of $\Phi$ --- to save the computation time.
+
+The most simple cache strategy is final result cache.
+We know indicator vector $\vec{\lambda}$ will not change if there is no intersection context during spreading.
+That means the final classification $\lambda_\Phi$ will not change, too.
+Thus, those faces sharing the same $\lambda$ can be classified as a whole.
+
+Also, we can also do intermediate result cache.
+It should be noticed that $\Phi(\vec{\lambda}(f))$ can be simplified if some components of $\vec{\lambda}$ is fixed.
+For example, assume we have a Boolean expression $M_1\cup (M_2\cap M_3-M_4)$.
+Given the values of two indicators $\lambda_1(x)=out$, $\lambda_2(x)=in$, the expression can be rewritten as $out\cup (in\cap M_3-M_4)$.
+Using the combination rules we can simplify the expression as $M_3-M_4$.
+This fact is important because for a large CSG tree, a certain primitive, denoted as $M_x$, often only intersects with a few other primitives $\Theta= \{M_{n_1}, M_{n_2}, \cdots, M_{n_k}\}$.
+That means all the faces in $M_x$ has the same indicators for the primitives not in $\Theta$.
+Therefore, we can first determine these fixed indicators and simplify the Boolean function $\Phi$ into a simpler one $\Phi_{M_x}$, and then use $\Phi_{M_x}$ to compute the final indicator for each faces.
+
+\section{Experiments}
+
+\section{Summary}
+
 In this paper, we proposed a novel method to evaluate CSG with triangular mesh primitives.

### 2016-06-12 summary.tex
before delete equation 3.

@@
 
-As we discussed in Section \ref{sec:paradigm}, one of the problem in Boolean evaluation under vertex-based representation is it inevitably introduces new vertices, whose coordinates cannot be exactly represented using standard float-point number.
-On the other hand, if plane-based representation is used, no new geometry information needs to be constructed---the result mesh is composed of the planes of the input primitives.
-Therefore, we can use only geometric decision predicates to perform the Boolean operation.
-
-Using plane-based representation, each face of polyhedron is represented by a supporting plane $S$, where the face lies, and a list bounding planes $\{B_i\}$, each corresponding an edge of the face.
-Edge line is represented by intersection of $S$ and the related $B_i$.
-Corner point is then the intersection of $S$ and two consecutive bounding planes $B_i$ and $B_{i+1}$.
+As we discussed in Section \ref{sec:paradigm}, one of the problem in Boolean evaluation under vertex-based representation is it inevitably introduces new vertices, whose coordinates cannot be exactly represented using common float-point number.
+On the other hand, if plane-based representation is used, no new geometry information needs to be constructed.
+Therefore, we can use only geometric decision predicates to perform the boundary evaluation, which means it is exact and robust.
+
+Using plane-based representation, each face of polyhedron is represented by a supporting plane $p^s$, where the face lies, and a list bounding planes $\{p^b_i \ \vert\  i = 1, 2, 3\}$, each has  a corresponding edge.
+Edge line is represented by intersection of $p^s$ and the related $p^b_i$.
+Corner vertex is then the intersection of $p^s$ and two consecutive bounding planes $p^b_i$ and $p^b_{i+1}$.
 Efficient and exact conversion from the vertex-based representation to plane-based representation is described in detail in \cite{campen2010exact}.
-If the input vertex coordinates precision is $L$, the maximum precision $P$ required to represent the plane coefficients is:
+If the input vertices precision is $L$, the maximum precision $P$ required to represent the plane coefficients is:
 \begin{equation}
@@
 \end{equation}
-where $K$  is the maximum bits to represent edge vector coordinates.
-If the plane coefficient has $M$ bit precision, $M$ have to greater than $P$ for exact representation.
-We rigorously enforce the criterion to $M \ge P+1$, and we will explain it in section \ref{sec:embed}.
+where $K$  is the maximum bits to represent edge vector components.
+If the plane coefficient has $M$ bit precision, $M$ have to greater than or equal to $P$ for exact conversion.
+However, different from \cite{campen2010exact}, we choose to enforce the criterion to $M \ge P+1$, and we will explain the enforcement in section \ref{sec:embed}.
 
@@
 longest edge in the mesh (relative to the bounding box).
-If we use IEEE 754 double precision ($M=53$) and assume $\delta \le 2^{-5.5}$, the maximum input precision $L$ can reach to 20, which is enough for most CAD application.
+If we use IEEE 754 double precision ($M=53$) and assume $\delta \le 2^{-5.5} \approx 0.22$, the maximum input precision $L$ can reach to 20, which is enough for most application.
 As the precision of input coordinates is finite, we can determine in advance the upper boundary of precision needed to perform a precise decision, with which we can use fixed precision predicates techniques to gain much performance while keeping exactness.
@@
 Our method rigorously follows the paradigm of plane-based geometry.
-All decision predicates are computed using planes as input.
+Predicates are all computed using planes as input.
 These predicates include checking coincidence and co-orientation of planes, orientation of a plane with respect to a point, and whether three planes intersect in a unique point, etc.
-We omit the discussion of the predicates which is already in prior work \cite{bernstein2009fast,banerjee1996topologically}, and focus on specific predicates in our method in the following.
+In the following, we only focus on two specific predicates.
+Other substrates may refer to \cite{bernstein2009fast}.
 
 Before we start the discussion, we first introduce several regulations frequently used in the rest of our paper.
-A plane $P_x$ can be represented by plane coefficients $(a_x, b_x, c_x, d_x)$.
-The normal of $P_x$ is denoted as $\vec{N}_x$.
-Under plane-based representation, a line $L$ can be represented by intersection of two planes $(P_m, P_n)$, or in short $L: (P_m, P_n)$.
-The positive direction of $L$ is defined by cross product of the normals of $P_a$ and $P_b$, that is, $\vec{L}=(a_m, b_m, c_m) \times (a_n, b_n, c_n)$.
-A point $p$ is represented by plane triples $(P_a, P_b, P_c)$, or in short $p: (P_a, P_b, P_c)$.
-
-Given two points $p$ and $q$ in the same edge line $L: (P_u, P_v)$, the two points can be represented by plane triples $(P_u, P_v, P_p)$ and $(P_u, P_v, P_q)$, sharing the same first two components.
-We want to determine if $q$ is in positive side of $p$ along the $\vec{L}$.
-We call this two-point comparison.
-This predicates can be converted to the problem of orientation of a plane $P_p$ with respect to a point $q$, except that there is an extra request---we have to guarantee cosine between $\vec{L}$ and the normal $\vec{N}_p$ be positive, that is:
+A plane $p_x$ can be represented by plane coefficients $(a_x, b_x, c_x, d_x)$.
+The normal of $p_x$ is denoted as $\vec{n}_x$.
+Under plane-based representation, a line $l$ can be represented by intersection of two planes $(p_m, p_n)$, or in short, $l: (p_m, p_n)$.
+The positive direction of $l$ is defined by cross product of the normals of $p_a$ and $p_b$, that is, $\vec{l} = \vec{n}_a \times \vec{n}_b$.
+A point $v$ is represented by plane triples $(p_a, p_b, p_c)$, or in short, $v: (p_a, p_b, p_c)$.
+
+Suppose there is an edge $e_i(f)$ of a face $f$, and the line of $e_i(f)$, denoted as $l_{i}(f)$, can represented as intersection of supporting plane $p^s(f)$ and bounding plane $p_i^b(f)$.
+Given two arbitrary points $v_p$ and $v_q$ on $l_{i}(f)$, they can be represented by plane triples $(p^s(f), p_i^b(f), p_p)$ and $(p^s(f), p_i^b(f), p_q)$, sharing the same first two components.
+We want to determine if $v_q$ is in positive side of $v_p$ along $\vec{l}_{i}(f)$.
+We call this predicate as \emph{two-point-one-line comparison}.
+This problem can be converted to the problem of orientation of a plane $p_p$ with respect to a point $v_q$, except that there is an extra request---we have to guarantee cosine between $\vec{l}_{i}(f)$ and the $\vec{n}_p$ (normal of plane $p_p$) be positive, that is:
 \begin{equation}
@@
 \end{equation}
-If not, we negate $P_p$ to be the test plane. The computation of this predicates is described in \cite{bernstein2009fast}.
+If not, we negate $P_p$ to be the test plane.
 

### 2016-06-12 summary.tex
即将去掉不鲁棒的示意图部分。

@@
 The normal of $p_x$ is denoted as $\vec{n}_x$.
-Under plane-based representation, a line $l$ can be represented by intersection of two planes $(p_m, p_n)$, or in short, $l: (p_m, p_n)$.
+Under plane-based representation, a line $l$ can be represented by intersection of two planes $(p_m, p_n)$, or in short, $l\colon(p_m, p_n)$.
 The positive direction of $l$ is defined by cross product of the normals of $p_a$ and $p_b$, that is, $\vec{l} = \vec{n}_a \times \vec{n}_b$.
-A point $v$ is represented by plane triples $(p_a, p_b, p_c)$, or in short, $v: (p_a, p_b, p_c)$.
+A point $v$ is represented by plane triples $(p_a, p_b, p_c)$, or in short, $v\colon(p_a, p_b, p_c)$.
 
@@
 We call this predicate as \emph{two-point-one-line comparison}.
-This problem can be converted to the problem of orientation of a plane $p_p$ with respect to a point $v_q$, except that there is an extra request---we have to guarantee cosine between $\vec{l}_{i}(f)$ and the $\vec{n}_p$ (normal of plane $p_p$) be positive, that is:
+This problem can be converted to the problem of orientation of a plane $p_p$ with respect to a point $v_q$, except that there is an extra request---we have to guarantee cosine between $\vec{l}_{i}(f)$ and the $\vec{n}_p$ (normal of plane $p_p$) be positive.
+If not, we negate the normal of $p_p$, and the coordinate of  $v_p\colon(p^s(f), p_i^b(f), p_p)$ remains unchanged.
+
+Another predicates is used when tessellating a face (section \ref{sec:tessellation}).
+Given two coplanar lines $l_a\colon(p_0, p_a)$ and $l_b\colon(p_0, p_b)$, we want decide whether the cross product of $\vec{l}_a$ and $\vec{l}_b$ has the same orientation as the normal $\vec{n}_0$ (the normal of $p_0$) (Fig.
+\ref{fig:substrates}).
+Direct solution requires to explicitly compute the vector of $l_a$ and $l_b$ and then decide the sign of $\vec{n}_0 \cdot (\vec{l}_a \times \vec{l}_b)$.
+However, explicit representation of $\vec{l}_a$ and $\vec{l}_b$ requires more bits than standard double precision float point number, bringing extra computation burden.
+
+To solve this, we decompose the normal vectors of $p_a$ and $p_b$: $\vec{n}_a = \vec{n}^\parallel_a + \vec{n}^\perp_a$ and $\vec{n}_b = \vec{n}^\parallel_b + \vec{n}^\perp_b$.
+Here superscript `$\parallel$` means the vector is in the plane $p_0$ and `$\perp$` means it is orthogonal to $p_0$.
+Then $\vec{n}_a \times \vec{n}_b = \vec{n}^\parallel_a \times \vec{n}^\parallel_b + \vec{n}^\perp_a \times \vec{n}^\parallel_b + \vec{n}^\parallel_a \times \vec{n}^\perp_b + \vec{n}^\perp_a \times \vec{n}^\perp_b$.
+As we know $\vec{n}^\perp_a$ and $\vec{n}^\perp_b$ is parallel, $\vec{n}^\perp_a \times \vec{n}^\perp_b = \textbf{0}$.
+Now, we evaluate the expression $\vec{n}_0 \cdot (\vec{n}_a \times \vec{n}_b)$.
+Since $\vec{n}_s$ is orthogonal to both $\vec{n}^\perp_a \times \vec{n}^\parallel_b $ and $\vec{n}^\parallel_a \times \vec{n}^\perp_b $, we deduce $\vec{n}_0 \cdot (\vec{n}_a \times \vec{n}_b) = \vec{n}_0 \cdot (\vec{n}^\parallel_a \times \vec{n}^\parallel_b)$.
+Here we make an essential observation that $\vec{n}^\parallel_a \times \vec{n}^\parallel_b$ has the same direction as $\vec{l}_a \times \vec{l}_b$, that is:
 \begin{equation}
-\label{eq:pointcomp}
-   \left|
-  \begin{array}{ccc}   %该矩阵一共3列，每一列都居中放置
-  a_u  & b_u & c_u \\
-  a_v  & b_v & c_v \\
-  a_p  & b_p & c_p
-  \end{array}
-  \right| > 0,
+\begin{split}
+\label{eq:cosine}
+sign(\vec{n}_0 \cdot (\vec{n}_a \times \vec{n}_b)) &= sign(\vec{n}_0 \cdot (\vec{n}^\parallel_a \times \vec{n}^\parallel_b)) \\
+&=  sign(\vec{n}_0 \cdot (\vec{l}_a \times \vec{l}_b)),
+\end{split}
 \end{equation}
-If not, we negate $P_p$ to be the test plane.
-
-Another predicates is used when tessellating a face (further explanation of its application is shown in Section \ref{}).
-Given two lines $L_a: (P_s, P_a)$ and $L_b: (P_s, P_b)$, which are on the same plane $P_s$, we want decide whether the sign of cross product of $\vec{L}_a$ and $\vec{L}_b$ has the same orientation as the normal $\vec{N}_s$.
-Direct solution requires to explicitly compute the vector of $L_a$ and $L_b$ and then decide the sign by $\vec{N}_s \cdot (\vec{L}_a \times \vec{L}_b)$.
-However, explicit representation of $\vec{L}_a$ and $\vec{L}_b$ requires more bits than standard double precision float point number, bringing extra computation burden.
-
-To solve this, we decompose the normal vectors of $P_a$ and $P_b$: $\vec{N}_a = \vec{N}^\parallel_a + \vec{N}^\perp_a$ and $\vec{N}_b = \vec{N}^\parallel_b + \vec{N}^\perp_b$.
-Here superscript `$\parallel$` means the vector is in the plane $P_s$ and `$\perp$` means it is orthogonal to $P_s$.
-Then $\vec{N}_a \times \vec{N}_b = \vec{N}^\parallel_a \times \vec{N}^\parallel_b + \vec{N}^\perp_a \times \vec{N}^\parallel_b + \vec{N}^\parallel_a \times \vec{N}^\perp_b + \vec{N}^\perp_a \times \vec{N}^\perp_b$.
-As we know $\vec{N}^\perp_a$ and $\vec{N}^\perp_b$ is parallel, $\vec{N}^\perp_a \times \vec{N}^\perp_b = \textbf{0}$.
-Now, we evaluate the expression: $\vec{N}_s \cdot (\vec{N}_a \times \vec{N}_b)$.
-Since $\vec{N}_s$ is orthogonal to both $\vec{N}^\perp_a \times \vec{N}^\parallel_b $ and $\vec{N}^\parallel_a \times \vec{N}^\perp_b $, we deduce $\vec{N}_s \cdot (\vec{N}_a \times \vec{N}_b) = \vec{N}_s \cdot (\vec{N}^\parallel_a \times \vec{N}^\parallel_b)$.
-Here we make an essential observation that $\vec{N}^\parallel_a \times \vec{N}^\parallel_b$ has the same direction as $\vec{L}_a \times \vec{L}_b$, that is:
-\begin{equation}
-\label{eq:cosine}
-sign(\vec{N}_s \cdot (\vec{N}_a \times \vec{N}_b)) = sign(\vec{N}_s \cdot (\vec{L}_a \times \vec{L}_b)),
-\end{equation}
-which means we do not need to explicitly compute $\vec{L}_a$ or $\vec{L}_b$. Instead, we only have to evaluate the left expression of equation \ref{eq:cosine}.
+which means we do not need to explicitly compute $\vec{l}_a$ or $\vec{l}_b$. Instead, we only have to evaluate the left expression of equation \ref{eq:cosine}, which is much easier to compute.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=2.5in]{substrates}
+\caption{The configuration of two-line-one-plane test. $l_a\colon(p_0, p_a)$ and $l_b\colon(p_0, p_b)$ are coplanar in $p_0$. We want to compute $sign(\vec{n}_0 \cdot (\vec{l}_a \times \vec{l}_b))$.}
+\label{fig:substrates}
+\end{figure}
 
@@
 \label{section:isect}
-In this step, intersections between faces are computed through the triangle-triangle intersection test within each critical cell.
+In this step, intersections between faces are computed through the triangle-triangle intersection test within each critical cell of octree.
 We adopt M\"{o}ller's intersection detection algorithm \cite{moller1997fast} on account of its efficiency and simplicity.
-However, because collision detection algorithms are often accompanied by non-robustness problems, a conventional implementation of this algorithm may cause unpredictable results.
-Therefore, we integrate plane-based geometry representation \cite{sugihara1990solid} into M\"{o}ller's algorithm to make it unconditionally precise and robust.
-In the following, we first make a quick review of M\"{o}ller's algorithm, then discuss the way to make it unconditional robust.
-At last, we talk about how to deal with degenerate cases.
+However, because collision detection algorithms are often accompanied by non-robustness problems, a naive implementation may cause unpredictable results when there comes degenerate cases.
+Therefore, we integrate plane-based geometry representation into M\"{o}ller's algorithm to make it unconditionally robust and exact.
+In the following, we first make a quick review of M\"{o}ller's algorithm, then discuss the way to integrate plane-based geometry.
+At last, we talk about how to deal with degenerate case, such as intersecting on points and coplanar case.
 
@@
 \includegraphics[width=2.5in]{projection}
-\caption{$Seg_1$ is the intersection between $S_2$ and $F_1$.
-$Seg_2$ is the intersection between $S_1$ and $F_2$.
-The intersection between $F_1$ and $F_2$, which is the line segment in red, is the overlap of $Seg_1$ and $Seg_2$.}
+\caption{$Seg_1$ is the intersection between $p^s(f_2)$ and $f_1$.
+$Seg_2$ is the intersection between $p^s(f_1)$ and $f_2$.
+The intersection between $f_1$ and $f_2$, which is the line segment in red, is the overlap of $Seg_1$ and $Seg_2$.}
 \label{fig_projection}
@@
 
-M\"{o}ller's algorithm computes the intersection between two triangles $F_1$ and $F_2$ in three steps (Fig. \ref{fig_projection}).
+M\"{o}ller's algorithm computes the intersection between two triangles $f_1$ and $f_2$ in three steps (Fig. \ref{fig_projection}).
 \begin{itemize}[leftmargin=0.45cm]
-\item[1)] An early rejection is performed by testing whether $F_1$ intersects the plane where $F_2$ lies, which is denoted as $S_2$.
-This is a necessary condition of intersection between $F_1$ and $F_2$.
-If this test is passed, then the same is performed for $F_2$ and $S_1$, where $S_1$ is the plane of $F_1$.
-\item[2)]The intersection between $F_1$ and $S_2$, denoted as $Seg_1$, and the intersection between $F_2$ and $S_1$, denoted as $Seg_2$, are separately computed .
- \item[3)]The intersection between $F_1$ and $F_2$ is determined by computing the overlap area of $Seg_1$ and $Seg_2$ .
+\item[1)] An early rejection is performed by testing whether $f_1$ intersects $p^s(f_2)$, the supporting plane of $f_2$.
+This is a necessary condition of intersection between $f_1$ and $f_2$.
+If this test is passed, then the same is performed for $f_2$ and $p^s(f_1)$.
+\item[2)]The intersection between $f_1$ and $p^s(f_2)$, denoted as $Seg_1$, and the intersection between $f_2$ and $p^s(f_1)$, denoted as $Seg_2$, are separately computed .
+ \item[3)]The intersection between $f_1$ and $f_2$ is determined by computing the overlap area of $Seg_1$ and $Seg_2$ .
 \end{itemize}
@@
 
-Conventional implementations of M\"{o}ller's algorithm use vertex-based representation and common float point arithmetic, which is neither exact nor robust.
+Conventional implementations of M\"{o}ller's algorithm use vertex-based geometry, which is neither exact nor robust unless arbitrary precision arithmetic is used.
 In Fig.

### 2016-06-14 summary.tex
6/14

@@
 
-Our non-intersected mesh, called linked halfedge, is a variance of halfedge, a well-known data structure to represent solids.
+Our non-intersected mesh, called Linked Halfedge, is a variance of halfedge, a well-known data structure to represent solids.
 Halfedge has two advantages: first, since halfedge is popular, using it as the intermediate data structure can avoid unnecessary conversion, which has the potential to create simpler algorithm and better performance and result topology; second, the geometry connectivity, by which we accelerate classification using local coherence of space indicators, can be easily retrieved through halfedge.
@@
 Therefore, we utilize plane-based representation to avoid computing new coordinates.
-In addition, we detect all coincident vertices among primitives and linked them together (that is why it is called linked halfedge).
+In addition, we detect all coincident vertices among primitives and linked them together (that is why it is called Linked Halfedge).
 This information is used for avoiding repetitive vertices, reconstructing geometry connectivity, and ensuring the topology correctness.
@@
 \cite{feito2013fast}, we found that the the topology near intersection lines between faces can benefit point-in-polyhedron test by dramatically reducing the number of faces needing traversing.
-Therefore, we add extra information into the linked halfedge, called \emph{intersection context}, to facilitate afterwards face classification.
+Therefore, we add extra information into the Linked Halfedge, called \emph{intersection context}, to facilitate afterwards face classification.
 Intersection context identifies where an intersection lies on the surface of the related primitives.
-An edge of linked halfedge has intersection context only if it is coincident with a certain intersection line segment between primitives.
+An edge of Linked Halfedge has intersection context only if it is coincident with a certain intersection line segment between primitives.
 We will give the definition and usage of intersection context in details in the following sections.
 
-To give a overall impression of how we design linked halfedge, we summarize the above content and highlight the following features:
+To give a overall impression of how we design Linked Halfedge, we summarize the above content and highlight the following features:
 
 \begin{itemize}
-  \item Each input primitive mesh is tessellated into a linked halfedge. Faces in a linked halfedge must not cross any other linked halfedges.
-  \item Coincident vertices between different linked halfedge should be linked, that is, coincident vertices are shared among linked halfedges.
-  \item If a certain edge of linked halfedge is coincident with intersection line segment(s), it should be associated with the corresponding intersection context(s).
+  \item Each input primitive mesh is tessellated into a Linked Halfedge. Faces in a Linked Halfedge must not cross any other Linked Halfedges.
+  \item Coincident vertices between different Linked Halfedge should be linked, that is, coincident vertices are shared among Linked Halfedges.
+  \item If a certain edge of Linked Halfedge is coincident with intersection line segment(s), it should be associated with the corresponding intersection context(s).
 \end{itemize}
@@
 
-Once all intersections are detected, we need to tessellate the input primitives and construct the linked halfedges..
+Once all intersections are detected, we need to tessellate the input primitives and construct the Linked Halfedges..
 In many methods like \cite{ogayar2015deferred}, constraint Delaunay triangulation (CDT) is applied to perform tessellation, since the intersections are naturally the constraints of CDT.
@@
 Finally, as our intersection vertices are represented exactly by planes, implementation of CDT could be complex and inefficient, as most CDT methods were not designed to handle planes.
-Therefore, we design a simple structure, called tessellation graph, to guide the tessellation of each single face, and develop a very fast but exact method to construct linked halfedges from tessellation graphs, which is suitable for dealing with plane-based representation of intersections.
+Therefore, we design a simple structure, called tessellation graph, to guide the tessellation of each single face, and develop a very fast but exact method to construct Linked Halfedges from tessellation graphs, which is suitable for dealing with plane-based representation of intersections.
 Details are shown in section \ref{sec:tessellation}.
@@
 
-This step is to choose faces from the linked halfedges to generate the final mesh.
+This step is to choose faces from the Linked Halfedges to generate the final mesh.
 Literally compute all the space indicators of each face is unacceptable slow for large CSG trees.
@@
 Another predicates is used when tessellating a face (section \ref{sec:tessellation}).
-Given two coplanar lines $l_a\colon(p_0, p_a)$ and $l_b\colon(p_0, p_b)$, we want decide whether the cross product of $\vec{l}_a$ and $\vec{l}_b$ has the same orientation as the normal $\vec{n}_0$ (the normal of $p_0$) (Fig.
+Given two coplanar lines $l_a\colon(p_0, p_a)$ and $l_b\colon(p_0, p_b)$, we want decide whether the cross product of $\vec{l}_a$ and $\vec{l}_b$ has the same orientation as $\vec{n}_0$ (the normal of $p_0$).
+We call it as \emph{two-line-one-plane comparison}(Fig.
 \ref{fig:substrates}).
@@
 \includegraphics[width=2.5in]{substrates}
-\caption{The configuration of two-line-one-plane test. $l_a\colon(p_0, p_a)$ and $l_b\colon(p_0, p_b)$ are coplanar in $p_0$. We want to compute $sign(\vec{n}_0 \cdot (\vec{l}_a \times \vec{l}_b))$.}
+\caption{The configuration of two-line-one-plane comparison.
+$l_a\colon(p_0, p_a)$ and $l_b\colon(p_0, p_b)$ are coplanar in $p_0$.
+We want to compute $sign(\vec{n}_0 \cdot (\vec{l}_a \times \vec{l}_b))$.}
 \label{fig:substrates}
@@
 
-Conventional implementations of M\"{o}ller's algorithm use vertex-based geometry, which is neither exact nor robust unless arbitrary precision arithmetic is used.
-In Fig.
-\ref{fig:precision}, we illustrate a non-robust 2D case of the Boolean operation.
+Conventional implementations of M\"{o}ller's algorithm use vertex-based geometry, which is neither exact nor robust.
 Although implementing M\"{o}ller's algorithm with arbitrary precision arithmetic could make it robust, it is too costly for a large CSG evaluation.
@@
 \ref{fig_projection}) are computed as intermediate results.
-On the other hand, if the computation can be restricted to \emph{predicates}, which make a two or three-way decision based on known coordinates, we could quickly and robustly implement this algorithm.
+We use plane-based geometry to solve these problems by avoiding explicitly computing the coordinates of new vertices.
 
@@
 \label{sec:embed}
-According to the method described in section \ref{sec:convert}, triangle faces $f$ are firstly converted to its plane-based representation: a supporting plane $P_{s,f}$ surrounded by three bounding planes $P^i_{b,f}, i = 1,2,3$.
-We introduce the plane-based implementation of M\"{o}ller's algorithm step by step in the following:
+According to the method described in section \ref{sec:convert}, triangle faces $f$ are firstly converted to its plane-based representation: a supporting plane $p^s(f)$ surrounded by three bounding planes $\{p^b_i\ |\  i = 1,2,3\}$.
+We integrate the plane-based geometry into each of the tree steps of M\"{o}ller's algorithm as following:
 
@@
 \begin{itemize}[leftmargin=0.45cm]
-\item[1)] In this step, we only need to compute the orientation of a plane $(a, b, c, d)$
-with respect to a point $(x, y, z)$, that is to compute:
-\begin{equation}
+\item[1)] The basic routine of the first step is given two faces $f_1$ and $f_2$, computing the orientation of the supporting plane (denoted as $p(f_1)\colon(a, b, c, d)$) of a face with respect to a certain vertex (denoted as  $v_i(f_2)\colon(x, y, z)$) of the other face.
+That is to compute:
+\begin{equation}\label{eq:plane}
 sign(ax+by+cz+d).
 \end{equation}
-Using the notation in section \ref{sec:convert},  we know the coordinates of the points are precisely represented by $L$ bits.
-Also, after the conversion, the precisions of four coefficients of the supporting plane are $(P', P', P', P)$, where $P'=P-(L-1)-2$ and $P$ is defined in equation \ref{eq:precision}.
-Using the strengthened criterion $M \ge P+1$, we find that $M$ bits are enough to perform the predicates.
-This observation allow us to perform very efficient early discard on the triangle-triangle intersection test, which is the key idea to stay efficiency while perusing exactness.
-\item[2)]In step 2, constructions are avoid by explicitly represent the end points of $Seg_1$ and $Seg_2$ using plane triples.
+Reviewing the discussion of section \ref{sec:convert},  the coordinates of vertices are represented by three L-bit float point numbers.Precisions of the four coefficients of the supporting plane are $(P^\star, P^\star, P^\star, P)$.
+Here $P$ is defined in equation \ref{eq:precision}, and $$P^\star=P-(L-1)-2.$$ Using the enforced criterion $M \ge P+1$, we find that $M$ bits are enough to perform the predicate of equation \ref{eq:plane}.
+This allow us to perform the early discard efficiently.
+\item[2)]In step 2, the end points of $Seg_1$ and $Seg_2$ are implicitly represented using intersections of plane triples.
+Take $Seg_1$ as an example.
 As illustrated in Fig.
-\ref{fig:isect}(a), these points are the intersection between an edge line of a face and the supporting plane of the other face.
-Because the edge line of $f_1$ ($f_2$) can be represented as $[P_{s, f_1}, P^i_{b, f_1}]$ ($[P_{s, f_2}, P^i_{b, f_2}]$), the end points of $Seg_1$ ($Seg_2$) can be represented in the form of $[P_{s, f_1}, P_{s, f_2}, P^i_{b, f_2}]$ ($[P_{s, f_1}, P_{s, f_2}, P^i_{b, f_1}]$).
+\ref{fig:isect}, $Seg_1$ are the intersection between $f_1$ and $p_s(f_2)$.
+Because the edge $e_i(f_1)$ can be represented as $(p^s( f_1), p^b_i(f_1))$, the end points of $Seg_1$ can be represented in the form of $(p^s( f_1), p^s(f_2), p^b_i(f_1))$.
 In Fig.
-\ref{fig:isect}, we list all intersection situations between a triangle and a plane, and the corresponding bounding plane in each situation.
-Note, coplanar situation will be discussed later in section \ref{sec:degenerate}.
+\ref{fig:isect}, we list all intersection situations between $f_1$ and $p_s(f_2)$, and the corresponding bounding plane $p^b_i(f_1)$ in each situation.
+Coplanar conditions will be discussed later in section \ref{sec:degenerate}.
  \item[3)] The intersection between $f_1$ and $f_2$ is the overlap area of $Seg_1$ and $Seg_2$.
-It can be easily computed by comparing the end points of $Seg_1$ and $Seg_2$ along $L$ (Fig.
-\ref{fig_projection}), where $L$ is the intersection between $P_{s, f_1}$ and $P_{s, f_2}$.
-Because end points are all represented using plane triples, we can use the technique discussed in section \ref{sec:substrates} to implement the comparison.
+It can be easily computed by comparing the end points of $Seg_1$ and $Seg_2$ along $l$ (Fig.
+\ref{fig_projection}), where $l$ is the intersection between $p_s(f_1)$ and $p_s(f_2)$.
+Because end points are all represented using plane triples, we can use the two-line-one-plane comparison discussed in section \ref{sec:substrates} to perform the comparison.
 \end{itemize}
@@
 
-The output of this stage, or what we call triangle-triangle intersection record (TTIR), is the data structure which organize the results of triangle-triangle intersection test.
-TTIR is also the input of tessellation, and is in deep couple with the tessellation method.
-It is hard to give full idea of how we design TTIR before we introduce our tessellation algorithm.
-We first give several requirements from tessellation stage, and then discuss the compositions of TTIR.
-To have a comprehensive understanding of TTIR, readers may need to review this section after finish reading section \ref{sec:tessellation}.
-
-We recall our description of LHEC in section \ref{sec:meshes}, we need to transfer necessary information by TTIR to tessellation stage for LHEC construction. Necessary information includes:
-\begin{itemize}
-  \item The plane-based representation of intersection vertices.
-  \item Intersection line segments, each consisting of references of two end points.
-  \item Intersection context of the intersection line segments.
-\end{itemize}
-
-For example, assume two triangle faces $f_1$ and $f_2$, from primitive $A$ and $B$, intersect at line segment $(v_1, v_2)$, where $v_1$ and $v_2$ are references of two end points.
-First, $v_1$ and $v_2$ are introduced to $A$ and $B$, then intersection line segment $(v_1, v_2)$ is stored on both $f_1$ and $f_2$.
-At last, intersection context of $(v_1, v_2)$ is attached as an attribute.
-In this case, the intersection context of $(v_1, v_2)$  is $f_1$ for $A$ and $f_2$ for $B$.
-
-In LHEC, there must not be any repetitive vertices within each LHEC or among LHECs in order to reconstruct the correct topology.
+The output of this stage, or what we call intersection record (IR), is the data structure which organize the results of triangle-triangle intersection test.
+IR is also the input of tessellation, and is in deep couple with the tessellation method.
+It is hard to give full idea of why the IR is like that before we introduce our tessellation algorithm.
+Therefore, in this section, we first give several requirements for IR from tessellation stage, and then discuss the IR structure.
+To have a comprehensive understanding of IR, readers may need to review this section after finish reading section \ref{sec:tessellation} about tessellation stage.
+
+We recall our definition of Linked Halfedge in section \ref{sec:meshes}, we need to transfer necessary information by IR to tessellation stage for Linked Halfedge construction.
+For each intersection line segment, we use a five-component vector  $\gamma \colon(v_b, v_e, f, p, C)$ to describe it.
+Here, $v_b$ and $v_e$ are the two end points of $\gamma$.
+Component $f$ is the face where the $\gamma$ lies.
+Component $C$ is the intersection context, and will be further explained later.
+Component $p$ is the plane representation of the line where $\gamma$ lies (denoted as $\vec{n}_\gamma$).
+Normally, line is represented by two planes.
+However, one of the planes for $\vec{n}_\gamma$ must be $f$'s supporting plane $p^s(f)$, so we just omit it, and use the other plane as the representation for $\vec{n}_\gamma$ .
+
+To illustrate, assume two triangle faces $f_1$ and $f_2$, from primitive $P_1$ and $P_2$, intersect at line segment $\gamma$.
+Note that there are two versions of $\gamma$ for each of the two faces respectively, denoted as $\gamma(f_1)$ and $\gamma(f_2)$.
+For $\gamma(f_1)$, $v_b$ and $v_e$ are the two end points of $\gamma$ and $f=f_1$.
+The representation plane $p$ is $p^s(f_2)$.
+Note that $p^s(f_2)$ must not be coplanar with $f_1$.
+The intersection context $C=f_2$ in most cases.
+It means that, in primitive $P_2$, $\gamma(f_1)$ lies on the face $f_2$.
+However, sometimes, intersection may lie on the edge, instead of face,  of other primitive.
+In that case,  the intersection context is an edge, and we discuss such degenerate case in the next section.
+The situation of $\gamma(f_2)$ is similar we omit the discussion here.
+
+In the Linked Halfedge, there must not be any repetitive vertices in order to reconstruct the correct topology.
 Therefore, repetitive vertices elimination must be performed.
 Checking whether there are coincident points in a global scope can be quite inefficient.
-Fortunately, it is easy to figure out the location of an intersection vertex---whether it is inside, on a certain edge, or coincident with one of the three corners of intersection faces.
-Therefore, if we store the references of vertices on faces, edges, coincidence detection is localized and repetitive vertices elimination can be very fast.
-
-// 区分context and plane representation
+Our implementation use a localized scheme that store the reference of intersection vertices into their corresponding geometry location, like edges and faces.
+Therefore, coincidence detection performed within the geometry elements and repetitive vertices elimination can be very fast.
 
@@
 
-Before we discuss the degenerate cases, we give three principles for handling them.
+To solve degenerate cases, we have three principles.
 First, we want our method be unconditional robust and exact, so all degenerate cases should be well handled (completeness).
-Second, to control the complexity of tessellation, we want degenerate cases to be invisible to tessellation, that is, degenerate cases have the same format of output as non-degenerate cases (invisibility).
+Second, to control the complexity of tessellation, we want degenerate cases to be invisible to tessellation, that is, degenerate cases have the same format of output, in our method, IR, as non-degenerate cases (invisibility).
 Third, we want the outcome of tessellation be as simple as possible.
-That is, intersection line segments that will not help tessellation, if recognized, are disposed (simplicity).
-
-To ensure the completeness, we classify all degenerate cases into three categories by the dimension of intersection:
+That is, intersection line segments that will not help tessellation, if recognized, are disposed (concision).
+
+To ensure the completeness, we classify all degenerate cases into three categories by the dimension of intersection, and solving each of them as follows.
 
 \subsubsection{Intersects on point}
-Point is degenerate case of line segment with zero length.
-The intersection point is potentially a vertex in the LHEC.
-There are two kinds of vertices, depending on whether the vertex is isolated.
-An isolated vertex does not need to participate tessellation.
-On the other side, if the intersection point is not isolated, it is end point of other intersection line segment and will be introduced when that intersection line segment is detected.
-Therefore, we treat the cases of intersection on point as non-intersection cases.
-
-\subsubsection{Intersects on line segment}
-This category is often not degenerate cases.
-However, when intersection line segment lies on a edge of one of the two triangle faces (Fig.
-\ref{fig:isect}b), error will occur if not careful.
-In this case, there will be another pair of triangle faces that will have exactly the same intersection line segment (Fig.
-\ref{fig:isect2}).
-This is what we called twin intersections.
-With twin intersections exist, one intersection line segment will be inserted twice, requiring extra effort to eliminate repetitions.
-To make things worse, the intersection will have different intersection contexts.
-
-Twin intersection can be treated as union to resolve this.
-
-\subsubsection{Coplanar}
+When two triangles intersect on a single point, there are two different conditions (Fig.
+\ref{fig:isolated}), depending on whether the point is isolated.
+If the point is isolated, it means that there is no other intersection line segment sharing the point.
+This condition may cause non-manifold surface because of the singularity of the isolated intersection point.
+Also, isolated intersection point will not affect the tessellation of the intersection face.
+On the other hand, if the intersection point is not isolated, there must be other intersection line segments that contain the point, thus the point will be introduced at least twice.
+Therefore, no matter which condition it is, when two triangle faces intersect on point, we can just omit this intersection and this will not affect the correctness of the final topology.
 
@@
 \centering
-\includegraphics[width=3.5in]{degenerate}
-\caption{}
-\label{fig:isect2}
+\includegraphics[width=3.5in]{isolated}
+\caption{Two situations of point intersections.
+(a) The intersection point is isolated, and there is no adjacent intersection line segment.
+This situation may cause non-manifold surface in Boolean operation.
+(b) The intersection point is not isolated.
+The intersection point can be introduced by other face pairs during intersection tests.}
+\label{fig:isolated}
 \end{figure}
+
+\subsubsection{Intersects on face edges}
+When intersection line segment lies on an edge (Fig.
+\ref{fig:isect}b), there will be another pair of triangle faces that will have exactly the same intersection line segment (Fig.
+\ref{fig:twin}).
+We call this condition as \emph{twin intersections}.
+When there are twin intersections, the intersection line segment will be inserted twice, requiring extra effort to eliminate repetitions.
+Also, twin intersections lies on the edge, so they will have different type of intersection contexts.
+Finally, in some configurations, twin intersections will cause non-manifold surface as isolated intersection point does, which have to be detected and eliminated.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=3.5in]{twin}
+\caption{Four situations of twin intersections.
+(a) Triangles are located in two sides, cross condition.
+(b) Triangles are located in the same sides, invalid condition.
+(c) One of the triangles are coplanar, coplanar condition.
+(d) Double twin intersections, cross condition.
+(e) Double twin intersections, coplanar condition.
+(f) Double twin intersections, coplanar condition.}
+\label{fig:twin}
+\end{figure}
+
+The basic situations of twin intersections are shown in Fig. \ref{fig:twin} (a)(b)(c).
+
+\subsubsection{Coplanar}
 
@@
 \label{sec:classification}
-As the final stage, face classification classify all candidate faces in linked halfedges, and decides which faces belong to the final mesh.
+As the final stage, face classification classify all candidate faces in Linked Halfedges, and decides which faces belong to the final mesh.
 Classification is done by evaluating the indicator vector of each face.
@@
 In our method, it means there will be intersection context on the shared edge of the two faces (section ??).
-Because the indicator change can be figured out  by the intersection context efficiently (section ??), we can classify all the faces of linked halfedges using flood-filling method.
+Because the indicator change can be figured out  by the intersection context efficiently (section ??), we can classify all the faces of Linked Halfedges using flood-filling method.
 
@@
 
-Another thing needs to be noticed is that the neighborhood of a certain face $f$ from primitive $A$ in linked halfedges does not only contain the face in $A$, but also include faces from other primitives which share edges with $f$.
-It can be efficiently found because in linked halfedges, coincident vertices between primitives are shared.
+Another thing needs to be noticed is that the neighborhood of a certain face $f$ from primitive $A$ in Linked Halfedges does not only contain the face in $A$, but also include faces from other primitives which share edges with $f$.
+It can be efficiently found because in Linked Halfedges, coincident vertices between primitives are shared.
 Therefore, the indicator vector can be transfer not only intra-primitive, but also inter-primitive.

### 2016-06-16 summary.tex
before change
Signed-off-by: button <jhcz@sjtu.edu.cn>

@@
 
-To solve degenerate cases, we have three principles.
-First, we want our method be unconditional robust and exact, so all degenerate cases should be well handled (completeness).
-Second, to control the complexity of tessellation, we want degenerate cases to be invisible to tessellation, that is, degenerate cases have the same format of output, in our method, IR, as non-degenerate cases (invisibility).
-Third, we want the outcome of tessellation be as simple as possible.
-That is, intersection line segments that will not help tessellation, if recognized, are disposed (concision).
-
-To ensure the completeness, we classify all degenerate cases into three categories by the dimension of intersection, and solving each of them as follows.
+Assume there are two faces $f_1$ and $f_2$ from primitive $P_1$ and $P_2$ respectively.
+These two faces intersect on line segment $\gamma$, which has two versions of IR $\gamma(f_1)$ and $\gamma(f_2)$ for the two faces respectively.
+Without loss of generality, we only discuss the configuration of $\gamma(f_1)$, as $\gamma(f_2)$ can be figured out similarly.
+We classify all degenerate cases into three categories by the dimension of intersection.
+Each of them is discussed separately in the following.
+
+Before we go into details, there are three principles that we follow to solve degenerate cases:
+\begin{itemize}
+\item We want our method be unconditional robust and exact, so all degenerate cases should be well handled (completeness).
+  \item To control the complexity of tessellation, we want degenerate cases to be invisible to tessellation, that is, degenerate cases have the same format of output, in our method, IR, as non-degenerate cases (invisibility).
+  \item we want the outcome of tessellation be as simple as possible. That is, intersection line segments that will not help tessellation, if recognized, are disposed (concision).
+\end{itemize}
+The criterion of whether an intersection help tessellation is by its necessity: if the intersection is not presented, whether some faces from the linked halfedge will cross the boundary of primitives.
+The word 'cross' do not only include the situation that a face is partly outside and partly inside of a primitive, but also can mean that a face is partly inside (outside) and part on the boundary of the primitive.
 
 \subsubsection{Intersects on point}
+\label{sec:ipoint}
 When two triangles intersect on a single point, there are two different conditions (Fig.
@@
 When intersection line segment lies on an edge (Fig.
-\ref{fig:isect}b), there will be another pair of triangle faces that will have exactly the same intersection line segment (Fig.
 \ref{fig:twin}).
-We call this condition as \emph{twin intersections}.
-When there are twin intersections, the intersection line segment will be inserted twice, requiring extra effort to eliminate repetitions.
-Also, twin intersections lies on the edge, so they will have different type of intersection contexts.
-Finally, in some configurations, twin intersections will cause non-manifold surface as isolated intersection point does, which have to be detected and eliminated.
+we call it as \emph{edge intersections}.
+When there are edge intersections, the intersection line segment will be inserted several times, requiring extra effort to eliminate repetitions.
+Also, as edge intersections lies on the edge, their intersection contexts are edges, not faces.
+Finally, in some configurations, edge intersections will cause non-manifold surface as isolated intersection point does, which have to be detected and carefully handled.
+
+There are generally two kinds of edge intersections.
+If $\gamma(f_1)$ lies on the edge of $f_1$ or $f_2$, but on the inside the face of the other one, then we called it as edge-face intersections (Fig.
+\ref{fig:twin}(a), (b), (c)).
+If $l$ lies on the edges of both $f_1$ and $f_2$, we call it as edge-edge intersections (Fig.
+\ref{fig:twin}(e), (f), (g)).
+To eliminate repetitive intersection records, when there is edge-face intersection, we treat it as the intersection of three faces $f_1$, $f_2$ and $f_1^\star$ (or $f_2^\star$).
+When there is edge-edge intersection, we treat it as the intersection of four faces $f_1$, $f_2$, $f_1^\star$ and $f_2^\star$.
+The $f_1^\star$ (or $f_2^\star$), known as \emph{companion face},  is the neighboring face which shares the intersection edge with $f_1$ (or $f_2$).
 
@@
 \includegraphics[width=3.5in]{twin}
-\caption{Four situations of twin intersections.
+\caption{Six situations of edge intersections.
+The first three subgraphs are edge-face intersections.
+The last three ones are edge-edge intersections.
 (a) Triangles are located in two sides, cross condition.
@@
 
-The basic situations of twin intersections are shown in Fig. \ref{fig:twin} (a)(b)(c).
-
-\subsubsection{Coplanar}
-
-Coplanar cases can also be seen as a special type of twin intersections. One is valid case, another is not.
+Both edge-face and edge-edge intersection can be further classified into three subclasses by the location of companion faces---cross condition, coplanar condition and invalid condition.
+We first consider edge-face intersection.
+Without generality, assume $f_1$ and $f_2$ intersect on the edge of $f_1$ and there is a companion face $f_1^\star$.
+If $f_1$ and $f_1^\star$ are on the same side of $f_2$, it is cross condition.
+If they are on the same side, it is invalid condition.
+If $f_1^\star$ is coplanar with $f_2$, it is coplanar condition.
+Consider the cross and coplanar condition.
+For $f_2$, the IR is the same as the common situation, except that the intersection context is an edge.
+For $f_1$ and $f_1^\star$, they have to share the intersection line segment, while the intersection context is $f_2$.
+However, when there is invalid condition, we should not record the intersection for the similar reasons of isolated point intersection (section \ref{sec:ipoint}).
+
+The handling of edge-edge intersection is similar with edge-face intersection.
+The difference is that the intersection contexts are edges for both $f_1$ and $f_2$.
+We still can classify edge-edge intersection into three subclasses by the relative location of companion faces.
+There is one difference, though, that in edge-face intersection, we compute on which side of $f_2$ the companion face $f_1^\star$ lies, and compare with $f_1$.
+However, in edge-edge intersection, we have to consider the space split by both $f_2$ and $f_2^\star$ instead of only $f_2$.
+Similar with edge-face intersections, we record the intersection of cross and coplanar condition, while omit the invalid condition for concision and also topology correctness.
+
+\subsubsection{Coplanar cases}
+
+When two triangle faces are coplanar, they may intersect with each other depending on whether they overlap in some area.
+Many methods \cite{feito2013fast} claim that it is important to compute the overlap in a 2D intersection way and to tessellate the face according to the intersection result afterwards.
+We will show that this is not necessary in our method.
+We simply omit coplanar cases in our intersection test and it will not affect the correctness of our tessellation stage.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=3.5in]{coplanar}
+\caption{a) Coplanar cases and the b) the possible configurations of the companion faces. In any configurations, their is no need to record the intersection of coplanar cases.}
+\label{fig:coplanar}
+\end{figure}
+
+Consider two triangle faces $f_1$ and $f_2$ intersect within the supporting plane (Fig.
+\ref{fig:coplanar}).
+Both $f_1$ and $f_2$ will be divided into two areas---the overlap area and the exclusive part.
+The boundary of these two parts are the boundary from the other face.
+Following the concision principle, whether we have to split face according to these boundaries depends on the necessity.
+That is, we have to
 

### 2016-07-13 summary.tex
last modified

@@
 we call it as \emph{edge intersections}.
-When there are edge intersections, the intersection line segment will be inserted several times, requiring extra effort to eliminate repetitions.
-Also, as edge intersections lies on the edge, their intersection contexts are edges, not faces.
-Finally, in some configurations, edge intersections will cause non-manifold surface as isolated intersection point does, which have to be detected and carefully handled.
-
 There are generally two kinds of edge intersections.
-If $\gamma(f_1)$ lies on the edge of $f_1$ or $f_2$, but on the inside the face of the other one, then we called it as edge-face intersections (Fig.
-\ref{fig:twin}(a), (b), (c)).
-If $l$ lies on the edges of both $f_1$ and $f_2$, we call it as edge-edge intersections (Fig.
-\ref{fig:twin}(e), (f), (g)).
-To eliminate repetitive intersection records, when there is edge-face intersection, we treat it as the intersection of three faces $f_1$, $f_2$ and $f_1^\star$ (or $f_2^\star$).
+If $\gamma$ lies on the edge of $f_1$ or $f_2$, but inside of the face of the other one, then we called it as edge-face intersections.
+If $\gamma$ lies on the edges of both $f_1$ and $f_2$, we call it as edge-edge intersections.
+When there is edge-face intersection, we treat it as the intersection of three faces $f_1$, $f_2$ and $f_1^\star$ (or $f_2^\star$).
 When there is edge-edge intersection, we treat it as the intersection of four faces $f_1$, $f_2$, $f_1^\star$ and $f_2^\star$.
 The $f_1^\star$ (or $f_2^\star$), known as \emph{companion face},  is the neighboring face which shares the intersection edge with $f_1$ (or $f_2$).
+In this way, we avoid repetitive insertion of the same edge intersections, since the companion faces share the same intersection with its neighborhood $f_1$ or $f_2$.
 
@@
 We first consider edge-face intersection.
-Without generality, assume $f_1$ and $f_2$ intersect on the edge of $f_1$ and there is a companion face $f_1^\star$.
 If $f_1$ and $f_1^\star$ are on the same side of $f_2$, it is cross condition.

### 2016-07-14 summary.tex
tess-graph

@@
 \usepackage{slashbox}
+\usepackage{color}
 %\usepackage{ulem}
@@
 The concept of plane-based representation of polygonal meshes was first described by Sugihara and Iri \cite{sugihara1990solid}. Plane-based representation provides one important advantage
-when it comes to tasks that involve changing the topology of solids represented by meshes like the evaluation of Boolean expressions: no new primary geometry information has to be constructed to obtain the resulting polyhedron – it is composed of a subset of the planes of the input polyhedra.
+when it comes to tasks that involve changing the topology of solids represented by meshes like the evaluation of Boolean expressions: no new primary geometry information has to be constructed to obtain the resulting polyhedron ¨C it is composed of a subset of the planes of the input polyhedra.
 Hence, opposed to the case of using vertex coordinates, that inevitably necessitates the construction of new geometry information, only geometric decision predicates are required to compose the output polyhedron from the face planes of the input.
@@
 Finally, as our intersection vertices are represented exactly by planes, implementation of CDT could be complex and inefficient, as most CDT methods were not designed to handle planes.
-Therefore, we design a simple structure, called tessellation graph, to guide the tessellation of each single face, and develop a very fast but exact method to construct Linked Halfedges from tessellation graphs, which is suitable for dealing with plane-based representation of intersections.
+Therefore, we design a simple structure, called Tess-graph, to guide the tessellation of each single face, and develop a very fast but exact method to construct Linked Halfedges from Tess-graphs, which is suitable for dealing with plane-based representation of intersections.
 Details are shown in section \ref{sec:tessellation}.
@@
 
-\section{Plane-based geometry}
+\section{Plane-based Geometry}
 
@@
 
-\subsection{Vertex-based method review}
+\subsection{Vertex-Based Method Review}
 
@@
 
-\subsection{Plane-based technique embedding}
+\subsection{Plane-based Technique Embedding}
 
@@
 
-\subsection{Intersection record}
+\subsection{Intersection Representation}
 \label{sec:ir}
+
+// change the title to Indentifying intersections
 
@@
 We recall our definition of Linked Halfedge in section \ref{sec:meshes}, we need to transfer necessary information by IR to tessellation stage for Linked Halfedge construction.
-For each intersection line segment, we use a five-component vector  $\gamma \colon(v_b, v_e, f, p, C)$ to describe it.
+For each intersection line segment, we use a five-component vector {\color{red}{$\gamma \colon(T, v_0, v_1, p, C)$}} to describe it.
 Here, $v_b$ and $v_e$ are the two end points of $\gamma$.
@@
 
-\subsection{Degenerate cases}
+\subsection{Degenerate Cases}
 \label{sec:degenerate}
@@
 \subsubsection{Intersects on face edges}
+
+// intersect on face edges does not create new line segments, it is part of the edges from other meshes, and will to be duplicated.
+
+// whose edge? need to be further explained and better defined. an edge intersection divide edge in a triangle and will be duplicated in the other
+
 When intersection line segment lies on an edge (Fig.
@@
 
-When two triangle faces are coplanar, they may intersect with each other depending on whether they overlap in some area.
-Many methods \cite{feito2013fast} claim that it is important to compute the overlap in a 2D intersection way and to tessellate the face according to the intersection result afterwards.
-We will show that this is not necessary in our method.
-We simply omit coplanar cases in our intersection test and it will not affect the correctness of our tessellation stage.
-
 \begin{figure}[t]
@@
 
-Consider two triangle faces $f_1$ and $f_2$ intersect within the supporting plane (Fig.
+Consider two triangle faces $T_1$ and $T_2$ intersect within a common plane.
+Both $T_1$ and $T_2$ will divide each other into two areas---the overlapped area and the exclusive part (Fig.
 \ref{fig:coplanar}).
-Both $f_1$ and $f_2$ will be divided into two areas---the overlap area and the exclusive part.
-The boundary of these two parts are the boundary from the other face.
-Following the concision principle, whether we have to split face according to these boundaries depends on the necessity.
-That is, we have to
+Obviously, if we tessellate both $T_1$ and $T_2$ according to the boundary of overlapped area, we can guarantee that the tessellated meshes will not cross the boundary of any other meshes.
+In fact, many methods \cite{feito2013fast} claim that it is important to tessellate faces according to the 2D-intersection result.
+We will show that this is not necessary in our method.
+We do not care whether $T_1$ and $T_2$ really intersect in 2D.
+We simply omit all coplanar cases, treating them as they do not intersect.
+This simplify our intersection test, making it more robust and fast (coplanar cases can be usual in a CSG of artificial object), while doing no harm to the correctness of our method.
+
+The key observation is that coplanar cases do not create new edges, just like edge intersection in the last section.
+The difference is that in a non-coplanar case, there is only one edge intersection.
+In a coplanar, there are at most three intersections.
+Therefore, we can decompose it into three edge intersections and record each edge intersection independently.
+However, there is a better way that we do not process them at all.
+This is because there is companion face, like $T_1^*$, in edge intersection.
+If $T_1^*$ is not coplanar with $T_2$, then we can solve the intersection between $T_1^*$ and $T_2$ in a 3D way, which is the case in Fig \ref{fig:twin}(c).
+On the other hand, if $T_1^*$ is coplanar with $T_2$, we instantly know that both sides of shared edge $e(T_1, T_1^*)$ have the same indicator $\lambda_1$, which imply that this intersection is not necessary for tessellation and we can omit it by the principle of concision.
+In sum-up, we do not need to handle with coplanar intersection cases.
 
@@
 
+{\color{red}{red alert start}}
+
 \label{sec:tessellation}
-This is the step to process TTIR and output LHIC, where the tessellation happens.
-We called this process as deferred tessellation because we do not tessellate until we collect all intersection line segments.
+This is the step to tessellate input meshes with intersections, outputting linked halfedge.
+We called this stage as deferred tessellation because it happens until we collect all necessary intersections.
 For this problem, Ogayar-Anguita et.
 al.
-\cite{ogayar2015deferred} try to use Constrained Delaunay Triangulation (CDT) to solve, as the recorded intersection is naturally the constraints.
+\cite{ogayar2015deferred} try to use Constrained Delaunay Triangulation (CDT) to solve, as the intersections is naturally the constraints and triangle faces is naturally a convex zone.
 It works fine for Boolean operation of two primitives.
-However, when there are more than two primitives, simply using CDT covers the complexity of tessellation.
-In such case, the intersection line segments may cross, overlap and even coincident with each other, introducing new vertex, splitting original intersection line segments.
-Naive implementation of CDT may lead to holes, repetitive edges, and other topology errors.
-
-To solve these problems, we first refine the TTIR into an intermediate data structure---\emph{tessellation graph}.
-In this process, we resolve any intersection between intersection.
-After this, we tessellation each face according its corresponding tessellation graph.
-To make this process unconditional robust and exact, we utilize plane-based techniques and do not compute explicitly the coordinates of intersection points throughout this step.
-
-\subsection{Tessellation graph}
-
-TTIRs are only loose data that store the coordinates of intersection line segments.
-To perform tessellation and extract sub-faces, we need to organize TTIRs in a face scope.
-We use a graph-based data structure---tessellation graph---for this purpose.
-For each intersection face which needs tessellation, we construct tessellation graph.
-A tessellation graph is the graph-like description of the tessellated face topology.
-Nodes of tessellation graph represent vertices, and edges represent edges in LHIC.
-To avoid ambiguity, we call original three edges of the face as \emph{face boundaries} in the following.
-An important feature of tessellation graph is that it uses uniform representation for intersection vertices and line segments, and face boundaries and the original three corners.
-This dramatically reduces complexity of extracting sub-faces and allowing the following process simple and fast.
-
-\subsubsection{Definition and construction}
-
-Nodes of tessellation graph represent vertices and store the coordinates of them.
-Edges are nondirectional ones, and store the intersection context if exist.
-We classify graph edges into two types: we call edges on face boundaries as \emph{boundary edges} and edges inside face as \emph{inner edges}.
-They are different in at least two aspects: first, the boundary edges may not have a intersection context since it is not coincident with any TTIR; second, in the view of halfedge, inner edges represent two halfedges but boundary edges represent only one halfedge.
-The same classification is for intersection line segments: if the intersection are inside the face, it is an inner intersection, otherwise a boundary intersection.
-//可以提前到degenreate case
-
-Recall our definition of TTIR in section \ref{sec:ir}, we find most of the work has already been done.
+However, when there are more than two primitives, simply applying CDT covers the complexity of tessellation.
+The major problem here is that the intersections may be \emph{irregular}.
+The definition of regular intersection is that it does not cross or overlap with other intersections.
+In CSG cases with more than two meshes, irregular intersections can introduce new vertex, split original intersection line segments.
+Naive algorithm of CDT [there should be algorithm for instance] may lead to holes, repetitive edges, and other topology errors when there are irregular intersections {\color{red}{(Fig.
+?, use CGAL or fade2d for testing)}}.
+
+To solve these problems, we first refine the intersections and eliminate any irregular intersections.
+When all intersections are regular, we can directly use CDT to tessellate.
+{\color{red}{However?xxxx(after I research CDT)}}.
+Therefore, we develop a new tessellation algorithm that guarantee topology correctness and unconditional robust.
+We organize intersections into single face scope, generating an intermediate data structure---\emph{Tess-graph}, After that, we tessellate each face by subtract sub-faces from its corresponding Tess-graph.
+Throughout this stage, we utilize plane-based techniques and do not compute explicitly the coordinates of intersection points.
+
+\subsection{Eliminating Irregular Intersection}
+
+Regular intersections are guaranteed when there are only two meshes, because the surfaces of primitives are all without self-intersection.
+However, when there are more than two primitives, this constraint can be violated.
+In the view of intersection detection, it is not enough to find all intersection vertices by only triangle-triangle intersection test.
+This is because in such case, the new vertex can be introduced not only by intersection between edge and plane, but also by intersections of three planes, which involves more than two faces.
+
+Intersection refinement is performed in a local scope.
+For each face, we detect irregular intersections by intersection test between pairs of intersections.
+Because primitive meshes are not self-intersected, we only check intersections between intersections made by different meshes.
+Face intersecting only one other mesh do not need refinement, since they do not have such intersection pairs.
+
+Using plane-based representation, whether two intersections intersects each other is determined by predicate of orientation of plane against a point.
+For example, we want determine whether $\lambda_1$ and $\lambda_2$ intersects.
+Using the notation of section \ref{sec:ir}, we perform the test by checking whether $v_0(\lambda_1), v_1(\lambda_1)$ are on two sides of $p(\lambda_2)$ and whether $v_0(\lambda_2), v_1(\lambda_2)$ are on two sides of $p(\lambda_1)$.
+If yes, $\lambda_1$ and $\lambda_2$ intersects and introduces new intersection vertex $v_{new}$, which is the intersection of $p(\lambda_1), p(\lambda_2)$ and the supporting plane of $T(\lambda_1)$.
+The new vertex $v_{new}$ should be added into both $\lambda_1$ and $\lambda_2$ as a segment point.
+Since there may be more than one segment point added into a certain intersection during the whole test, we do not divide the intersection until all intersection pairs are tested.
+
+Degenerate cases are when the two intersections intersect on one of the end points or are collinear.
+In the first condition {\color{red}{Fig.
+??(a)}}, there is no new vertex generated and only one of the intersection needs splitting.
+The collinear case {\color{red}{Fig.
+??(b)}} is intersection in 1D and are tested exactly by two-point-on-line comparison between the end points of intersections.
+If there is intersection between them, it should be straightforward to figure out the segment points for each intersections.
+
+After all segment points are found, the related intersections have to be split.
+For a certain intersection, we sort the segment points by two-point-on-line comparisons and subtract child intersections along the direction of their father one by one.
+The representation of the child intersections should be the same with their father except the coordinate components $v_0$ and $v_1$.
+So far, we guarantee that all refined intersections need not be further divided as the potential edges of the Linked Halfedge.
+However, if there are collinear cases, there will be coincident child intersections from different fathers.
+We choose to resolve them in Tess-graph.
+If CDT is chosen instead of Tess-graph, coincidence can be handled like-wise.
+
+\subsection{Tess-Graph}
+
+So far, intersections are only loose data that store the coordinates and neighbouring information.
+To perform tessellation and extract sub-faces, we need to organize them to reveal the topology.
+We use Tess-graph for this purpose.
+A Tess-graph is the graph description of the tessellated face topology.
+For each face to be tessellated, we construct a Tess-graph according to the refined intersections.
+The final Linked Halfedge merges both the original topology and the intersections in the same representation.
+And the construction of Tess-graph is the first step towards such uniformity.
+By only nodes and connections, it represents both the intersections and the original boundary of triangle face.
+This reduces complexity of the following processes and allowing them to be simple and fast.
+
+Nodes of Tess-graph represent vertices and store the coordinates of them.
+Connections are nondirectional, represent edges in Linked Halfedge, storing the I-rep if it is coincident with an intersection.
+Sometimes, there will be more than one coincident intersections and all I-reps have to be stored.
+
+We classify connections into two types: we call connections on face boundaries as \emph{boundary connections} and connections inside face as \emph{inner connections}.
+They are different in two aspects: first, the boundary connections may not have an intersection representation since it is not coincident with any intersection; second, in the view of halfedge, inner connections represent two halfedges but boundary connections represent only one halfedge.
+{\color{red}{The same classification is for intersection line segments: if the intersection are inside the face, it is an inner intersection, otherwise a boundary intersection.
+// can be forward to the previous place}}
+
+Construction of Tess-graph from I-rep is straightforward except one thing: we have to merge face boundary with the intersections lies on the boundary.
+
+Using the notation of I-rep, we find most of the work has already been done.
 To construct inner edges, we only need to first collect all vertices on the face (including both inside vertices and boundary vertices) to be the nodes, and then connect nodes by inner intersections.
@@
 
-\subsubsection{Intersection refinement}
-
-Since tessellation graph is a graph-like description of halfedge, it has extra constraints on its form.
-The most important one is that edges should not intersect each other.
-This can be guaranteed when there are only two primitives,  because the surface of primitives is all watertight, non-manifold, and without self-intersection.
-However, when there are more than two primitives, this constraint can be violated.
-In the view of intersection detection, it is not enough to find all intersection vertices by only triangle-triangle intersection test.
-This is because the new vertex can be formed not only by edge intersects plane, but also by three planes, which involves more than two triangles.
-Therefore, an extra processing--intersection refinement---is necessary to resolve these intersections before constructing tessellation graph.
-
-Intersection refinement is performed between every two intersection line segments from different primitives.
-Using plane-based representation, whether two intersection line segments intersect is determined by predicate of orientation of plane against a point.
-For example, we want determine whether $I_v$: $(v_b, v_e, P_v, f_0, C_v)$ and $I_u$: $(u_b, u_e, P_u, f_0, C_u)$ intersects.
-% 需要在IR那一章补充plane rep of intersection这一部分。intersection is describe with 四元组。
-It is done by checking whether $u_b, u_e$ is on different sides of $P_v$ and whether $v_b, v_e$ is on different sides of $P_u$.
-If yes, $I_v$ and $I_u$ intersects and introduced new intersection vertex, which is the intersection of $P_u, P_v$ and the supporting plane $f_0$.
-
-Degenerate cases will occur when $I_u$ and $I_v$ intersect on end point(s) or $I_v$ and $I_v$ are collinear.
-
-\subsection{Extracting sub-faces}
+\subsection{Extracting Sub-faces}
 The last step of tessellation is to really change the topology of input primitive to construct LHICs.
@@
 
-There is yet another problem on this method. Our method of extracting sub-faces assume that the tessellation graph is connected. However, this assumption can be false (Fig.).
+There is yet another problem on this method. Our method of extracting sub-faces assume that the Tess-graph is connected. However, this assumption can be false (Fig.).
 
@@
 
-\subsection{Basic idea}
+\subsection{Basic Idea}
 
@@
 
-\subsection{Fast and exact face classification}
+\subsection{Fast and Exact Face Classification}
 
@@
 
-\subsection{Caching evaluation results}
+\subsection{Caching Evaluation Results}
 

### 2016-07-20 summary.tex
lallaala, ming tian bu shagn ban

@@
 %
-\usepackage{algorithmic}
+%\usepackage{algorithmic}
 % algorithmic.sty was written by Peter Williams and Rogerio Brito.
@@
 \usepackage{enumitem}
+%\usepackage[]{algorithm2e}
+\usepackage[]{algpseudocode}
 \usepackage{algorithm}
@@
 \newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}
-\floatname{algorithm}{Procedure}
+
+\floatname{algorithm}{Algorithm}
 
@@
 In CSG cases with more than two meshes, irregular intersections can introduce new vertex, split original intersection line segments.
-Naive algorithm of CDT [there should be algorithm for instance] may lead to holes, repetitive edges, and other topology errors when there are irregular intersections {\color{red}{(Fig.
-?, use CGAL or fade2d for testing)}}.
+However, most CDT algorithms \cite{chew1989constrained}, or even just constrained triangulation [Computational geometry: an introduction] require that constraints do not cross each other, and will cause topology deficiency if not satisfied.
 
@@
 When all intersections are regular, we can directly use CDT to tessellate.
-{\color{red}{However?xxxx(after I research CDT)}}.
-Therefore, we develop a new tessellation algorithm that guarantee topology correctness and unconditional robust.
-We organize intersections into single face scope, generating an intermediate data structure---\emph{Tess-graph}, After that, we tessellate each face by subtract sub-faces from its corresponding Tess-graph.
-Throughout this stage, we utilize plane-based techniques and do not compute explicitly the coordinates of intersection points.
+However, 2D constrained triangulation algorithm \cite{chew1989constrained} [Computational geometry: an introduction] require cross detection between arbitrary connections of vertices, coordinates projection, which is hard to exactly performed using plane-reps geometry.
+Therefore, we develop a new tessellation algorithm using only plane-based geometry, ensuring topology correctness and unconditional robust.
+We first organize intersections into single face scope, generating an intermediate data structure---\emph{Tess-graph}.
+Then we tessellate each face by subtract sub-faces from its corresponding Tess-graph.
+In compensate, we do not guarantee the faces of the final mesh are triangles, leaving the flexibility to post-processing.
 
@@
 Sometimes, there will be more than one coincident intersections and all I-reps have to be stored.
-
-We classify connections into two types: we call connections on face boundaries as \emph{boundary connections} and connections inside face as \emph{inner connections}.
-They are different in two aspects: first, the boundary connections may not have an intersection representation since it is not coincident with any intersection; second, in the view of halfedge, inner connections represent two halfedges but boundary connections represent only one halfedge.
-{\color{red}{The same classification is for intersection line segments: if the intersection are inside the face, it is an inner intersection, otherwise a boundary intersection.
-// can be forward to the previous place}}
-
-Construction of Tess-graph from I-rep is straightforward except one thing: we have to merge face boundary with the intersections lies on the boundary.
-
-Using the notation of I-rep, we find most of the work has already been done.
-To construct inner edges, we only need to first collect all vertices on the face (including both inside vertices and boundary vertices) to be the nodes, and then connect nodes by inner intersections.
-However, boundary edge construction is not that easy.
-We cannot simply connect the three face corners to be the boundary edges, since there may be boundary intersections, and face edges have to be splitted.
-
-To construct boundary edges of graph, we first need to first sort vertices on each face edge along the edge line.
-This is done by two-point comparison in section \ref{sec:substrates}.
-After the sort, we connect the nodes by their sequence on the edge line to form the boundary edges.
-If any boundary edge is coincident with boundary intersection, we assign the intersection context of the boundary intersection to the boundary edge.
+Construction of Tess-graph from I-rep is straightforward except one thing: we have to merge face boundary with the intersections lies on the face boundary {\color{red}{Fig}}.
+This lead to an extra step beforehand.
+For each edge boundary of face, we treat it as pseudo-intersections with only coordinates information, and perform collinear intersection test with all intersections lies on it, splitting it by corresponding segment points.
 
 \subsection{Extracting Sub-faces}
-The last step of tessellation is to really change the topology of input primitive to construct LHICs.
-We could apply CDT here since the intersection is refined and there is no intersection between the constraints.
-However, we choose to design a new method to extract sub-faces from intersection face for the efficiency:
-\begin{itemize}
-  \item lose topology information
-  \item may not need to triangulate, classify in a whole
-  \item hard to implement with planes
-\end{itemize}
-
-There is yet another problem on this method. Our method of extracting sub-faces assume that the Tess-graph is connected. However, this assumption can be false (Fig.).
+
+The difference between a graph and a mesh surface is that there is no concept of face in graph. In this step, we extract faces from Tess-graph to construct Linked Halfedge.
+
+First, We classify connections of Tess-graph into two types: connections on face boundaries as \emph{boundary connections} and connections inside face as \emph{inner connections}.
+In the view of halfedge data structure, inner connections represent two opposite halfedges but boundary connections represent only one.
+We add an attribute for each connection to identify their directions, and thus we get a directed version of Tess-graph.
+A sub-face is a halfedge loop on the directed Tess-graph.
+Extracting faces are process of searching for valid loops which meet certain geometry constraints.
+After all faces are extracted, all halfedges of directed Tess-graph should be used exactly once.
+
+There two geometry constraints for valid loops.
+First, the direction of loops should be coherent with the face normal, counter-clockwise for example.
+Second, consecutive halfedges on the loop should be angle adjacent, which means there is no other halfedges between the angle contained by these two halfedges {\color{red}{Fig.?}}.
+To meet these constraints, we sort the halfedges counter-clockwise for each nodes with more than two halfedges starting from them.
+This is implemented by using the divide-and-conquer framework of quick sort.
+During each recursion, we pick a random halfedge and split the rest into two sets according to the sign of two-line-on-plane comparison.
+To make the results of two-line-on-plane comparisons coherent, we assume that for each halfedge $h_i$, the normal directions of its plane-rep, denoted as $\vec{n}(h_i)$, meets the following criterion:
+\begin{equation}
+(\vec{n}(h_i) \times \vec{n}_0) \cdot \vec{l}(h_i) > 0,
+\end{equation}
+where $\vec{n}_0$ is the normal of the face, and $\vec{l}(h_i)$ is the direction of $h_i$.
+The plane-rep of halfedge can be inherited from the corresponding connections from the undirected Tess-graph.
+Since we {\color{red}{guarantee that each connection has a plane-rep //need insert//}}, sorting can be exactly and fast performed.
+After connections are sorted in each nodes, we can know which connections are adjacent and what is the right direction during the loop search.
 
@@
 \label{sec:classification}
-As the final stage, face classification classify all candidate faces in Linked Halfedges, and decides which faces belong to the final mesh.
-Classification is done by evaluating the indicator vector of each face.
+This stage traverses all candidate faces in the Linked Halfedge, and classifies which of them belong to the final mesh.
+Classification is done by evaluating the indicator vector of each face {\color{red}{(indicator vector?)}}.
 During this process, we take advantage of plane-based representation to ensure unconditional correct classification.
-Also, as we maintain the geometry intra-primitive connectivity (by halfedge structure) and inter-primitive (by denoting shared vertex), we can utilize the space coherence of indicator vectors to accelerate this process.
-
-In this section, we will first give a overall framework of face classification, then introduce how to classify each individual face.
-At last, we discuss how to accelerate this process by caching intermediate classification result.
-
-\subsection{Basic Idea}
-
-The space coherence of indicator vectors means neighboring faces often have the same indicator vector, or share most components of indicator vectors.
-This means if we figure out the indicator vector of a face, we may know the indicator vectors of its neighboring faces instantly.
-In other cases, modification must be applied to the indicator vector.
-The necessary and sufficient condition of indicator change is that the two faces lie on different side of the primitive boundary.
-In our method, it means there will be intersection context on the shared edge of the two faces (section ??).
-Because the indicator change can be figured out  by the intersection context efficiently (section ??), we can classify all the faces of Linked Halfedges using flood-filling method.
-
-The indicator vector of the first face is special.
-We can guarantee that the whole vector can be figured out only by intersection context of the face edges.
-Thus, point-in-polyhedron test is used for compensation.
-This works well under the assumption that the indicator of the sample point is the same with the face.
-For the point inside the face, the answer is absolutely yes, because the whole face must be classified as a whole.
-However, the coordinates of the inner points cannot be exactly represented, thus may lead to wrong predicates.
-Therefore, we choose to the use the face corners for point-in-polyhedron test.
-The test must be guaranteed to be exact, and, on the other hand, efficiency is not so important as we won't need many such tests.
-If ray-trace algorithm is used for the point-in-polyhedron test, the octree built during space division might be useful [].
-
-However, use face corner instead of inner points has another problem.
-The indicator vector of the corner may not be the same as the of the indicator vector of the whole face.
-Figure ?
-shows such condition occurs when any of the face edge is on the boundary of other primitive.
-Nevertheless, we do not to worry about this.
-This is because when such case occurs, one of the edge adjacent to that corner will have intersection context to of that primitive, by which we can figure out the real indicator.
-
-Another thing needs to be noticed is that the neighborhood of a certain face $f$ from primitive $A$ in Linked Halfedges does not only contain the face in $A$, but also include faces from other primitives which share edges with $f$.
-It can be efficiently found because in Linked Halfedges, coincident vertices between primitives are shared.
-Therefore, the indicator vector can be transfer not only intra-primitive, but also inter-primitive.
+In addition, since we maintain the intra-primitive geometry connectivity and inter-primitive geometry connectivity in Linked Halfedge, we can utilize the space coherence of face indicator vectors to accelerate this process.
+
+In this section, we will first give an overall framework of face classification, and then introduce how to classify each individual face.
+At last, we discuss how to accelerate this process by caching intermediate results.
+
+\subsection{Framework}
+
+The space coherence of indicator vectors means neighboring faces could share the same indicator vector, or most components of indicator vectors.
+For example, given two neighboring faces $t_1$ and $t_2$, indicator vectors $\Lambda(t_1)$ and $\Lambda(t_2)$ would often be the same.
+Only when there is boundary of some meshes, say $P_k$, on the shared edge $e(t_1, t_2)$ and split $t_1$ and $t_2$ in two sides, the corresponding components $\lambda(t_1, P_k)$ and $\lambda(t_2, P_k)$ can be different.
+And other components of $\Lambda(t_1)$ and $\Lambda(t_2)$ will remain the same.
+If we can compute the indicator changes between neighboring faces efficiently, we can start from a single face with a indicator vector as the seed, propagating to all faces with geometry connectivity, reusing indicator vectors according to the spatial coherence and classifying faces very fast.
+
+Fortunately, in the Linked Halfedge, it is straightforward to know whether $\lambda(t_1, P_k)$ and $\lambda(t_2, P_k)$ are different, because it means $e(t_1, t_2)$ will be on the boundary of $P_k$, and there will be corresponding I-reps stored on $e(t_1, t_2)$.
+In addition, both $\lambda(t_1, P_k)$ and $\lambda(t_2, P_k)$ can be computed efficiently according to the I-reps (details in Section \ref{sec:individual}).
+We outline our classification method in Algorithm 1.
+
+\begin{algorithm}
+\caption{Fast Face Classification}
+\label{code:floodfill}
+\textbf{Input: } Linked Halfedge structure $\Omega$
+
+\textbf{Output: } Classification of each face $f(\Lambda(t_i)), t_i \in \Omega$
+
+\begin{algorithmic}[1]
+\State Select a proper seed face $t_s$
+\State Compute the first indicator vector $\Lambda(t_s)$
+\State \Call{propagate} { $t_s$ , $\Lambda(t_s)$}
+\State
+\Function{propagate}{ $t_c$ , $\Lambda(t_c)$}
+    \State Compute $f(\Lambda(t_c))$
+    \For {each neighboring face $t_i^c$}
+        \If {there are I-reps $\{\gamma_k\}$ on $e(t_i^c, t_c)$}
+            \State Compute $\Lambda(t_i^c)$ using $\Lambda(t_c)$ and $\{\gamma_k\}$
+            \State \Call{propagate} { $t_i^c$ , $\Lambda(t_i^c)$}
+        \Else
+            \State \Call{propagate} { $t_i^c$ , $\Lambda(t_c)$}
+        \EndIf
+    \EndFor
+\EndFunction
+\end{algorithmic}
+\end{algorithm}
+
+\subsection{Seed Indicator Vector}
+
+Our classification method starts from computing the seed indicator vector using point-in-polyhedron test \cite{ogayar2005point}.
+Conventionally, the barycenter of the face is used for the test to compute the indicator vector of the whole face.
+This is because the whole face is classified as a whole, and every inner point will have the same indicator vector.
+However, the coordinates of the inner points cannot be exactly represented by float point numbers, which may lead to wrong predicates, especially when it is an on-boundary case.
+Therefore, we use the original vertices, whose exact coordinates are known, for point-in-polyhedron test.
+For this reason, only tessellated faces with at least one original vertex can be the seed face.
+The point-in-polyhedron test is guaranteed to be exact.
+On the other hand, efficiency is not so important as there will not be many such tests.
+If ray-trace algorithms (e.g., \cite{frisken2002simple}) are used, the octree constructed during space division can be used for acceleration \cite{havran1999summary}.
+
+However, using point on the boundary instead of an inner one has another problem.
+Given a face $s$ (may not be triangle) and one of its vertex $v_b^i(s)$, the vertex indicator $\lambda(v_{i}(s), P_k)$ may cause ambiguity to deduce the face indicator $\lambda(s, P_k)$.
+In {\color{red}{Fig.
+?}}, $\lambda(v_b^1(s), P_k) = on$, then $\lambda(s, P_k)$ can be any of the four conditions.
+We solve this problem by trying other vertices in $s$ for the ambiguous components.
+If all vertices indicators are $on$ and the ambiguity still cannot be resolved, the current face is not proper for being the seed and select a new one instead.
 
 \subsection{Fast and Exact Face Classification}
+
+\label{sec:individual}
+
+Feito et.
+al.
+\cite{feito2013fast} had noticed that intersection neighborhood can be used for fast classification of faces around that intersection.
+According to their method, faces adjacent to intersection have neighbors from other primitive(s) that define the position and orientation for each other, by which the indicators are determined.
+However, Feito et.
+al.
+did not give detail description of how to implement an exact and robust classification.
+Their implementation of using vertex coordinates may have problems for the degenerate cases.
+Because geometry connectivity is used, local incorrect classification can be spread to the neighborhoods, leading to errors in wide ranges.
+
+{\color{red}{fdafdafdsfafdfadsfa}}
 
@@
 In these conditions, we can select a triangle subset of $f_i$ to represent $f_i$, since $f_i$ is guaranteed to be classified as a whole.
-
-Feito et.
-al.
-had noticed that intersection neighborhood can be used for fast classification of faces around the intersection.
-According to their method, faces adjacent to intersection line segments must have neighbors from other primitive(s) that define the position and orientation for each other.
-Unfortunately, Feito et.
-al.
-did not give detail description of how to implement a exact classification, nor discuss about degenerate cases such as coplanar faces.
-As Feito et.
-al.
-use geometry connectivity for classification, any incorrect classification can be spread to neighborhoods, which may cause errors in a wide range.
 
@@
 
-\section{Experiments}
+\section{Implementation}
+
+\vspace{0.5em}
+\textbf{Generate Seed Indicator Vector.} Our method of generating the first indicator vector will fail on extreme conditions when each face in Linked halfedge is coincident with more than one primitive face (e.g., the union of the same mesh).
+In order to be robust, we use the face barycenter with high-precision coordinates for the point-in-polyhedron test to generate the seed indicator vector after several failures of choosing a proper seed face.
+
+\vspace{0.5em}
+\noindent \textbf{Generate Seed Indicator Vector.} Our method of generating the first indicator vector will fail on extreme conditions when each face in Linked halfedge is coincident with more than one primitive face (e.g., the union of the same mesh).
+In order to be robust, we use the face barycenter with high-precision coordinates for the point-in-polyhedron test to generate the seed indicator vector after several failures of choosing a proper seed face.
 

### 2016-07-31 summary.tex
before delete

@@
 
-Face classification is to evaluate whether a given face $x$ belongs to the final geometry according to the n-primitive Boolean function $\Phi$ :
+Face classification is to evaluate whether a given face $x$ belongs to the final geometry according to the n-primitive Boolean function $f$ :
 \begin{equation}
-\lambda_\Phi(x) = \Phi(\lambda_1(x), \lambda_2(x), \cdots, \lambda_n(x)).
+\lambda_f(x) = f(\boldsymbol{\Lambda}(x)) = f(\lambda_1(x), \lambda_2(x), \cdots, \lambda_n(x)).
 \end{equation}
 The parameter $\lambda_i(x)$ is space indicator with respect to primitive $P_i$.
-This means to classify a face, one has to know the space indicators with respect to all the primitives (or the whole indicator vector $\vec{\lambda}(x)$ for short).
+This means to classify a face, one has to know the space indicators with respect to all the primitives (or the whole indicator vector $\boldsymbol{\Lambda}(x)$ for short).
 A space indicator has four conditions: completely inside (\emph{in}), completely outside (\emph{out}), on the boundary with consistent normals (\emph{same}) or opposite normals (\emph{oppo}).
@@
 We recall our definition of Linked Halfedge in section \ref{sec:meshes}, we need to transfer necessary information by IR to tessellation stage for Linked Halfedge construction.
-For each intersection line segment, we use a five-component vector {\color{red}{$\gamma \colon(T, v_0, v_1, p, C)$}} to describe it.
-Here, $v_b$ and $v_e$ are the two end points of $\gamma$.
-Component $f$ is the face where the $\gamma$ lies.
+For each intersection line segment, we use a five-component vector {\color{red}{$\Gamma \colon(t, v_0, v_1, p, C_{P_h \backslash P_i})$}} to describe it.
+Here, $v_b$ and $v_e$ are the two end points of $\Gamma$.
+Component $f$ is the face where the $\Gamma$ lies.
 Component $C$ is the intersection context, and will be further explained later.
-Component $p$ is the plane representation of the line where $\gamma$ lies (denoted as $\vec{n}_\gamma$).
+Component $p$ is the plane representation of the line where $\Gamma$ lies (denoted as $\vec{n}_\Gamma$).
 Normally, line is represented by two planes.
-However, one of the planes for $\vec{n}_\gamma$ must be $f$'s supporting plane $p^s(f)$, so we just omit it, and use the other plane as the representation for $\vec{n}_\gamma$ .
-
-To illustrate, assume two triangle faces $f_1$ and $f_2$, from primitive $P_1$ and $P_2$, intersect at line segment $\gamma$.
-Note that there are two versions of $\gamma$ for each of the two faces respectively, denoted as $\gamma(f_1)$ and $\gamma(f_2)$.
-For $\gamma(f_1)$, $v_b$ and $v_e$ are the two end points of $\gamma$ and $f=f_1$.
+However, one of the planes for $\vec{n}_\Gamma$ must be $f$'s supporting plane $p^s(f)$, so we just omit it, and use the other plane as the representation for $\vec{n}_{\boldsymbol{\Gamma}}$ .
+
+To illustrate, assume two triangle faces $f_1$ and $f_2$, from primitive $P_1$ and $P_2$, intersect at line segment ${\boldsymbol{\Gamma}}$.
+Note that there are two versions of ${\boldsymbol{\Gamma}}$ for each of the two faces respectively, denoted as ${\boldsymbol{\Gamma}}(f_1)$ and ${\boldsymbol{\Gamma}}(f_2)$.
+For ${\boldsymbol{\Gamma}}(f_1)$, $v_b$ and $v_e$ are the two end points of ${\boldsymbol{\Gamma}}$ and $f=f_1$.
 The representation plane $p$ is $p^s(f_2)$.
@@
 The intersection context $C=f_2$ in most cases.
-It means that, in primitive $P_2$, $\gamma(f_1)$ lies on the face $f_2$.
+It means that, in primitive $P_2$, ${\boldsymbol{\Gamma}}(f_1)$ lies on the face $f_2$.
 However, sometimes, intersection may lie on the edge, instead of face,  of other primitive.
 In that case,  the intersection context is an edge, and we discuss such degenerate case in the next section.
-The situation of $\gamma(f_2)$ is similar we omit the discussion here.
+The situation of ${\boldsymbol{\Gamma}}(f_2)$ is similar we omit the discussion here.
 
@@
 Assume there are two faces $f_1$ and $f_2$ from primitive $P_1$ and $P_2$ respectively.
-These two faces intersect on line segment $\gamma$, which has two versions of IR $\gamma(f_1)$ and $\gamma(f_2)$ for the two faces respectively.
-Without loss of generality, we only discuss the configuration of $\gamma(f_1)$, as $\gamma(f_2)$ can be figured out similarly.
+These two faces intersect on line segment ${\boldsymbol{\Gamma}}$, which has two versions of IR ${\boldsymbol{\Gamma}}(f_1)$ and ${\boldsymbol{\Gamma}}(f_2)$ for the two faces respectively.
+Without loss of generality, we only discuss the configuration of ${\boldsymbol{\Gamma}}(f_1)$, as ${\boldsymbol{\Gamma}}(f_2)$ can be figured out similarly.
 We classify all degenerate cases into three categories by the dimension of intersection.
@@
 There are generally two kinds of edge intersections.
-If $\gamma$ lies on the edge of $f_1$ or $f_2$, but inside of the face of the other one, then we called it as edge-face intersections.
-If $\gamma$ lies on the edges of both $f_1$ and $f_2$, we call it as edge-edge intersections.
+If ${\boldsymbol{\Gamma}}$ lies on the edge of $f_1$ or $f_2$, but inside of the face of the other one, then we called it as edge-face intersections.
+If ${\boldsymbol{\Gamma}}$ lies on the edges of both $f_1$ and $f_2$, we call it as edge-edge intersections.
 When there is edge-face intersection, we treat it as the intersection of three faces $f_1$, $f_2$ and $f_1^\star$ (or $f_2^\star$).
@@
 If $T_1^*$ is not coplanar with $T_2$, then we can solve the intersection between $T_1^*$ and $T_2$ in a 3D way, which is the case in Fig \ref{fig:twin}(c).
-On the other hand, if $T_1^*$ is coplanar with $T_2$, we instantly know that both sides of shared edge $e(T_1, T_1^*)$ have the same indicator $\lambda_1$, which imply that this intersection is not necessary for tessellation and we can omit it by the principle of concision.
+On the other hand, if $T_1^*$ is coplanar with $T_2$, we instantly know that both sides of shared edge $e(T_1, T_1^*)$ have the same indicator $\boldsymbol{\Lambda}_1$, which imply that this intersection is not necessary for tessellation and we can omit it by the principle of concision.
 In sum-up, we do not need to handle with coplanar intersection cases.
@@
 Using plane-based representation, whether two intersections intersects each other is determined by predicate of orientation of plane against a point.
-For example, we want determine whether $\lambda_1$ and $\lambda_2$ intersects.
-Using the notation of section \ref{sec:ir}, we perform the test by checking whether $v_0(\lambda_1), v_1(\lambda_1)$ are on two sides of $p(\lambda_2)$ and whether $v_0(\lambda_2), v_1(\lambda_2)$ are on two sides of $p(\lambda_1)$.
-If yes, $\lambda_1$ and $\lambda_2$ intersects and introduces new intersection vertex $v_{new}$, which is the intersection of $p(\lambda_1), p(\lambda_2)$ and the supporting plane of $T(\lambda_1)$.
-The new vertex $v_{new}$ should be added into both $\lambda_1$ and $\lambda_2$ as a segment point.
+For example, we want determine whether ${\boldsymbol{\Gamma}}_1$ and ${\boldsymbol{\Gamma}}_2$ intersects.
+Using the notation of section \ref{sec:ir}, we perform the test by checking whether $v_0({\boldsymbol{\Gamma}}_1), v_1({\boldsymbol{\Gamma}}_1)$ are on two sides of $p({\boldsymbol{\Gamma}}_2)$ and whether $v_0({\boldsymbol{\Gamma}}_2), v_1({\boldsymbol{\Gamma}}_2)$ are on two sides of $p({\boldsymbol{\Gamma}}_1)$.
+If yes, ${\boldsymbol{\Gamma}}_1$ and ${\boldsymbol{\Gamma}}_2$ intersects and introduces new intersection vertex $v_{new}$, which is the intersection of $p({\boldsymbol{\Gamma}}_1), p({\boldsymbol{\Gamma}}_2)$ and the supporting plane of $t({\boldsymbol{\Gamma}}_1)$.
+The new vertex $v_{new}$ should be added into both ${\boldsymbol{\Gamma}}_1$ and ${\boldsymbol{\Gamma}}_2$ as a segment point.
 Since there may be more than one segment point added into a certain intersection during the whole test, we do not divide the intersection until all intersection pairs are tested.
@@
 The space coherence of indicator vectors means neighboring faces could share the same indicator vector, or most components of indicator vectors.
-For example, given two neighboring faces $t_1$ and $t_2$, indicator vectors $\Lambda(t_1)$ and $\Lambda(t_2)$ would often be the same.
-Only when there is boundary of some meshes, say $P_k$, on the shared edge $e(t_1, t_2)$ and split $t_1$ and $t_2$ in two sides, the corresponding components $\lambda(t_1, P_k)$ and $\lambda(t_2, P_k)$ can be different.
-And other components of $\Lambda(t_1)$ and $\Lambda(t_2)$ will remain the same.
+For example, given two neighboring faces $t_1$ and $t_2$, indicator vectors $\boldsymbol{\Lambda}(t_1)$ and $\boldsymbol{\Lambda}(t_2)$ would often be the same.
+Only when there is boundary of some meshes, say $P_k$, on the shared edge $e(t_1, t_2)$ and split $t_1$ and $t_2$ in two sides, the corresponding components $\boldsymbol{\Lambda}(t_1, P_k)$ and $\boldsymbol{\Lambda}(t_2, P_k)$ can be different.
+And other components of $\boldsymbol{\Lambda}(t_1)$ and $\boldsymbol{\Lambda}(t_2)$ will remain the same.
 If we can compute the indicator changes between neighboring faces efficiently, we can start from a single face with a indicator vector as the seed, propagating to all faces with geometry connectivity, reusing indicator vectors according to the spatial coherence and classifying faces very fast.
 
-Fortunately, in the Linked Halfedge, it is straightforward to know whether $\lambda(t_1, P_k)$ and $\lambda(t_2, P_k)$ are different, because it means $e(t_1, t_2)$ will be on the boundary of $P_k$, and there will be corresponding I-reps stored on $e(t_1, t_2)$.
-In addition, both $\lambda(t_1, P_k)$ and $\lambda(t_2, P_k)$ can be computed efficiently according to the I-reps (details in Section \ref{sec:individual}).
+Fortunately, in the Linked Halfedge, it is straightforward to know whether $\boldsymbol{\Lambda}(t_1, P_k)$ and $\boldsymbol{\Lambda}(t_2, P_k)$ are different, because it means $e(t_1, t_2)$ will be on the boundary of $P_k$, and there will be corresponding I-reps stored on $e(t_1, t_2)$.
+In addition, both $\boldsymbol{\Lambda}(t_1, P_k)$ and $\boldsymbol{\Lambda}(t_2, P_k)$ can be computed efficiently according to the I-reps (details in Section \ref{sec:individual}).
 We outline our classification method in Algorithm 1.
@@
 
-\textbf{Output: } Classification of each face $f(\Lambda(t_i)), t_i \in \Omega$
+\textbf{Output: } Classification of each face $f(\boldsymbol{\Lambda}(t_i)), t_i \in \Omega$
 
@@
 \State Select a proper seed face $t_s$
-\State Compute the first indicator vector $\Lambda(t_s)$
-\State \Call{propagate} { $t_s$ , $\Lambda(t_s)$}
+\State Compute the first indicator vector $\boldsymbol{\Lambda}(t_s)$
+\State \Call{propagate} { $t_s$ , $\boldsymbol{\Lambda}(t_s)$}
 \State
-\Function{propagate}{ $t_c$ , $\Lambda(t_c)$}
-    \State Compute $f(\Lambda(t_c))$
+\Function{propagate}{ $t_c$ , $\boldsymbol{\Lambda}(t_c)$}
+    \State Compute $f(\boldsymbol{\Lambda}(t_c))$
     \For {each neighboring face $t_i^c$}
-        \If {there are I-reps $\{\gamma_k\}$ on $e(t_i^c, t_c)$}
-            \State Compute $\Lambda(t_i^c)$ using $\Lambda(t_c)$ and $\{\gamma_k\}$
-            \State \Call{propagate} { $t_i^c$ , $\Lambda(t_i^c)$}
+        \If {there are I-reps $\{{\boldsymbol{\Gamma}}_k\}$ on $e(t_i^c, t_c)$}
+            \State Compute $\boldsymbol{\Lambda}(t_i^c)$ using $\boldsymbol{\Lambda}(t_c)$ and $\{{\boldsymbol{\Gamma}}_k\}$
+            \State \Call{propagate} { $t_i^c$ , $\boldsymbol{\Lambda}(t_i^c)$}
         \Else
-            \State \Call{propagate} { $t_i^c$ , $\Lambda(t_c)$}
+            \State \Call{propagate} { $t_i^c$ , $\boldsymbol{\Lambda}(t_c)$}
         \EndIf
@@
 
-\subsection{Seed Indicator Vector}
+\subsection{Precise Seed Generation}
 
@@
 However, using point on the boundary instead of an inner one has another problem.
-Given a face $s$ (may not be triangle) and one of its vertex $v_b^i(s)$, the vertex indicator $\lambda(v_{i}(s), P_k)$ may cause ambiguity to deduce the face indicator $\lambda(s, P_k)$.
+Given a face $s$ (may not be triangle) and one of its vertex $v_b^i(s)$, the vertex indicator $\boldsymbol{\Lambda}(v_{i}(s), P_k)$ may cause ambiguity to deduce the face indicator $\boldsymbol{\Lambda}(s, P_k)$.
 In {\color{red}{Fig.
-?}}, $\lambda(v_b^1(s), P_k) = on$, then $\lambda(s, P_k)$ can be any of the four conditions.
-We solve this problem by trying other vertices in $s$ for the ambiguous components.
-If all vertices indicators are $on$ and the ambiguity still cannot be resolved, the current face is not proper for being the seed and select a new one instead.
+?}}, $\boldsymbol{\Lambda}(v_b^1(s), P_k) = on$, then $\boldsymbol{\Lambda}(s, P_k)$ can be any of the four conditions.
+We solve this problem by trying other vertices in $s$ for ambiguous indicators.
+If all vertices indicators are $on$ and the ambiguity cannot be resolved, the current face is not proper for being the seed and we select a new one instead.
 
@@
 did not give detail description of how to implement an exact and robust classification.
-Their implementation of using vertex coordinates may have problems for the degenerate cases.
-Because geometry connectivity is used, local incorrect classification can be spread to the neighborhoods, leading to errors in wide ranges.
-
-{\color{red}{fdafdafdsfafdfadsfa}}
+Their implementation of using vertex coordinates might misclassify faces by numeric errors and fail in degenerate cases.
+Because geometry connectivity is used, local misclassification can be spread to the neighborhoods, leading to errors in wide ranges.
+
+We develop an classification method that is unconditionally robust and exact based on the idea of using intersection neighborhood information.
+The neighborhood information is stored in the context component of I-reps during previous stages .
+In the following, we discuss the conditions that the face to be classified is a triangle.
+If the face is not a triangle, we select a triangle slice of the face instead, as the whole face is guaranteed to be classified together.
+Note that the chosen slice should contain the edge where the I-reps lie, by which we compute the new indicators.
+
+Given a face $t_i$ to be classified and an I-rep $\boldsymbol\Gamma$ of intersection on one of $t_i$'s edge, we denote the three corners it as $v_0^{\Gamma}, v_1^{\Gamma}, v_2,$ where the superscript $\boldsymbol\Gamma$ means the vertices are on the edge where $\boldsymbol\Gamma$ lies.
+We also denote the context component of $\boldsymbol\Gamma$ as $C_{P_h \backslash P_j}$, meaning $t_i$ is from primitive $P_j$ and intersects primitive $P_h$.
+From previous discussion (section \ref{sec:ir}){\color{red}{may be more than one}}, we know there are two types of intersection context---face neighborhood and edge neighborhood.
+In both conditions, the one or two faces involving in the context split the space into two in and out space by its (their) orientation(s).
+We will see that under such division (denoted as $\boldsymbol{D}(C_{P_h \backslash P_j})$), we can compute $\lambda(t_i, P_j)$ exactly.
+
+Since the faces involving in $C_{P_h \backslash P_j}$ is part of primitive $P_j$, the space division $\boldsymbol{D}(C_{P_h \backslash P_j})$ is homogeneous with the space division by $P_j$ in neighborhood of $\boldsymbol{\Gamma}$.
+The basic idea is to choose one point $v_x$ on $t_i$ close enough to $\boldsymbol{\Gamma}$ to compute $\lambda(v_x, P_j)$, and then compute $\lambda(t_i, P_j)$ accordingly.
+However, the problem is that we cannot find such a $v_x$ that can be represented exactly, which means robust classification cannot be performed.
+Fortunately, we observe that we can choose $v_2$, which is not so close to $\boldsymbol{\Gamma}$ instead.
+To illustrate, assume there is another point $v_{x'}$ in $t_i$ that is very close to $v_2$ ({\color{red}{Fig.
+x}}).
+Because all inner points of $t_i$ have the same indicator, $\lambda(v_x, P_j) = \lambda(v_{x'}, P_j)$.
+On the other hand, we find that $\lambda(v_{x'}, P_j)$ and $\lambda(v_2, P_j)$ are always equal under division $\boldsymbol{D}(C_{P_h \backslash P_j})$ ({\color{red}{may be proved}}).
+Therefore, $\lambda(v_2, P_j)$ is equal to $\lambda(v_x, P_j)$ under $\boldsymbol{D}(C_{P_h \backslash P_j})$, which is coherent with $\lambda(t_i, P_j)$ under the division of whole primitive $P_j$.
+One additional thing is that when $\lambda(v_2, P_j)=on$, $\lambda(t_i, P_j)$ can be either $same$ or $oppo$.
+The orientation test have to be performed to eliminate the ambiguity.
+
+{\color{red}{fen ge xian}}
 
@@
 The indicator of the face $i_A(f)$ should be the same as $i_A (v_2)$.
-It is because under a BSP structure with only two division planes, any sample point on $f$ except those on $I$ has the same $\lambda_A$ (Fig.
+It is because under a BSP structure with only two division planes, any sample point on $f$ except those on $I$ has the same $\boldsymbol{\Lambda}_A$ (Fig.
 ??).
@@
 
-If the CSG tree is large, with tens of, or even hundreds of nodes, computing $\lambda_\Phi(f) = \Phi(\vec{\lambda}(f))$ for every face can be costly.
+If the CSG tree is large, with tens of, or even hundreds of nodes, computing $\boldsymbol{\Lambda}_\Phi(f) = \Phi(\vec{\boldsymbol{\Lambda}}(f))$ for every face can be costly.
 Considering the space coherence of indicator, we use cache techniques --- by storing the evaluation result of $\Phi$ --- to save the computation time.
@@
 The most simple cache strategy is final result cache.
-We know indicator vector $\vec{\lambda}$ will not change if there is no intersection context during spreading.
-That means the final classification $\lambda_\Phi$ will not change, too.
-Thus, those faces sharing the same $\lambda$ can be classified as a whole.
+We know indicator vector $\vec{\boldsymbol{\Lambda}}$ will not change if there is no intersection context during spreading.
+That means the final classification $\boldsymbol{\Lambda}_\Phi$ will not change, too.
+Thus, those faces sharing the same $\boldsymbol{\Lambda}$ can be classified as a whole.
 
 Also, we can also do intermediate result cache.
-It should be noticed that $\Phi(\vec{\lambda}(f))$ can be simplified if some components of $\vec{\lambda}$ is fixed.
+It should be noticed that $\Phi(\vec{\boldsymbol{\Lambda}}(f))$ can be simplified if some components of $\vec{\boldsymbol{\Lambda}}$ is fixed.
 For example, assume we have a Boolean expression $M_1\cup (M_2\cap M_3-M_4)$.
-Given the values of two indicators $\lambda_1(x)=out$, $\lambda_2(x)=in$, the expression can be rewritten as $out\cup (in\cap M_3-M_4)$.
+Given the values of two indicators $\boldsymbol{\Lambda}_1(x)=out$, $\boldsymbol{\Lambda}_2(x)=in$, the expression can be rewritten as $out\cup (in\cap M_3-M_4)$.
 Using the combination rules we can simplify the expression as $M_3-M_4$.
@@
 \vspace{0.5em}
-\textbf{Generate Seed Indicator Vector.} Our method of generating the first indicator vector will fail on extreme conditions when each face in Linked halfedge is coincident with more than one primitive face (e.g., the union of the same mesh).
+\textbf{Generate Seed Indicator Vector.} Our method of generating the first indicator vector will fail on extreme conditions when all faces in Linked halfedge are coincident with more than one primitive face (e.g., the union of the same mesh).
 In order to be robust, we use the face barycenter with high-precision coordinates for the point-in-polyhedron test to generate the seed indicator vector after several failures of choosing a proper seed face.

### 2016-07-31 summary.tex
upload

@@
         \If {there are I-reps $\{{\boldsymbol{\Gamma}}_k\}$ on $e(t_i^c, t_c)$}
-            \State Compute $\boldsymbol{\Lambda}(t_i^c)$ using $\boldsymbol{\Lambda}(t_c)$ and $\{{\boldsymbol{\Gamma}}_k\}$
+            \State $\boldsymbol{\Lambda}(t_c), \{{\boldsymbol{\Gamma}}_k\} \Longrightarrow \boldsymbol{\Lambda}(t_i^c)$
             \State \Call{propagate} { $t_i^c$ , $\boldsymbol{\Lambda}(t_i^c)$}
@@
 
-\subsection{Fast and Exact Face Classification}
+\subsection{Fast and Exact Classification}
 
@@
 
-Given a face $t_i$ to be classified and an I-rep $\boldsymbol\Gamma$ of intersection on one of $t_i$'s edge, we denote the three corners it as $v_0^{\Gamma}, v_1^{\Gamma}, v_2,$ where the superscript $\boldsymbol\Gamma$ means the vertices are on the edge where $\boldsymbol\Gamma$ lies.
+Given a face $t_i$ to be classified and an I-rep $\boldsymbol\Gamma$ of intersection on one of $t_i$'s edge, we denote the three corners it as $v_{b*}^{0}(t_i), v_{b*}^{1}(t_i), v_b^2(t_i),$ where the subscript $*$ means the vertices are on the edge where $\boldsymbol\Gamma$ lies.
 We also denote the context component of $\boldsymbol\Gamma$ as $C_{P_h \backslash P_j}$, meaning $t_i$ is from primitive $P_j$ and intersects primitive $P_h$.
@@
 Since the faces involving in $C_{P_h \backslash P_j}$ is part of primitive $P_j$, the space division $\boldsymbol{D}(C_{P_h \backslash P_j})$ is homogeneous with the space division by $P_j$ in neighborhood of $\boldsymbol{\Gamma}$.
-The basic idea is to choose one point $v_x$ on $t_i$ close enough to $\boldsymbol{\Gamma}$ to compute $\lambda(v_x, P_j)$, and then compute $\lambda(t_i, P_j)$ accordingly.
-However, the problem is that we cannot find such a $v_x$ that can be represented exactly, which means robust classification cannot be performed.
-Fortunately, we observe that we can choose $v_2$, which is not so close to $\boldsymbol{\Gamma}$ instead.
-To illustrate, assume there is another point $v_{x'}$ in $t_i$ that is very close to $v_2$ ({\color{red}{Fig.
+The basic idea is to choose one point $v_x(t_i)$ on $t_i$ close enough to $\boldsymbol{\Gamma}$ to compute $\lambda(v_x(t_i), P_j)$, and then compute $\lambda(t_i, P_j)$ accordingly.
+However, the problem is that we cannot find such a $v_x(t_i)$ that can be represented exactly, which means robust classification cannot be performed.
+Fortunately, we observe that we can choose $v_b^2(t_i)$, which is not so close to $\boldsymbol{\Gamma}$ instead.
+To illustrate, assume there is another point $v_{x'}(t_i)$ inside of $t_i$ that is very close to $v_b^2(t_i)$ ({\color{red}{Fig.
 x}}).
-Because all inner points of $t_i$ have the same indicator, $\lambda(v_x, P_j) = \lambda(v_{x'}, P_j)$.
-On the other hand, we find that $\lambda(v_{x'}, P_j)$ and $\lambda(v_2, P_j)$ are always equal under division $\boldsymbol{D}(C_{P_h \backslash P_j})$ ({\color{red}{may be proved}}).
-Therefore, $\lambda(v_2, P_j)$ is equal to $\lambda(v_x, P_j)$ under $\boldsymbol{D}(C_{P_h \backslash P_j})$, which is coherent with $\lambda(t_i, P_j)$ under the division of whole primitive $P_j$.
-One additional thing is that when $\lambda(v_2, P_j)=on$, $\lambda(t_i, P_j)$ can be either $same$ or $oppo$.
-The orientation test have to be performed to eliminate the ambiguity.
-
-{\color{red}{fen ge xian}}
-
-During flood-filling, we propagate the indicator vector of the current face $f_0$ to its neighboring faces, which have shared edges with the current face.
-If one of shared edges has intersection context $C_{I_v \mapsto A}$, it means the indicator of primitive $A$, denoted as $i_A$, could be different for the corresponding neighboring face $f_i$.
-In this section, we will show that $C_{I_v \mapsto A}$ is enough to compute the new $i_A$ for $f_i$.
-We only discuss the condition that $f_i$ is a triangle in the following.
-However, $f_i$ may not be triangle, not even a convex polygon.
-In these conditions, we can select a triangle subset of $f_i$ to represent $f_i$, since $f_i$ is guaranteed to be classified as a whole.
-
-We develop an exact and robust classification method based on the idea of using intersection neighborhood information.
-The intersection neighborhood is abstracted into two situations of intersection context (section ??).
-To make a clear description, we denote the three corners of neighboring face $f$ as $v_0^I$, $v_1^I$, $v_2$, where the superscript means the vertex lies on the intersection line segment $I$ with intersection context $C_{I \mapsto A}$.
-In the first situation, the intersection $I$ lies on the face of primitive $A$.
-That is, $C_{I \mapsto A} = f_x^A$.
-To calculate indicator $i_A$ for $f$, we only need to decide on which side of $f_x^A$ the current  face $f$ lies.
-Any sample point on $f$ except those on $I$ can be used for this predicates.
-As we can get the exact coordinates of corners, we choose $v_2$ to compute $i_A(f)$.
-
-If $I$ lies on edge of primitive $A$,  the intersection context is face pair: $C_{I \mapsto A} = (f_p^A, f_q^A)$.
-This situation is a little more complex that we cannot decide $i_A$ until we check the orientations of both $f_p^A$ and $f_q^A$.
-To correctly classify $f$, we first build BSP structure using $f_p^A$ and $f_q^A$ [?], and then determine the space indicator $i_A(v_2)$ by the BSP.
-As coordinate of $v_2$ and all the planes can be exactly computed, the classification is exact.
-The indicator of the face $i_A(f)$ should be the same as $i_A (v_2)$.
-It is because under a BSP structure with only two division planes, any sample point on $f$ except those on $I$ has the same $\boldsymbol{\Lambda}_A$ (Fig.
-??).
+Because all inner points of $t_i$ have the same indicator, $\lambda(v_x(t_i), P_j) = \lambda(v_{x'}(t_i), P_j)$.
+On the other hand, we find that $\lambda(v_{x'}(t_i), P_j)$ and $\lambda(v_b^2(t_i), P_j)$ are always equal under division $\boldsymbol{D}(C_{P_h \backslash P_j})$ ({\color{red}{see Appendix \ref{app:profind}}}).
+Therefore, $\lambda(v_b^2(t_i), P_j)$ is equal to $\lambda(v_x(t_i), P_j)$ under $\boldsymbol{D}(C_{P_h \backslash P_j})$, and are coherent with $\lambda(t_i, P_j)$ under the division of whole primitive $P_j$.
+One additional thing is that when $\lambda(v_2(t_i), P_j)=on$, then $\lambda(t_i, P_j)$ can be either $same$ or $oppo$.
+The normal orientation test have to be performed to eliminate such ambiguity.
 
@@
 
-If the CSG tree is large, with tens of, or even hundreds of nodes, computing $\boldsymbol{\Lambda}_\Phi(f) = \Phi(\vec{\boldsymbol{\Lambda}}(f))$ for every face can be costly.
-Considering the space coherence of indicator, we use cache techniques --- by storing the evaluation result of $\Phi$ --- to save the computation time.
-
-The most simple cache strategy is final result cache.
-We know indicator vector $\vec{\boldsymbol{\Lambda}}$ will not change if there is no intersection context during spreading.
-That means the final classification $\boldsymbol{\Lambda}_\Phi$ will not change, too.
+If the CSG tree is large, with hundreds of primitive nodes, computing $\lambda_f(x)$ from $\boldsymbol{\Lambda}(x)$ for every face can be costly.
+Thanks to the space coherence of $\boldsymbol{\Lambda}(x)$, we can save the computation time by caching the evaluation result of Boolean operations.
+
+The basic cache strategy is to cache final result, that is, the value of $\lambda_f(x)$.
+We know indicator vector $\boldsymbol{\Lambda}$ will not change if there is no intersections during spreading.
+That means the final classification $\lambda_f(x)$ will not change, too.
 Thus, those faces sharing the same $\boldsymbol{\Lambda}$ can be classified as a whole.
 
-Also, we can also do intermediate result cache.
-It should be noticed that $\Phi(\vec{\boldsymbol{\Lambda}}(f))$ can be simplified if some components of $\vec{\boldsymbol{\Lambda}}$ is fixed.
-For example, assume we have a Boolean expression $M_1\cup (M_2\cap M_3-M_4)$.
-Given the values of two indicators $\boldsymbol{\Lambda}_1(x)=out$, $\boldsymbol{\Lambda}_2(x)=in$, the expression can be rewritten as $out\cup (in\cap M_3-M_4)$.
-Using the combination rules we can simplify the expression as $M_3-M_4$.
-This fact is important because for a large CSG tree, a certain primitive, denoted as $M_x$, often only intersects with a few other primitives $\Theta= \{M_{n_1}, M_{n_2}, \cdots, M_{n_k}\}$.
-That means all the faces in $M_x$ has the same indicators for the primitives not in $\Theta$.
-Therefore, we can first determine these fixed indicators and simplify the Boolean function $\Phi$ into a simpler one $\Phi_{M_x}$, and then use $\Phi_{M_x}$ to compute the final indicator for each faces.
+Also, we can perform intermediate results cache.
+We noticed that the Boolean expression can be simplified if some components of $\boldsymbol{\Lambda}(x)$ is fixed.
+For example, assume we have a Boolean expression $P_1\cup (P_2\cap P_3-P_4)$.
+Given the values of two indicators $\lambda_1(x)=out$, $\lambda_2(x)=in$, the expression can be rewritten as $out\cup (in\cap P_3-P_4)$.
+Using the combination rules we can simplify the expression as $P_3-P_4$.
+This fact is important because for a large CSG, a certain primitive, denoted as $P_x$, often only intersects with a few other primitives, like, $\Theta(P_x)= \{P_{n_1}, P_{n_2}, \cdots, P_{n_k}\}$.
+That means all the faces in $P_x$ has the same indicators for the primitives not in $\Theta(P_x)$.
+Therefore, we can first determine these fixed indicators and simplify the Boolean function, and then use simplified one to compute the final indicator for each faces in $P_x$.
 
@@
 \vspace{0.5em}
-\textbf{Generate Seed Indicator Vector.} Our method of generating the first indicator vector will fail on extreme conditions when all faces in Linked halfedge are coincident with more than one primitive face (e.g., the union of the same mesh).
-In order to be robust, we use the face barycenter with high-precision coordinates for the point-in-polyhedron test to generate the seed indicator vector after several failures of choosing a proper seed face.
+\textbf{Seed Indicator Vector Generation.} Our method of generating the first indicator vector will fail on extreme conditions when all faces in Linked halfedge are coincident with more than one primitive face (e.g., the union of the same mesh).
+In order to be robust, we use the high-precision face barycenter with the point-in-polyhedron test to generate the seed indicator vector instead after several failures of choosing a proper seed face.
 
 \vspace{0.5em}
-\noindent \textbf{Generate Seed Indicator Vector.} Our method of generating the first indicator vector will fail on extreme conditions when each face in Linked halfedge is coincident with more than one primitive face (e.g., the union of the same mesh).
-In order to be robust, we use the face barycenter with high-precision coordinates for the point-in-polyhedron test to generate the seed indicator vector after several failures of choosing a proper seed face.
+\noindent \textbf{Exact Face Classification.} In Linked halfedge, all the supporting planes of faces and all the vertices can be exactly represented.
+Based on that, when computing the new indicator according to I-reps, we can use BSP techniques similar to \cite{bernstein2009fast} to conduct robust predicates.
+Since the intersection context is neither face or edge, the space division planes in each BSP will be no more than two, which guarantees fast construction and classification.
+
+\section{Experiments}
 
@@
 
+\section{Proof of Indicator Equality}
+\label{app:profind}
+
+Using the notation in section \ref{sec:individual}, we prove the equality of $\lambda(v_{x'}(t_i), P_j)$ and $ \lambda(v_b^2(t_i), P_j)$ under the space division $\boldsymbol{D}(C_{P_h \backslash P_j})$.
+
+Because $v_{x'}(t_i)$ can be arbitrarily close to $v_b^2(t_i)$, if $\lambda(v_b^2(t_i), P_j) = in | out$, $\lambda(v_{x'}(t_i), P_j)=\lambda(v_b^2(t_i), P_j)$ holds for the continuity of space.
+If $\lambda(v_b^2(t_i), P_j) = on$, we divide the proof of $\lambda(v_{x'}(t_i), P_j)=on$ into two parts.
+If $C_{P_h \backslash P_j}$ is face neighboring type, $\boldsymbol{D}(C_{P_h \backslash P_j})$
+
 \end{document}

### 2016-08-01 summary.tex
done with the first round

@@
 
-Because $v_{x'}(t_i)$ can be arbitrarily close to $v_b^2(t_i)$, if $\lambda(v_b^2(t_i), P_j) = in | out$, $\lambda(v_{x'}(t_i), P_j)=\lambda(v_b^2(t_i), P_j)$ holds for the continuity of space.
-If $\lambda(v_b^2(t_i), P_j) = on$, we divide the proof of $\lambda(v_{x'}(t_i), P_j)=on$ into two parts.
-If $C_{P_h \backslash P_j}$ is face neighboring type, $\boldsymbol{D}(C_{P_h \backslash P_j})$
+Given $v_{x'}(t_i)$ can be arbitrarily close to $v_b^2(t_i)$, if $\lambda(v_b^2(t_i), P_j) = in | out$, the equality holds because of the continuity of space.
+If $\lambda(v_b^2(t_i), P_j) = on$, we divide the proof of equality into two parts according to the type of intersection context.
+If $C_{P_h \backslash P_j}$ is face neighboring type, $\boldsymbol{D}(C_{P_h \backslash P_j})$ is a single face, say, $t_0^c$.
+We have already know that the other two corners $v_{b*}^{0}(t_i)$ and $v_{b*}^{1}(t_i)$ are on $s_0$.
+Since $\lambda(v_b^2(t_i), P_j) = on$, we know $v_b^2(t_i)$ is on $t_0^c$, too.
+There comes the conclusion that the whole triangle $t_i$ is coplanar with $t_0^c$.
+Therefore, $v_{x'}(t_i)$ is on $t_0^c$ and $\lambda(v_{x'}(t_i), P_j) = on$, too.
+On the other hand, if $C_{P_h \backslash P_j}$ is edge neighboring type, $\boldsymbol{D}(C_{P_h \backslash P_j})$ are two neighboring faces (denoted as $t_1^c, t_2^c$).
+We know that both $v_{b*}^{0}(t_i)$ and $v_{b*}^{1}(t_i)$ are on the shared edge $e(v_{b*}^{0}(t_i), v_{b*}^{1}(t_i))$.
+It means both vertices are on both $t_1^c$ and $t_2^c$.
+Using the same deduction of the first condition, we can conclude $\lambda(v_{x'}(t_i), P_j) = on$ whenever $\lambda(v_b^2(t_i), P_j) = on$.
 

### 2016-08-05 summary.tex
8-5

@@
         Hongbo~Fu,~
-        Bin~Sheng,~and
+        Bin~Sheng,~
+        Ping Li~and
         Enhua~Wu
@@
 
+\IEEEcompsocthanksitem P. Li is with the Department of Mathematics and Information Technology, The Hong Kong Institute of Education. Email: pli@ied.edu.hk
+
 \IEEEcompsocthanksitem E. Wu is currently a research professor at State Key Lab. of Computer Science, Institute of Software, Chinese Academy of Sciences. Email: ehwu@umac.mo}
@@
 \begin{abstract}
-  In this paper, we propose an efficient non-incremental approach to evaluate the boundary of constructive solid geometry (CSG).
-The face membership classification step is a bottleneck in many existing CSG evaluation approaches.
-The key idea of our approach is to use local coherence of space labels to accelerate this step.
-We employ a two-level grouping scheme to group faces that share the same space labels.
-Therefore, these common space labels can be shared within each group to avoid repetitive computation.
-Our method is optimized for a non-incremental evaluation.
-It generates the entire result model at once, rather than performing a step-by-step evaluation of Boolean operations.
-To achieve a robust evaluation, our approach introduces plane-based geometry into the intersection computation step.
-Comparison experiments with state-of-the-art techniques show that our method can more efficiently perform boundary evaluation of both trivial and complicated CSG with massive faces while maintaining robustness.
+  Constructive solid geometry is widely used for computer aided design and manufacturing.
+However, boolean operations, which compute the boundary representation of constructive solid geometry, has been suffered from robustness and efficiency problem for more than three decades.
+In this paper, we propose a fast and exact boolean operation approach which is theoretically robust for valid triangle mesh inputs.
+This is done by introducing plane-based geometry into boolean operations and strictly follow the principle of no constructions during processing.
+Different from previous BSP-based method, our method works on halfedge, with only one-time conversion to the plane representation in intersection areas, instead of a series of complex conversions between different representations.
+Also, by using geometry connectivity and space neighboring information, our method reuse the computation iteratively, saving much computation time.
+Comparison experiments with state-of-the-art techniques show that our method is unconditionally exact and robust, while is competitively efficient with non-robust methods and much faster than exact, robust ones.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Boolean operations, triangle mesh, CSG evaluation, plane-based geometry.
+boolean operations, triangle mesh, CSG evaluation, plane-based geometry
 \end{IEEEkeywords}
@@
 \IEEEPARstart{C}{onstructive} solid geometry (CSG) has long been a popular modeling tool of computer-aided design and computer-aided manufacturing (CAD/CAM).
-It constructs complex models by combining primitives using a series of regularized Boolean operations \cite{requicha1977mathematical}: union, intersection and difference.
-CSG is often represented by a binary tree, called a CSG tree, whose leaves are primitives and whose internal nodes are Boolean operations.
-
-CSG can be converted into the widely-used  boundary representation (i.e., triangle mesh) through boundary evaluation.
-It is an classical topic with history of over three decades.
-However, one always have to make a bargain between robustness and efficiency of the boundary evaluation.
-One could use rational number arithmetic to avoid errors and thus ensure unconditional robustness, which could be over 20 times slower than a non-robust one [?].
-On the other hand, using an approximate method for boundary evaluation can be very fast, but lack exactness.
-
-Most recent methods [???] try to find a faster way to evaluate boundary of CSG, yet for robustness, the answers are often ambiguous workarounds, like setting a tolerance [?], using higher precision float point number [?] or rotating the primitive with small angle to avoid coplanar cases [?], etc.
-These tricks are often too vague to implement, heavily depend on the experiments, thus not reliable.
-Campen et.
+It constructs complex models by combining primitives using a series of regularized Boolean operations \cite{requicha1977mathematical,tilove1980closure}: union, intersection and difference.
+CSG can be converted into the widely-used boundary representation (i.e., triangle mesh) through boolean operations, which is an classical topic with history of over three decades.
+
+In general, there are two major types of Boolean algorithms according to how they deal with intersection between primitive meshes.
+Approximate methods redicretize the intersection areas, fit vertices approximatively and rearrange topology.
+On the other hand, exact method do not change vertex positions, retain as many input elements as possible (e.g., faces, vertices and topology).
+In many applications, exact methods are preferred for there accuracy.
+Also, using exact methods, the clear mapping between the surface of input and output meshes makes it easier for the inheritance of information like face colors and materials.
+However, for exact boolean operation methods, there is always a bargain between robustness and efficiency.
+Recent exact boolean operation methods try to find a faster way to compute boundaries of CSG.
+However, for robustness, the answers are often exact arithmetic \cite{barki2015exact,zhou2016mesh} or trivial workarounds, like setting a tolerance \cite{feito2013fast,segal1990using} or rotating the primitive with small angles to avoid coplanar cases \cite{douze2015quickcsg}.
+However, none of the solution is good enough.
+While exact-arithmetic based methods are significantly slower, workarounds are often case dependent and not reliable for complex CSGs.
+
+We develop an unconditionally robust and exact boolean operation method for triangle meshes without using exact arithmetic.
+The robustness of our method is based on the observations by Sugihara and Iri \cite{sugihara1990solid} that boolean operations can be performed requiring geometry constructions if representations are based on planes and not vertices.
+This idea of using plane-based representation has been developed by Berstein and Fussell \cite{bernstein2009fast} by combining it with binary search partition (BSP) techniques \cite{naylor1990merging,thibault1987set}.
+Later, Campen et.
 al.
-[?] gave a good paradigm of a unconditional robust and exact boundary evaluation methods.
-It proved to be fairly efficient, and never crashed with legal inputs.
-Since then, few exact evaluation methods declare themselves as an unconditional robust one.
-
-We prove that exact boundary evaluation of CSG can be even faster, while keeping unconditional robust.
-We adapt the plane-based techniques of Campen et.
-al.'s method for robustness, but use a framework very different from Campen et.
-al.'s, taking advantage of the recent popular idea of using geometry connectivity for face classification acceleration.
-In addition, unlike many other methods, our method can perform boundary evaluation directly for CSG with more than two primitives.
-That is, we do not incrementally generate the intermediate meshes of each Boolean operation.
-In opposite, we generate the final mesh directly.
-In this way, extra complexity of method is introduced, but we can save much computation time.
+\cite{campen2010exact} improved the method using octrees to resolve intersections locally, avoiding inefficient large BSP tree construction.
+Despite of that, Campen et.
+al.'s method still suffers from performance problem because of the complex conversions among B-reps, plane-based representations and BSP representations.
+Also, the incoherence between BSP representation, where boolean operations actually happens, and B-reps, which are input and output meshes, requires an extra stitching step to connect the reconstructed intersection areas with the untouched
+meshes, leading to extra computation burden.
+
+We adopt plane-based techniques and strictly follow the principle of no geometry construction, yet develop a very different framework based on halfedges, requiring only one-time conversion to the plane representation in intersection areas.
+Since the geometry connectivity is stored in halfedge, it allow us to take advantage of geometry connectivity for classification acceleration \cite{feito2013fast,ogayar2015deferred,updegrove2016boolean}, which is hard to for a BSP-based method.
+In addition, our method can perform boolean operations with more than two primitives in one call, instead of recursively doing binary boolean operations.
+In this way, extra complexity of our method is introduced.
+But we can save much computation time by avoiding repetitive computation.
 The experiment shows that our method is much faster than Campen et.
-al.'s method, while only about twice slower than the state-of-art non-robust methods [??].
+al.'s method, while only about two to three times slower than the state-of-art non-robust method \cite{douze2015quickcsg}.
 
 \section{Related Work}
+
+\subsection{Exact methods}
+
+Boolean operations have long been notorious with robustness issue since its inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}.
+Many researchers have attempted to solve such an issue using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}.
+However, these methods are often too expensive in computation time and memory to be practical for evaluation of CSG with massive faces.
+For example, in the Computational Geometry Algorithms Library (CGAL) \cite{cgal:hk-bonp3-15a}, the state-of-the-art robust Boolean operation algorithm \cite{hachenberger2005boolean} (implemented with arbitrary precision arithmetic) is more than 20 times slower than its non-robust version.
+
+\subsection{Approximative methods}
+
+With the development of general-purpose computing on graphics processing units (GPGPUs), many researchers  \cite{wang2011approximate, zhao2011parallel, museth2002level, chen1999volumetic, eisemann2008single} have tried to utilize the grand computation power of graphics hardware for Boolean operations.
+These methods often have good performance and are suitable for interactive applications, such as digital sculpting.
+However, owing to the paralleled features of graphics hardware, these methods are usually voxel-based and support only approximate evaluation that inevitably suffers from geometric detail loss, especially at the intersection areas of primitives.
 
@@
 We implement them using filtering techniques proposed by Shewchuk.
-
-\subsection{Exact evaluation methods}
-
-CSG evaluation has had notorious problems with robustness since its inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}.
-The non-robustness is inherited from the building blocks of CSG: Boolean operations on solids.
-Many researchers have attempted to solve such an issue using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}.
-However, these methods are often too expensive in computation time and memory to be practical for evaluation of CSG with massive faces.
-For example, in the Computational Geometry Algorithms Library (CGAL) \cite{cgal:hk-bonp3-15a}, the state-of-the-art robust Boolean operation algorithm \cite{hachenberger2005boolean} (implemented with arbitrary precision arithmetic) is more than 20 times slower than its non-robust version.
-
-\subsection{Approximative evaluation methods}
-
-With the development of general-purpose computing on graphics processing units (GPGPUs), many researchers  \cite{wang2011approximate, zhao2011parallel, museth2002level, chen1999volumetic, eisemann2008single} have tried to utilize the grand computation power of graphics hardware for Boolean operations.
-These methods often have good performance and are suitable for interactive applications, such as digital sculpting.
-However, owing to the paralleled features of graphics hardware, these methods are usually voxel-based and support only approximate evaluation that inevitably suffers from geometric detail loss, especially at the intersection areas of primitives.
 

### 2016-08-08 summary.tex
0808

@@
 \usepackage{color}
+\usepackage[numbers,sort&compress]{natbib}
 %\usepackage{ulem}
@@
   Constructive solid geometry is widely used for computer aided design and manufacturing.
-However, boolean operations, which compute the boundary representation of constructive solid geometry, has been suffered from robustness and efficiency problem for more than three decades.
+However, boolean operations, which compute the boundary representation of constructive solid geometry, have been suffered from robustness and efficiency problem for more than three decades.
 In this paper, we propose a fast and exact boolean operation approach which is theoretically robust for valid triangle mesh inputs.
@@
 \IEEEPARstart{C}{onstructive} solid geometry (CSG) has long been a popular modeling tool of computer-aided design and computer-aided manufacturing (CAD/CAM).
-It constructs complex models by combining primitives using a series of regularized Boolean operations \cite{requicha1977mathematical,tilove1980closure}: union, intersection and difference.
-CSG can be converted into the widely-used boundary representation (i.e., triangle mesh) through boolean operations, which is an classical topic with history of over three decades.
-
-In general, there are two major types of Boolean algorithms according to how they deal with intersection between primitive meshes.
+It constructs complex models by combining primitives using a series of regularized boolean operations \cite{requicha1977mathematical,tilove1980closure}: union, intersection and difference.
+CSG can be converted into the widely-used boundary representation (B-rep) through boolean operations, which is an classical topic with history of over three decades.
+
+In general, there are two major types of boolean algorithms according to how they deal with intersection between primitive meshes.
 Approximate methods redicretize the intersection areas, fit vertices approximatively and rearrange topology.
-On the other hand, exact method do not change vertex positions, retain as many input elements as possible (e.g., faces, vertices and topology).
-In many applications, exact methods are preferred for there accuracy.
+On the other hand, exact method do not change vertex positions, retain as many input elements  (e.g., faces, vertices and topology) as possible.
+In many applications, exact methods are preferred for their accuracy.
 Also, using exact methods, the clear mapping between the surface of input and output meshes makes it easier for the inheritance of information like face colors and materials.
 However, for exact boolean operation methods, there is always a bargain between robustness and efficiency.
-Recent exact boolean operation methods try to find a faster way to compute boundaries of CSG.
+Recent exact boolean operation methods try to find faster ways to compute boundaries of CSG.
 However, for robustness, the answers are often exact arithmetic \cite{barki2015exact,zhou2016mesh} or trivial workarounds, like setting a tolerance \cite{feito2013fast,segal1990using} or rotating the primitive with small angles to avoid coplanar cases \cite{douze2015quickcsg}.
@@
 al.'s method still suffers from performance problem because of the complex conversions among B-reps, plane-based representations and BSP representations.
-Also, the incoherence between BSP representation, where boolean operations actually happens, and B-reps, which are input and output meshes, requires an extra stitching step to connect the reconstructed intersection areas with the untouched
-meshes, leading to extra computation burden.
+Also, the incoherence between BSP representation, where boolean operations actually happens, and B-reps, which are input and output meshes, requires extra steps to connect the reconstructed intersection areas with the untouched meshes, leading to extra computation burden and complex topology.
 
@@
 In addition, our method can perform boolean operations with more than two primitives in one call, instead of recursively doing binary boolean operations.
-In this way, extra complexity of our method is introduced.
+In this way, extra complexity is introduced.
 But we can save much computation time by avoiding repetitive computation.
+The major difficulty of applying plane-based representation on halfedge is by the incoherence between the two representations.
+Halfedge is a vertex-based representation.
+Many geometry operations (e.g., coordinates projection and compute the barycenter coordinate of triangle) available on halfedge can be very complex and thus inefficient under plane-based representation.
+On the other hand, we have to compute under plane-based representation for exactness and robustness.
+Therefore, we manage to limit our computation of boolean operations to several basic plane-based predicates.
 The experiment shows that our method is much faster than Campen et.
@@
 
-\subsection{Exact methods}
-
-Boolean operations have long been notorious with robustness issue since its inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}.
-Many researchers have attempted to solve such an issue using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}.
-However, these methods are often too expensive in computation time and memory to be practical for evaluation of CSG with massive faces.
-For example, in the Computational Geometry Algorithms Library (CGAL) \cite{cgal:hk-bonp3-15a}, the state-of-the-art robust Boolean operation algorithm \cite{hachenberger2005boolean} (implemented with arbitrary precision arithmetic) is more than 20 times slower than its non-robust version.
-
-\subsection{Approximative methods}
-
-With the development of general-purpose computing on graphics processing units (GPGPUs), many researchers  \cite{wang2011approximate, zhao2011parallel, museth2002level, chen1999volumetic, eisemann2008single} have tried to utilize the grand computation power of graphics hardware for Boolean operations.
-These methods often have good performance and are suitable for interactive applications, such as digital sculpting.
-However, owing to the paralleled features of graphics hardware, these methods are usually voxel-based and support only approximate evaluation that inevitably suffers from geometric detail loss, especially at the intersection areas of primitives.
-
-\subsection{Plane-based geometry representation}
-
-The primary information of commonly used representation of solids are the vertex coordinates.
-In this way, edges and faces are implicitly represented by combination of vertices.
-In contrast, in plane-based representation, the primary elements are planes.
-Vertices and edges are all implicitly represented by plane intersections.
-
-The concept of plane-based representation of polygonal meshes was first described by Sugihara and Iri \cite{sugihara1990solid}. Plane-based representation provides one important advantage
-when it comes to tasks that involve changing the topology of solids represented by meshes like the evaluation of Boolean expressions: no new primary geometry information has to be constructed to obtain the resulting polyhedron ¨C it is composed of a subset of the planes of the input polyhedra.
-Hence, opposed to the case of using vertex coordinates, that inevitably necessitates the construction of new geometry information, only geometric decision predicates are required to compose the output polyhedron from the face planes of the input.
-Since the input is usually given in a numerical representation with finite precision, we can determine an upper bound on the precision that is needed to make correct decisions.
-The a priori knowledge of this upper bound allows us to use fixed precision predicates that are specifically tailored to the precision required in the worst case, resulting in a vastly better performance compared to techniques for arbitrary numerical precision, that are usually required when
-constructions are part of the processing.
-Our processing is rigorously based on this paradigm of plane-based geometry representation that allows us to perform fully robust, exact computations using only fast fixed precision predicates.
-These predicates take planes as arguments and check coincidence and co-orientation of planes, orientation of a plane with respect to a point defined by the intersection of three planes, and whether three planes intersect in a unique point.
-The latter one can also be used in negated form to check if three planes, that are known to intersect in a common point, even intersect in a common line.
-We implement them using filtering techniques proposed by Shewchuk.
+Boolean operations have long been researched for over three decades since it inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}.
+Most previous work of boolean operations can be classified into two categories: exact and approximate methods.
+Exact methods retain vertex positions.
+And the topology of the input meshes is also preserved as much as possible.
+The coordinates of intersection points between input meshes are computed by input configurations to construct the topology around intersection.
+However, the coordinates cannot be represented exactly using fix-precision float point numbers and the robustness is often a problem.
+Using exact arithmetic is too expensive in computing.
+Therefore, exact methods face the problem of the balance between performance and robustness.
+On the other hand, approximate methods rediscretize the input mesh surfaces using techniques such as voxels, octrees and Layered Depth Images and can reach better performance and robustness.
+
+\subsection{Exact Methods}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=2.5in]{coplanarexample}
+\caption{{\color{red}{Sketch: the example of coplanar cases in a boolean operations with four cylinders}}}
+\label{fig:coplanarexample}
+\end{figure}
+
+For exact methods, some \cite{ogayar2015deferred,douze2015quickcsg,zhou2016mesh,xu2013fast,feito2013fast} pursues efficiency but cannot guarantee robustness in degenerate cases such as coplanar conditions.
+Most of them are implemented by fix-precision float-point arithmetic and round errors accumulation is often inevitable.
+Douze et al.
+\cite{douze2015quickcsg} implemented very efficient boolean operations that can handle very large meshes.
+Also, their method is able to perform variadic boolean operations: evaluating the final result mesh of CSG all at once instead of decomposing the CSG into a series of binary boolean operations.
+However, their method cannot deal with coplanar cases nor guarantee accuracy for common situations.
+On the contrary, CSGs with large meshes contain are more complex and more likely to contain degenerate cases.
+Also, coplanar cases can regularly happens for man-made artifact modeling (Fig.
+\ref{fig:coplanarexample}) and should not be treated as exceptions for boolean operation methods.
+
+Many researchers have attempted to solve robustness issue for exact boolean operations using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}.
+These methods are often too expensive in computation time and memory to be practical for CSG with massive faces.
+For example,
+the current standard of robust exact boolean operations method is CGAL's \cite{cgal:hk-bonp3-15a} exact-arithmetic implementation \cite{granados2003boolean} of Nef polyhedra \cite{bieri1988elementary}.
+It requires conversions between Nef polyhedra and input mesh data structures during evaluation and is more than 50 times slower than non-robust booleans \cite{bernstein2009fast}.
+
+\subsection{Approximative Methods}
+
+Since efficiency, accuracy and robustness seem unable to be obtained at the same time, starting from \cite{museth2002level}, some sacrifice accuracy for better efficiency and robustness.
+Most of such methods are based on conversion to volumetric representations.
+However, the quality of result mesh depends on the resolution of the volume grid and better quality requires higher resolution.
+To accelerate this process, some try to reduce the complexity of the output mesh \cite{varadhan2004topology} and others try to preserve non-intersected areas of the input mesh to avoid redundant tessellation \cite{pavic2010hybrid,wang2011approximate,zhao2011parallel,hable2005blister,ogayar2006gpu}.
+Also, with the development of general-purpose computing on graphics processing units, many of them utilize the grand computation power of graphics hardware for boolean operations.
+These methods often have good performance and are suitable for interactive applications.
+However, the fundamental problem of approximate methods is owing to grid-depend nature of volumetric calculations: they inevitably suffers from geometric detail loss and unwieldy topology changes.
+
+\subsection{Plane-Based Methods}
+\label{sec:pbrelated}
+
+The concept of plane-based representation of polygonal meshes was first described by Sugihara and Iri \cite{sugihara1990solid}.
+Such representation provides important advantage that for boolean operations, no new primary geometry information has to be constructed to obtain the result polyhedron---it is composed of a subset of the planes of the input polyhedra.
+Berstein and Fussell \cite{bernstein2009fast} combined the plane-based representation with binary space partitioning (BSP) \cite{thibault1987set,naylor1990merging} to develop an unconditionally robust boolean operation method.
+Compared to volume-grid based methods, their BSP-based method increases mesh complexity more moderately and the input topology can be reconstructed better.
+However, it requires conversions between input data structures and plane-based representation which are inefficient from both storage and time views.
+Also, the merge of two BSP trees is an $O(mn)$ time complexity process, where $m$ and $n$ are the size of the trees.
+It makes this method impractical for very large input meshes.
+Campen and Kobbelt \cite{campen2010exact} improved their method by localization using an octree.
+And the refinement only takes place locally near intersections.
 
@@
 \label{sec:overview}
-Our method is designed for boundary evaluation of Boolean operations on arbitrary number of primitives.
-Input primitives should be watertight and non-manifold  triangle meshes, represented by halfedge structures\cite{mcguire2000half}.
-Our method is unconditional robust, exact, while keeping good performance.
-In this section, we first introduce the motivation of our method, then describe where we start to design our boundary evaluation method.
-At last, we give the overview of the method.
-
-\subsection{Motivation}
+Our method is designed for boolean operations on arbitrary number of triangle meshes.
+Input mesh primitives are required to be watertight and not self-intersected, with manifold surface, represented by wide-used halfedges \cite{mcguire2000half}.
+Despite of so many constraints, our method is not sensitive to topology deficiencies and works well if deficiencies are not near the intersection areas between meshes.
+
+\subsection{Background \& Motiviation}
 \label{sec:paradigm}
 
-The boundary evaluation is in essence a process of selection.
-In other words, given a Boolean function, it reserves those primitive faces that pass the function and drop the others to generate the final mesh.
-Unfortunately, for B-reps primitives such as triangle mesh, not all the facets from the input primitives can be classified in a whole, since some of them intersect other primitives.
-Therefore, we need an extra step aiming at detecting the intersection between primitives and performing the tessellation.
-In general, most of the boundary evaluation methods follow the two-step paradigm  \cite{wang2011approximate} above, which consists of intersection computation and face classification.
-
-During the intersection computation, primitive facets are tested in pairs to compute their intersection.
-Each input primitives are tessellated according to the intersection test results, making every face be either inside, outside or on the boundary of other primitives.
-They are what we called \emph{non-intersected meshes}.
-Every face of non-intersected meshes can be classified in a whole during classification.
-Unfortunately, under common float-point coordinate system, intersection test is error-prone.
-There are mainly two causes: first, there are a large amount of degenerate cases which are hard to be exactly detected; second, when there are intersections, new vertices are introduced into the geometry, whose coordinates usually can not be exactly represented by float-point number.
-
-Face classification is to evaluate whether a given face $x$ belongs to the final geometry according to the n-primitive Boolean function $f$ :
+The boolean operation of triangle meshes is in essence a process of selection.
+In other words, given a boolean function, it reserves those primitive faces that pass the function and drop the others to generate the final mesh.
+Unfortunately, for B-reps primitives such as triangle mesh, not all the facets from the input primitives can be classified as a whole, since some of them intersect other primitives.
+Therefore, we need an extra step aiming at detecting the intersection between primitives and performing tessellation.
+Most of the boolean operation methods follow this two-step paradigm, which consists of intersection computation and face classification.
+So is our method.
+
+During the intersection computation, primitive facets are tested in pairs to compute their intersections.
+Each input meshes are tessellated according to the intersection results, making every face be either inside, outside or on the boundary of other primitives.
+The retessellated meshes are what we called \emph{non-intersected meshes}.
+Unfortunately, under fix-precision float-point arithmetic, intersection test is error-prone for two causes: first, there are a large amount of degenerate cases which are hard to be precisely classified; second, when there are intersections, new vertices are introduced into the geometry, whose coordinates cannot be exactly represented by float-point numbers.
+
+The second step, face classification, is to evaluate whether a given face $x$ belongs to the final geometry according to the n-primitive boolean function $f$ :
 \begin{equation}
@@
 The parameter $\lambda_i(x)$ is space indicator with respect to primitive $P_i$.
-This means to classify a face, one has to know the space indicators with respect to all the primitives (or the whole indicator vector $\boldsymbol{\Lambda}(x)$ for short).
+To classify a single face $x$, one has to know the space indicators with respect to all the primitives (or their vector representation $\boldsymbol{\Lambda}(x)$).
 A space indicator has four conditions: completely inside (\emph{in}), completely outside (\emph{out}), on the boundary with consistent normals (\emph{same}) or opposite normals (\emph{oppo}).
-The rules of Boolean function evaluation by these indicators are described in \cite{douze2015quickcsg}\cite{feito2013fast}.
+The rules of Boolean function evaluation by these indicators are described in \cite{douze2015quickcsg,feito2013fast}.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=2.5in]{falseclass}
+\caption{{\color{red}{Sketch: False classification}}}
+\label{fig:falseclass}
+\end{figure}
 
 Face classification also suffers from robustness and exactness problems.
-Many methods classify face according to the indicators of its barycenter, and use point-in-polyhedron test to compute these indicators.
-However, coordinates of barycenters cannot be exactly represented and have the potential to generate false classification.
-In addition, to classify a single face, all the components of its space indicator vector must be figured out.
-Considering the large amount of faces, acceleration is usually necessary.
-Many algorithms take the benefits of the local coherence of indicators, classifying neighboring faces together.
-While this does improve the performance, it can make the exactness problem worse because the false classification can be propagated to neighboring faces.
-
-We want to develop a new boundary evaluation method based on the two-step paradigm, keeping unconditional robust, exact and as fast as possible.
-Combined with the analysis above, we think our method should includes the following features:
+Many methods classify face according to the indicators of its barycenter, which can be computed by point-in-polyhedron test \cite{feito2013fast,campen2010exact}.
+However, coordinates of barycenters cannot be exactly represented and have the potential to generate false classification (Fig.
+\ref{fig:falseclass}).
+In addition, for the large amount of faces and input meshes, many methods take the benefits of the local coherence of indicators, classifying neighboring faces together \cite{pavic2010hybrid,feito2013fast,ogayar2015deferred,zhou2016mesh}.
+While this does improve the performance, it can make the robustness problem worse because the false classification may be propagated to neighboring faces.
+
+We want to develop an exact boolean operation method based on the two-step paradigm, being unconditional robust and as fast as possible.
+Considering the analysis above, we think our method have to include the following features:
 \begin{itemize}
-    \item It has to avoid errors when introducing new vertices during intersection computation. All degenerate cases of intersection have to be well resolved.
-    \item Face classification has to be exact. On the other hand, acceleration using local coherence of indicators may be helpful.
-    \item The exactness and robustness should not rely on arbitrary precision arithmetic, because it is too slow.
-Instead, we choose the plane-based techniques from \cite{bernstein2009fast}\cite{campen2010exact} to ensure good performance.
+    \item Intersection computation has to avoid errors when introducing new vertices into meshes.
+    \item All degenerate cases of intersection between input meshes have to be well resolved.
+    \item Face classification has to be exact and robust.
+    \item Acceleration using geometry connectivity is necessary for face classification.
 \end{itemize}
 
-\subsection{Linked halfedge}
+For efficiency, the exactness and robustness should not rely on arbitrary precision arithmetic.
+Instead, we choose the plane-based techniques from \cite{campen2010exact}.
+However, as we discussed in section \ref{sec:pbrelated}, BSP structure does not support geometry connectivity query in nature, and we do not want fussy conversions between different representations.
+Therefore, we use halfedge instead as our major data structure and embed plane-based representation into it.
+
+\subsection{Linked Halfedge}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=2.5in]{linkedhalfedge}
+\caption{{\color{red}{Sketch: The Linked Halfedge structure}}}
+\label{fig:linkedhalfedge}
+\end{figure}
+
+\begin{figure*}[!t]
+\centering
+\includegraphics[width=7.1in]{flowchart}
+\caption{{\color{red}{Sketch: overview, will be replaced}}}
+\label{fig:overview}
+\end{figure*}
 
 \label{sec:meshes}
-We make an essential observation that the non-intersected meshes, as intermediate result of intersection computation, plays a very important role of the method design.
-It is a bridge that controls the complexity of intersection computation and facilitates the face classification.
-After the non-intersected meshes is determined, all things left are how to construct such a data structure and how to classify according to it.
-
-Our non-intersected mesh, called Linked Halfedge, is a variance of halfedge, a well-known data structure to represent solids.
-Halfedge has two advantages: first, since halfedge is popular, using it as the intermediate data structure can avoid unnecessary conversion, which has the potential to create simpler algorithm and better performance and result topology; second, the geometry connectivity, by which we accelerate classification using local coherence of space indicators, can be easily retrieved through halfedge.
+We made an observation that the non-intersected meshes, as intermediate result of intersection computation, plays an important role of boolean operations.
+It is a bridge that controls the complexity of intersection computation and facilitates face classification.
+After the data structure of non-intersected meshes is determined, all things left are how to construct this structure and how to classify according to it.
+
+Our non-intersected mesh, called Linked Halfedge (Fig.
+\ref{fig:linkedhalfedge}), is a variance of halfedge, a wide-used data structure to represent solids.
+Halfedge has two advantages: first, since halfedge is popular, using it as the intermediate data structure can avoid unnecessary conversion, which has the potential to have better performance and result topology; second, the geometry connectivity, by which we accelerate classification using local coherence of space indicators, can be easily retrieved through halfedge.
 
@@
 Therefore, we utilize plane-based representation to avoid computing new coordinates.
-In addition, we detect all coincident vertices among primitives and linked them together (that is why it is called Linked Halfedge).
-This information is used for avoiding repetitive vertices, reconstructing geometry connectivity, and ensuring the topology correctness.
+In addition, we detect all coincident vertices among input meshes (including intersection vertices).
+This information is used for avoiding repetitive vertices in the final mesh, reconstructing geometry connectivity, and ensuring the topology correctness.
 
@@
 \cite{feito2013fast}, we found that the the topology near intersection lines between faces can benefit point-in-polyhedron test by dramatically reducing the number of faces needing traversing.
-Therefore, we add extra information into the Linked Halfedge, called \emph{intersection context}, to facilitate afterwards face classification.
+Therefore, we add what we call \emph{intersection context} into the our non-intersected meshes to facilitate afterwards face classification.
 Intersection context identifies where an intersection lies on the surface of the related primitives.
-An edge of Linked Halfedge has intersection context only if it is coincident with a certain intersection line segment between primitives.
-We will give the definition and usage of intersection context in details in the following sections.
-
-To give a overall impression of how we design Linked Halfedge, we summarize the above content and highlight the following features:
+An edge of Linked Halfedge stores intersection context only if it is coincident with a certain intersection line segment between primitives.
+We will give the definition and usage of intersection context in details in section \ref{sec:ir}.
+
+To give an overall impression of Linked Halfedge, we summarize the above content and highlight the features of Linked Halfedge as follows:
 
 \begin{itemize}
-  \item Each input primitive mesh is tessellated into a Linked Halfedge. Faces in a Linked Halfedge must not cross any other Linked Halfedges.
+  \item Each input mesh is tessellated into a Linked Halfedge by intersection computation.
   \item Coincident vertices between different Linked Halfedge should be linked, that is, coincident vertices are shared among Linked Halfedges.
@@
 
-\subsection{Method overview}
+\subsection{Method Overview}
+
+As illustrated in Fig. \ref{fig:overview}, we divide our methods into four steps as follows.
 
@@
 Intersection between triangle faces and octree leaves can be efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}.
-Octree leaves are classified into two types: if all faces that intersect a leaf belong to the same primitive, we call it a \emph{non-critical cell}.
-Otherwise, it is a \emph{critical cell}.
-
-The difference between our space division and many others \cite{ogayar2015deferred}\cite{feito2013fast} is the octree node subdivision termination criterion.
-In our method, we do not need subdivide any non-critical cell no matter how many faces it contains.
-This is because subdividing non-critical cells benefits only the ray-casting point-in-polyhedron test, which rarely appears in our method.
-This simplification can bring large performance advantage, especially for those cases where intersections between primitives are not complex and limited in small regions.
+Octree leaves are classified into two types: if all faces that intersect a leaf belong to the same primitive, we call it a \emph{normal cell}.
+Otherwise, it is a \emph{critical cell}, within which the following intersection detection is performed.
+
+The difference between our space division and Ogayar et al.'s is that we do not subdivide any normal cell no matter how many faces it contains.
+This is because subdividing normal cells benefits only the ray-casting point-in-polyhedron test  \cite{frisken2002simple}, which seldom uses in our method.
+This simplification can bring large performance advantage, especially for those cases where intersections between primitives are not complex and limited in small regions (e.g.
+Fig.
+\ref{fig:models}(x)).
 
@@
 Our algorithm is largely based on vertex-based M\"{o}ller's algorithm \cite{moller1997fast}, which is very efficient to compute intersection between two triangles.
-However, naive implementation of M\"{o}ller's algorithm always incurs robustness issues when computing the coordinates of new vertices.
-To avoid an unexpected failure caused by numeric errors, we integrate plane-based representation of polyhedra \cite{sugihara1990solid} into the implementation of M\"{o}ller's algorithm.
-Adaptive precision predicate technique \cite{shewchuk1997adaptive} is applied for efficiency of plane-based geometry computation.
-Moreover, to make our method robust, we classify all the intersection cases into three major classes and respectively discuss how to each condition.
+However, naive implementation of M\"{o}ller's algorithm always incurs robustness issues.
+To avoid an unexpected failure caused by numeric errors, we integrate plane-based representation of polyhedra into M\"{o}ller's algorithm.
+All intersection vertices are represented using plane intersections to avoid geometry constructions.
+Also, we carefully identify all degenerate cases of triangle intersections, including point intersection, line intersection and coplanar intersection, and respectively discuss how to deal with each of them.
 Details are provided in Section \ref{section:isect}.
@@
 
-Once all intersections are detected, we need to tessellate the input primitives and construct the Linked Halfedges..
+Once all intersections are detected, we need to tessellate the input primitives and construct the Linked Halfedges.
 In many methods like \cite{ogayar2015deferred}, constraint Delaunay triangulation (CDT) is applied to perform tessellation, since the intersections are naturally the constraints of CDT.
-However, for a CSG with more than two primitives, the intersection vertices may be generated by intersections of three faces from different primitives, which cannot be computed during the previous step.
-Also, intersection line segments may overlap or intersect with each other, and cannot be used for constraints of CDT directly.
-Finally, as our intersection vertices are represented exactly by planes, implementation of CDT could be complex and inefficient, as most CDT methods were not designed to handle planes.
-Therefore, we design a simple structure, called Tess-graph, to guide the tessellation of each single face, and develop a very fast but exact method to construct Linked Halfedges from Tess-graphs, which is suitable for dealing with plane-based representation of intersections.
+However, for a CSG with more than two primitives, the intersection vertices may be generated by intersections of three faces from different primitives, which cannot be computed during by triangle-triangle intersections in the previous step.
+Intersection line segments may overlap or intersect with each other, and cannot be used for constraints of CDT directly.
+In addition, as our intersection vertices are represented exactly by planes, implementation of CDT are complex and inefficient, as most CDT methods were not designed to handle planes and requires explicit coordinates.
+Therefore, we design a structure suited for plane-based representation, called \emph{Tess-graph}, to guide the tessellation of each single face, and develop a very fast but exact method to construct Linked Halfedges from Tess-graphs.
 Details are shown in section \ref{sec:tessellation}.
@@
 This step is to choose faces from the Linked Halfedges to generate the final mesh.
-Literally compute all the space indicators of each face is unacceptable slow for large CSG trees.
-Enlightened by Feito et.
-al.
-\cite{feito2013fast}, we utilize the geometry connectivity to accelerate this process.
-In Feito et.
-al.'s method, the faces of tessellated meshes are first grouped according to whether they have the same indicator vector.
-After the grouping, each group is classified as a whole.
-This is based on the observation that indicators of faces are spatially coherent.
-That is, if a face $f$ is outside of primitive $M_0$, the neighbor of $f$ are likely to be out of $M_0$, too.
-Different from Feito et.
-al.'s method, we also consider the condition when the number of primitives is larger than two.
-In this condition, space vector of a face may be partly the same with its neighborhoods'.
-That is, we allow space indicators not only share within faces of the same group, but also among different groups and even primitives.
-This is useful when the number of primitives is large, or intersections between primitives is complex.
+Literally computing all the space indicators of each face is unacceptably slow for large CSG trees.
+We utilize the geometry connectivity to accelerate this process.
+This is based on the observation that indicators of faces are locally coherent.
+Many method uses barycenters of faces together with point-in-polyhedra test for face classification, which is not exact nor robust with fix-precision float-point coordinates.
+Douze et al.
+\cite{douze2015quickcsg} classifies faces using space indicators of vertices, but failed to deal with coplanar conditions because of coplanar leads to ambiguity in such configurations.
+Different from all above, we classify faces based on the classification results of exactly represented vertices, including input vertices and newly introduced intersection vertices, and carefully deal with coplanar conditions to ensure topology consistency.
 Details will be shown in section \ref{sec:classification}.
@@
 
-Vertex coordinates are commonly used in geometry computation.
-However, vertex coordinates suffer from inexact representation of intersection point between primitives.
-Therefore, we choose to use planes-based representation of polyhedrons and implicitly represent vertex by plane intersection.
-We start with a quick review of the basic conception of plane-based representation.
-After that, we introduce two substrates related to plane-based representation used in our method, since these two are rarely seen in related researches.
-Other substrates of plane-based representation can be seen in \cite{bernstein2009fast}.
+\begin{figure}
+  \centering
+  % Requires \usepackage{graphicx}
+  \includegraphics[width=1.7in]{p-reps}\\
+  \caption{Plane-based representation of triangles. The yellow triangle is represented by three bounding planes (green) and the supporting plane where the triangle lies.}\label{fig:p-reps}
+\end{figure}
+
+As we discussed in Section \ref{sec:paradigm}, one of the problem in boolean operations under vertex-based representation is it inevitably introduces new vertices, whose coordinates cannot be exactly represented using fix-precision float-point number.
+On the other hand, if plane-based representation is used, no new geometry information needs to be constructed.
+Therefore, we can use only geometric decision predicates to perform boolean operations.
+As the precision of input coordinates is finite, we can determine in advance the upper boundary of precision needed to perform a precise decision, with which we can use fixed precision predicates techniques to gain much performance while keeping exactness.
+For efficiency, we implement the predicates using filtering techniques proposed by Shewchuk \cite{shewchuk1997adaptive}.
+
+Using plane-based representation, each face of polyhedron is represented by a supporting plane $p^s$, where the face lies, and a list bounding planes $\{p^b_i \ \vert\  i = 1, 2, 3\}$, each has a corresponding edge (Fig.
+\ref{fig:p-reps}).
+Edge line is represented by intersection of $p^s$ and the related $p^b_i$.
+Corner vertex is the intersection of $p^s$ and two consecutive bounding planes $p^b_i$ and $p^b_{i+1}$.
+
+We also introduce some other notations before starting our discussion.
+A plane $p_x$ can be represented by plane coefficients $(a_x, b_x, c_x, d_x)$.
+The normal of $p_x$ is denoted as $\vec{n}_x$.
+A line $l$ can be represented by intersection of two planes $(p_m, p_n)$, or in short, $l\colon(p_m, p_n)$.
+The positive direction of the line $\vec{l}$ is defined by $\vec{n}_a \times \vec{n}_b$.
+A point $v$ is represented by non-trivial plane triples $(p_a, p_b, p_c)$, or in short, $v\colon(p_a, p_b, p_c)$.
 
@@
 
-As we discussed in Section \ref{sec:paradigm}, one of the problem in Boolean evaluation under vertex-based representation is it inevitably introduces new vertices, whose coordinates cannot be exactly represented using common float-point number.
-On the other hand, if plane-based representation is used, no new geometry information needs to be constructed.
-Therefore, we can use only geometric decision predicates to perform the boundary evaluation, which means it is exact and robust.
-
-Using plane-based representation, each face of polyhedron is represented by a supporting plane $p^s$, where the face lies, and a list bounding planes $\{p^b_i \ \vert\  i = 1, 2, 3\}$, each has  a corresponding edge.
-Edge line is represented by intersection of $p^s$ and the related $p^b_i$.
-Corner vertex is then the intersection of $p^s$ and two consecutive bounding planes $p^b_i$ and $p^b_{i+1}$.
 Efficient and exact conversion from the vertex-based representation to plane-based representation is described in detail in \cite{campen2010exact}.
@@
 If the plane coefficient has $M$ bit precision, $M$ have to greater than or equal to $P$ for exact conversion.
-However, different from \cite{campen2010exact}, we choose to enforce the criterion to $M \ge P+1$, and we will explain the enforcement in section \ref{sec:embed}.
-
-Let $\delta = 2^{K-L-1}$ be the relative length (in max-norm) of the
-longest edge in the mesh (relative to the bounding box).
+However, different from \cite{campen2010exact}, we choose to enforce the criterion to $M \ge P+1$.
+This enforcement of criterion allow us to perform predicates of orientation of plane $p_x$ with respect to a point $v$ with exact $L$-bit coordinates by simply compute the sign ${\vec{n}_x}\cdot{v} + d_x$ within $M$-bit precision, instead of first converting $v$ into its plane-based representation and then computing the sign of 4x4 determinant.
+This can save much computation time by avoid unnecessary conversion for intersection computation.
+
+Let $\delta = 2^{K-L-1}$ be the relative length (in max-norm) of the longest edge in the mesh (relative to the bounding box).
 If we use IEEE 754 double precision ($M=53$) and assume $\delta \le 2^{-5.5} \approx 0.22$, the maximum input precision $L$ can reach to 20, which is enough for most application.
-As the precision of input coordinates is finite, we can determine in advance the upper boundary of precision needed to perform a precise decision, with which we can use fixed precision predicates techniques to gain much performance while keeping exactness.
-We implement the predicates using filtering techniques proposed by Shewchuk \cite{shewchuk1997adaptive}.
 
@@
 
-Before we start the discussion, we first introduce several regulations frequently used in the rest of our paper.
-A plane $p_x$ can be represented by plane coefficients $(a_x, b_x, c_x, d_x)$.
-The normal of $p_x$ is denoted as $\vec{n}_x$.
-Under plane-based representation, a line $l$ can be represented by intersection of two planes $(p_m, p_n)$, or in short, $l\colon(p_m, p_n)$.
-The positive direction of $l$ is defined by cross product of the normals of $p_a$ and $p_b$, that is, $\vec{l} = \vec{n}_a \times \vec{n}_b$.
-A point $v$ is represented by plane triples $(p_a, p_b, p_c)$, or in short, $v\colon(p_a, p_b, p_c)$.
-
-Suppose there is an edge $e_i(f)$ of a face $f$, and the line of $e_i(f)$, denoted as $l_{i}(f)$, can represented as intersection of supporting plane $p^s(f)$ and bounding plane $p_i^b(f)$.
-Given two arbitrary points $v_p$ and $v_q$ on $l_{i}(f)$, they can be represented by plane triples $(p^s(f), p_i^b(f), p_p)$ and $(p^s(f), p_i^b(f), p_q)$, sharing the same first two components.
-We want to determine if $v_q$ is in positive side of $v_p$ along $\vec{l}_{i}(f)$.
-We call this predicate as \emph{two-point-one-line comparison}.
-This problem can be converted to the problem of orientation of a plane $p_p$ with respect to a point $v_q$, except that there is an extra request---we have to guarantee cosine between $\vec{l}_{i}(f)$ and the $\vec{n}_p$ (normal of plane $p_p$) be positive.
-If not, we negate the normal of $p_p$, and the coordinate of  $v_p\colon(p^s(f), p_i^b(f), p_p)$ remains unchanged.
-
-Another predicates is used when tessellating a face (section \ref{sec:tessellation}).
+Given an arbitrary line $l\colon(p_m, p_n)$ with two points $v_p$ and $v_q$ on $l$, the two points can be represented by plane triples $(p_m, p_n, p_p)$ and $(p_m, p_n, p_q)$, sharing the same first two components.
+We want to determine if $v_q$ is in positive side of $v_p$ along $\vec{l}$.
+We call this predicate as \emph{two-point-one-line comparison} (Fig.
+\ref{fig:twopointoneline}).
+This problem can be converted to the problem of orientation of a plane $p_p$ with respect to a point $v_q$, except that there is an extra request---we have to guarantee $\vec{l}$ and $\vec{n}_p$ have the same orientation.
+If not, we negate the normal of $p_p$, and the implicit coordinate of  $v_p\colon(p_m, p_n, p_p)$ remains unchanged.
+
+Another predicates is called \emph{two-line-one-plane comparison} (Fig.
+\ref{fig:substrates}).
 Given two coplanar lines $l_a\colon(p_0, p_a)$ and $l_b\colon(p_0, p_b)$, we want decide whether the cross product of $\vec{l}_a$ and $\vec{l}_b$ has the same orientation as $\vec{n}_0$ (the normal of $p_0$).
-We call it as \emph{two-line-one-plane comparison}(Fig.
-\ref{fig:substrates}).
 Direct solution requires to explicitly compute the vector of $l_a$ and $l_b$ and then decide the sign of $\vec{n}_0 \cdot (\vec{l}_a \times \vec{l}_b)$.
-However, explicit representation of $\vec{l}_a$ and $\vec{l}_b$ requires more bits than standard double precision float point number, bringing extra computation burden.
-
-To solve this, we decompose the normal vectors of $p_a$ and $p_b$: $\vec{n}_a = \vec{n}^\parallel_a + \vec{n}^\perp_a$ and $\vec{n}_b = \vec{n}^\parallel_b + \vec{n}^\perp_b$.
+However, explicit representation of $\vec{l}_a$ and $\vec{l}_b$ cannot be represented by the float point number.
+
+To solve this, we decompose the normal vectors of $p_a$ and $p_b$ by the normal of $p_0$: $\vec{n}_a = \vec{n}^\parallel_a + \vec{n}^\perp_a$ and $\vec{n}_b = \vec{n}^\parallel_b + \vec{n}^\perp_b$.
 Here superscript `$\parallel$` means the vector is in the plane $p_0$ and `$\perp$` means it is orthogonal to $p_0$.
@@
 
+\begin{figure}
+  \centering
+  % Requires \usepackage{graphicx}
+  \includegraphics[width=2.5in]{twopointoneline}\\
+  \caption{{\color{red}{Sketch: config of two point one line comparison}}}\label{fig:twopointoneline}
+\end{figure}
+
 \begin{figure}[t]
@@
 \includegraphics[width=2.5in]{projection}
-\caption{$Seg_1$ is the intersection between $p^s(f_2)$ and $f_1$.
-$Seg_2$ is the intersection between $p^s(f_1)$ and $f_2$.
-The intersection between $f_1$ and $f_2$, which is the line segment in red, is the overlap of $Seg_1$ and $Seg_2$.}
+\caption{$Seg_1$ is the intersection between $p^s(t_2)$ and $t_1$.
+$Seg_2$ is the intersection between $p^s(t_1)$ and $t_2$.
+The intersection between $t_1$ and $t_2$, which is the line segment in red, is the overlap of $Seg_1$ and $Seg_2$.}
 \label{fig_projection}
@@
 
-M\"{o}ller's algorithm computes the intersection between two triangles $f_1$ and $f_2$ in three steps (Fig. \ref{fig_projection}).
+M\"{o}ller's algorithm computes the intersection between two triangles $t_1$ and $t_2$ in three steps (Fig. \ref{fig_projection}).
 \begin{itemize}[leftmargin=0.45cm]
-\item[1)] An early rejection is performed by testing whether $f_1$ intersects $p^s(f_2)$, the supporting plane of $f_2$.
-This is a necessary condition of intersection between $f_1$ and $f_2$.
-If this test is passed, then the same is performed for $f_2$ and $p^s(f_1)$.
-\item[2)]The intersection between $f_1$ and $p^s(f_2)$, denoted as $Seg_1$, and the intersection between $f_2$ and $p^s(f_1)$, denoted as $Seg_2$, are separately computed .
- \item[3)]The intersection between $f_1$ and $f_2$ is determined by computing the overlap area of $Seg_1$ and $Seg_2$ .
+\item[1)] An early rejection is performed by testing whether $t_1$ intersects $p^s(t_2)$, the supporting plane of $t_2$.
+This is a necessary condition of intersection between $t_1$ and $t_2$.
+If this test is passed, then the same is performed for $t_2$ and $p^s(t_1)$.
+\item[2)]The intersection between $t_1$ and $p^s(t_2)$, denoted as $Seg_1$, and the intersection between $t_2$ and $p^s(t_1)$, denoted as $Seg_2$, are separately computed .
+ \item[3)]The intersection between $t_1$ and $t_2$ is determined by computing the overlap area of $Seg_1$ and $Seg_2$ .
 \end{itemize}
-
-\begin{figure}[t]
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=3.0in]{nonrobust}\\
-  \caption{The left edges of A and B (\emph{left}) are nearly but not exactly collinear.
-However, under usual float point arithmetic, they might be judged as collinear causing discontinuous edges in the final result (\emph{right}).}\label{fig:precision}
-\end{figure}
 
@@
 \caption{We denote the signed distance from point $X$ to plane $S_2$ as $d_X$.
-All the four conditions of intersection between $F_1$ and $S_2$ (denoted as $Seg_1$) are:  (a) $d_A\cdot d_C<0$, $d_B\cdot d_C<0$; (b) $d_A=0$, $d_B=0$, $d_C\neq 0$; (c) $d_A=0$, $d_B\cdot d_C<0$; (d) $d_A=0$, $d_B\cdot d_C>0$.
-End points of $Seg_1$ are intersections between $S_2$ and related edge lines of $F_1$ (bold edges).}
+All the four conditions of intersection between $t_1$ and $S_2$ (denoted as $Seg_1$) are:  (a) $d_A\cdot d_C<0$, $d_B\cdot d_C<0$; (b) $d_A=0$, $d_B=0$, $d_C\neq 0$; (c) $d_A=0$, $d_B\cdot d_C<0$; (d) $d_A=0$, $d_B\cdot d_C>0$.
+End points of $Seg_1$ are intersections between $S_2$ and related edge lines of $t_1$ (bold edges).}
 \label{fig:isect}
@@
 \begin{itemize}[leftmargin=0.45cm]
-\item[1)] The basic routine of the first step is given two faces $f_1$ and $f_2$, computing the orientation of the supporting plane (denoted as $p(f_1)\colon(a, b, c, d)$) of a face with respect to a certain vertex (denoted as  $v_i(f_2)\colon(x, y, z)$) of the other face.
+\item[1)] The basic routine of the first step is given two faces $t_1$ and $t_2$, computing the orientation of the supporting plane (denoted as $p(t_1)\colon(a, b, c, d)$) of a face with respect to a certain vertex (denoted as  $v_i(t_2)\colon(x, y, z)$) of the other face.
 That is to compute:
@@
 As illustrated in Fig.
-\ref{fig:isect}, $Seg_1$ are the intersection between $f_1$ and $p_s(f_2)$.
-Because the edge $e_i(f_1)$ can be represented as $(p^s( f_1), p^b_i(f_1))$, the end points of $Seg_1$ can be represented in the form of $(p^s( f_1), p^s(f_2), p^b_i(f_1))$.
+\ref{fig:isect}, $Seg_1$ are the intersection between $t_1$ and $p_s(t_2)$.
+Because the edge $e_i(t_1)$ can be represented as $(p^s( t_1), p^b_i(t_1))$, the end points of $Seg_1$ can be represented in the form of $(p^s( t_1), p^s(t_2), p^b_i(t_1))$.
 In Fig.
-\ref{fig:isect}, we list all intersection situations between $f_1$ and $p_s(f_2)$, and the corresponding bounding plane $p^b_i(f_1)$ in each situation.
+\ref{fig:isect}, we list all intersection situations between $t_1$ and $p_s(t_2)$, and the corresponding bounding plane $p^b_i(t_1)$ in each situation.
 Coplanar conditions will be discussed later in section \ref{sec:degenerate}.
- \item[3)] The intersection between $f_1$ and $f_2$ is the overlap area of $Seg_1$ and $Seg_2$.
+ \item[3)] The intersection between $t_1$ and $t_2$ is the overlap area of $Seg_1$ and $Seg_2$.
 It can be easily computed by comparing the end points of $Seg_1$ and $Seg_2$ along $l$ (Fig.
-\ref{fig_projection}), where $l$ is the intersection between $p_s(f_1)$ and $p_s(f_2)$.
+\ref{fig_projection}), where $l$ is the intersection between $p_s(t_1)$ and $p_s(t_2)$.
 Because end points are all represented using plane triples, we can use the two-line-one-plane comparison discussed in section \ref{sec:substrates} to perform the comparison.
@@
 
-To illustrate, assume two triangle faces $f_1$ and $f_2$, from primitive $P_1$ and $P_2$, intersect at line segment ${\boldsymbol{\Gamma}}$.
-Note that there are two versions of ${\boldsymbol{\Gamma}}$ for each of the two faces respectively, denoted as ${\boldsymbol{\Gamma}}(f_1)$ and ${\boldsymbol{\Gamma}}(f_2)$.
-For ${\boldsymbol{\Gamma}}(f_1)$, $v_b$ and $v_e$ are the two end points of ${\boldsymbol{\Gamma}}$ and $f=f_1$.
-The representation plane $p$ is $p^s(f_2)$.
-Note that $p^s(f_2)$ must not be coplanar with $f_1$.
-The intersection context $C=f_2$ in most cases.
-It means that, in primitive $P_2$, ${\boldsymbol{\Gamma}}(f_1)$ lies on the face $f_2$.
+To illustrate, assume two triangle faces $t_1$ and $t_2$, from primitive $P_1$ and $P_2$, intersect at line segment ${\boldsymbol{\Gamma}}$.
+Note that there are two versions of ${\boldsymbol{\Gamma}}$ for each of the two faces respectively, denoted as ${\boldsymbol{\Gamma}}(t_1)$ and ${\boldsymbol{\Gamma}}(t_2)$.
+For ${\boldsymbol{\Gamma}}(t_1)$, $v_b$ and $v_e$ are the two end points of ${\boldsymbol{\Gamma}}$ and $f=t_1$.
+The representation plane $p$ is $p^s(t_2)$.
+Note that $p^s(t_2)$ must not be coplanar with $t_1$.
+The intersection context $C=t_2$ in most cases.
+It means that, in primitive $P_2$, ${\boldsymbol{\Gamma}}(t_1)$ lies on the face $t_2$.
 However, sometimes, intersection may lie on the edge, instead of face,  of other primitive.
 In that case,  the intersection context is an edge, and we discuss such degenerate case in the next section.
-The situation of ${\boldsymbol{\Gamma}}(f_2)$ is similar we omit the discussion here.
+The situation of ${\boldsymbol{\Gamma}}(t_2)$ is similar we omit the discussion here.
 
@@
 
-Assume there are two faces $f_1$ and $f_2$ from primitive $P_1$ and $P_2$ respectively.
-These two faces intersect on line segment ${\boldsymbol{\Gamma}}$, which has two versions of IR ${\boldsymbol{\Gamma}}(f_1)$ and ${\boldsymbol{\Gamma}}(f_2)$ for the two faces respectively.
-Without loss of generality, we only discuss the configuration of ${\boldsymbol{\Gamma}}(f_1)$, as ${\boldsymbol{\Gamma}}(f_2)$ can be figured out similarly.
+Assume there are two faces $t_1$ and $t_2$ from primitive $P_1$ and $P_2$ respectively.
+These two faces intersect on line segment ${\boldsymbol{\Gamma}}$, which has two versions of IR ${\boldsymbol{\Gamma}}(t_1)$ and ${\boldsymbol{\Gamma}}(t_2)$ for the two faces respectively.
+Without loss of generality, we only discuss the configuration of ${\boldsymbol{\Gamma}}(t_1)$, as ${\boldsymbol{\Gamma}}(t_2)$ can be figured out similarly.
 We classify all degenerate cases into three categories by the dimension of intersection.
@@
 There are generally two kinds of edge intersections.
-If ${\boldsymbol{\Gamma}}$ lies on the edge of $f_1$ or $f_2$, but inside of the face of the other one, then we called it as edge-face intersections.
-If ${\boldsymbol{\Gamma}}$ lies on the edges of both $f_1$ and $f_2$, we call it as edge-edge intersections.
-When there is edge-face intersection, we treat it as the intersection of three faces $f_1$, $f_2$ and $f_1^\star$ (or $f_2^\star$).
-When there is edge-edge intersection, we treat it as the intersection of four faces $f_1$, $f_2$, $f_1^\star$ and $f_2^\star$.
-The $f_1^\star$ (or $f_2^\star$), known as \emph{companion face},  is the neighboring face which shares the intersection edge with $f_1$ (or $f_2$).
-In this way, we avoid repetitive insertion of the same edge intersections, since the companion faces share the same intersection with its neighborhood $f_1$ or $f_2$.
+If ${\boldsymbol{\Gamma}}$ lies on the edge of $t_1$ or $t_2$, but inside of the face of the other one, then we called it as edge-face intersections.
+If ${\boldsymbol{\Gamma}}$ lies on the edges of both $t_1$ and $t_2$, we call it as edge-edge intersections.
+When there is edge-face intersection, we treat it as the intersection of three faces $t_1$, $t_2$ and $t_1^\star$ (or $t_2^\star$).
+When there is edge-edge intersection, we treat it as the intersection of four faces $t_1$, $t_2$, $t_1^\star$ and $t_2^\star$.
+The $t_1^\star$ (or $t_2^\star$), known as \emph{companion face},  is the neighboring face which shares the intersection edge with $t_1$ (or $t_2$).
+In this way, we avoid repetitive insertion of the same edge intersections, since the companion faces share the same intersection with its neighborhood $t_1$ or $t_2$.
 
@@
 We first consider edge-face intersection.
-If $f_1$ and $f_1^\star$ are on the same side of $f_2$, it is cross condition.
+If $t_1$ and $t_1^\star$ are on the same side of $t_2$, it is cross condition.
 If they are on the same side, it is invalid condition.
-If $f_1^\star$ is coplanar with $f_2$, it is coplanar condition.
+If $t_1^\star$ is coplanar with $t_2$, it is coplanar condition.
 Consider the cross and coplanar condition.
-For $f_2$, the IR is the same as the common situation, except that the intersection context is an edge.
-For $f_1$ and $f_1^\star$, they have to share the intersection line segment, while the intersection context is $f_2$.
+For $t_2$, the IR is the same as the common situation, except that the intersection context is an edge.
+For $t_1$ and $t_1^\star$, they have to share the intersection line segment, while the intersection context is $t_2$.
 However, when there is invalid condition, we should not record the intersection for the similar reasons of isolated point intersection (section \ref{sec:ipoint}).
@@
 The handling of edge-edge intersection is similar with edge-face intersection.
-The difference is that the intersection contexts are edges for both $f_1$ and $f_2$.
+The difference is that the intersection contexts are edges for both $t_1$ and $t_2$.
 We still can classify edge-edge intersection into three subclasses by the relative location of companion faces.
-There is one difference, though, that in edge-face intersection, we compute on which side of $f_2$ the companion face $f_1^\star$ lies, and compare with $f_1$.
-However, in edge-edge intersection, we have to consider the space split by both $f_2$ and $f_2^\star$ instead of only $f_2$.
+There is one difference, though, that in edge-face intersection, we compute on which side of $t_2$ the companion face $t_1^\star$ lies, and compare with $t_1$.
+However, in edge-edge intersection, we have to consider the space split by both $t_2$ and $t_2^\star$ instead of only $t_2$.
 Similar with edge-face intersections, we record the intersection of cross and coplanar condition, while omit the invalid condition for concision and also topology correctness.

### 2016-09-02 summary.tex
now

@@
 Our method is designed for boolean operations on arbitrary number of triangle meshes.
-Input mesh primitives are required to be watertight and not self-intersected, with manifold surface, represented by wide-used halfedges \cite{mcguire2000half}.
+Input mesh primitives are required to be watertight and not self-intersecting, with manifold surface, represented by wide-used halfedges \cite{mcguire2000half}.
 Despite of so many constraints, our method is not sensitive to topology deficiencies and works well if deficiencies are not near the intersection areas between meshes.
@@
 \ref{fig:isect}, we list all intersection situations between $t_1$ and $p_s(t_2)$, and the corresponding bounding plane $p^b_i(t_1)$ in each situation.
-Coplanar conditions will be discussed later in section \ref{sec:degenerate}.
+The conditions that $t_1$ is inside the plane $p_s(t_2)$ (coplanar cases) will be discussed later in section \ref{sec:degenerate}.
  \item[3)] The intersection between $t_1$ and $t_2$ is the overlap area of $Seg_1$ and $Seg_2$.
@@
 For each face, we detect irregular intersections by intersection test between pairs of intersections.
-Because primitive meshes are not self-intersected, we only check intersections between intersections made by different meshes.
+Because primitive meshes are not self-intersecting, we only check intersections between intersections made by different meshes.
 Face intersecting only one other mesh do not need refinement, since they do not have such intersection pairs.

### 2016-09-22 summary.tex
........

@@
 \usepackage{color}
-
+\usepackage{bm}
 % correct bad hyphenation here
@@
 This is because subdividing normal cells benefits only the ray-casting point-in-polyhedron test  \cite{frisken2002simple}, which seldom uses in our method.
-This simplification can bring large performance advantage, especially for those cases where intersections between primitives are not complex and limited in small regions (e.g.
+This simplification can save much computing time, especially when intersections between primitives are not complex and located in small regions (e.g.
 Fig.
@@
 We also introduce some other notations before starting our discussion.
-A plane $p_x$ can be represented by plane coefficients $(a_x, b_x, c_x, d_x)$.
-The normal of $p_x$ is denoted as $\vec{n}_x$.
+A plane $\bm{p}$ can be represented by plane coefficients $(a, b, c, d)$.
+The normal of $p$ is denoted as $\bm{n}=(a,b,c)$.
 A line $l$ can be represented by intersection of two planes $(p_m, p_n)$, or in short, $l\colon(p_m, p_n)$.
-The positive direction of the line $\vec{l}$ is defined by $\vec{n}_a \times \vec{n}_b$.
-A point $v$ is represented by non-trivial plane triples $(p_a, p_b, p_c)$, or in short, $v\colon(p_a, p_b, p_c)$.
+The positive direction of the line $\bm{l}$ is defined by $\bm{n}_a\times\bm{n}_b$.
+A point $v$ is represented by non-trivial plane triples $(p_m, p_n, p_l)$, or in short, $v\colon(p_m, p_n, p_l)$.
 
@@
 
-Efficient and exact conversion from the vertex-based representation to plane-based representation is described in detail in \cite{campen2010exact}.
-If the input vertices precision is $L$, the maximum precision $P$ required to represent the plane coefficients is:
-\begin{equation}
-\label{eq:precision}
-P = (L-1)+2(K-1)+3+1,
-\end{equation}
-where $K$  is the maximum bits to represent edge vector components.
-If the plane coefficient has $M$ bit precision, $M$ have to greater than or equal to $P$ for exact conversion.
-However, different from \cite{campen2010exact}, we choose to enforce the criterion to $M \ge P+1$.
-This enforcement of criterion allow us to perform predicates of orientation of plane $p_x$ with respect to a point $v$ with exact $L$-bit coordinates by simply compute the sign ${\vec{n}_x}\cdot{v} + d_x$ within $M$-bit precision, instead of first converting $v$ into its plane-based representation and then computing the sign of 4x4 determinant.
-This can save much computation time by avoid unnecessary conversion for intersection computation.
+We use Campen et al.'s method \cite{campen2010exact} for efficient and exact conversion from the vertex-based representation to plane-based representation.
+Given the input vertex coordinates represented by $L$ bits including sign, the precisions of the four plane coefficients required for exact conversion are $L_a, L_b, L_c, L_d$, where $L_a=L_b=L_c=2(K-1)+1+1$ and $L_d=(L_a-1)+(L-1)+2+1$.
+Here $K$ is the maximum bits to represent edge vector components.
+If each coefficient is stored using $M$ bits, the constraint is $M \ge L_d$.
+In addition, different from Campen et al.'s method, we further enforce the constraint to $M \ge L_d+1$.
+In this way, given a $L$-bit vertex $\bm{v}$, we can compute predicate of orientation of plane with respect to the vertex by simply compute the sign $\bm{n}\cdot\bm{v} + d$ within $M$-bit precision.
+This allows fast predicates especially for early rejection in collision detection ($\S$ \ref{section:isect}).
 
 Let $\delta = 2^{K-L-1}$ be the relative length (in max-norm) of the longest edge in the mesh (relative to the bounding box).
-If we use IEEE 754 double precision ($M=53$) and assume $\delta \le 2^{-5.5} \approx 0.22$, the maximum input precision $L$ can reach to 20, which is enough for most application.
+If we use IEEE 754 double float point number ($M=53$) and assume $\delta \le 2^{-5.5} \approx 0.22$, the maximum input precision $L$ can reach to 20, which is enough for most application (note that IEEE 754 single float point number has only 24-bit precision).
 
@@
 \label{sec:substrates}
-Our method rigorously follows the paradigm of plane-based geometry.
-Predicates are all computed using planes as input.
-These predicates include checking coincidence and co-orientation of planes, orientation of a plane with respect to a point, and whether three planes intersect in a unique point, etc.
-In the following, we only focus on two specific predicates.
-Other substrates may refer to \cite{bernstein2009fast}.
-
+Plane-based geometry predicates include checking coincidence and co-orientation of planes, orientation of a plane with respect to a point, and whether three planes intersect in a unique point, etc.
+Most of them are well-discussed in previous work \cite{bernstein2009fast,banerjee1996topologically}.
+In the following, we focus on two advanced plane-based predicates---\emph{point ordering on line} and \emph{circular ordering of line}.
+
+\vspace{0.5em}
+\noindent \textbf{Point ordering on line}~~~~
 Given an arbitrary line $l\colon(p_m, p_n)$ with two points $v_p$ and $v_q$ on $l$, the two points can be represented by plane triples $(p_m, p_n, p_p)$ and $(p_m, p_n, p_q)$, sharing the same first two components.
@@
 
-Another predicates is called \emph{two-line-one-plane comparison} (Fig.
-\ref{fig:substrates}).
-Given two coplanar lines $l_a\colon(p_0, p_a)$ and $l_b\colon(p_0, p_b)$, we want decide whether the cross product of $\vec{l}_a$ and $\vec{l}_b$ has the same orientation as $\vec{n}_0$ (the normal of $p_0$).
+\vspace{0.5em}
+\noindent \textbf{Circular ordering of line}~~~~
+As in Fig.
+\ref{fig:substrates}, Given two coplanar but no parallel lines $l_a\colon(p_0, p_a)$ and $l_b\colon(p_0, p_b)$, they intersect on point $\bm{v}\colon(p_0,p_a,p_b)$.we want decide whether the cross product of $\vec{l}_a$ and $\vec{l}_b$ has the same orientation as $\vec{n}_0$ (the normal of $p_0$).
 Direct solution requires to explicitly compute the vector of $l_a$ and $l_b$ and then decide the sign of $\vec{n}_0 \cdot (\vec{l}_a \times \vec{l}_b)$.

### 2016-09-23 summary.tex
9.23

@@
 
-We use Campen et al.'s method \cite{campen2010exact} for efficient and exact conversion from the vertex-based representation to plane-based representation.
-Given the input vertex coordinates represented by $L$ bits including sign, the precisions of the four plane coefficients required for exact conversion are $L_a, L_b, L_c, L_d$, where $L_a=L_b=L_c=2(K-1)+1+1$ and $L_d=(L_a-1)+(L-1)+2+1$.
-Here $K$ is the maximum bits to represent edge vector components.
-If each coefficient is stored using $M$ bits, the constraint is $M \ge L_d$.
-In addition, different from Campen et al.'s method, we further enforce the constraint to $M \ge L_d+1$.
-In this way, given a $L$-bit vertex $\bm{v}$, we can compute predicate of orientation of plane with respect to the vertex by simply compute the sign $\bm{n}\cdot\bm{v} + d$ within $M$-bit precision.
-This allows fast predicates especially for early rejection in collision detection ($\S$ \ref{section:isect}).
+We use Campen et al.'s method \cite{campen2010exact} for exact conversion of triangles (represented by three vertices) from vertex-based representation to plane-based representation.
+Given that the input vertex coordinate has $L$-bit precision including sign, the precisions of the four plane coefficients are $L_a, L_b, L_c, L_d$, which have to meet the following requirements:
+\begin{equation}
+\begin{split}
+&L_a=L_b=L_c\ge 2(K-1)+1+1,\\
+&L_d\ge(L_a-1)+(L-1)+2+1.
+\end{split}
+\end{equation}
+Here $K$ is the maximum bits required to represent edge vector components in input meshes.
+If we use $M$ bits to store each plane coefficient, basically $M$ has to be greater than $L_d$.
+In our implementation, we actually use a more strong constraint $M \ge L_d+1$.
+Under this constraint, given a $L$-bit vertex $\bm{v}$, we can compute the orientation of plane with respect to $\bm{v}$ by the sign $\bm{n}\cdot\bm{v} + d$, which can be exactly computed using common float point arithmetic with limited $M$-bit precision.
+It allows very fast plane orientation predicates which benefits much the early rejection in our intersection computation ($\S$ \ref{section:isect}).
 
 Let $\delta = 2^{K-L-1}$ be the relative length (in max-norm) of the longest edge in the mesh (relative to the bounding box).
-If we use IEEE 754 double float point number ($M=53$) and assume $\delta \le 2^{-5.5} \approx 0.22$, the maximum input precision $L$ can reach to 20, which is enough for most application (note that IEEE 754 single float point number has only 24-bit precision).
+If we use IEEE 754 double float point number ($M=53$) and assume $\delta \le 2^{-5.5} \approx 0.022$, the maximum input precision $L$ can reach to 20, which is enough for most application (for standard IEEE 754 single float point number, the precision is 24-bit).
 
@@
 Most of them are well-discussed in previous work \cite{bernstein2009fast,banerjee1996topologically}.
-In the following, we focus on two advanced plane-based predicates---\emph{point ordering on line} and \emph{circular ordering of line}.
+In the following, we focus on two advanced plane-based predicates---\emph{point ordering on line} and \emph{circular ordering of line}, which are important building blocks of our method.
 
@@
 \noindent \textbf{Point ordering on line}~~~~
-Given an arbitrary line $l\colon(p_m, p_n)$ with two points $v_p$ and $v_q$ on $l$, the two points can be represented by plane triples $(p_m, p_n, p_p)$ and $(p_m, p_n, p_q)$, sharing the same first two components.
-We want to determine if $v_q$ is in positive side of $v_p$ along $\vec{l}$.
-We call this predicate as \emph{two-point-one-line comparison} (Fig.
+Given an arbitrary line $\bm{l}\colon(p_m, p_n)$ with two points $\bm{v}_1\colon(\bm{p}_1^0\cap\bm{p}_1^1\cap\bm{p}_1^2)$ and $\bm{v}_2\colon(\bm{p}_2^0\cap\bm{p}_2^1\cap\bm{p}_2^2)$ on it, we need to determine the linear order of the two points along $\bm{l}$ (Fig.
 \ref{fig:twopointoneline}).
-This problem can be converted to the problem of orientation of a plane $p_p$ with respect to a point $v_q$, except that there is an extra request---we have to guarantee $\vec{l}$ and $\vec{n}_p$ have the same orientation.
-If not, we negate the normal of $p_p$, and the implicit coordinate of  $v_p\colon(p_m, p_n, p_p)$ remains unchanged.
+To solve this problem, we choose one plane not parallel with $\bm{l}$ from the plane representation of each point.
+Then we convert this problem into linear order of planes and solve it using the same technique as Banerjee et al.
+\cite{banerjee1996topologically}.
+The chosen planes have to have the same orientation with $\bm{l}$ (the dot product between plane normal and $\bm{l}$ has to be positive) and unqualified planes are flipped.
 
@@
 \noindent \textbf{Circular ordering of line}~~~~
-As in Fig.
-\ref{fig:substrates}, Given two coplanar but no parallel lines $l_a\colon(p_0, p_a)$ and $l_b\colon(p_0, p_b)$, they intersect on point $\bm{v}\colon(p_0,p_a,p_b)$.we want decide whether the cross product of $\vec{l}_a$ and $\vec{l}_b$ has the same orientation as $\vec{n}_0$ (the normal of $p_0$).
+During face tessellation, we need to know the which edges are neighboring.
+While the relationships among original mesh edges are clear, the relations among newly introduced edges, which are generated by intersection between meshes, are totally unknown.
+Given two coplanar and not parallel lines $\bm{l}_a\colon(\bm{p}_0\cap\bm{p}_a)$ and $l_b\colon(p_0, p_b)$, they intersect on point $\bm{v}\colon(p_0,p_a,p_b)$.we want decide whether the cross product of $\vec{l}_a$ and $\vec{l}_b$ has the same orientation as $\vec{n}_0$ (the normal of $p_0$).
 Direct solution requires to explicitly compute the vector of $l_a$ and $l_b$ and then decide the sign of $\vec{n}_0 \cdot (\vec{l}_a \times \vec{l}_b)$.
-However, explicit representation of $\vec{l}_a$ and $\vec{l}_b$ cannot be represented by the float point number.
+However, explicit representation of $\vec{l}_a$ and $\vec{l}_b$ cannot be represented by the float point number.In Fig.
+\ref{fig:substrates},
 

### 2016-09-25 summary.tex
ss 4

@@
 
-\subsection{Linked Halfedge}
+\subsection{Intersection-Free Hybrid Mesh}
 
@@
 
-Using plane-based representation, each face of polyhedron is represented by a supporting plane $p^s$, where the face lies, and a list bounding planes $\{p^b_i \ \vert\  i = 1, 2, 3\}$, each has a corresponding edge (Fig.
+Using plane-based representation, each face $f$ of polyhedron is represented by a supporting plane $\bm{p}_{f,s}$, where the face lies, and a list bounding planes $\{\bm{p}_{f,b}^i \ \vert\  i = 1, 2, 3\}$, each has a corresponding edge (Fig.
 \ref{fig:p-reps}).
-Edge line is represented by intersection of $p^s$ and the related $p^b_i$.
-Corner vertex is the intersection of $p^s$ and two consecutive bounding planes $p^b_i$ and $p^b_{i+1}$.
-
-We also introduce some other notations before starting our discussion.
-A plane $\bm{p}$ can be represented by plane coefficients $(a, b, c, d)$.
-The normal of $p$ is denoted as $\bm{n}=(a,b,c)$.
-A line $l$ can be represented by intersection of two planes $(p_m, p_n)$, or in short, $l\colon(p_m, p_n)$.
-The positive direction of the line $\bm{l}$ is defined by $\bm{n}_a\times\bm{n}_b$.
-A point $v$ is represented by non-trivial plane triples $(p_m, p_n, p_l)$, or in short, $v\colon(p_m, p_n, p_l)$.
+Edge line is represented by intersection of $\bm{p}_{f,s}$ and the related $\bm{p}_{f,b}^i$.
+Corner vertex is the intersection of $\bm{p}_{f,s}$ and two consecutive bounding planes $\bm{p}_{f,b}^i$ and $\bm{p}_{f,b}^{i+1}$.
+
+We also introduce some commonly used notations for better presentation in the rest of paper.
+A plane $\bm{p}$ can be represented by four scalar coefficients $(a, b, c, d)$.
+The normal of $\bm{p}$ is denoted as $\bm{n}(\bm{p})$.
+A line $\bm{l}$ can be represented by intersection of two planes $(\bm{p}_l^0 \cap \bm{p}_l^1)$, or in short, $\bm{l}\colon(\bm{p}_l^0 \cap \bm{p}_l^1)$.
+The positive direction of the line $\bm{l}$ is defined by $\bm{n}(\bm{p}_l^0) \times \bm{n}(\bm{p}_l^1)$.
+A point $\bm{v}$ can be represented by non-trivial plane triples $(\bm{p}_v^0 \cap \bm{p}_v^1 \cap \bm{p}_v^2)$, or in short, $\bm{v}\colon(\bm{p}_v^0 \cap \bm{p}_v^1 \cap \bm{p}_v^2)$.
 
@@
 \vspace{0.5em}
-\noindent \textbf{Point ordering on line}~~~~
-Given an arbitrary line $\bm{l}\colon(p_m, p_n)$ with two points $\bm{v}_1\colon(\bm{p}_1^0\cap\bm{p}_1^1\cap\bm{p}_1^2)$ and $\bm{v}_2\colon(\bm{p}_2^0\cap\bm{p}_2^1\cap\bm{p}_2^2)$ on it, we need to determine the linear order of the two points along $\bm{l}$ (Fig.
+\noindent \textbf{Linear ordering on points}~~~~
+Given an arbitrary line $\bm{l}$ with two points $\bm{v}_1\colon(\bm{p}_1^0\cap\bm{p}_1^1\cap\bm{p}_1^2)$ and $\bm{v}_2\colon(\bm{p}_2^0\cap\bm{p}_2^1\cap\bm{p}_2^2)$ on it, we need to determine the linear order of the two points along $\bm{l}$ (Fig.
 \ref{fig:twopointoneline}).
@@
 \cite{banerjee1996topologically}.
-The chosen planes have to have the same orientation with $\bm{l}$ (the dot product between plane normal and $\bm{l}$ has to be positive) and unqualified planes are flipped.
+The chosen planes should have the same orientation with $\bm{l}$ (the dot product between plane normal and $\bm{l}$ has to be positive) and unqualified planes have to be flipped.
 
 \vspace{0.5em}
-\noindent \textbf{Circular ordering of line}~~~~
-During face tessellation, we need to know the which edges are neighboring.
-While the relationships among original mesh edges are clear, the relations among newly introduced edges, which are generated by intersection between meshes, are totally unknown.
-Given two coplanar and not parallel lines $\bm{l}_a\colon(\bm{p}_0\cap\bm{p}_a)$ and $l_b\colon(p_0, p_b)$, they intersect on point $\bm{v}\colon(p_0,p_a,p_b)$.we want decide whether the cross product of $\vec{l}_a$ and $\vec{l}_b$ has the same orientation as $\vec{n}_0$ (the normal of $p_0$).
-Direct solution requires to explicitly compute the vector of $l_a$ and $l_b$ and then decide the sign of $\vec{n}_0 \cdot (\vec{l}_a \times \vec{l}_b)$.
-However, explicit representation of $\vec{l}_a$ and $\vec{l}_b$ cannot be represented by the float point number.In Fig.
-\ref{fig:substrates},
-
-To solve this, we decompose the normal vectors of $p_a$ and $p_b$ by the normal of $p_0$: $\vec{n}_a = \vec{n}^\parallel_a + \vec{n}^\perp_a$ and $\vec{n}_b = \vec{n}^\parallel_b + \vec{n}^\perp_b$.
-Here superscript `$\parallel$` means the vector is in the plane $p_0$ and `$\perp$` means it is orthogonal to $p_0$.
-Then $\vec{n}_a \times \vec{n}_b = \vec{n}^\parallel_a \times \vec{n}^\parallel_b + \vec{n}^\perp_a \times \vec{n}^\parallel_b + \vec{n}^\parallel_a \times \vec{n}^\perp_b + \vec{n}^\perp_a \times \vec{n}^\perp_b$.
-As we know $\vec{n}^\perp_a$ and $\vec{n}^\perp_b$ is parallel, $\vec{n}^\perp_a \times \vec{n}^\perp_b = \textbf{0}$.
-Now, we evaluate the expression $\vec{n}_0 \cdot (\vec{n}_a \times \vec{n}_b)$.
-Since $\vec{n}_s$ is orthogonal to both $\vec{n}^\perp_a \times \vec{n}^\parallel_b $ and $\vec{n}^\parallel_a \times \vec{n}^\perp_b $, we deduce $\vec{n}_0 \cdot (\vec{n}_a \times \vec{n}_b) = \vec{n}_0 \cdot (\vec{n}^\parallel_a \times \vec{n}^\parallel_b)$.
-Here we make an essential observation that $\vec{n}^\parallel_a \times \vec{n}^\parallel_b$ has the same direction as $\vec{l}_a \times \vec{l}_b$, that is:
+\noindent \textbf{Circular ordering of lines}~~~~
+During face tessellation, we need to know the which edges are neighboring (Fig.
+\ref{fig:circularorder}), that is, circular ordering of directed lines around a vertex.
+Lines can be sorted in a divide-and-conquer way based on the relative order of each pair of lines.
+Therefore, this problem is converted to that given two coplanar lines $\bm{l}_a\colon(\bm{p}_a^0\cap\bm{p}_a^1)$ and $\bm{l}_b\colon(\bm{p}_b^0\cap\bm{p}_b^1)$ with their intersection point $\bm{v}_{ab}$, compute the circular order of the two lines.
+Supposing the common plane is $\bm{p}_s$, we can compute the order by the sign of $\sin{\theta_{ab}}$, where $\theta_{ab}\in(-\pi,\pi)$ is the angle from $\bm{l}_a$ to $\bm{l}_b$ under the top view of $\bm{p}_s$.
+And the sign of sine is the same as triple product $\bm{n}(\bm{p}_s) \cdot (\bm{l}_a\times\bm{l}_b)$,
+where $\bm{n}$ means the normal direction. However, explicit computing this equation is complicated because both $\bm{l}_a$ and $\bm{l}_b$ are implicitly represented by intersection of planes.
+
+We develop an easier way that requiring no explicit computation of $\bm{l}_a$ and $\bm{l}_b$.
+We orthogonally decompose $\bm{n}(\bm{p}_a)$ and $\bm{n}(\bm{p}_b)$ along the normal the common plane $\bm{p}_s$:
 \begin{equation}
 \begin{split}
-\label{eq:cosine}
-sign(\vec{n}_0 \cdot (\vec{n}_a \times \vec{n}_b)) &= sign(\vec{n}_0 \cdot (\vec{n}^\parallel_a \times \vec{n}^\parallel_b)) \\
-&=  sign(\vec{n}_0 \cdot (\vec{l}_a \times \vec{l}_b)),
+&\bm{n}(\bm{p}_a)= \bm{n}^\parallel(\bm{p}_a) + \bm{n}^\perp(\bm{p}_a)\\
+&\bm{n}(\bm{p}_b)= \bm{n}^\parallel(\bm{p}_b) + \bm{n}^\perp(\bm{p}_b)
 \end{split}
 \end{equation}
-which means we do not need to explicitly compute $\vec{l}_a$ or $\vec{l}_b$. Instead, we only have to evaluate the left expression of equation \ref{eq:cosine}, which is much easier to compute.
-
+Here superscript `$\parallel$` means the projection on $\bm{p}_s$ and `$\perp$` means orthogonal to $\bm{p}_s$.
+As we know $\bm{n}^\perp(\bm{p}_a)$ and $\bm{n}^\perp(\bm{p}_b)$ are both parallel to $\bm{n}(\bm{p}_s)$, we get:
+\begin{equation}
+\label{eq:circ1}
+\bm{n}(\bm{p}_s) \cdot (\bm{n}(\bm{p}_a) \times \bm{n}(\bm{p}_b)) = \bm{n}(\bm{p}_s) \cdot (\bm{n}^\parallel(\bm{p}_a) \times \bm{n}^\parallel(\bm{p}_b)).
+\end{equation}
+By simple geometry reasoning, we find that the angle between $\bm{n}^\parallel(\bm{p}_a)$ and $\bm{n}^\parallel(\bm{p}_b)$ is exactly $\theta_{ab}$.
+So the sign of the right side of equation \ref{eq:circ1} is exactly the sign of $\sin{\theta_{ab}}$.
+It means we have the following nice conclusion:
+\begin{equation}
+\label{eq:circ2}
+sign(\sin{\theta_{ab}})=  sign(\bm{n}(\bm{p}_s)\cdot(\bm{n}(\bm{p}_a) \times \bm{n}(\bm{p}_b)))
+\end{equation}
+
+Since all the three vectors are already explicitly represented, we only have to evaluate the sign of an 3x3 matrix and avoid complicated high precision float-point arithmetic.
 \begin{figure}
@@
 \centering
-\includegraphics[width=2.5in]{substrates}
+\includegraphics[width=2.5in]{circularorder}
 \caption{The configuration of two-line-one-plane comparison.
@@
 We want to compute $sign(\vec{n}_0 \cdot (\vec{l}_a \times \vec{l}_b))$.}
-\label{fig:substrates}
+\label{fig:circularorder}
 \end{figure}

### 2016-09-27 summary.tex
9.27

@@
 The robustness of our method is based on the observations by Sugihara and Iri \cite{sugihara1990solid} that boolean operations can be performed requiring geometry constructions if representations are based on planes and not vertices.
-This idea of using plane-based representation has been developed by Berstein and Fussell \cite{bernstein2009fast} by combining it with binary search partition (BSP) techniques \cite{naylor1990merging,thibault1987set}.
+This idea of using plane-based representation (P-rep) has been developed by Berstein and Fussell \cite{bernstein2009fast} by combining it with binary search partition (BSP) techniques \cite{naylor1990merging,thibault1987set}.
 Later, Campen et.
@@
 Despite of that, Campen et.
-al.'s method still suffers from performance problem because of the complex conversions among B-reps, plane-based representations and BSP representations.
+al.'s method still suffers from performance problem because of the complex conversions among B-reps, P-reps and BSP representations.
 Also, the incoherence between BSP representation, where boolean operations actually happens, and B-reps, which are input and output meshes, requires extra steps to connect the reconstructed intersection areas with the untouched meshes, leading to extra computation burden and complex topology.
@@
 But we can save much computation time by avoiding repetitive computation.
-The major difficulty of applying plane-based representation on halfedge is by the incoherence between the two representations.
+The major difficulty of applying P-rep on halfedge is by the incoherence between the two representations.
 Halfedge is a vertex-based representation.
-Many geometry operations (e.g., coordinates projection and compute the barycenter coordinate of triangle) available on halfedge can be very complex and thus inefficient under plane-based representation.
-On the other hand, we have to compute under plane-based representation for exactness and robustness.
+Many geometry operations (e.g., coordinates projection and compute the barycenter coordinate of triangle) available on halfedge can be very complex and thus inefficient under P-rep.
+On the other hand, we have to compute under P-rep for exactness and robustness.
 Therefore, we manage to limit our computation of boolean operations to several basic plane-based predicates.
@@
 
-The concept of plane-based representation of polygonal meshes was first described by Sugihara and Iri \cite{sugihara1990solid}.
+The concept of P-rep of polygonal meshes was first described by Sugihara and Iri \cite{sugihara1990solid}.
 Such representation provides important advantage that for boolean operations, no new primary geometry information has to be constructed to obtain the result polyhedron---it is composed of a subset of the planes of the input polyhedra.
-Berstein and Fussell \cite{bernstein2009fast} combined the plane-based representation with binary space partitioning (BSP) \cite{thibault1987set,naylor1990merging} to develop an unconditionally robust boolean operation method.
+Berstein and Fussell \cite{bernstein2009fast} combined the P-rep with binary space partitioning (BSP) \cite{thibault1987set,naylor1990merging} to develop an unconditionally robust boolean operation method.
 Compared to volume-grid based methods, their BSP-based method increases mesh complexity more moderately and the input topology can be reconstructed better.
-However, it requires conversions between input data structures and plane-based representation which are inefficient from both storage and time views.
+However, it requires conversions between input data structures and P-rep which are inefficient from both storage and time views.
 Also, the merge of two BSP trees is an $O(mn)$ time complexity process, where $m$ and $n$ are the size of the trees.
@@
 However, as we discussed in section \ref{sec:pbrelated}, BSP structure does not support geometry connectivity query in nature, and we do not want fussy conversions between different representations.
-Therefore, we use halfedge instead as our major data structure and embed plane-based representation into it.
+Therefore, we use halfedge instead as our major data structure and embed P-rep into it.
 
@@
 The vertex coordinates in halfedge are usually represented by float point number, which cannot exactly represent the newly introduced intersection points.
-Therefore, we utilize plane-based representation to avoid computing new coordinates.
+Therefore, we utilize P-rep to avoid computing new coordinates.
 In addition, we detect all coincident vertices among input meshes (including intersection vertices).
@@
 However, naive implementation of M\"{o}ller's algorithm always incurs robustness issues.
-To avoid an unexpected failure caused by numeric errors, we integrate plane-based representation of polyhedra into M\"{o}ller's algorithm.
+To avoid an unexpected failure caused by numeric errors, we integrate P-rep of polyhedra into M\"{o}ller's algorithm.
 All intersection vertices are represented using plane intersections to avoid geometry constructions.
@@
 In addition, as our intersection vertices are represented exactly by planes, implementation of CDT are complex and inefficient, as most CDT methods were not designed to handle planes and requires explicit coordinates.
-Therefore, we design a structure suited for plane-based representation, called \emph{Tess-graph}, to guide the tessellation of each single face, and develop a very fast but exact method to construct Linked Halfedges from Tess-graphs.
+Therefore, we design a structure suited for P-rep, called \emph{Tess-graph}, to guide the tessellation of each single face, and develop a very fast but exact method to construct Linked Halfedges from Tess-graphs.
 Details are shown in section \ref{sec:tessellation}.
@@
   \includegraphics[width=1.7in]{p-reps}\\
-  \caption{Plane-based representation of triangles. The yellow triangle is represented by three bounding planes (green) and the supporting plane where the triangle lies.}\label{fig:p-reps}
+  \caption{P-rep of triangles. The yellow triangle is represented by three bounding planes (green) and the supporting plane where the triangle lies.}\label{fig:p-reps}
 \end{figure}
@@
 As we discussed in Section \ref{sec:paradigm}, one of the problem in boolean operations under vertex-based representation is it inevitably introduces new vertices, whose coordinates cannot be exactly represented using fix-precision float-point number.
-On the other hand, if plane-based representation is used, no new geometry information needs to be constructed.
+On the other hand, if P-rep is used, no new geometry information needs to be constructed.
 Therefore, we can use only geometric decision predicates to perform boolean operations.
@@
 
-Using plane-based representation, each face $f$ of polyhedron is represented by a supporting plane $\bm{p}_{f,s}$, where the face lies, and a list bounding planes $\{\bm{p}_{f,b}^i \ \vert\  i = 1, 2, 3\}$, each has a corresponding edge (Fig.
-\ref{fig:p-reps}).
-Edge line is represented by intersection of $\bm{p}_{f,s}$ and the related $\bm{p}_{f,b}^i$.
-Corner vertex is the intersection of $\bm{p}_{f,s}$ and two consecutive bounding planes $\bm{p}_{f,b}^i$ and $\bm{p}_{f,b}^{i+1}$.
+As illustrated in Fig.
+\ref{fig:p-reps}, using P-rep, each face $f$ with $n$ edges is represented by a supporting plane $\bm{p}_{f,s}$, where the face lies, and a list bounding planes $\{\bm{p}_{f,b}^i \ \vert\  i = 0, 1,...,n-1\}$.
+Each edge line $\bm{e}_f^i$ is represented by intersection $\bm{p}_{f,s} \cap \bm{p}_{f,b}^i$.
+Corner vertex $\bm{v}_f^i$ is represented by intersection $\bm{p}_{f,s} \cap \bm{p}_{f,b}^i \cap \bm{p}_{f,b}^{{(i+1)}\bmod{n}}$.
 
 We also introduce some commonly used notations for better presentation in the rest of paper.
-A plane $\bm{p}$ can be represented by four scalar coefficients $(a, b, c, d)$.
-The normal of $\bm{p}$ is denoted as $\bm{n}(\bm{p})$.
+A plane $\bm{p}$ can be represented by four scalar coefficients $a(\bm{p}), b(\bm{p}), c(\bm{p}), d(\bm{p})$.
+The normal of $\bm{p}$ is denoted as $\bm{n}(\bm{p})$, which is a normalized vector consisting of the first three plane coefficients.
 A line $\bm{l}$ can be represented by intersection of two planes $(\bm{p}_l^0 \cap \bm{p}_l^1)$, or in short, $\bm{l}\colon(\bm{p}_l^0 \cap \bm{p}_l^1)$.
@@
 
-We use Campen et al.'s method \cite{campen2010exact} for exact conversion of triangles (represented by three vertices) from vertex-based representation to plane-based representation.
+We use Campen et al.'s method \cite{campen2010exact} for exact conversion of triangles (represented by three vertices) from vertex-based representation to P-rep.
 Given that the input vertex coordinate has $L$-bit precision including sign, the precisions of the four plane coefficients are $L_a, L_b, L_c, L_d$, which have to meet the following requirements:
@@
 In our implementation, we actually use a more strong constraint $M \ge L_d+1$.
-Under this constraint, given a $L$-bit vertex $\bm{v}$, we can compute the orientation of plane with respect to $\bm{v}$ by the sign $\bm{n}\cdot\bm{v} + d$, which can be exactly computed using common float point arithmetic with limited $M$-bit precision.
-It allows very fast plane orientation predicates which benefits much the early rejection in our intersection computation ($\S$ \ref{section:isect}).
+Under this constraint, given a $L$-bit vertex $\bm{v_i}$, we can compute the orientation of plane $p_j$ with respect to $\bm{v_i}$ by the sign $\bm{n}(\bm{p_j})\cdot\bm{v_i} + d(\bm{p_j})$, which can be exactly computed using common float point arithmetic with limited $M$-bit precision.
+It allows very fast plane orientation predicates which benefits much the early rejection in our intersection computation (\S \ref{section:isect}).
 
@@
 
-\section{Exact Intersection Detection}
+\section{Exact Intersection Computation}
 
 \label{section:isect}
-In this step, intersections between faces are computed through the triangle-triangle intersection test within each critical cell of octree.
-We adopt M\"{o}ller's intersection detection algorithm \cite{moller1997fast} on account of its efficiency and simplicity.
-However, because collision detection algorithms are often accompanied by non-robustness problems, a naive implementation may cause unpredictable results when there comes degenerate cases.
-Therefore, we integrate plane-based geometry representation into M\"{o}ller's algorithm to make it unconditionally robust and exact.
-In the following, we first make a quick review of M\"{o}ller's algorithm, then discuss the way to integrate plane-based geometry.
-At last, we talk about how to deal with degenerate case, such as intersecting on points and coplanar case.
-
-\subsection{Vertex-Based Method Review}
+In this step, intersections between faces are computed through triangle-triangle intersection test.
+We adopt M\"{o}ller's algorithm \cite{moller1997fast} on account of its efficiency and simplicity.
+However, a naive implementation of M\"{o}ller's algorithm may fail to produce correct results because of numerical errors.
+Therefore, we integrate plane-based geometry representation to make it unconditionally exact and robust.
+In the following, we first make a quick review of M\"{o}ller's algorithm, and then discuss the way to integrate plane-based geometry.
+After that, we talk about how to deal with degenerate cases.
+
+\subsection{M\"{o}ller's Vertex-Based Method}
 
@@
 
-M\"{o}ller's algorithm computes the intersection between two triangles $t_1$ and $t_2$ in three steps (Fig. \ref{fig_projection}).
+M\"{o}ller's algorithm computes the intersection between two triangles $t_1$ and $t_2$ in three steps as shown in Fig. \ref{fig_projection}:
 \begin{itemize}[leftmargin=0.45cm]
-\item[1)] An early rejection is performed by testing whether $t_1$ intersects $p^s(t_2)$, the supporting plane of $t_2$.
-This is a necessary condition of intersection between $t_1$ and $t_2$.
-If this test is passed, then the same is performed for $t_2$ and $p^s(t_1)$.
-\item[2)]The intersection between $t_1$ and $p^s(t_2)$, denoted as $Seg_1$, and the intersection between $t_2$ and $p^s(t_1)$, denoted as $Seg_2$, are separately computed .
- \item[3)]The intersection between $t_1$ and $t_2$ is determined by computing the overlap area of $Seg_1$ and $Seg_2$ .
+\item[1)] An early rejection is performed by testing whether $t_1$ intersects $\bm{p}_{t_2, s}$, the supporting plane of $t_2$. The same test is also done between $t_2$ and $\bm{p}_{t_1, s}$.
+\item[2)]The intersection between $t_1$ and $\bm{p}_{t_2, s}$, denoted as $Seg_1$, and the intersection between $t_2$ and $\bm{p}_{t_1, s}$, denoted as $Seg_2$, are separately computed .
+ \item[3)]The intersection between $t_1$ and $t_2$ is determined by computing the overlap between $Seg_1$ and $Seg_2$ .
 \end{itemize}
 
-Conventional implementations of M\"{o}ller's algorithm use vertex-based geometry, which is neither exact nor robust.
-Although implementing M\"{o}ller's algorithm with arbitrary precision arithmetic could make it robust, it is too costly for a large CSG evaluation.
-Actually, the non-robustness of this algorithm is from geometry \emph{constructions} \cite{bernstein2009fast}, which compute new coordinates of geometry objects based on the known coordinates of existing ones.
-In M\"{o}ller's algorithm, the coordinates of $Seg_1$ and $Seg_2$ (Fig.
-\ref{fig_projection}) are computed as intermediate results.
-We use plane-based geometry to solve these problems by avoiding explicitly computing the coordinates of new vertices.
+The non-robustness of this algorithm is from computing the coordinates of intersection vertices, which is the end points of $Seg1$ and $Seg2$.
+Although implementation with arbitrary precision arithmetic produces exact coordinates, it is too costly for boolean operations of large CSG.
+We use plane-based geometry to solve this problem by implicitly representing intersections with planes.
 
@@
 \label{sec:embed}
-According to the method described in section \ref{sec:convert}, triangle faces $f$ are firstly converted to its plane-based representation: a supporting plane $p^s(f)$ surrounded by three bounding planes $\{p^b_i\ |\  i = 1,2,3\}$.
+According to the method described in section \ref{sec:convert}, triangle faces $f$ are firstly converted to its P-rep: a supporting plane $\bm{p}_{t, s}$ surrounded by three bounding planes $\{\bm{p}_{t, b}^i|\ i = 0,1,2\}$.
 We integrate the plane-based geometry into each of the tree steps of M\"{o}ller's algorithm as following:
@@
 \begin{itemize}[leftmargin=0.45cm]
-\item[1)] The basic routine of the first step is given two faces $t_1$ and $t_2$, computing the orientation of the supporting plane (denoted as $p(t_1)\colon(a, b, c, d)$) of a face with respect to a certain vertex (denoted as  $v_i(t_2)\colon(x, y, z)$) of the other face.
-That is to compute:
-\begin{equation}\label{eq:plane}
-sign(ax+by+cz+d).
-\end{equation}
-Reviewing the discussion of section \ref{sec:convert},  the coordinates of vertices are represented by three L-bit float point numbers.Precisions of the four coefficients of the supporting plane are $(P^\star, P^\star, P^\star, P)$.
-Here $P$ is defined in equation \ref{eq:precision}, and $$P^\star=P-(L-1)-2.$$ Using the enforced criterion $M \ge P+1$, we find that $M$ bits are enough to perform the predicate of equation \ref{eq:plane}.
-This allow us to perform the early discard efficiently.
-\item[2)]In step 2, the end points of $Seg_1$ and $Seg_2$ are implicitly represented using intersections of plane triples.
+  \item[1)] The basic subroutine of the first step is given two faces $t_1$ and $t_2$, computing the orientation of of a face with respect to vertices from the other face.
+Reviewing the discussion of \S \ref{sec:convert}, under the constraint of $M \ge P+1$, we can compute the predicate within the precision of $M$ bits.
+This allow us to perform this early rejection efficiently.
+      \vspace{0.5em}
+  \item[2)] If $t_1$ and $t_2$ are not coplanar, the end points of $Seg_1$ and $Seg_2$ can be implicitly represented by plane triples.
 Take $Seg_1$ as an example.
-As illustrated in Fig.
-\ref{fig:isect}, $Seg_1$ are the intersection between $t_1$ and $p_s(t_2)$.
-Because the edge $e_i(t_1)$ can be represented as $(p^s( t_1), p^b_i(t_1))$, the end points of $Seg_1$ can be represented in the form of $(p^s( t_1), p^s(t_2), p^b_i(t_1))$.
+$Seg_1$ is the intersection between $t_1$ and $\bm{p}_{t_2, s}$ and the end points of $Seg_1$ are intersections between $\bm{p}_{t_2, s}$ and edges from $t_1$ (denoted as $\bm{e}^i_{t_1}$).
+Because $\bm{e}^i_{t_1}$ can be represented as $\bm{p}_{t_1, s}\cap \bm{p}^i_{t_1, b}$, the end points of $Seg_1$ can be represented in the form of $\bm{p}_{t_2, s} \cap \bm{p}_{t_1, s} \cap \bm{p}^i_{t_1, b}$.
 In Fig.
-\ref{fig:isect}, we list all intersection situations between $t_1$ and $p_s(t_2)$, and the corresponding bounding plane $p^b_i(t_1)$ in each situation.
-The conditions that $t_1$ is inside the plane $p_s(t_2)$ (coplanar cases) will be discussed later in section \ref{sec:degenerate}.
+\ref{fig:isect}, we list all possible intersecting situations between $t_1$ and $\bm{p}_{t_2, s}$.
+The two corresponding bounding planes $\bm{p}^i_{t_1, b}$ for each situation are also presented.
+The coplanar condition will be discussed later in \S \ref{sec:degenerate}.
+      \vspace{0.5em}
  \item[3)] The intersection between $t_1$ and $t_2$ is the overlap area of $Seg_1$ and $Seg_2$.
-It can be easily computed by comparing the end points of $Seg_1$ and $Seg_2$ along $l$ (Fig.
-\ref{fig_projection}), where $l$ is the intersection between $p_s(t_1)$ and $p_s(t_2)$.
-Because end points are all represented using plane triples, we can use the two-line-one-plane comparison discussed in section \ref{sec:substrates} to perform the comparison.
+It can be easily computed by sorting the end points of $Seg_1$ and $Seg_2$ along the line $\bm{l}\colon \bm{p}_{t_1, s} \cap \bm{p}_{t_2, s}$.
+Because end points are all represented using plane triples, we can use the linear order of points discussed in \S \ref{sec:substrates} to sort.
 \end{itemize}
 
-\subsection{Intersection Representation}
+Each time an intersection is computed, two intersections are generated (one for each triangle face) and the newly introduced vertices are introduced into related meshes.
+To avoid repetitive vertices in the final result, we do repetition elimination in this stage, merging coincident vertices even among different input meshes.
+Because we use P-reps, the comparison of vertices is exact.
+
+\subsection{Plane-Based Intersection Representation}
 \label{sec:ir}
 
-// change the title to Indentifying intersections
-
-The output of this stage, or what we call intersection record (IR), is the data structure which organize the results of triangle-triangle intersection test.
-IR is also the input of tessellation, and is in deep couple with the tessellation method.
-It is hard to give full idea of why the IR is like that before we introduce our tessellation algorithm.
-Therefore, in this section, we first give several requirements for IR from tessellation stage, and then discuss the IR structure.
-To have a comprehensive understanding of IR, readers may need to review this section after finish reading section \ref{sec:tessellation} about tessellation stage.
-
-We recall our definition of Linked Halfedge in section \ref{sec:meshes}, we need to transfer necessary information by IR to tessellation stage for Linked Halfedge construction.
-For each intersection line segment, we use a five-component vector {\color{red}{$\Gamma \colon(t, v_0, v_1, p, C_{P_h \backslash P_i})$}} to describe it.
-Here, $v_b$ and $v_e$ are the two end points of $\Gamma$.
-Component $f$ is the face where the $\Gamma$ lies.
-Component $C$ is the intersection context, and will be further explained later.
-Component $p$ is the plane representation of the line where $\Gamma$ lies (denoted as $\vec{n}_\Gamma$).
-Normally, line is represented by two planes.
-However, one of the planes for $\vec{n}_\Gamma$ must be $f$'s supporting plane $p^s(f)$, so we just omit it, and use the other plane as the representation for $\vec{n}_{\boldsymbol{\Gamma}}$ .
-
-To illustrate, assume two triangle faces $t_1$ and $t_2$, from primitive $P_1$ and $P_2$, intersect at line segment ${\boldsymbol{\Gamma}}$.
-Note that there are two versions of ${\boldsymbol{\Gamma}}$ for each of the two faces respectively, denoted as ${\boldsymbol{\Gamma}}(t_1)$ and ${\boldsymbol{\Gamma}}(t_2)$.
-For ${\boldsymbol{\Gamma}}(t_1)$, $v_b$ and $v_e$ are the two end points of ${\boldsymbol{\Gamma}}$ and $f=t_1$.
-The representation plane $p$ is $p^s(t_2)$.
-Note that $p^s(t_2)$ must not be coplanar with $t_1$.
-The intersection context $C=t_2$ in most cases.
-It means that, in primitive $P_2$, ${\boldsymbol{\Gamma}}(t_1)$ lies on the face $t_2$.
-However, sometimes, intersection may lie on the edge, instead of face,  of other primitive.
-In that case,  the intersection context is an edge, and we discuss such degenerate case in the next section.
-The situation of ${\boldsymbol{\Gamma}}(t_2)$ is similar we omit the discussion here.
-
-In the Linked Halfedge, there must not be any repetitive vertices in order to reconstruct the correct topology.
-Therefore, repetitive vertices elimination must be performed.
-Checking whether there are coincident points in a global scope can be quite inefficient.
-Our implementation use a localized scheme that store the reference of intersection vertices into their corresponding geometry location, like edges and faces.
-Therefore, coincidence detection performed within the geometry elements and repetitive vertices elimination can be very fast.
-
-\subsection{Degenerate Cases}
+Once intersections are computed, proper representation is needed to guarantee exact transfer of information and low cost to process.
+In our method, each line segment intersection $\bm{\Gamma}$ between triangles is represented by our plane-based intersection representation (PBI-rep) as $\{t, \bm{p}_{ext}, (\bm{p}^0, \bm{p}^1),\bm{\Psi}\}$.
+The first component indicates $\bm{\Gamma}$ is on triangle $t$, and second one $\bm{p}_{ext}$ indicates $\bm{\Gamma}$ lies on a line $\bm{l}_{\bm{\Gamma}}\colon(\bm{p}_{t, s} \cap \bm{p}_{ext})$.
+The two end points of $\bm{\Gamma}$ are $\bm{l}_{\bm{\Gamma}}\cap\bm{p}^0$ and $\bm{l}_{\bm{\Gamma}}\cap\bm{p}^1$.
+The last component $\bm{\Psi}$ is a vector that represents the neighborhood of the intersection, which is for fast face classification in later stages.
+For each component of $\bm{\Psi}$, if $\bm{\Gamma}$ is on the surface of primitive $P_k$, the $k^{th}$ component $\Psi_{k}$ is the edge or face of $P_k$ where $\bm{\Gamma}$ lies.
+Otherwise, $\Psi_{k}=0$, meaning default empty data.
+
+To illustrate, assume two triangle faces $t_1$ and $t_2$, from primitive $P_a$ and $P_b$, intersect on a line segment.
+Then it generates two intersections for both triangles respectively, denoted as ${\boldsymbol{\Gamma}}_{12}$ and ${\boldsymbol{\Gamma}}_{21}$.
+For ${\boldsymbol{\Gamma}}_{12}$, the first two components are $t_1$ and $\bm{p}_{t_2, s}$.
+The computation of the third component is discussed in \S\ref{sec:embed}.
+The neighborhood $\bm{\Psi}$ is zero for all components except $\Psi_a$ and $\Psi_b$.
+In most time, $\Psi_a=t_1$ and $\Psi_b=t_2$.
+However, sometimes, intersections may lie on the primitive edges instead of faces.
+In that case, $\Psi_a$ and $\Psi_b$ are edges.
+We postpone this discussion until \S\ref{sec:degenerate}.
+The computation of ${\boldsymbol{\Gamma}}_{21}$ is similar.
+
+\subsection{Degenerate Situations}
 \label{sec:degenerate}
 
-Assume there are two faces $t_1$ and $t_2$ from primitive $P_1$ and $P_2$ respectively.
-These two faces intersect on line segment ${\boldsymbol{\Gamma}}$, which has two versions of IR ${\boldsymbol{\Gamma}}(t_1)$ and ${\boldsymbol{\Gamma}}(t_2)$ for the two faces respectively.
-Without loss of generality, we only discuss the configuration of ${\boldsymbol{\Gamma}}(t_1)$, as ${\boldsymbol{\Gamma}}(t_2)$ can be figured out similarly.
-We classify all degenerate cases into three categories by the dimension of intersection.
-Each of them is discussed separately in the following.
-
-Before we go into details, there are three principles that we follow to solve degenerate cases:
-\begin{itemize}
-\item We want our method be unconditional robust and exact, so all degenerate cases should be well handled (completeness).
-  \item To control the complexity of tessellation, we want degenerate cases to be invisible to tessellation, that is, degenerate cases have the same format of output, in our method, IR, as non-degenerate cases (invisibility).
-  \item we want the outcome of tessellation be as simple as possible. That is, intersection line segments that will not help tessellation, if recognized, are disposed (concision).
-\end{itemize}
-The criterion of whether an intersection help tessellation is by its necessity: if the intersection is not presented, whether some faces from the linked halfedge will cross the boundary of primitives.
+Which two triangles, if intersecting, intersect on a line segment in most situations, they can also intersect on a point or a convex area (coplanar case).
+Even if line segment is the intersection, the intersection can be on triangle edges or inside triangles.
+These degenerate situations are troublesome to develop a robust boolean method.
+In this section, we offer simple but robust way to deal with all the degenerations and conceal the complexity of intersections behind the concise intersection representation in \S\ref{sec:ir}.
+
+%The criterion of whether an intersection help tessellation is by its necessity: if the intersection is not presented, whether some faces from the linked halfedge will cross the boundary of primitives.
 The word 'cross' do not only include the situation that a face is partly outside and partly inside of a primitive, but also can mean that a face is partly inside (outside) and part on the boundary of the primitive.
 
-\subsubsection{Intersects on point}
+\subsubsection{Point intersection}
 \label{sec:ipoint}
-When two triangles intersect on a single point, there are two different conditions (Fig.
-\ref{fig:isolated}), depending on whether the point is isolated.
-If the point is isolated, it means that there is no other intersection line segment sharing the point.
-This condition may cause non-manifold surface because of the singularity of the isolated intersection point.
-Also, isolated intersection point will not affect the tessellation of the intersection face.
-On the other hand, if the intersection point is not isolated, there must be other intersection line segments that contain the point, thus the point will be introduced at least twice.
-Therefore, no matter which condition it is, when two triangle faces intersect on point, we can just omit this intersection and this will not affect the correctness of the final topology.
+If two triangles intersect on a single point (Fig.
+\ref{fig:isolated}), the intersection cannot be represented using our four-component description.
+Therefore, we simply add the intersection point into the meshes to guarantee correct tessellation, and no intersection is introduced.
 
@@
 
-\subsubsection{Intersects on face edges}
-
-// intersect on face edges does not create new line segments, it is part of the edges from other meshes, and will to be duplicated.
-
-// whose edge? need to be further explained and better defined. an edge intersection divide edge in a triangle and will be duplicated in the other
+\subsubsection{Edge intersection}
+
+% intersect on face edges does not create new line segments, it is part of the edges from other meshes, and will to be duplicated.
+
+% whose edge? need to be further explained and better defined. an edge intersection divide edge in a triangle and will be duplicated in the other
 
@@
 \ref{fig:twin}).
-we call it as \emph{edge intersections}.
-There are generally two kinds of edge intersections.
-If ${\boldsymbol{\Gamma}}$ lies on the edge of $t_1$ or $t_2$, but inside of the face of the other one, then we called it as edge-face intersections.
-If ${\boldsymbol{\Gamma}}$ lies on the edges of both $t_1$ and $t_2$, we call it as edge-edge intersections.
-When there is edge-face intersection, we treat it as the intersection of three faces $t_1$, $t_2$ and $t_1^\star$ (or $t_2^\star$).
-When there is edge-edge intersection, we treat it as the intersection of four faces $t_1$, $t_2$, $t_1^\star$ and $t_2^\star$.
-The $t_1^\star$ (or $t_2^\star$), known as \emph{companion face},  is the neighboring face which shares the intersection edge with $t_1$ (or $t_2$).
-In this way, we avoid repetitive insertion of the same edge intersections, since the companion faces share the same intersection with its neighborhood $t_1$ or $t_2$.
+we call it \emph{edge intersection}.
+The only difference between edge intersection and the general case is the neighborhood representation $\Psi$.
+The space near edge intersection is decided by both face in the two side of the intersected edge, instead of just one triangle face (Fig.
+X).
+Therefore, supposing intersection is on the edge from mesh $P_k$, the neighborhood $\Psi_k$ is then an edge.
+Note that an intersection can be on edges from different meshes.
+Then there are more than one component of $\bm{\Psi}$ are edges.
+
+One thing need to be noticed is that there will be repetitive detection of edge intersections.
+In Fig.
+\ref{fig:twin}a, the same intersection on $t_1$ will be detected twice with both $t_2$ and $t_2^{\star}$.
+We solve this duplication together with other interactions among intersections in \S\ref{sec:tessellation}.
+We call $t_2$ and $t_2^{\star}$ as \emph{companion triangles} in an edge intersection, a concept which will be referred again in the discussion of coplanar cases.
 
@@
 
-Both edge-face and edge-edge intersection can be further classified into three subclasses by the location of companion faces---cross condition, coplanar condition and invalid condition.
-We first consider edge-face intersection.
-If $t_1$ and $t_1^\star$ are on the same side of $t_2$, it is cross condition.
-If they are on the same side, it is invalid condition.
-If $t_1^\star$ is coplanar with $t_2$, it is coplanar condition.
-Consider the cross and coplanar condition.
-For $t_2$, the IR is the same as the common situation, except that the intersection context is an edge.
-For $t_1$ and $t_1^\star$, they have to share the intersection line segment, while the intersection context is $t_2$.
-However, when there is invalid condition, we should not record the intersection for the similar reasons of isolated point intersection (section \ref{sec:ipoint}).
-
-The handling of edge-edge intersection is similar with edge-face intersection.
-The difference is that the intersection contexts are edges for both $t_1$ and $t_2$.
-We still can classify edge-edge intersection into three subclasses by the relative location of companion faces.
-There is one difference, though, that in edge-face intersection, we compute on which side of $t_2$ the companion face $t_1^\star$ lies, and compare with $t_1$.
-However, in edge-edge intersection, we have to consider the space split by both $t_2$ and $t_2^\star$ instead of only $t_2$.
-Similar with edge-face intersections, we record the intersection of cross and coplanar condition, while omit the invalid condition for concision and also topology correctness.
-
-\subsubsection{Coplanar cases}
+\subsubsection{Copalnar}
 
@@
 
-Consider two triangle faces $T_1$ and $T_2$ intersect within a common plane.
-Both $T_1$ and $T_2$ will divide each other into two areas---the overlapped area and the exclusive part (Fig.
+Consider two triangle faces $t_1$ and $t_2$ intersect within a common plane.
+Both $t_1$ and $t_2$ will divide each other into two areas---a convex overlapping area and exclusive parts (Fig.
 \ref{fig:coplanar}).
-Obviously, if we tessellate both $T_1$ and $T_2$ according to the boundary of overlapped area, we can guarantee that the tessellated meshes will not cross the boundary of any other meshes.
-In fact, many methods \cite{feito2013fast} claim that it is important to tessellate faces according to the 2D-intersection result.
-We will show that this is not necessary in our method.
-We do not care whether $T_1$ and $T_2$ really intersect in 2D.
-We simply omit all coplanar cases, treating them as they do not intersect.
-This simplify our intersection test, making it more robust and fast (coplanar cases can be usual in a CSG of artificial object), while doing no harm to the correctness of our method.
-
-The key observation is that coplanar cases do not create new edges, just like edge intersection in the last section.
-The difference is that in a non-coplanar case, there is only one edge intersection.
-In a coplanar, there are at most three intersections.
-Therefore, we can decompose it into three edge intersections and record each edge intersection independently.
-However, there is a better way that we do not process them at all.
-This is because there is companion face, like $T_1^*$, in edge intersection.
-If $T_1^*$ is not coplanar with $T_2$, then we can solve the intersection between $T_1^*$ and $T_2$ in a 3D way, which is the case in Fig \ref{fig:twin}(c).
-On the other hand, if $T_1^*$ is coplanar with $T_2$, we instantly know that both sides of shared edge $e(T_1, T_1^*)$ have the same indicator $\boldsymbol{\Lambda}_1$, which imply that this intersection is not necessary for tessellation and we can omit it by the principle of concision.
-In sum-up, we do not need to handle with coplanar intersection cases.
+Obviously, if we tessellate both $t_1$ and $t_2$ according to the boundary of overlapping area, we can guarantee that the tessellated meshes will not cross the boundary of any other meshes.
+In fact, many methods \cite{feito2013fast,zhou2016mesh} claim that tessellating faces according to this 2D-intersection result is necessary.
+However, in our method, we do not test whether $t_1$ and $t_2$ really intersect in 2D.
+We simply omit all coplanar situations, treating them as they do not intersect at all.
+This simplify our method, making it more robust and fast, while doing no harm to the topology correctness.
+
+The key observation is that intersection in 2D does not create new valid edges.
+The word `valid` means the edge is necessary or possibly necessary for the final result mesh.
+We find that each intersection line segment in 2D is on the edges from input meshes.
+That means we can view 2D intersections as special cases of edge intersection.
+The only difference is that there can be up to three edge intersections in one 2D intersection (Fig.
+x).
+As we have discussed, edge intersection will be detected twice.
+That means we can rely on the companion triangle faces to detect intersections.
+There is more extreme case that the companion triangles are coplanar, meaning neither of them will record the intersection.
+However, in this case, the intersection is not valid.
+The two sides of the intersection are both retained or both dropped and we do not rely the it for tessellation.
 
@@
 
-{\color{red}{red alert start}}
-
 \label{sec:tessellation}
-This is the step to tessellate input meshes with intersections, outputting linked halfedge.
-We called this stage as deferred tessellation because it happens until we collect all necessary intersections.
-For this problem, Ogayar-Anguita et.
+After intersection computation, tessellation is performed on each intersecting triangle face and generate the intersection-free hybrid mesh.
+We call this stage as deferred tessellation because the tessellation happens until all valid intersections are computed.
+Ogayar-Anguita et.
 al.
-\cite{ogayar2015deferred} try to use Constrained Delaunay Triangulation (CDT) to solve, as the intersections is naturally the constraints and triangle faces is naturally a convex zone.
-It works fine for Boolean operation of two primitives.
-However, when there are more than two primitives, simply applying CDT covers the complexity of tessellation.
-The major problem here is that the intersections may be \emph{irregular}.
-The definition of regular intersection is that it does not cross or overlap with other intersections.
-In CSG cases with more than two meshes, irregular intersections can introduce new vertex, split original intersection line segments.
-However, most CDT algorithms \cite{chew1989constrained}, or even just constrained triangulation [Computational geometry: an introduction] require that constraints do not cross each other, and will cause topology deficiency if not satisfied.
-
-To solve these problems, we first refine the intersections and eliminate any irregular intersections.
-When all intersections are regular, we can directly use CDT to tessellate.
-However, 2D constrained triangulation algorithm \cite{chew1989constrained} [Computational geometry: an introduction] require cross detection between arbitrary connections of vertices, coordinates projection, which is hard to exactly performed using plane-reps geometry.
-Therefore, we develop a new tessellation algorithm using only plane-based geometry, ensuring topology correctness and unconditional robust.
+\cite{ogayar2015deferred} use Constrained Delaunay Triangulation (CDT) to perform deferred tessellation.
+They treat triangle faces as convex triangulation zones and intersections as constraints.
+However, CDT has at least two drawbacks for this problem.
+
+The first problem is the dilemma of precision and efficiency.
+Constrained triangulation algorithms \cite{chew1989constrained,preparata2012computational} usually require coordinates projection or intersection detection between arbitrary connections of input vertices.
+These geometry predicates are hard to guarantee computation efficiency and precision simultaneously neither by arbitrary precision arithmetic or P-rep geometry.
+
+The second problem is that when there are more than two primitives, simply applying constrained triangulation covers the complexity of intersections between mesh.
+The intersections may intersect each other, introducing new vertices, splitting original intersection line segments (Fig.
+x).
+However, most constrained triangulation algorithms assume that constraint edges do not intersect.
+They may fail to output the correct topology if the assumption is broken.
+
+To solve these problems, we first perform 2D intersection detection between intersections.
+After that, we develop a new tessellation method using only plane-based geometry, ensuring unconditional topology correctness.
 We first organize intersections into single face scope, generating an intermediate data structure---\emph{Tess-graph}.
-Then we tessellate each face by subtract sub-faces from its corresponding Tess-graph.
+Then we tessellate each face by extract subfaces from its corresponding Tess-graph.
 In compensate, we do not guarantee the faces of the final mesh are triangles, leaving the flexibility to post-processing.
@@
 \subsection{Eliminating Irregular Intersection}
+
+In IFS-mesh, there must not be any repetitive vertices in order to reconstruct the correct topology.
+Therefore, repetitive vertices elimination must be performed.
+Checking whether there are coincident points in a global scope can be quite inefficient.
+Our implementation use a localized scheme that store the reference of intersection vertices into their corresponding geometry location, like edges and faces.
+Therefore, coincidence detection performed within the geometry elements and repetitive vertices elimination can be very fast.
 
@@
 
-Using plane-based representation, whether two intersections intersects each other is determined by predicate of orientation of plane against a point.
+Using P-rep, whether two intersections intersects each other is determined by predicate of orientation of plane against a point.
 For example, we want determine whether ${\boldsymbol{\Gamma}}_1$ and ${\boldsymbol{\Gamma}}_2$ intersects.
@@
 Classification is done by evaluating the indicator vector of each face {\color{red}{(indicator vector?)}}.
-During this process, we take advantage of plane-based representation to ensure unconditional correct classification.
+During this process, we take advantage of P-rep to ensure unconditional correct classification.
 In addition, since we maintain the intra-primitive geometry connectivity and inter-primitive geometry connectivity in Linked Halfedge, we can utilize the space coherence of face indicator vectors to accelerate this process.

### 2016-09-27 summary.tex
9.27+
9.27

@@
 \usepackage{bm}
+%\usepackage{mathrsfs}
+\usepackage[mathcal]{eucal}
+\usepackage{amsfonts}
 % correct bad hyphenation here
@@
 
+\iffalse
 \begin{figure*}[!t]
@@
 \end{figure*}
+\fi
 
@@
 
-Each time an intersection is computed, two intersections are generated (one for each triangle face) and the newly introduced vertices are introduced into related meshes.
-To avoid repetitive vertices in the final result, we do repetition elimination in this stage, merging coincident vertices even among different input meshes.
+Each time an intersection is computed, two intersections are generated (one for each triangle) and the newly generated vertices are added into meshes.
+To avoid repetitive vertices in the final result, we perform vertex repetition elimination in this stage, merging coincident vertices even among different input meshes.
 Because we use P-reps, the comparison of vertices is exact.
@@
 Once intersections are computed, proper representation is needed to guarantee exact transfer of information and low cost to process.
-In our method, each line segment intersection $\bm{\Gamma}$ between triangles is represented by our plane-based intersection representation (PBI-rep) as $\{t, \bm{p}_{ext}, (\bm{p}^0, \bm{p}^1),\bm{\Psi}\}$.
-The first component indicates $\bm{\Gamma}$ is on triangle $t$, and second one $\bm{p}_{ext}$ indicates $\bm{\Gamma}$ lies on a line $\bm{l}_{\bm{\Gamma}}\colon(\bm{p}_{t, s} \cap \bm{p}_{ext})$.
-The two end points of $\bm{\Gamma}$ are $\bm{l}_{\bm{\Gamma}}\cap\bm{p}^0$ and $\bm{l}_{\bm{\Gamma}}\cap\bm{p}^1$.
+In our method, an intersection line segment $\mathbb{I}$ is represented by our plane-based intersection representation (PBI-rep) as $\{t, \bm{p}_{ext}, (\bm{p}^0, \bm{p}^1),\bm{\Psi}\}$.
+The first component indicates $\mathbb{I}$ is on triangle $t$, and second one $\bm{p}_{ext}$ indicates $\mathbb{I}$ lies on a line $\bm{l}_{\mathbb{I}}\colon(\bm{p}_{t, s} \cap \bm{p}_{ext})$.
+The two end points of $\mathbb{I}$ are $\bm{l}_{\mathbb{I}}\cap\bm{p}^0$ and $\bm{l}_{\mathbb{I}}\cap\bm{p}^1$.
 The last component $\bm{\Psi}$ is a vector that represents the neighborhood of the intersection, which is for fast face classification in later stages.
-For each component of $\bm{\Psi}$, if $\bm{\Gamma}$ is on the surface of primitive $P_k$, the $k^{th}$ component $\Psi_{k}$ is the edge or face of $P_k$ where $\bm{\Gamma}$ lies.
+For each component of $\bm{\Psi}$, if $\mathbb{I}$ is on the surface of primitive $P_k$, the $k^{th}$ component $\Psi_{k}$ is the edge or face of $P_k$ where $\mathbb{I}$ lies.
 Otherwise, $\Psi_{k}=0$, meaning default empty data.
@@
 To illustrate, assume two triangle faces $t_1$ and $t_2$, from primitive $P_a$ and $P_b$, intersect on a line segment.
-Then it generates two intersections for both triangles respectively, denoted as ${\boldsymbol{\Gamma}}_{12}$ and ${\boldsymbol{\Gamma}}_{21}$.
-For ${\boldsymbol{\Gamma}}_{12}$, the first two components are $t_1$ and $\bm{p}_{t_2, s}$.
+Then it generates two intersections for both triangles respectively, denoted as ${\mathbb{I}}_{12}$ and ${\mathbb{I}}_{21}$.
+For ${\mathbb{I}}_{12}$, the first two components are $t_1$ and $\bm{p}_{t_2, s}$.
 The computation of the third component is discussed in \S\ref{sec:embed}.
@@
 We postpone this discussion until \S\ref{sec:degenerate}.
-The computation of ${\boldsymbol{\Gamma}}_{21}$ is similar.
-
-\subsection{Degenerate Situations}
+The computation of ${\mathbb{I}}_{21}$ is similar.
+
+\subsection{Degenerate Case Handling}
 \label{sec:degenerate}
@@
 We solve this duplication together with other interactions among intersections in \S\ref{sec:tessellation}.
-We call $t_2$ and $t_2^{\star}$ as \emph{companion triangles} in an edge intersection, a concept which will be referred again in the discussion of coplanar cases.
+We call such $t_2$ and $t_2^{\star}$ as \emph{companion triangles} in an edge intersection, a concept which will be referred again in the discussion of coplanar cases.
 
@@
 They treat triangle faces as convex triangulation zones and intersections as constraints.
-However, CDT has at least two drawbacks for this problem.
-
-The first problem is the dilemma of precision and efficiency.
-Constrained triangulation algorithms \cite{chew1989constrained,preparata2012computational} usually require coordinates projection or intersection detection between arbitrary connections of input vertices.
-These geometry predicates are hard to guarantee computation efficiency and precision simultaneously neither by arbitrary precision arithmetic or P-rep geometry.
-
-The second problem is that when there are more than two primitives, simply applying constrained triangulation covers the complexity of intersections between mesh.
-The intersections may intersect each other, introducing new vertices, splitting original intersection line segments (Fig.
+
+Our first try is to implement a robust CDT and apply to our method.
+However, we fail because of the dilemma of precision and efficiency.
+CDT algorithms \cite{chew1989constrained,preparata2012computational} usually require coordinates projection or intersection detection between arbitrary connections of vertices within triangulation zone.
+Because vertices may be implicitly represented in our method, these geometry predicates are hard to guarantee computation efficiency and precision simultaneously.
+Moreover, when there are more than two primitives, simply applying CDT omits the complexity of intersections between meshes.
+The intersections may intersect each other, introducing new vertices and splitting original intersection line segments (Fig.
 x).
-However, most constrained triangulation algorithms assume that constraint edges do not intersect.
-They may fail to output the correct topology if the assumption is broken.
-
-To solve these problems, we first perform 2D intersection detection between intersections.
-After that, we develop a new tessellation method using only plane-based geometry, ensuring unconditional topology correctness.
-We first organize intersections into single face scope, generating an intermediate data structure---\emph{Tess-graph}.
-Then we tessellate each face by extract subfaces from its corresponding Tess-graph.
-In compensate, we do not guarantee the faces of the final mesh are triangles, leaving the flexibility to post-processing.
-
-\subsection{Eliminating Irregular Intersection}
-
-In IFS-mesh, there must not be any repetitive vertices in order to reconstruct the correct topology.
-Therefore, repetitive vertices elimination must be performed.
-Checking whether there are coincident points in a global scope can be quite inefficient.
-Our implementation use a localized scheme that store the reference of intersection vertices into their corresponding geometry location, like edges and faces.
-Therefore, coincidence detection performed within the geometry elements and repetitive vertices elimination can be very fast.
-
-Regular intersections are guaranteed when there are only two meshes, because the surfaces of primitives are all without self-intersection.
-However, when there are more than two primitives, this constraint can be violated.
-In the view of intersection detection, it is not enough to find all intersection vertices by only triangle-triangle intersection test.
-This is because in such case, the new vertex can be introduced not only by intersection between edge and plane, but also by intersections of three planes, which involves more than two faces.
+This breaks the assumption of most CDT algorithms and may lead to incorrect output topology.
+
+To solve these problems, we first perform intersection refinement to eliminate any crossing or overlapping between intersections.
+After that, we perform conservative tessellation based on plane-based geometry, ensuring unconditional topology correctness.
+The word `conservative` means we tessellate face into polygons, not triangles.
+During tessellation, we organize intersections and generate an \emph{tess-graph}, which is a graph-like description of intersections.
+At last, we extract subfaces from tess-graph of each triangle face and construct the intersection-free hybrid meshes.
+
+\subsection{Intersection Refinement}
+
+The intersection vertices are not only introduced by intersection between an edge and a triangle, but also introduced by intersections of three triangles.
+It is not enough to find all of them by only triangle-triangle intersection tests.
+Also, because of degenerate cases, there will be other forms of intersections involving three or even more triangles.
+To make tessellation easier and more robust, we have to refine these intersections and all unusual conditions have to be removed before it.
 
 Intersection refinement is performed in a local scope.
-For each face, we detect irregular intersections by intersection test between pairs of intersections.
-Because primitive meshes are not self-intersecting, we only check intersections between intersections made by different meshes.
-Face intersecting only one other mesh do not need refinement, since they do not have such intersection pairs.
-
-Using P-rep, whether two intersections intersects each other is determined by predicate of orientation of plane against a point.
-For example, we want determine whether ${\boldsymbol{\Gamma}}_1$ and ${\boldsymbol{\Gamma}}_2$ intersects.
-Using the notation of section \ref{sec:ir}, we perform the test by checking whether $v_0({\boldsymbol{\Gamma}}_1), v_1({\boldsymbol{\Gamma}}_1)$ are on two sides of $p({\boldsymbol{\Gamma}}_2)$ and whether $v_0({\boldsymbol{\Gamma}}_2), v_1({\boldsymbol{\Gamma}}_2)$ are on two sides of $p({\boldsymbol{\Gamma}}_1)$.
-If yes, ${\boldsymbol{\Gamma}}_1$ and ${\boldsymbol{\Gamma}}_2$ intersects and introduces new intersection vertex $v_{new}$, which is the intersection of $p({\boldsymbol{\Gamma}}_1), p({\boldsymbol{\Gamma}}_2)$ and the supporting plane of $t({\boldsymbol{\Gamma}}_1)$.
-The new vertex $v_{new}$ should be added into both ${\boldsymbol{\Gamma}}_1$ and ${\boldsymbol{\Gamma}}_2$ as a segment point.
-Since there may be more than one segment point added into a certain intersection during the whole test, we do not divide the intersection until all intersection pairs are tested.
-
-Degenerate cases are when the two intersections intersect on one of the end points or are collinear.
-In the first condition {\color{red}{Fig.
-??(a)}}, there is no new vertex generated and only one of the intersection needs splitting.
-The collinear case {\color{red}{Fig.
-??(b)}} is intersection in 1D and are tested exactly by two-point-on-line comparison between the end points of intersections.
-If there is intersection between them, it should be straightforward to figure out the segment points for each intersections.
-
-After all segment points are found, the related intersections have to be split.
-For a certain intersection, we sort the segment points by two-point-on-line comparisons and subtract child intersections along the direction of their father one by one.
-The representation of the child intersections should be the same with their father except the coordinate components $v_0$ and $v_1$.
-So far, we guarantee that all refined intersections need not be further divided as the potential edges of the Linked Halfedge.
-However, if there are collinear cases, there will be coincident child intersections from different fathers.
-We choose to resolve them in Tess-graph.
-If CDT is chosen instead of Tess-graph, coincidence can be handled like-wise.
-
-\subsection{Tess-Graph}
-
-So far, intersections are only loose data that store the coordinates and neighbouring information.
-To perform tessellation and extract sub-faces, we need to organize them to reveal the topology.
-We use Tess-graph for this purpose.
-A Tess-graph is the graph description of the tessellated face topology.
-For each face to be tessellated, we construct a Tess-graph according to the refined intersections.
-The final Linked Halfedge merges both the original topology and the intersections in the same representation.
-And the construction of Tess-graph is the first step towards such uniformity.
-By only nodes and connections, it represents both the intersections and the original boundary of triangle face.
-This reduces complexity of the following processes and allowing them to be simple and fast.
-
-Nodes of Tess-graph represent vertices and store the coordinates of them.
-Connections are nondirectional, represent edges in Linked Halfedge, storing the I-rep if it is coincident with an intersection.
-Sometimes, there will be more than one coincident intersections and all I-reps have to be stored.
-Construction of Tess-graph from I-rep is straightforward except one thing: we have to merge face boundary with the intersections lies on the face boundary {\color{red}{Fig}}.
-This lead to an extra step beforehand.
-For each edge boundary of face, we treat it as pseudo-intersections with only coordinates information, and perform collinear intersection test with all intersections lies on it, splitting it by corresponding segment points.
-
-\subsection{Extracting Sub-faces}
-
-The difference between a graph and a mesh surface is that there is no concept of face in graph. In this step, we extract faces from Tess-graph to construct Linked Halfedge.
-
-First, We classify connections of Tess-graph into two types: connections on face boundaries as \emph{boundary connections} and connections inside face as \emph{inner connections}.
-In the view of halfedge data structure, inner connections represent two opposite halfedges but boundary connections represent only one.
+For each intersecting face $t_i$, we collect all intersections on $t$ as a set $\bm{\Gamma}(t)=\{\mathbb{I}_{t}^i, i=0,1,2,...\}\cup\{\mathbb{I}_{t}^{e_i},i=0,1,2\}$ and refine them together.
+The set $\{\mathbb{I}_{t}^{e_i},i=0,1,2\}$ is the PBI-reps of the three edges of $t$.
+We treat edges as intersections for simplicity in this stage.
+The neighborhood component $\bm{\Psi}(\mathbb{I}_{t}^{e_i})$ is set as $\bm{0}$.
+Other components of $\mathbb{I}_{t}^{e_i}$ are straightforward to determine.
+Refinement on $\bm{\Gamma}(t)$ is done using only plane-based geometry predicates by the following three steps:
+
+\vspace{0.5em}
+\noindent \textbf{Collinear splitting}~~~~
+Each intersection $\mathbb{I}_{t}^x$ are testing whether they are collinearly overlapping with other intersections.
+If yes, $\mathbb{I}_{t}^x$ is split by the end points of overlapping intersections (Fig.
+x).
+Because $\mathbb{I}_{t}^x$ may collinearly overlap more than one other intersection, the splitting may be deferred until all splitting points are found.
+The subroutine linear order of points (\S\ref{sec:substrates}) is used to sort these splitting points along $\mathbb{I}_{t}^x$.
+The PBI-reps of split segments inherit their father's except the second component the end points.
+
+\vspace{0.5em}
+\noindent \textbf{Coincidence elimination}~~~~
+We merge coincidence intersections which have the same end points.
+Intersections are undirected so intersections with inverse end points are also coincident.
+The PBI-rep of the new intersection is inherited from either of the old one's except the neighborhood component $\bm{\Psi}$.
+We follow the merging rules below:
+\begin{equation}
+  \Psi_k(\mathbb{I}_{t}^{12})=\left\{
+   \begin{array}{l}
+   \Psi_k(\mathbb{I}_{t}^1)\mbox{ or }\Psi_k(\mathbb{I}_{t}^2),\ \mbox{ if } \Psi_k(\mathbb{I}_{t}^1)=\Psi_k(\mathbb{I}_{t}^2) \\
+   \Psi_k(\mathbb{I}_{t}^1),\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \mbox{ if } \Psi_k(\mathbb{I}_{t}^2)=0  \\
+   \Psi_k(\mathbb{I}_{t}^2),\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \mbox{ if } \Psi_k(\mathbb{I}_{t}^1)=0  \\
+   \end{array}
+  \right.
+\end{equation}
+, where $\mathbb{I}_{t}^1$ and $\mathbb{I}_{t}^2$ are old intersections and $\mathbb{I}_{t}^{12}$ is the new one.
+
+\vspace{0.5em}
+\noindent \textbf{Crossing intersection resolving}~~~~
+After the process of two previous steps, there are no overlapping intersections in $\bm{\Gamma}(t)$.
+We check whether any pair of intersections intersect each other.
+The definition of \emph{intersect} does not include the situation that two intersections share end points.
+In Fig.
+x, we illustrate the only two situations.
+In both situations, one intersection is split by other, and the same splitting routine is used as in collinear splitting.
+
+%\vspace{0.5em}
+%There is one more thing that we give intersections generated (by merging or splitting) from the PBI-reps of edges  the positive directions.
+That means all intersections lies on triangle edges have a positive direction.
+Direction is defined by the direction of edge the intersection lies on.
+
+\subsection{Tessellation by Tess-Graph}
+
+So far, intersections are only independent data that store the coordinates and neighbouring information.
+To perform tessellation and extract subfaces, we need to organize them to reveal the topology.
+We use tess-graph for this purpose.
+A tess-graph is the graph description of the tessellated face topology.
+For each face to be tessellated, we construct a tess-graph according to the refined intersections.
+Nodes of tess-graph represent end points of intersections and undirectional connections between nodes represent intersections.
+The construction of tess-graph is straightforward and the reader will not have problem filling the details.
+
+After we have tess-graph, we tessellate face and extract subfaces according to it.
+This is done by tracing loops on tess-graph.
+A valid loop that corresponds to a subface must satisfy two criterions: 1) the direction of loops should be coherent with the face normal, and 2) consecutive connections on the loop should be adjacent by circular order {\color{red}{Fig.?}}.
+After we find out all valid loops on tess-graph, the tessellation is done on that triangle face.
+More details are discussed in \S\ref{sec:}.
+
+%In our implementation, we find that it is not easy to check whether the loop direction is coherent with face normal by plane-based geometry.
+
+%First, We classify connections of tess-graph into two types: connections on face boundaries as \emph{boundary connections} and connections inside face as \emph{inner connections} by the whether they have positive directions.
+In the view of halfedge, inner connections represent two opposite halfedges but boundary connections represent only one.
 We add an attribute for each connection to identify their directions, and thus we get a directed version of Tess-graph.
@@
 Extracting faces are process of searching for valid loops which meet certain geometry constraints.
-After all faces are extracted, all halfedges of directed Tess-graph should be used exactly once.
-
-There two geometry constraints for valid loops.
-First, the direction of loops should be coherent with the face normal, counter-clockwise for example.
-Second, consecutive halfedges on the loop should be angle adjacent, which means there is no other halfedges between the angle contained by these two halfedges {\color{red}{Fig.?}}.
+After all faces are extracted, all halfedges of directed Tess-graph should be used
+
+%There two geometry constraints for valid loops.
+Second, consecutive connections on the loop should be adjacent by circular order {\color{red}{Fig.?}}.
 To meet these constraints, we sort the halfedges counter-clockwise for each nodes with more than two halfedges starting from them.
@@
 To make the results of two-line-on-plane comparisons coherent, we assume that for each halfedge $h_i$, the normal directions of its plane-rep, denoted as $\vec{n}(h_i)$, meets the following criterion:
-\begin{equation}
-(\vec{n}(h_i) \times \vec{n}_0) \cdot \vec{l}(h_i) > 0,
-\end{equation}
-where $\vec{n}_0$ is the normal of the face, and $\vec{l}(h_i)$ is the direction of $h_i$.
+%\begin{equation}
+%(\vec{n}(h_i) \times \vec{n}_0) \cdot \vec{l}(h_i) > 0,
+%\end{equation}
+%where $\vec{n}_0$ is the normal of the face, and $\vec{l}(h_i)$ is the direction of $h_i$.
 The plane-rep of halfedge can be inherited from the corresponding connections from the undirected Tess-graph.
@@
 
-\section{Face Classification}
+\section{Face Classification, p->e->f, patial sort}
 
@@
     \For {each neighboring face $t_i^c$}
-        \If {there are I-reps $\{{\boldsymbol{\Gamma}}_k\}$ on $e(t_i^c, t_c)$}
-            \State $\boldsymbol{\Lambda}(t_c), \{{\boldsymbol{\Gamma}}_k\} \Longrightarrow \boldsymbol{\Lambda}(t_i^c)$
+        \If {there are I-reps $\{{\mathbb{I}}_k\}$ on $e(t_i^c, t_c)$}
+            \State $\boldsymbol{\Lambda}(t_c), \{{\mathbb{I}}_k\} \Longrightarrow \boldsymbol{\Lambda}(t_i^c)$
             \State \Call{propagate} { $t_i^c$ , $\boldsymbol{\Lambda}(t_i^c)$}
@@
 
-Since the faces involving in $C_{P_h \backslash P_j}$ is part of primitive $P_j$, the space division $\boldsymbol{D}(C_{P_h \backslash P_j})$ is homogeneous with the space division by $P_j$ in neighborhood of $\boldsymbol{\Gamma}$.
-The basic idea is to choose one point $v_x(t_i)$ on $t_i$ close enough to $\boldsymbol{\Gamma}$ to compute $\lambda(v_x(t_i), P_j)$, and then compute $\lambda(t_i, P_j)$ accordingly.
+Since the faces involving in $C_{P_h \backslash P_j}$ is part of primitive $P_j$, the space division $\boldsymbol{D}(C_{P_h \backslash P_j})$ is homogeneous with the space division by $P_j$ in neighborhood of $\mathbb{I}$.
+The basic idea is to choose one point $v_x(t_i)$ on $t_i$ close enough to $\mathbb{I}$ to compute $\lambda(v_x(t_i), P_j)$, and then compute $\lambda(t_i, P_j)$ accordingly.
 However, the problem is that we cannot find such a $v_x(t_i)$ that can be represented exactly, which means robust classification cannot be performed.
-Fortunately, we observe that we can choose $v_b^2(t_i)$, which is not so close to $\boldsymbol{\Gamma}$ instead.
+Fortunately, we observe that we can choose $v_b^2(t_i)$, which is not so close to $\mathbb{I}$ instead.
 To illustrate, assume there is another point $v_{x'}(t_i)$ inside of $t_i$ that is very close to $v_b^2(t_i)$ ({\color{red}{Fig.
@@
 
-\subsection{Caching Evaluation Results}
-
+\section{Implementation}
+
+\vspace{0.5em}
+\textbf{Seed Indicator Vector Generation.} Our method of generating the first indicator vector will fail on extreme conditions when all faces in Linked halfedge are coincident with more than one primitive face (e.g., the union of the same mesh).
+In order to be robust, we use the high-precision face barycenter with the point-in-polyhedron test to generate the seed indicator vector instead after several failures of choosing a proper seed face.
+
+\vspace{0.5em}
+\noindent \textbf{Exact Face Classification.} In Linked halfedge, all the supporting planes of faces and all the vertices can be exactly represented.
+Based on that, when computing the new indicator according to I-reps, we can use BSP techniques similar to \cite{bernstein2009fast} to conduct robust predicates.
+Since the intersection context is neither face or edge, the space division planes in each BSP will be no more than two, which guarantees fast construction and classification.
+
+\vspace{0.5em}
+\noindent \textbf{Continuous operations.}
+
+\vspace{0.5em}
+\noindent \textbf{Parallel.}
+
+\vspace{0.5em}
+\noindent \textbf{Lazy intersection.}
+
+\vspace{0.5em}
+\noindent \textbf{Caching Evaluation Results}
 If the CSG tree is large, with hundreds of primitive nodes, computing $\lambda_f(x)$ from $\boldsymbol{\Lambda}(x)$ for every face can be costly.
@@
 
-\section{Implementation}
-
-\vspace{0.5em}
-\textbf{Seed Indicator Vector Generation.} Our method of generating the first indicator vector will fail on extreme conditions when all faces in Linked halfedge are coincident with more than one primitive face (e.g., the union of the same mesh).
-In order to be robust, we use the high-precision face barycenter with the point-in-polyhedron test to generate the seed indicator vector instead after several failures of choosing a proper seed face.
-
-\vspace{0.5em}
-\noindent \textbf{Exact Face Classification.} In Linked halfedge, all the supporting planes of faces and all the vertices can be exactly represented.
-Based on that, when computing the new indicator according to I-reps, we can use BSP techniques similar to \cite{bernstein2009fast} to conduct robust predicates.
-Since the intersection context is neither face or edge, the space division planes in each BSP will be no more than two, which guarantees fast construction and classification.
-
-\section{Experiments}
-
-\section{Summary}
-
-In this paper, we proposed a novel method to evaluate CSG with triangular mesh primitives.
-It is able to efficiently perform non-incremental evaluation of large CSG with massive faces.
-The key idea of our approach is to use the local coherence of face space labels to accelerate face membership classification.
-A two-level grouping framework is developed to group neighboring faces together and thus space labels can be shared within each group.
-This scheme saves much time for space label computation, which is often very time-consuming for conventional Boolean evaluation algorithms.
-Additionally, in order to be robust, plane-based geometry computation is introduced into the intersection computation step of our approach.
-Experiments have verified the proposed approach is more efficient than the state-of-the-art techniques while retaining robustness and stability.
-We will further investigate the robust tessellation in future.
-
-\appendices
-
-%\newpage
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,citation}
-
-%\newpage
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{rui}}]{Rui Wang}
-is currently a postgraduate student at the Department of Computer Science and Technology, the Shanghai Jiao Tong University.
-His main research interests include real-time computer graphics and virtual reality applications.
-\end{IEEEbiography}
-
-% if you will not have a photo at all:
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{xudong}}]{Xudong Jiang}
-received his Master degree in Computer Science from Shanghai Jiao Tong University in 2014.
-He is currently working in Autodesk China Research \& Development Center.
-His research interest includes computer-aided geometric design and solid modeling.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{hongbo}}]{Hongbu Fu}
-is an Associate Professor in the School of Creative Media, City University of Hong Kong.
-He received the PhD degree in computer science from the Hong Kong University of Science and Technology in 2007 and the BS degree in information sciences from Peking University, China, in 2002.
-His primary research interests fall in the fields of computer graphics and human computer interaction.
-He has served as an associate editor of The Visual Computer, Computers \& Graphics, and Computer Graphics Forum.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{sheng}}]{Bin Sheng}
-received his BS degree in computer science from Huazhong University of Science and Technology in 2004, MS degree in software engineering from University of Macau in 2007, and PhD Degree in computer science from The Chinese University of Hong Kong in 2011.
-He is currently an associate professor in the Department of Computer Science and Engineering at Shanghai Jiao Tong University.
-His research interests include virtual reality, computer graphics, and image-based techniques.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{wu}}]{Enhua Wu}
-received the BS degree from Tsinghua University in 1970, and the PhD degree from the University of Manchester (UK) in 1984.
-He is currently a research professor at the Institute of Software, Chinese Academy of Sciences, and Fellow of China Computer Federation.
-He has also been teaching at the University of Macau since 1997, where he is currently an Emeritus Professor.
-His research interests include realistic image synthesis, virtual reality, and scientific visualization.
-He has served as an associate editor of The Visual Computer, Computer Animation and Virtual Worlds.
-\end{IEEEbiography}
-
-\section{Proof of Indicator Equality}
+\vspace{0.5em}
+\noindent \textbf{Proof of Indicator Equality}
 \label{app:profind}
@@
 
+\section{Experiments}
+
+\section{Summary}
+
+In this paper, we proposed a novel method to evaluate CSG with triangular mesh primitives.
+It is able to efficiently perform non-incremental evaluation of large CSG with massive faces.
+The key idea of our approach is to use the local coherence of face space labels to accelerate face membership classification.
+A two-level grouping framework is developed to group neighboring faces together and thus space labels can be shared within each group.
+This scheme saves much time for space label computation, which is often very time-consuming for conventional Boolean evaluation algorithms.
+Additionally, in order to be robust, plane-based geometry computation is introduced into the intersection computation step of our approach.
+Experiments have verified the proposed approach is more efficient than the state-of-the-art techniques while retaining robustness and stability.
+We will further investigate the robust tessellation in future.
+
+\appendices
+
+%\newpage
+\bibliographystyle{IEEEtran}
+\bibliography{IEEEabrv,citation}
+
+%\newpage
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{rui}}]{Rui Wang}
+is currently a postgraduate student at the Department of Computer Science and Technology, the Shanghai Jiao Tong University.
+His main research interests include real-time computer graphics and virtual reality applications.
+\end{IEEEbiography}
+
+% if you will not have a photo at all:
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{xudong}}]{Xudong Jiang}
+received his Master degree in Computer Science from Shanghai Jiao Tong University in 2014.
+He is currently working in Autodesk China Research \& Development Center.
+His research interest includes computer-aided geometric design and solid modeling.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{hongbo}}]{Hongbu Fu}
+is an Associate Professor in the School of Creative Media, City University of Hong Kong.
+He received the PhD degree in computer science from the Hong Kong University of Science and Technology in 2007 and the BS degree in information sciences from Peking University, China, in 2002.
+His primary research interests fall in the fields of computer graphics and human computer interaction.
+He has served as an associate editor of The Visual Computer, Computers \& Graphics, and Computer Graphics Forum.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{sheng}}]{Bin Sheng}
+received his BS degree in computer science from Huazhong University of Science and Technology in 2004, MS degree in software engineering from University of Macau in 2007, and PhD Degree in computer science from The Chinese University of Hong Kong in 2011.
+He is currently an associate professor in the Department of Computer Science and Engineering at Shanghai Jiao Tong University.
+His research interests include virtual reality, computer graphics, and image-based techniques.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{wu}}]{Enhua Wu}
+received the BS degree from Tsinghua University in 1970, and the PhD degree from the University of Manchester (UK) in 1984.
+He is currently a research professor at the Institute of Software, Chinese Academy of Sciences, and Fellow of China Computer Federation.
+He has also been teaching at the University of Macau since 1997, where he is currently an Emeritus Professor.
+His research interests include realistic image synthesis, virtual reality, and scientific visualization.
+He has served as an associate editor of The Visual Computer, Computer Animation and Virtual Worlds.
+\end{IEEEbiography}
+
 \end{document}

### 2016-09-29 summary.tex
done with $7

@@
 Each time an intersection is computed, two intersections are generated (one for each triangle) and the newly generated vertices are added into meshes.
-To avoid repetitive vertices in the final result, we perform vertex repetition elimination in this stage, merging coincident vertices even among different input meshes.
+To avoid repetitive vertices in the final result, we perform vertex repetition elimination in this stage, merging coincident vertices even if they come from different input meshes.
 Because we use P-reps, the comparison of vertices is exact.
@@
 This is done by tracing loops on tess-graph.
-A valid loop that corresponds to a subface must satisfy two criterions: 1) the direction of loops should be coherent with the face normal, and 2) consecutive connections on the loop should be adjacent by circular order {\color{red}{Fig.?}}.
-After we find out all valid loops on tess-graph, the tessellation is done on that triangle face.
-More details are discussed in \S\ref{sec:}.
+A valid loop that corresponds to a subface must satisfy two criterions: 1) the direction of loops should be coherent with the face normal, and 2) consecutive connections on the loop should be adjacent by circular order ({\color{red}{Fig.?}}).
+After we find out all valid loops on tess-graph, we finish tessellating the corresponding face.
+
+When all faces are tessellated, meshes are intersection-free.
+We further attach the PBI-reps of intersections to the edges generated from tess-graph connections which corresponds to an intersection.
+Finally, we get the intersection-free hybrid meshes, while `hybrid` means some parts of meshes are both vertex-based and plane-based represented.
 
@@
 
-\section{Face Classification, p->e->f, patial sort}
+\section{Exact Face Classification}
 
 \label{sec:classification}
-This stage traverses all candidate faces in the Linked Halfedge, and classifies which of them belong to the final mesh.
-Classification is done by evaluating the indicator vector of each face {\color{red}{(indicator vector?)}}.
-During this process, we take advantage of P-rep to ensure unconditional correct classification.
-In addition, since we maintain the intra-primitive geometry connectivity and inter-primitive geometry connectivity in Linked Halfedge, we can utilize the space coherence of face indicator vectors to accelerate this process.
-
-In this section, we will first give an overall framework of face classification, and then introduce how to classify each individual face.
-At last, we discuss how to accelerate this process by caching intermediate results.
+We traverse each face in the hybrid meshes, and classify which one belongs to the final mesh.
+Classification is done by evaluating the indicator vector of each face.
+The basic idea of our classification method is to utilize the space coherence of face indicator vectors to reuse the classification results.
+Also, because we store the PBI-reps which contains neighborhood information in the edges which intersect other meshes, the search space of point-in-polyhedron test is limited to only a few faces, which makes the indicator computation very fast.
+Also, by using P-reps, our classification method can deal with any degenerate cases.
 
@@
 The space coherence of indicator vectors means neighboring faces could share the same indicator vector, or most components of indicator vectors.
-For example, given two neighboring faces $t_1$ and $t_2$, indicator vectors $\boldsymbol{\Lambda}(t_1)$ and $\boldsymbol{\Lambda}(t_2)$ would often be the same.
-Only when there is boundary of some meshes, say $P_k$, on the shared edge $e(t_1, t_2)$ and split $t_1$ and $t_2$ in two sides, the corresponding components $\boldsymbol{\Lambda}(t_1, P_k)$ and $\boldsymbol{\Lambda}(t_2, P_k)$ can be different.
-And other components of $\boldsymbol{\Lambda}(t_1)$ and $\boldsymbol{\Lambda}(t_2)$ will remain the same.
-If we can compute the indicator changes between neighboring faces efficiently, we can start from a single face with a indicator vector as the seed, propagating to all faces with geometry connectivity, reusing indicator vectors according to the spatial coherence and classifying faces very fast.
-
-Fortunately, in the Linked Halfedge, it is straightforward to know whether $\boldsymbol{\Lambda}(t_1, P_k)$ and $\boldsymbol{\Lambda}(t_2, P_k)$ are different, because it means $e(t_1, t_2)$ will be on the boundary of $P_k$, and there will be corresponding I-reps stored on $e(t_1, t_2)$.
-In addition, both $\boldsymbol{\Lambda}(t_1, P_k)$ and $\boldsymbol{\Lambda}(t_2, P_k)$ can be computed efficiently according to the I-reps (details in Section \ref{sec:individual}).
-We outline our classification method in Algorithm 1.
+Therefore, we start from a seed face $s_0$ with its indicator vector $\bm{\Lambda}(s_0)$ known, and propagate to other faces in a flood-filling manner.
+The trace of indicator propagation is:
+\begin{equation}
+\label{eq:trace}
+s_0\to s_1\to s_2\to s_3\to ...
+\end{equation}
+
+Our hybrid meshes facilitate this process by accelerating the indicator propagation.
+Given adjacent faces $s_1$ and $s_2$, it is straightforward to know whether $\bm{\Lambda}(s_1)$ and $\bm{\Lambda}(s_2)$ are different.
+The two indicator vectors are the same unless the shared edge $e_{12}$ lies on the boundary of some meshes, and it means there is an intersection $\mathbb{I}(e_{12})$ stored on $e_{12}$.
+For a certain indicator $\lambda_k$, it always stands:
+\begin{equation}
+\label{eq:eq1}
+{\lambda_k}(s_1) = {\lambda_k}(s_2),\ \ \  \mbox{if }\Psi_k(\mathbb{I}(e_{12}))= 0.
+\end{equation}
+Even if $\Psi_k(\mathbb{I}(e_{12})) \neq 0$, both $\lambda_k(t_1)$ and $\lambda_k(t_2)$ can be computed efficiently and exactly according to $\mathbb{I}(e_{12})$ (\S\ref{sec:propagation}).
+We outline our classification method in Algorithm \ref{code:floodfill}.
 
@@
 \label{code:floodfill}
-\textbf{Input: } Linked Halfedge structure $\Omega$
-
-\textbf{Output: } Classification of each face $f(\boldsymbol{\Lambda}(t_i)), t_i \in \Omega$
+\textbf{Input: } IFH meshes $\bm{P'}$, a boolean function $f$
+
+\textbf{Output: } Classification $f(\bm{\Lambda}(s_i))$, for all faces $s_i$ from $\bm{P'}$
 
 \begin{algorithmic}[1]
-\State Select a proper seed face $t_s$
-\State Compute the first indicator vector $\boldsymbol{\Lambda}(t_s)$
-\State \Call{propagate} { $t_s$ , $\boldsymbol{\Lambda}(t_s)$}
+\State Select a proper seed face $s_0$
+\State Compute the first indicator vector $\boldsymbol{\Lambda}(s_0)$
+\State \Call{propagate} { $s_0$ , $\boldsymbol{\Lambda}(s_0)$}
 \State
-\Function{propagate}{ $t_c$ , $\boldsymbol{\Lambda}(t_c)$}
-    \State Compute $f(\boldsymbol{\Lambda}(t_c))$
-    \For {each neighboring face $t_i^c$}
-        \If {there are I-reps $\{{\mathbb{I}}_k\}$ on $e(t_i^c, t_c)$}
-            \State $\boldsymbol{\Lambda}(t_c), \{{\mathbb{I}}_k\} \Longrightarrow \boldsymbol{\Lambda}(t_i^c)$
-            \State \Call{propagate} { $t_i^c$ , $\boldsymbol{\Lambda}(t_i^c)$}
+\Function{propagate}{ $s$ , $\boldsymbol{\Lambda}(s)$}
+    \State Compute $f(\boldsymbol{\Lambda}(s))$
+    \For {each neighboring face $s_i$}
+        \If {$s_i$ has been classified}
+            \State continue
+        \EndIf
+        \If {there are PBI-reps $\{{\mathbb{I}}_k\}$ on $e(s_i, s)$}
+            \State compute $\boldsymbol{\Lambda}(s_i)$ by $\boldsymbol{\Lambda}(s)$ and $\{{\mathbb{I}}_k\}$
+            \State \Call{propagate} { $s_i$ , $\boldsymbol{\Lambda}(s_i)$}
         \Else
-            \State \Call{propagate} { $t_i^c$ , $\boldsymbol{\Lambda}(t_c)$}
+            \State \Call{propagate} { $s_i$ , $\boldsymbol{\Lambda}(s)$}
         \EndIf
@@
 
+\iffalse
 \subsection{Precise Seed Generation}
@@
 
-\subsection{Fast and Exact Classification}
+\fi
+
+\subsection{Indicator Propagation}
+\label{sec:propagation}
+Now, our meshes consist of vertices, edges and faces.
+Classification is required to perform on face level.
+However, polyhedron in-out test is performed based on points.
+Conventionally, face inner point such as barycenter is used to compute the indicator of the whole face.
+This is because in intersection-free meshes, face is classified as a whole, and every inner point will have the same indicator as the face's.
+However, the coordinates of inner points cannot be exactly represented by float point numbers, which may lead to wrong predicates, especially when the face lies on the surface of other mesh (Fig.
+x).
+Therefore, we use the vertices, whose exact representations are known, for indicator computation.
+
+%For example, given a face $s$ and one of its vertex $v^i(s)$, if $\lambda_k(v^i(s))=on$, $\lambda_k(s)$ can be any of $on$, $in$ or $out$ (see {\color{red}{Fig. ?}})
+However, there are two gaps between face indicator and vertex indicator.
+First, the indicator of vertex does not always equal to indicator of face.
+Second, face indicator has two conditions in $on$ case, $same$ and $oppo$, because the face has its orientation.
+
+To solve these problems, we discuss our indicator trace (\ref{eq:trace}) in finer granularity.
+In the beginning, we start from a seed vertex $v_0$ on seed face $s_0$.
+We assume indicator vector $\bm{\Lambda}(v_0)$ is known.
+Then we use $\bm{\Lambda}(v_0)$ to compute $\bm{\Lambda}(s_0)$.
+In addition, we add the edge layer into the trace.
+Then it changes to:
+\begin{equation}
+v_0\to e_0\to s_0\to e_1\to s_1\to e_2\to s_2\to ...
+\end{equation}
+, where $v, e$ means vertex and edge respectively.
+We find that there are three kinds of basic operations in the trace: $v_e\to e$, $e_s\to s$ and $s\to e_s$, where $v_e$ means the vertex is the end point of $e$, and $e_s$ means the edge is the edge of $s$.
+
+Given the partial order $on \succ in$ and $on \succ out$, our key observation is that the following relation always stands for indicators:
+\begin{equation}
+\label{eq:porder}
+\lambda_k(v_{e_s}) \succeq \lambda_k(e_s) \succeq \lambda_k(s)
+\end{equation}
+, where $\lambda_k(x)$ means the indicator of $x$ against a certain primitive $P_k$.
+This relation can be inferred from continuous space assumption and the definition of intersection-free mesh (def.
+\ref{eq:ifmdef}).
+It tells us when we perform $v_e\to e$ and $e_s\to s$, we decide whether the $on$ indicator change to $in$ or $out$ or remain $on$.
+When we perform $s\to e_s$, we decide whether $in$ and $out$ indicators change to $on$.
+In addition, considering the orientation of face, we also need to figure out whether the $on$ indicators change to $same$ or $oppo$ during $e_s\to s$ operation.
+
+\vspace{0.5em}
+\noindent\textbf{$\bm{s\to e_s}$}~~~~ When $\lambda_k(e_s)=on$, there will be PBI-rep $\mathbb{I}(e_s)$ attached to $e_s$ and the related neighborhood $\Psi_k(\mathbb{I}(e_s))$ must be nonzero, since it is on the surface of mesh $P_k$:
+\begin{equation}
+\label{eq:eq1}
+\lambda_k(e_s)=on,\ \ \  \mbox{iff. }\Psi_k(\mathbb{I}(e_s))\neq 0.
+\end{equation}
+So all we need is to iterate over all nonzero components of $\bm{\Psi}(\mathbb{I}(e_s))$ and change corresponding indicators to $on$.
+
+\vspace{0.5em}
+\noindent\textbf{$\bm{e_s\to s}$}~~~~From eq.
+\ref{eq:porder}, we know if $\lambda_k(e_s) \neq on$, then $\lambda_k(e_s)=\lambda_k(s)$.
+When $\lambda_k(e_s) = on$, we figure out $\lambda_k(s)$ using $\Psi_k(\mathbb{I}(e_s))$.
+From eq.
+\ref{eq:eq1}, we know $\Psi_k(\mathbb{I}(e_s)) \neq 0$ and can be either a triangle face or an edge.
+If $\Psi_k(\mathbb{I}(e_s))$ is a face, we can build a trivial BSP \cite{thibault1987set} using the face on the space near $e_s$.
+If $\Psi_k(\mathbb{I}(e_s))$ is an edge, we can still build BSP using the opposite two faces along $e_s$.
+In both cases, the BSP can be used to compute $\lambda_k(s)$ if we can sample a point from $s$ that near $e_s$.
+Unfortunately, we cannot guarantee to find such a point with precise coordinates.
+Instead, we choose a point $v_x$ from the half plane $\bm{p}_{s, s}^+$, which is on the supporting plane of $s$ and on the positive side of bounding plane $\bm{p}_{s, b}^{e_s}$ (Fig.
+x).
+There is at least one such $v_x$ among the vertices of $s$.
+We find that the BSP is so simple that indicators of all points on $\bm{p}_{s, s}^+$ are the same.
+Thus we can compute $\lambda_k(s)$ by figuring out $\lambda_k(v_x)$.
+Also, if we assign each BSP splitting plane a normal by the normal of triangle it contains, we can use it to decide the orientation ($same$ or $oppo$) when $v_x$ is on a splitting plane, which means $\lambda_k(s)=on$.
+
+\vspace{0.5em}
+\noindent\textbf{$\bm{v_e\to e}$}~~~~ While this is yet another propagation from low dimension to high dimension, there is no auxiliary information stored on vertex.
+If $\lambda_k(v_e)=on$, we first check whether $\lambda_k(e) = on$ by (\ref{eq:eq1}).
+If not, we need to find where $v_e$ lies on the surface of $P_k$.
+It may be a vertex, an edge or a face.
+The same BSP trick as in ${e_s\to s}$ is applied and we use the other vertex of $e$ to be the sample point $v_x$.
+
+\vspace{0.5em}
+
+\iffalse
+\subsection{Implementation}
 
@@
 
+\fi
+
 \section{Implementation}
@@
 \noindent \textbf{Continuous operations.}
+
+\vspace{0.5em}
+\noindent \textbf{Valid loops}
 

### 2016-10-04 summary.tex
10.4

@@
 \usepackage{amsfonts}
+\usepackage{amssymb}
 % correct bad hyphenation here
@@
 
-\subsection{Plane-based Technique Embedding}
+\subsection{Plane-Based Intersection}
 
@@
 \subsection{Tessellation by Tess-Graph}
-
+\label{sec:tess}
 So far, intersections are only independent data that store the coordinates and neighbouring information.
@@
 After we have tess-graph, we tessellate face and extract subfaces according to it.
-This is done by tracing loops on tess-graph.
+This is done by extract valid loops on tess-graph.
 A valid loop that corresponds to a subface must satisfy two criterions: 1) the direction of loops should be coherent with the face normal, and 2) consecutive connections on the loop should be adjacent by circular order ({\color{red}{Fig.?}}).
+Each valid loop corresponds to a intersection-free face.
 After we find out all valid loops on tess-graph, we finish tessellating the corresponding face.
@@
 Unfortunately, we cannot guarantee to find such a point with precise coordinates.
-Instead, we choose a point $v_x$ from the half plane $\bm{p}_{s, s}^+$, which is on the supporting plane of $s$ and on the positive side of bounding plane $\bm{p}_{s, b}^{e_s}$ (Fig.
+Instead, we choose a point $v_x$ from the half plane $\bm{p}_{s, sp}^+$, which is on the supporting plane of $s$ and on the positive side of bounding plane $\bm{p}_{s, b}^{e_s}$ (Fig.
 x).
-There is at least one such $v_x$ among the vertices of $s$.
-We find that the BSP is so simple that indicators of all points on $\bm{p}_{s, s}^+$ are the same.
-Thus we can compute $\lambda_k(s)$ by figuring out $\lambda_k(v_x)$.
+For polygons, there is at least one such $v_x$ among the vertices of $s$.
+We find that the BSP is so simple that indicators $\lambda_k$ of all points on $\bm{p}_{s, sp}^+$ are the same.
+Since $\bm{p}_{s, sp}^+ \cap s \neq \varnothing$, we can compute $\lambda_k(s)$ by figuring out $\lambda_k(v_x)$.
 Also, if we assign each BSP splitting plane a normal by the normal of triangle it contains, we can use it to decide the orientation ($same$ or $oppo$) when $v_x$ is on a splitting plane, which means $\lambda_k(s)=on$.
@@
 \vspace{0.5em}
-\noindent\textbf{$\bm{v_e\to e}$}~~~~ While this is yet another propagation from low dimension to high dimension, there is no auxiliary information stored on vertex.
+\noindent\textbf{$\bm{v_e\to e}$}~~~~ While this is yet another propagation from low dimension to high dimension, there is no neighborhood information stored on vertex.
 If $\lambda_k(v_e)=on$, we first check whether $\lambda_k(e) = on$ by (\ref{eq:eq1}).
-If not, we need to find where $v_e$ lies on the surface of $P_k$.
-It may be a vertex, an edge or a face.
-The same BSP trick as in ${e_s\to s}$ is applied and we use the other vertex of $e$ to be the sample point $v_x$.
-
-\vspace{0.5em}
+If not, we need to find where $v_e$ lies on the surface of $P_k$ and determine the neighborhood of $v_e$.
+In most cases, it is straightforward since coincident vertices among different intersection-free meshes are shared.
+Exceptions are discussion is in \S\ref{sec:esubroutine}.
+The neighborhood may be a vertex, an edge or a face.
+After computing the neighborhood, the same BSP-based classification method is used as in ${e_s\to s}$ to determine the high dimensional $\lambda_k(e)$.
+We use the other vertex of $e$ to be the sample point $v_x$ for the BSP classification.
 
@@
 
-\section{Implementation}
-
-\vspace{0.5em}
-\textbf{Seed Indicator Vector Generation.} Our method of generating the first indicator vector will fail on extreme conditions when all faces in Linked halfedge are coincident with more than one primitive face (e.g., the union of the same mesh).
+\section{Discussion}
+
+\vspace{0.5em}
+
+\subsection{Essential Subroutines}
+\label{sec:esubroutine}
+
+\vspace{0.5em}
+\noindent\textbf{Searching valid loops}~~~~ In \S\ref{sec:tess}, we claim a valid loops on tess-graph has to be correct with its orientation.
+However, since tess-graph is undirectional, it is not easy to check whether a loop orientation agrees with the face's.
+We observe that the graph connections lie on face edges have their unambiguous directions (Fig.
+x).
+Starting from these edges, we can guarantee that the loops have the right orientations.
+After we find a valid loop, more graph connections will have unambiguous directions because one connection can participate two valid loops at most.
+In such way, the correct orientation will propagate in a flood-filling way.
+
+\vspace{0.5em}\noindent There is another problem that the tess-graph may not be a connected graph.
+We avoid this problem by inserting fake-intersections into the tess-graph.
+An fake intersection links the vertex of face (on the outer connected component) with the vertex on the inner connected component.
+The intersection refinement has to be performed again if the fake intersections cross any other intersections.
+To guarantee the fake intersection has a valid PBI-rep, we require the vertex from inner connected component generated by edge-face intersection, which means it is introduced during triangle-triangle intersection test.
+In this way, we can find an exact plane with the fake intersection on it (Fig.
+x).
+
+\vspace{0.5em}
+\noindent\textbf{Seed indicator generation}~~~~In \S\ref{sec:propagation}, we claim that our flood-filling starts from a seed vertex $v_0$.
+While the indicator vector of the seed $\bm{\Lambda}(v_0)$ can be generated by point-in-polyhedron test \cite{ogayar2005point} with the octree as acceleration structure \cite{frisken2002simple}, we have simpler strategies by using vertex with known indicators as the seed.
+We choose the `peak vertex` with the max x coordinate as the seed.
+In this way, $\lambda_k(v_0)$ is either $out$ ($in$, if complement is applied on mesh) or $on$.
+The $on$ indicators are easy to determine in most time.
+Though sometimes exception occur because of multi-coplanar situation, this will not happen if we carefully choose the right peak vertex whose neighbor faces are not coplanar (Fig.
+x).
+
+\vspace{0.5em}\noindent The indicator vectors can propagate not only among single meshes, but can also between different meshes by the vertices and edges they share.
+Therefore in most time, we only need one single seed vertex for classification.
+However, if there are lonely meshes that do not intersect with other meshes, we need to new seeds.
+The indicators of the second and later seeds can only be computed by point-in-polyhedron tests.
+
+%Our method of generating the first indicator vector will fail on extreme conditions when all faces in Linked halfedge are coincident with more than one primitive face (e.g., the union of the same mesh).
 In order to be robust, we use the high-precision face barycenter with the point-in-polyhedron test to generate the seed indicator vector instead after several failures of choosing a proper seed face.
 
-\vspace{0.5em}
-\noindent \textbf{Exact Face Classification.} In Linked halfedge, all the supporting planes of faces and all the vertices can be exactly represented.
-Based on that, when computing the new indicator according to I-reps, we can use BSP techniques similar to \cite{bernstein2009fast} to conduct robust predicates.
-Since the intersection context is neither face or edge, the space division planes in each BSP will be no more than two, which guarantees fast construction and classification.
-
-\vspace{0.5em}
-\noindent \textbf{Continuous operations.}
-
-\vspace{0.5em}
-\noindent \textbf{Valid loops}
-
-\vspace{0.5em}
-\noindent \textbf{Parallel.}
-
-\vspace{0.5em}
-\noindent \textbf{Lazy intersection.}
-
-\vspace{0.5em}
-\noindent \textbf{Caching Evaluation Results}
-If the CSG tree is large, with hundreds of primitive nodes, computing $\lambda_f(x)$ from $\boldsymbol{\Lambda}(x)$ for every face can be costly.
-Thanks to the space coherence of $\boldsymbol{\Lambda}(x)$, we can save the computation time by caching the evaluation result of Boolean operations.
-
-The basic cache strategy is to cache final result, that is, the value of $\lambda_f(x)$.
-We know indicator vector $\boldsymbol{\Lambda}$ will not change if there is no intersections during spreading.
-That means the final classification $\lambda_f(x)$ will not change, too.
-Thus, those faces sharing the same $\boldsymbol{\Lambda}$ can be classified as a whole.
-
-Also, we can perform intermediate results cache.
-We noticed that the Boolean expression can be simplified if some components of $\boldsymbol{\Lambda}(x)$ is fixed.
-For example, assume we have a Boolean expression $P_1\cup (P_2\cap P_3-P_4)$.
-Given the values of two indicators $\lambda_1(x)=out$, $\lambda_2(x)=in$, the expression can be rewritten as $out\cup (in\cap P_3-P_4)$.
-Using the combination rules we can simplify the expression as $P_3-P_4$.
-This fact is important because for a large CSG, a certain primitive, denoted as $P_x$, often only intersects with a few other primitives, like, $\Theta(P_x)= \{P_{n_1}, P_{n_2}, \cdots, P_{n_k}\}$.
-That means all the faces in $P_x$ has the same indicators for the primitives not in $\Theta(P_x)$.
-Therefore, we can first determine these fixed indicators and simplify the Boolean function, and then use simplified one to compute the final indicator for each faces in $P_x$.
-
-\vspace{0.5em}
-\noindent \textbf{Proof of Indicator Equality}
-\label{app:profind}
-
-Using the notation in section \ref{sec:individual}, we prove the equality of $\lambda(v_{x'}(t_i), P_j)$ and $ \lambda(v_b^2(t_i), P_j)$ under the space division $\boldsymbol{D}(C_{P_h \backslash P_j})$.
+\iffalse
+
+\subsection{Robustness}
+
+\vspace{0.5em}
+\noindent\textbf{Indicator up-propagation}~~~~
+In \S\ref{sec:propagation}, we point out that up-propagation (from low dimension to high dimension, $v_e\to e$ and $e_s\to s$, etc.) can be done by using sample points.
+Here we give use a heuristic method to prove our claim in $e_s\to s$.
+Extension to $v_e\to e$ should not take much effort.
+
+\vspace{0.5em}\noindent We prove $\lambda_k(v_x)=\lambda_k(v_{\delta})$ in the BSP of $e_s$'s neighborhood, where $ v_x$ is the sample point from $\bm{p}_{s, sp}^+$ and $v_{\delta}$ is from the neighborhood $U(e_s, \delta)$.
+If $\lambda_k(v_x) \neq on$, then
 
@@
 
+\vspace{0.5em}
+\noindent\textbf{Proof of Robustness}
+
+\fi
+
+\subsection{Extensions}
+
+\vspace{0.5em}
+\noindent\textbf{Converting to float-point number}~~~~
+The vertices of final mesh in our method are represented in both P-reps and plain coordinates.
+While the vertices from the input meshes have there exact coordinates, the vertices newly introduced by intersection between meshes require round-off when converting to coordinates representation.
+Though we guarantee the correct topology in the result mesh, such round-off can still cause topology deficiencies such as self-intersections.
+Here we adopt Zhou et al.'s method \cite{zhou2016mesh} to solve it iteratively.
+
+\vspace{0.5em}
+\noindent\textbf{Incremental evaluation}~~~~While we claim in many CSGs, a non-incremental evaluation is faster by avoiding repetitive computation, one can easily find counter-examples that non-incremental evaluation contains useless intersection computation.
+For example, if 100 spheres densely locate in a small region, each sphere will need to intersect with other 99 spheres.
+However, if evaluating incrementally, we do not need computing so many intersections.
+Fortunately, our method can also perform incremental evaluation.
+For exactness and robustness, we have to deal with non-triangle input meshes in incremental evaluations and intersection vertices should not be converted to float-point.
+
+\vspace{0.5em}
+\noindent\textbf{Extending to polygon meshes}~~~~
+In our method, we claim the inputs are triangle meshes mainly to avoid plane fitting when converting to P-reps.
+However, if we assume the P-reps of non-triangle faces are exactly known, our method can be easily extend to polygon meshes.
+
+\vspace{0.5em}\noindent The only different part is intersection computation.
+The first step of M\''{o}ller's triangle-triangle intersection method is to test each edge-plane pair respectively.
+This idea can be transferred to polygon intersections without any change.
+Then we can get two plane-face intersections $Seg1$ and $Seg2$, except that in polygon cases, $Seg1$ and $Seg2$ are two sets of line segments, not single segments.
+And the later processes are the same.
+
+\vspace{0.5em}
+\noindent\textbf{Classification acceleration}~~~~If the CSG tree is large with hundreds of primitive nodes, computing $\lambda_f(s_x)$ from $\boldsymbol{\Lambda}(s_x)$ for every face $s_x$ can be costly.
+Thanks to the indicator space coherence, we can save the computation time by caching the evaluation result $f(\boldsymbol{\Lambda}(s_x))$ during flood-filling.
+
+The basic cache strategy is to cache final result, that is, the value of $\lambda_f(s_x)$.
+We know indicator vector will not change if there is no intersections during propagation.
+That means the final classification $\lambda_f(s_x)$ will not change, too.
+Thus, those faces sharing the same indicator vector can be classified as a whole.
+
+Also, we can perform intermediate results cache.
+We noticed that the boolean expression can be simplified if some components of $\boldsymbol{\Lambda}(s_x)$ is fixed.
+For example, assume we have a boolean expression $f = P_1\cup (P_2\cap P_3-P_4)$.
+Given the values of two indicators $\lambda_1(s_x)=out$, $\lambda_2(s_x)=in$, the expression can be rewritten as $f(\lambda_1=out, \lambda_2=in)=out\cup (in\cap P_3-P_4)$.
+Using the combination rules we can simplify the expression as $f(\lambda_1=out, \lambda_2=in)=P_3-P_4$.
+This fact is important because for a large CSG, a certain primitive (denoted as $P_k$) often only intersects with a few other primitives $\Theta(P_k)= \{P_{n_1}, P_{n_2}, \cdots, P_{n_k}\}$.
+That means all the faces in $P_k$ has the same indicators $\lambda_{i}, P_{i} \notin \Theta(P_k)$.
+Therefore, we can first determine these fixed indicators and simplify the boolean function, and then use simplified one to compute the final indicator for each faces in $P_k$.
+
+\iffalse
+\vspace{0.5em}
+\noindent\textbf{Lazy intersection}~~~~
+Another way to avoid useless intersection computation is to use lazy intersection technique
+\fi
+
 \section{Experiments}

### 2016-10-04 summary.tex
10.5

@@
 \begin{abstract}
-  Constructive solid geometry is widely used for computer aided design and manufacturing.
-However, boolean operations, which compute the boundary representation of constructive solid geometry, have been suffered from robustness and efficiency problem for more than three decades.
-In this paper, we propose a fast and exact boolean operation approach which is theoretically robust for valid triangle mesh inputs.
-This is done by introducing plane-based geometry into boolean operations and strictly follow the principle of no constructions during processing.
-Different from previous BSP-based method, our method works on halfedge, with only one-time conversion to the plane representation in intersection areas, instead of a series of complex conversions between different representations.
+  Constructive solid geometry (CSG) is widely used for computer aided design and manufacturing.
+However, boolean operations, which compute the boundary representation of CSG, have been suffered from robustness and efficiency problem for more than three decades.
+In this paper, we propose a fast and exact boolean operation approach which is theoretically robust for regular meshes.
+This is done by introducing plane-based geometry into boolean operations and strictly follow the principle of no geometry constructions during processing.
+Different from previous BSP-based methods, our method is with only one-time conversion to the plane representation in intersection areas, instead of a series of complex conversions between different representations.
 Also, by using geometry connectivity and space neighboring information, our method reuse the computation iteratively, saving much computation time.
-Comparison experiments with state-of-the-art techniques show that our method is unconditionally exact and robust, while is competitively efficient with non-robust methods and much faster than exact, robust ones.
+Comparison experiments with state-of-the-art techniques show that our method is unconditionally exact and robust, while is competitively efficient with non-robust methods and much faster than the robust ones.
 \end{abstract}
@@
 However, none of the solution is good enough.
-While exact-arithmetic based methods are significantly slower, workarounds are often case dependent and not reliable for complex CSGs.
+While methods using exact arithmetic are significantly slower, workarounds are often case dependent and not reliable for complex CSGs.
 
 We develop an unconditionally robust and exact boolean operation method for triangle meshes without using exact arithmetic.
-The robustness of our method is based on the observations by Sugihara and Iri \cite{sugihara1990solid} that boolean operations can be performed requiring geometry constructions if representations are based on planes and not vertices.
+The robustness of our method is based on the observations by Sugihara and Iri \cite{sugihara1990solid} that boolean operations can be performed requiring geometry constructions if representations are based on planes.
 This idea of using plane-based representation (P-rep) has been developed by Berstein and Fussell \cite{bernstein2009fast} by combining it with binary search partition (BSP) techniques \cite{naylor1990merging,thibault1987set}.
@@
 
-We adopt plane-based techniques and strictly follow the principle of no geometry construction, yet develop a very different framework based on halfedges, requiring only one-time conversion to the plane representation in intersection areas.
-Since the geometry connectivity is stored in halfedge, it allow us to take advantage of geometry connectivity for classification acceleration \cite{feito2013fast,ogayar2015deferred,updegrove2016boolean}, which is hard to for a BSP-based method.
-In addition, our method can perform boolean operations with more than two primitives in one call, instead of recursively doing binary boolean operations.
-In this way, extra complexity is introduced.
-But we can save much computation time by avoiding repetitive computation.
-The major difficulty of applying P-rep on halfedge is by the incoherence between the two representations.
-Halfedge is a vertex-based representation.
-Many geometry operations (e.g., coordinates projection and compute the barycenter coordinate of triangle) available on halfedge can be very complex and thus inefficient under P-rep.
-On the other hand, we have to compute under P-rep for exactness and robustness.
-Therefore, we manage to limit our computation of boolean operations to several basic plane-based predicates.
-The experiment shows that our method is much faster than Campen et.
-al.'s method, while only about two to three times slower than the state-of-art non-robust method \cite{douze2015quickcsg}.
+We develop a boolean operation method based on vertex-based representation of mesh (e.g., halfedge) and embed plane-based techniques into it, requiring only one-time conversion to the plane representation in intersection areas.
+It allows us to take advantage of geometry connectivity for classification acceleration \cite{feito2013fast,ogayar2015deferred,updegrove2016boolean}, which is hard for BSP-based methods.
+In addition, our method can perform boolean operations with more than two primitives in one call, instead of recursively doing incremental boolean operations.
+Despite of extra complexity, non-incremental boolean operation may save much computation time by avoiding repetitive computation.
+The major difficulty of embed P-rep on vertex-based representation is by the incoherence between the two representations.
+Many geometry operations (e.g., coordinates projection and compute the barycenter coordinate of triangle) available on vertex-based representations can be very complex and thus inefficient under P-rep.
+On the other hand, we have to compute all under P-rep for exactness and robustness.
+Therefore, we manage to limit our computation of boolean operations to several basic plane-based geometry predicates.
+The experiment shows that our method is much faster than exact, robust methods, while only about two to three times slower than the state-of-art non-robust method \cite{douze2015quickcsg}.
 

### 2016-10-10 summary.tex
10.10

@@
 
-We develop a boolean operation method based on vertex-based representation of mesh (e.g., halfedge) and embed plane-based techniques into it, requiring only one-time conversion to the plane representation in intersection areas.
-It allows us to take advantage of geometry connectivity for classification acceleration \cite{feito2013fast,ogayar2015deferred,updegrove2016boolean}, which is hard for BSP-based methods.
+We develop a boolean operation method based on B-reps of meshes with geometry connectivity (e.g., halfedge).
+We further embed P-rep of faces into the B-rep, forming a hybrid representation, which allows us to take the advantage of both representations.
+This hybrid representation is fast that requires only one-time conversion to the P-rep in intersection areas of meshes.
+%that allows us to take advantage of geometry connectivity for classification acceleration \cite{feito2013fast,ogayar2015deferred,updegrove2016boolean}, which is hard for BSP-based methods.
 In addition, our method can perform boolean operations with more than two primitives in one call, instead of recursively doing incremental boolean operations.
 Despite of extra complexity, non-incremental boolean operation may save much computation time by avoiding repetitive computation.
-The major difficulty of embed P-rep on vertex-based representation is by the incoherence between the two representations.
-Many geometry operations (e.g., coordinates projection and compute the barycenter coordinate of triangle) available on vertex-based representations can be very complex and thus inefficient under P-rep.
-On the other hand, we have to compute all under P-rep for exactness and robustness.
-Therefore, we manage to limit our computation of boolean operations to several basic plane-based geometry predicates.
+The major difficulty of embed P-rep into B-rep is caused by the incoherence between the two representations.
+Many geometry operations (e.g., coordinates projection and compute the barycenter coordinate of triangle) available on B-reps can be very complex and thus inefficient under P-rep.
+On the contrary, all computations have to be performed under P-rep for exactness and robustness.
+Therefore, we manage to constrain our computation to several basic plane-based geometry predicates.
 The experiment shows that our method is much faster than exact, robust methods, while only about two to three times slower than the state-of-art non-robust method \cite{douze2015quickcsg}.
@@
 
-Boolean operations have long been researched for over three decades since it inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}.
-Most previous work of boolean operations can be classified into two categories: exact and approximate methods.
+Boolean operations have been researched for over three decades since it inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}.
+Previous work of boolean operations can be classified into two categories: exact and approximate methods.
 Exact methods retain vertex positions.
@@
 The coordinates of intersection points between input meshes are computed by input configurations to construct the topology around intersection.
-However, the coordinates cannot be represented exactly using fix-precision float point numbers and the robustness is often a problem.
-Using exact arithmetic is too expensive in computing.
+However, the coordinates cannot be represented exactly using fix-precision float-point numbers and the robustness is often a problem.
+However, using exact arithmetic is too expensive in computing.
 Therefore, exact methods face the problem of the balance between performance and robustness.
@@
 For exact methods, some \cite{ogayar2015deferred,douze2015quickcsg,zhou2016mesh,xu2013fast,feito2013fast} pursues efficiency but cannot guarantee robustness in degenerate cases such as coplanar conditions.
-Most of them are implemented by fix-precision float-point arithmetic and round errors accumulation is often inevitable.
+Most of them are implemented by fix-precision float-point arithmetic and round errors accumulation is inevitable.
 Douze et al.
 \cite{douze2015quickcsg} implemented very efficient boolean operations that can handle very large meshes.
-Also, their method is able to perform variadic boolean operations: evaluating the final result mesh of CSG all at once instead of decomposing the CSG into a series of binary boolean operations.
-However, their method cannot deal with coplanar cases nor guarantee accuracy for common situations.
-On the contrary, CSGs with large meshes contain are more complex and more likely to contain degenerate cases.
+Also, their method is able to perform non-incremental boolean operations: evaluating the final result mesh of CSG all at once instead of decomposing the CSG into a series of incremental boolean operations.
+However, their method can neither deal with coplanar cases nor guarantee accuracy for common situations.
+On the contrary, CSGs with large number of faces contain are more complex and more likely to contain degenerate cases.
 Also, coplanar cases can regularly happens for man-made artifact modeling (Fig.

### 2016-10-10 summary.tex
10.10

@@
 \usepackage{amssymb}
+\usepackage{wrapfig}
 % correct bad hyphenation here
@@
 We develop an unconditionally robust and exact boolean operation method for triangle meshes without using exact arithmetic.
-The robustness of our method is based on the observations by Sugihara and Iri \cite{sugihara1990solid} that boolean operations can be performed requiring geometry constructions if representations are based on planes.
+The robustness of our method is based on the observations by Sugihara and Iri \cite{sugihara1990solid} that boolean operations can be performed without geometry constructions if representations are based on planes.
 This idea of using plane-based representation (P-rep) has been developed by Berstein and Fussell \cite{bernstein2009fast} by combining it with binary search partition (BSP) techniques \cite{naylor1990merging,thibault1987set}.
@@
 al.'s method still suffers from performance problem because of the complex conversions among B-reps, P-reps and BSP representations.
-Also, the incoherence between BSP representation, where boolean operations actually happens, and B-reps, which are input and output meshes, requires extra steps to connect the reconstructed intersection areas with the untouched meshes, leading to extra computation burden and complex topology.
-
-We develop a boolean operation method based on B-reps of meshes with geometry connectivity (e.g., halfedge).
-We further embed P-rep of faces into the B-rep, forming a hybrid representation, which allows us to take the advantage of both representations.
-This hybrid representation is fast that requires only one-time conversion to the P-rep in intersection areas of meshes.
+Also, the incoherence between BSP representation, where boolean operations actually happens, and B-reps, which are input and output meshes, requires extra steps to connect the reconstructed intersection areas with the unchanged areas, leading to extra computation burden and complex topology.
+
+We develop a boolean operation method based on B-reps of meshes with geometry connectivity (e.g., halfedge \cite{mcguire2000half}).
+Additionally, we embed P-rep of faces into the B-rep, forming a hybrid representation, which allows us to take the advantage of both representations for robustness and efficiency.
+This hybrid representation requires only one-time conversion from B-rep to P-rep in intersection areas of meshes.
 %that allows us to take advantage of geometry connectivity for classification acceleration \cite{feito2013fast,ogayar2015deferred,updegrove2016boolean}, which is hard for BSP-based methods.
-In addition, our method can perform boolean operations with more than two primitives in one call, instead of recursively doing incremental boolean operations.
+Moreover, our method can perform boolean operations with more than two primitives in one call, instead of recursively doing incremental boolean operations.
 Despite of extra complexity, non-incremental boolean operation may save much computation time by avoiding repetitive computation.
-The major difficulty of embed P-rep into B-rep is caused by the incoherence between the two representations.
-Many geometry operations (e.g., coordinates projection and compute the barycenter coordinate of triangle) available on B-reps can be very complex and thus inefficient under P-rep.
-On the contrary, all computations have to be performed under P-rep for exactness and robustness.
-Therefore, we manage to constrain our computation to several basic plane-based geometry predicates.
-The experiment shows that our method is much faster than exact, robust methods, while only about two to three times slower than the state-of-art non-robust method \cite{douze2015quickcsg}.
+The major difficulty of embedding P-rep into B-rep is the incoherence between the two representations.
+Many geometry operations (e.g., coordinates projection and compute the barycenter coordinate of triangle) available on B-rep can be very complex and thus inefficient on P-rep.
+On the contrary, all geometry predicates have to be performed under P-rep for exactness and robustness.
+We solve this problem by various methods to constrain the computation within plane-based geometry predicates.
+The experiments show that our method is much faster than existing robust exact methods, while only about two to three times slower than the state-of-art non-robust exact methods.
 
@@
 Boolean operations have been researched for over three decades since it inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}.
-Previous work of boolean operations can be classified into two categories: exact and approximate methods.
+Previous works of boolean operations can be classified into two categories: exact methods and approximate methods.
 Exact methods retain vertex positions.
-And the topology of the input meshes is also preserved as much as possible.
+Also the topology of the input meshes is preserved as much as possible.
 The coordinates of intersection points between input meshes are computed by input configurations to construct the topology around intersection.
-However, the coordinates cannot be represented exactly using fix-precision float-point numbers and the robustness is often a problem.
-However, using exact arithmetic is too expensive in computing.
-Therefore, exact methods face the problem of the balance between performance and robustness.
-On the other hand, approximate methods rediscretize the input mesh surfaces using techniques such as voxels, octrees and Layered Depth Images and can reach better performance and robustness.
+However, the coordinates cannot be represented exactly using fix-precision float-point numbers and the robustness is always a problem.
+On the other hand, approximate methods rediscretize the input mesh surfaces using techniques such as voxels, octrees and Layered Depth Images.
+They can reach better performance and robustness, but loss of geometry information and precision is inevitable.
 
@@
 
+\iffalse
 \begin{figure}[t]
@@
 \end{figure}
-
-For exact methods, some \cite{ogayar2015deferred,douze2015quickcsg,zhou2016mesh,xu2013fast,feito2013fast} pursues efficiency but cannot guarantee robustness in degenerate cases such as coplanar conditions.
-Most of them are implemented by fix-precision float-point arithmetic and round errors accumulation is inevitable.
+\fi
+
+For exact methods, some \cite{ogayar2015deferred,douze2015quickcsg,zhou2016mesh,xu2013fast,feito2013fast} pursues efficiency but cannot guarantee robustness in degenerate cases.
+Most of them are implemented by fix-precision float-point arithmetic and numerical errors are inevitable.
 Douze et al.
-\cite{douze2015quickcsg} implemented very efficient boolean operations that can handle very large meshes.
-Also, their method is able to perform non-incremental boolean operations: evaluating the final result mesh of CSG all at once instead of decomposing the CSG into a series of incremental boolean operations.
-However, their method can neither deal with coplanar cases nor guarantee accuracy for common situations.
-On the contrary, CSGs with large number of faces contain are more complex and more likely to contain degenerate cases.
-Also, coplanar cases can regularly happens for man-made artifact modeling (Fig.
-\ref{fig:coplanarexample}) and should not be treated as exceptions for boolean operation methods.
+\cite{douze2015quickcsg} implemented very efficient method that can handle very large meshes.
+Also, they can perform non-incremental boolean operations: evaluating the final result mesh of CSG all at once instead of decomposing the CSG into a series of incremental boolean operations.
+However, their method can neither deal with coplanar cases nor guarantee accuracy of topology.
+In fact, large CSGs are more complex and more likely to contain degenerate cases, and more vulnerable under numerical errors.
+Efficiency only is far from being practical.
+%Also, coplanar cases can regularly happens for man-made artifact modeling (Fig. \ref{fig:coplanarexample}) and should not be treated as exceptions for boolean operation methods.
 
 Many researchers have attempted to solve robustness issue for exact boolean operations using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}.
-These methods are often too expensive in computation time and memory to be practical for CSG with massive faces.
-For example,
-the current standard of robust exact boolean operations method is CGAL's \cite{cgal:hk-bonp3-15a} exact-arithmetic implementation \cite{granados2003boolean} of Nef polyhedra \cite{bieri1988elementary}.
+However, these methods are too expensive in computation time and memory to be practical for CSGs with massive faces.
+For example, the current standard of robust exact boolean operations method is CGAL's \cite{cgal:hk-bonp3-15a} exact-arithmetic implementation \cite{granados2003boolean} of Nef polyhedra \cite{bieri1988elementary}.
 It requires conversions between Nef polyhedra and input mesh data structures during evaluation and is more than 50 times slower than non-robust booleans \cite{bernstein2009fast}.
@@
 
-Since efficiency, accuracy and robustness seem unable to be obtained at the same time, starting from \cite{museth2002level}, some sacrifice accuracy for better efficiency and robustness.
+Since efficiency, accuracy and robustness are hard to be satisfied at the same time, starting from \cite{museth2002level}, some sacrifice accuracy for better efficiency and robustness.
 Most of such methods are based on conversion to volumetric representations.
-However, the quality of result mesh depends on the resolution of the volume grid and better quality requires higher resolution.
+However, the quality of result mesh depends on the resolution of the volume grid and better quality requires dramatically higher resolution.
 To accelerate this process, some try to reduce the complexity of the output mesh \cite{varadhan2004topology} and others try to preserve non-intersected areas of the input mesh to avoid redundant tessellation \cite{pavic2010hybrid,wang2011approximate,zhao2011parallel,hable2005blister,ogayar2006gpu}.
-Also, with the development of general-purpose computing on graphics processing units, many of them utilize the grand computation power of graphics hardware for boolean operations.
+Also, with the development of general-purpose computing on graphics processing units (GPGPU), many of them utilize the grand computation power of graphics hardware for boolean operations.
 These methods often have good performance and are suitable for interactive applications.
@@
 
-The concept of P-rep of polygonal meshes was first described by Sugihara and Iri \cite{sugihara1990solid}.
-Such representation provides important advantage that for boolean operations, no new primary geometry information has to be constructed to obtain the result polyhedron---it is composed of a subset of the planes of the input polyhedra.
+The concept of plane-based representation of polygonal meshes was first described by Sugihara and Iri \cite{sugihara1990solid}.
+P-rep provides important advantage that for boolean operations, no new primary geometry information has to be constructed to obtain the result polyhedron---it is composed of a subset of the planes of the input polyhedra.
 Berstein and Fussell \cite{bernstein2009fast} combined the P-rep with binary space partitioning (BSP) \cite{thibault1987set,naylor1990merging} to develop an unconditionally robust boolean operation method.
@@
 
-\section{Motivation and Overview}
+\section{Background and Overview}
 
 \label{sec:overview}
-Our method is designed for boolean operations on arbitrary number of triangle meshes.
-Input mesh primitives are required to be watertight and not self-intersecting, with manifold surface, represented by wide-used halfedges \cite{mcguire2000half}.
-Despite of so many constraints, our method is not sensitive to topology deficiencies and works well if deficiencies are not near the intersection areas between meshes.
-
-\subsection{Background \& Motiviation}
+Our method is designed for boolean operations on arbitrary number of regular triangle meshes \cite{requicha1985boolean}.
+Input meshes are required to be without self-intersecting, represented with B-reps with geometry connectivity (e.g., halfedge, winged-edge, etc.).
+Despite of these requirements, our method is not sensitive to topology deficiencies like holes and self-intersections and works correctly deficiencies are not near the intersection areas between meshes.
+
+\subsection{Background}
 \label{sec:paradigm}
 
-The boolean operation of triangle meshes is in essence a process of selection.
-In other words, given a boolean function, it reserves those primitive faces that pass the function and drop the others to generate the final mesh.
-Unfortunately, for B-reps primitives such as triangle mesh, not all the facets from the input primitives can be classified as a whole, since some of them intersect other primitives.
-Therefore, we need an extra step aiming at detecting the intersection between primitives and performing tessellation.
+The boolean operation of triangle meshes is in essence a process of face selection.
+Namely, given a boolean function, it reserves those primitive faces that pass the function and drop the others to generate the final mesh.
+Unfortunately, for B-rep meshes, not all the input faces can be classified as a whole, since only part of the faces belong to the final mesh.
+Therefore, we need an extra step aiming at detecting intersections between meshes and performing tessellation.
 Most of the boolean operation methods follow this two-step paradigm, which consists of intersection computation and face classification.
@@
 
-During the intersection computation, primitive facets are tested in pairs to compute their intersections.
+During the intersection computation, input faces are tested in pairs to compute their intersections.
 Each input meshes are tessellated according to the intersection results, making every face be either inside, outside or on the boundary of other primitives.
-The retessellated meshes are what we called \emph{non-intersected meshes}.
-Unfortunately, under fix-precision float-point arithmetic, intersection test is error-prone for two causes: first, there are a large amount of degenerate cases which are hard to be precisely classified; second, when there are intersections, new vertices are introduced into the geometry, whose coordinates cannot be exactly represented by float-point numbers.
-
-The second step, face classification, is to evaluate whether a given face $x$ belongs to the final geometry according to the n-primitive boolean function $f$ :
+The tessellated meshes are what we called \emph{intersection-free meshes}.
+Unfortunately, under fix-precision float-point arithmetic, intersection tests are error-prone: first, degenerate cases of intersection are hard to detect; second, when there are intersections, new vertices are introduced into the geometry, whose coordinates cannot be exactly represented by fix-precision float-point numbers.
+
+During face classification, we evaluate whether a given face $s$ belongs to the final geometry according to the n-primitive boolean function $f$ :
 \begin{equation}
-\lambda_f(x) = f(\boldsymbol{\Lambda}(x)) = f(\lambda_1(x), \lambda_2(x), \cdots, \lambda_n(x)).
+\lambda_f(s) = f(\boldsymbol{\Lambda}(s)) = f(\lambda_1(s), \lambda_2(s), \cdots, \lambda_n(s)).
 \end{equation}
-The parameter $\lambda_i(x)$ is space indicator with respect to primitive $P_i$.
-To classify a single face $x$, one has to know the space indicators with respect to all the primitives (or their vector representation $\boldsymbol{\Lambda}(x)$).
+The parameter $\lambda_i(s)$ is space indicator with respect to mesh $P_i$.
+To compute $\lambda_f(s)$ and classify $s$, one has to know the space indicators with respect to all the primitives (denoted as $\boldsymbol{\Lambda}(s)$).
 A space indicator has four conditions: completely inside (\emph{in}), completely outside (\emph{out}), on the boundary with consistent normals (\emph{same}) or opposite normals (\emph{oppo}).
-The rules of Boolean function evaluation by these indicators are described in \cite{douze2015quickcsg,feito2013fast}.
+The rules of boolean function evaluation are described in \cite{douze2015quickcsg,feito2013fast}.
 
@@
 \includegraphics[width=2.5in]{falseclass}
-\caption{{\color{red}{Sketch: False classification}}}
+\caption{In a 2D view, face $s$ is on the surface of mesh $P$.
+However, because we use barycenter $v_c(s)$ to compute the indicator  and the coordinates of $v_c(s)$ contain round-off error, we might falsely classify $s$ as outside of $P$.}
 \label{fig:falseclass}
@@
 
-Face classification also suffers from robustness and exactness problems.
+Face classification also suffers from robustness problems.
 Many methods classify face according to the indicators of its barycenter, which can be computed by point-in-polyhedron test \cite{feito2013fast,campen2010exact}.
-However, coordinates of barycenters cannot be exactly represented and have the potential to generate false classification (Fig.
+However, coordinates of barycenters cannot be exactly represented and could generate false classification (Fig.
 \ref{fig:falseclass}).
 In addition, for the large amount of faces and input meshes, many methods take the benefits of the local coherence of indicators, classifying neighboring faces together \cite{pavic2010hybrid,feito2013fast,ogayar2015deferred,zhou2016mesh}.
-While this does improve the performance, it can make the robustness problem worse because the false classification may be propagated to neighboring faces.
-
-We want to develop an exact boolean operation method based on the two-step paradigm, being unconditional robust and as fast as possible.
-Considering the analysis above, we think our method have to include the following features:
+Despite of the performance improvement, it can make the robustness problem worse because the false classification may propagate to neighboring faces.
+
+We develop an exact boolean operation method based on the two-step paradigm, being unconditional robust and as fast as possible. 
+\iffalse
+Our method includes the following features:
 \begin{itemize}
@@
 \end{itemize}
-
-For efficiency, the exactness and robustness should not rely on arbitrary precision arithmetic.
-Instead, we choose the plane-based techniques from \cite{campen2010exact}.
-However, as we discussed in section \ref{sec:pbrelated}, BSP structure does not support geometry connectivity query in nature, and we do not want fussy conversions between different representations.
-Therefore, we use halfedge instead as our major data structure and embed P-rep into it.
-
+\fi
+For efficiency, the robustness of method does not rely on arbitrary precision arithmetic.
+Instead, we apply the plane-based techniques from BSP-based method \cite{campen2010exact}.
+However, BSP structure does not support geometry connectivity query in nature, which is essential for classification acceleration.
+Also, we do not want complex conversions between different representations.
+Therefore, our method is based on B-rep and we embed P-rep into intersection areas to guarantee the robust geometry computations.
+
+\iffalse
 \subsection{Intersection-Free Hybrid Mesh}
@@
 
-\iffalse
 \begin{figure*}[!t]
@@
 \end{figure*}
-\fi
 
@@
 An edge of Linked Halfedge stores intersection context only if it is coincident with a certain intersection line segment between primitives.
-We will give the definition and usage of intersection context in details in section \ref{sec:ir}.
+We will give the definition and usage of intersection context in details in \S\ref{sec:ir}.
 
@@
 
+\fi
 \subsection{Method Overview}
 
-As illustrated in Fig. \ref{fig:overview}, we divide our methods into four steps as follows.
+There are generally four stages for our boolean method.
+The first three stages are to compute intersection, which can be seen as pre-processing, processing and post-processing.
+After that, the input meshes are tessellated into intersection-free meshes with hybrid representations.
+The last step is to classify each face and get the final result mesh of boolean operations.
 
@@
 
-This step is the preparation of intersection detection.
+\begin{wrapfigure}{r}[0in]{0in}
+\includegraphics[width=1.2in]{octreediff}
+\end{wrapfigure}
+
 As intersection detection is performed between each pair of faces, localization is necessary to filter invalid pairs beforehand.
-In general, any space division data structure can be applied in this step.
-We use the adaptive octree for its simplicity.
-Our implementation is akin to the implementation in \cite{ogayar2015deferred}.
-Intersection between triangle faces and octree leaves can be efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}.
+Many space division methods can be used in this step.
+We use the adaptive octree for its simplicity and efficiency.
+Our implementation is akin to the implementation in Ogayar et al.'s method \cite{ogayar2015deferred}.
+Intersection between triangle faces and octree leaves are efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}.
 Octree leaves are classified into two types: if all faces that intersect a leaf belong to the same primitive, we call it a \emph{normal cell}.
-Otherwise, it is a \emph{critical cell}, within which the following intersection detection is performed.
-
-The difference between our space division and Ogayar et al.'s is that we do not subdivide any normal cell no matter how many faces it contains.
-This is because subdividing normal cells benefits only the ray-casting point-in-polyhedron test  \cite{frisken2002simple}, which seldom uses in our method.
-This simplification can save much computing time, especially when intersections between primitives are not complex and located in small regions (e.g.
-Fig.
-\ref{fig:models}(x)).
-
-\subsubsection{Intersection detection}
-
-This step is to detect intersections between primitives in a robust and exact way.
-Our algorithm is largely based on vertex-based M\"{o}ller's algorithm \cite{moller1997fast}, which is very efficient to compute intersection between two triangles.
-However, naive implementation of M\"{o}ller's algorithm always incurs robustness issues.
-To avoid an unexpected failure caused by numeric errors, we integrate P-rep of polyhedra into M\"{o}ller's algorithm.
-All intersection vertices are represented using plane intersections to avoid geometry constructions.
-Also, we carefully identify all degenerate cases of triangle intersections, including point intersection, line intersection and coplanar intersection, and respectively discuss how to deal with each of them.
-Details are provided in Section \ref{section:isect}.
+Otherwise, it is a \emph{critical cell}, within which the following intersection computation is performed.
+
+The difference between our octree and Ogayar et al.'s is that we do not subdivide any normal cell no matter how many faces it contains.
+This is because subdividing normal cells benefits only the point-in-polyhedron test  \cite{frisken2002simple}, which seldom uses in our method.
+This simplification can save much computing time, especially when intersections between primitives are not complex and located in small regions.
+
+\subsubsection{Triangle-triangle intersection}
+
+Our triangle-triangle intersection test is largely based on M\"{o}ller's algorithm \cite{moller1997fast}, which is very efficient to compute intersection between two triangles.
+However, naive implementation of M\"{o}ller's algorithm using vertex-based geometry brings numerical errors.
+Therefore, we integrate P-rep into M\"{o}ller's algorithm.
+All intersection points and line segments are represented using plane intersections to avoid explicitly computing the coordinates.
+Also, we carefully deal with degenerate cases of triangle intersections, including point intersection, edge intersection and coplanar situation.
+Details are provided in \S\ref{section:isect}.
 
@@
 
-Once all intersections are detected, we need to tessellate the input primitives and construct the Linked Halfedges.
-In many methods like \cite{ogayar2015deferred}, constraint Delaunay triangulation (CDT) is applied to perform tessellation, since the intersections are naturally the constraints of CDT.
-However, for a CSG with more than two primitives, the intersection vertices may be generated by intersections of three faces from different primitives, which cannot be computed during by triangle-triangle intersections in the previous step.
-Intersection line segments may overlap or intersect with each other, and cannot be used for constraints of CDT directly.
-In addition, as our intersection vertices are represented exactly by planes, implementation of CDT are complex and inefficient, as most CDT methods were not designed to handle planes and requires explicit coordinates.
-Therefore, we design a structure suited for P-rep, called \emph{Tess-graph}, to guide the tessellation of each single face, and develop a very fast but exact method to construct Linked Halfedges from Tess-graphs.
-Details are shown in section \ref{sec:tessellation}.
-
-\subsubsection{Face classification}
-
-This step is to choose faces from the Linked Halfedges to generate the final mesh.
-Literally computing all the space indicators of each face is unacceptably slow for large CSG trees.
-We utilize the geometry connectivity to accelerate this process.
-This is based on the observation that indicators of faces are locally coherent.
-Many method uses barycenters of faces together with point-in-polyhedra test for face classification, which is not exact nor robust with fix-precision float-point coordinates.
-Douze et al.
-\cite{douze2015quickcsg} classifies faces using space indicators of vertices, but failed to deal with coplanar conditions because of coplanar leads to ambiguity in such configurations.
-Different from all above, we classify faces based on the classification results of exactly represented vertices, including input vertices and newly introduced intersection vertices, and carefully deal with coplanar conditions to ensure topology consistency.
-Details will be shown in section \ref{sec:classification}.
-
-\section{Plane-based Geometry}
+Once all intersections between triangles are detected, we need to tessellate the input meshes and construct the intersection-free meshes.
+In many methods like \cite{ogayar2015deferred}, constraint Delaunay triangulation (CDT) is applied to perform tessellation.
+However, for a CSG with more than two meshes, intersections may overlap or intersect with each other, and cannot be used for constraints of CDT directly.
+In addition, as our intersections are represented by planes, implementation of CDT are complex and inefficient, as most CDT algorithms (e.g.
+\cite{chew1989constrained}, \cite{de1992line}) is not designed to handle planes and requires explicit coordinates.
+Therefore, we first perform intersection refinement to resolve intersecting intersections.
+After that, we construct a graph-like structure suitable for P-rep intersections, called \emph{tess-graph}, to guide the exact tessellation of each face.
+After all faces are tessellated, we get our intersection-free hybrid meshes, where 'hybrid' means the meshes are represented by both B-rep and P-rep.
+Details are shown in \S\ref{sec:tessellation}.
 
@@
   % Requires \usepackage{graphicx}
-  \includegraphics[width=1.7in]{p-reps}\\
-  \caption{P-rep of triangles. The yellow triangle is represented by three bounding planes (green) and the supporting plane where the triangle lies.}\label{fig:p-reps}
+  \includegraphics[width=1.7in]{sgen}\\
+  \caption{Triangle-triangle intersections made by different triangle pairs may (a) overlap or (b) intersect with each other.
+(c) Such situation introduces extra vertex which is intersection of triangles from three different meshes.}\label{fig:p-reps}
 \end{figure}
 
-As we discussed in Section \ref{sec:paradigm}, one of the problem in boolean operations under vertex-based representation is it inevitably introduces new vertices, whose coordinates cannot be exactly represented using fix-precision float-point number.
+\subsubsection{Face classification}
+
+This step is to choose faces from the intersection-free meshes to generate the final mesh.
+However, literally computing all the space indicators of each face is unacceptably slow for large CSG mesh.
+We utilize the geometry connectivity to propagate indicators in a flood-filling way, which is based on the spatial coherence of face indicators.
+In addition, many methods use barycenters of faces together with point-in-polyhedra test for face classification, which is not exact nor robust with fix-precision float-point arithmetics.
+Douze et al.
+\cite{douze2015quickcsg} classifies faces using space indicators of vertices, but failed to deal with coplanar conditions because of coplanar leads to ambiguity of $same$ and $oppo$ in such configurations.
+Different from them, we classify faces based on the classification results of exactly represented vertices, including input vertices and newly introduced intersection vertices, and carefully deal with coplanar conditions to ensure topology consistency.
+Details will be shown in \S\ref{sec:classification}.
+
+\section{Plane-based Geometry}
+
+As we discussed in \S\ref{sec:paradigm}, one of the problem in boolean operations under vertex-based representation is it inevitably introduces new vertices, whose coordinates cannot be exactly represented using fix-precision float-point number.
 On the other hand, if P-rep is used, no new geometry information needs to be constructed.
@@
 
-As illustrated in Fig.
-\ref{fig:p-reps}, using P-rep, each face $f$ with $n$ edges is represented by a supporting plane $\bm{p}_{f,s}$, where the face lies, and a list bounding planes $\{\bm{p}_{f,b}^i \ \vert\  i = 0, 1,...,n-1\}$.
+\begin{wrapfigure}{r}[0in]{0in}
+\includegraphics[width=1.4in]{p-reps}
+\end{wrapfigure}
+
+Using P-rep, each face $f$ with $n$ edges is represented by a supporting plane $\bm{p}_{f,s}$, where the face lies, and a list bounding planes $\{\bm{p}_{f,b}^i \ \vert\  i = 0, 1,...,n-1\}$.
 Each edge line $\bm{e}_f^i$ is represented by intersection $\bm{p}_{f,s} \cap \bm{p}_{f,b}^i$.

### 2016-10-12 summary.tex
10.11

@@
 
-As we discussed in \S\ref{sec:paradigm}, one of the problem in boolean operations under vertex-based representation is it inevitably introduces new vertices, whose coordinates cannot be exactly represented using fix-precision float-point number.
+%As we discussed in \S\ref{sec:paradigm}, one of the problem in boolean operations under vertex-based representation is it inevitably introduces new vertices, whose coordinates cannot be exactly represented using fix-precision float-point number.
 On the other hand, if P-rep is used, no new geometry information needs to be constructed.
 Therefore, we can use only geometric decision predicates to perform boolean operations.
-As the precision of input coordinates is finite, we can determine in advance the upper boundary of precision needed to perform a precise decision, with which we can use fixed precision predicates techniques to gain much performance while keeping exactness.
-For efficiency, we implement the predicates using filtering techniques proposed by Shewchuk \cite{shewchuk1997adaptive}.
 
 \begin{wrapfigure}{r}[0in]{0in}
-\includegraphics[width=1.4in]{p-reps}
+\includegraphics[width=1.2in]{p-reps}
+%\caption{Plane-based representation of triangle}
 \end{wrapfigure}
 
-Using P-rep, each face $f$ with $n$ edges is represented by a supporting plane $\bm{p}_{f,s}$, where the face lies, and a list bounding planes $\{\bm{p}_{f,b}^i \ \vert\  i = 0, 1,...,n-1\}$.
-Each edge line $\bm{e}_f^i$ is represented by intersection $\bm{p}_{f,s} \cap \bm{p}_{f,b}^i$.
-Corner vertex $\bm{v}_f^i$ is represented by intersection $\bm{p}_{f,s} \cap \bm{p}_{f,b}^i \cap \bm{p}_{f,b}^{{(i+1)}\bmod{n}}$.
-
-We also introduce some commonly used notations for better presentation in the rest of paper.
+Using Plane-based representation, each face $s$ with $n$ edges is represented by a supporting plane $\bm{p}_{s,sp}$, where the face lies, and a list bounding planes $\{\bm{p}_{s,b}^i \ \vert\  i = 0, 1,...,n-1\}$.
+Each edge line $\bm{e}_s^i$ is represented by intersection $\bm{p}_{s,sp} \cap \bm{p}_{s,b}^i$.
+Corner vertex $\bm{v}_s^i$ is represented by intersection $\bm{p}_{s,sp} \cap \bm{p}_{s,b}^i \cap \bm{p}_{s,b}^{{(i+1)}\bmod{n}}$.
+
+Other commonly used notations in this paper are presented here.
 A plane $\bm{p}$ can be represented by four scalar coefficients $a(\bm{p}), b(\bm{p}), c(\bm{p}), d(\bm{p})$.
@@
 
+As the precision of input coordinates is finite, we can determine in advance the upper boundary of precision needed to perform a precise decision, with which we can use fixed precision predicates to improve performance.
+For efficiency, we implement all geometry predicates using filtering techniques proposed by Shewchuk \cite{shewchuk1997adaptive}.
+
 \subsection{Conversion}
@@
 
-We use Campen et al.'s method \cite{campen2010exact} for exact conversion of triangles (represented by three vertices) from vertex-based representation to P-rep.
-Given that the input vertex coordinate has $L$-bit precision including sign, the precisions of the four plane coefficients are $L_a, L_b, L_c, L_d$, which have to meet the following requirements:
+We use Campen et al.'s method \cite{campen2010exact} for exact conversion of triangles from their vertex-based representation to plane-based representation.
+Given that the input vertex coordinate has $L$-bit precision including sign, the precisions of the four plane coefficients are $L_a, L_b, L_c, L_d$, which have to satisfy the following requirements:
 \begin{equation}
@@
 In our implementation, we actually use a more strong constraint $M \ge L_d+1$.
-Under this constraint, given a $L$-bit vertex $\bm{v_i}$, we can compute the orientation of plane $p_j$ with respect to $\bm{v_i}$ by the sign $\bm{n}(\bm{p_j})\cdot\bm{v_i} + d(\bm{p_j})$, which can be exactly computed using common float point arithmetic with limited $M$-bit precision.
-It allows very fast plane orientation predicates which benefits much the early rejection in our intersection computation (\S \ref{section:isect}).
+Under this constraint, given a $L$-bit vertex $\bm{v_i}$, we can compute the orientation of plane $p_j$ with respect to $\bm{v_i}$ by the sign $\bm{n}(\bm{p_j})\cdot\bm{v_i} + d(\bm{p_j})$, which requires no more than $M$ bits.
+It allows very fast plane orientation predicates which accelerates the early rejection in our triangle-triangle intersection tests (\S \ref{section:isect}).
 
@@
 \label{sec:substrates}
-Plane-based geometry predicates include checking coincidence and co-orientation of planes, orientation of a plane with respect to a point, and whether three planes intersect in a unique point, etc.
+Plane-based geometry predicates used in our method include checking coincidence and co-orientation of planes, orientation of a plane with respect to a point, and whether three planes intersect in a unique point, etc.
 Most of them are well-discussed in previous work \cite{bernstein2009fast,banerjee1996topologically}.
-In the following, we focus on two advanced plane-based predicates---\emph{point ordering on line} and \emph{circular ordering of line}, which are important building blocks of our method.
-
-\vspace{0.5em}
-\noindent \textbf{Linear ordering on points}~~~~
-Given an arbitrary line $\bm{l}$ with two points $\bm{v}_1\colon(\bm{p}_1^0\cap\bm{p}_1^1\cap\bm{p}_1^2)$ and $\bm{v}_2\colon(\bm{p}_2^0\cap\bm{p}_2^1\cap\bm{p}_2^2)$ on it, we need to determine the linear order of the two points along $\bm{l}$ (Fig.
+In the following, we focus on two advanced plane-based predicates, which are also important building blocks of our method.
+
+\vspace{0.5em}
+\noindent \textbf{Linear ordering of points}~~~~
+Given an line $\bm{l}_{ab}$ with two points $\bm{v}_a\colon(\bm{p}_a^0\cap\bm{p}_a^1\cap\bm{p}_a^2)$ and $\bm{v}_b\colon(\bm{p}_b^0\cap\bm{p}_b^1\cap\bm{p}_b^2)$ on it, we need to determine the linear order of the two points along $\bm{l}_{ab}$ (Fig.
 \ref{fig:twopointoneline}).
-To solve this problem, we choose one plane not parallel with $\bm{l}$ from the plane representation of each point.
+To solve this problem, we choose one plane not parallel with $\bm{l}_{ab}$ from the plane representation of each point.
 Then we convert this problem into linear order of planes and solve it using the same technique as Banerjee et al.
 \cite{banerjee1996topologically}.
-The chosen planes should have the same orientation with $\bm{l}$ (the dot product between plane normal and $\bm{l}$ has to be positive) and unqualified planes have to be flipped.
+The chosen planes should have the same orientation with $\bm{l}_{ab}$ (the dot product between plane normal and $\bm{l}_{ab}$ has to be positive) and unqualified planes have to be flipped.
 
@@
 Lines can be sorted in a divide-and-conquer way based on the relative order of each pair of lines.
-Therefore, this problem is converted to that given two coplanar lines $\bm{l}_a\colon(\bm{p}_a^0\cap\bm{p}_a^1)$ and $\bm{l}_b\colon(\bm{p}_b^0\cap\bm{p}_b^1)$ with their intersection point $\bm{v}_{ab}$, compute the circular order of the two lines.
-Supposing the common plane is $\bm{p}_s$, we can compute the order by the sign of $\sin{\theta_{ab}}$, where $\theta_{ab}\in(-\pi,\pi)$ is the angle from $\bm{l}_a$ to $\bm{l}_b$ under the top view of $\bm{p}_s$.
-And the sign of sine is the same as triple product $\bm{n}(\bm{p}_s) \cdot (\bm{l}_a\times\bm{l}_b)$,
+Therefore, this problem is converted to that given two coplanar lines $\bm{l}_a$ and $\bm{l}_b$ with their intersection point $\bm{v}_{ab}$, compute the circular order of the two lines.
+Supposing the common plane of $\bm{l}_a$ and $\bm{l}_b$ is $\bm{p}_0$, we can compute the order by the sign of $\sin{\theta_{ab}}$, where $\theta_{ab}\in(-\pi,\pi)$ is the angle from $\bm{l}_a$ to $\bm{l}_b$ under the top view of $\bm{p}_0$.
+The sign of $\sin{\theta_{ab}}$ is the same as triple product $\bm{n}(\bm{p}_0) \cdot (\bm{l}_a\times\bm{l}_b)$,
 where $\bm{n}$ means the normal direction. However, explicit computing this equation is complicated because both $\bm{l}_a$ and $\bm{l}_b$ are implicitly represented by intersection of planes.
@@
 We develop an easier way that requiring no explicit computation of $\bm{l}_a$ and $\bm{l}_b$.
-We orthogonally decompose $\bm{n}(\bm{p}_a)$ and $\bm{n}(\bm{p}_b)$ along the normal the common plane $\bm{p}_s$:
+First, we write the P-reps of two lines as $\bm{l}_a\colon(\bm{p}_0\cap\bm{p}_a)$ and $\bm{l}_b\colon(\bm{p}_0\cap\bm{p}_b)$.
+Then we orthogonally decompose $\bm{n}(\bm{p}_a)$ and $\bm{n}(\bm{p}_b)$ along the normal the common plane $\bm{p}_0$:
 \begin{equation}
@@
 \end{equation}
-Here superscript `$\parallel$` means the projection on $\bm{p}_s$ and `$\perp$` means orthogonal to $\bm{p}_s$.
-As we know $\bm{n}^\perp(\bm{p}_a)$ and $\bm{n}^\perp(\bm{p}_b)$ are both parallel to $\bm{n}(\bm{p}_s)$, we get:
+Here superscript `$\parallel$` means the projection on $\bm{p}_s$ and `$\perp$` means orthogonal to $\bm{p}_0$.
+As we know $\bm{n}^\perp(\bm{p}_a)$ and $\bm{n}^\perp(\bm{p}_b)$ are both parallel to $\bm{n}(\bm{p}_0)$, we get:
 \begin{equation}
 \label{eq:circ1}
-\bm{n}(\bm{p}_s) \cdot (\bm{n}(\bm{p}_a) \times \bm{n}(\bm{p}_b)) = \bm{n}(\bm{p}_s) \cdot (\bm{n}^\parallel(\bm{p}_a) \times \bm{n}^\parallel(\bm{p}_b)).
+\bm{n}(\bm{p}_0) \cdot (\bm{n}(\bm{p}_a) \times \bm{n}(\bm{p}_b)) = \bm{n}(\bm{p}_0) \cdot (\bm{n}^\parallel(\bm{p}_a) \times \bm{n}^\parallel(\bm{p}_b)).
 \end{equation}
@@
 \label{eq:circ2}
-sign(\sin{\theta_{ab}})=  sign(\bm{n}(\bm{p}_s)\cdot(\bm{n}(\bm{p}_a) \times \bm{n}(\bm{p}_b)))
+sign(\sin{\theta_{ab}})=  sign(\bm{n}(\bm{p}_0)\cdot(\bm{n}(\bm{p}_a) \times \bm{n}(\bm{p}_b)))
 \end{equation}
 
-Since all the three vectors are already explicitly represented, we only have to evaluate the sign of an 3x3 matrix and avoid complicated high precision float-point arithmetic.
+Since all the three vectors on the right side are already explicitly represented, we only have to evaluate the sign of an 3x3 matrix and avoid complicated high precision float-point arithmetic.
 \begin{figure}
@@
   \includegraphics[width=2.5in]{twopointoneline}\\
-  \caption{{\color{red}{Sketch: config of two point one line comparison}}}\label{fig:twopointoneline}
+  \caption{The configuration of linear ordering of points.
+Points $\bm{v}_a$ and $\bm{v}_b$ are both on line $\bm{l}_{ab}$.
+We convert this problem into the plane ordering between $\bm{p}_a$ and $\bm{p}_b$ along $\bm{l}_{ab}$.}\label{fig:twopointoneline}
 \end{figure}
@@
 \includegraphics[width=2.5in]{circularorder}
-\caption{The configuration of two-line-one-plane comparison.
-$l_a\colon(p_0, p_a)$ and $l_b\colon(p_0, p_b)$ are coplanar in $p_0$.
-We want to compute $sign(\vec{n}_0 \cdot (\vec{l}_a \times \vec{l}_b))$.}
+\caption{The configuration of circular ordering of lines. $\bm{l}_a\colon(\bm{p}_0 \cap \bm{p}_a)$ and $\bm{l}_b\colon(\bm{p}_0 \cap \bm{p}_b)$ are coplanar in $\bm{p}_0$.}
 \label{fig:circularorder}
@@
 However, a naive implementation of M\"{o}ller's algorithm may fail to produce correct results because of numerical errors.
-Therefore, we integrate plane-based geometry representation to make it unconditionally exact and robust.
-In the following, we first make a quick review of M\"{o}ller's algorithm, and then discuss the way to integrate plane-based geometry.
-After that, we talk about how to deal with degenerate cases.
+Therefore, we integrate plane-based geometry to make it unconditionally exact and robust.
+In the following, we first make a quick review of M\"{o}ller's algorithm, and then discuss the way to embed plane-based geometry.
+After that, we discuss how to deal with degenerate cases.
 
@@
 \includegraphics[width=2.5in]{projection}
-\caption{$Seg_1$ is the intersection between $p^s(t_2)$ and $t_1$.
-$Seg_2$ is the intersection between $p^s(t_1)$ and $t_2$.
+\caption{$Seg_1$ is the intersection between $\bm{p}_{t_2, sp}$ and $t_1$.
+$Seg_2$ is the intersection between $\bm{p}_{t_1, sp}$ and $t_2$.
 The intersection between $t_1$ and $t_2$, which is the line segment in red, is the overlap of $Seg_1$ and $Seg_2$.}
@@
 \begin{itemize}[leftmargin=0.45cm]
-\item[1)] An early rejection is performed by testing whether $t_1$ intersects $\bm{p}_{t_2, s}$, the supporting plane of $t_2$. The same test is also done between $t_2$ and $\bm{p}_{t_1, s}$.
-\item[2)]The intersection between $t_1$ and $\bm{p}_{t_2, s}$, denoted as $Seg_1$, and the intersection between $t_2$ and $\bm{p}_{t_1, s}$, denoted as $Seg_2$, are separately computed .
+\item[1)] An early rejection is performed by testing whether $t_1$ intersects $\bm{p}_{t_2, sp}$, the supporting plane of $t_2$. The same test is also done between $t_2$ and $\bm{p}_{t_1, sp}$.
+\item[2)]The intersection between $t_1$ and $\bm{p}_{t_2, sp}$, denoted as $Seg_1$, and the intersection between $t_2$ and $\bm{p}_{t_1, sp}$, denoted as $Seg_2$, are separately computed .
  \item[3)]The intersection between $t_1$ and $t_2$ is determined by computing the overlap between $Seg_1$ and $Seg_2$ .
@@
 \label{sec:embed}
-According to the method described in section \ref{sec:convert}, triangle faces $f$ are firstly converted to its P-rep: a supporting plane $\bm{p}_{t, s}$ surrounded by three bounding planes $\{\bm{p}_{t, b}^i|\ i = 0,1,2\}$.
+According to the method described in \S\ref{sec:convert}, triangle faces $t$ are firstly converted to its P-rep: a supporting plane $\bm{p}_{t, sp}$ surrounded by three bounding planes $\{\bm{p}_{t, b}^i|\ i = 0,1,2\}$.
 We integrate the plane-based geometry into each of the tree steps of M\"{o}ller's algorithm as following:
@@
 \includegraphics[width=3.5in]{sign}
-\caption{We denote the signed distance from point $X$ to plane $S_2$ as $d_X$.
-All the four conditions of intersection between $t_1$ and $S_2$ (denoted as $Seg_1$) are:  (a) $d_A\cdot d_C<0$, $d_B\cdot d_C<0$; (b) $d_A=0$, $d_B=0$, $d_C\neq 0$; (c) $d_A=0$, $d_B\cdot d_C<0$; (d) $d_A=0$, $d_B\cdot d_C>0$.
-End points of $Seg_1$ are intersections between $S_2$ and related edge lines of $t_1$ (bold edges).}
+\caption{We denote the signed distance from point $v_i$ to plane $\bm{p}_{t_2, sp}$ as $d_i$.
+All the four conditions of intersection between $t_1$ and $\bm{p}_{t_2, sp}$ are:  (a) $d_0\cdot d_2<0$, $d_1\cdot d_2<0$; (b) $d_0=0$, $d_1=0$, $d_2\neq 0$; (c) $d_0=0$, $d_1\cdot d_2<0$; (d) $d_0=0$, $d_1\cdot d_2>0$.
+End points of $Seg_1$ are intersections between $\bm{p}_{t_2, sp}$ and related edges of $t_1$ (red bold lines).}
 \label{fig:isect}
@@
 Take $Seg_1$ as an example.
-$Seg_1$ is the intersection between $t_1$ and $\bm{p}_{t_2, s}$ and the end points of $Seg_1$ are intersections between $\bm{p}_{t_2, s}$ and edges from $t_1$ (denoted as $\bm{e}^i_{t_1}$).
-Because $\bm{e}^i_{t_1}$ can be represented as $\bm{p}_{t_1, s}\cap \bm{p}^i_{t_1, b}$, the end points of $Seg_1$ can be represented in the form of $\bm{p}_{t_2, s} \cap \bm{p}_{t_1, s} \cap \bm{p}^i_{t_1, b}$.
+$Seg_1$ is the intersection between $t_1$ and $\bm{p}_{t_2, sp}$ and the end points of $Seg_1$ are intersections between $\bm{p}_{t_2, sp}$ and edges from $t_1$ (denoted as $\bm{e}^i_{t_1}$).
+Because $\bm{e}^i_{t_1}$ can be represented as $\bm{p}_{t_1, s}\cap \bm{p}^i_{t_1, b}$, the end points of $Seg_1$ can be represented in the form of $\bm{p}_{t_2, sp} \cap \bm{p}_{t_1, sp} \cap \bm{p}^i_{t_1, b}$.
 In Fig.
-\ref{fig:isect}, we list all possible intersecting situations between $t_1$ and $\bm{p}_{t_2, s}$.
-The two corresponding bounding planes $\bm{p}^i_{t_1, b}$ for each situation are also presented.
-The coplanar condition will be discussed later in \S \ref{sec:degenerate}.
+\ref{fig:isect}, we list all possible intersecting situations between $t_1$ and $\bm{p}_{t_2, sp}$.
+The two intersection edges $\bm{e}^i_{t_1}$ for each situation are also presented.
+The coplanar situation will be discussed later in \S \ref{sec:degenerate}.
       \vspace{0.5em}
  \item[3)] The intersection between $t_1$ and $t_2$ is the overlap area of $Seg_1$ and $Seg_2$.
-It can be easily computed by sorting the end points of $Seg_1$ and $Seg_2$ along the line $\bm{l}\colon \bm{p}_{t_1, s} \cap \bm{p}_{t_2, s}$.
+It can be easily computed by sorting the end points of $Seg_1$ and $Seg_2$ along the line $\bm{l}\colon \bm{p}_{t_1, sp} \cap \bm{p}_{t_2, sp}$.
 Because end points are all represented using plane triples, we can use the linear order of points discussed in \S \ref{sec:substrates} to sort.
@@
 \end{figure}
+\fi
 
@@
 However, in this case, the intersection is not valid.
-The two sides of the intersection are both retained or both dropped and we do not rely the it for tessellation.
+The two sides of the intersection are both retained or both dropped and we do not rely it for tessellation.
 

### 2016-10-13 summary.tex
10.13

@@
 
-Once intersections are computed, proper representation is needed to guarantee exact transfer of information and low cost to process.
-In our method, an intersection line segment $\mathbb{I}$ is represented by our plane-based intersection representation (PBI-rep) as $\{t, \bm{p}_{ext}, (\bm{p}^0, \bm{p}^1),\bm{\Psi}\}$.
-The first component indicates $\mathbb{I}$ is on triangle $t$, and second one $\bm{p}_{ext}$ indicates $\mathbb{I}$ lies on a line $\bm{l}_{\mathbb{I}}\colon(\bm{p}_{t, s} \cap \bm{p}_{ext})$.
-The two end points of $\mathbb{I}$ are $\bm{l}_{\mathbb{I}}\cap\bm{p}^0$ and $\bm{l}_{\mathbb{I}}\cap\bm{p}^1$.
-The last component $\bm{\Psi}$ is a vector that represents the neighborhood of the intersection, which is for fast face classification in later stages.
-For each component of $\bm{\Psi}$, if $\mathbb{I}$ is on the surface of primitive $P_k$, the $k^{th}$ component $\Psi_{k}$ is the edge or face of $P_k$ where $\mathbb{I}$ lies.
-Otherwise, $\Psi_{k}=0$, meaning default empty data.
-
-To illustrate, assume two triangle faces $t_1$ and $t_2$, from primitive $P_a$ and $P_b$, intersect on a line segment.
-Then it generates two intersections for both triangles respectively, denoted as ${\mathbb{I}}_{12}$ and ${\mathbb{I}}_{21}$.
-For ${\mathbb{I}}_{12}$, the first two components are $t_1$ and $\bm{p}_{t_2, s}$.
-The computation of the third component is discussed in \S\ref{sec:embed}.
-The neighborhood $\bm{\Psi}$ is zero for all components except $\Psi_a$ and $\Psi_b$.
-In most time, $\Psi_a=t_1$ and $\Psi_b=t_2$.
+In our method, intersection between two triangles is denoted as $\bm{\mathcal{I}}\colon\{t, \bm{p}_{ext}, (\bm{p}^0, \bm{p}^1),\bm{\Psi}\}$, which is called plane-based intersection representation (PBI-rep).
+The first component $t$ indicates $\bm{\mathcal{I}}$ is on triangle $t$, and second one $\bm{p}_{ext}$ indicates $\bm{\mathcal{I}}$ lies on $\bm{p}_{ext}$, which also means it lies on line $\bm{p}_{t, sp} \cap \bm{p}_{ext}$.
+The two end points of $\bm{\mathcal{I}}$ are $\bm{p}_{t, sp} \cap \bm{p}_{ext}\cap\bm{p}^0$ and $\bm{p}_{t, sp} \cap \bm{p}_{ext}\cap\bm{p}^1$.
+The last component $\bm{\Psi}$ is a set that represents the neighborhood of the intersection.
+If $\bm{\mathcal{I}}$ is on the surface of mesh $P_k$, an element $(P_{k}, \Psi_{k})$ is added to $\bm{\Psi}$, where $\Psi_{k}$ is the edge or face of $P_k$ where $\bm{\mathcal{I}}$ lies.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=2in]{pbi}
+\caption{Triangle $t_1$ and $t_2$ are from mesh $P_i, P_j$ respectively.
+They intersect on line segment, generating intersection $\bm{\mathcal{I}}_{12}$ on $t_1$ and $\bm{\mathcal{I}}_{21}$ on $t_2$.
+The PBI-rep of $\bm{\mathcal{I}}_{12}$ is $\{t_1, \bm{p}_{t_2, sp}, (\bm{p}_{t_2, b}^0, \bm{p}_{t_2, b}^1),\{(P_i, \Psi_i), (P_j, \Psi_j)\}\}$.}
+\label{fig:pbi}
+\end{figure}
+
+For example, in Fig.
+\ref{fig:pbi}, two triangle faces $t_1$ and $t_2$ from mesh $P_i$ and $P_j$ respectively intersect on a line segment.
+Then it generates two intersections for each of the two triangles, denoted as ${\bm{\mathcal{I}}}_{12}$ and ${\bm{\mathcal{I}}}_{21}$.
+For ${\bm{\mathcal{I}}}_{12}$, the first two components are $t_1$ and $\bm{p}_{t_2, sp}$.
+The computation of the third component has already been discussed in \S\ref{sec:embed}.
+The neighborhood $\bm{\Psi} = \{(P_i, \Psi_i), (P_j, \Psi_j)\}$.
+In most time, $\Psi_i=t_1$ and $\Psi_j=t_2$.
 However, sometimes, intersections may lie on the primitive edges instead of faces.
-In that case, $\Psi_a$ and $\Psi_b$ are edges.
+In that case, $\Psi_i$ and $\Psi_j$ are edges (Fig.
+\ref{fig:twin}).
 We postpone this discussion until \S\ref{sec:degenerate}.
-The computation of ${\mathbb{I}}_{21}$ is similar.
+The computation of ${\bm{\mathcal{I}}}_{21}$ is similar.
 
@@
 
-Which two triangles, if intersecting, intersect on a line segment in most situations, they can also intersect on a point or a convex area (coplanar case).
-Even if line segment is the intersection, the intersection can be on triangle edges or inside triangles.
-These degenerate situations are troublesome to develop a robust boolean method.
-In this section, we offer simple but robust way to deal with all the degenerations and conceal the complexity of intersections behind the concise intersection representation in \S\ref{sec:ir}.
+While two triangles, if intersecting, intersect on a line segment in most situations, they can also intersect on a point or a convex area (coplanar case).
+Even if the intersection is a line segment, the intersection can be on triangle edges.
+These degenerate situations prevent us from performing robust boolean operations.
+In this section, we offer simple but effective way to deal with all these degenerations and conceal the complexity of intersections behind the concise PBI-rep.
 
@@
 The word 'cross' do not only include the situation that a face is partly outside and partly inside of a primitive, but also can mean that a face is partly inside (outside) and part on the boundary of the primitive.
+\begin{figure}[t]
+\centering
+\includegraphics[width=3.5in]{isolated}
+\caption{Two situations of point intersections.
+(a) $\bm{v}_{iso}$ is isolated, and there is no adjacent intersection line segment.
+We need to add the $\bm{v}_{iso}$ to triangle $t_1$.
+(b) $\bm{v}_{non-iso}$ is not isolated.
+We do not need to add $\bm{v}_{non-iso}$ into $t_1$ because it can be added by other triangle pairs which intersect on line segments.
+However, for simplicity, we add the intersection point into $t_1$ in both situations.}
+\label{fig:isolated}
+\end{figure}
 
@@
 \ref{fig:isolated}), the intersection cannot be represented using our four-component description.
-Therefore, we simply add the intersection point into the meshes to guarantee correct tessellation, and no intersection is introduced.
-
-\iffalse
-\begin{figure}[t]
-\centering
-\includegraphics[width=3.5in]{isolated}
-\caption{Two situations of point intersections.
-(a) The intersection point is isolated, and there is no adjacent intersection line segment.
-This situation may cause non-manifold surface in Boolean operation.
-(b) The intersection point is not isolated.
-The intersection point can be introduced by other face pairs during intersection tests.}
-\label{fig:isolated}
-\end{figure}
-\fi
+Therefore, we simply add the intersection point into the related triangles to guarantee correct tessellation, and no intersection is introduced.
 
@@
 X).
-Therefore, supposing intersection is on the edge from mesh $P_k$, the neighborhood $\Psi_k$ is then an edge.
+Therefore, supposing intersection is on the edge $\bm{e}_{k, i}$ of mesh $P_k$, then the neighborhood $\Psi_k = \bm{e}_{k, i}$.
 Note that an intersection can be on edges from different meshes.
-Then there are more than one component of $\bm{\Psi}$ are edges.
-
-One thing need to be noticed is that there will be repetitive detection of edge intersections.
+Then there are more than one component of $\bm{\Psi}$ are edges (Fig.
+\ref{fig:twin}d).
+
+Another thing needs to be noticed is that there will be repetitive detection of edge intersections.
 In Fig.
@@
 \ref{fig:coplanar}).
-Obviously, if we tessellate both $t_1$ and $t_2$ according to the boundary of overlapping area, we can guarantee that the tessellated meshes will not cross the boundary of any other meshes.
+Apparantly, if we tessellate both $t_1$ and $t_2$ according to the boundary of overlapping area, we can guarantee that the tessellated meshes will not cross the boundary of any other meshes.
 In fact, many methods \cite{feito2013fast,zhou2016mesh} claim that tessellating faces according to this 2D-intersection result is necessary.
 However, in our method, we do not test whether $t_1$ and $t_2$ really intersect in 2D.
-We simply omit all coplanar situations, treating them as they do not intersect at all.
-This simplify our method, making it more robust and fast, while doing no harm to the topology correctness.
+We treat them as they do not intersect at all.
+In this way, we simplify our method, making it more robust and fast, while doing no harm to the topology correctness.
 
@@
 We find that each intersection line segment in 2D is on the edges from input meshes.
-That means we can view 2D intersections as special cases of edge intersection.
+That means we can view 2D intersection as a special case of edge intersection.
 The only difference is that there can be up to three edge intersections in one 2D intersection (Fig.
-x).
+\ref{fig:coplanar}).
 As we have discussed, edge intersection will be detected twice.
 That means we can rely on the companion triangle faces to detect intersections.
-There is more extreme case that the companion triangles are coplanar, meaning neither of them will record the intersection.
-However, in this case, the intersection is not valid.
-The two sides of the intersection are both retained or both dropped and we do not rely it for tessellation.
+However, if the companion triangles are also coplanar, neither of the two triangles will record the intersection.
+In fact, we do not need to worry about this, because in this case, the intersection is not valid.
+The two sides of the intersection are both retained or both dropped and we do not need it for tessellation.
 
@@
 \label{sec:tessellation}
-After intersection computation, tessellation is performed on each intersecting triangle face and generate the intersection-free hybrid mesh.
+After intersection computation, tessellation is performed on each intersecting triangle face and generate our intersection-free meshes.
 We call this stage as deferred tessellation because the tessellation happens until all valid intersections are computed.
-Ogayar-Anguita et.
+
+In previous work, Ogayar-Anguita et.
 al.
@@
 They treat triangle faces as convex triangulation zones and intersections as constraints.
-
-Our first try is to implement a robust CDT and apply to our method.
-However, we fail because of the dilemma of precision and efficiency.
-CDT algorithms \cite{chew1989constrained,preparata2012computational} usually require coordinates projection or intersection detection between arbitrary connections of vertices within triangulation zone.
+Our first try is to implement a robust plane-based CDT.
+However, CDT algorithms \cite{chew1989constrained,preparata2012computational} usually require coordinates projection or intersection detection between arbitrary connections of vertices within triangulation zone.
 Because vertices may be implicitly represented in our method, these geometry predicates are hard to guarantee computation efficiency and precision simultaneously.
@@
 The intersections may intersect each other, introducing new vertices and splitting original intersection line segments (Fig.
+\ref{fig:iisect}).
+This breaks the assumption of most CDT algorithms and may lead to incorrect output topology.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=2in]{iisect}
+\caption{suppose? actual?}
+\label{fig:iisect}
+\end{figure}
+
+To solve these problems, we first perform intersection refinement to eliminate any crossing or overlapping between intersections.
+After that, we perform conservative tessellation based on \emph{tess-graph}, ensuring unconditional topology correctness.
+An tess-graph is a graph-like description of intersections on a certain face.
+The word `conservative` means we tessellate face into polygons, not triangles.
+This is because if triangles are required, we need construct new bounding planes for these new triangles, which violating our principle of no geometry construction (Fig.
 x).
-This breaks the assumption of most CDT algorithms and may lead to incorrect output topology.
-
-To solve these problems, we first perform intersection refinement to eliminate any crossing or overlapping between intersections.
-After that, we perform conservative tessellation based on plane-based geometry, ensuring unconditional topology correctness.
-The word `conservative` means we tessellate face into polygons, not triangles.
-During tessellation, we organize intersections and generate an \emph{tess-graph}, which is a graph-like description of intersections.
-At last, we extract subfaces from tess-graph of each triangle face and construct the intersection-free hybrid meshes.
 
@@
 Intersection refinement is performed in a local scope.
-For each intersecting face $t_i$, we collect all intersections on $t$ as a set $\bm{\Gamma}(t)=\{\mathbb{I}_{t}^i, i=0,1,2,...\}\cup\{\mathbb{I}_{t}^{e_i},i=0,1,2\}$ and refine them together.
-The set $\{\mathbb{I}_{t}^{e_i},i=0,1,2\}$ is the PBI-reps of the three edges of $t$.
+For each intersecting face $t_i$, we collect all intersections on $t$ as a set $\bm{\Gamma}(t)=\{\bm{\mathcal{I}}_{t}^i, i=0,1,2,...\}\cup\{\bm{\mathcal{I}}_{t}^{e_i},i=0,1,2\}$ and refine them together.
+The set $\{\bm{\mathcal{I}}_{t}^{e_i},i=0,1,2\}$ is the PBI-reps of the three edges of $t$.
 We treat edges as intersections for simplicity in this stage.
-The neighborhood component $\bm{\Psi}(\mathbb{I}_{t}^{e_i})$ is set as $\bm{0}$.
-Other components of $\mathbb{I}_{t}^{e_i}$ are straightforward to determine.
+The neighborhood component $\bm{\Psi}(\bm{\mathcal{I}}_{t}^{e_i})$ is set as $\bm{0}$.
+Other components of $\bm{\mathcal{I}}_{t}^{e_i}$ are straightforward to determine.
 Refinement on $\bm{\Gamma}(t)$ is done using only plane-based geometry predicates by the following three steps:
@@
 \noindent \textbf{Collinear splitting}~~~~
-Each intersection $\mathbb{I}_{t}^x$ are testing whether they are collinearly overlapping with other intersections.
-If yes, $\mathbb{I}_{t}^x$ is split by the end points of overlapping intersections (Fig.
+Each intersection $\bm{\mathcal{I}}_{t}^x$ are testing whether they are collinearly overlapping with other intersections.
+If yes, $\bm{\mathcal{I}}_{t}^x$ is split by the end points of overlapping intersections (Fig.
 x).
-Because $\mathbb{I}_{t}^x$ may collinearly overlap more than one other intersection, the splitting may be deferred until all splitting points are found.
-The subroutine linear order of points (\S\ref{sec:substrates}) is used to sort these splitting points along $\mathbb{I}_{t}^x$.
+Because $\bm{\mathcal{I}}_{t}^x$ may collinearly overlap more than one other intersection, the splitting may be deferred until all splitting points are found.
+The subroutine linear order of points (\S\ref{sec:substrates}) is used to sort these splitting points along $\bm{\mathcal{I}}_{t}^x$.
 The PBI-reps of split segments inherit their father's except the second component the end points.
@@
 \begin{equation}
-  \Psi_k(\mathbb{I}_{t}^{12})=\left\{
+  \Psi_k(\bm{\mathcal{I}}_{t}^{12})=\left\{
    \begin{array}{l}
-   \Psi_k(\mathbb{I}_{t}^1)\mbox{ or }\Psi_k(\mathbb{I}_{t}^2),\ \mbox{ if } \Psi_k(\mathbb{I}_{t}^1)=\Psi_k(\mathbb{I}_{t}^2) \\
-   \Psi_k(\mathbb{I}_{t}^1),\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \mbox{ if } \Psi_k(\mathbb{I}_{t}^2)=0  \\
-   \Psi_k(\mathbb{I}_{t}^2),\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \mbox{ if } \Psi_k(\mathbb{I}_{t}^1)=0  \\
+   \Psi_k(\bm{\mathcal{I}}_{t}^1)\mbox{ or }\Psi_k(\bm{\mathcal{I}}_{t}^2),\ \mbox{ if } \Psi_k(\bm{\mathcal{I}}_{t}^1)=\Psi_k(\bm{\mathcal{I}}_{t}^2) \\
+   \Psi_k(\bm{\mathcal{I}}_{t}^1),\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \mbox{ if } \Psi_k(\bm{\mathcal{I}}_{t}^2)=0  \\
+   \Psi_k(\bm{\mathcal{I}}_{t}^2),\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \mbox{ if } \Psi_k(\bm{\mathcal{I}}_{t}^1)=0  \\
    \end{array}
@@
 \end{equation}
-, where $\mathbb{I}_{t}^1$ and $\mathbb{I}_{t}^2$ are old intersections and $\mathbb{I}_{t}^{12}$ is the new one.
+, where $\bm{\mathcal{I}}_{t}^1$ and $\bm{\mathcal{I}}_{t}^2$ are old intersections and $\bm{\mathcal{I}}_{t}^{12}$ is the new one.
 
@@
 Given adjacent faces $s_1$ and $s_2$, it is straightforward to know whether $\bm{\Lambda}(s_1)$ and $\bm{\Lambda}(s_2)$ are different.
-The two indicator vectors are the same unless the shared edge $e_{12}$ lies on the boundary of some meshes, and it means there is an intersection $\mathbb{I}(e_{12})$ stored on $e_{12}$.
+The two indicator vectors are the same unless the shared edge $e_{12}$ lies on the boundary of some meshes, and it means there is an intersection $\bm{\mathcal{I}}(e_{12})$ stored on $e_{12}$.
 For a certain indicator $\lambda_k$, it always stands:
@@
 \label{eq:eq1}
-{\lambda_k}(s_1) = {\lambda_k}(s_2),\ \ \  \mbox{if }\Psi_k(\mathbb{I}(e_{12}))= 0.
+{\lambda_k}(s_1) = {\lambda_k}(s_2),\ \ \  \mbox{if }\Psi_k(\bm{\mathcal{I}}(e_{12}))= 0.
 \end{equation}
-Even if $\Psi_k(\mathbb{I}(e_{12})) \neq 0$, both $\lambda_k(t_1)$ and $\lambda_k(t_2)$ can be computed efficiently and exactly according to $\mathbb{I}(e_{12})$ (\S\ref{sec:propagation}).
+Even if $\Psi_k(\bm{\mathcal{I}}(e_{12})) \neq 0$, both $\lambda_k(t_1)$ and $\lambda_k(t_2)$ can be computed efficiently and exactly according to $\bm{\mathcal{I}}(e_{12})$ (\S\ref{sec:propagation}).
 We outline our classification method in Algorithm \ref{code:floodfill}.
@@
         \EndIf
-        \If {there are PBI-reps $\{{\mathbb{I}}_k\}$ on $e(s_i, s)$}
-            \State compute $\boldsymbol{\Lambda}(s_i)$ by $\boldsymbol{\Lambda}(s)$ and $\{{\mathbb{I}}_k\}$
+        \If {there are PBI-reps $\{{\bm{\mathcal{I}}}_k\}$ on $e(s_i, s)$}
+            \State compute $\boldsymbol{\Lambda}(s_i)$ by $\boldsymbol{\Lambda}(s)$ and $\{{\bm{\mathcal{I}}}_k\}$
             \State \Call{propagate} { $s_i$ , $\boldsymbol{\Lambda}(s_i)$}
@@
 \vspace{0.5em}
-\noindent\textbf{$\bm{s\to e_s}$}~~~~ When $\lambda_k(e_s)=on$, there will be PBI-rep $\mathbb{I}(e_s)$ attached to $e_s$ and the related neighborhood $\Psi_k(\mathbb{I}(e_s))$ must be nonzero, since it is on the surface of mesh $P_k$:
+\noindent\textbf{$\bm{s\to e_s}$}~~~~ When $\lambda_k(e_s)=on$, there will be PBI-rep $\bm{\mathcal{I}}(e_s)$ attached to $e_s$ and the related neighborhood $\Psi_k(\bm{\mathcal{I}}(e_s))$ must be nonzero, since it is on the surface of mesh $P_k$:
 \begin{equation}
 \label{eq:eq1}
-\lambda_k(e_s)=on,\ \ \  \mbox{iff. }\Psi_k(\mathbb{I}(e_s))\neq 0.
+\lambda_k(e_s)=on,\ \ \  \mbox{iff. }\Psi_k(\bm{\mathcal{I}}(e_s))\neq 0.
 \end{equation}
-So all we need is to iterate over all nonzero components of $\bm{\Psi}(\mathbb{I}(e_s))$ and change corresponding indicators to $on$.
+So all we need is to iterate over all nonzero components of $\bm{\Psi}(\bm{\mathcal{I}}(e_s))$ and change corresponding indicators to $on$.
 
@@
 \ref{eq:porder}, we know if $\lambda_k(e_s) \neq on$, then $\lambda_k(e_s)=\lambda_k(s)$.
-When $\lambda_k(e_s) = on$, we figure out $\lambda_k(s)$ using $\Psi_k(\mathbb{I}(e_s))$.
+When $\lambda_k(e_s) = on$, we figure out $\lambda_k(s)$ using $\Psi_k(\bm{\mathcal{I}}(e_s))$.
 From eq.
-\ref{eq:eq1}, we know $\Psi_k(\mathbb{I}(e_s)) \neq 0$ and can be either a triangle face or an edge.
-If $\Psi_k(\mathbb{I}(e_s))$ is a face, we can build a trivial BSP \cite{thibault1987set} using the face on the space near $e_s$.
-If $\Psi_k(\mathbb{I}(e_s))$ is an edge, we can still build BSP using the opposite two faces along $e_s$.
+\ref{eq:eq1}, we know $\Psi_k(\bm{\mathcal{I}}(e_s)) \neq 0$ and can be either a triangle face or an edge.
+If $\Psi_k(\bm{\mathcal{I}}(e_s))$ is a face, we can build a trivial BSP \cite{thibault1987set} using the face on the space near $e_s$.
+If $\Psi_k(\bm{\mathcal{I}}(e_s))$ is an edge, we can still build BSP using the opposite two faces along $e_s$.
 In both cases, the BSP can be used to compute $\lambda_k(s)$ if we can sample a point from $s$ that near $e_s$.
@@
 
-Since the faces involving in $C_{P_h \backslash P_j}$ is part of primitive $P_j$, the space division $\boldsymbol{D}(C_{P_h \backslash P_j})$ is homogeneous with the space division by $P_j$ in neighborhood of $\mathbb{I}$.
-The basic idea is to choose one point $v_x(t_i)$ on $t_i$ close enough to $\mathbb{I}$ to compute $\lambda(v_x(t_i), P_j)$, and then compute $\lambda(t_i, P_j)$ accordingly.
+Since the faces involving in $C_{P_h \backslash P_j}$ is part of primitive $P_j$, the space division $\boldsymbol{D}(C_{P_h \backslash P_j})$ is homogeneous with the space division by $P_j$ in neighborhood of $\bm{\mathcal{I}}$.
+The basic idea is to choose one point $v_x(t_i)$ on $t_i$ close enough to $\bm{\mathcal{I}}$ to compute $\lambda(v_x(t_i), P_j)$, and then compute $\lambda(t_i, P_j)$ accordingly.
 However, the problem is that we cannot find such a $v_x(t_i)$ that can be represented exactly, which means robust classification cannot be performed.
-Fortunately, we observe that we can choose $v_b^2(t_i)$, which is not so close to $\mathbb{I}$ instead.
+Fortunately, we observe that we can choose $v_b^2(t_i)$, which is not so close to $\bm{\mathcal{I}}$ instead.
 To illustrate, assume there is another point $v_{x'}(t_i)$ inside of $t_i$ that is very close to $v_b^2(t_i)$ ({\color{red}{Fig.

### 2016-10-15 summary.tex
10.15

@@
 
-During face classification, we evaluate whether a given face $s$ belongs to the final geometry according to the n-primitive boolean function $f$ :
+During face classification, we evaluate whether a given face $\bm{s}$ belongs to the final geometry according to the n-primitive boolean function $f$ :
 \begin{equation}
@@
 The parameter $\lambda_i(s)$ is space indicator with respect to mesh $P_i$.
-To compute $\lambda_f(s)$ and classify $s$, one has to know the space indicators with respect to all the primitives (denoted as $\boldsymbol{\Lambda}(s)$).
+To compute $\lambda_f(s)$ and classify $\bm{s}$, one has to know the space indicators with respect to all the primitives (denoted as $\boldsymbol{\Lambda}(s)$).
 A space indicator has four conditions: completely inside (\emph{in}), completely outside (\emph{out}), on the boundary with consistent normals (\emph{same}) or opposite normals (\emph{oppo}).
@@
 \includegraphics[width=2.5in]{falseclass}
-\caption{In a 2D view, face $s$ is on the surface of mesh $P$.
-However, because we use barycenter $v_c(s)$ to compute the indicator  and the coordinates of $v_c(s)$ contain round-off error, we might falsely classify $s$ as outside of $P$.}
+\caption{In a 2D view, face $\bm{s}$ is on the surface of mesh $P$.
+However, because we use barycenter $v_c(s)$ to compute the indicator  and the coordinates of $v_c(s)$ contain round-off error, we might falsely classify $\bm{s}$ as outside of $P$.}
 \label{fig:falseclass}
@@
 
+\iffalse
 \begin{figure}
@@
 
-Using Plane-based representation, each face $s$ with $n$ edges is represented by a supporting plane $\bm{p}_{s,sp}$, where the face lies, and a list bounding planes $\{\bm{p}_{s,b}^i \ \vert\  i = 0, 1,...,n-1\}$.
+Using Plane-based representation, each face $\bm{s}$ with $n$ edges is represented by a supporting plane $\bm{p}_{s,sp}$, where the face lies, and a list bounding planes $\{\bm{p}_{s,b}^i \ \vert\  i = 0, 1,...,n-1\}$.
 Each edge line $\bm{e}_s^i$ is represented by intersection $\bm{p}_{s,sp} \cap \bm{p}_{s,b}^i$.
@@
 \includegraphics[width=2in]{iisect}
-\caption{suppose? actual?}
+\caption{suppose? actual?plane-triples}
 \label{fig:iisect}
@@
 The intersection vertices are not only introduced by intersection between an edge and a triangle, but also introduced by intersections of three triangles.
-It is not enough to find all of them by only triangle-triangle intersection tests.
-Also, because of degenerate cases, there will be other forms of intersections involving three or even more triangles.
-To make tessellation easier and more robust, we have to refine these intersections and all unusual conditions have to be removed before it.
+In order to find all intersection vertices, it is not enough by only triangle-triangle intersection tests.
+To make tessellation easier and more robust, we have to refine these intersections and resolve the intersections between intersections.
 
 Intersection refinement is performed in a local scope.
-For each intersecting face $t_i$, we collect all intersections on $t$ as a set $\bm{\Gamma}(t)=\{\bm{\mathcal{I}}_{t}^i, i=0,1,2,...\}\cup\{\bm{\mathcal{I}}_{t}^{e_i},i=0,1,2\}$ and refine them together.
-The set $\{\bm{\mathcal{I}}_{t}^{e_i},i=0,1,2\}$ is the PBI-reps of the three edges of $t$.
-We treat edges as intersections for simplicity in this stage.
-The neighborhood component $\bm{\Psi}(\bm{\mathcal{I}}_{t}^{e_i})$ is set as $\bm{0}$.
-Other components of $\bm{\mathcal{I}}_{t}^{e_i}$ are straightforward to determine.
-Refinement on $\bm{\Gamma}(t)$ is done using only plane-based geometry predicates by the following three steps:
+For each intersecting face $t$ from mesh $P_t$, we collect all intersections on $t$ into a set $\bm{\Gamma}(t)=\{\bm{\mathcal{I}}_{t}^i, i=0,1,2,...\}\cup\{\bm{\mathcal{I}}_{t}^{\bm{e}_i},i=0,1,2\}$ and refine them together.
+The set $\{\bm{\mathcal{I}}_{t}^{\bm{e}_i},i=0,1,2\}$ is the PBI-reps of the three edges of $t$.
+We treat edges as special intersections for simplicity, since edges also participate in tessellation.
+The neighborhood components of the edge $\bm{\Psi}(\bm{\mathcal{I}}_{t}^{\bm{e}_i})$ is set as $\{(P_t, \bm{e}_i )\}$.
+Other components of $\bm{\mathcal{I}}_{t}^{\bm{e}_i}$ can be determined by the P-reps of $\bm{e}_i$.
+The refinement on $\bm{\Gamma}(t)$ is done using only plane-based geometry predicates by the following three steps (Fig.
+x):
 
@@
 The subroutine linear order of points (\S\ref{sec:substrates}) is used to sort these splitting points along $\bm{\mathcal{I}}_{t}^x$.
-The PBI-reps of split segments inherit their father's except the second component the end points.
+The PBI-reps of split segments inherit their father's except the third component which identifies the end points.
 
@@
 The PBI-rep of the new intersection is inherited from either of the old one's except the neighborhood component $\bm{\Psi}$.
+The value element of the new neighborhood is the union of the two old ones'.
+\iffalse 
  We follow the merging rules below:
@@
 \end{equation}
+
 , where $\bm{\mathcal{I}}_{t}^1$ and $\bm{\mathcal{I}}_{t}^2$ are old intersections and $\bm{\mathcal{I}}_{t}^{12}$ is the new one.
+\fi
 
@@
 In Fig.
-x, we illustrate the only two situations.
-In both situations, one intersection is split by other, and the same splitting routine is used as in collinear splitting.
+x, we illustrate the two valid situations.
+In both situations, one intersection is split by the other, and the same splitting routine is used as in collinear splitting.
 
@@
 \label{sec:classification}
-We traverse each face in the hybrid meshes, and classify which one belongs to the final mesh.
+We traverse each face in the intersection-free meshes, and classify which one belongs to the final mesh.
 Classification is done by evaluating the indicator vector of each face.
 The basic idea of our classification method is to utilize the space coherence of face indicator vectors to reuse the classification results.
-Also, because we store the PBI-reps which contains neighborhood information in the edges which intersect other meshes, the search space of point-in-polyhedron test is limited to only a few faces, which makes the indicator computation very fast.
+Because we store the PBI-reps which contains neighborhood information in the edges which intersect other meshes, the search space of point-in-polyhedron test is limited to only a few faces, which makes the indicator computation very fast.
 Also, by using P-reps, our classification method can deal with any degenerate cases.
@@
 The space coherence of indicator vectors means neighboring faces could share the same indicator vector, or most components of indicator vectors.
-Therefore, we start from a seed face $s_0$ with its indicator vector $\bm{\Lambda}(s_0)$ known, and propagate to other faces in a flood-filling manner.
+Therefore, we start from a seed face $\bm{s}_0$ with its indicator vector $\bm{\Lambda}(\bm{s}_0)$ known, and propagate to other faces in a flood-filling manner.
 The trace of indicator propagation is:
@@
 \label{eq:trace}
-s_0\to s_1\to s_2\to s_3\to ...
+\bm{s}_0\to \bm{s}_1\to \bm{s}_2\to \bm{s}_3\to ...
 \end{equation}
@@
 Our hybrid meshes facilitate this process by accelerating the indicator propagation.
-Given adjacent faces $s_1$ and $s_2$, it is straightforward to know whether $\bm{\Lambda}(s_1)$ and $\bm{\Lambda}(s_2)$ are different.
-The two indicator vectors are the same unless the shared edge $e_{12}$ lies on the boundary of some meshes, and it means there is an intersection $\bm{\mathcal{I}}(e_{12})$ stored on $e_{12}$.
-For a certain indicator $\lambda_k$, it always stands:
+Given adjacent faces $\bm{s}_1$ and $\bm{s}_2$, it is straightforward to know whether $\bm{\Lambda}(\bm{s}_1)$ and $\bm{\Lambda}(\bm{s}_2)$ are different.
+The two indicator vectors are the same unless the shared edge $\bm{e}_{12}$ lies on the boundary of some meshes, and it means there is an intersection (denoted as $\bm{\mathcal{I}}(\bm{e}_{12})$) stored on $\bm{e}_{12}$.
+The neighborhood of $\bm{\mathcal{I}}(\bm{e}_{12})$ indicates which components of indicator vector differ between $\bm{s}_1$ and $\bm{s}_2$.
+ \iffalse
+ Namely, for a certain indicator $\lambda_k$ of $\bm{s}_1$ and $\bm{s}_2$, it always stands:
 \begin{equation}
 \label{eq:eq1}
-{\lambda_k}(s_1) = {\lambda_k}(s_2),\ \ \  \mbox{if }\Psi_k(\bm{\mathcal{I}}(e_{12}))= 0.
+{\lambda_k}(\bm{s}_1) = {\lambda_k}(\bm{s}_2),\ \ \  \mbox{if }\Psi_k(\bm{\mathcal{I}}(e_{12}))= 0.
 \end{equation}
-Even if $\Psi_k(\bm{\mathcal{I}}(e_{12})) \neq 0$, both $\lambda_k(t_1)$ and $\lambda_k(t_2)$ can be computed efficiently and exactly according to $\bm{\mathcal{I}}(e_{12})$ (\S\ref{sec:propagation}).
+\fi
+If there is a neighborhood $(P_k, \Psi_k) \in \bm{\Psi}(\bm{\mathcal{I}}(\bm{e}_{12}))$, both $\lambda_k(\bm{s}_1)$ and $\lambda_k(\bm{s}_2)$ can be computed efficiently and exactly according to $\Psi_k$ (\S\ref{sec:propagation}).
 We outline our classification method in Algorithm \ref{code:floodfill}.
@@
 \label{code:floodfill}
-\textbf{Input: } IFH meshes $\bm{P'}$, a boolean function $f$
-
-\textbf{Output: } Classification $f(\bm{\Lambda}(s_i))$, for all faces $s_i$ from $\bm{P'}$
+\textbf{Input: } Intersection-free hybrid meshes, boolean function $f$
+
+\textbf{Output: } Classification $f(\bm{\Lambda}(\bm{s}_i))$ for all faces $\bm{s}_i$
 
 \begin{algorithmic}[1]
-\State Select a proper seed face $s_0$
-\State Compute the first indicator vector $\boldsymbol{\Lambda}(s_0)$
-\State \Call{propagate} { $s_0$ , $\boldsymbol{\Lambda}(s_0)$}
+\State Select a proper seed face $\bm{s}_0$
+\State Compute the seed indicator vector $\boldsymbol{\Lambda}(\bm{s}_0)$
+\State \Call{propagate} { $\bm{s}_0$ , $\boldsymbol{\Lambda}(\bm{s}_0)$}
 \State
-\Function{propagate}{ $s$ , $\boldsymbol{\Lambda}(s)$}
+\Function{propagate}{ $\bm{s}$ , $\boldsymbol{\Lambda}(s)$}
     \State Compute $f(\boldsymbol{\Lambda}(s))$
-    \For {each neighboring face $s_i$}
-        \If {$s_i$ has been classified}
+    \For {each neighboring face $\bm{s}_{s, i}$}
+        \If {$\bm{s}_i$ has been classified}
             \State continue
         \EndIf
-        \If {there are PBI-reps $\{{\bm{\mathcal{I}}}_k\}$ on $e(s_i, s)$}
-            \State compute $\boldsymbol{\Lambda}(s_i)$ by $\boldsymbol{\Lambda}(s)$ and $\{{\bm{\mathcal{I}}}_k\}$
-            \State \Call{propagate} { $s_i$ , $\boldsymbol{\Lambda}(s_i)$}
+        \If {there are PBI-reps ${\bm{\mathcal{I}}}_k$ on $\bm{e}(\bm{s}_{s, i}, s)$}
+            \State compute $\boldsymbol{\Lambda}(\bm{s}_{s, i})$ by $\boldsymbol{\Lambda}(s)$ and ${\bm{\mathcal{I}}}_k$
+            \State \Call{propagate} { $\bm{s}_{s, i}$ , $\boldsymbol{\Lambda}(\bm{s}_{s, i})$}
         \Else
-            \State \Call{propagate} { $s_i$ , $\boldsymbol{\Lambda}(s)$}
+            \State \Call{propagate} { $\bm{s}_{s, i}$ , $\boldsymbol{\Lambda}(s)$}
         \EndIf
@@
 However, using point on the boundary instead of an inner one has another problem.
-Given a face $s$ (may not be triangle) and one of its vertex $v_b^i(s)$, the vertex indicator $\boldsymbol{\Lambda}(v_{i}(s), P_k)$ may cause ambiguity to deduce the face indicator $\boldsymbol{\Lambda}(s, P_k)$.
+Given a face $\bm{s}$ (may not be triangle) and one of its vertex $v_b^i(s)$, the vertex indicator $\boldsymbol{\Lambda}(v_{i}(s), P_k)$ may cause ambiguity to deduce the face indicator $\boldsymbol{\Lambda}(s, P_k)$.
 In {\color{red}{Fig.
 ?}}, $\boldsymbol{\Lambda}(v_b^1(s), P_k) = on$, then $\boldsymbol{\Lambda}(s, P_k)$ can be any of the four conditions.
-We solve this problem by trying other vertices in $s$ for ambiguous indicators.
+We solve this problem by trying other vertices in $\bm{s}$ for ambiguous indicators.
 If all vertices indicators are $on$ and the ambiguity cannot be resolved, the current face is not proper for being the seed and we select a new one instead.
@@
 \label{sec:propagation}
-Now, our meshes consist of vertices, edges and faces.
-Classification is required to perform on face level.
+Meshes consist of vertices, edges and faces.
+Classification is required to perform on the face level.
 However, polyhedron in-out test is performed based on points.
-Conventionally, face inner point such as barycenter is used to compute the indicator of the whole face.
-This is because in intersection-free meshes, face is classified as a whole, and every inner point will have the same indicator as the face's.
-However, the coordinates of inner points cannot be exactly represented by float point numbers, which may lead to wrong predicates, especially when the face lies on the surface of other mesh (Fig.
-x).
-Therefore, we use the vertices, whose exact representations are known, for indicator computation.
-
-%For example, given a face $s$ and one of its vertex $v^i(s)$, if $\lambda_k(v^i(s))=on$, $\lambda_k(s)$ can be any of $on$, $in$ or $out$ (see {\color{red}{Fig. ?}})
+Gaps exist between the them.
+Conventionally, face barycenter is used to compute the indicator of the whole face.
+This is because in intersection-free meshes, face is classified as a whole, and every face inner point will have the same indicator as the face's.
+However, the computation of inner point coordinates requires geometry construction, which introduces errors without exact arithmetic.
+Therefore, we use the vertices instead, whose exact representations are known, for indicator computation.
+
+%For example, given a face $\bm{s}$ and one of its vertex $v^i(s)$, if $\lambda_k(v^i(s))=on$, $\lambda_k(s)$ can be any of $on$, $in$ or $out$ (see {\color{red}{Fig. ?}})
 However, there are two gaps between face indicator and vertex indicator.
 First, the indicator of vertex does not always equal to indicator of face.
-Second, face indicator has two conditions in $on$ case, $same$ and $oppo$, because the face has its orientation.
-
-To solve these problems, we discuss our indicator trace (\ref{eq:trace}) in finer granularity.
-In the beginning, we start from a seed vertex $v_0$ on seed face $s_0$.
-We assume indicator vector $\bm{\Lambda}(v_0)$ is known.
-Then we use $\bm{\Lambda}(v_0)$ to compute $\bm{\Lambda}(s_0)$.
+Second, face indicator has two conditions in $on$ case---$same$ and $oppo$, because the face has its orientation.
+
+To overcome the gaps, we discuss our indicator trace (\ref{eq:trace}) in finer granularity.
+In the beginning, we start from a seed vertex $\bm{v}_0$ on seed face $\bm{s}_0$.
+We assume indicator vector $\bm{\Lambda}(\bm{v}_0)$ is known.
+Then we use $\bm{\Lambda}(\bm{v}_0)$ to compute $\bm{\Lambda}(\bm{s}_0)$.
 In addition, we add the edge layer into the trace.
@@
 \begin{equation}
-v_0\to e_0\to s_0\to e_1\to s_1\to e_2\to s_2\to ...
+\bm{v}_0\to \bm{e}_0\to \bm{s}_0\to \bm{e}_1\to \bm{s}_1\to \bm{e}_2\to \bm{s}_2\to ...
 \end{equation}
-, where $v, e$ means vertex and edge respectively.
-We find that there are three kinds of basic operations in the trace: $v_e\to e$, $e_s\to s$ and $s\to e_s$, where $v_e$ means the vertex is the end point of $e$, and $e_s$ means the edge is the edge of $s$.
+, where $\bm{v}, \bm{e}$ means vertex and edge respectively.
+We find that there are three kinds of basic operations in the trace: $\bm{v}_{\bm{e}}\to \bm{e}$, $\bm{e}_s\to \bm{s}$ and $\bm{s}\to \bm{e}_s$, where $\bm{v}_{\bm{e}}$ means the end point of $\bm{e}$, and $\bm{e}_s$ means the edge of $\bm{s}$.
 
@@
 \label{eq:porder}
-\lambda_k(v_{e_s}) \succeq \lambda_k(e_s) \succeq \lambda_k(s)
+\lambda_k(\bm{v}_{\bm{e}_s}) \succeq \lambda_k(\bm{e}_s) \succeq \lambda_k(s)
 \end{equation}
 , where $\lambda_k(x)$ means the indicator of $x$ against a certain primitive $P_k$.
-This relation can be inferred from continuous space assumption and the definition of intersection-free mesh (def.
-\ref{eq:ifmdef}).
-It tells us when we perform $v_e\to e$ and $e_s\to s$, we decide whether the $on$ indicator change to $in$ or $out$ or remain $on$.
-When we perform $s\to e_s$, we decide whether $in$ and $out$ indicators change to $on$.
-In addition, considering the orientation of face, we also need to figure out whether the $on$ indicators change to $same$ or $oppo$ during $e_s\to s$ operation.
-
-\vspace{0.5em}
-\noindent\textbf{$\bm{s\to e_s}$}~~~~ When $\lambda_k(e_s)=on$, there will be PBI-rep $\bm{\mathcal{I}}(e_s)$ attached to $e_s$ and the related neighborhood $\Psi_k(\bm{\mathcal{I}}(e_s))$ must be nonzero, since it is on the surface of mesh $P_k$:
+This relation can be inferred from continuous space assumption and the definition of intersection-free mesh.
+It tells us when we perform $\bm{v}_{\bm{e}}\to \bm{e}$ and $\bm{e}_{\bm{s}}\to \bm{s}$, we decide whether the $on$ indicator change to $in$ or $out$ or remain $on$.
+When we perform $\bm{s}\to \bm{e}_s$, we decide whether $in$ and $out$ indicators change to $on$.
+In addition, considering the orientation of face, we also need to figure out whether the $on$ indicators change to $same$ or $oppo$ during $\bm{e}_s\to s$ operation.
+
+\vspace{0.5em}
+\noindent\textbf{$\bm{s\to \bm{e}_s}$}~~~~ When $\lambda_k(\bm{e}_s)=on$, there will be PBI-rep $\bm{\mathcal{I}}(\bm{e}_s)$ attached to $\bm{e}_s$ and the related neighborhood $\Psi_k(\bm{\mathcal{I}}(\bm{e}_s))$ must be nonzero, since it is on the surface of mesh $P_k$:
 \begin{equation}
 \label{eq:eq1}
-\lambda_k(e_s)=on,\ \ \  \mbox{iff. }\Psi_k(\bm{\mathcal{I}}(e_s))\neq 0.
+\lambda_k(\bm{e}_s)=on,\ \ \  \mbox{iff. }\Psi_k(\bm{\mathcal{I}}(\bm{e}_s))\neq 0.
 \end{equation}
-So all we need is to iterate over all nonzero components of $\bm{\Psi}(\bm{\mathcal{I}}(e_s))$ and change corresponding indicators to $on$.
-
-\vspace{0.5em}
-\noindent\textbf{$\bm{e_s\to s}$}~~~~From eq.
-\ref{eq:porder}, we know if $\lambda_k(e_s) \neq on$, then $\lambda_k(e_s)=\lambda_k(s)$.
-When $\lambda_k(e_s) = on$, we figure out $\lambda_k(s)$ using $\Psi_k(\bm{\mathcal{I}}(e_s))$.
+So all we need is to iterate over all nonzero components of $\bm{\Psi}(\bm{\mathcal{I}}(\bm{e}_s))$ and change corresponding indicators to $on$.
+
+\vspace{0.5em}
+\noindent\textbf{$\bm{\bm{e}_s\to s}$}~~~~From eq.
+\ref{eq:porder}, we know if $\lambda_k(\bm{e}_s) \neq on$, then $\lambda_k(\bm{e}_s)=\lambda_k(s)$.
+When $\lambda_k(\bm{e}_s) = on$, we figure out $\lambda_k(s)$ using $\Psi_k(\bm{\mathcal{I}}(\bm{e}_s))$.
 From eq.
-\ref{eq:eq1}, we know $\Psi_k(\bm{\mathcal{I}}(e_s)) \neq 0$ and can be either a triangle face or an edge.
-If $\Psi_k(\bm{\mathcal{I}}(e_s))$ is a face, we can build a trivial BSP \cite{thibault1987set} using the face on the space near $e_s$.
-If $\Psi_k(\bm{\mathcal{I}}(e_s))$ is an edge, we can still build BSP using the opposite two faces along $e_s$.
-In both cases, the BSP can be used to compute $\lambda_k(s)$ if we can sample a point from $s$ that near $e_s$.
+\ref{eq:eq1}, we know $\Psi_k(\bm{\mathcal{I}}(\bm{e}_s)) \neq 0$ and can be either a triangle face or an edge.
+If $\Psi_k(\bm{\mathcal{I}}(\bm{e}_s))$ is a face, we can build a trivial BSP \cite{thibault1987set} using the face on the space near $\bm{e}_s$.
+If $\Psi_k(\bm{\mathcal{I}}(\bm{e}_s))$ is an edge, we can still build BSP using the opposite two faces along $\bm{e}_s$.
+In both cases, the BSP can be used to compute $\lambda_k(s)$ if we can sample a point from $\bm{s}$ that near $\bm{e}_s$.
 Unfortunately, we cannot guarantee to find such a point with precise coordinates.
-Instead, we choose a point $v_x$ from the half plane $\bm{p}_{s, sp}^+$, which is on the supporting plane of $s$ and on the positive side of bounding plane $\bm{p}_{s, b}^{e_s}$ (Fig.
+Instead, we choose a point $\bm{v}_x$ from the half plane $\bm{p}_{s, sp}^+$, which is on the supporting plane of $\bm{s}$ and on the positive side of bounding plane $\bm{p}_{s, b}^{\bm{e}_s}$ (Fig.
 x).
-For polygons, there is at least one such $v_x$ among the vertices of $s$.
+For polygons, there is at least one such $\bm{v}_x$ among the vertices of $\bm{s}$.
 We find that the BSP is so simple that indicators $\lambda_k$ of all points on $\bm{p}_{s, sp}^+$ are the same.
-Since $\bm{p}_{s, sp}^+ \cap s \neq \varnothing$, we can compute $\lambda_k(s)$ by figuring out $\lambda_k(v_x)$.
-Also, if we assign each BSP splitting plane a normal by the normal of triangle it contains, we can use it to decide the orientation ($same$ or $oppo$) when $v_x$ is on a splitting plane, which means $\lambda_k(s)=on$.
-
-\vspace{0.5em}
-\noindent\textbf{$\bm{v_e\to e}$}~~~~ While this is yet another propagation from low dimension to high dimension, there is no neighborhood information stored on vertex.
-If $\lambda_k(v_e)=on$, we first check whether $\lambda_k(e) = on$ by (\ref{eq:eq1}).
-If not, we need to find where $v_e$ lies on the surface of $P_k$ and determine the neighborhood of $v_e$.
+Since $\bm{p}_{s, sp}^+ \cap s \neq \varnothing$, we can compute $\lambda_k(s)$ by figuring out $\lambda_k(\bm{v}_x)$.
+Also, if we assign each BSP splitting plane a normal by the normal of triangle it contains, we can use it to decide the orientation ($same$ or $oppo$) when $\bm{v}_x$ is on a splitting plane, which means $\lambda_k(s)=on$.
+
+\vspace{0.5em}
+\noindent\textbf{$\bm{\bm{v}_{\bm{e}}\to e}$}~~~~ While this is yet another propagation from low dimension to high dimension, there is no neighborhood information stored on vertex.
+If $\lambda_k(\bm{v}_{\bm{e}})=on$, we first check whether $\lambda_k(e) = on$ by (\ref{eq:eq1}).
+If not, we need to find where $\bm{v}_{\bm{e}}$ lies on the surface of $P_k$ and determine the neighborhood of $\bm{v}_{\bm{e}}$.
 In most cases, it is straightforward since coincident vertices among different intersection-free meshes are shared.
@@
 The neighborhood may be a vertex, an edge or a face.
-After computing the neighborhood, the same BSP-based classification method is used as in ${e_s\to s}$ to determine the high dimensional $\lambda_k(e)$.
-We use the other vertex of $e$ to be the sample point $v_x$ for the BSP classification.
+After computing the neighborhood, the same BSP-based classification method is used as in ${\bm{e}_s\to s}$ to determine the high dimensional $\lambda_k(e)$.
+We use the other vertex of $e$ to be the sample point $\bm{v}_x$ for the BSP classification.
 
@@
 
-Given a face $t_i$ to be classified and an I-rep $\boldsymbol\Gamma$ of intersection on one of $t_i$'s edge, we denote the three corners it as $v_{b*}^{0}(t_i), v_{b*}^{1}(t_i), v_b^2(t_i),$ where the subscript $*$ means the vertices are on the edge where $\boldsymbol\Gamma$ lies.
+Given a face $t_i$ to be classified and an I-rep $\boldsymbol\Gamma$ of intersection on one of $t_i$'s edge, we denote the three corners it as $\bm{v}_{b*}^{0}(t_i), \bm{v}_{b*}^{1}(t_i), \bm{v}_b^2(t_i),$ where the subscript $*$ means the vertices are on the edge where $\boldsymbol\Gamma$ lies.
 We also denote the context component of $\boldsymbol\Gamma$ as $C_{P_h \backslash P_j}$, meaning $t_i$ is from primitive $P_j$ and intersects primitive $P_h$.
@@
 Since the faces involving in $C_{P_h \backslash P_j}$ is part of primitive $P_j$, the space division $\boldsymbol{D}(C_{P_h \backslash P_j})$ is homogeneous with the space division by $P_j$ in neighborhood of $\bm{\mathcal{I}}$.
-The basic idea is to choose one point $v_x(t_i)$ on $t_i$ close enough to $\bm{\mathcal{I}}$ to compute $\lambda(v_x(t_i), P_j)$, and then compute $\lambda(t_i, P_j)$ accordingly.
-However, the problem is that we cannot find such a $v_x(t_i)$ that can be represented exactly, which means robust classification cannot be performed.
-Fortunately, we observe that we can choose $v_b^2(t_i)$, which is not so close to $\bm{\mathcal{I}}$ instead.
-To illustrate, assume there is another point $v_{x'}(t_i)$ inside of $t_i$ that is very close to $v_b^2(t_i)$ ({\color{red}{Fig.
+The basic idea is to choose one point $\bm{v}_x(t_i)$ on $t_i$ close enough to $\bm{\mathcal{I}}$ to compute $\lambda(\bm{v}_x(t_i), P_j)$, and then compute $\lambda(t_i, P_j)$ accordingly.
+However, the problem is that we cannot find such a $\bm{v}_x(t_i)$ that can be represented exactly, which means robust classification cannot be performed.
+Fortunately, we observe that we can choose $\bm{v}_b^2(t_i)$, which is not so close to $\bm{\mathcal{I}}$ instead.
+To illustrate, assume there is another point $\bm{v}_{x'}(t_i)$ inside of $t_i$ that is very close to $\bm{v}_b^2(t_i)$ ({\color{red}{Fig.
 x}}).
-Because all inner points of $t_i$ have the same indicator, $\lambda(v_x(t_i), P_j) = \lambda(v_{x'}(t_i), P_j)$.
-On the other hand, we find that $\lambda(v_{x'}(t_i), P_j)$ and $\lambda(v_b^2(t_i), P_j)$ are always equal under division $\boldsymbol{D}(C_{P_h \backslash P_j})$ ({\color{red}{see Appendix \ref{app:profind}}}).
-Therefore, $\lambda(v_b^2(t_i), P_j)$ is equal to $\lambda(v_x(t_i), P_j)$ under $\boldsymbol{D}(C_{P_h \backslash P_j})$, and are coherent with $\lambda(t_i, P_j)$ under the division of whole primitive $P_j$.
-One additional thing is that when $\lambda(v_2(t_i), P_j)=on$, then $\lambda(t_i, P_j)$ can be either $same$ or $oppo$.
+Because all inner points of $t_i$ have the same indicator, $\lambda(\bm{v}_x(t_i), P_j) = \lambda(\bm{v}_{x'}(t_i), P_j)$.
+On the other hand, we find that $\lambda(\bm{v}_{x'}(t_i), P_j)$ and $\lambda(\bm{v}_b^2(t_i), P_j)$ are always equal under division $\boldsymbol{D}(C_{P_h \backslash P_j})$ ({\color{red}{see Appendix \ref{app:profind}}}).
+Therefore, $\lambda(\bm{v}_b^2(t_i), P_j)$ is equal to $\lambda(\bm{v}_x(t_i), P_j)$ under $\boldsymbol{D}(C_{P_h \backslash P_j})$, and are coherent with $\lambda(t_i, P_j)$ under the division of whole primitive $P_j$.
+One additional thing is that when $\lambda(\bm{v}_2(t_i), P_j)=on$, then $\lambda(t_i, P_j)$ can be either $same$ or $oppo$.
 The normal orientation test have to be performed to eliminate such ambiguity.
@@
 \vspace{0.5em}
-\noindent\textbf{Seed indicator generation}~~~~In \S\ref{sec:propagation}, we claim that our flood-filling starts from a seed vertex $v_0$.
-While the indicator vector of the seed $\bm{\Lambda}(v_0)$ can be generated by point-in-polyhedron test \cite{ogayar2005point} with the octree as acceleration structure \cite{frisken2002simple}, we have simpler strategies by using vertex with known indicators as the seed.
+\noindent\textbf{Seed indicator generation}~~~~In \S\ref{sec:propagation}, we claim that our flood-filling starts from a seed vertex $\bm{v}_0$.
+While the indicator vector of the seed $\bm{\Lambda}(\bm{v}_0)$ can be generated by point-in-polyhedron test \cite{ogayar2005point} with the octree as acceleration structure \cite{frisken2002simple}, we have simpler strategies by using vertex with known indicators as the seed.
 We choose the `peak vertex` with the max x coordinate as the seed.
-In this way, $\lambda_k(v_0)$ is either $out$ ($in$, if complement is applied on mesh) or $on$.
+In this way, $\lambda_k(\bm{v}_0)$ is either $out$ ($in$, if complement is applied on mesh) or $on$.
 The $on$ indicators are easy to determine in most time.
@@
 \noindent\textbf{Indicator up-propagation}~~~~
-In \S\ref{sec:propagation}, we point out that up-propagation (from low dimension to high dimension, $v_e\to e$ and $e_s\to s$, etc.) can be done by using sample points.
-Here we give use a heuristic method to prove our claim in $e_s\to s$.
-Extension to $v_e\to e$ should not take much effort.
-
-\vspace{0.5em}\noindent We prove $\lambda_k(v_x)=\lambda_k(v_{\delta})$ in the BSP of $e_s$'s neighborhood, where $ v_x$ is the sample point from $\bm{p}_{s, sp}^+$ and $v_{\delta}$ is from the neighborhood $U(e_s, \delta)$.
-If $\lambda_k(v_x) \neq on$, then
-
-Given $v_{x'}(t_i)$ can be arbitrarily close to $v_b^2(t_i)$, if $\lambda(v_b^2(t_i), P_j) = in | out$, the equality holds because of the continuity of space.
-If $\lambda(v_b^2(t_i), P_j) = on$, we divide the proof of equality into two parts according to the type of intersection context.
+In \S\ref{sec:propagation}, we point out that up-propagation (from low dimension to high dimension, $\bm{v}_{\bm{e}}\to e$ and $\bm{e}_s\to s$, etc.) can be done by using sample points.
+Here we give use a heuristic method to prove our claim in $\bm{e}_s\to s$.
+Extension to $\bm{v}_{\bm{e}}\to e$ should not take much effort.
+
+\vspace{0.5em}\noindent We prove $\lambda_k(\bm{v}_x)=\lambda_k(\bm{v}_{\delta})$ in the BSP of $\bm{e}_s$'s neighborhood, where $ \bm{v}_x$ is the sample point from $\bm{p}_{s, sp}^+$ and $\bm{v}_{\delta}$ is from the neighborhood $U(\bm{e}_s, \delta)$.
+If $\lambda_k(\bm{v}_x) \neq on$, then
+
+Given $\bm{v}_{x'}(t_i)$ can be arbitrarily close to $\bm{v}_b^2(t_i)$, if $\lambda(\bm{v}_b^2(t_i), P_j) = in | out$, the equality holds because of the continuity of space.
+If $\lambda(\bm{v}_b^2(t_i), P_j) = on$, we divide the proof of equality into two parts according to the type of intersection context.
 If $C_{P_h \backslash P_j}$ is face neighboring type, $\boldsymbol{D}(C_{P_h \backslash P_j})$ is a single face, say, $t_0^c$.
-We have already know that the other two corners $v_{b*}^{0}(t_i)$ and $v_{b*}^{1}(t_i)$ are on $s_0$.
-Since $\lambda(v_b^2(t_i), P_j) = on$, we know $v_b^2(t_i)$ is on $t_0^c$, too.
+We have already know that the other two corners $\bm{v}_{b*}^{0}(t_i)$ and $\bm{v}_{b*}^{1}(t_i)$ are on $\bm{s}_0$.
+Since $\lambda(\bm{v}_b^2(t_i), P_j) = on$, we know $\bm{v}_b^2(t_i)$ is on $t_0^c$, too.
 There comes the conclusion that the whole triangle $t_i$ is coplanar with $t_0^c$.
-Therefore, $v_{x'}(t_i)$ is on $t_0^c$ and $\lambda(v_{x'}(t_i), P_j) = on$, too.
+Therefore, $\bm{v}_{x'}(t_i)$ is on $t_0^c$ and $\lambda(\bm{v}_{x'}(t_i), P_j) = on$, too.
 On the other hand, if $C_{P_h \backslash P_j}$ is edge neighboring type, $\boldsymbol{D}(C_{P_h \backslash P_j})$ are two neighboring faces (denoted as $t_1^c, t_2^c$).
-We know that both $v_{b*}^{0}(t_i)$ and $v_{b*}^{1}(t_i)$ are on the shared edge $e(v_{b*}^{0}(t_i), v_{b*}^{1}(t_i))$.
+We know that both $\bm{v}_{b*}^{0}(t_i)$ and $\bm{v}_{b*}^{1}(t_i)$ are on the shared edge $e(\bm{v}_{b*}^{0}(t_i), \bm{v}_{b*}^{1}(t_i))$.
 It means both vertices are on both $t_1^c$ and $t_2^c$.
-Using the same deduction of the first condition, we can conclude $\lambda(v_{x'}(t_i), P_j) = on$ whenever $\lambda(v_b^2(t_i), P_j) = on$.
+Using the same deduction of the first condition, we can conclude $\lambda(\bm{v}_{x'}(t_i), P_j) = on$ whenever $\lambda(\bm{v}_b^2(t_i), P_j) = on$.
 
@@
 \vspace{0.5em}
-\noindent\textbf{Classification acceleration}~~~~If the CSG tree is large with hundreds of primitive nodes, computing $\lambda_f(s_x)$ from $\boldsymbol{\Lambda}(s_x)$ for every face $s_x$ can be costly.
-Thanks to the indicator space coherence, we can save the computation time by caching the evaluation result $f(\boldsymbol{\Lambda}(s_x))$ during flood-filling.
-
-The basic cache strategy is to cache final result, that is, the value of $\lambda_f(s_x)$.
+\noindent\textbf{Classification acceleration}~~~~If the CSG tree is large with hundreds of primitive nodes, computing $\lambda_f(\bm{s}_x)$ from $\boldsymbol{\Lambda}(\bm{s}_x)$ for every face $\bm{s}_x$ can be costly.
+Thanks to the indicator space coherence, we can save the computation time by caching the evaluation result $f(\boldsymbol{\Lambda}(\bm{s}_x))$ during flood-filling.
+
+The basic cache strategy is to cache final result, that is, the value of $\lambda_f(\bm{s}_x)$.
 We know indicator vector will not change if there is no intersections during propagation.
-That means the final classification $\lambda_f(s_x)$ will not change, too.
+That means the final classification $\lambda_f(\bm{s}_x)$ will not change, too.
 Thus, those faces sharing the same indicator vector can be classified as a whole.
@@
 Also, we can perform intermediate results cache.
-We noticed that the boolean expression can be simplified if some components of $\boldsymbol{\Lambda}(s_x)$ is fixed.
+We noticed that the boolean expression can be simplified if some components of $\boldsymbol{\Lambda}(\bm{s}_x)$ is fixed.
 For example, assume we have a boolean expression $f = P_1\cup (P_2\cap P_3-P_4)$.
-Given the values of two indicators $\lambda_1(s_x)=out$, $\lambda_2(s_x)=in$, the expression can be rewritten as $f(\lambda_1=out, \lambda_2=in)=out\cup (in\cap P_3-P_4)$.
+Given the values of two indicators $\lambda_1(\bm{s}_x)=out$, $\lambda_2(\bm{s}_x)=in$, the expression can be rewritten as $f(\lambda_1=out, \lambda_2=in)=out\cup (in\cap P_3-P_4)$.
 Using the combination rules we can simplify the expression as $f(\lambda_1=out, \lambda_2=in)=P_3-P_4$.
@@
 Therefore, we can first determine these fixed indicators and simplify the boolean function, and then use simplified one to compute the final indicator for each faces in $P_k$.
+
+\vspace{0.5em}
+\noindent\textbf{Extend to piece-wise wind number mesh}~~~~Recent works claim that the piece-wise wind number (PWN) are more powerful to identify the inside and outside of meshes \cite{zhou2016mesh}.
+Our method is straightforward to apply PWN because we can use the neighborhoods of intersections to compute the PWN of each point easily.
+By using PWN, we can extend our input from regular set mesh without self-intersection to so-called PWN mesh that allows deficiencies such as self-intersection and multi-component.
+However, the cost of this extension is that we have to check every triangle pairs for intersections, even if they are from the same input mesh.
+Considering this cost, we prefer a pre-computation to resolve topology deficiencies only on those input meshes that we think that might be 'unclean'.
 

### 2016-10-15 summary.tex
done with text

@@
     \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
+  % declare the path(\bm{s}) where your graphic files are
     \graphicspath{{./pics/}}
@@
   % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
+  % declare the path(\bm{s}) where your graphic files are
   % \graphicspath{{../eps/}}
@@
 \begin{equation}
-\lambda_f(s) = f(\boldsymbol{\Lambda}(s)) = f(\lambda_1(s), \lambda_2(s), \cdots, \lambda_n(s)).
+\lambda_f(\bm{s}) = f(\boldsymbol{\Lambda}(\bm{s})) = f(\lambda_1(\bm{s}), \lambda_2(\bm{s}), \cdots, \lambda_n(\bm{s})).
 \end{equation}
-The parameter $\lambda_i(s)$ is space indicator with respect to mesh $P_i$.
-To compute $\lambda_f(s)$ and classify $\bm{s}$, one has to know the space indicators with respect to all the primitives (denoted as $\boldsymbol{\Lambda}(s)$).
+The parameter $\lambda_i(\bm{s})$ is space indicator with respect to mesh $P_i$.
+To compute $\lambda_f(\bm{s})$ and classify $\bm{s}$, one has to know the space indicators with respect to all the primitives (denoted as $\boldsymbol{\Lambda}(\bm{s})$).
 A space indicator has four conditions: completely inside (\emph{in}), completely outside (\emph{out}), on the boundary with consistent normals (\emph{same}) or opposite normals (\emph{oppo}).
@@
 \caption{In a 2D view, face $\bm{s}$ is on the surface of mesh $P$.
-However, because we use barycenter $v_c(s)$ to compute the indicator  and the coordinates of $v_c(s)$ contain round-off error, we might falsely classify $\bm{s}$ as outside of $P$.}
+However, because we use barycenter $v_c(\bm{s})$ to compute the indicator  and the coordinates of $v_c(\bm{s})$ contain round-off error, we might falsely classify $\bm{s}$ as outside of $P$.}
 \label{fig:falseclass}
@@
   \item Coincident vertices between different Linked Halfedge should be linked, that is, coincident vertices are shared among Linked Halfedges.
-  \item If a certain edge of Linked Halfedge is coincident with intersection line segment(s), it should be associated with the corresponding intersection context(s).
+  \item If a certain edge of Linked Halfedge is coincident with intersection line segment(\bm{s}), it should be associated with the corresponding intersection context(\bm{s}).
 \end{itemize}
@@
 Using Plane-based representation, each face $\bm{s}$ with $n$ edges is represented by a supporting plane $\bm{p}_{s,sp}$, where the face lies, and a list bounding planes $\{\bm{p}_{s,b}^i \ \vert\  i = 0, 1,...,n-1\}$.
-Each edge line $\bm{e}_s^i$ is represented by intersection $\bm{p}_{s,sp} \cap \bm{p}_{s,b}^i$.
+Each edge line $\bm{e}_{\bm{s}}^i$ is represented by intersection $\bm{p}_{s,sp} \cap \bm{p}_{s,b}^i$.
 Corner vertex $\bm{v}_s^i$ is represented by intersection $\bm{p}_{s,sp} \cap \bm{p}_{s,b}^i \cap \bm{p}_{s,b}^{{(i+1)}\bmod{n}}$.
@@
 \State
-\Function{propagate}{ $\bm{s}$ , $\boldsymbol{\Lambda}(s)$}
-    \State Compute $f(\boldsymbol{\Lambda}(s))$
+\Function{propagate}{ $\bm{s}$ , $\boldsymbol{\Lambda}(\bm{s})$}
+    \State Compute $f(\boldsymbol{\Lambda}(\bm{s}))$
     \For {each neighboring face $\bm{s}_{s, i}$}
@@
         \If {there are PBI-reps ${\bm{\mathcal{I}}}_k$ on $\bm{e}(\bm{s}_{s, i}, s)$}
-            \State compute $\boldsymbol{\Lambda}(\bm{s}_{s, i})$ by $\boldsymbol{\Lambda}(s)$ and ${\bm{\mathcal{I}}}_k$
+            \State compute $\boldsymbol{\Lambda}(\bm{s}_{s, i})$ by $\boldsymbol{\Lambda}(\bm{s})$ and ${\bm{\mathcal{I}}}_k$
             \State \Call{propagate} { $\bm{s}_{s, i}$ , $\boldsymbol{\Lambda}(\bm{s}_{s, i})$}
         \Else
-            \State \Call{propagate} { $\bm{s}_{s, i}$ , $\boldsymbol{\Lambda}(s)$}
+            \State \Call{propagate} { $\bm{s}_{s, i}$ , $\boldsymbol{\Lambda}(\bm{s})$}
         \EndIf
@@
 However, using point on the boundary instead of an inner one has another problem.
-Given a face $\bm{s}$ (may not be triangle) and one of its vertex $v_b^i(s)$, the vertex indicator $\boldsymbol{\Lambda}(v_{i}(s), P_k)$ may cause ambiguity to deduce the face indicator $\boldsymbol{\Lambda}(s, P_k)$.
+Given a face $\bm{s}$ (may not be triangle) and one of its vertex $v_b^i(\bm{s})$, the vertex indicator $\boldsymbol{\Lambda}(v_{i}(\bm{s}), P_k)$ may cause ambiguity to deduce the face indicator $\boldsymbol{\Lambda}(s, P_k)$.
 In {\color{red}{Fig.
-?}}, $\boldsymbol{\Lambda}(v_b^1(s), P_k) = on$, then $\boldsymbol{\Lambda}(s, P_k)$ can be any of the four conditions.
+?}}, $\boldsymbol{\Lambda}(v_b^1(\bm{s}), P_k) = on$, then $\boldsymbol{\Lambda}(s, P_k)$ can be any of the four conditions.
 We solve this problem by trying other vertices in $\bm{s}$ for ambiguous indicators.
@@
 
-%For example, given a face $\bm{s}$ and one of its vertex $v^i(s)$, if $\lambda_k(v^i(s))=on$, $\lambda_k(s)$ can be any of $on$, $in$ or $out$ (see {\color{red}{Fig. ?}})
+%For example, given a face $\bm{s}$ and one of its vertex $v^i(\bm{s})$, if $\lambda_k(v^i(\bm{s}))=on$, $\lambda_k(\bm{s})$ can be any of $on$, $in$ or $out$ (see {\color{red}{Fig. ?}})
 However, there are two gaps between face indicator and vertex indicator.
@@
 , where $\bm{v}, \bm{e}$ means vertex and edge respectively.
-We find that there are three kinds of basic operations in the trace: $\bm{v}_{\bm{e}}\to \bm{e}$, $\bm{e}_s\to \bm{s}$ and $\bm{s}\to \bm{e}_s$, where $\bm{v}_{\bm{e}}$ means the end point of $\bm{e}$, and $\bm{e}_s$ means the edge of $\bm{s}$.
+We find that there are three kinds of basic operations in the trace: $\bm{v}_{\bm{e}}\to \bm{e}$, $\bm{e}_{\bm{s}}\to \bm{s}$ and $\bm{s}\to \bm{e}_{\bm{s}}$, where $\bm{v}_{\bm{e}}$ means the end point of $\bm{e}$, and $\bm{e}_{\bm{s}}$ means the edge of $\bm{s}$.
 
@@
 \label{eq:porder}
-\lambda_k(\bm{v}_{\bm{e}_s}) \succeq \lambda_k(\bm{e}_s) \succeq \lambda_k(s)
+\lambda_k(\bm{v}_{\bm{e}_{\bm{s}}}) \succeq \lambda_k(\bm{e}_{\bm{s}}) \succeq \lambda_k(\bm{s})
 \end{equation}
@@
 This relation can be inferred from continuous space assumption and the definition of intersection-free mesh.
-It tells us when we perform $\bm{v}_{\bm{e}}\to \bm{e}$ and $\bm{e}_{\bm{s}}\to \bm{s}$, we decide whether the $on$ indicator change to $in$ or $out$ or remain $on$.
-When we perform $\bm{s}\to \bm{e}_s$, we decide whether $in$ and $out$ indicators change to $on$.
-In addition, considering the orientation of face, we also need to figure out whether the $on$ indicators change to $same$ or $oppo$ during $\bm{e}_s\to s$ operation.
-
-\vspace{0.5em}
-\noindent\textbf{$\bm{s\to \bm{e}_s}$}~~~~ When $\lambda_k(\bm{e}_s)=on$, there will be PBI-rep $\bm{\mathcal{I}}(\bm{e}_s)$ attached to $\bm{e}_s$ and the related neighborhood $\Psi_k(\bm{\mathcal{I}}(\bm{e}_s))$ must be nonzero, since it is on the surface of mesh $P_k$:
-\begin{equation}
-\label{eq:eq1}
-\lambda_k(\bm{e}_s)=on,\ \ \  \mbox{iff. }\Psi_k(\bm{\mathcal{I}}(\bm{e}_s))\neq 0.
-\end{equation}
-So all we need is to iterate over all nonzero components of $\bm{\Psi}(\bm{\mathcal{I}}(\bm{e}_s))$ and change corresponding indicators to $on$.
-
-\vspace{0.5em}
-\noindent\textbf{$\bm{\bm{e}_s\to s}$}~~~~From eq.
-\ref{eq:porder}, we know if $\lambda_k(\bm{e}_s) \neq on$, then $\lambda_k(\bm{e}_s)=\lambda_k(s)$.
-When $\lambda_k(\bm{e}_s) = on$, we figure out $\lambda_k(s)$ using $\Psi_k(\bm{\mathcal{I}}(\bm{e}_s))$.
-From eq.
-\ref{eq:eq1}, we know $\Psi_k(\bm{\mathcal{I}}(\bm{e}_s)) \neq 0$ and can be either a triangle face or an edge.
-If $\Psi_k(\bm{\mathcal{I}}(\bm{e}_s))$ is a face, we can build a trivial BSP \cite{thibault1987set} using the face on the space near $\bm{e}_s$.
-If $\Psi_k(\bm{\mathcal{I}}(\bm{e}_s))$ is an edge, we can still build BSP using the opposite two faces along $\bm{e}_s$.
-In both cases, the BSP can be used to compute $\lambda_k(s)$ if we can sample a point from $\bm{s}$ that near $\bm{e}_s$.
+It tells us when we perform $\bm{v}_{\bm{e}}\to \bm{e}$ and $\bm{e}_{\bm{s}}\to \bm{s}$, we decide whether the $on$ indicator changes to $in$ or $out$ or remains $on$.
+When we perform $\bm{s}\to \bm{e}_{\bm{s}}$, we decide whether $in$ and $out$ indicators change to $on$.
+In addition, considering the orientation of face, we also need to figure out whether the $on$ indicators changes to $same$ or $oppo$ during $\bm{e}_{\bm{s}}\to \bm{s}$ operation.
+
+\vspace{0.5em}
+\noindent\textbf{$\bm{s\to \bm{e}_{\bm{s}}}$}~~~~ When $\lambda_k(\bm{e}_{\bm{s}})=on$, there will be intersection $\bm{\mathcal{I}}(\bm{e}_{\bm{s}})$ attached to $\bm{e}_{\bm{s}}$ and the related neighborhood $\Psi_k$ in $\bm{\mathcal{I}}(\bm{e}_{\bm{s}})$.
+Therefore, in this operation, all we need is to iterate over all components of $\bm{\Psi}(\bm{\mathcal{I}}(\bm{e}_{\bm{s}}))$ and change corresponding indicators to $on$.
+
+\vspace{0.5em}
+\noindent\textbf{$\bm{\bm{e}_{\bm{s}}\to \bm{s}}$}~~~~From eq.
+\ref{eq:porder}, we know if $\lambda_k(\bm{e}_{\bm{s}}) \neq on$, then $\lambda_k(\bm{e}_{\bm{s}})=\lambda_k(\bm{s})$.
+When $\lambda_k(\bm{e}_{\bm{s}}) = on$, we figure out $\lambda_k(\bm{s})$ using $\Psi_k$ from $\bm{\Psi}(\bm{\mathcal{I}}(\bm{e}_{\bm{s}}))$.
+We know $\Psi_k$ and can be either a triangle face or an edge from mesh $P_k$.
+If $\Psi_k$ is a face, we can build a trivial BSP \cite{thibault1987set} using the face on the space near $\bm{e}_{\bm{s}}$.
+If $\Psi_k$ is an edge, we can still build BSP using the faces adjacent to $\bm{e}_{\bm{s}}$.
+In both cases, the BSP can be used to compute $\lambda_k(\bm{s})$ if we can sample a point from $\bm{s}$ that near $\bm{e}_{\bm{s}}$.
 Unfortunately, we cannot guarantee to find such a point with precise coordinates.
-Instead, we choose a point $\bm{v}_x$ from the half plane $\bm{p}_{s, sp}^+$, which is on the supporting plane of $\bm{s}$ and on the positive side of bounding plane $\bm{p}_{s, b}^{\bm{e}_s}$ (Fig.
+Instead, we choose a point $\bm{v}_x$ from the half plane $\bm{p}_{\bm{s}, sp}^+$, which is on the supporting plane of $\bm{s}$ and on the positive side of bounding plane $\bm{p}_{\bm{s}, b}^{\bm{e}_{\bm{s}}}$ (Fig.
 x).
 For polygons, there is at least one such $\bm{v}_x$ among the vertices of $\bm{s}$.
-We find that the BSP is so simple that indicators $\lambda_k$ of all points on $\bm{p}_{s, sp}^+$ are the same.
-Since $\bm{p}_{s, sp}^+ \cap s \neq \varnothing$, we can compute $\lambda_k(s)$ by figuring out $\lambda_k(\bm{v}_x)$.
-Also, if we assign each BSP splitting plane a normal by the normal of triangle it contains, we can use it to decide the orientation ($same$ or $oppo$) when $\bm{v}_x$ is on a splitting plane, which means $\lambda_k(s)=on$.
+We find that the BSP is so simple that indicators $\lambda_k$ of all points on $\bm{p}_{\bm{s}, sp}^+$ are the same.
+Since $\bm{p}_{\bm{s}, sp}^+ \cap \bm{s} \neq \varnothing$, we can compute $\lambda_k(\bm{s})$ by figuring out $\lambda_k(\bm{v}_x)$.
+Also, if we assign each BSP splitting plane a normal by the normal of triangle it contains, we can use it to decide the orientation ($same$ or $oppo$) when $\bm{v}_x$ is on a splitting plane, which means $\lambda_k(\bm{s})=on$.
 
@@
 \noindent\textbf{$\bm{\bm{v}_{\bm{e}}\to e}$}~~~~ While this is yet another propagation from low dimension to high dimension, there is no neighborhood information stored on vertex.
-If $\lambda_k(\bm{v}_{\bm{e}})=on$, we first check whether $\lambda_k(e) = on$ by (\ref{eq:eq1}).
+If $\lambda_k(\bm{v}_{\bm{e}})=on$, we first check whether $\lambda_k(\bm{e}) = on$ by checking the neighborhood component of the intersection on $\bm{e}$.
 If not, we need to find where $\bm{v}_{\bm{e}}$ lies on the surface of $P_k$ and determine the neighborhood of $\bm{v}_{\bm{e}}$.
@@
 The neighborhood may be a vertex, an edge or a face.
-After computing the neighborhood, the same BSP-based classification method is used as in ${\bm{e}_s\to s}$ to determine the high dimensional $\lambda_k(e)$.
-We use the other vertex of $e$ to be the sample point $\bm{v}_x$ for the BSP classification.
+After computing the neighborhood, the same BSP-based classification method is used as in ${\bm{e}_{\bm{s}}\to \bm{s}}$ to determine the high dimension indicator $\lambda_k(\bm{e})$.
+We use the other end point of $\bm{e}$ to be the sample point for the BSP classification.
 
@@
 \cite{feito2013fast} had noticed that intersection neighborhood can be used for fast classification of faces around that intersection.
-According to their method, faces adjacent to intersection have neighbors from other primitive(s) that define the position and orientation for each other, by which the indicators are determined.
+According to their method, faces adjacent to intersection have neighbors from other primitive(\bm{s}) that define the position and orientation for each other, by which the indicators are determined.
 However, Feito et.
@@
 From previous discussion (section \ref{sec:ir}){\color{red}{may be more than one}}, we know there are two types of intersection context---face neighborhood and edge neighborhood.
-In both conditions, the one or two faces involving in the context split the space into two in and out space by its (their) orientation(s).
+In both conditions, the one or two faces involving in the context split the space into two in and out space by its (their) orientation(\bm{s}).
 We will see that under such division (denoted as $\boldsymbol{D}(C_{P_h \backslash P_j})$), we can compute $\lambda(t_i, P_j)$ exactly.
@@
 \vspace{0.5em}\noindent There is another problem that the tess-graph may not be a connected graph.
-We avoid this problem by inserting fake-intersections into the tess-graph.
-An fake intersection links the vertex of face (on the outer connected component) with the vertex on the inner connected component.
-The intersection refinement has to be performed again if the fake intersections cross any other intersections.
-To guarantee the fake intersection has a valid PBI-rep, we require the vertex from inner connected component generated by edge-face intersection, which means it is introduced during triangle-triangle intersection test.
-In this way, we can find an exact plane with the fake intersection on it (Fig.
+We avoid this problem by inserting auxiliary intersections into the tess-graph to make it connected.
+An auxiliary intersection links the vertex of face on the outer connected component with the vertex on the inner connected component.
+The intersection refinement has to be performed again if the auxiliary intersections cross any other intersections.
+To guarantee the auxiliary intersection has a valid PBI-rep, we require the vertex from inner connected component generated by edge-face intersection, which means it is introduced during triangle-triangle intersection test.
+In this way, we can find an exact plane with the auxiliary intersection on it (Fig.
 x).
@@
 While the indicator vector of the seed $\bm{\Lambda}(\bm{v}_0)$ can be generated by point-in-polyhedron test \cite{ogayar2005point} with the octree as acceleration structure \cite{frisken2002simple}, we have simpler strategies by using vertex with known indicators as the seed.
-We choose the `peak vertex` with the max x coordinate as the seed.
+We choose the vertex with the max $x$-coordinate as the seed.
 In this way, $\lambda_k(\bm{v}_0)$ is either $out$ ($in$, if complement is applied on mesh) or $on$.
 The $on$ indicators are easy to determine in most time.
-Though sometimes exception occur because of multi-coplanar situation, this will not happen if we carefully choose the right peak vertex whose neighbor faces are not coplanar (Fig.
+Though sometimes exception occur because of multi-coplanar situation, this will not happen if we carefully choose the right vertex whose neighbor faces are not coplanar (Fig.
 x).
@@
 \noindent\textbf{Indicator up-propagation}~~~~
-In \S\ref{sec:propagation}, we point out that up-propagation (from low dimension to high dimension, $\bm{v}_{\bm{e}}\to e$ and $\bm{e}_s\to s$, etc.) can be done by using sample points.
-Here we give use a heuristic method to prove our claim in $\bm{e}_s\to s$.
+In \S\ref{sec:propagation}, we point out that up-propagation (from low dimension to high dimension, $\bm{v}_{\bm{e}}\to e$ and $\bm{e}_{\bm{s}}\to s$, etc.) can be done by using sample points.
+Here we give use a heuristic method to prove our claim in $\bm{e}_{\bm{s}}\to s$.
 Extension to $\bm{v}_{\bm{e}}\to e$ should not take much effort.
 
-\vspace{0.5em}\noindent We prove $\lambda_k(\bm{v}_x)=\lambda_k(\bm{v}_{\delta})$ in the BSP of $\bm{e}_s$'s neighborhood, where $ \bm{v}_x$ is the sample point from $\bm{p}_{s, sp}^+$ and $\bm{v}_{\delta}$ is from the neighborhood $U(\bm{e}_s, \delta)$.
+\vspace{0.5em}\noindent We prove $\lambda_k(\bm{v}_x)=\lambda_k(\bm{v}_{\delta})$ in the BSP of $\bm{e}_{\bm{s}}$'s neighborhood, where $ \bm{v}_x$ is the sample point from $\bm{p}_{s, sp}^+$ and $\bm{v}_{\delta}$ is from the neighborhood $U(\bm{e}_{\bm{s}}, \delta)$.
 If $\lambda_k(\bm{v}_x) \neq on$, then
@@
 \vspace{0.5em}
-\noindent\textbf{Incremental evaluation}~~~~While we claim in many CSGs, a non-incremental evaluation is faster by avoiding repetitive computation, one can easily find counter-examples that non-incremental evaluation contains useless intersection computation.
+\noindent\textbf{Incremental evaluation}~~~~While we claim that in many CSGs, a non-incremental evaluation is faster by avoiding repetitive computation, one can easily find counter-examples that non-incremental evaluation contains useless intersection computation.
 For example, if 100 spheres densely locate in a small region, each sphere will need to intersect with other 99 spheres.
-However, if evaluating incrementally, we do not need computing so many intersections.
+However, if evaluating incrementally, we might not need to compute so many intersections.
 Fortunately, our method can also perform incremental evaluation.
-For exactness and robustness, we have to deal with non-triangle input meshes in incremental evaluations and intersection vertices should not be converted to float-point.
+For exactness and robustness, we have to deal with non-triangle input meshes in incremental evaluations and intersection vertices should not be converted to float-point coordinate representation.
 
@@
 \vspace{0.5em}\noindent The only different part is intersection computation.
-The first step of M\''{o}ller's triangle-triangle intersection method is to test each edge-plane pair respectively.
-This idea can be transferred to polygon intersections without any change.
-Then we can get two plane-face intersections $Seg1$ and $Seg2$, except that in polygon cases, $Seg1$ and $Seg2$ are two sets of line segments, not single segments.
-And the later processes are the same.
-
-\vspace{0.5em}
-\noindent\textbf{Classification acceleration}~~~~If the CSG tree is large with hundreds of primitive nodes, computing $\lambda_f(\bm{s}_x)$ from $\boldsymbol{\Lambda}(\bm{s}_x)$ for every face $\bm{s}_x$ can be costly.
-Thanks to the indicator space coherence, we can save the computation time by caching the evaluation result $f(\boldsymbol{\Lambda}(\bm{s}_x))$ during flood-filling.
-
-The basic cache strategy is to cache final result, that is, the value of $\lambda_f(\bm{s}_x)$.
-We know indicator vector will not change if there is no intersections during propagation.
-That means the final classification $\lambda_f(\bm{s}_x)$ will not change, too.
+The first step of M\"{o}ller's triangle-triangle intersection method is to test each edge-plane pair respectively.
+This idea can be extended to polygon intersections.
+Then we can get two plane-face intersections $Seg1$ and $Seg2$, except that in polygon cases, $Seg1$ and $Seg2$ are two sets of line segments, instead of single segments.
+Later processes are the same.
+
+\vspace{0.5em}
+\noindent\textbf{Classification acceleration}~~~~If the CSG tree is large with hundreds of primitive nodes, computing $\lambda_f(\bm{s}_i)$ from $\boldsymbol{\Lambda}(\bm{s}_i)$ for every face $\bm{s}_i$ can be costly.
+Thanks to the indicator space coherence, we can save the computation time by caching the evaluation result $f(\boldsymbol{\Lambda}(\bm{s}_i))$ during flood-filling.
+
+The basic cache strategy is to cache final result, that is, the value of $\lambda_f(\bm{s}_i)$.
+We know indicator vector will not change if there is no intersections on the edge during propagation.
+That means the final classification $\lambda_f(\bm{s}_i)$ will not change, too.
 Thus, those faces sharing the same indicator vector can be classified as a whole.
@@
 Also, we can perform intermediate results cache.
-We noticed that the boolean expression can be simplified if some components of $\boldsymbol{\Lambda}(\bm{s}_x)$ is fixed.
+We noticed that the boolean expression can be simplified if some components of $\boldsymbol{\Lambda}(\bm{s}_i)$ is fixed.
 For example, assume we have a boolean expression $f = P_1\cup (P_2\cap P_3-P_4)$.
-Given the values of two indicators $\lambda_1(\bm{s}_x)=out$, $\lambda_2(\bm{s}_x)=in$, the expression can be rewritten as $f(\lambda_1=out, \lambda_2=in)=out\cup (in\cap P_3-P_4)$.
+Given the values of two indicators $\lambda_1(\bm{s}_i)=out$, $\lambda_2(\bm{s}_i)=in$, the expression can be rewritten as $f(\lambda_1=out, \lambda_2=in)=out\cup (in\cap P_3-P_4)$.
 Using the combination rules we can simplify the expression as $f(\lambda_1=out, \lambda_2=in)=P_3-P_4$.
-This fact is important because for a large CSG, a certain primitive (denoted as $P_k$) often only intersects with a few other primitives $\Theta(P_k)= \{P_{n_1}, P_{n_2}, \cdots, P_{n_k}\}$.
+This fact is important because for a large CSG, a certain primitive (denoted as $P_k$) often intersects with only a few other meshes $\Theta(P_k)= \{P_{n_1}, P_{n_2}, \cdots, P_{n_x}\}$.
 That means all the faces in $P_k$ has the same indicators $\lambda_{i}, P_{i} \notin \Theta(P_k)$.
@@
 In this paper, we proposed a novel method to evaluate CSG with triangular mesh primitives.
-It is able to efficiently perform non-incremental evaluation of large CSG with massive faces.
-The key idea of our approach is to use the local coherence of face space labels to accelerate face membership classification.
-A two-level grouping framework is developed to group neighboring faces together and thus space labels can be shared within each group.
-This scheme saves much time for space label computation, which is often very time-consuming for conventional Boolean evaluation algorithms.
-Additionally, in order to be robust, plane-based geometry computation is introduced into the intersection computation step of our approach.
+It is able to efficiently perform unconditionally robust non-incremental boolean operations of CSG with massive faces.
+The key idea of our approach is to strictly follow the principle of plane-based geometry, avoiding geometry construction all along the method.
+Also, we use the local coherence of face space labels to accelerate face membership classification.
 Experiments have verified the proposed approach is more efficient than the state-of-the-art techniques while retaining robustness and stability.
-We will further investigate the robust tessellation in future.
 

### 2016-10-16 summary.tex
10.17
Signed-off-by: RUI WANG <RUI WANG>

@@
 \includegraphics[width=2.5in]{falseclass}
-\caption{In a 2D view, face $\bm{s}$ is on the surface of mesh $P$.
-However, because we use barycenter $v_c(\bm{s})$ to compute the indicator  and the coordinates of $v_c(\bm{s})$ contain round-off error, we might falsely classify $\bm{s}$ as outside of $P$.}
+\caption{In a 2D view, face $\bm{s}$ from $P_2$ is on the surface of mesh $P_1$.
+However, because we use face barycenter $\bm{v}_c$ to compute the indicator, the coordinates of $\bm{v}_c$ contain round-off error and move to $\bm{v}'_c$, we might falsely classify $\bm{s}$ as outside of $P_2$.}
 \label{fig:falseclass}
@@
 \begin{wrapfigure}{r}[0in]{0in}
-\includegraphics[width=1.2in]{p-reps}
+\includegraphics[width=1.5 in]{p-reps}
 %\caption{Plane-based representation of triangle}
@@
 \centering
-\includegraphics[width=2in]{pbi}
+\includegraphics[width=3.5in]{pbirep}
 \caption{Triangle $t_1$ and $t_2$ are from mesh $P_i, P_j$ respectively.
@@
 \centering
-\includegraphics[width=3.5in]{twin}
-\caption{Six situations of edge intersections.
+\includegraphics[width=3.5in]{edgeisect}
+\caption{Six situations of edge interse ctions.
 The first three subgraphs are edge-face intersections.

### 2016-11-20 summary.tex
SDASDASDASDSADAS

@@
 
+\subsection{Classification Acceleration}
+\label{sec:acc}
+If the CSG tree is large with hundreds of primitive nodes, computing $\lambda_f(\bm{s}_i)$ from $\boldsymbol{\Lambda}(\bm{s}_i)$ for every face $\bm{s}_i$ can be costly.
+Thanks to the indicator space coherence, we can save the computation time by caching the evaluation result $f(\boldsymbol{\Lambda}(\bm{s}_i))$ during flood-filling.
+
+The basic cache strategy is to cache final result, that is, the value of $\lambda_f(\bm{s}_i)$.
+We know indicator vector will not change if there is no intersections on the edge during propagation.
+That means the final classification $\lambda_f(\bm{s}_i)$ will not change, too.
+Thus, those faces sharing the same indicator vector can be classified as a whole.
+
+Also, we can perform intermediate results cache.
+We noticed that the boolean expression can be simplified if some components of $\boldsymbol{\Lambda}(\bm{s}_i)$ is fixed.
+For example, assume we have a boolean expression $f = P_1\cup (P_2\cap P_3-P_4)$.
+Given the values of two indicators $\lambda_1(\bm{s}_i)=out$, $\lambda_2(\bm{s}_i)=in$, the expression can be rewritten as $f(\lambda_1=out, \lambda_2=in)=out\cup (in\cap P_3-P_4)$.
+Using the combination rules we can simplify the expression as $f(\lambda_1=out, \lambda_2=in)=P_3-P_4$.
+This fact is important because for a large CSG, a certain primitive (denoted as $P_k$) often intersects with only a few other meshes $\Theta(P_k)= \{P_{n_1}, P_{n_2}, \cdots, P_{n_x}\}$.
+That means all the faces in $P_k$ has the same indicators $\lambda_{i}, P_{i} \notin \Theta(P_k)$.
+Therefore, we can first determine these fixed indicators and simplify the boolean function, and then use simplified one to compute the final indicator for each faces in $P_k$.
+
+\subsection{Deferred Tessellation}
+We find for a CSG with many meshes, a large percentage of intersections are not necessary to produce the final result (Fig.
+\ref{}).
+Thus tessellating according to every detected intersections is not necessary.
+Using the accelerating strategy in \S\ref{sec:acc}, we can use the intersections information of faces to give an early prediction of whether the face have to be tessellated.
+
 \iffalse
@@
 \fi
-
-\section{Discussion}
-
-\vspace{0.5em}
-
-\subsection{Essential Subroutines}
+\section{Experiments}
+
+\begin{table*}[ht]
+\caption{Computation Time Statistics (Seconds)}
+\label{tab:performance}
+\centering
+\begin{tabular}{*{13}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
+\hline
+\multirow{2}{*}{No.} & \multirow{2}{*}{Figure} & \multicolumn{3}{c|}{Face Num.$^\nabla$} & \multirow{2}{*}{\tabincell{c}{Primitive\\Count}} & \multirow{2}{*}{\tabincell{c}{CGAL}} & \multirow{2}{*}{\tabincell{c}{Maya}} & \multirow{2}{*}{\tabincell{c}{Cork/Carve}} & \multirow{2}{*}{\tabincell{c}{QuickCSG}}& \multicolumn{4}{c}{Our Approach}\\
+\cline{3-5} \cline{11-14}
+ & & Total & Min & Max &&&&&& Total$^\circ$ & Step 1 & Step 2 & Step 3\\
+\hline \hline
+1 & \ref{fig:models}(a) & 37.6K & 180 & 1.6K & 201 & 1350 & 49.9 & - & 15.9 & \textbf{3.13}  & 0.328 & 1.69 & 0.922 \\
+2 & \ref{fig:models}(a) & 146K & 180 & 1.6K & 801  & TLE & 1400 & TLE & Fail* & \textbf{12.8}  & 1.36 & 6.41 & 4.00 \\
+3 & \ref{fig:models}(b) & 377K & 2.56K & 346K & 7 & TLE & 224.5 & 45.7 & 11.7 & \textbf{1.44} & 0.438 & 0.062 & 0.563 \\
+4 & \ref{fig:models}(c) & 79.2K & 12 & 38.2K & 4  & 97.6 & Fail & 3.58 & 1.69 & \textbf{0.563}  & 0.187 & 0.141 & 0.172 \\
+5 & \ref{fig:models}(d) & 36K & 800 & 2.4K & 29 & 34.1 & 7.03 & 18.7 & 4.05 & \textbf{0.313} & 0.094 & 0.094 & 0.081 \\
+6 & \ref{fig:models}(e) & 597K & 96.9K & 500K & 2 & TLE & 38.3 & 26.4 & 5.63 & \textbf{2.13} & 0.563 & 0.031 & 0.984 \\
+7 & \ref{fig:models}(f) & 170K & 69.7K & 100K & 2  & 218 & 7.45 & 13.8 & 2.39 & \textbf{0.891} & 0.328 & 0.125 & 0.266 \\
+8 & \ref{fig:models}(g) & 362K & 6.91K & 276K & 22 & TLE & 344 & 256 & 19.2 & \textbf{1.80} & 0.766 & 0.172 & 0.593 \\
+9 & \ref{fig:budda} & 2.16M & 1.08M & 1.08M & 2 & Fail & Fail & MLE$^\bullet$ & Fail & \textbf{11.3} & 5.55 & 1.36 & 3.01 \\
+\hline
+\end{tabular}
+\begin{flushleft}
+$^{\nabla}$~~\emph{Min} (\emph{Max}) means the minimum (maximum) number of faces of a single primitive.
+
+$^{\circ}$~~The total computation time of our method includes the construction of half-edge structure and the three steps in Section \ref{sec:overview}.
+
+\end{flushleft}
+\end{table*}
+
+We implemented the proposed method in C++ and tested a series of models on a laptop with Intel Core i5 1.5GHz CPU and 8GB RAM.
+To prove both the efficiency and robustness, we perform boolean evaluation on various CSGs with different complexity.
+Extreme degenerate cases such as self-union are also tested.
+
+We compared our method with several previous works with available implementations, including CGAL \cite{cgal:hk-bonp3-15a}, Maya \cite{Maya2015,barki2015exact},"Cork" \cite{Cork}, "QuickCSG" \cite{douze2015quickcsg}, "Carve" \cite{Carve}, and online service of Campen and Kobbelt's plane-based method \cite{campen2010exact,WebBSP}.
+
+\vspace{0.5em}
+\noindent\textbf{Coplanar and self-union}~~~~
+Our method is unconditionally robust for regular set meshes.
+Even extreme degenerate cases will not cause invalid output.
+To prove that, we tested the self-union of several models and some CSG with coplanar faces.
+We find that our method always produces visually correct results.
+QuickCSG and Cork failed to produce the result in most of these cases, because they cannot deal with coplanar faces.
+Even after perturbation, the result meshes are still full with deficiencies (holes, boundary edges, etc.).
+For the bunny model, we found our result face count was slightly deviation from the original mesh.
+This is because the original mesh contains self-intersection in the bunny chest (the green faces).
+
+\vspace{0.5em}
+\noindent\textbf{Binary boolean operations}~~~~
+The most common situation of CSG evaluation is to perform boolean operations one by one, since many designers are used to change the model progressly.
+While our method can evaluate multiple boolean operations once for all, we compared the performance of binary boolean operations to prove the efficiency.
+Table \ref{tab:performance} shows the evaluation time of different methods.
+We can clearly see our method is very fast that is only slightly slower than the fastest non-robust QuickCSG.
+Other robust methods such as Maya and CGAL are much slower because both of them use the arbitrary precision arithmetic.
+It should be noted that in some cases (), most time is spent on octree construction.
+It means other stages which involve plane-based geometry take only a small percentage of time, proving the efficiency of our plane-based geometry.
+
+\vspace{0.5em}
+\noindent\textbf{CSGs with many primitives}~~~~
+To identify the ability of evaluating large CSG, we also test some CSG with tens or hundreds of meshes.
+Maya and CGAL cannot perform multiple boolean operations, so we can only give the comparison of incremental boolean evaluation.
+We
+
+\section{Essential Subroutines}
 \label{sec:esubroutine}
@@
 
-\subsection{Extensions}
+\section{Extensions}
 
@@
 \vspace{0.5em}
-\noindent\textbf{Classification acceleration}~~~~If the CSG tree is large with hundreds of primitive nodes, computing $\lambda_f(\bm{s}_i)$ from $\boldsymbol{\Lambda}(\bm{s}_i)$ for every face $\bm{s}_i$ can be costly.
-Thanks to the indicator space coherence, we can save the computation time by caching the evaluation result $f(\boldsymbol{\Lambda}(\bm{s}_i))$ during flood-filling.
-
-The basic cache strategy is to cache final result, that is, the value of $\lambda_f(\bm{s}_i)$.
-We know indicator vector will not change if there is no intersections on the edge during propagation.
-That means the final classification $\lambda_f(\bm{s}_i)$ will not change, too.
-Thus, those faces sharing the same indicator vector can be classified as a whole.
-
-Also, we can perform intermediate results cache.
-We noticed that the boolean expression can be simplified if some components of $\boldsymbol{\Lambda}(\bm{s}_i)$ is fixed.
-For example, assume we have a boolean expression $f = P_1\cup (P_2\cap P_3-P_4)$.
-Given the values of two indicators $\lambda_1(\bm{s}_i)=out$, $\lambda_2(\bm{s}_i)=in$, the expression can be rewritten as $f(\lambda_1=out, \lambda_2=in)=out\cup (in\cap P_3-P_4)$.
-Using the combination rules we can simplify the expression as $f(\lambda_1=out, \lambda_2=in)=P_3-P_4$.
-This fact is important because for a large CSG, a certain primitive (denoted as $P_k$) often intersects with only a few other meshes $\Theta(P_k)= \{P_{n_1}, P_{n_2}, \cdots, P_{n_x}\}$.
-That means all the faces in $P_k$ has the same indicators $\lambda_{i}, P_{i} \notin \Theta(P_k)$.
-Therefore, we can first determine these fixed indicators and simplify the boolean function, and then use simplified one to compute the final indicator for each faces in $P_k$.
-
-\vspace{0.5em}
 \noindent\textbf{Extend to piece-wise wind number mesh}~~~~Recent works claim that the piece-wise wind number (PWN) are more powerful to identify the inside and outside of meshes \cite{zhou2016mesh}.
@@
 \fi
-
-\section{Experiments}
 

### 2016-11-21 summary.tex
cao

--- 2016-10-16 summary.tex
@@
 
+We use Campen et al.'s method \cite{campen2010exact} for exact conversion of triangles from their vertex-based representation to plane-based representation.
+During the conversion, the coordinates of input vertices is rounded to certain precision which is dependent on the precision used to represent plane coefficients during boolean operation.
+If IEEE 754 double precision float-point number is used, 20-bit precision is allowed, which is enough for most CAD applications.
 As the precision of input coordinates is finite, we can determine in advance the upper boundary of precision needed to perform a precise decision, with which we can use fixed precision predicates to improve performance.
@@
 
-\subsection{Conversion}
-
-\label{sec:convert}
-
-We use Campen et al.'s method \cite{campen2010exact} for exact conversion of triangles from their vertex-based representation to plane-based representation.
+\iffalse
 Given that the input vertex coordinate has $L$-bit precision including sign, the precisions of the four plane coefficients are $L_a, L_b, L_c, L_d$, which have to satisfy the following requirements:
@@
 If we use IEEE 754 double float point number ($M=53$) and assume $\delta \le 2^{-5.5} \approx 0.022$, the maximum input precision $L$ can reach to 20, which is enough for most application (for standard IEEE 754 single float point number, the precision is 24-bit).
-
-\subsection{Substrates}
+\fi
+
 \label{sec:substrates}
@@
 Most of them are well-discussed in previous work \cite{bernstein2009fast,banerjee1996topologically}.
-In the following, we focus on two advanced plane-based predicates, which are also important building blocks of our method.
+In the following, we focus on two advanced predicates, which are also important building blocks of our method.
 
@@
 
-Since all the three vectors on the right side are already explicitly represented, we only have to evaluate the sign of an 3x3 matrix and avoid complicated high precision float-point arithmetic.
+Since all the three vectors on the right side are already explicitly represented, we only have to evaluate the sign of an 3$\times$3 matrix and avoid complicated high precision float-point arithmetic.
 \begin{figure}
@@
   % Requires \usepackage{graphicx}
-  \includegraphics[width=2.5in]{twopointoneline}\\
+  \includegraphics[width=3.5in]{twopointoneline}\\
   \caption{The configuration of linear ordering of points.
 Points $\bm{v}_a$ and $\bm{v}_b$ are both on line $\bm{l}_{ab}$.
-We convert this problem into the plane ordering between $\bm{p}_a$ and $\bm{p}_b$ along $\bm{l}_{ab}$.}\label{fig:twopointoneline}
+We convert this problem into the plane ordering of $\bm{p}_a$ and $\bm{p}_b$ along $\bm{l}_{ab}$.}\label{fig:twopointoneline}
 \end{figure}
@@
 \centering
-\includegraphics[width=2.5in]{circularorder}
+\includegraphics[width=3.5in]{circularorder}
 \caption{The configuration of circular ordering of lines. $\bm{l}_a\colon(\bm{p}_0 \cap \bm{p}_a)$ and $\bm{l}_b\colon(\bm{p}_0 \cap \bm{p}_b)$ are coplanar in $\bm{p}_0$.}
@@
 \label{sec:embed}
-According to the method described in \S\ref{sec:convert}, triangle faces $t$ are firstly converted to its P-rep: a supporting plane $\bm{p}_{t, sp}$ surrounded by three bounding planes $\{\bm{p}_{t, b}^i|\ i = 0,1,2\}$.
+Given a triangle face $t$, it is firstly converted to its P-rep: a supporting plane $\bm{p}_{t, sp}$ surrounded by three bounding planes $\{\bm{p}_{t, b}^i|\ i = 0,1,2\}$.
 We integrate the plane-based geometry into each of the tree steps of M\"{o}ller's algorithm as following:
@@
   \item[1)] The basic subroutine of the first step is given two faces $t_1$ and $t_2$, computing the orientation of of a face with respect to vertices from the other face.
-Reviewing the discussion of \S \ref{sec:convert}, under the constraint of $M \ge P+1$, we can compute the predicate within the precision of $M$ bits.
+We find that since the exact coordinates of each triangle corners are known, we can compute the point-plane orientation within the precision of plane coefficients---namely, using simple fix float-point arithmetic.
 This allow us to perform this early rejection efficiently.
@@
 The word 'cross' do not only include the situation that a face is partly outside and partly inside of a primitive, but also can mean that a face is partly inside (outside) and part on the boundary of the primitive.
+
+\iffalse
 \begin{figure}[t]
@@
 \includegraphics[width=3.5in]{isolated}
-\caption{Two situations of point intersections.
+%\caption{Two situations of point intersections.
 (a) $\bm{v}_{iso}$ is isolated, and there is no adjacent intersection line segment.
@@
 \label{sec:ipoint}
-If two triangles intersect on a single point (Fig.
-\ref{fig:isolated}), the intersection cannot be represented using our four-component description.
-Therefore, we simply add the intersection point into the related triangles to guarantee correct tessellation, and no intersection is introduced.
+If two triangles intersect on a single point (e.g., Fig.
+\ref{fig:isect}d), the intersection cannot be represented using our four-component description since the line segment collapses into a single point.
+In these cases, we simply add the intersection point into the related triangles to guarantee correct tessellation, and no intersection is introduced.
 
@@
 we call it \emph{edge intersection}.
-The only difference between edge intersection and the general case is the neighborhood representation $\Psi$.
-The space near edge intersection is decided by both face in the two side of the intersected edge, instead of just one triangle face (Fig.
+The speciality of edge intersection is the neighborhood representation $\Psi$.
+The space near edge intersection is divided by both face in the two side of the intersected edge, instead of just one triangle face (Fig.
 X).
-Therefore, supposing intersection is on the edge $\bm{e}_{k, i}$ of mesh $P_k$, then the neighborhood $\Psi_k = \bm{e}_{k, i}$.
+Therefore, supposing intersection is on the edge $\bm{e}_{k, i}$ of mesh $P_k$, we denote the neighborhood as $\Psi_k = \bm{e}_{k, i}$.
 Note that an intersection can be on edges from different meshes.
@@
 
-The key observation is that intersection in 2D does not create new valid edges.
-The word `valid` means the edge is necessary or possibly necessary for the final result mesh.
+The key observation is that intersections in 2D are either duplicated added or invalid.
+The word `valid` means the intersections will appear as an edge in the final mesh.
+Namely, faces of intersection neighborhood have different classification results:
+\begin{equation}
+\lambda_f(\bm{s^i}) = f(\bm{\Lambda}(\bm{s}_i)) = constant, \bm{s}^i \in \mathcal{N}(\mathcal{I})
+\end{equation}
+, where $f$ is the CSG function, and $\bm{s}^i \in \mathcal{N}(\mathcal{I})$ is the neighboring faces of intersection $\mathcal{I}$.
+In principle, the validation of intersection is not known until classification stage.
+However, we can perform an early rejection to eliminate intersections that are invalid in certain.
+
 We find that each intersection line segment in 2D is on the edges from input meshes.
@@
 However, if the companion triangles are also coplanar, neither of the two triangles will record the intersection.
-In fact, we do not need to worry about this, because in this case, the intersection is not valid.
-The two sides of the intersection are both retained or both dropped and we do not need it for tessellation.
+Fortunately, in this case, the intersection is not valid.
+The two sides of the intersection have the same indicators and are both retained or both dropped and we do not need it for tessellation.
 
@@
 
+\subsection{Acceleration by Caching}
+\label{sec:acc}
+If the CSG tree is large with hundreds of primitive nodes, computing $\lambda_f(\bm{s}_i)$ from $\boldsymbol{\Lambda}(\bm{s}_i)$ for every face $\bm{s}_i$ can be costly.
+Thanks to the indicator space coherence, we can save the computation time by caching the evaluation result $f(\boldsymbol{\Lambda}(\bm{s}_i))$ during flood-filling.
+
+The basic cache strategy is to cache final result, that is, the value of $\lambda_f(\bm{s}_i)$.
+We know indicator vector will not change if there is no intersections on the edge during propagation.
+That means the final classification $\lambda_f(\bm{s}_i)$ will not change, too.
+Thus, those faces sharing the same indicator vector can be classified as a whole.
+
+Also, we can perform intermediate results cache.
+We noticed that the boolean expression can be simplified if some components of $\boldsymbol{\Lambda}(\bm{s}_i)$ is fixed.
+For example, assume we have a boolean expression $f = P_1\cup (P_2\cap P_3-P_4)$.
+Given the values of two indicators $\lambda_1(\bm{s}_i)=out$, $\lambda_2(\bm{s}_i)=in$, the expression can be rewritten as $f(\lambda_1=out, \lambda_2=in)=out\cup (in\cap P_3-P_4)$.
+Using the combination rules we can simplify the expression as $f(\lambda_1=out, \lambda_2=in)=P_3-P_4$.
+This fact is important because for a large CSG, a certain primitive (denoted as $P_k$) often intersects with only a few other meshes $\Theta(P_k)= \{P_{n_1}, P_{n_2}, \cdots, P_{n_x}\}$.
+That means all the faces in $P_k$ has the same indicators $\lambda_{i}, P_{i} \notin \Theta(P_k)$.
+Therefore, we can first determine these fixed indicators and simplify the boolean function, and then use simplified one to compute the final indicator for each faces in $P_k$.
+
+\subsection{Tessellating on Classification}
+We find for a CSG with many meshes, a large percentage of intersections are invalid (see \S\ref{sec:degenerate} for 'invalid').
+Tessellation according to these invalid intersections is not necessary.
+To avoid unnecessary tessellation, we can give an early prediction of which intersections are invalid by intersections information of faces, but have to embed the tessellation stage into the classification stage, which we call it 'tessellating on classification'.
+
+In most situations, a certain faces $\bm{s}$ only intersect with a few other meshes $\Theta(\bm{s})$.
+We can use the same cache strategy in \S\ref{sec:acc} to shrink the original CSG into a smaller one by the common indicators of $\{P_i\}\backslash\Theta(\bm{s})$, where $\{P_i\}$ means all the primitive meshes.
+After the shrinking, the primitive meshes of the CSG must be from $\Theta(\bm{s})$.
+If any mesh in $\Theta(\bm{s})$ does not appear in the shrinked CSG, it means the indicator of that mesh does not change the classification result, which in another word, intersections on $\bm{s}$ from that mesh are invalid and do not affect the classification of any subfaces of $\bm{s}$.
+If the shrinked CSG is trivial which does not contain any primitives, it means $\bm{s}$ does not need tessellation.
+In this way, we save the computation time, and simplify the topology of the final result mesh.
+Because we can only shrink the CSG for $\bm{s}$ when we classify it---before that the indicators of meshes from $\{P_i\}\backslash\Theta(\bm{s})$ are not known---we do not perform tessellation until we do the classification.
+
 \iffalse
@@
 
-\section{Discussion}
-
-\vspace{0.5em}
-
-\subsection{Essential Subroutines}
+\section{Essential Subroutines}
 \label{sec:esubroutine}
@@
 In order to be robust, we use the high-precision face barycenter with the point-in-polyhedron test to generate the seed indicator vector instead after several failures of choosing a proper seed face.
+
+\section{Experiments}
+
+\begin{table*}[ht]
+\caption{Computation Time Statistics of Binary Boolean Operation (Seconds)}
+\label{tab:performance}
+\centering
+\begin{tabular}{*{9}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
+\hline
+{No.} & {Figure} & {Triangle Num. 1} & {Triangle Num. 2} &
+CGAL & Maya & Cork & Carve & QuickCSG & Our Method
+\\
+\hline\hline
+1 & budda \& lion & 1.08M & 0.4M & - & - & - & - & 3.44 & 6.88\\
+2 & dragon \& bunny & 277k & 70k & - & - & - & - & - & -\\
+3 & armadillo \& armadillo* & 150k & 150k & - & - & - & - & - & -\\
+4 & horse \& corpse & 150k & 150k & - & - & - & - & - & -\\
+5 & dinasour \& ironman & 150k & 150k & - & - & - & - & - & -\\
+\hline
+\end{tabular}
+\begin{flushleft}
+
+\end{flushleft}
+\end{table*}
+
+\begin{table*}[ht]
+\caption{Computation Time Statistics of Large CSG Evaluation (Seconds)}
+\label{tab:performance}
+\centering
+\begin{tabular}{*{9}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
+\hline
+{No.} & {Figure} & {Triangle Num.} & {Primitive Num.} &
+CGAL* & Maya* & Cork & Carve & QuickCSG & Our Method
+\\
+\hline\hline
+1 & Sprocket & 1.08M & 0.4M & - & - & - & - & 3.44 & 6.88\\
+2 & ring and ball & 277k & 70k & - & - & - & - & - & -\\
+3 & t1 & 150k & 150k & - & - & - & - & - & -\\
+4 & t2 & 150k & 150k & - & - & - & - & - & -\\
+5 & h & 150k & 150k & - & - & - & - & - & -\\
+6 & Organic & 150k & 150k & - & - & - & - & - & -\\
+7 & 6 Budda & 150k & 150k & - & - & - & - & - & -\\
+8 & Serpent & 150k & 150k & - & - & - & - & - & -\\
+9 & Dithering & 150k & 150k & - & - & - & - & - & -\\
+\hline
+\end{tabular}
+\begin{flushleft}
+$^{\nabla}$~~\emph{Min} (\emph{Max}) means the minimum (maximum) number of faces of a single primitive.
+
+$^{\circ}$~~The total computation time of our method includes the construction of half-edge structure and the three steps in Section \ref{sec:overview}.
+
+\end{flushleft}
+\end{table*}
+
+We implemented the proposed method in C++ and tested a series of models on a laptop with Intel Core i5 1.5GHz CPU and 8GB RAM.
+To prove both the efficiency and robustness, we perform boolean evaluation on various CSGs with different complexity.
+Extreme degenerate cases such as self-union are also tested.
+
+We compared our method with several previous works with available implementations, including CGAL \cite{cgal:hk-bonp3-15a}, Maya \cite{Maya2015,barki2015exact},"Cork" \cite{Cork}, "QuickCSG" \cite{douze2015quickcsg}, "Carve" \cite{Carve}, and online service of Campen and Kobbelt's plane-based method \cite{campen2010exact,WebBSP}.
+
+\vspace{0.5em}
+\noindent\textbf{Coplanar and self-union}~~~~
+Our method is unconditionally robust for regular set meshes.
+Even extreme degenerate cases will not cause invalid output.
+To prove that, we tested the self-union of several models and some CSG with coplanar faces.
+We find that our method always produces visually correct results.
+QuickCSG and Cork failed to produce the result in most of these cases, because they cannot deal with coplanar faces.
+Even after perturbation, their results are still full with deficiencies (holes, boundary edges, etc.).
+For the bunny model, we found our result face count was slightly deviated from the original mesh.
+This is because the original mesh contains self-intersection in the bunny chest (the green faces), which causes errors during classification.
+
+\vspace{0.5em}
+\noindent\textbf{Binary boolean operations}~~~~
+The most common situation of CSG evaluation is to perform boolean operations one by one, since many designers are used to modify models progressively.
+While our method can evaluate multiple boolean operations once for all, we also compared the performance of binary boolean operations to prove the efficiency.
+Table \ref{tab:performance} shows the evaluation time of different methods.
+We can clearly see our method is very fast that is only slightly slower than the fastest non-robust QuickCSG.
+Other robust methods such as Maya and CGAL are much slower because both of them use the arbitrary precision arithmetic.
+It should be noted that in some cases (), most time is spent on octree construction in our method.
+It means other stages which involve plane-based geometry take only a small percentage of time, proving the efficiency of our plane-based geometry.
+
+\vspace{0.5em}
+\noindent\textbf{CSGs with large number of meshes}~~~~
+To identify the ability of evaluating large CSG, we also test some CSG with tens or hundreds of meshes.
+Maya and CGAL cannot perform multiple boolean operations, so we can only give the comparison of incremental boolean evaluation for these methods.
+We see that the computation time of robust methods like CGAL and Maya grows rapidly when the number of meshes grows.
+On the other hand, our method keeps good performance while stay robust.
+During our experiments, we noticed Maya gives the correct results in the first few boolean operations, but failed in the later ones.
+It proves another disadvantage of incremental boolean operation methods: if it cannot guarantee exactness, it will accumulate numerical errors which affects the algorithm stability.
 
@@
 \vspace{0.5em}
-\noindent\textbf{Classification acceleration}~~~~If the CSG tree is large with hundreds of primitive nodes, computing $\lambda_f(\bm{s}_i)$ from $\boldsymbol{\Lambda}(\bm{s}_i)$ for every face $\bm{s}_i$ can be costly.
-Thanks to the indicator space coherence, we can save the computation time by caching the evaluation result $f(\boldsymbol{\Lambda}(\bm{s}_i))$ during flood-filling.
-
-The basic cache strategy is to cache final result, that is, the value of $\lambda_f(\bm{s}_i)$.
-We know indicator vector will not change if there is no intersections on the edge during propagation.
-That means the final classification $\lambda_f(\bm{s}_i)$ will not change, too.
-Thus, those faces sharing the same indicator vector can be classified as a whole.
-
-Also, we can perform intermediate results cache.
-We noticed that the boolean expression can be simplified if some components of $\boldsymbol{\Lambda}(\bm{s}_i)$ is fixed.
-For example, assume we have a boolean expression $f = P_1\cup (P_2\cap P_3-P_4)$.
-Given the values of two indicators $\lambda_1(\bm{s}_i)=out$, $\lambda_2(\bm{s}_i)=in$, the expression can be rewritten as $f(\lambda_1=out, \lambda_2=in)=out\cup (in\cap P_3-P_4)$.
-Using the combination rules we can simplify the expression as $f(\lambda_1=out, \lambda_2=in)=P_3-P_4$.
-This fact is important because for a large CSG, a certain primitive (denoted as $P_k$) often intersects with only a few other meshes $\Theta(P_k)= \{P_{n_1}, P_{n_2}, \cdots, P_{n_x}\}$.
-That means all the faces in $P_k$ has the same indicators $\lambda_{i}, P_{i} \notin \Theta(P_k)$.
-Therefore, we can first determine these fixed indicators and simplify the boolean function, and then use simplified one to compute the final indicator for each faces in $P_k$.
-
-\vspace{0.5em}
-\noindent\textbf{Extend to piece-wise wind number mesh}~~~~Recent works claim that the piece-wise wind number (PWN) are more powerful to identify the inside and outside of meshes \cite{zhou2016mesh}.
+\noindent\textbf{Extend to piece-wise wind number meshes}~~~~Recent works claim that the piece-wise wind number (PWN) are more powerful to identify the inside and outside of meshes \cite{zhou2016mesh}.
 Our method is straightforward to apply PWN because we can use the neighborhoods of intersections to compute the PWN of each point easily.

### 2016-11-22 summary.tex
ao ye!!!!

@@
 \title{Efficient, Robust and Exact Boolean Operations on N Triangular Mesh Primitives}
-\author{Rui~Wang,~
-        Xudong~Jiang,~
-        Hongbo~Fu,~
-        Bin~Sheng,~
-        Ping Li~and
-        Enhua~Wu
+\author{%Rui~Wang,~
+        %Xudong~Jiang,~
+        %Hongbo~Fu,~
+        %Ping~Li,~
+        %Bin~Sheng~and
+        %Enhua~Wu
 \IEEEcompsocitemizethanks{
@@
 
-We develop a boolean operation method based on B-reps of meshes with geometry connectivity (e.g., halfedge \cite{mcguire2000half}).
-Additionally, we embed P-rep of faces into the B-rep, forming a hybrid representation, which allows us to take the advantage of both representations for robustness and efficiency.
+Our method is based on B-reps of meshes with geometry connectivity (e.g., halfedge \cite{mcguire2000half}).
+We embed P-rep of faces into the B-rep, forming a hybrid representation, which allows us to take the advantage of both representations for robustness and efficiency.
 This hybrid representation requires only one-time conversion from B-rep to P-rep in intersection areas of meshes.
@@
 
-In our method, intersection between two triangles is denoted as $\bm{\mathcal{I}}\colon\{t, \bm{p}_{ext}, (\bm{p}^0, \bm{p}^1),\bm{\Psi}\}$, which is called plane-based intersection representation (PBI-rep).
+In our method, intersection on triangle $t$ is denoted as $\bm{\mathcal{I}}\colon\{t, \bm{p}_{ext}, (\bm{p}^0, \bm{p}^1),(P, \mathcal{N})\}$, which is called plane-based intersection representation (PBI-rep).
 The first component $t$ indicates $\bm{\mathcal{I}}$ is on triangle $t$, and second one $\bm{p}_{ext}$ indicates $\bm{\mathcal{I}}$ lies on $\bm{p}_{ext}$, which also means it lies on line $\bm{p}_{t, sp} \cap \bm{p}_{ext}$.
 The two end points of $\bm{\mathcal{I}}$ are $\bm{p}_{t, sp} \cap \bm{p}_{ext}\cap\bm{p}^0$ and $\bm{p}_{t, sp} \cap \bm{p}_{ext}\cap\bm{p}^1$.
-The last component $\bm{\Psi}$ is a set that represents the neighborhood of the intersection.
-If $\bm{\mathcal{I}}$ is on the surface of mesh $P_k$, an element $(P_{k}, \Psi_{k})$ is added to $\bm{\Psi}$, where $\Psi_{k}$ is the edge or face of $P_k$ where $\bm{\mathcal{I}}$ lies.
+The last component $(P, \mathcal{N})$ represents the neighborhood of the intersection $\bm{\mathcal{I}}$.
+It indicates $\bm{\mathcal{I}}$ is intersection of triangle $t$ with $\mathcal{N}$ from mesh $P$, where $\mathcal{N}$ can be either a edge or a face.
 
@@
 They intersect on line segment, generating intersection $\bm{\mathcal{I}}_{12}$ on $t_1$ and $\bm{\mathcal{I}}_{21}$ on $t_2$.
-The PBI-rep of $\bm{\mathcal{I}}_{12}$ is $\{t_1, \bm{p}_{t_2, sp}, (\bm{p}_{t_2, b}^0, \bm{p}_{t_2, b}^1),\{(P_i, \Psi_i), (P_j, \Psi_j)\}\}$.}
+The PBI-rep of $\bm{\mathcal{I}}_{12}$ is $\{t_1, \bm{p}_{t_2, sp}, (\bm{p}_{t_2, b}^0, \bm{p}_{t_2, b}^1),\{(P_i, \mathcal{N}_i), (P_j, \mathcal{N}_j)\}\}$.}
 \label{fig:pbi}
@@
 For example, in Fig.
-\ref{fig:pbi}, two triangle faces $t_1$ and $t_2$ from mesh $P_i$ and $P_j$ respectively intersect on a line segment.
-Then it generates two intersections for each of the two triangles, denoted as ${\bm{\mathcal{I}}}_{12}$ and ${\bm{\mathcal{I}}}_{21}$.
+\ref{fig:pbi}, two triangle faces $t_1$ and $t_2$ from mesh $P_i$ and $P_j$ intersect.
+Then it generates two intersections for each of the two triangles--- ${\bm{\mathcal{I}}}_{12}$ on $t_1$ and ${\bm{\mathcal{I}}}_{21}$ on $t_2$.
 For ${\bm{\mathcal{I}}}_{12}$, the first two components are $t_1$ and $\bm{p}_{t_2, sp}$.
-The computation of the third component has already been discussed in \S\ref{sec:embed}.
-The neighborhood $\bm{\Psi} = \{(P_i, \Psi_i), (P_j, \Psi_j)\}$.
-In most time, $\Psi_i=t_1$ and $\Psi_j=t_2$.
-However, sometimes, intersections may lie on the primitive edges instead of faces.
-In that case, $\Psi_i$ and $\Psi_j$ are edges (Fig.
-\ref{fig:twin}).
-We postpone this discussion until \S\ref{sec:degenerate}.
-The computation of ${\bm{\mathcal{I}}}_{21}$ is similar.
+The third component is boundary planes from $t_2$ which has already been discussed in \S\ref{sec:embed}.
+The last component is $(P_j, t_2)$, meaning the neighborhood of ${\bm{\mathcal{I}}}_{12}$ is the face $t_2$.
+Sometimes intersections may lie on the mesh edges instead of faces (Fig.
+\ref{fig:twin}), which is called 'edge intersection'.
+In that case, the second component of neighborhood is the corresponding edge.
+We postpone the discussion of edge intersection to \S\ref{sec:degenerate}.
 
@@
 
-% intersect on face edges does not create new line segments, it is part of the edges from other meshes, and will to be duplicated.
-
-% whose edge? need to be further explained and better defined. an edge intersection divide edge in a triangle and will be duplicated in the other
-
 When intersection line segment lies on an edge (Fig.
@@
 we call it \emph{edge intersection}.
-The speciality of edge intersection is the neighborhood representation $\Psi$.
-The space near edge intersection is divided by both face in the two side of the intersected edge, instead of just one triangle face (Fig.
-X).
-Therefore, supposing intersection is on the edge $\bm{e}_{k, i}$ of mesh $P_k$, we denote the neighborhood as $\Psi_k = \bm{e}_{k, i}$.
-Note that an intersection can be on edges from different meshes.
-Then there are more than one component of $\bm{\Psi}$ are edges (Fig.
-\ref{fig:twin}d).
+The space near edge intersection is divided by faces around the intersected edge, instead of just one face.
+If intersection is on the edge $\bm{e}_{k, i}$ from mesh $P_k$, the neighborhood of the intersection is then $(P_k, \bm{e}_{k, i})$, where we use $\bm{e}_{k, i}$ to represent all faces from $P_k$ adjacent to $\bm{e}_{k, i}$.
 
 Another thing needs to be noticed is that there will be repetitive detection of edge intersections.
-In Fig.
-\ref{fig:twin}a, the same intersection on $t_1$ will be detected twice with both $t_2$ and $t_2^{\star}$.
-We solve this duplication together with other interactions among intersections in \S\ref{sec:tessellation}.
+For example, in Fig.
+\ref{fig:twin}a, the same intersection on $t_1$ will be detected twice because $t_1$ intersect both $t_2$ and $t_2^{\star}$ in the same place.
+We solve this duplication together with other interactions among different intersections in \S\ref{sec:tessellation}.
 We call such $t_2$ and $t_2^{\star}$ as \emph{companion triangles} in an edge intersection, a concept which will be referred again in the discussion of coplanar cases.
@@
 \includegraphics[width=3.5in]{edgeisect}
-\caption{Six situations of edge interse ctions.
+\caption{Different conditions of edge intersection.
+Triangle faces $t_1$ and $t_1^*$ are companion faces.
+Triangle faces $t_2$ and $t_2^*$ are companion faces.
+a) $t_2$ and $t_2^*$ are in different sides of $t_1$.
+b) $t_2$ and $t_2^*$ are in the same side of $t_1$.
+c) $t_2^*$ is coplanar with $t_1$.
+d) Both $t_1$ and $t_2$ have companion faces: the intersection is edge intersection for both $t_1$ and $t_2$ (instead of only for $t_1$ is previous three conditions).
+}
+%\caption{Six situations of edge interse ctions.
 The first three subgraphs are edge-face intersections.
@@
 \includegraphics[width=3.5in]{coplanar}
-\caption{a) Coplanar cases and the b) the possible configurations of the companion faces. In any configurations, their is no need to record the intersection of coplanar cases.}
+\caption{a) Coplanar cases, $t_1$ and $t_2$ intersect in 2D, forming three intersections $\mathcal{I}_a$, $\mathcal{I}_b$ and $\mathcal{I}_c$ on $t_1$.
+b) The possible configurations of the companion faces.
+For $\mathcal{I}_a$, the companion triangle $t_a^*$ is coplanar with $t_1$.
+Therefore, the red and the green areas do not need to be split during tessellation, and $\mathcal{I}_a$ is invalid.
+For $\mathcal{I}_b$ and $\mathcal{I}_c$, the companion faces are not coplanar, so these intersection can be recorded during intersection test between $t_1$ and the companion faces $t_b^*$ and $t_c^*$.
+In any configurations, their is no need to record the intersection.}
 \label{fig:coplanar}
@@
 Both $t_1$ and $t_2$ will divide each other into two areas---a convex overlapping area and exclusive parts (Fig.
-\ref{fig:coplanar}).
-Apparantly, if we tessellate both $t_1$ and $t_2$ according to the boundary of overlapping area, we can guarantee that the tessellated meshes will not cross the boundary of any other meshes.
-In fact, many methods \cite{feito2013fast,zhou2016mesh} claim that tessellating faces according to this 2D-intersection result is necessary.
-However, in our method, we do not test whether $t_1$ and $t_2$ really intersect in 2D.
-We treat them as they do not intersect at all.
+\ref{fig:coplanar}a).
+Apparantly, if we tessellate both $t_1$ and $t_2$ according to the boundary of overlapping area, we can guarantee that the tessellated meshes will not cross the meshes where $t_1$ and $t_2$ are from.
+Many methods \cite{feito2013fast,zhou2016mesh} claim that tessellating faces according to 2D-intersections is necessary.
+However, in our method, we do not test whether $t_1$ and $t_2$ really intersect in 2D once we find they are coplanar.
+We treat coplanar situations as they do not intersect at all.
 In this way, we simplify our method, making it more robust and fast, while doing no harm to the topology correctness.
-
-The key observation is that intersections in 2D are either duplicated added or invalid.
-The word `valid` means the intersections will appear as an edge in the final mesh.
-Namely, faces of intersection neighborhood have different classification results:
-\begin{equation}
-\lambda_f(\bm{s^i}) = f(\bm{\Lambda}(\bm{s}_i)) = constant, \bm{s}^i \in \mathcal{N}(\mathcal{I})
-\end{equation}
-, where $f$ is the CSG function, and $\bm{s}^i \in \mathcal{N}(\mathcal{I})$ is the neighboring faces of intersection $\mathcal{I}$.
-In principle, the validation of intersection is not known until classification stage.
-However, we can perform an early rejection to eliminate intersections that are invalid in certain.
 
@@
 The only difference is that there can be up to three edge intersections in one 2D intersection (Fig.
-\ref{fig:coplanar}).
+\ref{fig:coplanar}b).
 As we have discussed, edge intersection will be detected twice.
 That means we can rely on the companion triangle faces to detect intersections.
+
 However, if the companion triangles are also coplanar, neither of the two triangles will record the intersection.
 Fortunately, in this case, the intersection is not valid.
-The two sides of the intersection have the same indicators and are both retained or both dropped and we do not need it for tessellation.
+The word `valid` means the intersections will appear as an edge in the final mesh, thus is necessary to put into tessellation.
+Supposing the intersection is on triangle $t_1$, this definition equals to:
+\begin{equation}
+% = f(\bm{\Lambda}(\bm{s}_i))
+\lambda_f(\bm{x}_i) \neq constant, \bm{x}_i \in \bm{U}(\mathcal{I}) \cup t_1
+\end{equation}
+, where $f$ is the CSG function, and $\bm{x}_i \in \bm{U}(\mathcal{I})$ is the points from the neighborhood of  intersection $\mathcal{I}$.
+This inequation indicates the two sides of $\mathcal{I}$ have different classification and must be split according to $\mathcal{I}$ during tessellation.
+However, in most time, the validation of intersection is not known until classification stage, because we have to know the indicators of points in $\bm{U}(\mathcal{I}) \cup t_1$.
+Fortunately, if companion faces are both coplanar with $t_1$, both sides of $\mathcal{I}$ have the same indicators and thus the same classification.
+It means $\mathcal{I}$ is invalid and we do not need to record it either.
 
@@
 The intersections may intersect each other, introducing new vertices and splitting original intersection line segments (Fig.
-\ref{fig:iisect}).
+\ref{fig:iisect}a).
 This breaks the assumption of most CDT algorithms and may lead to incorrect output topology.
@@
 \centering
-\includegraphics[width=2in]{iisect}
-\caption{suppose? actual?plane-triples}
+\includegraphics[width=3.5in]{iisect}
+\caption{a) Different colors indicate the intersections are from different meshes.
+The blue intersections and the red ones intersect at a point.
+Also, the yellow intersections overlap with the red ones.
+b) After refinement, we introduce a new vertex $a$, and merge overlapping intersections into a new one $\mathcal{I}_b$.
+c) Our tessellation does not guarantee to obtain triangles.
+d) If triangulation is performed, new edges (gray ones) are introduced and we cannot give the precise plane-based representation for these new edges.}
 \label{fig:iisect}
@@
 This is because if triangles are required, we need construct new bounding planes for these new triangles, which violating our principle of no geometry construction (Fig.
-x).
+\ref{fig:iisect}d).
 
@@
 
-Intersection refinement is performed in a local scope.
-For each intersecting face $t$ from mesh $P_t$, we collect all intersections on $t$ into a set $\bm{\Gamma}(t)=\{\bm{\mathcal{I}}_{t}^i, i=0,1,2,...\}\cup\{\bm{\mathcal{I}}_{t}^{\bm{e}_i},i=0,1,2\}$ and refine them together.
-The set $\{\bm{\mathcal{I}}_{t}^{\bm{e}_i},i=0,1,2\}$ is the PBI-reps of the three edges of $t$.
-We treat edges as special intersections for simplicity, since edges also participate in tessellation.
-The neighborhood components of the edge $\bm{\Psi}(\bm{\mathcal{I}}_{t}^{\bm{e}_i})$ is set as $\{(P_t, \bm{e}_i )\}$.
-Other components of $\bm{\mathcal{I}}_{t}^{\bm{e}_i}$ can be determined by the P-reps of $\bm{e}_i$.
-The refinement on $\bm{\Gamma}(t)$ is done using only plane-based geometry predicates by the following three steps (Fig.
-x):
-
-\vspace{0.5em}
-\noindent \textbf{Collinear splitting}~~~~
-Each intersection $\bm{\mathcal{I}}_{t}^x$ are testing whether they are collinearly overlapping with other intersections.
-If yes, $\bm{\mathcal{I}}_{t}^x$ is split by the end points of overlapping intersections (Fig.
-x).
-Because $\bm{\mathcal{I}}_{t}^x$ may collinearly overlap more than one other intersection, the splitting may be deferred until all splitting points are found.
-The subroutine linear order of points (\S\ref{sec:substrates}) is used to sort these splitting points along $\bm{\mathcal{I}}_{t}^x$.
-The PBI-reps of split segments inherit their father's except the third component which identifies the end points.
+Intersection refinement is performed in a local scope. For each intersecting face $t$ from mesh $P_t$, we collect all intersections on $t$ as set $\bm{\Gamma}(t)$
+%$\bm{\Gamma}(t)=\{\bm{\mathcal{I}}_{t}^i, i=0,1,2,...\}\cup\{\bm{\mathcal{I}}_{t}^{\bm{e}_i},i=0,1,2\}$
+and refine them together.
+For simpler processing, we also include the three edges of $t$ into $\bm{\Gamma}(t)$, since edges also participate in tessellation.
+In $\bm{\Gamma}(t)$, edges are represented as PBI.
+The neighborhood components of edges are set as $None$ because they do not have a neighborhood edge or face.
+Other PBI-rep components can be determined by the P-reps of edges.
+The refinement on $\bm{\Gamma}(t)$ is done using only plane-based geometry predicates by the following three steps:
 
@@
 Intersections are undirected so intersections with inverse end points are also coincident.
-The PBI-rep of the new intersection is inherited from either of the old one's except the neighborhood component $\bm{\Psi}$.
-The value element of the new neighborhood is the union of the two old ones'.
-\iffalse
- We follow the merging rules below:
-\begin{equation}
-  \Psi_k(\bm{\mathcal{I}}_{t}^{12})=\left\{
-   \begin{array}{l}
-   \Psi_k(\bm{\mathcal{I}}_{t}^1)\mbox{ or }\Psi_k(\bm{\mathcal{I}}_{t}^2),\ \mbox{ if } \Psi_k(\bm{\mathcal{I}}_{t}^1)=\Psi_k(\bm{\mathcal{I}}_{t}^2) \\
-   \Psi_k(\bm{\mathcal{I}}_{t}^1),\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \mbox{ if } \Psi_k(\bm{\mathcal{I}}_{t}^2)=0  \\
-   \Psi_k(\bm{\mathcal{I}}_{t}^2),\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \mbox{ if } \Psi_k(\bm{\mathcal{I}}_{t}^1)=0  \\
-   \end{array}
-  \right.
-\end{equation}
-
-, where $\bm{\mathcal{I}}_{t}^1$ and $\bm{\mathcal{I}}_{t}^2$ are old intersections and $\bm{\mathcal{I}}_{t}^{12}$ is the new one.
-\fi
-
-\vspace{0.5em}
-\noindent \textbf{Crossing intersection resolving}~~~~
+The PBI-rep of the new intersection is inherited from either of the old one's except the neighborhood component.
+The new neighborhood is the combination of the merged ones', meaning the intersection has two (or more) neighborhoods.
+
+\begin{wrapfigure}{r}[0in]{0in}
+\includegraphics[width=2 in]{resolve}
+%\caption{Plane-based representation of triangle}
+\end{wrapfigure}
+\vspace{0.5em}
+\noindent \textbf{Cross and overlap resolving}~~~~
 After the process of two previous steps, there are no overlapping intersections in $\bm{\Gamma}(t)$.
-We check whether any pair of intersections intersect each other.
-The definition of \emph{intersect} does not include the situation that two intersections share end points.
-In Fig.
-x, we illustrate the two valid situations.
-In both situations, one intersection is split by the other, and the same splitting routine is used as in collinear splitting.
+We check whether any pair of intersections cross or overlap (collinear) each other.
+The definition of \emph{cross} does not include the situation that two intersections share end points, since no splitting is required in this situation.
+When there is crossing or overlapping, at least one of the intersections have to be split.
+Because one intersection may may 'touch' more than one other intersections, the splitting is deferred until all splitting points are found.
+The subroutine linear order of points (\S\ref{sec:substrates}) is used to sort these splitting points along the splitting intersection.
+The PBI-reps of split segments inherit their father's except the third component which identifies the end points.
+
+\vspace{0.5em}
+\noindent \textbf{Coincidence elimination (again)}~~~~
+Unfortunately, the overlap resolving may bring new coincident intersections. Therefore the first step is run again in the final step.
 
@@
 \label{sec:tess}
+
 So far, intersections are only independent data that store the coordinates and neighbouring information.
@@
 This is done by extract valid loops on tess-graph.
-A valid loop that corresponds to a subface must satisfy two criterions: 1) the direction of loops should be coherent with the face normal, and 2) consecutive connections on the loop should be adjacent by circular order ({\color{red}{Fig.?}}).
+A valid loop that corresponds to a subface must satisfy two criterions: 1) the direction of loops should be coherent with the face normal, and 2) consecutive connections on the loop should be adjacent by circular order.
 Each valid loop corresponds to a intersection-free face.
 After we find out all valid loops on tess-graph, we finish tessellating the corresponding face.
+To facilitate the later process, we also store neighborhood information into the edges of the new faces.
+Because the edges of new faces are generated from intersections, the neighborhood information of the edges is inherent from the corresponding intersections.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=3in]{circularadj}
+\caption{\emph{Left}: we find all valid loops on tess-graph to tesselate a triangle.
+The direction of loops have to be coherent with the triangle normal (assume the normal points to the outside of paper).
+\emph{Right}: each circular adjacent edge pair is an angle of the tessellated polygon.}
+\label{fig:cadj}
+\end{figure}
 
@@
 We further attach the PBI-reps of intersections to the edges generated from tess-graph connections which corresponds to an intersection.
-Finally, we get the intersection-free hybrid meshes, while `hybrid` means some parts of meshes are both vertex-based and plane-based represented.
+Finally, we get the intersection-free hybrid meshes, with some edges contains neighborhood information which indicates there are intersections between meshes.
 
@@
 Given adjacent faces $\bm{s}_1$ and $\bm{s}_2$, it is straightforward to know whether $\bm{\Lambda}(\bm{s}_1)$ and $\bm{\Lambda}(\bm{s}_2)$ are different.
-The two indicator vectors are the same unless the shared edge $\bm{e}_{12}$ lies on the boundary of some meshes, and it means there is an intersection (denoted as $\bm{\mathcal{I}}(\bm{e}_{12})$) stored on $\bm{e}_{12}$.
-The neighborhood of $\bm{\mathcal{I}}(\bm{e}_{12})$ indicates which components of indicator vector differ between $\bm{s}_1$ and $\bm{s}_2$.
+The two indicator vectors are the same unless the shared edge $\bm{e}_{12}$ lies on the boundary of some other meshes, which means there is neighborhood information, say, $\bm{\mathcal{N}(\bm{e}_{12})} = \{(P_k, \mathcal{N}_k)\}$, stored on $\bm{e}_{12}$.
+The neighborhood information indicates which components of indicator vector differ between $\bm{s}_1$ and $\bm{s}_2$.
  \iffalse
@@
 \label{eq:eq1}
-{\lambda_k}(\bm{s}_1) = {\lambda_k}(\bm{s}_2),\ \ \  \mbox{if }\Psi_k(\bm{\mathcal{I}}(e_{12}))= 0.
+{\lambda_k}(\bm{s}_1) = {\lambda_k}(\bm{s}_2),\ \ \  \mbox{if }\mathcal{N}_k(\bm{\mathcal{I}}(e_{12}))= 0.
 \end{equation}
 \fi
-If there is a neighborhood $(P_k, \Psi_k) \in \bm{\Psi}(\bm{\mathcal{I}}(\bm{e}_{12}))$, both $\lambda_k(\bm{s}_1)$ and $\lambda_k(\bm{s}_2)$ can be computed efficiently and exactly according to $\Psi_k$ (\S\ref{sec:propagation}).
+If there is a neighborhood $(P_k, \mathcal{N}_k) \in \bm{\mathcal{N}}(\bm{\bm{e}_{12}})$, the $k^{th}$ indicators $\lambda_k(\bm{s}_1)$ and $\lambda_k(\bm{s}_2)$ can be computed efficiently and exactly according to $\mathcal{N}_k$ (\S\ref{sec:propagation}).
 We outline our classification method in Algorithm \ref{code:floodfill}.
@@
 \label{sec:propagation}
+
 Meshes consist of vertices, edges and faces.
@@
 
+\begin{wrapfigure}{r}[0in]{0in}
+\includegraphics[width=1.3 in]{propagate}
+\end{wrapfigure}
+
 %For example, given a face $\bm{s}$ and one of its vertex $v^i(\bm{s})$, if $\lambda_k(v^i(\bm{s}))=on$, $\lambda_k(\bm{s})$ can be any of $on$, $in$ or $out$ (see {\color{red}{Fig. ?}})
@@
 \begin{equation}
-\bm{v}_0\to \bm{e}_0\to \bm{s}_0\to \bm{e}_1\to \bm{s}_1\to \bm{e}_2\to \bm{s}_2\to ...
+\bm{v}_0\to \bm{e}_0\to \bm{s}_0\to (\bm{e}_1)\to \bm{s}_1\to (\bm{e}_2)\to \bm{s}_2\to ...
 \end{equation}
 , where $\bm{v}, \bm{e}$ means vertex and edge respectively.
+The bracket here means propagating to edge is optional because if the edge does not contain neighborhood information, the indicators on the two side are the same and we do not need to propagate to the edge.
 We find that there are three kinds of basic operations in the trace: $\bm{v}_{\bm{e}}\to \bm{e}$, $\bm{e}_{\bm{s}}\to \bm{s}$ and $\bm{s}\to \bm{e}_{\bm{s}}$, where $\bm{v}_{\bm{e}}$ means the end point of $\bm{e}$, and $\bm{e}_{\bm{s}}$ means the edge of $\bm{s}$.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=3in]{bsps}
+\caption{a) Because we cannot use inner sample point includes geometry construction, we choose the vertices (green one) instead to compute the face indicator.
+b-d): Different situations of classification.
+The simple structure of neighborhood BSP guarantees the same classification result of the points on $\bm{p}_{\bm{s}, sp}^+$.
+In \emph{a}, the BSP contains two half-planes because it is constructed from two neighborhood faces.
+In \emph{d}, the classification result is $on$ so we need to determine the orientation by the normal of half-plane $q$ and the face $p$.
+In this condition, the indicator should be $oppo$ since $p$ and $q$ are opposite.}
+\label{fig:bsps}
+\end{figure}
 
@@
 \vspace{0.5em}
-\noindent\textbf{$\bm{s\to \bm{e}_{\bm{s}}}$}~~~~ When $\lambda_k(\bm{e}_{\bm{s}})=on$, there will be intersection $\bm{\mathcal{I}}(\bm{e}_{\bm{s}})$ attached to $\bm{e}_{\bm{s}}$ and the related neighborhood $\Psi_k$ in $\bm{\mathcal{I}}(\bm{e}_{\bm{s}})$.
-Therefore, in this operation, all we need is to iterate over all components of $\bm{\Psi}(\bm{\mathcal{I}}(\bm{e}_{\bm{s}}))$ and change corresponding indicators to $on$.
+\noindent\textbf{$\bm{s\to \bm{e}_{\bm{s}}}$}~~~~ We need to find which indicators change to $on$.
+We known when $\lambda_k(\bm{e}_{\bm{s}})=on$, there will be neighborhood information related to mesh $P_k$ stored on $\bm{e}_{\bm{s}}$.
+Therefore, in this operation, all we need is to iterate over neighborhoods of $\bm{e}_{\bm{s}}$ and change corresponding indicators to $on$.
 
@@
 \ref{eq:porder}, we know if $\lambda_k(\bm{e}_{\bm{s}}) \neq on$, then $\lambda_k(\bm{e}_{\bm{s}})=\lambda_k(\bm{s})$.
-When $\lambda_k(\bm{e}_{\bm{s}}) = on$, we figure out $\lambda_k(\bm{s})$ using $\Psi_k$ from $\bm{\Psi}(\bm{\mathcal{I}}(\bm{e}_{\bm{s}}))$.
-We know $\Psi_k$ and can be either a triangle face or an edge from mesh $P_k$.
-If $\Psi_k$ is a face, we can build a trivial BSP \cite{thibault1987set} using the face on the space near $\bm{e}_{\bm{s}}$.
-If $\Psi_k$ is an edge, we can still build BSP using the faces adjacent to $\bm{e}_{\bm{s}}$.
+On the other hand, when $\lambda_k(\bm{e}_{\bm{s}}) = on$, we figure out $\lambda_k(\bm{s})$ using neighborhood information related to $P_k$.
+We know the corresponding neighborhood $\mathcal{N}_k$ and can be either a triangle face or an edge from mesh $P_k$.
+If $\mathcal{N}_k$ is a face, we can build a trivial BSP \cite{thibault1987set} using the face on the space near $\bm{e}_{\bm{s}}$.
+If $\mathcal{N}_k$ is an edge, we can still build BSP using the faces adjacent to $\bm{e}_{\bm{s}}$.
 In both cases, the BSP can be used to compute $\lambda_k(\bm{s})$ if we can sample a point from $\bm{s}$ that near $\bm{e}_{\bm{s}}$.
 Unfortunately, we cannot guarantee to find such a point with precise coordinates.
-Instead, we choose a point $\bm{v}_x$ from the half plane $\bm{p}_{\bm{s}, sp}^+$, which is on the supporting plane of $\bm{s}$ and on the positive side of bounding plane $\bm{p}_{\bm{s}, b}^{\bm{e}_{\bm{s}}}$ (Fig.
-x).
-For polygons, there is at least one such $\bm{v}_x$ among the vertices of $\bm{s}$.
-We find that the BSP is so simple that indicators $\lambda_k$ of all points on $\bm{p}_{\bm{s}, sp}^+$ are the same.
-Since $\bm{p}_{\bm{s}, sp}^+ \cap \bm{s} \neq \varnothing$, we can compute $\lambda_k(\bm{s})$ by figuring out $\lambda_k(\bm{v}_x)$.
+
+We find that the BSP constructed from edge neighborhood is so simple that indicators $\lambda_k$ of all points on the half plane $\bm{p}_{\bm{s}, sp}^+$ are the same.
+Here $\bm{p}_{\bm{s}, sp}^+$ is half of the supporting plane of $\bm{s}$ that on the positive side of bounding plane $\bm{p}_{\bm{s}, b}^{\bm{e}_{\bm{s}}}$ (Fig.
+\ref{fig:bsps}).
+Since $\bm{p}_{\bm{s}, sp}^+ \cap \bm{s} \neq \varnothing$, we can compute $\lambda_k(\bm{s})$ by figuring out $\lambda_k(\bm{v}_x)$, where $\bm{v}_x \in \bm{p}_{\bm{s}, sp}^+$.
+For polygons, there is at least one vertex on $\bm{p}_{\bm{s}, sp}^+$, whose exact coordinates are known.
+Therefore that vertex is used as the $v_x$.
 Also, if we assign each BSP splitting plane a normal by the normal of triangle it contains, we can use it to decide the orientation ($same$ or $oppo$) when $\bm{v}_x$ is on a splitting plane, which means $\lambda_k(\bm{s})=on$.
@@
 \vspace{0.5em}
+\begin{wrapfigure}{r}[0in]{0in}
+\includegraphics[width=1.3 in]{vneighbor}
+\end{wrapfigure}
 \noindent\textbf{$\bm{\bm{v}_{\bm{e}}\to e}$}~~~~ While this is yet another propagation from low dimension to high dimension, there is no neighborhood information stored on vertex.
@@
 
-\section{Essential Subroutines}
+\section{Discussion}
 \label{sec:esubroutine}
 
+\begin{figure*}[!t]
+\centering
+\includegraphics[width=7in]{null}
+\caption{different models...........}
+\label{fig:models}
+\end{figure*}
+
 \vspace{0.5em}
 \noindent\textbf{Searching valid loops}~~~~ In \S\ref{sec:tess}, we claim a valid loops on tess-graph has to be correct with its orientation.
-However, since tess-graph is undirectional, it is not easy to check whether a loop orientation agrees with the face's.
-We observe that the graph connections lie on face edges have their unambiguous directions (Fig.
-x).
+However, since tess-graph is undirectional, it is not easy to check whether a loop orientation agrees with the face's (Fig.
+\ref{fig:dual}a).
+We observe that the graph connections lie on face edges have their unambiguous directions.
 Starting from these edges, we can guarantee that the loops have the right orientations.
@@
 
-\vspace{0.5em}\noindent There is another problem that the tess-graph may not be a connected graph.
+\begin{figure}[h]
+\centering
+\includegraphics[width=3in]{dual}
+\caption{a) We cannot easily figure out the correct orientation of the loop.
+b) When there are more than one connected component, we use auxiliary intersection (red line) to connect the two component.
+}
+\label{fig:dual}
+\end{figure}
+
+\vspace{0.5em} There is another problem that the tess-graph may not be a connected graph.
 We avoid this problem by inserting auxiliary intersections into the tess-graph to make it connected.
-An auxiliary intersection links the vertex of face on the outer connected component with the vertex on the inner connected component.
+An auxiliary intersection links the vertex of face (denoted as $\bm{v}_i$) on the outer connected component with the vertex on the inner connected component.
 The intersection refinement has to be performed again if the auxiliary intersections cross any other intersections.
-To guarantee the auxiliary intersection has a valid PBI-rep, we require the vertex from inner connected component generated by edge-face intersection, which means it is introduced during triangle-triangle intersection test.
-In this way, we can find an exact plane with the auxiliary intersection on it (Fig.
-x).
+To guarantee the auxiliary intersection has a valid PBI-rep, we require the vertex from inner connected component generated by intersection between the face and an edge (denoted as $\bm{e}_j$) from other meshes---all newly introduced vertices during triangle-triangle intersection are this type.
+In this way, we get three vertices with exact coordinates ($\bm{v}_i$ and the two end points of $\bm{e}_j$) and can construct an exact plane where the auxiliary intersection lies.
 
@@
 The $on$ indicators are easy to determine in most time.
-Though sometimes exception occur because of multi-coplanar situation, this will not happen if we carefully choose the right vertex whose neighbor faces are not coplanar (Fig.
-x).
-
-\vspace{0.5em}\noindent The indicator vectors can propagate not only among single meshes, but can also between different meshes by the vertices and edges they share.
+Though sometimes exception occur because of multi-coplanar situation, this will not happen if we carefully choose the right vertex whose neighbor faces are not coplanar.
+
+\vspace{0.5em} The indicator vectors can propagate not only among single meshes, but can also between different meshes by the vertices and edges they share.
 Therefore in most time, we only need one single seed vertex for classification.
-However, if there are lonely meshes that do not intersect with other meshes, we need to new seeds.
-The indicators of the second and later seeds can only be computed by point-in-polyhedron tests.
+However, if there are more than two connected components among meshes, we need to new seeds to propagate each component.
+The indicators of the second and later seeds can be computed by point-in-polyhedron tests.
 
@@
 \hline
-{No.} & {Figure} & {Triangle Num. 1} & {Triangle Num. 2} &
+{No.} & {Model} & {Triangle Num. 1} & {Triangle Num. 2} &
 CGAL & Maya & Cork & Carve & QuickCSG & Our Method
@@
 \hline\hline
-1 & budda \& lion & 1.08M & 0.4M & - & - & - & - & 3.44 & 6.88\\
-2 & dragon \& bunny & 277k & 70k & - & - & - & - & - & -\\
-3 & armadillo \& armadillo* & 150k & 150k & - & - & - & - & - & -\\
-4 & horse \& corpse & 150k & 150k & - & - & - & - & - & -\\
-5 & dinasour \& ironman & 150k & 150k & - & - & - & - & - & -\\
+1 & Budda $\cup$ Lion & 1.08M & 0.4M & - & - & - & - & 3.44 & 6.88\\
+2 & Dragon $\cup$ Bunny & 100k & 70k & - & - & - & - & 0.334 & 0.636 \\
+3 & Armadillo $\cup$ Armadillo2 & 150k & 150k & - & - & - & - & 0.746 & 1.62\\
+4 & Horse $\cup$ Corpse & - & - & - & - & - & - & - & -\\
+5 & Dinasour $\cup$ Ironman & - & - & - & - & - & - & - & -\\
 \hline
@@
 \caption{Computation Time Statistics of Large CSG Evaluation (Seconds)}
-\label{tab:performance}
+\label{tab:performance2}
 \centering
@@
 \hline
-{No.} & {Figure} & {Triangle Num.} & {Primitive Num.} &
+{No.} & {Model} & {Triangle Num.} & {Primitive Num.} &
 CGAL* & Maya* & Cork & Carve & QuickCSG & Our Method
@@
 \hline\hline
-1 & Sprocket & 1.08M & 0.4M & - & - & - & - & 3.44 & 6.88\\
-2 & ring and ball & 277k & 70k & - & - & - & - & - & -\\
-3 & t1 & 150k & 150k & - & - & - & - & - & -\\
-4 & t2 & 150k & 150k & - & - & - & - & - & -\\
-5 & h & 150k & 150k & - & - & - & - & - & -\\
-6 & Organic & 150k & 150k & - & - & - & - & - & -\\
-7 & 6 Budda & 150k & 150k & - & - & - & - & - & -\\
-8 & Serpent & 150k & 150k & - & - & - & - & - & -\\
-9 & Dithering & 150k & 150k & - & - & - & - & - & -\\
+1 & Sprocket & - & 52 & - & - & - & - & 0.059 & -\\
+2 & ring and ball & - & 201 & - & - & - & - & - & -\\
+3 & T1 & - & 50 & - & - & - & - & 0.433 & 10.1\\
+4 & T2 & - & 50 & - & - & - & - & 0.804 & -\\
+5 & H & - & 42 & - & - & - & - & 2.22 & -\\
+6 & Organic & - & 6 & - & - & - & - & 0.590 & -\\
+7 & 6 Budda & - & 6 & - & - & - & - & - & -\\
+8 & Serpent & - & - & - & - & - & - & - & -\\
+9 & Dithering & - & - & - & - & - & - & - & -\\
 \hline
@@
 \begin{flushleft}
-$^{\nabla}$~~\emph{Min} (\emph{Max}) means the minimum (maximum) number of faces of a single primitive.
-
-$^{\circ}$~~The total computation time of our method includes the construction of half-edge structure and the three steps in Section \ref{sec:overview}.
-
+\end{flushleft}
+\end{table*}
+
+\begin{table*}[ht]
+\caption{Face Number of the Results of Self-Union Evaluation}
+\label{tab:selfunion}
+\centering
+\begin{tabular}{*{9}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
+\hline
+{No.} & {Model} & {Orig. Num.} &
+CGAL & Maya & Cork & Carve & QuickCSG & QuickCSG2* & Our Method
+\\
+\hline\hline
+1 & Ball & 360  & - & 360 & - & - & 1 & 360 & 360 \\
+2 & head & 2,716& - & 2,716 & - & - & 5 & 2,716 & 2,716\\
+3 & Bunny & 69,666  & - & 69,664 & - & -& 0 & 69,668 & 69,669\\
+4 & Dragon & 276,972 & - & 0 & - & -& 1 & 276,702 & 277,987 \\
+\hline
+\end{tabular}
+\begin{flushleft}
+~~~~~~~~~~~~~~~~~~~~~$^{*}$~~We perturb the model by 1e-6 to give QuickCSG the ability to partly solve coplanar cases.
 \end{flushleft}
@@
 \vspace{0.5em}
-\noindent\textbf{Coplanar and self-union}~~~~
+\noindent\textbf{Self-union}~~~~
 Our method is unconditionally robust for regular set meshes.
@@
 To prove that, we tested the self-union of several models and some CSG with coplanar faces.
-We find that our method always produces visually correct results.
-QuickCSG and Cork failed to produce the result in most of these cases, because they cannot deal with coplanar faces.
-Even after perturbation, their results are still full with deficiencies (holes, boundary edges, etc.).
-For the bunny model, we found our result face count was slightly deviated from the original mesh.
-This is because the original mesh contains self-intersection in the bunny chest (the green faces), which causes errors during classification.
+Table \ref{tab:selfunion} compares the difference between input meshes and result meshes by their face number.
+We find that our method always produces correct or at least near correct results.
+The slightly deviation of our result from the original one is caused by self-intersection in the original models.
+QuickCSG failed to produce the result in all coplanar cases, because they cannot deal with coplanar faces.
+After perturbation, results of QuickCSG are visually OK.
+However, the topology of their results is messy.
+We can see hundreds of boundary edges on their results which do not exist in the original model (Fig.
+\ref{fig:boundaryedge}).
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=3in]{null}
+\caption{boundary edges on the models........}
+\label{fig:boundaryedge}
+\end{figure}
 
@@
 Other robust methods such as Maya and CGAL are much slower because both of them use the arbitrary precision arithmetic.
-It should be noted that in some cases (), most time is spent on octree construction in our method.
+It should be noted that in (some) very large CSGs, most time is spent on octree construction in our method.
 It means other stages which involve plane-based geometry take only a small percentage of time, proving the efficiency of our plane-based geometry.

### 2016-12-07 summary.tex
before 1st change
20161207

@@
 \begin{document}
-\title{Efficient, Robust and Exact Boolean Operations on N Triangular Mesh Primitives}
+\title{Efficient and Robust Plane-Based Boolean Operations on N Meshes}
 \author{%Rui~Wang,~
@@
 However, boolean operations, which compute the boundary representation of CSG, have been suffered from robustness and efficiency problem for more than three decades.
-In this paper, we propose a fast and exact boolean operation approach which is theoretically robust for regular meshes.
-This is done by introducing plane-based geometry into boolean operations and strictly follow the principle of no geometry constructions during processing.
-Different from previous BSP-based methods, our method is with only one-time conversion to the plane representation in intersection areas, instead of a series of complex conversions between different representations.
-Also, by using geometry connectivity and space neighboring information, our method reuse the computation iteratively, saving much computation time.
+In this paper, we propose a fast and exact boolean operation method which is unconditionally robust for regular set solids.
+We notice that among previous works, plane-based boolean methods are easy to achieve robustness, but hard to be efficient.
+On the other hand, methods based on B-reps of meshes are fast but not robust unless exact arithmetic is applied.
+We choose to combine plane-based representations (P-reps) with B-reps, which allows us to take the advantages of both.
+Our method is globally based on B-reps for its efficiency, and P-rep geometry is applied locally to ensure robustness.
 Comparison experiments with state-of-the-art techniques show that our method is unconditionally exact and robust, while is competitively efficient with non-robust methods and much faster than the robust ones.
@@
 \begin{IEEEkeywords}
-boolean operations, triangle mesh, CSG evaluation, plane-based geometry
+boolean operations, CSG evaluation, plane-based geometry
 \end{IEEEkeywords}
@@
 In general, there are two major types of boolean algorithms according to how they deal with intersection between primitive meshes.
-Approximate methods redicretize the intersection areas, fit vertices approximatively and rearrange topology.
+Approximate methods \cite{wang2011approximate,pavic2010hybrid,biermann2001approximate} redicretize the intersection areas, fit vertices approximatively and rearrange topology.
 On the other hand, exact method do not change vertex positions, retain as many input elements  (e.g., faces, vertices and topology) as possible.
@@
 Also, using exact methods, the clear mapping between the surface of input and output meshes makes it easier for the inheritance of information like face colors and materials.
+
 However, for exact boolean operation methods, there is always a bargain between robustness and efficiency.
-Recent exact boolean operation methods try to find faster ways to compute boundaries of CSG.
-However, for robustness, the answers are often exact arithmetic \cite{barki2015exact,zhou2016mesh} or trivial workarounds, like setting a tolerance \cite{feito2013fast,segal1990using} or rotating the primitive with small angles to avoid coplanar cases \cite{douze2015quickcsg}.
-However, none of the solution is good enough.
-While methods using exact arithmetic are significantly slower, workarounds are often case dependent and not reliable for complex CSGs.
-
-We develop an unconditionally robust and exact boolean operation method for triangle meshes without using exact arithmetic.
-The robustness of our method is based on the observations by Sugihara and Iri \cite{sugihara1990solid} that boolean operations can be performed without geometry constructions if representations are based on planes.
-This idea of using plane-based representation (P-rep) has been developed by Berstein and Fussell \cite{bernstein2009fast} by combining it with binary search partition (BSP) techniques \cite{naylor1990merging,thibault1987set}.
-Later, Campen et.
-al.
-\cite{campen2010exact} improved the method using octrees to resolve intersections locally, avoiding inefficient large BSP tree construction.
-Despite of that, Campen et.
-al.'s method still suffers from performance problem because of the complex conversions among B-reps, P-reps and BSP representations.
-Also, the incoherence between BSP representation, where boolean operations actually happens, and B-reps, which are input and output meshes, requires extra steps to connect the reconstructed intersection areas with the unchanged areas, leading to extra computation burden and complex topology.
-
-Our method is based on B-reps of meshes with geometry connectivity (e.g., halfedge \cite{mcguire2000half}).
-We embed P-rep of faces into the B-rep, forming a hybrid representation, which allows us to take the advantage of both representations for robustness and efficiency.
-This hybrid representation requires only one-time conversion from B-rep to P-rep in intersection areas of meshes.
-%that allows us to take advantage of geometry connectivity for classification acceleration \cite{feito2013fast,ogayar2015deferred,updegrove2016boolean}, which is hard for BSP-based methods.
+Many exact boolean operation methods focus on efficiency.
+But for robustness, the solutions are either exact arithmetic \cite{barki2015exact,zhou2016mesh} or trivial workarounds to avoid degenerations, such as setting a tolerance \cite{feito2013fast,segal1990using} and rotating the primitive with small angles \cite{douze2015quickcsg}.
+Methods using exact arithmetic are significantly slower, and workarounds are often case dependent and not reliable.
+Recently, some methods \cite{bernstein2009fast,campen2010exact} seek unconditional robustness by avoiding geometry constructions (such as computing new vertex coordinates) and using only predicates.
+Their key idea is to utilize plane-based representations (P-reps) of meshes instead of B-reps, which comes from the observation of Sugihara and Iri \cite{sugihara1990solid} that boolean operations can be performed without geometry constructions if P-reps are used.
+While these plane-based methods are generally faster than exact arithmetic ones, they still suffer from performance issue because of the complex conversions among different representations.
+Also, the incoherence between different representations requires extra steps to reconstruct geometry connectivity, leading to extra computation burden and more complex topology.
+
+Inspired by these previous work, we develop an unconditionally robust boolean operation method which is as robust as P-rep-based method and as fast as non-robust B-rep-based method.
+To achieve this, we embed P-rep information into faces of B-reps, forming hybrid representation of meshes.
+We avoid geometry constructions throughout our method, and convert all necessary computation into predicates under the hybrid representation.
+In general, the B-reps information is used for coarse tests and efficient face neighbor query, while P-reps information is for exact geometry computation.
 Moreover, our method can perform boolean operations with more than two primitives in one call, instead of recursively doing incremental boolean operations.
-Despite of extra complexity, non-incremental boolean operation may save much computation time by avoiding repetitive computation.
-The major difficulty of embedding P-rep into B-rep is the incoherence between the two representations.
-Many geometry operations (e.g., coordinates projection and compute the barycenter coordinate of triangle) available on B-rep can be very complex and thus inefficient on P-rep.
-On the contrary, all geometry predicates have to be performed under P-rep for exactness and robustness.
-We solve this problem by various methods to constrain the computation within plane-based geometry predicates.
-The experiments show that our method is much faster than existing robust exact methods, while only about two to three times slower than the state-of-art non-robust exact methods.
+In this way, our method could save computation time by avoiding repetitive computation.
+The experiments show that our method is much faster than existing robust exact methods, while only about two times slower than the state-of-art non-robust exact methods.
 
@@
 
-Since efficiency, accuracy and robustness are hard to be satisfied at the same time, starting from \cite{museth2002level}, some sacrifice accuracy for better efficiency and robustness.
+Since efficiency, accuracy and robustness are hard to be satisfied at the same time, some method choose to sacrifice accuracy for better efficiency and robustness.
 Most of such methods are based on conversion to volumetric representations.
@@
 
-The concept of plane-based representation of polygonal meshes was first described by Sugihara and Iri \cite{sugihara1990solid}.
-P-rep provides important advantage that for boolean operations, no new primary geometry information has to be constructed to obtain the result polyhedron---it is composed of a subset of the planes of the input polyhedra.
-Berstein and Fussell \cite{bernstein2009fast} combined the P-rep with binary space partitioning (BSP) \cite{thibault1987set,naylor1990merging} to develop an unconditionally robust boolean operation method.
-Compared to volume-grid based methods, their BSP-based method increases mesh complexity more moderately and the input topology can be reconstructed better.
-However, it requires conversions between input data structures and P-rep which are inefficient from both storage and time views.
-Also, the merge of two BSP trees is an $O(mn)$ time complexity process, where $m$ and $n$ are the size of the trees.
-It makes this method impractical for very large input meshes.
-Campen and Kobbelt \cite{campen2010exact} improved their method by localization using an octree.
+The concept of plane-based representations (P-reps) of polygonal meshes was first described by Sugihara and Iri \cite{sugihara1990solid}.
+P-reps provide essential benefit that for boolean operations, no new primary geometry information has to be constructed to obtain the resultss---it is composed of a subset of the planes of the input polyhedra.
+It means no constructions is required and the computation can include only predicates, which are much easier to be exact and robust.
+Inspired by this observation, Berstein and Fussell \cite{bernstein2009fast} combined the P-reps with binary space partitioning (BSP) \cite{thibault1987set,naylor1990merging} to develop an unconditionally robust boolean operation method.
+Compared to B-rep-based methods, their method does not require exact arithmetic, which makes it more efficient.
+However, the merge of two BSP trees is an $O(mn)$ time complexity process, where $m$ and $n$ are the size of the trees.
+It makes this method impractical for large meshes.
+Later, Campen and Kobbelt \cite{campen2010exact} improved their method by localization using an octree.
 And the refinement only takes place locally near intersections.
@@
 
-\subsection{Background}
+\subsection{Boolean Numerical Errors}
 \label{sec:paradigm}
@@
 Each input meshes are tessellated according to the intersection results, making every face be either inside, outside or on the boundary of other primitives.
-The tessellated meshes are what we called \emph{intersection-free meshes}.
+The tessellated meshes are w hat we called \emph{intersection-free meshes}.
 Unfortunately, under fix-precision float-point arithmetic, intersection tests are error-prone: first, degenerate cases of intersection are hard to detect; second, when there are intersections, new vertices are introduced into the geometry, whose coordinates cannot be exactly represented by fix-precision float-point numbers.
@@
 \includegraphics[width=2.5in]{falseclass}
-\caption{In a 2D view, face $\bm{s}$ from $P_2$ is on the surface of mesh $P_1$.
-However, because we use face barycenter $\bm{v}_c$ to compute the indicator, the coordinates of $\bm{v}_c$ contain round-off error and move to $\bm{v}'_c$, we might falsely classify $\bm{s}$ as outside of $P_2$.}
+\caption{In a 2D view, face $\bm{s}$ (the red line segment) from $P_2$ is on the surface of mesh $P_1$.
+However, because we use face barycenter $\bm{v}_c$ to compute the indicator, the coordinates of $\bm{v}_c$ contain round-off error and move to $\bm{v}'_c$, and we might falsely classify $\bm{s}$ as outside of $P_1$.}
 \label{fig:falseclass}
@@
 
-Face classification also suffers from robustness problems.
+Face classification also suffers from numerical errors.
 Many methods classify face according to the indicators of its barycenter, which can be computed by point-in-polyhedron test \cite{feito2013fast,campen2010exact}.
@@
 In addition, for the large amount of faces and input meshes, many methods take the benefits of the local coherence of indicators, classifying neighboring faces together \cite{pavic2010hybrid,feito2013fast,ogayar2015deferred,zhou2016mesh}.
-Despite of the performance improvement, it can make the robustness problem worse because the false classification may propagate to neighboring faces.
-
-We develop an exact boolean operation method based on the two-step paradigm, being unconditional robust and as fast as possible.
-\iffalse
-Our method includes the following features:
-\begin{itemize}
-    \item Intersection computation has to avoid errors when introducing new vertices into meshes.
-    \item All degenerate cases of intersection between input meshes have to be well resolved.
-    \item Face classification has to be exact and robust.
-    \item Acceleration using geometry connectivity is necessary for face classification.
-\end{itemize}
-\fi
-For efficiency, the robustness of method does not rely on arbitrary precision arithmetic.
-Instead, we apply the plane-based techniques from BSP-based method \cite{campen2010exact}.
-However, BSP structure does not support geometry connectivity query in nature, which is essential for classification acceleration.
-Also, we do not want complex conversions between different representations.
-Therefore, our method is based on B-rep and we embed P-rep into intersection areas to guarantee the robust geometry computations.
-
-\iffalse
-\subsection{Intersection-Free Hybrid Mesh}
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=2.5in]{linkedhalfedge}
-\caption{{\color{red}{Sketch: The Linked Halfedge structure}}}
-\label{fig:linkedhalfedge}
-\end{figure}
-
-\begin{figure*}[!t]
-\centering
-\includegraphics[width=7.1in]{flowchart}
-\caption{{\color{red}{Sketch: overview, will be replaced}}}
-\label{fig:overview}
-\end{figure*}
-
-\label{sec:meshes}
-We made an observation that the non-intersected meshes, as intermediate result of intersection computation, plays an important role of boolean operations.
-It is a bridge that controls the complexity of intersection computation and facilitates face classification.
-After the data structure of non-intersected meshes is determined, all things left are how to construct this structure and how to classify according to it.
-
-Our non-intersected mesh, called Linked Halfedge (Fig.
-\ref{fig:linkedhalfedge}), is a variance of halfedge, a wide-used data structure to represent solids.
-Halfedge has two advantages: first, since halfedge is popular, using it as the intermediate data structure can avoid unnecessary conversion, which has the potential to have better performance and result topology; second, the geometry connectivity, by which we accelerate classification using local coherence of space indicators, can be easily retrieved through halfedge.
-
-However, naive halfedge is far from enough.
-The vertex coordinates in halfedge are usually represented by float point number, which cannot exactly represent the newly introduced intersection points.
-Therefore, we utilize P-rep to avoid computing new coordinates.
-In addition, we detect all coincident vertices among input meshes (including intersection vertices).
-This information is used for avoiding repetitive vertices in the final mesh, reconstructing geometry connectivity, and ensuring the topology correctness.
-
-Enlightened by Feito et.
-al.
-\cite{feito2013fast}, we found that the the topology near intersection lines between faces can benefit point-in-polyhedron test by dramatically reducing the number of faces needing traversing.
-Therefore, we add what we call \emph{intersection context} into the our non-intersected meshes to facilitate afterwards face classification.
-Intersection context identifies where an intersection lies on the surface of the related primitives.
-An edge of Linked Halfedge stores intersection context only if it is coincident with a certain intersection line segment between primitives.
-We will give the definition and usage of intersection context in details in \S\ref{sec:ir}.
-
-To give an overall impression of Linked Halfedge, we summarize the above content and highlight the features of Linked Halfedge as follows:
-
-\begin{itemize}
-  \item Each input mesh is tessellated into a Linked Halfedge by intersection computation.
-  \item Coincident vertices between different Linked Halfedge should be linked, that is, coincident vertices are shared among Linked Halfedges.
-  \item If a certain edge of Linked Halfedge is coincident with intersection line segment(\bm{s}), it should be associated with the corresponding intersection context(\bm{s}).
-\end{itemize}
-
-\fi
-\subsection{Method Overview}
-
-There are generally four stages for our boolean method.
-The first three stages are to compute intersection, which can be seen as pre-processing, processing and post-processing.
-After that, the input meshes are tessellated into intersection-free meshes with hybrid representations.
-The last step is to classify each face and get the final result mesh of boolean operations.
-
-\subsubsection{Space division}
-
-\begin{wrapfigure}{r}[0in]{0in}
-\includegraphics[width=1.2in]{octreediff}
-\end{wrapfigure}
-
-As intersection detection is performed between each pair of faces, localization is necessary to filter invalid pairs beforehand.
-Many space division methods can be used in this step.
-We use the adaptive octree for its simplicity and efficiency.
-Our implementation is akin to the implementation in Ogayar et al.'s method \cite{ogayar2015deferred}.
-Intersection between triangle faces and octree leaves are efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}.
-Octree leaves are classified into two types: if all faces that intersect a leaf belong to the same primitive, we call it a \emph{normal cell}.
-Otherwise, it is a \emph{critical cell}, within which the following intersection computation is performed.
-
-The difference between our octree and Ogayar et al.'s is that we do not subdivide any normal cell no matter how many faces it contains.
-This is because subdividing normal cells benefits only the point-in-polyhedron test  \cite{frisken2002simple}, which seldom uses in our method.
-This simplification can save much computing time, especially when intersections between primitives are not complex and located in small regions.
-
-\subsubsection{Triangle-triangle intersection}
-
-Our triangle-triangle intersection test is largely based on M\"{o}ller's algorithm \cite{moller1997fast}, which is very efficient to compute intersection between two triangles.
-However, naive implementation of M\"{o}ller's algorithm using vertex-based geometry brings numerical errors.
-Therefore, we integrate P-rep into M\"{o}ller's algorithm.
-All intersection points and line segments are represented using plane intersections to avoid explicitly computing the coordinates.
-Also, we carefully deal with degenerate cases of triangle intersections, including point intersection, edge intersection and coplanar situation.
-Details are provided in \S\ref{section:isect}.
-
-\subsubsection{Tessellation}
-
-Once all intersections between triangles are detected, we need to tessellate the input meshes and construct the intersection-free meshes.
-In many methods like \cite{ogayar2015deferred}, constraint Delaunay triangulation (CDT) is applied to perform tessellation.
-However, for a CSG with more than two meshes, intersections may overlap or intersect with each other, and cannot be used for constraints of CDT directly.
-In addition, as our intersections are represented by planes, implementation of CDT are complex and inefficient, as most CDT algorithms (e.g.
-\cite{chew1989constrained}, \cite{de1992line}) is not designed to handle planes and requires explicit coordinates.
-Therefore, we first perform intersection refinement to resolve intersecting intersections.
-After that, we construct a graph-like structure suitable for P-rep intersections, called \emph{tess-graph}, to guide the exact tessellation of each face.
-After all faces are tessellated, we get our intersection-free hybrid meshes, where 'hybrid' means the meshes are represented by both B-rep and P-rep.
-Details are shown in \S\ref{sec:tessellation}.
-
-\iffalse
-\begin{figure}
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=1.7in]{sgen}\\
-  \caption{Triangle-triangle intersections made by different triangle pairs may (a) overlap or (b) intersect with each other.
-(c) Such situation introduces extra vertex which is intersection of triangles from three different meshes.}\label{fig:p-reps}
-\end{figure}
-\fi
-
-\subsubsection{Face classification}
-
-This step is to choose faces from the intersection-free meshes to generate the final mesh.
-However, literally computing all the space indicators of each face is unacceptably slow for large CSG mesh.
-We utilize the geometry connectivity to propagate indicators in a flood-filling way, which is based on the spatial coherence of face indicators.
-In addition, many methods use barycenters of faces together with point-in-polyhedra test for face classification, which is not exact nor robust with fix-precision float-point arithmetics.
-Douze et al.
-\cite{douze2015quickcsg} classifies faces using space indicators of vertices, but failed to deal with coplanar conditions because of coplanar leads to ambiguity of $same$ and $oppo$ in such configurations.
-Different from them, we classify faces based on the classification results of exactly represented vertices, including input vertices and newly introduced intersection vertices, and carefully deal with coplanar conditions to ensure topology consistency.
-Details will be shown in \S\ref{sec:classification}.
-
-\section{Plane-based Geometry}
-
-%As we discussed in \S\ref{sec:paradigm}, one of the problem in boolean operations under vertex-based representation is it inevitably introduces new vertices, whose coordinates cannot be exactly represented using fix-precision float-point number.
-On the other hand, if P-rep is used, no new geometry information needs to be constructed.
-Therefore, we can use only geometric decision predicates to perform boolean operations.
+Despite of the performance improvement, it can make the numerical problem worse because the false classification may propagate to neighboring faces.
+
+\subsection{Plane-based Geometry}
 
@@
 
-Using Plane-based representation, each face $\bm{s}$ with $n$ edges is represented by a supporting plane $\bm{p}_{s,sp}$, where the face lies, and a list bounding planes $\{\bm{p}_{s,b}^i \ \vert\  i = 0, 1,...,n-1\}$.
+In our method, we introduce plane-based representations (P-reps) into conventional B-rep-based boolean algorithms and substitute constructions under B-reps with predicates under P-reps.
+In this way, we avoid numerical errors.
+Using P-reps, each face $\bm{s}$ with $n$ edges is represented by a supporting plane $\bm{p}_{s,sp}$, where the face lies, and a list bounding planes $\{\bm{p}_{s,b}^i \ \vert\  i = 0, 1,...,n-1\}$.
 Each edge line $\bm{e}_{\bm{s}}^i$ is represented by intersection $\bm{p}_{s,sp} \cap \bm{p}_{s,b}^i$.
 Corner vertex $\bm{v}_s^i$ is represented by intersection $\bm{p}_{s,sp} \cap \bm{p}_{s,b}^i \cap \bm{p}_{s,b}^{{(i+1)}\bmod{n}}$.
+We use Campen et al.'s method \cite{campen2010exact} for exact conversion of triangles to their P-reps.
+All geometry predicates are computed using filtering techniques proposed by Shewchuk \cite{shewchuk1997adaptive} for both exactness and efficiency.
 
@@
 A point $\bm{v}$ can be represented by non-trivial plane triples $(\bm{p}_v^0 \cap \bm{p}_v^1 \cap \bm{p}_v^2)$, or in short, $\bm{v}\colon(\bm{p}_v^0 \cap \bm{p}_v^1 \cap \bm{p}_v^2)$.
-
-We use Campen et al.'s method \cite{campen2010exact} for exact conversion of triangles from their vertex-based representation to plane-based representation.
-During the conversion, the coordinates of input vertices is rounded to certain precision which is dependent on the precision used to represent plane coefficients during boolean operation.
-If IEEE 754 double precision float-point number is used, 20-bit precision is allowed, which is enough for most CAD applications.
-As the precision of input coordinates is finite, we can determine in advance the upper boundary of precision needed to perform a precise decision, with which we can use fixed precision predicates to improve performance.
-For efficiency, we implement all geometry predicates using filtering techniques proposed by Shewchuk \cite{shewchuk1997adaptive}.
 
@@
 \label{sec:substrates}
-Plane-based geometry predicates used in our method include checking coincidence and co-orientation of planes, orientation of a plane with respect to a point, and whether three planes intersect in a unique point, etc.
-Most of them are well-discussed in previous work \cite{bernstein2009fast,banerjee1996topologically}.
-In the following, we focus on two advanced predicates, which are also important building blocks of our method.
+Plane-based geometry predicates used in our method are mostly well-discussed in previous work \cite{bernstein2009fast,banerjee1996topologically}.
+In the following, we focus on two predicates related to sorting, which we think are necessary to discussed particularly.
 
@@
 
+\subsection{Method Overview}
+
+There are generally three steps in our method.
+The first step is to compute intersections between each triangle face pairs.
+After that, the input meshes are tessellated into intersection-free meshes according to these intersections.
+The last step is to classify each face and generate the final result mesh.
+
+\subsubsection{Intersection computation}
+
+In this step, we only compute intersections between triangle pairs.
+The triangle-triangle intersection test is largely based on M\"{o}ller's algorithm \cite{moller1997fast}, which is very efficient to compute intersection between two triangles.
+However, conventional implementation of M\"{o}ller's algorithm using vertex-based geometry brings numerical errors.
+Therefore, we integrate P-rep into M\"{o}ller's algorithm.
+All intersection points and line segments are represented using plane intersections to avoid explicitly computing the coordinates.
+Also, we carefully deal with degenerate cases of triangle intersections, including point intersection, edge intersection and coplanar situation.
+Details are provided in \S\ref{section:isect}.
+
+\subsubsection{Deferred tessellation}
+
+Once all intersections between triangles are detected, we need to tessellate the input meshes and construct the intersection-free meshes.
+In many methods like \cite{ogayar2015deferred}, constraint Delaunay triangulation (CDT) is applied to perform tessellation.
+However, for a CSG with more than two meshes, intersections may overlap or intersect with each other, and cannot be used for constraints of CDT directly.
+In addition, as our intersections are represented by planes, implementation of CDT are complex and inefficient, as most CDT algorithms (e.g.
+\cite{chew1989constrained}, \cite{de1992line}) is not designed to handle planes and requires explicit coordinates.
+Therefore, we first perform intersection refinement to resolve intersecting intersections.
+After that, we construct a graph-like structure suitable for P-rep intersections, called \emph{tess-graph}, to guide the exact tessellation of each face.
+After all faces are tessellated, we get our intersection-free meshes.
+Details are shown in \S\ref{sec:tessellation}.
+
+\iffalse
+\begin{figure}
+  \centering
+  % Requires \usepackage{graphicx}
+  \includegraphics[width=1.7in]{sgen}\\
+  \caption{Triangle-triangle intersections made by different triangle pairs may (a) overlap or (b) intersect with each other.
+(c) Such situation introduces extra vertex which is intersection of triangles from three different meshes.}\label{fig:p-reps}
+\end{figure}
+\fi
+
+\subsubsection{Face classification}
+
+This step is to choose faces from the intersection-free meshes to generate the final mesh.
+However, literally computing all the space indicators of each face is unacceptably slow for large CSG mesh.
+We utilize the geometry connectivity to propagate indicators in a flood-filling way, which is based on the spatial coherence of face indicators.
+In addition, many methods use barycenters of faces together with point-in-polyhedra test for face classification, which is not exact nor robust with fix-precision float-point arithmetics.
+Douze et al.
+\cite{douze2015quickcsg} classifies faces using space indicators of vertices, but failed to deal with coplanar conditions because of coplanar leads to ambiguity of $same$ and $oppo$ in such configurations.
+Different from them, we classify faces based on the classification results of exactly represented vertices, including input vertices and newly introduced intersection vertices, and carefully deal with coplanar conditions to ensure topology consistency.
+Details will be shown in \S\ref{sec:classification}.
+
 \section{Exact Intersection Computation}
@@
 After that, we discuss how to deal with degenerate cases.
+
+\subsection{Space Division}
+
+\begin{wrapfigure}{r}[0in]{0in}
+\includegraphics[width=1.2in]{octreediff}
+\end{wrapfigure}
+As intersection detection is performed between each pair of faces, localization is necessary to filter invalid pairs beforehand.
+Many space division methods can be used in this step.
+We use the adaptive octree for its simplicity and efficiency.
+Our implementation is akin to the implementation in Ogayar et al.'s method \cite{ogayar2015deferred}.
+Intersection between triangle faces and octree leaves are efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}.
+Octree leaves are classified into two types: if all faces that intersect a leaf belong to the same primitive, we call it a \emph{normal cell}.
+Otherwise, it is a \emph{critical cell}, within which the following intersection computation is performed.
+
+The difference between our octree and Ogayar et al.'s is that we do not subdivide any normal cell no matter how many faces it contains.
+This is because subdividing normal cells benefits only the point-in-polyhedron test  \cite{frisken2002simple}, which seldom uses in our method.
+This simplification can save much computing time, especially when intersections between primitives are not complex and located in small regions.
 
@@
 
-\section{Exact Face Classification}
+\section{Face Classification}
 
@@
 Also, by using P-reps, our classification method can deal with any degenerate cases.
-
-\subsection{Framework}
 
@@
 
+\iffalse
 \subsection{Tessellating on Classification}
@@
 
-\iffalse
 \subsection{Implementation}
@@
 
-\section{Discussion}
-\label{sec:esubroutine}
-
-\begin{figure*}[!t]
-\centering
-\includegraphics[width=7in]{null}
-\caption{different models...........}
-\label{fig:models}
-\end{figure*}
-
-\vspace{0.5em}
-\noindent\textbf{Searching valid loops}~~~~ In \S\ref{sec:tess}, we claim a valid loops on tess-graph has to be correct with its orientation.
-However, since tess-graph is undirectional, it is not easy to check whether a loop orientation agrees with the face's (Fig.
-\ref{fig:dual}a).
-We observe that the graph connections lie on face edges have their unambiguous directions.
-Starting from these edges, we can guarantee that the loops have the right orientations.
-After we find a valid loop, more graph connections will have unambiguous directions because one connection can participate two valid loops at most.
-In such way, the correct orientation will propagate in a flood-filling way.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=3in]{dual}
-\caption{a) We cannot easily figure out the correct orientation of the loop.
-b) When there are more than one connected component, we use auxiliary intersection (red line) to connect the two component.
-}
-\label{fig:dual}
-\end{figure}
-
-\vspace{0.5em} There is another problem that the tess-graph may not be a connected graph.
-We avoid this problem by inserting auxiliary intersections into the tess-graph to make it connected.
-An auxiliary intersection links the vertex of face (denoted as $\bm{v}_i$) on the outer connected component with the vertex on the inner connected component.
-The intersection refinement has to be performed again if the auxiliary intersections cross any other intersections.
-To guarantee the auxiliary intersection has a valid PBI-rep, we require the vertex from inner connected component generated by intersection between the face and an edge (denoted as $\bm{e}_j$) from other meshes---all newly introduced vertices during triangle-triangle intersection are this type.
-In this way, we get three vertices with exact coordinates ($\bm{v}_i$ and the two end points of $\bm{e}_j$) and can construct an exact plane where the auxiliary intersection lies.
-
-\vspace{0.5em}
-\noindent\textbf{Seed indicator generation}~~~~In \S\ref{sec:propagation}, we claim that our flood-filling starts from a seed vertex $\bm{v}_0$.
-While the indicator vector of the seed $\bm{\Lambda}(\bm{v}_0)$ can be generated by point-in-polyhedron test \cite{ogayar2005point} with the octree as acceleration structure \cite{frisken2002simple}, we have simpler strategies by using vertex with known indicators as the seed.
-We choose the vertex with the max $x$-coordinate as the seed.
-In this way, $\lambda_k(\bm{v}_0)$ is either $out$ ($in$, if complement is applied on mesh) or $on$.
-The $on$ indicators are easy to determine in most time.
-Though sometimes exception occur because of multi-coplanar situation, this will not happen if we carefully choose the right vertex whose neighbor faces are not coplanar.
-
-\vspace{0.5em} The indicator vectors can propagate not only among single meshes, but can also between different meshes by the vertices and edges they share.
-Therefore in most time, we only need one single seed vertex for classification.
-However, if there are more than two connected components among meshes, we need to new seeds to propagate each component.
-The indicators of the second and later seeds can be computed by point-in-polyhedron tests.
-
-%Our method of generating the first indicator vector will fail on extreme conditions when all faces in Linked halfedge are coincident with more than one primitive face (e.g., the union of the same mesh).
-In order to be robust, we use the high-precision face barycenter with the point-in-polyhedron test to generate the seed indicator vector instead after several failures of choosing a proper seed face.
-
-\section{Experiments}
+\section{Results and Discussion}
+
+We implemented the proposed method in C++ and tested a series of models on a laptop with Intel Core i5 1.5GHz CPU and 8GB RAM.
+To prove both the efficiency and robustness, we perform boolean evaluation on various CSGs with different complexity.To show our advantage, we also compared our method with several previous works with available implementations, including CGAL \cite{cgal:hk-bonp3-15a}, Maya \cite{Maya2015,barki2015exact},"Cork" \cite{Cork}, "QuickCSG" \cite{douze2015quickcsg}, "Carve" \cite{Carve}, and online service of Campen and Kobbelt's plane-based method \cite{campen2010exact,WebBSP}.
+
+\subsection{Robustness}
 
@@
 
-We implemented the proposed method in C++ and tested a series of models on a laptop with Intel Core i5 1.5GHz CPU and 8GB RAM.
-To prove both the efficiency and robustness, we perform boolean evaluation on various CSGs with different complexity.
-Extreme degenerate cases such as self-union are also tested.
-
-We compared our method with several previous works with available implementations, including CGAL \cite{cgal:hk-bonp3-15a}, Maya \cite{Maya2015,barki2015exact},"Cork" \cite{Cork}, "QuickCSG" \cite{douze2015quickcsg}, "Carve" \cite{Carve}, and online service of Campen and Kobbelt's plane-based method \cite{campen2010exact,WebBSP}.
-
-\vspace{0.5em}
-\noindent\textbf{Self-union}~~~~
 Our method is unconditionally robust for regular set meshes.
@@
 
+\subsection{Performance}
 \vspace{0.5em}
@@
 
-\iffalse
-
-\subsection{Robustness}
+\subsection{Implementation Details}
+
+\begin{figure*}[!t]
+\centering
+\includegraphics[width=7in]{null}
+\caption{different models...........}
+\label{fig:models}
+\end{figure*}
 
 \vspace{0.5em}
-\noindent\textbf{Indicator up-propagation}~~~~
-In \S\ref{sec:propagation}, we point out that up-propagation (from low dimension to high dimension, $\bm{v}_{\bm{e}}\to e$ and $\bm{e}_{\bm{s}}\to s$, etc.) can be done by using sample points.
-Here we give use a heuristic method to prove our claim in $\bm{e}_{\bm{s}}\to s$.
-Extension to $\bm{v}_{\bm{e}}\to e$ should not take much effort.
-
-\vspace{0.5em}\noindent We prove $\lambda_k(\bm{v}_x)=\lambda_k(\bm{v}_{\delta})$ in the BSP of $\bm{e}_{\bm{s}}$'s neighborhood, where $ \bm{v}_x$ is the sample point from $\bm{p}_{s, sp}^+$ and $\bm{v}_{\delta}$ is from the neighborhood $U(\bm{e}_{\bm{s}}, \delta)$.
-If $\lambda_k(\bm{v}_x) \neq on$, then
-
-Given $\bm{v}_{x'}(t_i)$ can be arbitrarily close to $\bm{v}_b^2(t_i)$, if $\lambda(\bm{v}_b^2(t_i), P_j) = in | out$, the equality holds because of the continuity of space.
-If $\lambda(\bm{v}_b^2(t_i), P_j) = on$, we divide the proof of equality into two parts according to the type of intersection context.
-If $C_{P_h \backslash P_j}$ is face neighboring type, $\boldsymbol{D}(C_{P_h \backslash P_j})$ is a single face, say, $t_0^c$.
-We have already know that the other two corners $\bm{v}_{b*}^{0}(t_i)$ and $\bm{v}_{b*}^{1}(t_i)$ are on $\bm{s}_0$.
-Since $\lambda(\bm{v}_b^2(t_i), P_j) = on$, we know $\bm{v}_b^2(t_i)$ is on $t_0^c$, too.
-There comes the conclusion that the whole triangle $t_i$ is coplanar with $t_0^c$.
-Therefore, $\bm{v}_{x'}(t_i)$ is on $t_0^c$ and $\lambda(\bm{v}_{x'}(t_i), P_j) = on$, too.
-On the other hand, if $C_{P_h \backslash P_j}$ is edge neighboring type, $\boldsymbol{D}(C_{P_h \backslash P_j})$ are two neighboring faces (denoted as $t_1^c, t_2^c$).
-We know that both $\bm{v}_{b*}^{0}(t_i)$ and $\bm{v}_{b*}^{1}(t_i)$ are on the shared edge $e(\bm{v}_{b*}^{0}(t_i), \bm{v}_{b*}^{1}(t_i))$.
-It means both vertices are on both $t_1^c$ and $t_2^c$.
-Using the same deduction of the first condition, we can conclude $\lambda(\bm{v}_{x'}(t_i), P_j) = on$ whenever $\lambda(\bm{v}_b^2(t_i), P_j) = on$.
+\noindent\textbf{Searching valid loops}~~~~ In \S\ref{sec:tess}, we claim a valid loops on tess-graph has to be correct with its orientation.
+However, since tess-graph is undirectional, it is not easy to check whether a loop orientation agrees with the face's (Fig.
+\ref{fig:dual}a).
+We observe that the graph connections lie on face edges have their unambiguous directions.
+Starting from these edges, we can guarantee that the loops have the right orientations.
+After we find a valid loop, more graph connections will have unambiguous directions because one connection can participate two valid loops at most.
+In such way, the correct orientation will propagate in a flood-filling way.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=3in]{dual}
+\caption{a) We cannot easily figure out the correct orientation of the loop.
+b) When there are more than one connected component, we use auxiliary intersection (red line) to connect the two component.
+}
+\label{fig:dual}
+\end{figure}
+
+\vspace{0.5em} There is another problem that the tess-graph may not be a connected graph.
+We avoid this problem by inserting auxiliary intersections into the tess-graph to make it connected.
+An auxiliary intersection links the vertex of face (denoted as $\bm{v}_i$) on the outer connected component with the vertex on the inner connected component.
+The intersection refinement has to be performed again if the auxiliary intersections cross any other intersections.
+To guarantee the auxiliary intersection has a valid PBI-rep, we require the vertex from inner connected component generated by intersection between the face and an edge (denoted as $\bm{e}_j$) from other meshes---all newly introduced vertices during triangle-triangle intersection are this type.
+In this way, we get three vertices with exact coordinates ($\bm{v}_i$ and the two end points of $\bm{e}_j$) and can construct an exact plane where the auxiliary intersection lies.
 
 \vspace{0.5em}
-\noindent\textbf{Proof of Robustness}
-
-\fi
-
-\section{Extensions}
+\noindent\textbf{Seed indicator generation}~~~~In \S\ref{sec:propagation}, we claim that our flood-filling starts from a seed vertex $\bm{v}_0$.
+While the indicator vector of the seed $\bm{\Lambda}(\bm{v}_0)$ can be generated by point-in-polyhedron test \cite{ogayar2005point} with the octree as acceleration structure \cite{frisken2002simple}, we have simpler strategies by using vertex with known indicators as the seed.
+We choose the vertex with the max $x$-coordinate as the seed.
+In this way, $\lambda_k(\bm{v}_0)$ is either $out$ ($in$, if complement is applied on mesh) or $on$.
+The $on$ indicators are easy to determine in most time.
+Though sometimes exception occur because of multi-coplanar situation, this will not happen if we carefully choose the right vertex whose neighbor faces are not coplanar.
+
+\vspace{0.5em} The indicator vectors can propagate not only among single meshes, but can also between different meshes by the vertices and edges they share.
+Therefore in most time, we only need one single seed vertex for classification.
+However, if there are more than two connected components among meshes, we need to new seeds to propagate each component.
+The indicators of the second and later seeds can be computed by point-in-polyhedron tests.
 
 \vspace{0.5em}
-\noindent\textbf{Converting to float-point number}~~~~
+\noindent\textbf{Exporting to float-point number}~~~~
 The vertices of final mesh in our method are represented in both P-reps and plain coordinates.
@@
 
-\vspace{0.5em}
-\noindent\textbf{Incremental evaluation}~~~~While we claim that in many CSGs, a non-incremental evaluation is faster by avoiding repetitive computation, one can easily find counter-examples that non-incremental evaluation contains useless intersection computation.
-For example, if 100 spheres densely locate in a small region, each sphere will need to intersect with other 99 spheres.
-However, if evaluating incrementally, we might not need to compute so many intersections.
-Fortunately, our method can also perform incremental evaluation.
-For exactness and robustness, we have to deal with non-triangle input meshes in incremental evaluations and intersection vertices should not be converted to float-point coordinate representation.
-
-\vspace{0.5em}
-\noindent\textbf{Extending to polygon meshes}~~~~
-In our method, we claim the inputs are triangle meshes mainly to avoid plane fitting when converting to P-reps.
-However, if we assume the P-reps of non-triangle faces are exactly known, our method can be easily extend to polygon meshes.
-
-\vspace{0.5em}\noindent The only different part is intersection computation.
-The first step of M\"{o}ller's triangle-triangle intersection method is to test each edge-plane pair respectively.
-This idea can be extended to polygon intersections.
-Then we can get two plane-face intersections $Seg1$ and $Seg2$, except that in polygon cases, $Seg1$ and $Seg2$ are two sets of line segments, instead of single segments.
-Later processes are the same.
-
-\vspace{0.5em}
-\noindent\textbf{Extend to piece-wise wind number meshes}~~~~Recent works claim that the piece-wise wind number (PWN) are more powerful to identify the inside and outside of meshes \cite{zhou2016mesh}.
-Our method is straightforward to apply PWN because we can use the neighborhoods of intersections to compute the PWN of each point easily.
-By using PWN, we can extend our input from regular set mesh without self-intersection to so-called PWN mesh that allows deficiencies such as self-intersection and multi-component.
+\subsection{Limitations and Future Work}
+
+We noticed that for CSGs that contains a lot of meshes within small area (e.g., Table.
+\ref{tab:performance}, \emph{T1}), the performance of our method is poor.
+This is because in such situations, our method computes many intersections that will not appear as edges in the final mesh, which leads to unnecessary tessellation.
+Optimization may be explored to avoid such problem.
+
+The input of our method is limited to regular set meshes.
+However, recent works claim that the piece-wise wind number (PWN) are more powerful to identify the inside and outside of meshes \cite{zhou2016mesh}.
+By using PWN, the input requirements can be extended to so-called PWN mesh that allows deficiencies such as self-intersection and multi-component.
+Our method is suitable to be extended to PWN meshes because we can use the neighborhoods of intersections to compute the PWN of each point easily.
 However, the cost of this extension is that we have to check every triangle pairs for intersections, even if they are from the same input mesh.
-Considering this cost, we prefer a pre-computation to resolve topology deficiencies only on those input meshes that we think that might be 'unclean'.
-
-\iffalse
-\vspace{0.5em}
-\noindent\textbf{Lazy intersection}~~~~
-Another way to avoid useless intersection computation is to use lazy intersection technique
-\fi
 
@@
 
-In this paper, we proposed a novel method to evaluate CSG with triangular mesh primitives.
-It is able to efficiently perform unconditionally robust non-incremental boolean operations of CSG with massive faces.
-The key idea of our approach is to strictly follow the principle of plane-based geometry, avoiding geometry construction all along the method.
-Also, we use the local coherence of face space labels to accelerate face membership classification.
-Experiments have verified the proposed approach is more efficient than the state-of-the-art techniques while retaining robustness and stability.
+In this paper, we proposed a novel method to evaluate CSG with regular set primitives.
+It is able to efficiently perform unconditionally robust non-incremental boolean operations.
+The key idea of our approach is to embed P-reps information into B-reps.
+The P-reps give us the chance to strictly follow the principle of no geometry construction to avoid numerical errors.
+And the B-reps offer fast neighborhood query to accelerate the processing.
+Experiments have verified the performance of our method is competitive with state-of-the-art non-robust methods while guarantee unconditional robustness.
 

### 2016-12-08 summary.tex
almost complete with experiments

@@
 \usepackage{color}
-\usepackage[numbers,sort&compress]{natbib}
+%\usepackage[numbers,sort&compress]{natbib}
 %\usepackage{ulem}
@@
 \usepackage{wrapfig}
+
+\usepackage{amssymb}% http://ctan.org/pkg/amssymb
+\usepackage{pifont}% http://ctan.org/pkg/pifont
+\newcommand{\cmark}{\ding{51}}%
+\newcommand{\xmark}{\ding{55}}%
 % correct bad hyphenation here
@@
 However, boolean operations, which compute the boundary representation of CSG, have been suffered from robustness and efficiency problem for more than three decades.
-In this paper, we propose a fast and exact boolean operation method which is unconditionally robust for regular set solids.
-We notice that among previous works, plane-based boolean methods are easy to achieve robustness, but hard to be efficient.
-On the other hand, methods based on B-reps of meshes are fast but not robust unless exact arithmetic is applied.
-We choose to combine plane-based representations (P-reps) with B-reps, which allows us to take the advantages of both.
+We propose a fast and exact boolean operation method which is unconditionally robust for regular set solids.
+We notice that among previous works,boolean methods using plane representations (P-reps) of meshes are easy to achieve robustness, but hard to be efficient.
+On the other hand, methods based on boundary representation (B-reps) of meshes are fast but not robust unless exact arithmetic is applied.
+Therefore, we choose to combine P-reps with B-reps, which allows us to take the advantages of both.
 Our method is globally based on B-reps for its efficiency, and P-rep geometry is applied locally to ensure robustness.
-Comparison experiments with state-of-the-art techniques show that our method is unconditionally exact and robust, while is competitively efficient with non-robust methods and much faster than the robust ones.
+Comparison experiments with state-of-the-art techniques show that our method is unconditionally exact and robust, while is competitively efficient as non-robust methods.
 \end{abstract}
@@
 Plane-based geometry predicates used in our method are mostly well-discussed in previous work \cite{bernstein2009fast,banerjee1996topologically}.
-In the following, we focus on two predicates related to sorting, which we think are necessary to discussed particularly.
+In the following, we focus on two predicates related to sorting, which are designed for our method particularly.
 
@@
 To solve this problem, we choose one plane not parallel with $\bm{l}_{ab}$ from the plane representation of each point.
-Then we convert this problem into linear order of planes and solve it using the same technique as Banerjee et al.
+Then we convert this problem into linear order of planes, which can be solved by Banerjee et al.
 \cite{banerjee1996topologically}.
@@
 
-\section{Exact Intersection Computation}
+\section{Intersection Computation}
 
@@
 \end{wrapfigure}
-As intersection detection is performed between each pair of faces, localization is necessary to filter invalid pairs beforehand.
+As intersection detection is performed between each pair of faces, localization is necessary for large CSGs to reduce the number of testing pairs.
 Many space division methods can be used in this step.
@@
 
-In previous work, Ogayar-Anguita et.
+Ogayar-Anguita et.
 al.
@@
 Our first try is to implement a robust plane-based CDT.
-However, CDT algorithms \cite{chew1989constrained,preparata2012computational} usually require coordinates projection or intersection detection between arbitrary connections of vertices within triangulation zone.
-Because vertices may be implicitly represented in our method, these geometry predicates are hard to guarantee computation efficiency and precision simultaneously.
+However, CDT algorithms \cite{chew1989constrained,preparata2012computational} require coordinates projection or intersection detection between arbitrary connections of vertices within triangulation zone, which are difficult to be implemented under P-reps.
+From another perspective, CDT contains geometry constructions---new edges are generated to guarantee each subface is a triangle, which does not fit P-reps.
 Moreover, when there are more than two primitives, simply applying CDT omits the complexity of intersections between meshes.
@@
 An tess-graph is a graph-like description of intersections on a certain face.
-The word `conservative` means we tessellate face into polygons, not triangles.
+The word `conservative` means we .
 This is because if triangles are required, we need construct new bounding planes for these new triangles, which violating our principle of no geometry construction (Fig.
@@
 If not, we need to find where $\bm{v}_{\bm{e}}$ lies on the surface of $P_k$ and determine the neighborhood of $\bm{v}_{\bm{e}}$.
-In most cases, it is straightforward since coincident vertices among different intersection-free meshes are shared.
-Exceptions are discussion is in \S\ref{sec:esubroutine}.
+In most cases, it is straightforward since coincident vertices among different intersection-free meshes are shared (see \S\ref{sec:esubroutine} for exception discussion).
 The neighborhood may be a vertex, an edge or a face.
@@
 
+\begin{figure}[t]
+\centering
+\includegraphics[width=3in]{perturb}
+\caption{Even after perturbation, the self-union of \emph{bunny} under QuickCSG still suffers from topology problem. The green faces are boundary faces which indicating topology deficiencies.}
+\label{fig:boundaryedge}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=3in]{buddalion}
+\caption{ Different results from $Budda\cup Lion$: a) incorrect result by CGAL, b) incorrect result by Cork, c) correct result of our method. }
+\label{fig:buddalion}
+\end{figure}
+
 We implemented the proposed method in C++ and tested a series of models on a laptop with Intel Core i5 1.5GHz CPU and 8GB RAM.
@@
 \subsection{Robustness}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=3in]{dual}
+\caption{a) We cannot easily figure out the correct orientation of the loop.
+b) When there are more than one connected component, we use auxiliary intersection (red line) to connect the two component.
+}
+\label{fig:dual}
+\end{figure}
 
@@
 \hline\hline
-1 & Budda $\cup$ Lion & 1.08M & 0.4M & - & - & - & - & 3.44 & 6.88\\
-2 & Dragon $\cup$ Bunny & 100k & 70k & - & - & - & - & 0.334 & 0.636 \\
-3 & Armadillo $\cup$ Armadillo2 & 150k & 150k & - & - & - & - & 0.746 & 1.62\\
-4 & Horse $\cup$ Corpse & - & - & - & - & - & - & - & -\\
-5 & Dinasour $\cup$ Ironman & - & - & - & - & - & - & - & -\\
+1 & Budda $\cup$ Lion & 1.08M & 400k & - & - & - & - & 3.44 & 6.88\\
+2 & Dragon $\cup$ Bunny & 100k & 70k & - & - & - & - & 0.613 &1.70 \\
+3 & Armadillo $\cup$ Armadillo2 & 150k & 150k & 487 & 15.4 & 7.00 & 189 & 0.746 & 1.62\\
+4 & Horse $\cup$ Corpse & 145k & 499k & - & 38.6 & 12.6 & 1.52k & 0.630 & 1.00 \\
+5 & Budda $\cup$ Budda2 & 1.08M & 1.08M & - & - & - & - & 4.84 & -\\
 \hline
@@
 {No.} & {Model} & {Triangle Num.} & {Primitive Num.} &
-CGAL* & Maya* & Cork & Carve & QuickCSG & Our Method
+CGAL & Maya & Cork & Carve & QuickCSG & Our Method
 \\
 \hline\hline
-1 & Sprocket & - & 52 & - & - & - & - & 0.059 & -\\
-2 & ring and ball & - & 201 & - & - & - & - & - & -\\
-3 & T1 & - & 50 & - & - & - & - & 0.433 & 10.1\\
-4 & T2 & - & 50 & - & - & - & - & 0.804 & -\\
-5 & H & - & 42 & - & - & - & - & 2.22 & -\\
-6 & Organic & - & 6 & - & - & - & - & 0.590 & -\\
-7 & 6 Budda & - & 6 & - & - & - & - & - & -\\
-8 & Serpent & - & - & - & - & - & - & - & -\\
-9 & Dithering & - & - & - & - & - & - & - & -\\
+1 & Sprocket & 11k & 52 & 211 & ? & - & 4.26 & 0.132 & 0.804\\
+2 & Ring \& Ball & 146k & 801 & - & ? & - & 187 & - & 62.6\\
+3 & T1 & 80k & 50 & 1.00k & ? & 18.5 & 10.4 & 0.388 & 20.2\\
+4 & T2 & 7k & 50 & 2.81k & ? & - & 16.0 & 0.804 & -\\
+5 & H & 33k & 42 & - & ? & - & - & 2.22 & -\\
+6 & Organic & 219k & 6 & - & ? & 14.3 & 63.1 & 0.580 & 2.75\\
+%7 & 6 Budda & - & 43 & - & - & - & - & - & -\\
+%8 & Serpent & - & 5 & - & - & - & - & - & -\\
 \hline
@@
 \begin{table*}[ht]
-\caption{Face Number of the Results of Self-Union Evaluation}
+\caption{Results of Self-Union Evaluation}
 \label{tab:selfunion}
 \centering
-\begin{tabular}{*{9}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
+\begin{tabular}{*{8}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
 \hline
-{No.} & {Model} & {Orig. Num.} &
-CGAL & Maya & Cork & Carve & QuickCSG & QuickCSG2* & Our Method
+{No.} & {Model} & {Face Num.} &
+CGAL & Maya & Cork & Carve & QuickCSG  & Our Method
 \\
 \hline\hline
-1 & Ball & 360  & - & 360 & - & - & 1 & 360 & 360 \\
-2 & head & 2,716& - & 2,716 & - & - & 5 & 2,716 & 2,716\\
-3 & Bunny & 69,666  & - & 69,664 & - & -& 0 & 69,668 & 69,669\\
-4 & Dragon & 276,972 & - & 0 & - & -& 1 & 276,702 & 277,987 \\
+1 & Ball & 360  & \cmark & \cmark & \xmark & \cmark & \xmark & \cmark \\
+2 & head & 2,716& \cmark & \cmark & \xmark & \cmark & \xmark  & \cmark\\
+3 & Bunny & 69,666  & \xmark & \cmark & \xmark & \cmark & \xmark  & \cmark\\
+4 & Dragon & 276,972 & \xmark & \xmark & \xmark & \xmark & \xmark  & \cmark \\
 \hline
@@
 \begin{flushleft}
-~~~~~~~~~~~~~~~~~~~~~$^{*}$~~We perturb the model by 1e-6 to give QuickCSG the ability to partly solve coplanar cases.
+%~~~~~~~~~~~~~~~~~~~~~$^{*}$~~We perturb the model by 1e-6 to give QuickCSG the ability to partly solve coplanar cases.
 \end{flushleft}
@@
 The slightly deviation of our result from the original one is caused by self-intersection in the original models.
-QuickCSG failed to produce the result in all coplanar cases, because they cannot deal with coplanar faces.
-After perturbation, results of QuickCSG are visually OK.
+QuickCSG and Cork failed in all cases, because they cannot deal with coplanar faces.
+By perturb one of the operant, the results of QuickCSG are visually OK.
 However, the topology of their results is messy.
-We can see hundreds of boundary edges on their results which do not exist in the original model (Fig.
+We can see hundreds of boundary faces on their results which do not exist in the original model (Fig.
 \ref{fig:boundaryedge}).
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=3in]{null}
-\caption{boundary edges on the models........}
-\label{fig:boundaryedge}
-\end{figure}
 
@@
 Table \ref{tab:performance} shows the evaluation time of different methods.
-We can clearly see our method is very fast that is only slightly slower than the fastest non-robust QuickCSG.
+We can clearly see our method is very fast that is only twice as slower than the fastest non-robust QuickCSG.
 Other robust methods such as Maya and CGAL are much slower because both of them use the arbitrary precision arithmetic.
-It should be noted that in (some) very large CSGs, most time is spent on octree construction in our method.
+Moreover, these robust methods have very strict requirements on the inputs and fragile with topology deficiencies such as boundary edges or self-intersection.
+On the contrary, our   We also noticed that in (some) very large CSGs, most time is spent on octree construction in our method.
 It means other stages which involve plane-based geometry take only a small percentage of time, proving the efficiency of our plane-based geometry.
@@
 During our experiments, we noticed Maya gives the correct results in the first few boolean operations, but failed in the later ones.
-It proves another disadvantage of incremental boolean operation methods: if it cannot guarantee exactness, it will accumulate numerical errors which affects the algorithm stability.
-
-\subsection{Implementation Details}
+It proves a disadvantage of incremental boolean operation methods: if it cannot guarantee exactness, it will accumulate numerical errors which affects the algorithm stability.
 
@@
 \centering
-\includegraphics[width=7in]{null}
-\caption{different models...........}
+\includegraphics[width=7in]{models}
+\caption{***********different models: will be replaced}
 \label{fig:models}
 \end{figure*}
+
+\subsection{Implementation}
+\label{sec:esubroutine}
 
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=3in]{dual}
-\caption{a) We cannot easily figure out the correct orientation of the loop.
-b) When there are more than one connected component, we use auxiliary intersection (red line) to connect the two component.
-}
-\label{fig:dual}
-\end{figure}
-
 \vspace{0.5em} There is another problem that the tess-graph may not be a connected graph.
@@
 However, recent works claim that the piece-wise wind number (PWN) are more powerful to identify the inside and outside of meshes \cite{zhou2016mesh}.
-By using PWN, the input requirements can be extended to so-called PWN mesh that allows deficiencies such as self-intersection and multi-component.
-Our method is suitable to be extended to PWN meshes because we can use the neighborhoods of intersections to compute the PWN of each point easily.
-However, the cost of this extension is that we have to check every triangle pairs for intersections, even if they are from the same input mesh.
+By using PWN, the input requirements can be extended to so-called PWN meshes that allow deficiencies such as self-intersection and multi-component.
+It would be interesting to extend our method to PWN method in the future.
 

### 2016-12-12 paper.tex
here!!!!

--- 2016-05-09 newpaper.tex
@@
 \usepackage{slashbox}
+\usepackage{color}
+%\usepackage[numbers,sort&compress]{natbib}
 %\usepackage{ulem}
@@
 \usepackage{color}
-
+\usepackage{bm}
+%\usepackage{mathrsfs}
+\usepackage[mathcal]{eucal}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{wrapfig}
+
+\usepackage{amssymb}% http://ctan.org/pkg/amssymb
+\usepackage{pifont}% http://ctan.org/pkg/pifont
+\newcommand{\cmark}{\ding{51}}%
+\newcommand{\xmark}{\ding{55}}%
 % correct bad hyphenation here
@@
 \newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}
-\floatname{algorithm}{Procedure}
+
+\floatname{algorithm}{Algorithm}
 
 \begin{document}
-\title{Efficient Non-incremental Constructive Solid Geometry Evaluation for Triangular Meshes}
-\author{Rui~Wang,~
-        Xudong~Jiang,~
-        Hongbo~Fu,~
-        Bin~Sheng,~and
-        Enhua~Wu
+\title{Efficient and Robust Plane-Based Boolean Operations on N Meshes}
+\author{%Rui~Wang,~
+        %Xudong~Jiang,~
+        %Hongbo~Fu,~
+        %Ping~Li,~
+        %Bin~Sheng~and
+        %Enhua~Wu
 \IEEEcompsocitemizethanks{
@@
 \IEEEcompsocthanksitem H. Fu is with the School of Creative Media, City University of Hong Kong. Email: hongbofu@cityu.edu.hk
+
+\IEEEcompsocthanksitem P. Li is with the Department of Mathematics and Information Technology, The Hong Kong Institute of Education. Email: pli@ied.edu.hk
 
@@
 \begin{abstract}
+  Constructive solid geometry (CSG) is widely used for computer aided design and manufacturing.
+However, boolean operations, which compute the boundary representation of CSG, have been suffered from robustness and efficiency problem for more than three decades.
+We propose a fast and exact boolean operation method which is unconditionally robust for regular set solids.
+We notice that among previous works,boolean methods using plane representations (P-reps) of meshes are easy to achieve robustness, but hard to be efficient.
+On the other hand, methods based on boundary representation (B-reps) of meshes are fast but not robust unless exact arithmetic is applied.
+Therefore, we choose to combine P-reps with B-reps, which allows us to take the advantages of both.
+Our method is globally based on B-reps for its efficiency, and P-rep geometry is applied locally to ensure robustness.
+Comparison experiments with state-of-the-art techniques show that our method is unconditionally exact and robust, while is competitively efficient as non-robust methods.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Boolean operations, triangle mesh, CSG evaluation, plane-based geometry.
+boolean operations, CSG evaluation, plane-based geometry
 \end{IEEEkeywords}
@@
 \IEEEPARstart{C}{onstructive} solid geometry (CSG) has long been a popular modeling tool of computer-aided design and computer-aided manufacturing (CAD/CAM).
-It constructs complex models by combining primitives using a series of regularized Boolean operations \cite{requicha1977mathematical}: union, intersection and difference.
-CSG is often represented by a binary tree, called a CSG tree, whose leaves are primitives and whose internal nodes are Boolean operations.
-\newline
-
-{\color{red}{
-Main Contribution:
-
-1.
-We develop a united representation of intersection lines between CSG primitives.
-Under this representation, Face re-tessellation and classification can be done robustly in any degenerate cases by our pipeline, while keeping good performance.
-
-2.
-Unlike any of the previous method, during the algorithm, we conduct point-in-polyhedron tests only on single seed vertex.
-We develop a propagating to spread the classification information from the seed vertex into the whole CSG.
-In addition, because of this, we do not need to build a full space division to accelerate point-in-polyhedron tests, which is usually time-consuming.
-}}
+It constructs complex models by combining primitives using a series of regularized boolean operations \cite{requicha1977mathematical,tilove1980closure}: union, intersection and difference.
+CSG can be converted into the widely-used boundary representation (B-rep) through boolean operations, which is an classical topic with history of over three decades.
+
+In general, there are two major types of boolean algorithms according to how they deal with intersection between primitive meshes.
+Approximate methods \cite{wang2011approximate,pavic2010hybrid,biermann2001approximate} redicretize the intersection areas, fit vertices approximatively and rearrange topology.
+On the other hand, exact method do not change vertex positions, retain as many input elements  (e.g., faces, vertices and topology) as possible.
+In many applications, exact methods are preferred for their accuracy.
+Also, using exact methods, the clear mapping between the surface of input and output meshes makes it easier for the inheritance of information like face colors and materials.
+
+However, for exact boolean operation methods, there is always a bargain between robustness and efficiency.
+Many exact boolean operation methods focus on efficiency.
+But for robustness, the solutions are either exact arithmetic \cite{barki2015exact,zhou2016mesh} or trivial workarounds to avoid degenerations, such as setting a tolerance \cite{feito2013fast,segal1990using} and rotating the primitive with small angles \cite{douze2015quickcsg}.
+Methods using exact arithmetic are significantly slower, and workarounds are often case dependent and not reliable.
+Recently, some methods \cite{bernstein2009fast,campen2010exact} seek unconditional robustness by avoiding geometry constructions (such as computing new vertex coordinates) and using only predicates.
+Their key idea is to utilize plane-based representations (P-reps) of meshes instead of boundary representation (B-reps), which comes from the observation of Sugihara and Iri \cite{sugihara1990solid} that boolean operations can be performed without geometry constructions if P-reps are used.
+While these plane-based methods are generally faster than exact arithmetic ones, they still suffer from performance issue because of the complex conversions among different representations.
+Also, the incoherence between different representations requires extra steps to reconstruct geometry connectivity, leading to extra computation burden and more complex topology.
+
+Inspired by these previous work, we develop an unconditionally robust boolean operation method which is as robust as P-rep-based method and as fast as non-robust B-rep-based method.
+To achieve this, we embed P-rep information into faces of B-reps, forming hybrid representation of meshes.
+We avoid geometry constructions throughout our method, and convert all necessary computation into predicates under the hybrid representation.
+In general, the B-reps information is used for coarse tests and efficient face neighbor query, while P-reps information is for exact geometry computation.
+During intersection computation, we encode the intersections between meshes into sets of planes and use these planes to perform exact tessellation.
+After that, we classify each faces in the tessellated meshes using local binary space partition (BSP) trees, which also facilitate the previous plane-based representation to guarantee exactness.
+In addition, while most previous boolean operations can only deal with two meshes, our method can perform boolean operations with arbitrary meshes in one call, instead of recursively doing incremental boolean operations.
+In this way, our method could save computation time by avoiding repetitive computation.
+The experiments show that our method is much faster than existing robust exact methods, while only about two times slower than the state-of-art non-robust exact methods.
 
@@
 
-\begin{figure*}[!t]
-\centering
-\includegraphics[width=7.1in]{flowchart}
-\caption{An overview of the proposed method for CSG evaluation.
-In this toy example, the CSG tree represents a solid constructed by (Cube $\cup$ Sphere - Cylinder).
-(d) shows how to classify faces step by step using a flood filling algorithm.
-Faces of the same primitive are grouped as the inter-primitive group.
-Then faces of the same inter-primitive group are further divided into intra-primitive groups according to their conditions of intersection (c).
-The unvisited faces are black.
-Different colors of other faces indicate that they are accepted and belong to different intra-primitive groups.
-Rejected faces are rendered with wire-frame.
-The seed face of flood filling in each primitive is highlighted in red.}
-\label{fig_overview}
-\end{figure*}
-
-CSG evaluation has had notorious problems with robustness since its inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}.
-The non-robustness is inherited from the building blocks of CSG: Boolean operations on solids.
-Many researchers have attempted to solve such an issue using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}.
-However, these methods are often too expensive in computation time and memory to be practical for evaluation of CSG with massive faces.
-For example, in the Computational Geometry Algorithms Library (CGAL) \cite{cgal:hk-bonp3-15a}, the state-of-the-art robust Boolean operation algorithm \cite{hachenberger2005boolean} (implemented with arbitrary precision arithmetic) is more than 20 times slower than its non-robust version.
-
-Sugihara and Iri \cite{sugihara1990solid} introduced a plane-based representation of polyhedra.
-They found that Boolean operations are fundamentally robust using the plane equation as the primary geometry representation.
-In this condition, the evaluation of Boolean operations can be performed with no `constructions' \cite{shewchuk1999lecture}, thereby avoiding the introduction of any numerical errors.
-
-Berstein and Fussell \cite{bernstein2009fast} noted that a binary space partitioning (BSP) merging algorithm in Boolean operations \cite{thibault1987set, naylor1990merging} is actually a plane-based technique.
-Therefore, they combined the two conceptions---plane-based geometry and BSP merging---to develop an unconditionally robust method for Boolean operations of polyhedra.
-Using Shewchuk's adaptive geometry predicate technique \cite{shewchuk1997adaptive}, this method can be only twice slower than non-robust methods.
-Our approach adopts this technique in the stage of face classification to ensure the robustness.
-
-Berstein and Fussell's method does not alleviate the problem of high memory consumption of BSP-based algorithms.
-Thus, it remains unprepared for polyhedra with massive faces.
-However, it inspired Campen and Kobbelt to develop a more delicate approach  \cite{campen2010exact}.
-This approach solves the problem of exact and efficient conversion of polyhedra between vertex-based and plane-based representations.
-Moreover, by leveraging the adaptive octree, BSP structures are nested into octree cells where the intersection between primitives occurs.
-For efficiency, face classification is performed using cells as the basic classification units.
-This localized scheme saves considerable computing resources and retains the topology of non-intersected areas.
-
-Such localized scheme is widely used in different methods of CSG boundary evaluation \cite{pavic2010hybrid, wang2011approximate, feito2013fast, campen2010exact}.
-These methods are usually based on intersection computation and face membership classification.
-The success of such localized scheme is enabled by two facts.
-First, the intersections between primitives are locally distributed.
-Second, space labels of a face are often coherent with those of its neighborhood.
-The former makes it possible to reduce the space that requires an intersection test.
-The latter enables sharing of space labels between adjacent faces to accelerate face classification.
-
-However, most of these methods use the cube (e.g., voxels, octree cells) as the unit of the face group, which is often the natural result of reusing space-division data structures constructed for intersection computation.
-In this way, connected faces that share the same labels might be distributed in different cubes.
-Thus, repetitive classifications may be required for each cube.
-Furthermore, faces of different classifications may coexist within a small space, forming a ‘mixed’ area (e.g., the red areas in Figs.
-\ref{fig:cluster}(a) and (b)).
-Because the size of the cubes cannot be illimitably small, special cubes that contain faces with different space labels typically must be constructed in these mixed areas.
-Processing these special cubes is often complex and time-consuming.
-To more efficiently share space labels, we therefore use faces, rather than cubes, as the basic grouping units.
-Grouping is efficiently performed by utilizing geometry connectivity with a flood-filling algorithm.
-
-Recently, Feito et al.
-\cite{feito2013fast} proposed a method for Boolean evaluation.
-This method also uses a face-based grouping scheme.
-To share classification results, faces that do not intersect with other primitives are grouped together according to geometry connectivity.
-This method and the proposed method have similar stages for single Boolean operation evaluation.
-One of the major differences is that our method supports non-incremental evaluation of CSG.
-For this purpose, we designed a series of dedicated stages.
-Additionally, our face grouping scheme is intended for both non-intersected faces and faces that intersect with other primitives.
-It thus provides a uniform treatment for all faces and further accelerates the face classification stage.
-Moreover, the similarity between adjacent groups is omitted by Feito et al.'s method.
-Although different groups have different space labels, we observe that they may still share some of these labels if they are neighboring.
-We utilize this kind of space label coherence between groups for better performance.
-
-On the other hand, with the development of general-purpose computing on graphics processing units (GPGPUs), many researchers  \cite{wang2011approximate, zhao2011parallel, museth2002level, chen1999volumetic, eisemann2008single} have tried to utilize the grand computation power of graphics hardware for Boolean operations.
-These methods often have good performance and are suitable for interactive applications, such as digital sculpting.
-However, owing to the paralleled features of graphics hardware, these methods are usually voxel-based and support only approximate evaluation that inevitably suffers from geometric detail loss, especially at the intersection areas of primitives.
-
-\section{Overview}
+Boolean operations have been researched for over three decades since it inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}.
+Previous works can be classified into two categories: exact methods and approximate methods.
+Exact methods retain vertex positions.
+Also the topology of the input meshes is preserved as much as possible.
+The coordinates of intersection points between input meshes are computed by input configurations to construct the topology around intersection.
+However, the coordinates cannot be represented exactly using fix-precision float-point numbers and the robustness is always a problem.
+On the other hand, approximate methods rediscretize the input mesh surfaces using techniques such as voxels, octrees and Layered Depth Images.
+They can reach better performance and robustness, but the loss of geometry information and precision is inevitable.
+
+\subsection{Exact Methods}
+
+\iffalse
+\begin{figure}[t]
+\centering
+\includegraphics[width=2.5in]{coplanarexample}
+\caption{{\color{red}{Sketch: the example of coplanar cases in a boolean operations with four cylinders}}}
+\label{fig:coplanarexample}
+\end{figure}
+\fi
+
+For exact methods, some \cite{ogayar2015deferred,douze2015quickcsg,zhou2016mesh,xu2013fast,feito2013fast} pursues efficiency but cannot guarantee robustness in degenerate cases.
+Most of them are implemented by fix-precision float-point arithmetic and numerical errors are inevitable.
+Douze et al.
+\cite{douze2015quickcsg} implemented very efficient method that can handle very large meshes.
+Also, they can perform non-incremental boolean operations: evaluating the final result mesh of CSG all at once instead of decomposing the CSG into a series of incremental boolean operations.
+However, their method can neither deal with coplanar cases nor guarantee accuracy of topology.
+In fact, large CSGs are more complex and more likely to contain degenerate cases, and more vulnerable under numerical errors.
+Efficiency only is far from being practical.
+
+Many researchers have attempted to solve robustness issue for exact boolean operations using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}.
+However, these methods are too expensive in computation time and memory to be practical for large CSGs.
+For example, one of the available implementation of robust exact boolean operations method is CGAL's \cite{cgal:hk-bonp3-15a} exact-arithmetic implementation \cite{granados2003boolean} of Nef polyhedra \cite{bieri1988elementary}.
+It requires conversions between Nef polyhedra and input mesh data structures during evaluation and is more than 50 times slower than non-robust booleans \cite{bernstein2009fast}.
+
+\subsection{Approximative Methods}
+
+Since efficiency, accuracy and robustness are hard to be satisfied at the same time, some method choose to sacrifice accuracy for better efficiency and robustness.
+Most of such methods are based on conversion to volumetric representations.
+However, the quality of result mesh depends on the resolution of the volume grid and better quality requires dramatically higher resolution.
+To accelerate this process, some try to reduce the complexity of the output mesh \cite{varadhan2004topology} and others try to preserve non-intersected areas of the input mesh to avoid redundant tessellation \cite{pavic2010hybrid,wang2011approximate,zhao2011parallel,hable2005blister,ogayar2006gpu}.
+Also, with the development of general-purpose computing on graphics processing units (GPGPU), many of them utilize the grand computation power of graphics hardware for boolean operations.
+These methods have good performance and are suitable for interactive applications.
+However, the fundamental problem of approximate methods is owing to grid-depend nature of volumetric calculations: they inevitably suffers from geometric detail loss and unwieldy topology changes.
+
+\subsection{Plane-Based Methods}
+\label{sec:pbrelated}
+
+The concept of plane-based representations (P-reps) of polygonal meshes was first described by Sugihara and Iri \cite{sugihara1990solid}.
+P-reps provide essential benefit for boolean operations that no new geometry primitive has to be constructed to obtain the results---they can be composed of a subset of the planes from the input polyhedra.
+It means the computation can include only geometry predicates, which are much easier to be implemented exactly and robustly.
+Based on P-reps, Berstein and Fussell \cite{bernstein2009fast} combined the P-reps with binary space partition (BSP) trees \cite{thibault1987set,naylor1990merging} to develop a boolean operation method which is unconditionally robust under consistent inputs .
+Compared to B-rep-based methods, their method does not rely on exact arithmetics to be robust.
+However, the merge of two BSP trees is an $O(mn)$ time complexity process, where $m$ and $n$ are the size of the trees.
+It makes this method impractical for large meshes.
+Later, Campen and Kobbelt \cite{campen2010exact} improved their method by localize BSP operations using an octree.
+The mesh refinement only takes place locally near intersections, which is much faster than Berstein and Fussell's work.
+
+\section{Background and Overview}
 
 \label{sec:overview}
-
-As in most previous works \cite{feito2013fast, bernstein2009fast}, we require the input primitives of the CSG tree to be watertight Nef polyhedra with manifold surfaces.
-We assume there is no self-intersection.
-Because we adopt a flood-filling strategy, we additionally assume that the connectivity of adjacent faces is available.
-Our current implementation is dedicated to primitives of triangular meshes for simplicity.
-Our approach efficiently and robustly computes the boundary of CSG solids in three steps, as illustrated in Fig.
-\ref{fig_overview}.
-Our main contributions exist in Steps 2 and 3.
-
-\subsection{Adaptive Octree Construction}
-
-As a typical routine of localization, our method uses the adaptive octree to frequently accelerate the used spatial query afterwards.
-Our octree construction implementation is akin to the implementation in Feito et al.'s method \cite{feito2013fast}.
-The major difference is that, because our method is for non-incremental CSG evaluation, the octree is constructed on the bounding box that contains all input primitives (Fig.
-\ref{fig_overview}(b)).
-To avoid presentation ambiguity between a CSG leaf and an octree leaf, the latter is called a cell.
-Intersection detection between triangle faces and cells can be efficiently performed by using the separating axis theorem \cite{gottschalk1996obbtree}.
-Cells are classified into two types: if all triangles that intersect a cell belong to the same primitive, we call it a \emph{non-critical} cell.
-Otherwise, it is a \emph{critical} cell.
-This classification is needed for intersection computation in the next step.
-
-\subsection{United Representation of Intersection Construction}
-\label{sec:overview:isect}
-
-\subsection{Multilevel Flood-filling Classification}
-
-\section{United Representation of Primitive Intersection}
-{\color{red}{
-Primitive intersects primitive, generating intersection line segments (Fig. \ref{fig_raw1}).
-
-\begin{figure}
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=3.5in]{raw1}\\
-  \caption{triangle contains intersection lines, two-primitive case}\label{fig_raw1}
-\end{figure}
-
-Considering degenerate cases in n-primitives CSG can be very complex (Fig. \ref{fig_raw2}).
-
-\begin{figure}
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=3.5in]{raw2}\\
-  \caption{triangle contains intersection lines, n-primitives degenerate cases}\label{fig_raw2}
-\end{figure}
-
-We converted it into a united representation, making it clear and easy to process by the following process (Fig. \ref{fig_raw3}).
-
-\begin{figure}
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=3.5in]{raw3}\\
-  \caption{triangle contains intersection lines, n-primitives degenerate cases, using united representation}\label{fig_raw3}
-\end{figure}
-}}
-
-\subsection{Plane-based Triangle Intersection}
-
-{\color{red}{why using triangle intersection, rather than edge-face based, etc. --- for coplanar test.}}
-\newline\newline
+Our method is designed for boolean operations on arbitrary number of regular triangle meshes \cite{requicha1985boolean}.
+Input meshes are required to be free from self-intersecting, and they are represented with B-reps with geometry connectivity (e.g., halfedge, winged-edge, etc.).
+Despite of these requirements, our method is robust and not sensitive to topology deficiencies like holes and self-intersections and works correctly if deficiencies are not near the intersection areas between meshes.
+
+\subsection{Boolean Numerical Errors}
+\label{sec:paradigm}
+
+The boolean operation of triangle meshes is in essence a process of face selection.
+Namely, given a boolean function, it reserves those primitive faces that pass the function and drop the others to generate the final mesh.
+Unfortunately, for B-rep meshes, not all the input faces can be classified as a whole, since for faces near the intersections, only parts of them belong to the final mesh.
+Therefore, we need an extra step aiming at detecting intersections between meshes and performing tessellation.
+Most of the boolean operation methods follow this two-step paradigm, which consists of intersection computation and face classification.
+So is our method.
+
+The first step is intersection computation.
+Input faces are tested in pairs to compute their intersections.
+Each input meshes are tessellated according to the intersection results, making every face be completely inside, outside or on the boundary of other primitives.
+The tessellated meshes are what we called \emph{intersection-free meshes}.
+Unfortunately, under fix-precision float-point arithmetic, intersection tests are error-prone: first, degenerate cases of intersection are hard to detect; second, when there are intersections, new vertices are introduced into the geometry, whose coordinates cannot be exactly represented by fix-precision float-point numbers.
+
+The second step is face classification. We evaluate whether a given face $\bm{s}$ belongs to the final geometry according to the $n$-primitive boolean function $f$ :
+\begin{equation}
+\lambda_f(\bm{s}) = f(\boldsymbol{\Lambda}(\bm{s})) = f(\lambda_1(\bm{s}), \lambda_2(\bm{s}), \cdots, \lambda_n(\bm{s})).
+\end{equation}
+The parameter $\lambda_i(\bm{s})$ is space indicator with respect to mesh $M_i$.
+To compute $\lambda_f(\bm{s})$ and classify $\bm{s}$, one has to know the space indicators with respect to all the primitives ($\boldsymbol{\Lambda}(\bm{s})$).
+A space indicator has four conditions: completely inside (\emph{in}), completely outside (\emph{out}), on the boundary with consistent normals (\emph{same}) or opposite normals (\emph{oppo}).
+The rules of boolean function evaluation are described in \cite{douze2015quickcsg,feito2013fast}.
 
@@
 \centering
-\includegraphics[width=3.0in]{projection}
-\caption{$Seg_1$ is the intersection between $S_2$ and $F_1$.
-$Seg_2$ is the intersection between $S_1$ and $F_2$.
-The intersection between $F_1$ and $F_2$, which is the line segment in red, is the overlap of $Seg_1$ and $Seg_2$.}
-\label{fig_projection}
-\end{figure}
-
-M\"{o}ller's algorithm computes the intersection between two triangles $F_1$ and $F_2$ in three steps, as illustrated in Fig.
-\ref{fig_projection}.
-First, an early rejection is performed by testing whether $F_1$ intersects the plane where $F_2$ lies, which is denoted as $S_2$.
-This is a necessary condition of intersection between $F_1$ and $F_2$.
-If this test is passed, then the same is performed for $F_2$ and $S_1$, where $S_1$ is the plane of $F_1$.
-Second, the intersection between $F_1$ and $S_2$, denoted as $Seg_1$, and the intersection between $F_2$ and $S_1$, denoted as $Seg_2$, are separately computed .
-At last, the intersection between $F_1$ and $F_2$ is determined by computing the overlap area of $Seg_1$ and $Seg_2$ .
-
-\begin{figure}[t]
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=3.0in]{nonrobust}\\
-  \caption{The left edges of A and B (\emph{left}) are nearly but not exactly collinear.
-However, under usual float point arithmetic, they might be judged as collinear causing discontinuous edges in the final result (\emph{right}).}\label{fig:precision}
-\end{figure}
-
-Conventional implementations of M\"{o}ller's algorithm use vertex-based representation and usual float point arithmetic.
-However, this is neither exact nor robust.
-In Fig.
-\ref{fig:precision}, we illustrate a non-robust 2D case of the Boolean operation.
-Although implementing M\"{o}ller's algorithm with arbitrary precision arithmetic could make it robust, it is too costly for a large CSG evaluation.
-Actually, the non-robustness of this algorithm is from \emph{constructions} \cite{bernstein2009fast}, which compute new coordinates of geometry objects based on the known coordinates of existing ones.
-In M\"{o}ller's algorithm, the coordinates of $Seg_1$ and $Seg_2$ (Fig.
-\ref{fig_projection}) are computed as intermediate results.
-On the other hand, if the computation can be restricted to \emph{predicates}, which make a two or three-way decision based on known coordinates, we could quickly and robustly implement this algorithm.
-
-Fortunately, according to Sugihara and Iri \cite{sugihara1990solid}, geometry computation of Boolean operations can be restricted to predicates using plane-based representation of polyhedra.
-This motivated us to integrate plane-based representation into M\"{o}ller's algorithm.
-Exact and efficient predicate computation is performed using precise geometry predicate techniques \cite{shewchuk1997adaptive}.
-Details of our implementation are shown below.
-
-\begin{figure}
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=1.7in]{p-reps}\\
-  \caption{Plane-based representation of triangles. The yellow triangle is represented by three bounding planes (green) and the supporting plane where the triangle lies.}\label{fig:p-reps}
-\end{figure}
-
-We first convert $F_1$ and $F_2$ into their respective plane-based representations: a supporting plane surrounded by three bounding planes (Fig.
-\ref{fig:p-reps}).
-We implement this conversion using the exact conversion method by Campen and Kobbelt \cite{campen2010exact}.
-Then, in our implementation, the relative position of a point and a plane can be determined by computing the sign of the multiplication of determinants \cite{sugihara1990solid}.
-To avoid introducing errors, we represent the end points of $Seg_1$ and $Seg_2$  by intersections of plane triples, rather than by directly computing their coordinates.
-As illustrated in Fig.
-\ref{fig:isect}(a), these points are the intersection between an edge line of a face and the supporting plane of the other face.
-Because the edge line of $F_1$ can be represented as $[S_1, S_X]$ (or $[S_2, S_X]$ for an edge line of $F_2$), where $S_X$ is the corresponding bounding plane of the edge, the end points of $Seg_1$ or $Seg_2$ can be represented in the form of $[S_1,S_2,S_X]$.
-In Fig.
-\ref{fig:isect}, we list all intersection situations between a triangle and a plane, and the $S_X$  in each situation.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=3.5in]{sign}
-\caption{We denote the signed distance from point $X$ to plane $S_2$ as $d_X$.
-All the four conditions of intersection between $F_1$ and $S_2$ (denoted as $Seg_1$) are:  (a) $d_A\cdot d_C<0$, $d_B\cdot d_C<0$; (b) $d_A=0$, $d_B=0$, $d_C\neq 0$; (c) $d_A=0$, $d_B\cdot d_C<0$; (d) $d_A=0$, $d_B\cdot d_C>0$.
-End points of $Seg_1$ are intersections between $S_2$ and related edge lines of $F_1$ (bold edges).}
-\label{fig:isect}
-\end{figure}
-
-The intersection between $F_1$ and $F_2$ is the overlap area of $Seg_1$ and $Seg_2$.
-It can be easily computed by comparing the end points of $Seg_1$ and $Seg_2$ along $L$ (Fig.
-\ref{fig_projection}), where $L$ is the intersection between $S_1$ and $S_2$.
-Unlike M\"{o}ller's implementation, our approach uses no projection, which requires the exact point coordinates.
-We call the direction of vector $\vec{N}_1\times \vec{N}_2$ the positive direction, where $\vec{N}_1$ and $\vec{N}_2$ are normals of $S_1$ and $S_2$ respectively.
-Given two points $A$ and $B$ on $L$,  we compute the sign of the multiplication of determinants:
+\includegraphics[width=2.2in]{boolean-01}
+\caption{In the 2D view, face $\bm{s}$ (the red line segment) from mesh $M_2$ is on the surface of mesh $M_1$.
+However, because we use face barycenter $\bm{v}_{c(\bm{s})}$ to compute the indicator, whose coordinates contains round-off error, the point could  move to $\bm{v'}_{c(\bm{s})}$.
+Then we might falsely classify $\bm{s}$ as outside of $M_1$.}
+\label{fig:falseclass}
+\end{figure}
+
+Face classification also suffers from numerical errors.
+Many methods classify face according to the indicators of its barycenter using point-in-polyhedron test \cite{feito2013fast,campen2010exact}.
+However, coordinates of barycenters cannot be exactly represented and could generate false classification (illustrated in Fig.
+\ref{fig:falseclass}).
+What makes the problem worse is that for the large amount of faces and input meshes, many methods \cite{pavic2010hybrid,feito2013fast,ogayar2015deferred,zhou2016mesh} take the benefits of the local coherence of indicators, classifying neighboring faces together .
+Despite of the performance improvement, it can propagate false classification to neighboring faces and lead to wide-range failure.
+
+\subsection{Plane-based Geometry}
+
+\begin{wrapfigure}{r}[0in]{0in}
+\includegraphics[width=1.5 in]{p-reps}
+%\caption{Plane-based representation of triangle}
+\end{wrapfigure}
+
+In our method, we avoid numerical errors by embeding P-reps into conventional B-rep-based boolean algorithms and substituting constructions under B-reps with predicates under P-reps.
+Using P-reps, each face $\bm{s}$ with $n$ edges is represented by a supporting plane $\bm{p}_{s,sp}$, where the face lies, and a list bounding planes $\{\bm{p}_{s,b}^i \ \vert\  i = 0, 1,...,n-1\}$.
+Each edge line $\bm{e}_{\bm{s}}^i$ is represented by intersection $\bm{p}_{s,sp} \cap \bm{p}_{s,b}^i$.
+Corner vertex $\bm{v}_s^i$ is represented by $\bm{p}_{s,sp} \cap \bm{p}_{s,b}^i \cap \bm{p}_{s,b}^{{(i+1)}\bmod{n}}$.
+We use Campen et al.'s method \cite{campen2010exact} for exact conversion of triangles to their P-reps.
+All geometry predicates are computed using filtering techniques proposed by Shewchuk \cite{shewchuk1997adaptive} for both exactness and efficiency.
+
+Other commonly used notations in this paper are presented here.
+%A plane $\bm{p}$ can be represented by four scalar coefficients $a(\bm{p}), b(\bm{p}), c(\bm{p}), d(\bm{p})$.
+The normal of a plane $\bm{p}$ is denoted as $\bm{n}(\bm{p})$.
+A line $\bm{l}$ can be represented by intersection of two planes $(\bm{p}_l^0 \cap \bm{p}_l^1)$, or in short, $\bm{l}\colon(\bm{p}_l^0 \cap \bm{p}_l^1)$.
+The positive direction of the line $\bm{l}$ is defined by $\bm{n}(\bm{p}_l^0) \times \bm{n}(\bm{p}_l^1)$.
+A point $\bm{v}$ can be represented by non-trivial plane triples $(\bm{p}_v^0 \cap \bm{p}_v^1 \cap \bm{p}_v^2)$, or in short, $\bm{v}\colon(\bm{p}_v^0 \cap \bm{p}_v^1 \cap \bm{p}_v^2)$.
+
+\iffalse
+Given that the input vertex coordinate has $L$-bit precision including sign, the precisions of the four plane coefficients are $L_a, L_b, L_c, L_d$, which have to satisfy the following requirements:
 \begin{equation}
-\label{eq:sign}
-  K(A, B)=
-  \left|
-  \begin{array}{c}   %该矩阵一共3列，每一列都居中放置
-  \vec{S}_1 \\ \vec{S}_2 \\ \vec{S}_A \\ \vec{S}_B
-  \end{array}
-  \right|
-  \left|                 %左括号
-  \begin{array}{c}   %该矩阵一共3列，每一列都居中放置
-  \vec{N}_1 \\\vec{N}_2 \\\vec{N}_A
-  \end{array}
-  \right|
-  \left|                 %左括号
-  \begin{array}{c}   %该矩阵一共3列，每一列都居中放置
-  \vec{N}_1 \\\vec{N}_2 \\\vec{N}_B
-  \end{array}
-  \right|,
-\end{equation}
-where $\vec{S}_X$ is the coefficient vector of plane equation $[a_X,b_X,c_X,d_X]$,  and $ \vec{N}_X$ is the normal vector $[a_X,b_X,c_X]$.
-If $K(A, B)$ is positive (negative), this means that $A$ lies in the positive (negative) direction of $B$.
-Otherwise, $A$ and $B$ are concident.
-
-If $F_1$ and $F_2$ are coplanar, we check whether they overlap within the common plane using the algorithm by M\"{o}ller\cite{moller1997fast}.
-The substrate of this algorithm is to verify on which side of an edge $E$ a point $V$ lies.
-We implement it using plane-based geometry by substituting $E$ with its corresponding bounding plane $S_E$ and then computing the sign of distance from $V$ to $S_E$.
-
-\subsection{Generating United Representation}
-
-{\color{red}{Mainly deal with intersection between intersection line segments.}}
-
-\section{Multi-level Flood-filling Classification}
-\label{section:floodfill}
-
-{\color{red}{Flood-filling is all about giving a seed and propagation. In this chapter, from down to top, we introduce this process and explain how it can save computation time.}}
-
-In this step, we classify faces one by one to generate the final mesh.
-The intersection information computed in the previous section is used for re-tessellation and space label computation.
-To better explain our approach, we firstly introduce the background knowledge.
-Then the framework of this step is outlined.
-Afterwards, several important techniques in this step are detailed.
-
-\subsection{Background}
-\label{sec:intuitive}
-
-We firstly introduce the space labels, which comprise the basis of face membership classification.
-The space label of face $F$ with respect to primitive $M$, denoted as $L_F(M)$, is the relative location of $F$ with respect to $M$.
-Also, we use $L(M)$ to denote the space label with respect to $M$ which does not specify a face.
-In general, space label has four conditions: completely inside (\emph{In}), completely outside (\emph{Out}), on the boundary (\emph{On}) or not available (\emph{N/A}).
-In the last condition, $F$  crosses the boundary of $M$.
-Accordingly, it does not have a uniform label.
-In addition, if the normal direction of $F$ is considered, there are two derived conditions of \emph{On}: the normal points to the outside (\emph{Same}) and those to the inside (\emph{Oppo}) of $M$.
-
-The evaluation of Boolean operations between B-reps primitives $A$ and $B$ can be converted to the problem of surface selection according to the labels \cite{kuratowski1968set}:
-\begin{equation}
-\label{eq:select}
 \begin{split}
-&A\cup^*B:\{F_A~Out~B\}\cup\{F_B~Out~A\}\cup\{F_A~Same~B\},\\
-&A\cap^*B:\{F_A~In~B\}\cup\{F_B~In~A\}\cup\{F_A~Same~B\},\\
-&A-^*B:\{F_A~Out~B\}\cup\{(F_B~In~A)'\}\cup\{F_A~Oppo~B\},
+&L_a=L_b=L_c\ge 2(K-1)+1+1,\\
+&L_d\ge(L_a-1)+(L-1)+2+1.
 \end{split}
 \end{equation}
-
-\noindent where $F_X$ is the faces of $X$, and $F'$ means $F$ with an inverted normal.
-The stars ($^*$) after the operation notations ($\cup, \cap, -$) mean that the Boolean operations are regularized.
-
-Now, consider computing $L_F(T)$, where $T$ is a CSG solid $T$ with $n$ primitives $\{M_i~| ~i = 1,2,3,...,n\}$.
-Then there are a total of $n$ space labels for $F$: \{$L_F(M_i)~|~i = 1,2,3,...,n\}$ (or in vector form $\vec{L}_F$).
-If all elements in $\vec{L}_F$ are known and none of them is \emph{N/A}, $L_F(T)$ can be easily computed by traversing the whole CSG tree from bottom to top and progressively combining the space labels of the CSG nodes according to combination rules \cite{requicha1985boolean}:
+Here $K$ is the maximum bits required to represent edge vector components in input meshes.
+If we use $M$ bits to store each plane coefficient, basically $M$ has to be greater than $L_d$.
+In our implementation, we actually use a more strong constraint $M \ge L_d+1$.
+Under this constraint, given a $L$-bit vertex $\bm{v_i}$, we can compute the orientation of plane $p_j$ with respect to $\bm{v_i}$ by the sign $\bm{n}(\bm{p_j})\cdot\bm{v_i} + d(\bm{p_j})$, which requires no more than $M$ bits.
+It allows very fast plane orientation predicates which accelerates the early rejection in our triangle-triangle intersection tests (\S \ref{section:isect}).
+
+Let $\delta = 2^{K-L-1}$ be the relative length (in max-norm) of the longest edge in the mesh (relative to the bounding box).
+If we use IEEE 754 double float point number ($M=53$) and assume $\delta \le 2^{-5.5} \approx 0.022$, the maximum input precision $L$ can reach to 20, which is enough for most application (for standard IEEE 754 single float point number, the precision is 24-bit).
+\fi
+
+\label{sec:substrates}
+Plane-based geometry predicates used in our method are mostly well-discussed in previous work \cite{bernstein2009fast,banerjee1996topologically}.
+In the following, we focus on two predicates related to sorting, which are designed for our method particularly.
+
+\vspace{0.5em}
+\noindent \textbf{Linear ordering of points}
+
+\begin{figure}
+  \centering
+  % Requires \usepackage{graphicx}
+  \includegraphics[width=3.5in]{twopointoneline}\\
+  \caption{Geometry configuration of linear ordering of points.
+Points $\bm{v}_a$ and $\bm{v}_b$ are both on line $\bm{l}_{ab}$.
+We convert this problem into the plane ordering of $\bm{p}_a$ and $\bm{p}_b$ along $\bm{l}_{ab}$.}\label{fig:twopointoneline}
+\end{figure}
+
+\noindent Given an line $\bm{l}_{ab}$ with two points $\bm{v}_a\colon(\bm{p}_a^0\cap\bm{p}_a^1\cap\bm{p}_a^2)$ and $\bm{v}_b\colon(\bm{p}_b^0\cap\bm{p}_b^1\cap\bm{p}_b^2)$ on it, we need to determine the linear order of the two points along $\bm{l}_{ab}$ (Fig.
+\ref{fig:twopointoneline}).
+To solve this problem, we choose one plane not parallel with $\bm{l}_{ab}$ from the plane representation of each point and convert this problem into linear order of planes, which can be solved by Banerjee et al.'s method \cite{banerjee1996topologically}.
+The chosen planes should have the same orientation with $\bm{l}_{ab}$ (the dot product between plane normal and $\bm{l}_{ab}$ has to be positive) and unqualified planes have to be flipped.
+
+\begin{wrapfigure}{r}[0in]{0in}
+\includegraphics[width=1.5 in]{boolean-02}
+%\caption{Plane-based representation of triangle}
+\end{wrapfigure}
+\vspace{0.5em}
+\noindent \textbf{Circular ordering of lines}~~~~
+
+\noindent During face tessellation, we need to know the which edges are neighboring (Fig.
+\ref{fig:circularorder}), that is, circular ordering of directed lines around a vertex.
+Lines can be sorted in a divide-and-conquer way based on the relative order of each pair of lines.
+Therefore, this problem is converted to that given two lines $\bm{l}_a$ and $\bm{l}_b$ in a plane $\bm{p}_0$ and their intersection point $\bm{v}_{ab}$, compute the circular order of the two lines.
+We can compute the order by the sign of $\sin{\theta_{ab}}$, where $\theta_{ab}\in(-\pi,\pi)$ is the angle from $\bm{l}_a$ to $\bm{l}_b$ under the top view of $\bm{p}_0$.
+The sign of $\sin{\theta_{ab}}$ is the same as triple product $\bm{n}(\bm{p}_0) \cdot (\bm{l}_a\times\bm{l}_b)$.
+However, explicit computing this equation is complicated because both $\bm{l}_a$ and $\bm{l}_b$ are implicitly represented by intersection of planes.
+
+We develop an easier way that requiring no explicit computation of $\bm{l}_a$ and $\bm{l}_b$.
+First, we write the P-reps of two lines as $\bm{l}_a\colon(\bm{p}_0\cap\bm{p}_a)$ and $\bm{l}_b\colon(\bm{p}_0\cap\bm{p}_b)$.
+Then we orthogonally decompose $\bm{n}(\bm{p}_a)$ and $\bm{n}(\bm{p}_b)$ along $\bm{n}(\bm{p}_0)$:
 \begin{equation}
-\label{eq:comb}
 \begin{split}
-X\cup Out\Rightarrow X, ~~&X\cap Out\Rightarrow Out, \\
-X\cap In~~\Rightarrow X, ~~&X\cup In\Rightarrow In, \\
-X \cup X \Rightarrow X, ~~&X \cap X \Rightarrow X,\\
-Same \cup Oppo\Rightarrow In, ~~&Same \cap Oppo\Rightarrow Out,
+&\bm{n}(\bm{p}_a)= \bm{n}^\parallel(\bm{p}_a) + \bm{n}^\perp(\bm{p}_a)\\
+&\bm{n}(\bm{p}_b)= \bm{n}^\parallel(\bm{p}_b) + \bm{n}^\perp(\bm{p}_b)
 \end{split}
 \end{equation}
-where $X$ is an arbitrary label value.
-Note that the combination rules for difference operation are not shown here, because the difference operation can be converted into the intersection operation using De Morgan's transformations:
+Here superscript `$\parallel$` means the projection on $\bm{p}_0$ and `$\perp$` means orthogonal to $\bm{p}_0$.
+As we know $\bm{n}^\perp(\bm{p}_a)$ and $\bm{n}^\perp(\bm{p}_b)$ are both parallel to $\bm{n}(\bm{p}_0)$, we get:
 \begin{equation}
-\label{eq:demo}
-\begin{split}
-A-B\Rightarrow A\cap B^c, ~~~~~~~&(A^c)^c\Rightarrow A,\\
-(A\cap B)^c\Rightarrow A^c\cup B^c, ~~&(A\cup B)^c\Rightarrow A^c\cap B^c,
-\end{split}
+\label{eq:circ1}
+\bm{n}(\bm{p}_0) \cdot (\bm{n}(\bm{p}_a) \times \bm{n}(\bm{p}_b)) = \bm{n}(\bm{p}_0) \cdot (\bm{n}^\parallel(\bm{p}_a) \times \bm{n}^\parallel(\bm{p}_b)).
 \end{equation}
-where $X^c$ denotes the complement of $X$. If and only if $L_F(T) = Same$, $F$ lies on the boundary of the final model and has the correct normal; accordingly, $F$ belongs to the final result.
-
-If some elements in $\vec{L}_F$ are \emph{N/A} or cannot be computed, we may be unable to compute $L_F(T)$.
-However, the CSG tree $T$ can be trimmed into a smaller one with fewer primitives to reduce the complexity of further evaluation.
-For example, assume we have a CSG with its Boolean expression $M_1\cup (M_2\cap M_3-M_4)$.
-Given the values of two labels $L(M_1)=Out$, $L(M_2)=In$, the expression can be rewritten as $Out\cup (In\cap M_3-M_4)$.
-Using the combination rules we can simplify the expression as $M_3-M_4$.
-Thus, any face that shares the same two labels $L(M_1)$ and $L(M_2)$ can be classified based on the trimmed CSG tree $M_3-M_4$, which has only two primitives.
-
-\subsection{Face Classification Framework}
-\label{sec:framework}
-
+By observation we find that the angle between $\bm{n}^\parallel(\bm{p}_a)$ and $\bm{n}^\parallel(\bm{p}_b)$ is exactly $\theta_{ab}$.
+So the sign of the right side of equation \ref{eq:circ1} is exactly the sign of $\sin{\theta_{ab}}$.
+It means we have the following nice conclusion:
+\begin{equation}
+\label{eq:circ2}
+sign(\sin{\theta_{ab}})=  sign(\bm{n}(\bm{p}_0)\cdot(\bm{n}(\bm{p}_a) \times \bm{n}(\bm{p}_b)))
+\end{equation}
+
+Since all the three vectors on the right side are already explicitly represented, we only have to evaluate the sign of an 3$\times$3 matrix and avoid complicated arbitrary precision float-point arithmetic.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=3.5in]{circularorder}
+\caption{Geometry configuration of circular ordering of lines. $\bm{l}_a\colon(\bm{p}_0 \cap \bm{p}_a)$ and $\bm{l}_b\colon(\bm{p}_0 \cap \bm{p}_b)$ are within plane $\bm{p}_0$.}
+\label{fig:circularorder}
+\end{figure}
+
+\subsection{Method Overview}
+
+There are generally three steps in our method.
+The first step is to compute intersections between each triangle face pairs.
+After that, the input meshes are tessellated into intersection-free meshes according to these intersections.
+The last step is to classify each face and generate the final result mesh.
+
+\subsubsection{Intersection computation}
+
+In this step, we only compute intersections between triangle pairs.
+The triangle-triangle intersection test is largely based on M\"{o}ller's algorithm \cite{moller1997fast} for its efficiency.
+However, conventional implementation of M\"{o}ller's algorithm using vertex-based geometry brings numerical errors.
+Therefore, we integrate P-rep into M\"{o}ller's algorithm.
+All intersection points and line segments are represented using planes to avoid explicitly computing the coordinates.
+Also, we carefully deal with degenerate cases of triangle intersections, including point intersections, edge intersections and coplanar situations.
+In addition, octree is used to speed up the whole process.
+Details are provided in \S\ref{section:isect}.
+
+\subsubsection{Deferred tessellation}
+
+Once all intersections between triangles are detected, we need to tessellate the input meshes and construct the intersection-free meshes.
+In many methods like \cite{ogayar2015deferred}, constraint Delaunay triangulation (CDT) is applied to perform tessellation.
+However, for a CSG with more than two meshes, intersections may overlap or intersect with each other, and cannot be used for constraints of CDT directly.
+In addition, as our intersections are represented by planes, implementation of CDT are complex and inefficient, as most CDT algorithms (e.g.
+\cite{chew1989constrained}, \cite{de1992line}) is not designed to handle planes and requires explicit coordinates.
+Therefore, we first perform intersection refinement to resolve intersecting intersections.
+After that, we construct a graph-like structure suitable for P-rep intersections, called \emph{tess-graph}, to guide the exact tessellation of each face.
+After all faces are tessellated, we get our intersection-free meshes.
+Details are shown in \S\ref{sec:tessellation}.
+
+\iffalse
 \begin{figure}
   \centering
-\includegraphics[width=3.5in]{multilvl}
-\caption{Illustration of multi-level face grouping framework.
-Faces are grouped into smaller groups in each level.
-The trimmed CSG tree of a specific group is obtained by trimming the tree of its parent according to common labels of this group.
-When the group is not further subdivided, faces in this group are respectively classified based on the trimmed CSG tree of this group.}
-\label{fig:hierachy}
-\end{figure}
-
-Space labels of neighboring faces are often coherent.
-That is, given two neighboring faces $F_1$ and $F_2$, $L_{F_1}(M)$ and $L_{F_2}(M)$ are often the same.
-Therefore, we can group together neighboring faces and evaluate them based on the smaller CSG tree, which is trimmed by the common labels.
-The trimmed tree contains fewer leaves, thus enabling faster computation.
-If face grouping can be efficiently performed, this strategy will greatly accelerate the process of face membership classification.
-Moreover, a multi-level grouping scheme (Fig.
-\ref{fig:hierachy}) may provide even greater capability to shared labels.
-By using such a scheme, faces are first grouped into first-level groups; then, faces of the same first-level groups are further divided into second-level groups, and so on.
-Labels are shared in each level and the original CSG tree is trimmed step by step according to common labels in each level.
-We developed this idea into a novel classification algorithm that uses a two-level grouping scheme.
-The first level is the \emph{inter-primitive} level; the second is the \emph{intra-primitive} level.
-
-Before we begin face classification, pre-computation is conducted to make the subsequent analysis easier.
-The original CSG tree is converted into a \emph{positive} tree using the method by Rossignac and Voelcker \cite{rossignac1988active}.
-`Positive' means that the CSG tree contains no difference (-) operation.
-According to Equation \ref{eq:demo}, there may be some primitives with complement notation.
-The benefit is that we are not required to consider the difference operations in the following computation.
-
-The classification starts from face grouping in the inter-primitive level.
-In this level, faces of the same primitives are simply grouped together.
-Then, we give a rough estimation of the common labels of the group.
-Suppose the group is primitive $M$.
-Its face labels with respect to primitives whose bounding boxes are totally outside of $M$'s bounding box must be $Out$ (for primitives with complement notations, $In$).
-The original CSG tree is trimmed into the first trimmed CSG tree (as short as the \emph{the first trimmed tree}) according to these common labels plus an extra label $L(M)$ whose value is obviously $Same$.
-
-After that, the inter-primitive groups are further divided into smaller intra-primitive groups.
-To explain how to perform intra-primitive grouping, we firstly introduce an essential concept---intersection primitive (IP).
-The IPs of a face $F$ is defined as the primitives that $F$ intersects, excluding the primitive to which $F$ belongs (denoted as $M$).
-Primitives (excluding $M$) that do not intersect $F$ are called non-IPs.
-The set that contains all IPs of $F$ is the IP-set of $F$.
-That set can be computed by enumerating all the primitives in the cross list and coplanar list of $F$.
-
-Now, we require that the faces of the same intra-primitive group meet two requirements: they should be connected together and have the same IP-set.
-These two requirements give these faces very good properties, as discussed in Proposition 1.
-The labels referenced in Proposition 1 are used to trim the first trimmed tree into the second trimmed CSG tree (as short as \emph{the second trimmed tree}).
-For a specific intra-primitive group, the primitives of its second trimmed tree is a subset of the common IP-set of that group.
-This is because all space labels with respect to non-IPs are shared within the intra-primitive group and all these labels are either $In$ or $Out$.
-Therefore, all non-IPs must have been trimmed from the CSG tree (to be explained in Section \ref{sec:trim}).
-
-\vspace{0.8em}
-\noindent \textbf{Proposition 1.}~~~~If a group of faces are connected together and they have the same IP-set, they must share the same labels with respect to all non-IPs.
-These labels are either \emph{In} or \emph{Out}.
-
-\vspace{0.6em}
-\noindent \textbf{Proof.}~~~~We only prove that the conclusion stands for adjacent faces, which is a special case of connected faces.
-Promoting the conclusion to the general situation is obvious.
-Assume $M$ is a non-IP and label $L(M)$ is different for the two adjacent faces $A$ and $B$ .
-Then there must be faces from $M$ between $A$ and $B$ to cause the different space labels.
-Additionally,  because $A$ and $B$ are adjacent, at least one of $A$ and $B$ intersects the faces from primitive $M$.
-This contradicts the assumption that $M$ is non-IP.
-Therefore, $L(M)$ must be the same for $A$ and $B$.
-Moreover, because $M$  is non-IP, $L(M)$ is either \emph{In} or \emph{Out}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=3.5in]{mesh}\\
-  \caption{A snapshot during flood filling (\emph{left}), and the final grouping result (\emph{right}).
-Different intra-primitive groups are distinguished by different colors.
-From the final grouping result, the whole mesh is divided into 9 intra-primitive groups.}\label{fig:mesh}
-\end{figure}
-
-\vspace{1.0em}
-Because faces of the same intra-primitive group are connected together, we can efficiently group them using a flood filling algorithm.
-When visiting a face, its space label vector is instantly computed and its classification is performed.
-Our intra-level grouping is performed as follows:
+  % Requires \usepackage{graphicx}
+  \includegraphics[width=1.7in]{sgen}\\
+  \caption{Triangle-triangle intersections made by different triangle pairs may (a) overlap or (b) intersect with each other.
+(c) Such situation introduces extra vertex which is intersection of triangles from three different meshes.}\label{fig:p-reps}
+\end{figure}
+\fi
+
+\subsubsection{Face classification}
+
+This step is to choose faces from the intersection-free meshes to generate the final mesh.
+However, literally computing the indicator vector of each face is unacceptably slow for large CSGs.
+We utilize the geometry connectivity stored in B-reps to propagate indicators in a flood-filling manner.
+In addition, many methods use barycenters of faces together with point-in-polyhedra test for face classification, which is not exact nor robust with fix-precision float-point arithmetics.
+Different from them, we classify faces based on the classification results of exactly represented vertices, including input vertices and newly introduced intersection vertices, and carefully deal with coplanar conditions to ensure topology consistency.
+Details will be shown in \S\ref{sec:classification}.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=2.5in]{projection}
+\caption{$Seg_1$ is the intersection between $\bm{p}_{t_2, sp}$ and $t_1$.
+$Seg_2$ is the intersection between $\bm{p}_{t_1, sp}$ and $t_2$.
+The intersection between $t_1$ and $t_2$, which is the line segment in yellow, is the overlap of $Seg_1$ and $Seg_2$.}
+\label{fig_projection}
+\end{figure}
+\section{Intersection Computation}
+
+\label{section:isect}
+In this step, intersections between faces are computed through triangle-triangle intersection test.
+We adopt M\"{o}ller's algorithm \cite{moller1997fast} on account of its efficiency and simplicity.
+However, a naive implementation of M\"{o}ller's algorithm can introduce numerical errors and may fail to produce correct results.
+Therefore, we integrate plane-based geometry to make it exact.
+In the following, we first introduce our space division strategy to reduce the number of intersection test.
+Then we make a quick review of M\"{o}ller's algorithm, and discuss the way to embed plane-based geometry.
+After that, we discuss how to deal with degenerate cases.
+
+\subsection{Space Division}
+\begin{wrapfigure}{r}[0in]{0in}
+\includegraphics[width=1.2in]{octreediff}
+\end{wrapfigure}
+As intersection detection is performed between each pair of faces, localization is necessary for large CSGs to reduce the number of testing pairs.
+We use the adaptive octree for this purpose.
+Our implementation is akin to the implementation in Ogayar et al.'s method \cite{ogayar2015deferred}.
+Intersection between triangle faces and octree nodes are efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}.
+Octree leaves are classified into two types: if all faces that intersect a leaf belong to the same mesh, we call it a \emph{normal cell}.
+Otherwise, it is a \emph{critical cell}, within which the following intersection computation is performed.
+
+The difference between our octree and Ogayar et al.'s is that we do not subdivide any normal cell no matter how many faces it contains.
+This is because subdividing normal cells benefits only the point-in-polyhedron test  \cite{frisken2002simple}, which seldom uses in our method.
+This simplification can save much computing time, especially when intersections between primitives are not complex and located in small regions.
+
+\subsection{M\"{o}ller's Vertex-Based Method}
+
+M\"{o}ller's algorithm computes the intersection between two triangles $t_1$ and $t_2$ in three steps as shown in Fig. \ref{fig_projection}:
 \begin{itemize}[leftmargin=0.45cm]
-\item[1)]{\textbf{First seed generation.}}~A triangle face $F_{S0}$ is randomly chosen as the first seed (e.g., the red triangle in Fig.
-\ref{fig:mesh}).
-Labels of $F_{S0}$ with respect to non-IPs are determined by using $F_{S0}$'s barycenter as the sample point, through a ray-shooting algorithm \cite{havran1999summary} and by employing our octree as a spatial search structure \cite{frisken2002simple} to speed up.
-Note that because the original CSG tree is trimmed into the first trimmed tree, we only compute labels with respect to primitives within that first trimmed tree.
-\item[2)]{\textbf{Label propagation.}}~Once there is a seed $F_S$ with $L_{F_S}$ with respect to all non-IPs, we define the intra-primitive group $G_S$ as follows.
-All faces that belong to $G_S$ should have the same IP-set as $F_S$.
-The common labels of $G_S$ are $L_{F_S}$ with respect to all non-IPs.
-The first trimmed tree is trimmed into the second trimmed tree according to these common labels.
-Breadth-first flood filling is used to find all faces that belong to $G_S$.
-When visiting a face, we first check if it has the same IP-set as the seed.
-If so, set membership classification is performed based on the second trimmed tree of $G_S$ (detailed in Section \ref{section:setmemcls}).
-Otherwise, it is pushed into a candidate list for Step 3 (e.g., the black faces in Fig.
-\ref{fig:mesh} (left)).
- \item[3)]{\textbf{Secondary seed generation.}}~When the flood filling ends, which means no more faces belong to the current face group, a new seed is picked from the candidate list (e.g., the stippled faces in Fig.
-\ref{fig:mesh}).
-Then a new group is defined by the new seed and the labels with respect to non-IPs of the new seed are computed (details in Section \ref{sec:secondseed}).
-After that, Step 2 is repeated according to the newly defined group, until that candidate list is empty, indicating all faces of $M$ are classified.
+\item[1)] An early rejection is performed by testing whether $t_1$ intersects $\bm{p}_{t_2, sp}$, the supporting plane of $t_2$. The same test is also done between $t_2$ and $\bm{p}_{t_1, sp}$.
+\item[2)]The intersection between $t_1$ and $\bm{p}_{t_2, sp}$, denoted as $Seg_1$, and the intersection between $t_2$ and $\bm{p}_{t_1, sp}$, denoted as $Seg_2$, are separately computed .
+ \item[3)]The intersection between $t_1$ and $t_2$ is determined by computing the overlap between $Seg_1$ and $Seg_2$ .
 \end{itemize}
 
-The face membership classification of the whole CSG is accomplished by performing the above process for each primitive.
-Procedure \ref{code:floodfill} shows the framework as pseudo-code.
-To avoid repetitive visits during flood filling, we use an extra flag for each face to record its visiting status.
-
-\begin{algorithm}[!ht]
-\caption{FaceClassification(PrimitiveList, PosTree)}
+The non-robustness of this algorithm is from computing the coordinates of intersection vertices, which is the end points of $Seg1$ and $Seg2$.
+Although implementation with arbitrary precision arithmetic produces exact coordinates, it is too costly for boolean operations of large CSG.
+We use plane-based geometry to solve this problem by implicitly representing intersections with planes.
+
+\subsection{Plane-Based Intersection}
+
+\label{sec:embed}
+Given a triangle face $t$, it is firstly converted to its P-rep: a supporting plane $\bm{p}_{t, sp}$ surrounded by three bounding planes $\{\bm{p}_{t, b}^i|\ i = 0,1,2\}$.
+We integrate the plane-based geometry into each of the tree steps of M\"{o}ller's algorithm as following:
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=3.5in]{sign}
+\caption{We denote the signed distance from point $v_i$ to plane $\bm{p}_{t_2, sp}$ as $d_i$.
+All the four conditions of intersection between $t_1$ and $\bm{p}_{t_2, sp}$ are:  (a) $d_0\cdot d_2<0$, $d_1\cdot d_2<0$; (b) $d_0=0$, $d_1=0$, $d_2\neq 0$; (c) $d_0=0$, $d_1\cdot d_2<0$; (d) $d_0=0$, $d_1\cdot d_2>0$.
+End points of $Seg_1$ are intersections between $\bm{p}_{t_2, sp}$ and related edges of $t_1$ (red bold lines).}
+\label{fig:isect}
+\end{figure}
+
+\begin{itemize}[leftmargin=0.45cm]
+  \item[1)] The basic subroutine of the first step is to compute the orientation of of a face with respect to vertices of the other face.
+We find that since the exact coordinates of each triangle vertices are known, we can compute the point-plane orientation using vertex-based geometry predicates.
+This allow us to perform this early rejection efficiently.
+      \vspace{0.5em}
+  \item[2)] If $t_1$ and $t_2$ are not coplanar, the end points of $Seg_1$ and $Seg_2$ can be implicitly represented by plane triples.
+Take $Seg_1$ as an example.
+$Seg_1$ is the intersection between $t_1$ and $\bm{p}_{t_2, sp}$ and the end points of $Seg_1$ are intersections between $\bm{p}_{t_2, sp}$ and edges from $t_1$ (denoted as $\bm{e}^i_{t_1}, i\in\{0,1,2\}$).
+Because $\bm{e}^i_{t_1}$ can be represented as $\bm{p}_{t_1, s}\cap \bm{p}^i_{t_1, b}$, the end points of $Seg_1$ can be represented in the form of $\bm{p}_{t_2, sp} \cap \bm{p}_{t_1, sp} \cap \bm{p}^i_{t_1, b}$.
+In Fig.
+\ref{fig:isect}, we list all possible intersecting situations between $t_1$ and $\bm{p}_{t_2, sp}$ and the corresponding $\bm{e}^i_{t_1}$.
+The coplanar situation will be discussed later in \S \ref{sec:degenerate}.
+      \vspace{0.5em}
+ \item[3)] The intersection between $t_1$ and $t_2$ is the overlap area of $Seg_1$ and $Seg_2$.
+It can be easily computed by sorting the end points of $Seg_1$ and $Seg_2$ along the line $\bm{l}\colon \bm{p}_{t_1, sp} \cap \bm{p}_{t_2, sp}$.
+Because end points are all represented using plane triples, we can use the linear order of points discussed in \S \ref{sec:substrates} to sort.
+\end{itemize}
+
+Each time an intersection is computed, two intersections are generated (one for each triangle) and the newly generated vertices are added into meshes.
+To avoid repetitive vertices in the final result, we perform vertex repetition elimination in this step, merging coincident vertices even if they come from different input meshes.
+Because we use P-reps, the comparison of vertices is exact.
+
+\subsection{Plane-Based Intersection Representation}
+\label{sec:ir}
+
+In our method, intersection on triangle $t$ is stored as $\bm{\mathcal{I}}\colon\{T, \bm{P}_{ext}, (\bm{P}_0, \bm{P}_1), \mathcal{N}\}$, which is called plane-based intersection representation (PBI-rep,  see Fig.
+\ref{fig:pbi}).
+The first component $T$ indicates which triangle $\bm{\mathcal{I}}$ lies on.
+$\bm{P}_{ext}$ indicates $\bm{\mathcal{I}}$ lies on $\bm{P}_{ext}$, which also means it lies on line $\bm{p}_{t, sp} \cap \bm{P}_{ext}$.
+The two end points of $\bm{\mathcal{I}}$ are $\bm{p}_{t, sp} \cap \bm{P}_{ext}\cap\bm{P}_0$ and $\bm{p}_{t, sp} \cap \bm{P}_{ext}\cap\bm{P}_1$.
+The last component $\mathcal{N}$ represents the neighborhood of the intersection $\bm{\mathcal{I}}$.
+It indicates $\bm{\mathcal{I}}$ is intersection of triangle $t$ with $\mathcal{N}$ from other mesh, where $\mathcal{N}$ can be either a face or a set of faces sharing the same edges.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=3in]{pbirep2}
+\caption{The geometry meaning of planes in a PBI-rep. The yellow line segment is the represented intersection.}
+\label{fig:pbi}
+\end{figure}
+
+For example, two triangle faces $t_1$ and $t_2$ from mesh $M_i$ and $M_j$ intersect.
+Then it generates two intersections--- ${\bm{\mathcal{I}}}_{12}$ on $t_1$ and ${\bm{\mathcal{I}}}_{21}$ on $t_2$.
+For ${\bm{\mathcal{I}}}_{12}$ on $t_1$, $T = t_1$ and $\bm{P}_{ext}=\bm{p}_{t_2, sp}$.
+The third component is boundary planes from $t_2$ which has already been discussed in \S\ref{sec:embed}.
+The last component is $\mathcal{N}=t_2$.
+Sometimes intersections may lie on the mesh edges instead of faces (Fig.
+\ref{fig:twin}), which is called 'edge intersection'.
+In that case, the second component of neighborhood is a set of adjacent faces.
+We postpone the discussion of edge intersection to \S\ref{sec:degenerate}.
+
+\subsection{Degenerate Case Handling}
+\label{sec:degenerate}
+
+While two triangles, if intersecting, intersect on a line segment in most situations, they can also intersect on a point or a convex area (coplanar case).
+Even if the intersection is a line segment, the intersection can be on triangle edges.
+These degenerate situations prevent us from performing robust boolean operations.
+In this section, we offer simple but effective way to deal with all these degenerations, which conceals the complexity of intersections and simplifies later processing.
+
+%The criterion of whether an intersection help tessellation is by its necessity: if the intersection is not presented, whether some faces from the linked halfedge will cross the boundary of primitives.
+The word 'cross' do not only include the situation that a face is partly outside and partly inside of a primitive, but also can mean that a face is partly inside (outside) and part on the boundary of the primitive.
+
+\iffalse
+\begin{figure}[t]
+\centering
+\includegraphics[width=3.5in]{isolated}
+%\caption{Two situations of point intersections.
+(a) $\bm{v}_{iso}$ is isolated, and there is no adjacent intersection line segment.
+We need to add the $\bm{v}_{iso}$ to triangle $t_1$.
+(b) $\bm{v}_{non-iso}$ is not isolated.
+We do not need to add $\bm{v}_{non-iso}$ into $t_1$ because it can be added by other triangle pairs which intersect on line segments.
+However, for simplicity, we add the intersection point into $t_1$ in both situations.}
+\label{fig:isolated}
+\end{figure}
+\fi
+
+\subsubsection{Point intersection}
+\label{sec:ipoint}
+If two triangles intersect on a single point (e.g., Fig.
+\ref{fig:isect}d), the intersection cannot be represented using our four-component description since the line segment collapses into a single point.
+In these cases, we simply add the intersection point into the related triangles to guarantee correct tessellation.
+No intersection is introduced.
+
+\subsubsection{Edge intersection}
+
+When intersection line segment lies on the edge of face, we call it \emph{edge intersection}.
+The space near edge intersection is divided by faces around the intersected edge (typically two faces for a manifold edge), instead of just one face.
+Therefore, the neighborhood of the related intersection is a set of faces instead of a single one.
+For example, in Fig.
+\ref{fig:twin}, the neighborhood of the intersection on $t_1$ is $\{t_2, t^*_2\}$.
+
+Another thing needs to be noticed is that there will be repetitive detection of edge intersections.
+For example, in Fig.
+\ref{fig:twin}a, the same intersection on $t_1$ will be detected twice because $t_1$ intersect both $t_2$ and $t_2^{\star}$ in exactly the same intersection.
+We solve this duplication together with other interactions among different intersections in \S\ref{sec:tessellation}.
+We also call such $t_2$ and $t_2^{\star}$ as \emph{companion triangles} in an edge intersection because they share the same edge intersection.
+This concept will be referred again in the discussion of coplanar cases.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=3.5in]{edgeisect}
+\caption{Different conditions of edge intersection.
+Triangle faces $t_1$ and $t_1^*$ are companion faces.
+Triangle faces $t_2$ and $t_2^*$ are companion faces.
+a) $t_2$ and $t_2^*$ are in different sides of $t_1$.
+b) $t_2$ and $t_2^*$ are in the same side of $t_1$.
+c) $t_2^*$ is coplanar with $t_1$.
+d) Both $t_1$ and $t_2$ have companion faces: the intersection is edge intersection for both $t_1$ and $t_2$ (instead of only for $t_2$ is previous three conditions).
+}
+%\caption{Six situations of edge interse ctions.
+The first three subgraphs are edge-face intersections.
+The last three ones are edge-edge intersections.
+(a) Triangles are located in two sides, cross condition.
+(b) Triangles are located in the same sides, invalid condition.
+(c) One of the triangles are coplanar, coplanar condition.
+(d) Double twin intersections, cross condition.
+(e) Double twin intersections, coplanar condition.
+(f) Double twin intersections, coplanar condition.}
+\label{fig:twin}
+\end{figure}
+
+\subsubsection{Copalnar}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=3.5in]{boolean-03}
+\caption{a) Coplanar cases, $t_a$ and $t_b$ intersect in 2D, dividing each other into two areas---a convex overlapping area and exclusive parts.
+b) The possible configurations of the companion faces.
+The blue triangles are from the same mesh.
+For $\mathcal{I}_1$, the companion triangle $t_1$ is coplanar with the $t-a$.
+Therefore, the overlap areas do not need to be split by the yellow edge during tessellation, thus $\mathcal{I}_1$ is invalid.
+For $\mathcal{I}_2$ and $\mathcal{I}_3$, the companion faces are not coplanar, so these intersection can be recorded during intersection test between $t_a$ and $t_1$ and $t_2$.
+In any configurations, their is no need to record the intersection between $t_a$ and $t_b$.}
+\label{fig:coplanar}
+\end{figure}
+
+Consider two triangle faces $t_1$ and $t_2$ intersect within a common plane.
+Both $t_1$ and $t_2$ will divide each other into two areas---a convex overlapping area and exclusive parts (Fig.
+\ref{fig:coplanar}a).
+Apparantly, if we tessellate both $t_1$ and $t_2$ according to the boundary of overlapping area, we can guarantee that the tessellated meshes are intersection-free.
+Many previous methods \cite{feito2013fast,zhou2016mesh} use this method to guarantee topology correctness.
+However, in our method, we do not test whether $t_1$ and $t_2$ really intersect in 2D once we find they are coplanar.
+We treat coplanar situations as they do not intersect at all.
+In this way, we simplify our method, making it more robust and fast, while doing no harm to the topology correctness.
+
+We find that each intersection line segment in 2D is part of the edges from input meshes.
+That means we can view 2D intersection as a special case of edge intersection.
+The only difference is that there can be up to three edge intersections in one 2D intersection (red and yellow line segments in Fig.
+\ref{fig:coplanar}b).
+As we have discussed, edge intersection will be detected twice.
+That means we can rely on the companion triangle faces to detect intersections.
+
+However, if the companion triangles are also coplanar, neither of the two triangles will record the intersection.
+Fortunately, in this case, the intersection is not valid.
+The word `valid` means the intersections will appear as an edge in the final mesh, thus is necessary to put into tessellation.
+Supposing the intersection $\mathcal{I}$  is on triangle $t_1$, this definition equals to:
+\begin{equation}
+% = f(\bm{\Lambda}(\bm{s}_i))
+\lambda_f(\bm{x}_i) \neq constant, \bm{x}_i \in \bm{U}(\mathcal{I}) \cup t_1
+\end{equation}
+, where $f$ is the CSG function, and $\bm{U}(\mathcal{I})$ is the the neighborhood of $\mathcal{I}$.
+This inequation indicates the two sides of $\mathcal{I}$ have different classification and must be split according to $\mathcal{I}$ during tessellation.
+However, in most time, the validation of intersection is not known until classification stage, because we have to know the indicator of each point in $\bm{U}(\mathcal{I}) \cup t_1$.
+Fortunately, if companion faces are both coplanar with $t_1$, both sides of $\mathcal{I}$ have the same indicator $on$ and thus the same classification.
+It means $\mathcal{I}$ is invalid and we do not need to record it.
+
+\section{Deferred Tessellation}
+
+\label{sec:tessellation}
+After intersection computation, tessellation is performed on each intersecting triangle face and generate our intersection-free meshes.
+We call this stage as deferred tessellation because the tessellation happens until all valid intersections are computed.
+
+Ogayar-Anguita et.
+al.
+\cite{ogayar2015deferred} use Constrained Delaunay Triangulation (CDT) to perform deferred tessellation.
+They treat triangle faces as convex triangulation zones and intersections as constraints.
+Our first try is to implement a robust plane-based CDT.
+However, CDT algorithms \cite{chew1989constrained,preparata2012computational} require coordinates projection or intersection detection between arbitrary connections of vertices within triangulation zone, which are difficult to be implemented under P-reps.
+From another perspective, CDT contains geometry constructions---new edges are generated to guarantee each subface is a triangle, which does not fit P-reps.
+Moreover, when there are more than two primitives, simply applying CDT omits the complexity of intersections between meshes.
+The intersections may intersect each other, introducing new vertices and splitting original intersection line segments (Fig.
+\ref{fig:iisect}a).
+This breaks the assumption of most CDT algorithms and may lead to incorrect output topology.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=3.5in]{boolean-04}
+\caption{a) Different colors indicate the intersections are from different meshes.
+The blue intersections and the red ones intersect at a point.
+Also, the yellow intersections overlap with the red ones.
+b) After refinement, we introduce a new vertex $a$, and merge overlapping intersections into a new one $\mathcal{I}_b$.
+c) Our tessellation does not guarantee to obtain triangles.
+d) If triangulation is performed, new edges (gray ones) are introduced and we cannot give the precise plane-based representation for these new edges.}
+\label{fig:iisect}
+\end{figure}
+
+To solve these problems, we first perform intersection refinement to eliminate any crossing or overlapping between intersections.
+After that, we perform conservative tessellation based on \emph{tess-graph}, ensuring unconditional topology correctness.
+An tess-graph is a graph-like description of intersections on a certain face.
+The word `conservative` means we .
+This is because if triangles are required, we need construct new bounding planes for these new triangles, which violating our principle of no geometry construction (Fig.
+\ref{fig:iisect}d).
+
+\subsection{Intersection Refinement}
+
+The intersection vertices are not only introduced by intersection between an edge and a triangle, but also introduced by intersections of three triangles.
+In order to find all intersection vertices, it is not enough by only triangle-triangle intersection tests.
+To make tessellation easier and more robust, we have to refine these intersections and resolve the intersections between intersections.
+
+Intersection refinement is performed in a local scope. For each intersecting face $t$ from mesh $M_t$, we collect all intersections on $t$ as set $\bm{\Gamma}(t)$
+%$\bm{\Gamma}(t)=\{\bm{\mathcal{I}}_{t}^i, i=0,1,2,...\}\cup\{\bm{\mathcal{I}}_{t}^{\bm{e}_i},i=0,1,2\}$
+and refine them together.
+For simpler processing, we also include the three edges of $t$ into $\bm{\Gamma}(t)$, since edges also participate in tessellation.
+In $\bm{\Gamma}(t)$, edges are represented as PBI.
+The neighborhood components of edges are set as $None$ because they do not have a neighborhood edge or face.
+Other PBI-rep components can be determined by the P-reps of edges.
+The refinement on $\bm{\Gamma}(t)$ is done using only plane-based geometry predicates by the following three steps:
+
+\vspace{0.5em}
+\noindent \textbf{Coincidence elimination}~~~~
+We merge coincidence intersections which have the same end points.
+Intersections are undirected so intersections with inverse end points are also coincident.
+The PBI-rep of the new intersection is inherited from either of the old one's except the neighborhood component.
+The new neighborhood is the combination of the merged ones', meaning the intersection has two (or more) neighborhoods.
+
+\begin{wrapfigure}{r}[0in]{0in}
+\includegraphics[width=1.7 in]{resolve}
+%\caption{Plane-based representation of triangle}
+\end{wrapfigure}
+\vspace{0.5em}
+\noindent \textbf{Cross and overlap resolving}~~~~
+After the process of two previous steps, there are no overlapping intersections in $\bm{\Gamma}(t)$.
+We check whether any pair of intersections cross or overlap (collinear) each other.
+The definition of \emph{cross} does not include the situation that two intersections share end points, since no splitting is required in this situation.
+When there is crossing or overlapping, at least one of the intersections have to be split.
+Because one intersection may may 'touch' more than one other intersections, the splitting is deferred until all splitting points are found.
+The subroutine linear order of points (\S\ref{sec:substrates}) is used to sort these splitting points along the splitting intersection.
+The PBI-reps of split segments inherit their father's except the third component which identifies the end points.
+
+\vspace{0.5em}
+\noindent \textbf{Coincidence elimination (again)}~~~~
+Unfortunately, the overlap resolving may bring new coincident intersections. Therefore the first step is run again in the final step.
+
+%\vspace{0.5em}
+%There is one more thing that we give intersections generated (by merging or splitting) from the PBI-reps of edges  the positive directions.
+That means all intersections lies on triangle edges have a positive direction.
+Direction is defined by the direction of edge the intersection lies on.
+
+\subsection{Tessellation by Tess-Graph}
+\label{sec:tess}
+
+So far, intersections are only independent data that store the coordinates and neighbouring information.
+To perform tessellation and extract subfaces, we need to organize them to reveal the topology.
+We use tess-graph for this purpose.
+A tess-graph is the graph description of the tessellated face topology.
+For each face to be tessellated, we construct a tess-graph according to the refined intersections.
+Nodes of tess-graph represent end points of intersections and undirectional connections between nodes represent intersections.
+The construction of tess-graph is straightforward and the reader will not have problem filling the details.
+
+After we have tess-graph, we tessellate face and extract subfaces according to it.
+This is done by extract valid loops on tess-graph.
+A valid loop that corresponds to a subface must satisfy two criterions: 1) the direction of loops should be coherent with the face normal, and 2) consecutive connections on the loop should be adjacent by circular order.
+Each valid loop corresponds to a intersection-free face.
+After we find out all valid loops on tess-graph, we finish tessellating the corresponding face.
+To facilitate the later process, we also store neighborhood information into the edges of the new faces.
+Because the edges of new faces are generated from intersections, the neighborhood information of the edges is inherent from the corresponding intersections.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=3in]{circularadj}
+\caption{\emph{Left}: we find all valid loops on tess-graph to tesselate a triangle.
+The direction of loops have to be coherent with the triangle normal (assume the normal points to the outside of paper).
+\emph{Right}: each circular adjacent edge pair is an angle of the tessellated polygon.}
+\label{fig:cadj}
+\end{figure}
+
+When all faces are tessellated, meshes are intersection-free.
+We further attach the PBI-reps of intersections to the edges generated from tess-graph connections which corresponds to an intersection.
+Finally, we get the intersection-free hybrid meshes, with some edges contains neighborhood information which indicates there are intersections between meshes.
+
+%In our implementation, we find that it is not easy to check whether the loop direction is coherent with face normal by plane-based geometry.
+
+%First, We classify connections of tess-graph into two types: connections on face boundaries as \emph{boundary connections} and connections inside face as \emph{inner connections} by the whether they have positive directions.
+In the view of halfedge, inner connections represent two opposite halfedges but boundary connections represent only one.
+We add an attribute for each connection to identify their directions, and thus we get a directed version of Tess-graph.
+A sub-face is a halfedge loop on the directed Tess-graph.
+Extracting faces are process of searching for valid loops which meet certain geometry constraints.
+After all faces are extracted, all halfedges of directed Tess-graph should be used
+
+%There two geometry constraints for valid loops.
+Second, consecutive connections on the loop should be adjacent by circular order {\color{red}{Fig.?}}.
+To meet these constraints, we sort the halfedges counter-clockwise for each nodes with more than two halfedges starting from them.
+This is implemented by using the divide-and-conquer framework of quick sort.
+During each recursion, we pick a random halfedge and split the rest into two sets according to the sign of two-line-on-plane comparison.
+To make the results of two-line-on-plane comparisons coherent, we assume that for each halfedge $h_i$, the normal directions of its plane-rep, denoted as $\vec{n}(h_i)$, meets the following criterion:
+%\begin{equation}
+%(\vec{n}(h_i) \times \vec{n}_0) \cdot \vec{l}(h_i) > 0,
+%\end{equation}
+%where $\vec{n}_0$ is the normal of the face, and $\vec{l}(h_i)$ is the direction of $h_i$.
+The plane-rep of halfedge can be inherited from the corresponding connections from the undirected Tess-graph.
+Since we {\color{red}{guarantee that each connection has a plane-rep //need insert//}}, sorting can be exactly and fast performed.
+After connections are sorted in each nodes, we can know which connections are adjacent and what is the right direction during the loop search.
+
+\section{Face Classification}
+
+\label{sec:classification}
+We traverse each face in the intersection-free meshes, and classify which one belongs to the final mesh.
+Classification is done by evaluating the indicator vector of each face.
+The basic idea of our classification method is to utilize the space coherence of face indicator vectors to reuse the classification results.
+Because we store the PBI-reps which contains neighborhood information in the edges which intersect other meshes, the search space of point-in-polyhedron test is limited to only a few faces, which makes the indicator computation very fast.
+Also, by using P-reps, our classification method can deal with any degenerate cases.
+
+The space coherence of indicator vectors means neighboring faces could share the same indicator vector, or most components of indicator vectors.
+Therefore, we start from a seed face $\bm{s}_0$ with its indicator vector $\bm{\Lambda}(\bm{s}_0)$ known, and propagate to other faces in a flood-filling manner.
+The trace of indicator propagation is:
+\begin{equation}
+\label{eq:trace}
+\bm{s}_0\to \bm{s}_1\to \bm{s}_2\to \bm{s}_3\to ...
+\end{equation}
+
+Our hybrid meshes facilitate this process by accelerating the indicator propagation.
+Given adjacent faces $\bm{s}_1$ and $\bm{s}_2$, it is straightforward to know whether $\bm{\Lambda}(\bm{s}_1)$ and $\bm{\Lambda}(\bm{s}_2)$ are different.
+The two indicator vectors are the same unless the shared edge $\bm{e}_{12}$ lies on the boundary of some other meshes, which means there is neighborhood information, say, $\bm{\mathcal{N}(\bm{e}_{12})} = \{(P_k, \mathcal{N}_k)\}$, stored on $\bm{e}_{12}$.
+The neighborhood information indicates which components of indicator vector differ between $\bm{s}_1$ and $\bm{s}_2$.
+ \iffalse
+ Namely, for a certain indicator $\lambda_k$ of $\bm{s}_1$ and $\bm{s}_2$, it always stands:
+\begin{equation}
+\label{eq:eq1}
+{\lambda_k}(\bm{s}_1) = {\lambda_k}(\bm{s}_2),\ \ \  \mbox{if }\mathcal{N}_k(\bm{\mathcal{I}}(e_{12}))= 0.
+\end{equation}
+\fi
+If there is a neighborhood $(P_k, \mathcal{N}_k) \in \bm{\mathcal{N}}(\bm{\bm{e}_{12}})$, the $k^{th}$ indicators $\lambda_k(\bm{s}_1)$ and $\lambda_k(\bm{s}_2)$ can be computed efficiently and exactly according to $\mathcal{N}_k$ (\S\ref{sec:propagation}).
+We outline our classification method in Algorithm \ref{code:floodfill}.
+
+\begin{algorithm}
+\caption{Fast Face Classification}
 \label{code:floodfill}
+\textbf{Input: } Intersection-free hybrid meshes, boolean function $f$
+
+\textbf{Output: } Classification $f(\bm{\Lambda}(\bm{s}_i))$ for all faces $\bm{s}_i$
+
 \begin{algorithmic}[1]
-    \FOR {each $M_i$ in $PrimitiveList$}
-    \STATE Get common labels $CL^1$ of $M_i$;
-    \STATE Trim $PosTree$ into $TrimTree1$ by $CL^1$;
-    \STATE Select the first seed $F_0$ from $M_i$;
-    \STATE Put $F_0$ into $CandidateList$;
-    \WHILE {$CandidateList$ is not empty}
-    	\STATE Pick a seed $F_S$;
-        \STATE Define group $G_S$, where $F_S\in G_S$;
-        \STATE Compute the common labels of $F_S$, denoted as $CL^2$;
-        \STATE Trim $TrimTree1$ into $TrimTree2$ according to $CL^2$;
-    	\STATE Put $F_S$ into $FloodFillQueue$;
-    	\WHILE {$FloodFillQueue$ is not empty}
-    		\STATE Get the next face $F_i$ from $FloodFillQueue$;
-    		\STATE Do set membership classification of $F_i$ based on $TrimTree2$;
-    		\FOR {each adjacent face $F_{Neighbor}$}
-    			\IF {$F_{Neighbor}$ belongs to $G_s$}
-    				\STATE Put $F_{Neighbor}$ into $FloodFillQueue$;
-    			\ELSE
-                    \STATE Put $F_{Neighbor}$ into $CandidateList$;
-    			\ENDIF
-    		\ENDFOR
-    	\ENDWHILE
-    \ENDWHILE
-    \ENDFOR
+\State Select a proper seed face $\bm{s}_0$
+\State Compute the seed indicator vector $\boldsymbol{\Lambda}(\bm{s}_0)$
+\State \Call{propagate} { $\bm{s}_0$ , $\boldsymbol{\Lambda}(\bm{s}_0)$}
+\State
+\Function{propagate}{ $\bm{s}$ , $\boldsymbol{\Lambda}(\bm{s})$}
+    \State Compute $f(\boldsymbol{\Lambda}(\bm{s}))$
+    \For {each neighboring face $\bm{s}_{s, i}$}
+        \If {$\bm{s}_i$ has been classified}
+            \State continue
+        \EndIf
+        \If {there are PBI-reps ${\bm{\mathcal{I}}}_k$ on $\bm{e}(\bm{s}_{s, i}, s)$}
+            \State compute $\boldsymbol{\Lambda}(\bm{s}_{s, i})$ by $\boldsymbol{\Lambda}(\bm{s})$ and ${\bm{\mathcal{I}}}_k$
+            \State \Call{propagate} { $\bm{s}_{s, i}$ , $\boldsymbol{\Lambda}(\bm{s}_{s, i})$}
+        \Else
+            \State \Call{propagate} { $\bm{s}_{s, i}$ , $\boldsymbol{\Lambda}(\bm{s})$}
+        \EndIf
+    \EndFor
+\EndFunction
 \end{algorithmic}
@@
 
-\subsection{Trimming CSG Tree}
-\label{sec:trim}
-
-Trimming a CSG (binary) tree with the $In$ or $Out$ label is relatively simple.
-According to the first two lines of Equation \ref{eq:comb}, given a primitive $M$, if $L(M)$ is $In$ ($Out$), the label of $M$'s parent node is either $In$ ($Out$) or the value of its sibling.
-In either condition, the node representing $M$ can be trimmed from the tree.
-
-However, when trimming the original tree into the first trimmed tree for a specific inter-primitive group, a special label, $Same$, exists.
-This label means that the faces of the group are on the boundary of the primitive to which they belong, which is absolutely correct.
-This label is not easy to process because we cannot determine the label of its parent node unless we know the label of its sibling.
-Unfortunately, during tree trimming, the labels we have are incomplete.
-We may have to leave the $Same$ label unprocessed and wait for further information.
-This incurs considerable computation burden to check this special condition and makes the trimming algorithm inefficient.
-To solve the problems, we developed a new representation of the CSG tree, called CSGlist, to minimize the side effect of the special $Same$ label and enable early rejection of face groups that do not belong to the final model of the CSG.
-
-Given a face group from primitive $M$, we construct the CSGlist as follows.
-We cut the original CSG tree into a set of subtrees along the \emph{critical path}, which is the path from $M$ to the root (e.g., when $M=D$, the construction of CSGlist is shown in Fig.
-\ref{fig_trim}).
-Obviously, none of the subtrees contains the primitive $M$.
-Each subtree of CSGlist is associated with `desired' label values.
-That is, if the labels with respect to all subtrees meet their corresponding desired values respectively, the labels with respect to the original CSG tree is $Same$.
-On the contrary, if the labels with respect to any subtree are not desired, the labels with respect to the whole CSG tree is not $Same$; thus the related face group should be dropped.
-The desired value of a subtree is determined based on how the subtree connects to the critical path.
-According to the face selection rules (Equation \ref{eq:select}), if the subtree connects to a Union ($\cup$) node, then the desired value is $In$; otherwise, the desired value is $Out$.
-In addition, suppose the primitive $A$ in Equation \ref{eq:select} is the left child.
-Then if the subtree is in the left child of its parent node, $Same$ is also desired.
-
-Conversion to CSGlist is performed before the first trimming.
-After that, all the labels we use for CSG tree trimming are either $In$ or $Out$.
-Both the first and the second trimmed trees are represented by CSGlists.
-The subtrees of the CSGlist can be easily trimmed (since there is only $In$ and $Out$ labels) and their desired values are used to enable early rejection.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3.0in]{csgtree}
-\caption{Convert CSG tree into a CSGlist along the critical path (marked by the arrow) from primitive $D$ to the root.
-The CSGlist contain three subtrees.
-Each subtree has its desired label value.
-Subtree 1: $Out$ or $Same$.
-Subtree 2: $In$ or $Same$.
-Subtree 3: $Out$.}
-\label{fig_trim}
-\end{figure}
-
-\subsection{Classifying a Single Face}
-\label{section:setmemcls}
-
-If a face is non-intersected, the second trimmed tree will have single value, which can be used to determine whether the face is accepted.
-However, if it is an intersected face, further processing is needed.
-
-Intersected faces usually cannot be classified as a whole.
-They have to be tessellated into smaller non-intersected triangles, each of which is classified respectively.
-Robustness and efficiency are our main consideration.
-For these purposes, we nest the exact BSP structure \cite{bernstein2009fast, campen2010exact} into the intersected faces.
-We classify intersected face $F$ as follows.
+\iffalse
+\subsection{Precise Seed Generation}
+
+Our classification method starts from computing the seed indicator vector using point-in-polyhedron test \cite{ogayar2005point}.
+Conventionally, the barycenter of the face is used for the test to compute the indicator vector of the whole face.
+This is because the whole face is classified as a whole, and every inner point will have the same indicator vector.
+However, the coordinates of the inner points cannot be exactly represented by float point numbers, which may lead to wrong predicates, especially when it is an on-boundary case.
+Therefore, we use the original vertices, whose exact coordinates are known, for point-in-polyhedron test.
+For this reason, only tessellated faces with at least one original vertex can be the seed face.
+The point-in-polyhedron test is guaranteed to be exact.
+On the other hand, efficiency is not so important as there will not be many such tests.
+If ray-trace algorithms (e.g., \cite{frisken2002simple}) are used, the octree constructed during space division can be used for acceleration \cite{havran1999summary}.
+
+However, using point on the boundary instead of an inner one has another problem.
+Given a face $\bm{s}$ (may not be triangle) and one of its vertex $v_b^i(\bm{s})$, the vertex indicator $\boldsymbol{\Lambda}(v_{i}(\bm{s}), P_k)$ may cause ambiguity to deduce the face indicator $\boldsymbol{\Lambda}(s, P_k)$.
+In {\color{red}{Fig.
+?}}, $\boldsymbol{\Lambda}(v_b^1(\bm{s}), P_k) = on$, then $\boldsymbol{\Lambda}(s, P_k)$ can be any of the four conditions.
+We solve this problem by trying other vertices in $\bm{s}$ for ambiguous indicators.
+If all vertices indicators are $on$ and the ambiguity cannot be resolved, the current face is not proper for being the seed and we select a new one instead.
+
+\fi
+
+\subsection{Indicator Propagation}
+\label{sec:propagation}
+
+Meshes consist of vertices, edges and faces.
+Classification is required to perform on the face level.
+However, polyhedron in-out test is performed based on points.
+Gaps exist between the them.
+Conventionally, face barycenter is used to compute the indicator of the whole face.
+This is because in intersection-free meshes, face is classified as a whole, and every face inner point will have the same indicator as the face's.
+However, the computation of inner point coordinates requires geometry construction, which introduces errors without exact arithmetic.
+Therefore, we use the vertices instead, whose exact representations are known, for indicator computation.
+
+\begin{wrapfigure}{r}[0in]{0in}
+\includegraphics[width=1.3 in]{propagate}
+\end{wrapfigure}
+
+%For example, given a face $\bm{s}$ and one of its vertex $v^i(\bm{s})$, if $\lambda_k(v^i(\bm{s}))=on$, $\lambda_k(\bm{s})$ can be any of $on$, $in$ or $out$ (see {\color{red}{Fig. ?}})
+However, there are two gaps between face indicator and vertex indicator.
+First, the indicator of vertex does not always equal to indicator of face.
+Second, face indicator has two conditions in $on$ case---$same$ and $oppo$, because the face has its orientation.
+
+To overcome the gaps, we discuss our indicator trace (\ref{eq:trace}) in finer granularity.
+In the beginning, we start from a seed vertex $\bm{v}_0$ on seed face $\bm{s}_0$.
+We assume indicator vector $\bm{\Lambda}(\bm{v}_0)$ is known.
+Then we use $\bm{\Lambda}(\bm{v}_0)$ to compute $\bm{\Lambda}(\bm{s}_0)$.
+In addition, we add the edge layer into the trace.
+Then it changes to:
+\begin{equation}
+\bm{v}_0\to \bm{e}_0\to \bm{s}_0\to (\bm{e}_1)\to \bm{s}_1\to (\bm{e}_2)\to \bm{s}_2\to ...
+\end{equation}
+, where $\bm{v}, \bm{e}$ means vertex and edge respectively.
+The bracket here means propagating to edge is optional because if the edge does not contain neighborhood information, the indicators on the two side are the same and we do not need to propagate to the edge.
+We find that there are three kinds of basic operations in the trace: $\bm{v}_{\bm{e}}\to \bm{e}$, $\bm{e}_{\bm{s}}\to \bm{s}$ and $\bm{s}\to \bm{e}_{\bm{s}}$, where $\bm{v}_{\bm{e}}$ means the end point of $\bm{e}$, and $\bm{e}_{\bm{s}}$ means the edge of $\bm{s}$.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=3in]{bsps}
+\caption{a) Because we cannot use inner sample point includes geometry construction, we choose the vertices (green one) instead to compute the face indicator.
+b-d): Different situations of classification.
+The simple structure of neighborhood BSP guarantees the same classification result of the points on $\bm{p}_{\bm{s}, sp}^+$.
+In \emph{a}, the BSP contains two half-planes because it is constructed from two neighborhood faces.
+In \emph{d}, the classification result is $on$ so we need to determine the orientation by the normal of half-plane $q$ and the face $p$.
+In this condition, the indicator should be $oppo$ since $p$ and $q$ are opposite.}
+\label{fig:bsps}
+\end{figure}
+
+Given the partial order $on \succ in$ and $on \succ out$, our key observation is that the following relation always stands for indicators:
+\begin{equation}
+\label{eq:porder}
+\lambda_k(\bm{v}_{\bm{e}_{\bm{s}}}) \succeq \lambda_k(\bm{e}_{\bm{s}}) \succeq \lambda_k(\bm{s})
+\end{equation}
+, where $\lambda_k(x)$ means the indicator of $x$ against a certain primitive $M_k$.
+This relation can be inferred from continuous space assumption and the definition of intersection-free mesh.
+It tells us when we perform $\bm{v}_{\bm{e}}\to \bm{e}$ and $\bm{e}_{\bm{s}}\to \bm{s}$, we decide whether the $on$ indicator changes to $in$ or $out$ or remains $on$.
+When we perform $\bm{s}\to \bm{e}_{\bm{s}}$, we decide whether $in$ and $out$ indicators change to $on$.
+In addition, considering the orientation of face, we also need to figure out whether the $on$ indicators changes to $same$ or $oppo$ during $\bm{e}_{\bm{s}}\to \bm{s}$ operation.
 
 \vspace{0.5em}
-\noindent \textbf{Valid-IPs \& Pseudo-IPs}~~~~
-IPs of an intersected face are firstly divided into two types according to whether the IPs are in the second trimmed tree.
-The IP that is the primitive of the second trimmed tree is called the valid intersection primitive (valid-IP).
-Otherwise, it is called the pseudo-intersection primitive (pseudo-IP).
-Pseudo-IPs intersect the face; however, the labels with respect to pseudo-IPs do not affect the classification of $F$.
-In other words, the intersections of pseudo-IPs are not edges of the final models, as illustrated in Fig.
-\ref{fig:invalidcross}.
-Thus, we simply omit these pseudo-intersections during classification.
-This filtering stage saves computation time by avoiding unnecessary splitting of faces.
-An extreme instance is that there is no valid-IP.
-For this condition, the face is processed in the same way as a non-intersected face.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3.2in]{invalid-cross}
-\caption{2D illustration of pseudo-intersection. The vertices in red do not appear in the final model. They are so called pseudo-intersection vertices (line segments in the 3D case).}
-\label{fig:invalidcross}
-\end{figure}
+\noindent\textbf{$\bm{s\to \bm{e}_{\bm{s}}}$}~~~~ We need to find which indicators change to $on$.
+We known when $\lambda_k(\bm{e}_{\bm{s}})=on$, there will be neighborhood information related to mesh $M_k$ stored on $\bm{e}_{\bm{s}}$.
+Therefore, in this operation, all we need is to iterate over neighborhoods of $\bm{e}_{\bm{s}}$ and change corresponding indicators to $on$.
 
 \vspace{0.5em}
-\noindent \textbf{Tessellation}~~~~
-In this step, $F$ is divided into a set of sub-triangles using the intersections recorded in Section \ref{section:isect}.
-Because constrained Delaunay triangulation (CDT) \cite{chew1989constrained} has good topology characteristics, we convert the tessellation into a problem of CDT.
-The zone of CDT is $F$, and the constraints are all the intersections by valid-IPs.
-The constraints ensure that no sub-triangles will cross these intersection lines.
-Because CDT in our method is a vertex-based 2D problem, the 3D coordinates computed by their plane-based representation are projected on a 2D space, which is the axis-aligned plane where the area of $F$ is maximized.
-
-It should be noted that intersections from different valid-IPs may intersect (Fig.
-\ref{fig:cdt}(c)).
-Omitting these intersection points may cause false results of CDT.
-To obtain the correct constraints, intersections from different valid-IPs are tested to determine whether they intersect.
-We implement this test again using plane-based geometry for robustness.
-As we know this kind of special intersection is actually the cross point of the three faces: $F$,  and the two associated intersected faces from the valid-IPs (Fig.
-\ref{fig:cdt}(d)).
-Therefore, such a point can be represented by the three supporting planes of the three faces.
-We determine whether the cross point exists by testing if the point is inside all three of these faces.
-By adopting the routine of the relative position of a point to a plane \cite{sugihara1990solid}, this test is robust and efficient.
-If the cross point of different intersection lines is detected, these lines are split by the cross point and the constrains of CDT are updated accordingly.
-Moreover, because the cross point is actually shared by the three faces, it is added to the point lists (Section \ref{sec:isecthandle}) of all three of these faces.
-
-\begin{figure}
-\centering
-\includegraphics[width=3.5in]{cdt}
-\caption{We classify the face $F$ from primitive $M$: (a) faces of $M_1$ (yellow) that intersect $F$.
-BSP of $M_1$ is constructed according to these.
-(b) Faces of $M_2$ (green) that intersect $F$.
-BSP of $M_2$ is constructed according to them.
-(c) If $M_1$ and $M_2$ are the only valid-IPs of $F$, then triangulation can be performed according to intersection lines recorded in the cross list.
-The red area shows a possible result of sub-triangle classification.
-Note that there are intersections between lines from different primitives (marked as red stars), which are (d) intersections of three faces each from different primitives.}
-\label{fig:cdt}
-\end{figure}
-
-\noindent \textbf{Classification of sub-triangles}~~~~
-An intersected face $F$ is divided by faces from each valid-IPs into $In$ cells, $Out$ cells and $On$ cells (Figs.
-\ref{fig:isect}(a) and (b)).
-The BSP tree \cite{naylor1990merging} is very suitable for describing such partitions.
-The labels of sub-triangles can be efficiently computed according to a BSP representation using the BSP-based point-in-polyhedra test \cite{gordon1991front, fuchs80visible, james1999binary}.
-Details are discussed as follows.
-
-Given a valid-IP, denoted as $M$, we firstly build a BSP tree nested within $F$ according to the intersections between $F$ and $M$.
-This is a 2D partition problem.
-Nevertheless, constructing BSP in 2D space of $F$ will introduce errors on account of the involved conversion from plane triples (plane-based representation) into 2D coordinates.
-Therefore, it is better to construct the BSP tree in 3D space.
-If we limit the space of the BSP construction zone within the face $F$ with tiny thickness, denoted as $P_F$, it is obvious that all faces from $M$ that intersect $P_F$ are recorded in the cross list and the coplanar list of $F$.
-These faces give the correct space partition on $P_F$.
-We construct the 3D BSP tree according to the intersected faces.
-The construction of the BSP tree is implemented using an exact plane-based algorithm proposed by Berstein and Fussell \cite{bernstein2009fast}.
-Now, given a sub-triangle $SF$, the label $L_{SF}(M)$ is then computed based on the classification results of the three corners of $SF$ according to the constructed BSP.
-If all three classification results are $On$, then $L_{SF}(M)$ is either $Same$ or $Oppo$.
-If any classification of the corners is not $On$, $L_{SF}(M)$  is the same as the non-$On$ classification .
-
-After all space labels of a sub-triangle are computed, we judge whether the sub-triangle belongs to the final model based on the second trimmed tree represented as CSGlist.
-The subtrees in CSGlist are evaluated using the combination rules of labels.
-The sub-triangle is accepted if and only if the evaluation results of all subtrees are desired.
-We might accelerate this step if the coplanar list of $F $is empty or the faces in the coplanar list are all from pseudo-IPs.
-In this case, the labels with respect to valid-IPs are either $In$ or $Out$, and each subtree of CSGlist can be efficiently evaluated using Blist, which was proposed by Hable and Rossignac \cite{hable2005blister}.
-For CSG models in which the coplanar cases are rare, this acceleration saves considerable computation time.
-
-\subsection{Secondary Seeds Generation}
-
-\begin{figure}
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=2.0in]{sgen}\\
-  \caption{$F_x$ is the secondary seed, and $F_c$ is its associated face.
-The labels of $F_x$ with respect to primitives that intersect $F_c$ but do not intersect $F_x$ (e.g., the yellow intersection) can be computed using any point in $E_{x,c}$ as the sample.
-The labels of $F_x$ with respect to primitives that intersect neither $F_x$ nor $F_c$ are the same for both faces.
-Line segments of different colors are intersection lines by different primitives.}\label{fig:sgen}
-\end{figure}
-
-\label{sec:secondseed}
-
-As discussed in Section \ref{sec:framework}, during flood filling, faces belonging to the group of the current seed are classified according to the second trimmed tree of this group.
-The rest are added to a candidate list for generating secondary seeds when no more faces belong to the group of the current seed.
-The main task of secondary seed generation is to compute the space labels with respect to non-IPs of the new seeds.
-
-A straightforward scheme is to use the same approach as the first seed generation in Section \ref{sec:framework}.
-However, this scheme requires  recalculating all the space labels with respect to non-IPs using the time-consuming ray-shooting method.
-For complex CSG evaluation, in which secondary seed generation is frequently requested , we need a more efficient solution.
-Again, we use the information of neighboring faces to accelerate this process.
-When a face $F_x$ is added to the candidate list, we associate the following data with $F_x$: the face $F_c$ that is currently being visited (therefore $F_x$'s neighbor; see Fig.
-\ref{fig:sgen}) and the labels of $F_c$ with respect to $F_c$'s non-IPs.
-Note that the non-IP set of $F_x$, denoted as $C_x$, is different from that of $F_c$, denoted as $C_c$.
-
-Now, if $F_x$ is selected as a new secondary seed, we can compute the labels with respect to non-IPs of $F_x$ in two complementary ways: we can directly inherit from the labels of $F_c$, or represent $F_x$ with a point within $F_c$ and compute the label of this point using the BSP technique presented in Section \ref{section:setmemcls}.
-The former is used for the computation of the labels with respect to the primitives that are in $C_c\cap C_x$.
-The labels with respect to these primitives are the same for both $F_x$ and $F_c$.
-The latter is used for computing the labels with respect to the remaining of primitives (e.g., those in $C_c\setminus C_x$).
-According to Proposition 2, the sample point of $F_x$ can be chosen as any point in the common edge of $F_x$ and $F_c$, denoted as $E_{x,c}$.
-For robustness, we use one of the end points of $E_{x,c}$ as the sample point because we have its exact plane-based representation.
-
-\vspace{+1.0em}
-\noindent \textbf{Proposition 2.}~~~~Given two adjacent faces $F_c$ and $F_x$, the labels with respect to primitive $M$ for $F_x$ is the same as the classification result of any point on the common edge of $F_x$ and $F_c$ in the BSP tree of $M$ for $F_c$ (constructed in Section \ref{section:setmemcls}), if $M$ is in the IP-set of $F_c$ but not in the IP-set of $F_x$.
-\vspace{+0.5em}
-
-\noindent \textbf{Proof.}~~~~We know $M$ is not in the IP-set of $F_x$; therefore, it is obvious that all points on $F_x$ have the same labels with respect to $M$.
-Because the points on the common edge of $F_x$ and $F_c$ are in $F_x$, they have the same labels.
-\vspace{+1.0em}
-
-\section{Experiments and Discussion}
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3.2in]{raster}
-\caption{\emph{Cube} $\cup$ \emph{Sphere1} $\cap$ \emph{Sphere2}: our method resulted in simpler mesh connectivity than the method by Campen and Kobbelt \cite{campen2010exact}.}
-\label{fig:raster}
-\end{figure}
+\noindent\textbf{$\bm{\bm{e}_{\bm{s}}\to \bm{s}}$}~~~~From eq.
+\ref{eq:porder}, we know if $\lambda_k(\bm{e}_{\bm{s}}) \neq on$, then $\lambda_k(\bm{e}_{\bm{s}})=\lambda_k(\bm{s})$.
+On the other hand, when $\lambda_k(\bm{e}_{\bm{s}}) = on$, we figure out $\lambda_k(\bm{s})$ using neighborhood information related to $M_k$.
+We know the corresponding neighborhood $\mathcal{N}_k$ and can be either a triangle face or an edge from mesh $M_k$.
+If $\mathcal{N}_k$ is a face, we can build a trivial BSP \cite{thibault1987set} using the face on the space near $\bm{e}_{\bm{s}}$.
+If $\mathcal{N}_k$ is an edge, we can still build BSP using the faces adjacent to $\bm{e}_{\bm{s}}$.
+In both cases, the BSP can be used to compute $\lambda_k(\bm{s})$ if we can sample a point from $\bm{s}$ that near $\bm{e}_{\bm{s}}$.
+Unfortunately, we cannot guarantee to find such a point with precise coordinates.
+
+We find that the BSP constructed from edge neighborhood is so simple that indicators $\lambda_k$ of all points on the half plane $\bm{p}_{\bm{s}, sp}^+$ are the same.
+Here $\bm{p}_{\bm{s}, sp}^+$ is half of the supporting plane of $\bm{s}$ that on the positive side of bounding plane $\bm{p}_{\bm{s}, b}^{\bm{e}_{\bm{s}}}$ (Fig.
+\ref{fig:bsps}).
+Since $\bm{p}_{\bm{s}, sp}^+ \cap \bm{s} \neq \varnothing$, we can compute $\lambda_k(\bm{s})$ by figuring out $\lambda_k(\bm{v}_x)$, where $\bm{v}_x \in \bm{p}_{\bm{s}, sp}^+$.
+For polygons, there is at least one vertex on $\bm{p}_{\bm{s}, sp}^+$, whose exact coordinates are known.
+Therefore that vertex is used as the $v_x$.
+Also, if we assign each BSP splitting plane a normal by the normal of triangle it contains, we can use it to decide the orientation ($same$ or $oppo$) when $\bm{v}_x$ is on a splitting plane, which means $\lambda_k(\bm{s})=on$.
+
+\vspace{0.5em}
+\begin{wrapfigure}{r}[0in]{0in}
+ \includegraphics[width=1.3 in]{vneighbor}
+\end{wrapfigure}
+\noindent\textbf{$\bm{\bm{v}_{\bm{e}}\to e}$}~~~~ While this is yet another propagation from low dimension to high dimension, there is no neighborhood information stored on vertex.
+If $\lambda_k(\bm{v}_{\bm{e}})=on$, we first check whether $\lambda_k(\bm{e}) = on$ by checking the neighborhood component of the intersection on $\bm{e}$.
+If not, we need to find where $\bm{v}_{\bm{e}}$ lies on the surface of $M_k$ and determine the neighborhood of $\bm{v}_{\bm{e}}$.
+In most cases, it is straightforward since coincident vertices among different intersection-free meshes are shared (see \S\ref{sec:esubroutine} for exception discussion).
+The neighborhood may be a vertex, an edge or a face.
+After computing the neighborhood, the same BSP-based classification method is used as in ${\bm{e}_{\bm{s}}\to \bm{s}}$ to determine the high dimension indicator $\lambda_k(\bm{e})$.
+We use the other end point of $\bm{e}$ to be the sample point for the BSP classification.
+
+\subsection{Acceleration by Caching}
+\label{sec:acc}
+If the CSG tree is large with hundreds of primitive nodes, computing $\lambda_f(\bm{s}_i)$ from $\boldsymbol{\Lambda}(\bm{s}_i)$ for every face $\bm{s}_i$ can be costly.
+Thanks to the indicator space coherence, we can save the computation time by caching the evaluation result $f(\boldsymbol{\Lambda}(\bm{s}_i))$ during flood-filling.
+
+The basic cache strategy is to cache final result, that is, the value of $\lambda_f(\bm{s}_i)$.
+We know indicator vector will not change if there is no intersections on the edge during propagation.
+That means the final classification $\lambda_f(\bm{s}_i)$ will not change, too.
+Thus, those faces sharing the same indicator vector can be classified as a whole.
+
+Also, we can perform intermediate results cache.
+We noticed that the boolean expression can be simplified if some components of $\boldsymbol{\Lambda}(\bm{s}_i)$ is fixed.
+For example, assume we have a boolean expression $f = P_1\cup (P_2\cap P_3-P_4)$.
+Given the values of two indicators $\lambda_1(\bm{s}_i)=out$, $\lambda_2(\bm{s}_i)=in$, the expression can be rewritten as $f(\lambda_1=out, \lambda_2=in)=out\cup (in\cap P_3-P_4)$.
+Using the combination rules we can simplify the expression as $f(\lambda_1=out, \lambda_2=in)=P_3-P_4$.
+This fact is important because for a large CSG, a certain primitive (denoted as $M_k$) often intersects with only a few other meshes $\Theta(P_k)= \{P_{n_1}, P_{n_2}, \cdots, P_{n_x}\}$.
+That means all the faces in $M_k$ has the same indicators $\lambda_{i}, P_{i} \notin \Theta(P_k)$.
+Therefore, we can first determine these fixed indicators and simplify the boolean function, and then use simplified one to compute the final indicator for each faces in $M_k$.
+
+\iffalse
+\subsection{Tessellating on Classification}
+We find for a CSG with many meshes, a large percentage of intersections are invalid (see \S\ref{sec:degenerate} for 'invalid').
+Tessellation according to these invalid intersections is not necessary.
+To avoid unnecessary tessellation, we can give an early prediction of which intersections are invalid by intersections information of faces, but have to embed the tessellation stage into the classification stage, which we call it 'tessellating on classification'.
+
+In most situations, a certain faces $\bm{s}$ only intersect with a few other meshes $\Theta(\bm{s})$.
+We can use the same cache strategy in \S\ref{sec:acc} to shrink the original CSG into a smaller one by the common indicators of $\{P_i\}\backslash\Theta(\bm{s})$, where $\{P_i\}$ means all the primitive meshes.
+After the shrinking, the primitive meshes of the CSG must be from $\Theta(\bm{s})$.
+If any mesh in $\Theta(\bm{s})$ does not appear in the shrinked CSG, it means the indicator of that mesh does not change the classification result, which in another word, intersections on $\bm{s}$ from that mesh are invalid and do not affect the classification of any subfaces of $\bm{s}$.
+If the shrinked CSG is trivial which does not contain any primitives, it means $\bm{s}$ does not need tessellation.
+In this way, we save the computation time, and simplify the topology of the final result mesh.
+Because we can only shrink the CSG for $\bm{s}$ when we classify it---before that the indicators of meshes from $\{P_i\}\backslash\Theta(\bm{s})$ are not known---we do not perform tessellation until we do the classification.
+
+\subsection{Implementation}
+
+\label{sec:individual}
+
+Feito et.
+al.
+\cite{feito2013fast} had noticed that intersection neighborhood can be used for fast classification of faces around that intersection.
+According to their method, faces adjacent to intersection have neighbors from other primitive(\bm{s}) that define the position and orientation for each other, by which the indicators are determined.
+However, Feito et.
+al.
+did not give detail description of how to implement an exact and robust classification.
+Their implementation of using vertex coordinates might misclassify faces by numeric errors and fail in degenerate cases.
+Because geometry connectivity is used, local misclassification can be spread to the neighborhoods, leading to errors in wide ranges.
+
+We develop an classification method that is unconditionally robust and exact based on the idea of using intersection neighborhood information.
+The neighborhood information is stored in the context component of I-reps during previous stages .
+In the following, we discuss the conditions that the face to be classified is a triangle.
+If the face is not a triangle, we select a triangle slice of the face instead, as the whole face is guaranteed to be classified together.
+Note that the chosen slice should contain the edge where the I-reps lie, by which we compute the new indicators.
+
+Given a face $t_i$ to be classified and an I-rep $\boldsymbol\Gamma$ of intersection on one of $t_i$'s edge, we denote the three corners it as $\bm{v}_{b*}^{0}(t_i), \bm{v}_{b*}^{1}(t_i), \bm{v}_b^2(t_i),$ where the subscript $*$ means the vertices are on the edge where $\boldsymbol\Gamma$ lies.
+We also denote the context component of $\boldsymbol\Gamma$ as $C_{P_h \backslash P_j}$, meaning $t_i$ is from primitive $M_j$ and intersects primitive $M_h$.
+From previous discussion (section \ref{sec:ir}){\color{red}{may be more than one}}, we know there are two types of intersection context---face neighborhood and edge neighborhood.
+In both conditions, the one or two faces involving in the context split the space into two in and out space by its (their) orientation(\bm{s}).
+We will see that under such division (denoted as $\boldsymbol{D}(C_{P_h \backslash P_j})$), we can compute $\lambda(t_i, P_j)$ exactly.
+
+Since the faces involving in $C_{P_h \backslash P_j}$ is part of primitive $M_j$, the space division $\boldsymbol{D}(C_{P_h \backslash P_j})$ is homogeneous with the space division by $M_j$ in neighborhood of $\bm{\mathcal{I}}$.
+The basic idea is to choose one point $\bm{v}_x(t_i)$ on $t_i$ close enough to $\bm{\mathcal{I}}$ to compute $\lambda(\bm{v}_x(t_i), P_j)$, and then compute $\lambda(t_i, P_j)$ accordingly.
+However, the problem is that we cannot find such a $\bm{v}_x(t_i)$ that can be represented exactly, which means robust classification cannot be performed.
+Fortunately, we observe that we can choose $\bm{v}_b^2(t_i)$, which is not so close to $\bm{\mathcal{I}}$ instead.
+To illustrate, assume there is another point $\bm{v}_{x'}(t_i)$ inside of $t_i$ that is very close to $\bm{v}_b^2(t_i)$ ({\color{red}{Fig.
+x}}).
+Because all inner points of $t_i$ have the same indicator, $\lambda(\bm{v}_x(t_i), P_j) = \lambda(\bm{v}_{x'}(t_i), P_j)$.
+On the other hand, we find that $\lambda(\bm{v}_{x'}(t_i), P_j)$ and $\lambda(\bm{v}_b^2(t_i), P_j)$ are always equal under division $\boldsymbol{D}(C_{P_h \backslash P_j})$ ({\color{red}{see Appendix \ref{app:profind}}}).
+Therefore, $\lambda(\bm{v}_b^2(t_i), P_j)$ is equal to $\lambda(\bm{v}_x(t_i), P_j)$ under $\boldsymbol{D}(C_{P_h \backslash P_j})$, and are coherent with $\lambda(t_i, P_j)$ under the division of whole primitive $M_j$.
+One additional thing is that when $\lambda(\bm{v}_2(t_i), P_j)=on$, then $\lambda(t_i, P_j)$ can be either $same$ or $oppo$.
+The normal orientation test have to be performed to eliminate such ambiguity.
+
+\fi
+
+\section{Results and Discussion}
 
@@
 \centering
-\includegraphics[width=3.5in]{budda}
-\caption{Boolean operations on model \emph{Budda}: (a) two \emph{Buddas}, (b) results of \emph{Budda} $\cap$ \emph{Budda}, and (c) the incorrect result of \emph{Budda} $\cap$ \emph{Budda} generated by non-robust implementation of Feito et al.'s method \cite{feito2013fast}.}
-\label{fig:budda}
-\end{figure}
-
-\begin{figure*}[!t]
-\centering
-\includegraphics[width=7in]{models2}
-\caption{(a) Boolean operations between a \emph{Ring} and a set of \emph{Spheres}.
-$\langle 1\rangle$ after 200 operations.
-$\langle 2\rangle$ after 800 operations.
-(b) Union of \emph{Armadillo} and six \emph{Spoons}.
-(c) \emph{Head} - \emph{Cuboid} + \emph{LeftBrain} + \emph{RightBrain}.
-(d) Difference a \emph{BigCylinder} and 28 \emph{SmallCylinders}.
-(e) \emph{Man} $\cup$ \emph{Horse}.
-(f) \emph{Dragon} - \emph{Bunny}.
-(g) \emph{Palate} $\cup$ \emph{Mandible} $\cup$ (20 \emph{Teeth}).}
-\label{fig:models}
-\end{figure*}
+\includegraphics[width=3in]{perturb}
+\caption{Even after perturbation, the self-union of \emph{bunny} under QuickCSG still suffers from topology problem. The green faces are boundary faces which indicating topology deficiencies.}
+\label{fig:boundaryedge}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=3in]{buddalion}
+\caption{ Different results from $Budda\cup Lion$: a) incorrect result by CGAL, b) incorrect result by Cork, and c) correct result by our method. }
+\label{fig:buddalion}
+\end{figure}
+
+We implemented the proposed method in C++ and tested a series of models on a laptop with Intel Core i5 1.5GHz CPU and 8GB RAM.
+To prove both the efficiency and robustness, we perform boolean evaluation on various CSGs with different complexity.To show our advantage, we also compared our method with several previous works with available implementations, including CGAL \cite{cgal:hk-bonp3-15a}, Maya \cite{Maya2015,barki2015exact},"Cork" \cite{Cork}, "QuickCSG" \cite{douze2015quickcsg}, "Carve" \cite{Carve}, and online service of Campen and Kobbelt's plane-based method \cite{campen2010exact,WebBSP}.
+
+\subsection{Robustness}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=3in]{dual}
+\caption{a) We cannot easily figure out the correct orientation of the loop.
+b) When there are more than one connected component, we use auxiliary intersection (red line) to connect the two component.
+}
+\label{fig:dual}
+\end{figure}
 
 \begin{table*}[ht]
-\caption{Computation Time Statistics (Seconds)}
+\caption{Computation Time Statistics of Binary Boolean Operation (Seconds)}
 \label{tab:performance}
 \centering
-\begin{tabular}{*{13}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
+\begin{tabular}{*{9}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
 \hline
-\multirow{2}{*}{No.} & \multirow{2}{*}{Figure} & \multicolumn{3}{c|}{Face Num.$^\nabla$} & \multirow{2}{*}{\tabincell{c}{Primitive\\Num.}} & \multirow{2}{*}{\tabincell{c}{CGAL \\ \cite{cgal:hk-bonp3-15a}}} & \multirow{2}{*}{\tabincell{c}{Maya \\ \cite{Maya2015}}} & \multirow{2}{*}{\tabincell{c}{Campen \\ \cite{campen2010exact}}} & \multirow{2}{*}{\tabincell{c}{Feito \\ \cite{feito2013fast}}}& \multicolumn{4}{c}{Our Approach}\\
-\cline{3-5} \cline{11-14}
- & & Total & Min & Max &&&&&& Total$^\circ$ & Step 1 & Step 2 & Step 3\\
-\hline \hline
-1 & \ref{fig:models}(a) & 37.6K & 180 & 1.6K & 201 & 1350 & 49.9 & TLE$^{\dag}$ & 15.9 & \textbf{3.13}  & 0.328 & 1.69 & 0.922 \\
-2 & \ref{fig:models}(a) & 146K & 180 & 1.6K & 801  & TLE & 1400 & TLE & Fail* & \textbf{12.8}  & 1.36 & 6.41 & 4.00 \\
-3 & \ref{fig:models}(b) & 377K & 2.56K & 346K & 7 & TLE & 224.5 & 45.7 & 11.7 & \textbf{1.44} & 0.438 & 0.062 & 0.563 \\
-4 & \ref{fig:models}(c) & 79.2K & 12 & 38.2K & 4  & 97.6 & Fail & 3.58 & 1.69 & \textbf{0.563}  & 0.187 & 0.141 & 0.172 \\
-5 & \ref{fig:models}(d) & 36K & 800 & 2.4K & 29 & 34.1 & 7.03 & 18.7 & 4.05 & \textbf{0.313} & 0.094 & 0.094 & 0.081 \\
-6 & \ref{fig:models}(e) & 597K & 96.9K & 500K & 2 & TLE & 38.3 & 26.4 & 5.63 & \textbf{2.13} & 0.563 & 0.031 & 0.984 \\
-7 & \ref{fig:models}(f) & 170K & 69.7K & 100K & 2  & 218 & 7.45 & 13.8 & 2.39 & \textbf{0.891} & 0.328 & 0.125 & 0.266 \\
-8 & \ref{fig:models}(g) & 362K & 6.91K & 276K & 22 & TLE & 344 & 256 & 19.2 & \textbf{1.80} & 0.766 & 0.172 & 0.593 \\
-9 & \ref{fig:budda} & 2.16M & 1.08M & 1.08M & 2 & Fail & Fail & MLE$^\bullet$ & Fail & \textbf{11.3} & 5.55 & 1.36 & 3.01 \\
+{No.} & {Model} & {Triangle Num. 1} & {Triangle Num. 2} &
+CGAL & Maya & Cork & Carve & QuickCSG & Our Method
+\\
+\hline\hline
+1 & Budda $\cup$ Lion & 1.08M & 400k & - & - & - & - & 3.44 & 6.88\\
+2 & Dragon $\cup$ Bunny & 100k & 70k & - & - & - & - & 0.613 &1.70 \\
+3 & Armadillo $\cup$ Armadillo2 & 150k & 150k & 487 & 15.4 & 7.00 & 189 & 0.746 & 1.62\\
+4 & Horse $\cup$ Corpse & 145k & 499k & - & 38.6 & 12.6 & 1.52k & 0.630 & 1.00 \\
+5 & Budda $\cup$ Budda2 & 1.08M & 1.08M & - & - & - & - & 4.84 & -\\
 \hline
@@
 \begin{flushleft}
-$^{\nabla}$~~\emph{Min} (\emph{Max}) means the minimum (maximum) number of faces of a single primitive.
-
-$^{\circ}$~~The total computation time of our method includes the construction of half-edge structure and the three steps in Section \ref{sec:overview}.
-
-* ~~\emph{Fail} means nothing was returned, or we received the wrong evaluation results from the programs.
-
-$^{\dag}$~~\emph{TLE} means the processing time was more than  2,000 s.
-
-$^\bullet$~~\emph{MLE} denotes that the program was out of memory. The memory limit for our implementation of Campen et al.'s approach was around 1.2GB.
 
@@
 
-\begin{table}
-\caption{Number of Primitives and Computation Time (Seconds)}
-\label{tab:linear}
-\centering
-\begin{tabular}{*{4}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
+\begin{table*}[ht]
+\caption{Computation Time Statistics of Large CSG Evaluation (Seconds)}
+\label{tab:performance2}
+\centering
+\begin{tabular}{*{9}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
 \hline
-Number of Spheres & ~~100~~ & ~~200~~ & ~~300~~ & ~~400~~ \\
-\hline
-\hline
-Our Approach & \textbf{1.38} & \textbf{2.89} & \textbf{4.39 }& \textbf{5.97} \\
-Maya \cite{Maya2015} & 17.4 & 53.4 & 124 & 241 \\
-CGAL \cite{cgal:hk-bonp3-15a} & 439 & 1350 & - & -\\
-Feito \cite{feito2013fast} & 5.20 & 15.9 & 30.4 & -\\
-\hline
-\hline
-Number of Spheres  & 500 & 600 & 700 & 800 \\
-\hline
-\hline
-Our Approach & \textbf{7.90} & \textbf{9.49} & \textbf{11.0} & \textbf{12.8}\\
-Maya \cite{Maya2015} & 407 & 628 & 966 & 1400\\
-CGAL \cite{cgal:hk-bonp3-15a}& - & - & - & -\\
-Feito \cite{feito2013fast}& - & - & - & -\\
-\hline
-\end{tabular}
-\begin{flushleft}
-*~~This table was the computation time of the evaluation for Fig. \ref{fig:models} (a).
-\end{flushleft}
-\end{table}
-
-\iffalse
-\begin{table}
-\caption{Relations between Number of Operations and Computation Time (Millie Second)}
-\label{tab:subdivide}
-\centering
-\begin{tabular}{*{4}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
-\hline
-~~Face Number~~ & Step 1 & Step 2 & Step 3 & ~Total~ \\
-\hline
-\hline
-~~1.7K~~ & 6 & 12 & 15 & 37\\
-~~16K~~ & 50 & 37 & 51 & 153\\
-~~140K~~ & 302 & 121 & 249 & 790\\
-~~1300K~~ & 2006 & 372& 1508 & 4902\\
+{No.} & {Model} & {Triangle Num.} & {Primitive Num.} &
+CGAL & Maya & Cork & Carve & QuickCSG & Our Method
+\\
+\hline\hline
+1 & Sprocket & 11k & 52 & 211 & ? & - & 4.26 & 0.132 & 0.804\\
+2 & Ring \& Ball & 146k & 801 & - & ? & - & 187 & - & 62.6\\
+3 & T1 & 80k & 50 & 1.00k & ? & 18.5 & 10.4 & 0.388 & 20.2\\
+4 & T2 & 7k & 50 & 2.81k & ? & - & 16.0 & 0.804 & -\\
+5 & H & 33k & 42 & - & ? & - & - & 2.22 & -\\
+6 & Organic & 219k & 6 & - & ? & 14.3 & 63.1 & 0.580 & 2.75\\
+%7 & 6 Budda & - & 43 & - & - & - & - & - & -\\
+%8 & Serpent & - & 5 & - & - & - & - & - & -\\
 \hline
@@
 \end{flushleft}
-\end{table}
-\fi
-
-We implemented the proposed method in C++ and tested a series of examples with numerous primitives and/or faces on a consumer laptop with an Intel i5-4200D processor at 1.5GHz and with 8 GB of RAM.
-The OpenMesh library \cite{OpenMesh} is used for storing triangle meshes and supporting the query of neighboring faces.
-Tessellation of critical triangles is performed by constrained Delaunay triangulation using the Fade2D library \cite{Fade2D}.
-
-We compared four state-of-the-art Boolean evaluation techniques, including CGAL \cite{cgal:hk-bonp3-15a}, Maya 2015 \cite{Maya2015}, the method proposed by Campen and Kobbelt \cite{campen2010exact}, and the approach proposed by Feito et al.
-\cite{feito2013fast}.
-The latter two methods used localized schemes.
-Table \ref{tab:performance} shows the comparison in terms of computing time.
-It can be easily to seen that our approach was efficient in all these examples.
-Feito et al.'s method had performance relatively similar to ours for the examples with a  single Boolean operation (Examples 6, 7).
-This is because both the approaches use a face-based grouping scheme to accelerate face membership classification; thus have similar pipelines for single Boolean operations.
-However, when the number of primitives grows, the advantage of our non-incremental CSG evaluation approach becomes more obvious.
-In the examples of more than two primitives, our method is much faster than any other methods.
-In particular, our method worked out example 2 which consisted of 801 primitives, in 15 s, which was more than 100 times faster than the Boolean evaluation in Maya.
-
-Among the three main steps of our approach, the first step of the octree construction is a typical $O(n~log~n)$ algorithm, where $n$ is the total number of faces in the CSG.
-The second step of intersection computation is only performed within critical octree cells.
-The number of critical cells is often linear to the number of intersected faces $k$ (often an $O(\sqrt{n})$ number) in the CSG.
-Therefore, the computation complexity of the second step is almost $O(k)$.
-The condition of the third step of face membership classification is more complex.
-Although the flood filling algorithm used for intra-primitive grouping is $O(n)$ complex, classifying an intersected faces could consume much more time than classifying a non-intersected faces.
-Therefore, if we assume classifying an intersected faces spends $\theta$ times of computation time to classify a non-intersected face, we may generalize the time complexity of this step as $O(n+\theta\cdot k)$.
-When $k/n$ is constant, the third step is $O(n)$ complex.
-
-To further validate that our approach is efficient for non-incremental CSG evaluation, we analyzed how the computation time changes with respect to the number of primitives.
-Table \ref{tab:linear} shows the evaluation time for Fig.
-\ref{fig:models} (a), which was a CSG consisting of a ring and hundreds of identical spheres.
-We changed the number of spheres from 100 to 800 and recorded the evaluation times.
-In this condition, the $k/n$ was relatively constant, and as there are many intersected faces, the bottleneck lies in Step 2 and Step 3.
-The result shows that the computation time of our algorithm had a linear behavior, which conforms to our previous discussion.
-The computation time of other incremental approaches rapidly increased when the number of primitives increased, sometimes showing an $O(n^2)$ behavior.
-This is because for those approaches, as more spheres were added to or subtracted from the ring, the mesh of the ring became more complex, which made it more difficult to perform subsequent Boolean operations.
-
-One possible problem of a non-incremental CSG evaluation approach is memory inefficiency.
-Unlike incremental ones, non-incremental approaches (including ours) often require loading all the primitives into the memory before the evaluation.
-Fortunately, our approach does not significantly suffer from such a problem.
-Our implementation only constructs an octree, which needs typically an $O(n~log~n)$ size data structure, and some auxiliary information of intersected faces, which is usually $O(k)$ size.
-According to our experiment, our approach performed full evaluations in Table \ref{tab:performance} with less than 600MB.
-On the contrary, some incremental approaches can be very memory inefficient.
-For instance, in the evaluation of Example 6, CGAL consumed more than 6 GB of memory.
-Furthermore, in the evaluation of Example 2, which contained only 146 K faces, Maya 2015 used at least 5 GB of memory.
-
-Our method is robust and could correctly evaluate all the examples in Table \ref{tab:performance}.
-On the other hand, it is evident that the commercial software Maya could not even correctly evaluate Example 4, which contained only 38.6 k faces and four primitives.
-CGAL gave warnings when evaluating Example 9 and finally terminated without offering a result.
-Our implementation of Feito et al's method gave an incorrect result for Example 9 (Fig.
-\ref{fig:budda}(c)) and a result rife with small holes for Example 2.
-
-Topology simplicity is another significant characteristic of the quality of CSG evaluation.
-As shown in Fig.
-\ref{fig:raster}, our method led to less triangles to represent the final model than Campen et al.'s method without stages for surface merging.
-A simpler topology is preferred because it is easier to process.
-In fact, we found that it was owing to such inefficient tessellation that Campen et al.'s method took so long time to evaluate Examples 1 and 2.
-After hundreds of Boolean operations, the resulting surface became so fragmented that it could take tens of seconds to perform a single Boolean operation.
-
-\noindent \textbf{Limitations \& Future work}~~~~
-The major limitation of our method is that it is not unconditionally robust.
-Because the tessellation of intersected faces is performed using vertex-based representation, the computed vertex coordinates may shift from their real location, which may lead to incorrect tessellation in theory.
-From our tests, we have not found the visible failures caused by this problem, because that the coordinate errors in most cases are small without visible incorrect tessellation,  we will investigate to integrate plane-based geometry computation into intersected face tessellation in the future work.
-
-\section{Conclusion}
-In this paper, we proposed a novel method to evaluate CSG with triangular mesh primitives.
-It is able to efficiently perform non-incremental evaluation of large CSG with massive faces.
-The key idea of our approach is to use the local coherence of face space labels to accelerate face membership classification.
-A two-level grouping framework is developed to group neighboring faces together and thus space labels can be shared within each group.
-This scheme saves much time for space label computation, which is often very time-consuming for conventional Boolean evaluation algorithms.
-Additionally, in order to be robust, plane-based geometry computation is introduced into the intersection computation step of our approach.
-Experiments have verified the proposed approach is more efficient than the state-of-the-art techniques while retaining robustness and stability.
-We will further investigate the robust tessellation in future.
+\end{table*}
+
+\begin{table*}[ht]
+\caption{Results of Self-Union Evaluation}
+\label{tab:selfunion}
+\centering
+\begin{tabular}{*{8}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
+\hline
+{No.} & {Model} & {Face Num.} &
+CGAL & Maya & Cork & Carve & QuickCSG  & Our Method
+\\
+\hline\hline
+1 & Ball & 360  & \cmark & \cmark & \xmark & \cmark & \xmark & \cmark \\
+2 & head & 2,716& \cmark & \cmark & \xmark & \cmark & \xmark  & \cmark\\
+3 & Bunny & 69,666  & \xmark & \cmark & \xmark & \cmark & \xmark  & \cmark\\
+4 & Dragon & 276,972 & \xmark & \xmark & \xmark & \xmark & \xmark  & \cmark \\
+\hline
+\end{tabular}
+\begin{flushleft}
+%~~~~~~~~~~~~~~~~~~~~~$^{*}$~~We perturb the model by 1e-6 to give QuickCSG the ability to partly solve coplanar cases.
+\end{flushleft}
+\end{table*}
+
+Our method is unconditionally robust for regular set meshes.
+Even extreme degenerate cases will not cause invalid output.
+To prove that, we tested the self-union of several models and some CSG with coplanar faces.
+Table \ref{tab:selfunion} compares the difference between input meshes and result meshes by their face number.
+We find that our method always produces correct or at least near correct results.
+The slightly deviation of our result from the original one is caused by self-intersection in the original models.
+QuickCSG and Cork failed in all cases, because they cannot deal with coplanar faces.
+By perturb one of the operant, the results of QuickCSG are visually OK.
+However, the topology of their results is messy.
+We can see hundreds of boundary faces on their results which do not exist in the original model (Fig.
+\ref{fig:boundaryedge}).
+
+\subsection{Performance}
+\vspace{0.5em}
+\noindent\textbf{Binary boolean operations}~~~~
+The most common situation of CSG evaluation is to perform boolean operations one by one, since many designers are used to modify models progressively.
+While our method can evaluate multiple boolean operations once for all, we also compared the performance of binary boolean operations to prove the efficiency.
+Table \ref{tab:performance} shows the evaluation time of different methods.
+We can clearly see our method is very fast that is only twice as slower than the fastest non-robust QuickCSG.
+Other robust methods such as Maya and CGAL are much slower because both of them use the arbitrary precision arithmetic.
+Moreover, these robust methods have very strict requirements on the inputs and fragile with topology deficiencies such as boundary edges or self-intersection.
+On the contrary, our   We also noticed that in (some) very large CSGs, most time is spent on octree construction in our method.
+It means other stages which involve plane-based geometry take only a small percentage of time, proving the efficiency of our plane-based geometry.
+
+\vspace{0.5em}
+\noindent\textbf{CSGs with large number of meshes}~~~~
+To identify the ability of evaluating large CSG, we also test some CSG with tens or hundreds of meshes.
+Maya and CGAL cannot perform multiple boolean operations, so we can only give the comparison of incremental boolean evaluation for these methods.
+We see that the computation time of robust methods like CGAL and Maya grows rapidly when the number of meshes grows.
+On the other hand, our method keeps good performance while stay robust.
+During our experiments, we noticed Maya gives the correct results in the first few boolean operations, but failed in the later ones.
+It proves a disadvantage of incremental boolean operation methods: if it cannot guarantee exactness, it will accumulate numerical errors which affects the algorithm stability.
+
+\begin{figure*}[!t]
+\centering
+\includegraphics[width=7in]{models}
+\caption{***********different models: will be replaced}
+\label{fig:models}
+\end{figure*}
+
+\subsection{Implementation}
+\label{sec:esubroutine}
+
+\vspace{0.5em}
+\noindent\textbf{Searching valid loops}~~~~ In \S\ref{sec:tess}, we claim a valid loops on tess-graph has to be correct with its orientation.
+However, since tess-graph is undirectional, it is not easy to check whether a loop orientation agrees with the face's (Fig.
+\ref{fig:dual}a).
+We observe that the graph connections lie on face edges have their unambiguous directions.
+Starting from these edges, we can guarantee that the loops have the right orientations.
+After we find a valid loop, more graph connections will have unambiguous directions because one connection can participate two valid loops at most.
+In such way, the correct orientation will propagate in a flood-filling way.
+
+\vspace{0.5em} There is another problem that the tess-graph may not be a connected graph.
+We avoid this problem by inserting auxiliary intersections into the tess-graph to make it connected.
+An auxiliary intersection links the vertex of face (denoted as $\bm{v}_i$) on the outer connected component with the vertex on the inner connected component.
+The intersection refinement has to be performed again if the auxiliary intersections cross any other intersections.
+To guarantee the auxiliary intersection has a valid PBI-rep, we require the vertex from inner connected component generated by intersection between the face and an edge (denoted as $\bm{e}_j$) from other meshes---all newly introduced vertices during triangle-triangle intersection are this type.
+In this way, we get three vertices with exact coordinates ($\bm{v}_i$ and the two end points of $\bm{e}_j$) and can construct an exact plane where the auxiliary intersection lies.
+
+\vspace{0.5em}
+\noindent\textbf{Seed indicator generation}~~~~In \S\ref{sec:propagation}, we claim that our flood-filling starts from a seed vertex $\bm{v}_0$.
+While the indicator vector of the seed $\bm{\Lambda}(\bm{v}_0)$ can be generated by point-in-polyhedron test \cite{ogayar2005point} with the octree as acceleration structure \cite{frisken2002simple}, we have simpler strategies by using vertex with known indicators as the seed.
+We choose the vertex with the max $x$-coordinate as the seed.
+In this way, $\lambda_k(\bm{v}_0)$ is either $out$ ($in$, if complement is applied on mesh) or $on$.
+The $on$ indicators are easy to determine in most time.
+Though sometimes exception occur because of multi-coplanar situation, this will not happen if we carefully choose the right vertex whose neighbor faces are not coplanar.
+
+\vspace{0.5em} The indicator vectors can propagate not only among single meshes, but can also between different meshes by the vertices and edges they share.
+Therefore in most time, we only need one single seed vertex for classification.
+However, if there are more than two connected components among meshes, we need to new seeds to propagate each component.
+The indicators of the second and later seeds can be computed by point-in-polyhedron tests.
+
+\vspace{0.5em}
+\noindent\textbf{Exporting to float-point number}~~~~
+The vertices of final mesh in our method are represented in both P-reps and plain coordinates.
+While the vertices from the input meshes have there exact coordinates, the vertices newly introduced by intersection between meshes require round-off when converting to coordinates representation.
+Though we guarantee the correct topology in the result mesh, such round-off can still cause topology deficiencies such as self-intersections.
+Here we adopt Zhou et al.'s method \cite{zhou2016mesh} to solve it iteratively.
+
+\subsection{Limitations and Future Work}
+
+We noticed that for CSGs that contains a lot of meshes within small area (e.g., Table.
+\ref{tab:performance}, \emph{T1}), the performance of our method is poor.
+This is because in such situations, our method computes many intersections that will not appear as edges in the final mesh, which leads to unnecessary tessellation.
+Optimization may be explored to avoid such problem.
+
+The input of our method is limited to regular set meshes.
+However, recent works claim that the piece-wise wind number (PWN) are more powerful to identify the inside and outside of meshes \cite{zhou2016mesh}.
+By using PWN, the input requirements can be extended to so-called PWN meshes that allow deficiencies such as self-intersection and multi-component.
+It would be interesting to extend our method to PWN method in the future.
+
+\section{Summary}
+
+In this paper, we proposed a novel method to evaluate CSG with regular set primitives.
+It is able to efficiently perform unconditionally robust non-incremental boolean operations.
+The key idea of our approach is to embed P-reps information into B-reps.
+The P-reps give us the chance to strictly follow the principle of no geometry construction to avoid numerical errors.
+And the B-reps offer fast neighborhood query to accelerate the processing.
+Experiments have verified the performance of our method is competitive with state-of-the-art non-robust methods while guarantee unconditional robustness.
 

### 2016-12-25 paper.tex
before chagne

@@
 \begin{abstract}
-  Constructive solid geometry (CSG) is widely used for computer aided design and manufacturing.
-However, boolean operations, which compute the boundary representation of CSG, have been suffered from robustness and efficiency problem for more than three decades.
+  Constructive solid geometry (CSG) is widely used in computer aided design and manufacturing.
+However, boolean operations, which compute the boundary representations of CSG, have suffered from robustness and efficiency problems for more than three decades.
 We propose a fast and exact boolean operation method which is unconditionally robust for regular set solids.
-We notice that among previous works,boolean methods using plane representations (P-reps) of meshes are easy to achieve robustness, but hard to be efficient.
-On the other hand, methods based on boundary representation (B-reps) of meshes are fast but not robust unless exact arithmetic is applied.
-Therefore, we choose to combine P-reps with B-reps, which allows us to take the advantages of both.
-Our method is globally based on B-reps for its efficiency, and P-rep geometry is applied locally to ensure robustness.
-Comparison experiments with state-of-the-art techniques show that our method is unconditionally exact and robust, while is competitively efficient as non-robust methods.
+Previously reported boolean methods using plane representations (P-reps) of meshes are robust, but inefficient.
+Conversely, methods based on boundary representations (B-reps) of meshes are fast but not robust, unless exact arithmetic is applied.
+Therefore, we choose to combine P-reps with B-reps, which allowed us to use the advantages of both.
+Our method uses B-reps globally, for efficiency, then P-rep geometry is applied locally to ensure robustness.
+Comparison experiments with state-of-the-art techniques show that our method is unconditionally exact and robust, and similarly efficient to non-robust methods.
 \end{abstract}
@@
 CSG can be converted into the widely-used boundary representation (B-rep) through boolean operations, which is an classical topic with history of over three decades.
+
+ONSTRUCTIVE solid geometry (CSG) has long been a popular modeling tool for computer-aided design and computer-aided manufacturing (CAD/CAM).
+Complex models are constructed by combining primitives using a series of regularized boolean operations \cite{requicha1977mathematical,tilove1980closure}: union, intersection, and difference.
+CSG can be converted into the widely-used boundary representation (B-rep) through boolean operations.
 
@@
 For example, in Fig.
-\ref{fig:twin}a, the same intersection on $t_1$ will be detected twice because $t_1$ intersect both $t_2$ and $t_2^{\star}$ in exactly the same intersection.
+\ref{fig:twin}a, the same intersection on $t_1$ will be detected twice because $t_1$ intersect both $t_2$ and $t_2^*$ in exactly the same intersection.
 We solve this duplication together with other interactions among different intersections in \S\ref{sec:tessellation}.
-We also call such $t_2$ and $t_2^{\star}$ as \emph{companion triangles} in an edge intersection because they share the same edge intersection.
+We also call such $t_2$ and $t_2^*$ as \emph{companion triangles} in an edge intersection because they share the same edge intersection.
 This concept will be referred again in the discussion of coplanar cases.
@@
 \includegraphics[width=3.5in]{boolean-03}
-\caption{a) Coplanar cases, $t_a$ and $t_b$ intersect in 2D, dividing each other into two areas---a convex overlapping area and exclusive parts.
+\caption{a) Coplanar cases, $t_1$ and $t_2$ intersect in 2D, dividing each other into two areas---a convex overlapping area and exclusive parts.
 b) The possible configurations of the companion faces.
 The blue triangles are from the same mesh.
-For $\mathcal{I}_1$, the companion triangle $t_1$ is coplanar with the $t-a$.
-Therefore, the overlap areas do not need to be split by the yellow edge during tessellation, thus $\mathcal{I}_1$ is invalid.
-For $\mathcal{I}_2$ and $\mathcal{I}_3$, the companion faces are not coplanar, so these intersection can be recorded during intersection test between $t_a$ and $t_1$ and $t_2$.
-In any configurations, their is no need to record the intersection between $t_a$ and $t_b$.}
+For $\mathcal{I}_a$, the companion triangle $t_a$ is coplanar with the $t_1$.
+Therefore, the overlap areas ($t_1 \cap t_a$ and $t_1 \cap t_2$) do not need to be split by the yellow edge during tessellation, thus $\mathcal{I}_a$ is invalid.
+For $\mathcal{I}_b$ and $\mathcal{I}_c$, the companion faces are not coplanar, so these intersection can be recorded during intersection test between $t_1$ and $t_a$ or $t_1$ and $t_b$.
+In any situation, there is no need to record the intersection between $t_1$ and $t_2$.}
 \label{fig:coplanar}
@@
 
-Consider two triangle faces $t_1$ and $t_2$ intersect within a common plane.
+Consider two triangle faces $t_1\in M_x$ and $t_2 \in M_y$ intersect within a common plane.
 Both $t_1$ and $t_2$ will divide each other into two areas---a convex overlapping area and exclusive parts (Fig.
@@
 The word `valid` means the intersections will appear as an edge in the final mesh, thus is necessary to put into tessellation.
-Supposing the intersection $\mathcal{I}$  is on triangle $t_1$, this definition equals to:
+Supposing the intersection $\mathcal{I}$  is on $t_1$, this definition equals to:
 \begin{equation}
 % = f(\bm{\Lambda}(\bm{s}_i))
-\lambda_f(\bm{x}_i) \neq constant, \bm{x}_i \in \bm{U}(\mathcal{I}) \cup t_1
+\lambda_f(\bm{v}_i) \neq constant, \bm{v}_i \in \bm{U}(\mathcal{I}) \cap M_x
 \end{equation}
-, where $f$ is the CSG function, and $\bm{U}(\mathcal{I})$ is the the neighborhood of $\mathcal{I}$.
-This inequation indicates the two sides of $\mathcal{I}$ have different classification and must be split according to $\mathcal{I}$ during tessellation.
-However, in most time, the validation of intersection is not known until classification stage, because we have to know the indicator of each point in $\bm{U}(\mathcal{I}) \cup t_1$.
-Fortunately, if companion faces are both coplanar with $t_1$, both sides of $\mathcal{I}$ have the same indicator $on$ and thus the same classification.
+, where $f$ is the CSG function, and $\bm{U}(\mathcal{I})$ is the the neighborhood of $\mathcal{I}$ in $\mathbb{R}^3$.
+This inequation indicates the space near $\mathcal{I}$ on mesh $M_x$ have different classification and must be split according to $\mathcal{I}$.
+However, in most time, the validation of intersection is not known until classification stage, because we have to know the indicator of each point in $ \bm{U}(\mathcal{I}) \cap M_x$.
+Fortunately, if companion face of $t_2$ is coplanar with $t_2$, both sides of $\mathcal{I}$ on $t_1$ have the same indicator $\lambda_y=on$ and thus the same $\lambda_f$.
 It means $\mathcal{I}$ is invalid and we do not need to record it.
@@
 \label{sec:tessellation}
-After intersection computation, tessellation is performed on each intersecting triangle face and generate our intersection-free meshes.
-We call this stage as deferred tessellation because the tessellation happens until all valid intersections are computed.
+After intersection computation, tessellation is performed on each intersecting triangle face to generate the intersection-free meshes.
+We call this step as deferred tessellation because the tessellation happens until all valid intersections are computed, instead of clipping triangle incrementally by each intersection.
 
@@
 However, CDT algorithms \cite{chew1989constrained,preparata2012computational} require coordinates projection or intersection detection between arbitrary connections of vertices within triangulation zone, which are difficult to be implemented under P-reps.
-From another perspective, CDT contains geometry constructions---new edges are generated to guarantee each subface is a triangle, which does not fit P-reps.
-Moreover, when there are more than two primitives, simply applying CDT omits the complexity of intersections between meshes.
-The intersections may intersect each other, introducing new vertices and splitting original intersection line segments (Fig.
+From another perspective, CDT contains geometry constructions---new edges are generated to guarantee each subface is a triangle (see Fig.
+\ref{fig:iisect}d), which is not preferred in our method.
+Moreover, when there are more than two primitives, simply applying CDT omits the complexity of intersections between meshes---the intersections may intersect each other, introducing new vertices and splitting original intersection line segments (see Fig.
 \ref{fig:iisect}a).
@@
 \caption{a) Different colors indicate the intersections are from different meshes.
-The blue intersections and the red ones intersect at a point.
-Also, the yellow intersections overlap with the red ones.
-b) After refinement, we introduce a new vertex $a$, and merge overlapping intersections into a new one $\mathcal{I}_b$.
+The yellow intersection and the red intersection intersect at a point.
+Also, the yellow intersection overlap with the green intersection.
+b) After refinement, we introduce a new vertex $\bm{v}_a$, and merge overlapping intersections into one edge $\bm{e}_b$.
 c) Our tessellation does not guarantee to obtain triangles.
-d) If triangulation is performed, new edges (gray ones) are introduced and we cannot give the precise plane-based representation for these new edges.}
+d) If triangulation is performed, new edges (red lines) are introduced and we cannot give the precise plane-based representation for these new edges.}
 \label{fig:iisect}
@@
 An tess-graph is a graph-like description of intersections on a certain face.
-The word `conservative` means we .
-This is because if triangles are required, we need construct new bounding planes for these new triangles, which violating our principle of no geometry construction (Fig.
-\ref{fig:iisect}d).
+The word `conservative` means we do not add any new edge during tessellation, which do not guarantee the subfaces are triangles.
 
@@
 
+\label{sec:refine}
 The intersection vertices are not only introduced by intersection between an edge and a triangle, but also introduced by intersections of three triangles.
 In order to find all intersection vertices, it is not enough by only triangle-triangle intersection tests.
-To make tessellation easier and more robust, we have to refine these intersections and resolve the intersections between intersections.
-
-Intersection refinement is performed in a local scope. For each intersecting face $t$ from mesh $M_t$, we collect all intersections on $t$ as set $\bm{\Gamma}(t)$
-%$\bm{\Gamma}(t)=\{\bm{\mathcal{I}}_{t}^i, i=0,1,2,...\}\cup\{\bm{\mathcal{I}}_{t}^{\bm{e}_i},i=0,1,2\}$
-and refine them together.
-For simpler processing, we also include the three edges of $t$ into $\bm{\Gamma}(t)$, since edges also participate in tessellation.
-In $\bm{\Gamma}(t)$, edges are represented as PBI.
-The neighborhood components of edges are set as $None$ because they do not have a neighborhood edge or face.
+Thus, we have to refine these triangle-triangle intersections before the real tessellation.
+
+Intersection refinement is performed in a local scope.
+For each intersecting face $t$, we collect all intersections on $t$ as a set $\bm{\Gamma}(t)$ and refine them together.
+We also include the three edges of $t$ into $\bm{\Gamma}(t)$, since edges also participate in tessellation.
+In $\bm{\Gamma}(t)$, edges are represented as PBI: the neighborhood $\mathcal{N}$ of edges are set as $N/A$ because they do not have a neighborhood.
 Other PBI-rep components can be determined by the P-reps of edges.
@@
 Intersections are undirected so intersections with inverse end points are also coincident.
-The PBI-rep of the new intersection is inherited from either of the old one's except the neighborhood component.
-The new neighborhood is the combination of the merged ones', meaning the intersection has two (or more) neighborhoods.
+The PBI-rep of the merging intersection is inherited from either of the old one's except the neighborhood component.
+The new neighborhood is the union of the merged ones', meaning the intersection has two (or more) neighborhoods.
 
@@
 \vspace{0.5em}
-\noindent \textbf{Cross and overlap resolving}~~~~
+\noindent\textbf{Cross and overlap resolving}~~~~
 After the process of two previous steps, there are no overlapping intersections in $\bm{\Gamma}(t)$.
 We check whether any pair of intersections cross or overlap (collinear) each other.
-The definition of \emph{cross} does not include the situation that two intersections share end points, since no splitting is required in this situation.
+New vertices might be introduced in this step.
+The definition of \emph{cross} does not include the situation that two intersections share one end point, since no splitting is required in this situation.
 When there is crossing or overlapping, at least one of the intersections have to be split.
@@
 The subroutine linear order of points (\S\ref{sec:substrates}) is used to sort these splitting points along the splitting intersection.
-The PBI-reps of split segments inherit their father's except the third component which identifies the end points.
+The PBI-reps of split segments inherit their father's except the $\bm{P}_0, \bm{P}_1$, which identifies the P-reps of end points*.
 
@@
 \noindent \textbf{Coincidence elimination (again)}~~~~
-Unfortunately, the overlap resolving may bring new coincident intersections. Therefore the first step is run again in the final step.
+Unfortunately, the overlap resolving may bring new coincident intersections in overlap cases. Therefore the first step is run again in the final step.
 
@@
 
-So far, intersections are only independent data that store the coordinates and neighbouring information.
+So far, intersections are only independent data that store the coordinates and neighbourhood information.
 To perform tessellation and extract subfaces, we need to organize them to reveal the topology.
@@
 This is done by extract valid loops on tess-graph.
-A valid loop that corresponds to a subface must satisfy two criterions: 1) the direction of loops should be coherent with the face normal, and 2) consecutive connections on the loop should be adjacent by circular order.
+A valid loop must satisfy two criterions: 1) the direction of loops should be coherent with the face normal, and 2) consecutive connections on the loop should be adjacent by circular order.
 Each valid loop corresponds to a intersection-free face.
-After we find out all valid loops on tess-graph, we finish tessellating the corresponding face.
+After we find out all valid loops on tess-graph, we finish tessellating the corresponding face (see Fig.
+\ref{fig:cadj}).
 To facilitate the later process, we also store neighborhood information into the edges of the new faces.
-Because the edges of new faces are generated from intersections, the neighborhood information of the edges is inherent from the corresponding intersections.
+The neighborhood information is inherent from the corresponding intersections.
+When all faces are tessellated, meshes are intersection-free.
 
@@
 \centering
-\includegraphics[width=3in]{circularadj}
-\caption{\emph{Left}: we find all valid loops on tess-graph to tesselate a triangle.
+\includegraphics[width=3in]{boolean-05}
+\caption{a) We find all valid loops on tess-graph to tesselate a triangle.
 The direction of loops have to be coherent with the triangle normal (assume the normal points to the outside of paper).
-\emph{Right}: each circular adjacent edge pair is an angle of the tessellated polygon.}
+b) Each circular adjacent edge pair is an angle of the tessellated polygon.}
 \label{fig:cadj}
 \end{figure}
-
-When all faces are tessellated, meshes are intersection-free.
-We further attach the PBI-reps of intersections to the edges generated from tess-graph connections which corresponds to an intersection.
-Finally, we get the intersection-free hybrid meshes, with some edges contains neighborhood information which indicates there are intersections between meshes.
 
@@
 We traverse each face in the intersection-free meshes, and classify which one belongs to the final mesh.
-Classification is done by evaluating the indicator vector of each face.
-The basic idea of our classification method is to utilize the space coherence of face indicator vectors to reuse the classification results.
-Because we store the PBI-reps which contains neighborhood information in the edges which intersect other meshes, the search space of point-in-polyhedron test is limited to only a few faces, which makes the indicator computation very fast.
-Also, by using P-reps, our classification method can deal with any degenerate cases.
-
-The space coherence of indicator vectors means neighboring faces could share the same indicator vector, or most components of indicator vectors.
+Classification is done by evaluating the indicator vector $\bm{\Lambda}$ of each face.
+The basic idea of our classification method is to utilize the space coherence of face indicator vectors to share the classification results among neighboring faces.
+Also, because we store the neighborhood information in the edges which intersect other meshes, the search space of point-in-polyhedron test is limited to only a few faces.
+It makes the indicator computation very fast.
+Finally, by using P-reps, our classification method is exact can deal with any degenerate cases.
+
+The space coherence of indicator vectors means neighboring faces may have the same indicator vector, or most components of indicator vectors.
 Therefore, we start from a seed face $\bm{s}_0$ with its indicator vector $\bm{\Lambda}(\bm{s}_0)$ known, and propagate to other faces in a flood-filling manner.
@@
 
-Our hybrid meshes facilitate this process by accelerating the indicator propagation.
+Our intersection-free meshes facilitate this process by accelerating the indicator propagation.
 Given adjacent faces $\bm{s}_1$ and $\bm{s}_2$, it is straightforward to know whether $\bm{\Lambda}(\bm{s}_1)$ and $\bm{\Lambda}(\bm{s}_2)$ are different.
-The two indicator vectors are the same unless the shared edge $\bm{e}_{12}$ lies on the boundary of some other meshes, which means there is neighborhood information, say, $\bm{\mathcal{N}(\bm{e}_{12})} = \{(P_k, \mathcal{N}_k)\}$, stored on $\bm{e}_{12}$.
+The two indicator vectors are the same unless the shared edge $\bm{e}_{12}$ lies on the boundary of some other meshes, which means there is neighborhood information, say, $\bm{\mathcal{N}}(\bm{e}_{12}) = \{\mathcal{N}_k\}$, stored on $\bm{e}_{12}$.
+Noted that here we use $\bm{\mathcal{N}}$ to indicate that there may be more than one neighborhood for the edge (see \S\ref{sec:refine}).
 The neighborhood information indicates which components of indicator vector differ between $\bm{s}_1$ and $\bm{s}_2$.
@@
 \fi
-If there is a neighborhood $(P_k, \mathcal{N}_k) \in \bm{\mathcal{N}}(\bm{\bm{e}_{12}})$, the $k^{th}$ indicators $\lambda_k(\bm{s}_1)$ and $\lambda_k(\bm{s}_2)$ can be computed efficiently and exactly according to $\mathcal{N}_k$ (\S\ref{sec:propagation}).
+If there is a neighborhood from mesh $M_x$, the $x^{th}$ indicators $\lambda_x(\bm{s}_1)$ and $\lambda_x(\bm{s}_2)$ differ and can be computed efficiently and exactly according to the neighborhood.
 We outline our classification method in Algorithm \ref{code:floodfill}.
@@
 Classification is required to perform on the face level.
-However, polyhedron in-out test is performed based on points.
+However, polyhedron-in-out test is performed based on points.
 Gaps exist between the them.
@@
 However, the computation of inner point coordinates requires geometry construction, which introduces errors without exact arithmetic.
-Therefore, we use the vertices instead, whose exact representations are known, for indicator computation.
+Therefore, we use the face (or subface) vertices instead, whose exact representations are known, for indicator computation.
 
@@
 
-%For example, given a face $\bm{s}$ and one of its vertex $v^i(\bm{s})$, if $\lambda_k(v^i(\bm{s}))=on$, $\lambda_k(\bm{s})$ can be any of $on$, $in$ or $out$ (see {\color{red}{Fig. ?}})
-However, there are two gaps between face indicator and vertex indicator.
+However, there are two gaps between face indicator and face vertex indicator.
 First, the indicator of vertex does not always equal to indicator of face.
-Second, face indicator has two conditions in $on$ case---$same$ and $oppo$, because the face has its orientation.
-
-To overcome the gaps, we discuss our indicator trace (\ref{eq:trace}) in finer granularity.
+Second, face indicator has two extra classes in $on$ case---$same$ and $oppo$, because the face has its orientation.
+
+To overcome the gaps, we rewrite our indicator trace (\ref{eq:trace}) in finer granularity.
 In the beginning, we start from a seed vertex $\bm{v}_0$ on seed face $\bm{s}_0$.
@@
 Then we use $\bm{\Lambda}(\bm{v}_0)$ to compute $\bm{\Lambda}(\bm{s}_0)$.
-In addition, we add the edge layer into the trace.
+In addition, we add an optional edge layer into the trace.
 Then it changes to:
@@
 \includegraphics[width=3in]{bsps}
-\caption{a) Because we cannot use inner sample point includes geometry construction, we choose the vertices (green one) instead to compute the face indicator.
+\caption{a) Because inner sample point includes geometry construction, we choose the face vertex (orange one) instead to compute the face indicator.
 b-d): Different situations of classification.
 The simple structure of neighborhood BSP guarantees the same classification result of the points on $\bm{p}_{\bm{s}, sp}^+$.
-In \emph{a}, the BSP contains two half-planes because it is constructed from two neighborhood faces.
-In \emph{d}, the classification result is $on$ so we need to determine the orientation by the normal of half-plane $q$ and the face $p$.
+In d), the classification result is $on$ so we need to determine the orientation by the normal of BSP splitting plane $q$ and the face normal $p$.
 In this condition, the indicator should be $oppo$ since $p$ and $q$ are opposite.}
@@
 
-Given the partial order $on \succ in$ and $on \succ out$, our key observation is that the following relation always stands for indicators:
+Given the partial order $on \succ in$ and $on \succ out$, our key observation is that the following relation always stands for indicators within intersection-free meshes:
 \begin{equation}
@@
 , where $\lambda_k(x)$ means the indicator of $x$ against a certain primitive $M_k$.
-This relation can be inferred from continuous space assumption and the definition of intersection-free mesh.
-It tells us when we perform $\bm{v}_{\bm{e}}\to \bm{e}$ and $\bm{e}_{\bm{s}}\to \bm{s}$, we decide whether the $on$ indicator changes to $in$ or $out$ or remains $on$.
+This relation can be inferred from continuous space assumption and the definition of intersection-free mesh*.
+It tells us when we perform $\bm{v}_{\bm{e}}\to \bm{e}$ and $\bm{e}_{\bm{s}}\to \bm{s}$, from low-dimension to high-dimension, we decide whether the $on$ indicator changes to $in$ or $out$ or remains $on$.
 When we perform $\bm{s}\to \bm{e}_{\bm{s}}$, we decide whether $in$ and $out$ indicators change to $on$.
@@
 We known when $\lambda_k(\bm{e}_{\bm{s}})=on$, there will be neighborhood information related to mesh $M_k$ stored on $\bm{e}_{\bm{s}}$.
-Therefore, in this operation, all we need is to iterate over neighborhoods of $\bm{e}_{\bm{s}}$ and change corresponding indicators to $on$.
+Therefore, in this operation, all we need is to traverse over all neighborhoods of $\bm{e}_{\bm{s}}$ and change corresponding indicators to $on$.
 
@@
 On the other hand, when $\lambda_k(\bm{e}_{\bm{s}}) = on$, we figure out $\lambda_k(\bm{s})$ using neighborhood information related to $M_k$.
-We know the corresponding neighborhood $\mathcal{N}_k$ and can be either a triangle face or an edge from mesh $M_k$.
-If $\mathcal{N}_k$ is a face, we can build a trivial BSP \cite{thibault1987set} using the face on the space near $\bm{e}_{\bm{s}}$.
-If $\mathcal{N}_k$ is an edge, we can still build BSP using the faces adjacent to $\bm{e}_{\bm{s}}$.
-In both cases, the BSP can be used to compute $\lambda_k(\bm{s})$ if we can sample a point from $\bm{s}$ that near $\bm{e}_{\bm{s}}$.
+The neighborhood related to $M_k$ can be either a face or a set of faces from mesh $M_k$.
+We can build a trivial BSP \cite{thibault1987set} with these faces.
+The BSP can be used to compute $\lambda_k(\bm{s})$ if we can sample a point from $\bm{s} \cap \bm{U}(\bm{e}_{\bm{s}})$, where $\bm{U}(\bm{e}_{\bm{s}})$ is the neighborhood space of $\bm{e}_{\bm{s}}$.
 Unfortunately, we cannot guarantee to find such a point with precise coordinates.
 
-We find that the BSP constructed from edge neighborhood is so simple that indicators $\lambda_k$ of all points on the half plane $\bm{p}_{\bm{s}, sp}^+$ are the same.
-Here $\bm{p}_{\bm{s}, sp}^+$ is half of the supporting plane of $\bm{s}$ that on the positive side of bounding plane $\bm{p}_{\bm{s}, b}^{\bm{e}_{\bm{s}}}$ (Fig.
+However, we notice that our BSP is constructed from a single face or a set of faces sharing the same edge.
+Such BSP is so simple that indicators $\lambda_k$ of all points on the half plane $\bm{p}_{\bm{s}, sp}^+$ are the same.
+Here $\bm{p}_{\bm{s}, sp}^+$ is half of the supporting plane of $\bm{s}$ that on the positive side of bounding plane $\bm{p}_{\bm{s}, b}^{\bm{e}_{\bm{s}}}$ (see Fig.
 \ref{fig:bsps}).
-Since $\bm{p}_{\bm{s}, sp}^+ \cap \bm{s} \neq \varnothing$, we can compute $\lambda_k(\bm{s})$ by figuring out $\lambda_k(\bm{v}_x)$, where $\bm{v}_x \in \bm{p}_{\bm{s}, sp}^+$.
-For polygons, there is at least one vertex on $\bm{p}_{\bm{s}, sp}^+$, whose exact coordinates are known.
-Therefore that vertex is used as the $v_x$.
-Also, if we assign each BSP splitting plane a normal by the normal of triangle it contains, we can use it to decide the orientation ($same$ or $oppo$) when $\bm{v}_x$ is on a splitting plane, which means $\lambda_k(\bm{s})=on$.
+Since $\bm{p}_{\bm{s}, sp}^+ \cap \bm{s} \neq \varnothing$, we can compute $\lambda_k(\bm{s})$ by figuring out $\lambda_k(\bm{v}_x, \bm{v}_x \in \bm{p}_{\bm{s}, sp}^+)$.
+For polygons, there is at least one corner point on $\bm{p}_{\bm{s}, sp}^+$, whose exact coordinates are known.
+Then that corner point is used as the $\bm{v}_x$.
+Also, we assign each BSP splitting plane a normal by the normal of triangle it contains, by which we can decide the orientation ($same$ or $oppo$) when $\lambda_k(\bm{s})=on$.
 
@@
 \end{wrapfigure}
-\noindent\textbf{$\bm{\bm{v}_{\bm{e}}\to e}$}~~~~ While this is yet another propagation from low dimension to high dimension, there is no neighborhood information stored on vertex.
-If $\lambda_k(\bm{v}_{\bm{e}})=on$, we first check whether $\lambda_k(\bm{e}) = on$ by checking the neighborhood component of the intersection on $\bm{e}$.
-If not, we need to find where $\bm{v}_{\bm{e}}$ lies on the surface of $M_k$ and determine the neighborhood of $\bm{v}_{\bm{e}}$.
-In most cases, it is straightforward since coincident vertices among different intersection-free meshes are shared (see \S\ref{sec:esubroutine} for exception discussion).
-The neighborhood may be a vertex, an edge or a face.
-After computing the neighborhood, the same BSP-based classification method is used as in ${\bm{e}_{\bm{s}}\to \bm{s}}$ to determine the high dimension indicator $\lambda_k(\bm{e})$.
-We use the other end point of $\bm{e}$ to be the sample point for the BSP classification.
+\noindent\textbf{$\bm{\bm{v}_{\bm{e}}\to e}$}~~~~If $\lambda_k(\bm{v}_{\bm{e}})=on$, we first check whether $\lambda_k(\bm{e}) = on$ by checking whether there is neighborhood information related to $M_k$ on $\bm{e}$.
+If not, we need to find where $\bm{v}_{\bm{e}}$ lies on $M_k$.
+It is straightforward since the intersection-free meshes contains geometry connectivity.
+The $\bm{v}_{\bm{e}}$ may lie on a vertex, an edge or a face.
+We can see this information as the vertex version of neighborhood information, and the same BSP-based classification method is used as in ${\bm{e}_{\bm{s}}\to \bm{s}}$ to determine the high dimension indicator $\lambda_k(\bm{e})$.
+We use the other end point $\bm{v}'_{\bm{e}}$ to be the sample point for the BSP classification.
 
@@
 If the CSG tree is large with hundreds of primitive nodes, computing $\lambda_f(\bm{s}_i)$ from $\boldsymbol{\Lambda}(\bm{s}_i)$ for every face $\bm{s}_i$ can be costly.
-Thanks to the indicator space coherence, we can save the computation time by caching the evaluation result $f(\boldsymbol{\Lambda}(\bm{s}_i))$ during flood-filling.
+Thanks to the indicator space coherence, we can save the computation time by caching the evaluation result during flood-filling.
 
 The basic cache strategy is to cache final result, that is, the value of $\lambda_f(\bm{s}_i)$.
-We know indicator vector will not change if there is no intersections on the edge during propagation.
+We know indicator vector will not change if there is no intersection edge during propagation.
 That means the final classification $\lambda_f(\bm{s}_i)$ will not change, too.
@@
 We noticed that the boolean expression can be simplified if some components of $\boldsymbol{\Lambda}(\bm{s}_i)$ is fixed.
-For example, assume we have a boolean expression $f = P_1\cup (P_2\cap P_3-P_4)$.
-Given the values of two indicators $\lambda_1(\bm{s}_i)=out$, $\lambda_2(\bm{s}_i)=in$, the expression can be rewritten as $f(\lambda_1=out, \lambda_2=in)=out\cup (in\cap P_3-P_4)$.
+For example, assume we have a boolean expression $f = M_1\cup (M_2\cap M_3-M_4)$.
+Given the values of two indicators $\lambda_1(\bm{s}_i)=out$, $\lambda_2(\bm{s}_i)=in$, the expression can be rewritten as $f(\lambda_1=out, \lambda_2=in)=out\cup (in\cap M_3-M_4)$.
 Using the combination rules we can simplify the expression as $f(\lambda_1=out, \lambda_2=in)=P_3-P_4$.
-This fact is important because for a large CSG, a certain primitive (denoted as $M_k$) often intersects with only a few other meshes $\Theta(P_k)= \{P_{n_1}, P_{n_2}, \cdots, P_{n_x}\}$.
-That means all the faces in $M_k$ has the same indicators $\lambda_{i}, P_{i} \notin \Theta(P_k)$.
-Therefore, we can first determine these fixed indicators and simplify the boolean function, and then use simplified one to compute the final indicator for each faces in $M_k$.
+Because for a large CSG, a certain mesh often intersects with only a few other meshes $\Theta= \{M_{n_1}, M_{n_2}, \cdots, M_{n_x}\}$.
+That means all the faces in this mesh has the same indicators against $M_{i} \notin \Theta(M_k)$.
+Therefore, we can first determine these fixed indicators and simplify the boolean function, and then use simplified one to compute the final indicator for each faces in this mesh.
 
@@
 We implemented the proposed method in C++ and tested a series of models on a laptop with Intel Core i5 1.5GHz CPU and 8GB RAM.
-To prove both the efficiency and robustness, we perform boolean evaluation on various CSGs with different complexity.To show our advantage, we also compared our method with several previous works with available implementations, including CGAL \cite{cgal:hk-bonp3-15a}, Maya \cite{Maya2015,barki2015exact},"Cork" \cite{Cork}, "QuickCSG" \cite{douze2015quickcsg}, "Carve" \cite{Carve}, and online service of Campen and Kobbelt's plane-based method \cite{campen2010exact,WebBSP}.
-
-\subsection{Robustness}
+To prove both the efficiency and robustness, we perform boolean evaluation on various CSGs with different complexity.
+We also compared our method with several previous works with available implementations, including CGAL \cite{cgal:hk-bonp3-15a}, Maya \cite{Maya2015,barki2015exact},"Cork" \cite{Cork}, "QuickCSG" \cite{douze2015quickcsg}, "Carve" \cite{Carve}, and online service of Campen and Kobbelt's plane-based method \cite{campen2010exact,WebBSP}.
+
+\subsection{Robustness \& Performance}
 
@@
 \includegraphics[width=3in]{dual}
-\caption{a) We cannot easily figure out the correct orientation of the loop.
-b) When there are more than one connected component, we use auxiliary intersection (red line) to connect the two component.
+\caption{a) There is ambiguity with the orientation of the loop in a tess-graph.
+b) When there are more than one connected component in tess-graph, we use auxiliary intersection (yellow line) to connect the two component.
 }
@@
 \end{figure}
+
+\begin{table*}[ht]
+\caption{Results of Self-Union Evaluation}
+\label{tab:selfunion}
+\centering
+\begin{tabular}{*{8}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
+\hline
+{No.} & {Model} & {Face Num.} &
+CGAL & Maya & Cork & Carve & QuickCSG  & Our Method
+\\
+\hline\hline
+1 & Ball & 360  & \cmark & \cmark & \xmark & \cmark & \xmark & \cmark \\
+2 & Head & 2.7k& \cmark & \cmark & \xmark & \cmark & \xmark  & \cmark\\
+3 & Bunny & 70k  & \xmark & \cmark & \xmark & \cmark & \xmark  & \cmark\\
+4 & Dragon & 277k & \xmark & \xmark & \xmark & \xmark & \xmark  & \cmark \\
+\hline
+\end{tabular}
+\begin{flushleft}
+%~~~~~~~~~~~~~~~~~~~~~$^{*}$~~We perturb the model by 1e-6 to give QuickCSG the ability to partly solve coplanar cases.
+\end{flushleft}
+\end{table*}
 
@@
 \hline
-{No.} & {Model} & {Triangle Num. 1} & {Triangle Num. 2} &
+{No.} & {Model} & {Face Num. 1} & {Face Num. 2} &
 CGAL & Maya & Cork & Carve & QuickCSG & Our Method
@@
 \centering
-\begin{tabular}{*{9}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
+\begin{tabular}{*{8}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
 \hline
-{No.} & {Model} & {Triangle Num.} & {Primitive Num.} &
-CGAL & Maya & Cork & Carve & QuickCSG & Our Method
+{No.} & {Model} & {Face Num.} & {Mesh Num.} &
+CGAL  & Cork & Carve & QuickCSG & Our Method
 \\
 \hline\hline
-1 & Sprocket & 11k & 52 & 211 & ? & - & 4.26 & 0.132 & 0.804\\
-2 & Ring \& Ball & 146k & 801 & - & ? & - & 187 & - & 62.6\\
-3 & T1 & 80k & 50 & 1.00k & ? & 18.5 & 10.4 & 0.388 & 20.2\\
-4 & T2 & 7k & 50 & 2.81k & ? & - & 16.0 & 0.804 & -\\
-5 & H & 33k & 42 & - & ? & - & - & 2.22 & -\\
-6 & Organic & 219k & 6 & - & ? & 14.3 & 63.1 & 0.580 & 2.75\\
+1 & Sprocket & 11k & 52 & 211  & - & 4.26 & 0.132 & 0.804\\
+2 & Ring \& Ball & 146k & 801 & -  & - & 187 & - & 62.6\\
+3 & T1 & 80k & 50 & 1.00k & 18.5 & 10.4 & 0.388 & 20.2\\
+4 & T2 & 7k & 50 & 2.81k & - & 16.0 & 0.804 & -\\
+5 & H & 33k & 42 & - & - & - & 2.22 & -\\
+6 & Organic & 219k & 6 & - & 14.3 & 63.1 & 0.580 & 2.75\\
 %7 & 6 Budda & - & 43 & - & - & - & - & - & -\\
@@
 
-\begin{table*}[ht]
-\caption{Results of Self-Union Evaluation}
-\label{tab:selfunion}
-\centering
-\begin{tabular}{*{8}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
-\hline
-{No.} & {Model} & {Face Num.} &
-CGAL & Maya & Cork & Carve & QuickCSG  & Our Method
-\\
-\hline\hline
-1 & Ball & 360  & \cmark & \cmark & \xmark & \cmark & \xmark & \cmark \\
-2 & head & 2,716& \cmark & \cmark & \xmark & \cmark & \xmark  & \cmark\\
-3 & Bunny & 69,666  & \xmark & \cmark & \xmark & \cmark & \xmark  & \cmark\\
-4 & Dragon & 276,972 & \xmark & \xmark & \xmark & \xmark & \xmark  & \cmark \\
-\hline
-\end{tabular}
-\begin{flushleft}
-%~~~~~~~~~~~~~~~~~~~~~$^{*}$~~We perturb the model by 1e-6 to give QuickCSG the ability to partly solve coplanar cases.
-\end{flushleft}
-\end{table*}
-
-Our method is unconditionally robust for regular set meshes.
-Even extreme degenerate cases will not cause invalid output.
-To prove that, we tested the self-union of several models and some CSG with coplanar faces.
-Table \ref{tab:selfunion} compares the difference between input meshes and result meshes by their face number.
-We find that our method always produces correct or at least near correct results.
-The slightly deviation of our result from the original one is caused by self-intersection in the original models.
+\vspace{0.5em}
+\noindent\textbf{Self-union}~~~~
+Our method is unconditionally robust for regular set mesh inputs.
+Even extreme degenerate cases will not lead to failure.
+To prove that, we tested the self-union of several examples.
+Table \ref{tab:selfunion} shows whether the tested methods gave a valid outputs.
+The word 'valid' means the outputs are almost the same with the inputs.
+In fact, the example models \emph{Bunny} and \emph{Dragon} contain topology deficiencies like self-intersection that cannot perform regular set boolean operations.
+Despite of that, we find that our method works good in all these cases, indicating the robustness of our method.
 QuickCSG and Cork failed in all cases, because they cannot deal with coplanar faces.
-By perturb one of the operant, the results of QuickCSG are visually OK.
+By perturbing one of the operant, the results of QuickCSG are visually OK.
 However, the topology of their results is messy.
@@
 
-\subsection{Performance}
 \vspace{0.5em}
@@
 We can clearly see our method is very fast that is only twice as slower than the fastest non-robust QuickCSG.
-Other robust methods such as Maya and CGAL are much slower because both of them use the arbitrary precision arithmetic.
-Moreover, these robust methods have very strict requirements on the inputs and fragile with topology deficiencies such as boundary edges or self-intersection.
-On the contrary, our   We also noticed that in (some) very large CSGs, most time is spent on octree construction in our method.
-It means other stages which involve plane-based geometry take only a small percentage of time, proving the efficiency of our plane-based geometry.
+Other robust methods such as Maya and CGAL are much slower because they use the arbitrary precision arithmetic.
+Moreover, these robust methods have very strict requirements on the inputs and fragile with topology deficiencies.
+They simply crash when the inputs are not valid, while our method always tries to give an answer.
+We also noticed that in (some) very large CSGs, most time is spent on octree construction in our method.
+It means other stages which involve plane-based geometry take only a small percentage of time, which proves the efficiency of our plane-based algorithms*.
 
@@
 To identify the ability of evaluating large CSG, we also test some CSG with tens or hundreds of meshes.
-Maya and CGAL cannot perform multiple boolean operations, so we can only give the comparison of incremental boolean evaluation for these methods.
-We see that the computation time of robust methods like CGAL and Maya grows rapidly when the number of meshes grows.
-On the other hand, our method keeps good performance while stay robust.
-During our experiments, we noticed Maya gives the correct results in the first few boolean operations, but failed in the later ones.
-It proves a disadvantage of incremental boolean operation methods: if it cannot guarantee exactness, it will accumulate numerical errors which affects the algorithm stability.
+Only QuichCSG and our method can perform multiple boolean operations directly, while others have to decompose CSG trees into binary boolean operations..
+We see that the computation time of robust methods like CGAL and Maya is unacceptable long for large CSGs.
+On the other hand, our method keeps good performance and stability.
+During our experiments, we noticed sometimes Maya gives the correct results in the first few binary boolean operations, but failed in the later ones.
+It proves a disadvantage of incremental boolean operation methods---it could accumulate numerical errors which affects the algorithm stability.
 
@@
 \ref{fig:dual}a).
-We observe that the graph connections lie on face edges have their unambiguous directions.
+We observe that the graph connections on the triangle edges have unambiguous directions.
 Starting from these edges, we can guarantee that the loops have the right orientations.
-After we find a valid loop, more graph connections will have unambiguous directions because one connection can participate two valid loops at most.
+After we find a valid loop, more graph connections will have unambiguous directions because one connection can participate at most two valid loops.
 In such way, the correct orientation will propagate in a flood-filling way.
@@
 We avoid this problem by inserting auxiliary intersections into the tess-graph to make it connected.
-An auxiliary intersection links the vertex of face (denoted as $\bm{v}_i$) on the outer connected component with the vertex on the inner connected component.
+An auxiliary intersection links the corner vertex of triangle face (denoted as $\bm{v}_i$), which is certainly on the outer component, with the vertex on the inner component.
 The intersection refinement has to be performed again if the auxiliary intersections cross any other intersections.
-To guarantee the auxiliary intersection has a valid PBI-rep, we require the vertex from inner connected component generated by intersection between the face and an edge (denoted as $\bm{e}_j$) from other meshes---all newly introduced vertices during triangle-triangle intersection are this type.
+This trick slight obey the principle of no constructions.
+To guarantee the auxiliary intersection has a valid PBI-rep, we require the vertex from inner connected component generated by intersection between the triangle and an edge (denoted as $\bm{e}_j$) from other meshes---all intersection end points during triangle-triangle intersection are this type.
 In this way, we get three vertices with exact coordinates ($\bm{v}_i$ and the two end points of $\bm{e}_j$) and can construct an exact plane where the auxiliary intersection lies.
@@
 We choose the vertex with the max $x$-coordinate as the seed.
-In this way, $\lambda_k(\bm{v}_0)$ is either $out$ ($in$, if complement is applied on mesh) or $on$.
+In this way, its indicators are either $out$ ($in$, if complement is applied on mesh) or $on$.
 The $on$ indicators are easy to determine in most time.
-Though sometimes exception occur because of multi-coplanar situation, this will not happen if we carefully choose the right vertex whose neighbor faces are not coplanar.
+Sometimes exception occurs because of coplanar situation---vertices may not be registered on the mesh even if it is on the mesh.
+Fortunately, if we carefully choose the right vertex whose neighboring faces are not coplanar, this will not happen.
 
@@
 Therefore in most time, we only need one single seed vertex for classification.
-However, if there are more than two connected components among meshes, we need to new seeds to propagate each component.
+However, if there are more than two connected components among meshes, we extra seeds to propagate each component.
 The indicators of the second and later seeds can be computed by point-in-polyhedron tests.
@@
 \noindent\textbf{Exporting to float-point number}~~~~
-The vertices of final mesh in our method are represented in both P-reps and plain coordinates.
-While the vertices from the input meshes have there exact coordinates, the vertices newly introduced by intersection between meshes require round-off when converting to coordinates representation.
-Though we guarantee the correct topology in the result mesh, such round-off can still cause topology deficiencies such as self-intersections.
+The vertices of final mesh in our method are represented in either planes or vertex coordinates.
+While the vertices from the input meshes have there exact coordinates, the vertices newly introduced by intersection between meshes have only P-reps and require round-off when computing coordinates.
+Though we guarantee the correct topology in the result mesh, such round-off can still cause topology deficiencies.
 Here we adopt Zhou et al.'s method \cite{zhou2016mesh} to solve it iteratively.
@@
 However, recent works claim that the piece-wise wind number (PWN) are more powerful to identify the inside and outside of meshes \cite{zhou2016mesh}.
-By using PWN, the input requirements can be extended to so-called PWN meshes that allow deficiencies such as self-intersection and multi-component.
+By using PWN, the input requirements can be extended to so-called PWN meshes that allow topology deficiencies such as self-intersection and multi-component.
 It would be interesting to extend our method to PWN method in the future.
@@
 
-In this paper, we proposed a novel method to evaluate CSG with regular set primitives.
+In this paper, we proposed a novel method to evaluate CSG models.
 It is able to efficiently perform unconditionally robust non-incremental boolean operations.
@@
 And the B-reps offer fast neighborhood query to accelerate the processing.
-Experiments have verified the performance of our method is competitive with state-of-the-art non-robust methods while guarantee unconditional robustness.
+Experiments have verified the performance of our method is competitive with state-of-the-art non-robust methods while guarantee robustness.
 

### 2017-01-06 paper.tex
change to split files

--- 2016-05-09 paper.tex
@@
 \usepackage{slashbox}
+\usepackage{color}
+%\usepackage[numbers,sort&compress]{natbib}
 %\usepackage{ulem}
-%\usepackage[numbers,sort&compress]{natbib}
 \renewcommand{\arraystretch}{1.3}
 
+\usepackage{color}
+\usepackage{bm}
+%\usepackage{mathrsfs}
+\usepackage[mathcal]{eucal}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{wrapfig}
+
+\usepackage{amssymb}% http://ctan.org/pkg/amssymb
+\usepackage{pifont}% http://ctan.org/pkg/pifont
+\newcommand{\cmark}{\ding{51}}%
+\newcommand{\xmark}{\ding{55}}%
 % correct bad hyphenation here
@@
 
-\IEEEtitleabstractindextext{
-\begin{abstract}
-  In this paper, we propose an efficient non-incremental approach to evaluate the boundary of constructive solid geometry (CSG).
-The face membership classification step is a bottleneck in many existing CSG evaluation approaches.
-The key idea of our approach is to use local coherence of space labels to accelerate this step.
-We employ a two-level grouping scheme to group faces that share the same space labels.
-Therefore, these common space labels can be shared within each group to avoid repetitive computation.
-Our method is optimized for a non-incremental evaluation.
-It generates the entire result model at once, rather than performing a step-by-step evaluation of Boolean operations.
-To achieve a robust evaluation, our approach introduces plane-based geometry into the intersection computation step.
-Comparison experiments with state-of-the-art techniques show that our method can more efficiently perform boundary evaluation of both trivial and complicated CSG with massive faces while maintaining robustness.
-\end{abstract}
-
-\begin{IEEEkeywords}
-Boolean operations, triangle mesh, CSG evaluation, plane-based geometry.
-\end{IEEEkeywords}
-
-}
-
-\maketitle
-
-\IEEEdisplaynontitleabstractindextext
-\IEEEpeerreviewmaketitle
-
-\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
-\IEEEPARstart{C}{onstructive} solid geometry (CSG) has long been a popular modeling tool of computer-aided design and computer-aided manufacturing (CAD/CAM).
-It constructs complex models by combining primitives using a series of regularized Boolean operations \cite{requicha1977mathematical}: union, intersection and difference.
-CSG is often represented by a binary tree, called a CSG tree, whose leaves are primitives and whose internal nodes are Boolean operations..
-
-CSG can be converted into the widely-used  boundary representation (i.e., triangle mesh) through boundary evaluation.
-Most boundary evaluation methods are based first on intersection computation and then on face membership classification.
-Robustness and efficiency are their major issues.
-During the last three decades, many techniques have been developed to solve these problems.
-However, the efficiency of face membership classification still needs improvement.
-
-Computing face space labels is the basis of face classification with respect to CSG.
-For each face, the number of space labels to be computed is equal to the number of primitives.
-For large CSG with massive faces and primitives, computing these space labels can be very time-intensive.
-A common acceleration method is to use localized schemes.
-This method is based on the local coherence of space labels: if a face is inside (or outside) a specific primitive, the face's neighborhoods are likewise often inside (or outside) the primitive.
-Determining whether two adjacent faces share the same space labels is relatively simple (see also Section \ref{sec:framework}); therefore, we can locally group together faces of the same labels and reuse space labels to save computation.
-
-\begin{figure}
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=3.5in]{cluster}\\
-  \caption{2D illustration of grouping schemes.
-The boundaries of polygons are edges.
-Suppose each input mesh consists of hundreds of edges (not shown in the figure).
-Edges are grouped using (a) voxels, (b) octree cells, and (c) edges as the grouping units.
-Different groups in (c) are marked by different colors.} \label{fig:cluster}
-\end{figure}
-
-Several recent studies \cite{campen2010exact, pavic2010hybrid, wang2011approximate} have used such localized schemes.
-These approaches often use the cube (e.g., voxels, octree cells) as the basic grouping unit to reuse the space division data structures constructed during the intersection computation.
-However, using the cube as a basic grouping unit has several disadvantages.
-In general, connected faces with the same space labels should be grouped together.
-Thus, an ideal face group is a union of connected faces and can be of any shape.
-The cube-based grouping scheme can only provide a rough approximation of that shape.
-Therefore, extra computation, which is usually time-consuming, is needed to classify those ungrouped faces.
-For example, in Figs.
-\ref{fig:cluster}(a) and (b), the red cubes contain the intersection of two primitives.
-Thus, the edges (faces in 3D) in these red cubes should belong to different groups (because they have different labels).
-However, the size of cubes cannot be illimitably small to distinguish these different groups.
-Therefore, these edges in the red cubes are left as ungrouped edges.
-In contrast, a face-based grouping scheme can easily handle groups of arbitrary shapes and is potentially more efficient for face classification (Fig.
-\ref{fig:cluster}(c)).
-
-Another limitation of prior exact evaluation algorithms is that most of them are incremental ones \cite{campen2010exact, feito2013fast, bernstein2009fast}.
-This means that they can evaluate only one Boolean operation at a time.
-For a large CSG tree with more than two primitives, incremental algorithms have to decompose the CSG into a series of Boolean operations and then incrementally evaluate each one.
-This strategy is highly inefficient because it unnecessarily computes the CSG intermediate results.
-Incremental algorithms have been more popular for a considerable time because human designers typically construct CSG models by progressively adding primitives.
-However, recent techniques---such as GPU-based approximate evaluation algorithms \cite{pavic2010hybrid, wang2011approximate} and CSG visualization algorithms \cite{hable2007cst, rossignac2011ordered}---are more suitable for such a preview computation.
-Therefore, exact evaluation algorithms are now more likely to be used for final mesh generation (after all the primitives are added), where a non-incremental algorithm has more advantages.
-
-In this paper, we propose a method to perform CSG boundary evaluation with triangular mesh primitives.
-The proposed method uses the face (i.e., a triangle in our implementation) as the basic unit of the grouping and applies a flood-filling algorithm to group faces.
-Our method utilizes the local coherence of space labels.
-It propagates face space labels between adjacent faces and adjacent groups to save computation of space labels.
-The most prominent characteristics of our method are outlined below.
-\vspace{0.0em}
-\begin{itemize}[leftmargin=*]
-  \item{\textbf{Face classification using two-level grouping}}~~~~To efficiently classify faces, we use a two-level grouping scheme to reuse space labels.
-Input faces are firstly grouped into first-level groups at the primitive level; then, the first-level groups are further divided into second-level groups according to their labels (Fig.
-\ref{fig_overview}(d)).
-A flood-filling algorithm is applied to enable efficient grouping and label sharing among adjacent faces.
-This framework makes a balance between the benefit of face label sharing and the cost of grouping faces for the best performance.
-
-  \vspace{0.5em}
-  \item{\textbf{Efficient non-incremental evaluation}}~~~~Unlike many existing Boolean methods \cite{granados2003boolean, bernstein2009fast, campen2010exact, feito2013fast}, the proposed method can perform non-incremental evaluation of CSG, which computes the entire final model directly.
-Our approach is more efficient at evaluating large CSGs because it computes no intermediate results in the internal nodes of CSG trees.
-A non-incremental evaluation is more difficult to perform because the conditions of the intersection and face classification are more complicated.
-We developed a set of techniques, including face-nested binary space partitioning (BSP) and multi-level CSG trimming, to make our method highly efficient for non-incremental evaluation.
-
-  \vspace{0.5em}
-  \item{\textbf{Robustness and exactness}}~~~~In the field of solid modeling, efficiency without robustness is impractical.
-We therefore adopt a series of schemes to make our method robust.
-To avoid the introduction of errors during intersection computation, we combine a triangle-triangle intersection algorithm \cite{moller1997fast} with a plane-based representation \cite{sugihara1990solid}.
-In addition, an exact BSP construction technique \cite{bernstein2009fast, campen2010exact} is adopted to enhance the robustness of face classification.
-\end{itemize}
-\vspace{0.5em}
-
-Experiments performed confirm that our method is more efficient than state-of-the-art techniques \cite{cgal:hk-bonp3-15a, campen2010exact, feito2013fast, Maya2015}.
-It can quickly and robustly perform CSG evaluations not only for trivial CSGs, such as one with single Boolean operation, but also for large CSGs with hundreds of primitives.
-
-\section{Related Work}
-
-\begin{figure*}[!t]
-\centering
-\includegraphics[width=7.1in]{flowchart}
-\caption{An overview of the proposed method for CSG evaluation.
-In this toy example, the CSG tree represents a solid constructed by (Cube $\cup$ Sphere - Cylinder).
-(d) shows how to classify faces step by step using a flood filling algorithm.
-Faces of the same primitive are grouped as the inter-primitive group.
-Then faces of the same inter-primitive group are further divided into intra-primitive groups according to their conditions of intersection (c).
-The unvisited faces are black.
-Different colors of other faces indicate that they are accepted and belong to different intra-primitive groups.
-Rejected faces are rendered with wire-frame.
-The seed face of flood filling in each primitive is highlighted in red.}
-\label{fig_overview}
-\end{figure*}
-
-CSG evaluation has had notorious problems with robustness since its inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}.
-The non-robustness is inherited from the building blocks of CSG: Boolean operations on solids.
-Many researchers have attempted to solve such an issue using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}.
-However, these methods are often too expensive in computation time and memory to be practical for evaluation of CSG with massive faces.
-For example, in the Computational Geometry Algorithms Library (CGAL) \cite{cgal:hk-bonp3-15a}, the state-of-the-art robust Boolean operation algorithm \cite{hachenberger2005boolean} (implemented with arbitrary precision arithmetic) is more than 20 times slower than its non-robust version.
-
-Sugihara and Iri \cite{sugihara1990solid} introduced a plane-based representation of polyhedra.
-They found that Boolean operations are fundamentally robust using the plane equation as the primary geometry representation.
-In this condition, the evaluation of Boolean operations can be performed with no `constructions' \cite{shewchuk1999lecture}, thereby avoiding the introduction of any numerical errors.
-
-Berstein and Fussell \cite{bernstein2009fast} noted that a binary space partitioning (BSP) merging algorithm in Boolean operations \cite{thibault1987set, naylor1990merging} is actually a plane-based technique.
-Therefore, they combined the two conceptions---plane-based geometry and BSP merging---to develop an unconditionally robust method for Boolean operations of polyhedra.
-Using Shewchuk's adaptive geometry predicate technique \cite{shewchuk1997adaptive}, this method can be only twice slower than non-robust methods.
-Our approach adopts this technique in the stage of face classification to ensure the robustness.
-
-Berstein and Fussell's method does not alleviate the problem of high memory consumption of BSP-based algorithms.
-Thus, it remains unprepared for polyhedra with massive faces.
-However, it inspired Campen and Kobbelt to develop a more delicate approach  \cite{campen2010exact}.
-This approach solves the problem of exact and efficient conversion of polyhedra between vertex-based and plane-based representations.
-Moreover, by leveraging the adaptive octree, BSP structures are nested into octree cells where the intersection between primitives occurs.
-For efficiency, face classification is performed using cells as the basic classification units.
-This localized scheme saves considerable computing resources and retains the topology of non-intersected areas.
-
-Such localized scheme is widely used in different methods of CSG boundary evaluation \cite{pavic2010hybrid, wang2011approximate, feito2013fast, campen2010exact}.
-These methods are usually based on intersection computation and face membership classification.
-The success of such localized scheme is enabled by two facts.
-First, the intersections between primitives are locally distributed.
-Second, space labels of a face are often coherent with those of its neighborhood.
-The former makes it possible to reduce the space that requires an intersection test.
-The latter enables sharing of space labels between adjacent faces to accelerate face classification.
-
-However, most of these methods use the cube (e.g., voxels, octree cells) as the unit of the face group, which is often the natural result of reusing space-division data structures constructed for intersection computation.
-In this way, connected faces that share the same labels might be distributed in different cubes.
-Thus, repetitive classifications may be required for each cube.
-Furthermore, faces of different classifications may coexist within a small space, forming a ‘mixed’ area (e.g., the red areas in Figs.
-\ref{fig:cluster}(a) and (b)).
-Because the size of the cubes cannot be illimitably small, special cubes that contain faces with different space labels typically must be constructed in these mixed areas.
-Processing these special cubes is often complex and time-consuming.
-To more efficiently share space labels, we therefore use faces, rather than cubes, as the basic grouping units.
-Grouping is efficiently performed by utilizing geometry connectivity with a flood-filling algorithm.
-
-Recently, Feito et al.
-\cite{feito2013fast} proposed a method for Boolean evaluation.
-This method also uses a face-based grouping scheme.
-To share classification results, faces that do not intersect with other primitives are grouped together according to geometry connectivity.
-This method and the proposed method have similar stages for single Boolean operation evaluation.
-One of the major differences is that our method supports non-incremental evaluation of CSG.
-For this purpose, we designed a series of dedicated stages.
-Additionally, our face grouping scheme is intended for both non-intersected faces and faces that intersect with other primitives.
-It thus provides a uniform treatment for all faces and further accelerates the face classification stage.
-Moreover, the similarity between adjacent groups is omitted by Feito et al.'s method.
-Although different groups have different space labels, we observe that they may still share some of these labels if they are neighboring.
-We utilize this kind of space label coherence between groups for better performance.
-
-On the other hand, with the development of general-purpose computing on graphics processing units (GPGPUs), many researchers  \cite{wang2011approximate, zhao2011parallel, museth2002level, chen1999volumetic, eisemann2008single} have tried to utilize the grand computation power of graphics hardware for Boolean operations.
-These methods often have good performance and are suitable for interactive applications, such as digital sculpting.
-However, owing to the paralleled features of graphics hardware, these methods are usually voxel-based and support only approximate evaluation that inevitably suffers from geometric detail loss, especially at the intersection areas of primitives.
-
-\section{Overview}
-
-\label{sec:overview}
-
-As in most previous works \cite{feito2013fast, bernstein2009fast}, we require the input primitives of the CSG tree to be watertight Nef polyhedra with manifold surfaces.
-We assume there is no self-intersection.
-Because we adopt a flood-filling strategy, we additionally assume that the connectivity of adjacent faces is available.
-Our current implementation is dedicated to primitives of triangular meshes for simplicity.
-Our approach efficiently and robustly computes the boundary of CSG solids in three steps, as illustrated in Fig.
-\ref{fig_overview}.
-Our main contributions exist in Steps 2 and 3.
-
-\subsection{Adaptive Octree Construction}
-
-As a typical routine of localization, our method uses the adaptive octree to frequently accelerate the used spatial query afterwards.
-Our octree construction implementation is akin to the implementation in Feito et al.'s method \cite{feito2013fast}.
-The major difference is that, because our method is for non-incremental CSG evaluation, the octree is constructed on the bounding box that contains all input primitives (Fig.
-\ref{fig_overview}(b)).
-To avoid presentation ambiguity between a CSG leaf and an octree leaf, the latter is called a cell.
-Intersection detection between triangle faces and cells can be efficiently performed by using the separating axis theorem \cite{gottschalk1996obbtree}.
-Cells are classified into two types: if all triangles that intersect a cell belong to the same primitive, we call it a \emph{non-critical} cell.
-Otherwise, it is a \emph{critical} cell.
-This classification is needed for intersection computation in the next step.
-
-\subsection{Plane-based Intersection Computation}
-\label{sec:overview:isect}
-
-In this step, we compute all intersections between primitives and record them in intersected faces (e.g., the red triangles in Fig.
-\ref{fig_overview}(c)) for further computation.
-Because we have already constructed the octree and obtained its cell classification, it is instantly known that intersection between faces occurs only within critical cells.
-Thus, we limit the intersection test within these critical cells.
-The intersection test is performed for every pair of faces in each critical cell.
-We assume that primitives are not self-intersected; therefore, tests for faces from the same primitives are unnecessary.
-
-The triangle-triangle intersection test always incurs robustness issues.
-To avoid an unexpected failure caused by numeric errors, we integrate a plane-based representation of polyhedra \cite{sugihara1990solid} into the triangle-triangle intersection test.
-Adaptive precision predicate technique \cite{shewchuk1997adaptive} is applied for efficiency of plane-based geometry computation.
-Details are provided in Section \ref{section:isect}.
-
-\subsection{Face Classification Using Two-level Grouping}
-
-Face classification using two-level grouping is the most novel step of our algorithm.
-For each primitive face, we must determine whether it, or its part (when the face intersects with other faces), belongs to the final model.
-A breadth-first flood-filling algorithm is used to traverse faces of each primitive.
-Starting from a random seed whose space labels are all computed, these labels propagate to neighboring faces and vary according to intersection conditions (Fig.
-\ref{fig_overview}(d)).
-Each face is instantly classified once all of its space labels are computed.
-We use a two-level face grouping scheme to enable the maximum information reuse.
-The first level is the \emph{inter-primitive} level; the second is the \emph{intra-primitive} level.
-When visiting an intersected face, constrained Delaunay triangulation \cite{chew1989constrained} is applied to subdivide the face into smaller triangles, followed by individual classification of the subdivided triangles using BSP techniques.
-The robustness of this step is ensured by the exact BSP computation technique \cite{bernstein2009fast}.
-Details are shown in Section \ref{section:floodfill}.
-
-\section{Plane-based Intersection Computation}
-
-\label{section:isect}
-
-In this step, intersections between faces are computed through the triangle-triangle intersection test within each critical cell.
-We adopt M\"{o}ller's intersection detection algorithm \cite{moller1997fast} for this test on account of the algorithm's efficiency and simplicity.
-However, because collision detection algorithms are often accompanied by non-robustness problems, a conventional implementation of the algorithm may cause unpredictable results.
-Therefore, we integrate plane-based geometry representation \cite{sugihara1990solid} into M\"{o}ller's algorithm to make it unconditionally precise and robust.
-
-\subsection{Intersection Detection}
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=3.0in]{projection}
-\caption{$Seg_1$ is the intersection between $S_2$ and $F_1$.
-$Seg_2$ is the intersection between $S_1$ and $F_2$.
-The intersection between $F_1$ and $F_2$, which is the line segment in red, is the overlap of $Seg_1$ and $Seg_2$.}
-\label{fig_projection}
-\end{figure}
-
-M\"{o}ller's algorithm computes the intersection between two triangles $F_1$ and $F_2$ in three steps, as illustrated in Fig.
-\ref{fig_projection}.
-First, an early rejection is performed by testing whether $F_1$ intersects the plane where $F_2$ lies, which is denoted as $S_2$.
-This is a necessary condition of intersection between $F_1$ and $F_2$.
-If this test is passed, then the same is performed for $F_2$ and $S_1$, where $S_1$ is the plane of $F_1$.
-Second, the intersection between $F_1$ and $S_2$, denoted as $Seg_1$, and the intersection between $F_2$ and $S_1$, denoted as $Seg_2$, are separately computed .
-At last, the intersection between $F_1$ and $F_2$ is determined by computing the overlap area of $Seg_1$ and $Seg_2$ .
-
-\begin{figure}[t]
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=3.0in]{nonrobust}\\
-  \caption{The left edges of A and B (\emph{left}) are nearly but not exactly collinear.
-However, under usual float point arithmetic, they might be judged as collinear causing discontinuous edges in the final result (\emph{right}).}\label{fig:precision}
-\end{figure}
-
-Conventional implementations of M\"{o}ller's algorithm use vertex-based representation and usual float point arithmetic.
-However, this is neither exact nor robust.
-In Fig.
-\ref{fig:precision}, we illustrate a non-robust 2D case of the Boolean operation.
-Although implementing M\"{o}ller's algorithm with arbitrary precision arithmetic could make it robust, it is too costly for a large CSG evaluation.
-Actually, the non-robustness of this algorithm is from \emph{constructions} \cite{bernstein2009fast}, which compute new coordinates of geometry objects based on the known coordinates of existing ones.
-In M\"{o}ller's algorithm, the coordinates of $Seg_1$ and $Seg_2$ (Fig.
-\ref{fig_projection}) are computed as intermediate results.
-On the other hand, if the computation can be restricted to \emph{predicates}, which make a two or three-way decision based on known coordinates, we could quickly and robustly implement this algorithm.
-
-Fortunately, according to Sugihara and Iri \cite{sugihara1990solid}, geometry computation of Boolean operations can be restricted to predicates using plane-based representation of polyhedra.
-This motivated us to integrate plane-based representation into M\"{o}ller's algorithm.
-Exact and efficient predicate computation is performed using precise geometry predicate techniques \cite{shewchuk1997adaptive}.
-Details of our implementation are shown below.
-
-\begin{figure}
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=1.7in]{p-reps}\\
-  \caption{Plane-based representation of triangles. The yellow triangle is represented by three bounding planes (green) and the supporting plane where the triangle lies.}\label{fig:p-reps}
-\end{figure}
-
-We first convert $F_1$ and $F_2$ into their respective plane-based representations: a supporting plane surrounded by three bounding planes (Fig.
-\ref{fig:p-reps}).
-We implement this conversion using the exact conversion method by Campen and Kobbelt \cite{campen2010exact}.
-Then, in our implementation, the relative position of a point and a plane can be determined by computing the sign of the multiplication of determinants \cite{sugihara1990solid}.
-To avoid introducing errors, we represent the end points of $Seg_1$ and $Seg_2$  by intersections of plane triples, rather than by directly computing their coordinates.
-As illustrated in Fig.
-\ref{fig:isect}(a), these points are the intersection between an edge line of a face and the supporting plane of the other face.
-Because the edge line of $F_1$ can be represented as $[S_1, S_X]$ (or $[S_2, S_X]$ for an edge line of $F_2$), where $S_X$ is the corresponding bounding plane of the edge, the end points of $Seg_1$ or $Seg_2$ can be represented in the form of $[S_1,S_2,S_X]$.
-In Fig.
-\ref{fig:isect}, we list all intersection situations between a triangle and a plane, and the $S_X$  in each situation.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=3.5in]{sign}
-\caption{We denote the signed distance from point $X$ to plane $S_2$ as $d_X$.
-All the four conditions of intersection between $F_1$ and $S_2$ (denoted as $Seg_1$) are:  (a) $d_A\cdot d_C<0$, $d_B\cdot d_C<0$; (b) $d_A=0$, $d_B=0$, $d_C\neq 0$; (c) $d_A=0$, $d_B\cdot d_C<0$; (d) $d_A=0$, $d_B\cdot d_C>0$.
-End points of $Seg_1$ are intersections between $S_2$ and related edge lines of $F_1$ (bold edges).}
-\label{fig:isect}
-\end{figure}
-
-The intersection between $F_1$ and $F_2$ is the overlap area of $Seg_1$ and $Seg_2$.
-It can be easily computed by comparing the end points of $Seg_1$ and $Seg_2$ along $L$ (Fig.
-\ref{fig_projection}), where $L$ is the intersection between $S_1$ and $S_2$.
-Unlike M\"{o}ller's implementation, our approach uses no projection, which requires the exact point coordinates.
-We call the direction of vector $\vec{N}_1\times \vec{N}_2$ the positive direction, where $\vec{N}_1$ and $\vec{N}_2$ are normals of $S_1$ and $S_2$ respectively.
-Given two points $A$ and $B$ on $L$,  we compute the sign of the multiplication of determinants:
-\begin{equation}
-\label{eq:sign}
-  K(A, B)=
-  \left|
-  \begin{array}{c}   %该矩阵一共3列，每一列都居中放置
-  \vec{S}_1 \\ \vec{S}_2 \\ \vec{S}_A \\ \vec{S}_B
-  \end{array}
-  \right|
-  \left|                 %左括号
-  \begin{array}{c}   %该矩阵一共3列，每一列都居中放置
-  \vec{N}_1 \\\vec{N}_2 \\\vec{N}_A
-  \end{array}
-  \right|
-  \left|                 %左括号
-  \begin{array}{c}   %该矩阵一共3列，每一列都居中放置
-  \vec{N}_1 \\\vec{N}_2 \\\vec{N}_B
-  \end{array}
-  \right|,
-\end{equation}
-where $\vec{S}_X$ is the coefficient vector of plane equation $[a_X,b_X,c_X,d_X]$,  and $ \vec{N}_X$ is the normal vector $[a_X,b_X,c_X]$.
-If $K(A, B)$ is positive (negative), this means that $A$ lies in the positive (negative) direction of $B$.
-Otherwise, $A$ and $B$ are concident.
-
-If $F_1$ and $F_2$ are coplanar, we check whether they overlap within the common plane using the algorithm by M\"{o}ller\cite{moller1997fast}.
-The substrate of this algorithm is to verify on which side of an edge $E$ a point $V$ lies.
-We implement it using plane-based geometry by substituting $E$ with its corresponding bounding plane $S_E$ and then computing the sign of distance from $V$ to $S_E$.
-
-\subsection{Intersection Recording}
-\label{sec:isecthandle}
-
-The information of intersection is stored in the intersected faces where the intersection occurs.
-Because the intersection is generated by two (or more) faces, both (all) faces are intersected faces and store the same copy of intersection information.
-
-Each intersected face maintains two important lists for further processing: \emph{cross list} and \emph{coplanar list}.
-The cross list stores the end points of intersections, the associated faces of the intersections, and the primitives to which these associated faces belong.
-The coplanar list is relatively simple.
-It only stores coplanar faces and the primitives to which these coplanar faces belong.
-
-Moreover, in order to reconstruct geometry connectivity and to avoid coincident vertices in the final model, coincident points detected during intersection computation are merged.
-A \emph{point list} for each intersected face $F$ is used for this purpose.
-The list stores all the points inside $F$ or on the boundary of $F$.
-When introducing new vertices into the face (e.g., recording the new intersection line into the cross list, the two end points of the intersection line segment are newly introduced vertices), we determine if there exists a coincident point in the point list.
-Coincident points are merged.
-In addition, because the points on the edges of $F$ are shared by adjacent faces, these points should be added to the corresponding point lists of both two adjacent faces.
-
-There is a degenerate condition for intersection recording: $F_1$ and $F_2$ may intersect on a single point.
-We treat this condition as $F_1$ and $F_2$ being non-intersecting but add the intersected point into the point lists of both faces.
-Another point to notice is that if $F_1$ and $F_2$ are coplanar and overlap, $F_1$ is added to the coplanar list of $F_2$ and vice versa.
-No new point is introduced under this condition.
-
-\section{Face Classification}
-\label{section:floodfill}
-
-In this step, we classify faces one by one to generate the final mesh.
-The intersection information computed in the previous section is used for re-tessellation and space label computation.
-To better explain our approach, we firstly introduce the background knowledge.
-Then the framework of this step is outlined.
-Afterwards, several important techniques in this step are detailed.
-
-\subsection{Background}
-\label{sec:intuitive}
-
-We firstly introduce the space labels, which comprise the basis of face membership classification.
-The space label of face $F$ with respect to primitive $M$, denoted as $L_F(M)$, is the relative location of $F$ with respect to $M$.
-Also, we use $L(M)$ to denote the space label with respect to $M$ which does not specify a face.
-In general, space label has four conditions: completely inside (\emph{In}), completely outside (\emph{Out}), on the boundary (\emph{On}) or not available (\emph{N/A}).
-In the last condition, $F$  crosses the boundary of $M$.
-Accordingly, it does not have a uniform label.
-In addition, if the normal direction of $F$ is considered, there are two derived conditions of \emph{On}: the normal points to the outside (\emph{Same}) and those to the inside (\emph{Oppo}) of $M$.
-
-The evaluation of Boolean operations between B-reps primitives $A$ and $B$ can be converted to the problem of surface selection according to the labels \cite{kuratowski1968set}:
-\begin{equation}
-\label{eq:select}
-\begin{split}
-&A\cup^*B:\{F_A~Out~B\}\cup\{F_B~Out~A\}\cup\{F_A~Same~B\},\\
-&A\cap^*B:\{F_A~In~B\}\cup\{F_B~In~A\}\cup\{F_A~Same~B\},\\
-&A-^*B:\{F_A~Out~B\}\cup\{(F_B~In~A)'\}\cup\{F_A~Oppo~B\},
-\end{split}
-\end{equation}
-
-\noindent where $F_X$ is the faces of $X$, and $F'$ means $F$ with an inverted normal.
-The stars ($^*$) after the operation notations ($\cup, \cap, -$) mean that the Boolean operations are regularized.
-
-Now, consider computing $L_F(T)$, where $T$ is a CSG solid $T$ with $n$ primitives $\{M_i~| ~i = 1,2,3,...,n\}$.
-Then there are a total of $n$ space labels for $F$: \{$L_F(M_i)~|~i = 1,2,3,...,n\}$ (or in vector form $\vec{L}_F$).
-If all elements in $\vec{L}_F$ are known and none of them is \emph{N/A}, $L_F(T)$ can be easily computed by traversing the whole CSG tree from bottom to top and progressively combining the space labels of the CSG nodes according to combination rules \cite{requicha1985boolean}:
-\begin{equation}
-\label{eq:comb}
-\begin{split}
-X\cup Out\Rightarrow X, ~~&X\cap Out\Rightarrow Out, \\
-X\cap In~~\Rightarrow X, ~~&X\cup In\Rightarrow In, \\
-X \cup X \Rightarrow X, ~~&X \cap X \Rightarrow X,\\
-Same \cup Oppo\Rightarrow In, ~~&Same \cap Oppo\Rightarrow Out,
-\end{split}
-\end{equation}
-where $X$ is an arbitrary label value.
-Note that the combination rules for difference operation are not shown here, because the difference operation can be converted into the intersection operation using De Morgan's transformations:
-\begin{equation}
-\label{eq:demo}
-\begin{split}
-A-B\Rightarrow A\cap B^c, ~~~~~~~&(A^c)^c\Rightarrow A,\\
-(A\cap B)^c\Rightarrow A^c\cup B^c, ~~&(A\cup B)^c\Rightarrow A^c\cap B^c,
-\end{split}
-\end{equation}
-where $X^c$ denotes the complement of $X$. If and only if $L_F(T) = Same$, $F$ lies on the boundary of the final model and has the correct normal; accordingly, $F$ belongs to the final result.
-
-If some elements in $\vec{L}_F$ are \emph{N/A} or cannot be computed, we may be unable to compute $L_F(T)$.
-However, the CSG tree $T$ can be trimmed into a smaller one with fewer primitives to reduce the complexity of further evaluation.
-For example, assume we have a CSG with its Boolean expression $M_1\cup (M_2\cap M_3-M_4)$.
-Given the values of two labels $L(M_1)=Out$, $L(M_2)=In$, the expression can be rewritten as $Out\cup (In\cap M_3-M_4)$.
-Using the combination rules we can simplify the expression as $M_3-M_4$.
-Thus, any face that shares the same two labels $L(M_1)$ and $L(M_2)$ can be classified based on the trimmed CSG tree $M_3-M_4$, which has only two primitives.
-
-\subsection{Face Classification Framework}
-\label{sec:framework}
-
-\begin{figure}
-\centering
-\includegraphics[width=3.5in]{multilvl}
-\caption{Illustration of multi-level face grouping framework.
-Faces are grouped into smaller groups in each level.
-The trimmed CSG tree of a specific group is obtained by trimming the tree of its parent according to common labels of this group.
-When the group is not further subdivided, faces in this group are respectively classified based on the trimmed CSG tree of this group.}
-\label{fig:hierachy}
-\end{figure}
-
-Space labels of neighboring faces are often coherent.
-That is, given two neighboring faces $F_1$ and $F_2$, $L_{F_1}(M)$ and $L_{F_2}(M)$ are often the same.
-Therefore, we can group together neighboring faces and evaluate them based on the smaller CSG tree, which is trimmed by the common labels.
-The trimmed tree contains fewer leaves, thus enabling faster computation.
-If face grouping can be efficiently performed, this strategy will greatly accelerate the process of face membership classification.
-Moreover, a multi-level grouping scheme (Fig.
-\ref{fig:hierachy}) may provide even greater capability to shared labels.
-By using such a scheme, faces are first grouped into first-level groups; then, faces of the same first-level groups are further divided into second-level groups, and so on.
-Labels are shared in each level and the original CSG tree is trimmed step by step according to common labels in each level.
-We developed this idea into a novel classification algorithm that uses a two-level grouping scheme.
-The first level is the \emph{inter-primitive} level; the second is the \emph{intra-primitive} level.
-
-Before we begin face classification, pre-computation is conducted to make the subsequent analysis easier.
-The original CSG tree is converted into a \emph{positive} tree using the method by Rossignac and Voelcker \cite{rossignac1988active}.
-`Positive' means that the CSG tree contains no difference (-) operation.
-According to Equation \ref{eq:demo}, there may be some primitives with complement notation.
-The benefit is that we are not required to consider the difference operations in the following computation.
-
-The classification starts from face grouping in the inter-primitive level.
-In this level, faces of the same primitives are simply grouped together.
-Then, we give a rough estimation of the common labels of the group.
-Suppose the group is primitive $M$.
-Its face labels with respect to primitives whose bounding boxes are totally outside of $M$'s bounding box must be $Out$ (for primitives with complement notations, $In$).
-The original CSG tree is trimmed into the first trimmed CSG tree (as short as the \emph{the first trimmed tree}) according to these common labels plus an extra label $L(M)$ whose value is obviously $Same$.
-
-After that, the inter-primitive groups are further divided into smaller intra-primitive groups.
-To explain how to perform intra-primitive grouping, we firstly introduce an essential concept---intersection primitive (IP).
-The IPs of a face $F$ is defined as the primitives that $F$ intersects, excluding the primitive to which $F$ belongs (denoted as $M$).
-Primitives (excluding $M$) that do not intersect $F$ are called non-IPs.
-The set that contains all IPs of $F$ is the IP-set of $F$.
-That set can be computed by enumerating all the primitives in the cross list and coplanar list of $F$.
-
-Now, we require that the faces of the same intra-primitive group meet two requirements: they should be connected together and have the same IP-set.
-These two requirements give these faces very good properties, as discussed in Proposition 1.
-The labels referenced in Proposition 1 are used to trim the first trimmed tree into the second trimmed CSG tree (as short as \emph{the second trimmed tree}).
-For a specific intra-primitive group, the primitives of its second trimmed tree is a subset of the common IP-set of that group.
-This is because all space labels with respect to non-IPs are shared within the intra-primitive group and all these labels are either $In$ or $Out$.
-Therefore, all non-IPs must have been trimmed from the CSG tree (to be explained in Section \ref{sec:trim}).
-
-\vspace{0.8em}
-\noindent \textbf{Proposition 1.}~~~~If a group of faces are connected together and they have the same IP-set, they must share the same labels with respect to all non-IPs.
-These labels are either \emph{In} or \emph{Out}.
-
-\vspace{0.6em}
-\noindent \textbf{Proof.}~~~~We only prove that the conclusion stands for adjacent faces, which is a special case of connected faces.
-Promoting the conclusion to the general situation is obvious.
-Assume $M$ is a non-IP and label $L(M)$ is different for the two adjacent faces $A$ and $B$ .
-Then there must be faces from $M$ between $A$ and $B$ to cause the different space labels.
-Additionally,  because $A$ and $B$ are adjacent, at least one of $A$ and $B$ intersects the faces from primitive $M$.
-This contradicts the assumption that $M$ is non-IP.
-Therefore, $L(M)$ must be the same for $A$ and $B$.
-Moreover, because $M$  is non-IP, $L(M)$ is either \emph{In} or \emph{Out}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=3.5in]{mesh}\\
-  \caption{A snapshot during flood filling (\emph{left}), and the final grouping result (\emph{right}).
-Different intra-primitive groups are distinguished by different colors.
-From the final grouping result, the whole mesh is divided into 9 intra-primitive groups.}\label{fig:mesh}
-\end{figure}
-
-\vspace{1.0em}
-Because faces of the same intra-primitive group are connected together, we can efficiently group them using a flood filling algorithm.
-When visiting a face, its space label vector is instantly computed and its classification is performed.
-Our intra-level grouping is performed as follows:
-\begin{itemize}[leftmargin=0.45cm]
-\item[1)]{\textbf{First seed generation.}}~A triangle face $F_{S0}$ is randomly chosen as the first seed (e.g., the red triangle in Fig.
-\ref{fig:mesh}).
-Labels of $F_{S0}$ with respect to non-IPs are determined by using $F_{S0}$'s barycenter as the sample point, through a ray-shooting algorithm \cite{havran1999summary} and by employing our octree as a spatial search structure \cite{frisken2002simple} to speed up.
-Note that because the original CSG tree is trimmed into the first trimmed tree, we only compute labels with respect to primitives within that first trimmed tree.
-\item[2)]{\textbf{Label propagation.}}~Once there is a seed $F_S$ with $L_{F_S}$ with respect to all non-IPs, we define the intra-primitive group $G_S$ as follows.
-All faces that belong to $G_S$ should have the same IP-set as $F_S$.
-The common labels of $G_S$ are $L_{F_S}$ with respect to all non-IPs.
-The first trimmed tree is trimmed into the second trimmed tree according to these common labels.
-Breadth-first flood filling is used to find all faces that belong to $G_S$.
-When visiting a face, we first check if it has the same IP-set as the seed.
-If so, set membership classification is performed based on the second trimmed tree of $G_S$ (detailed in Section \ref{section:setmemcls}).
-Otherwise, it is pushed into a candidate list for Step 3 (e.g., the black faces in Fig.
-\ref{fig:mesh} (left)).
- \item[3)]{\textbf{Secondary seed generation.}}~When the flood filling ends, which means no more faces belong to the current face group, a new seed is picked from the candidate list (e.g., the stippled faces in Fig.
-\ref{fig:mesh}).
-Then a new group is defined by the new seed and the labels with respect to non-IPs of the new seed are computed (details in Section \ref{sec:secondseed}).
-After that, Step 2 is repeated according to the newly defined group, until that candidate list is empty, indicating all faces of $M$ are classified.
- \end{itemize}
-
-The face membership classification of the whole CSG is accomplished by performing the above process for each primitive.
-Procedure \ref{code:floodfill} shows the framework as pseudo-code.
-To avoid repetitive visits during flood filling, we use an extra flag for each face to record its visiting status.
-
-\begin{algorithm}[!ht]
-\caption{FaceClassification(PrimitiveList, PosTree)}
-\label{code:floodfill}
-    \begin{algorithmic}[1]
-    \FOR {each $M_i$ in $PrimitiveList$}
-    \STATE Get common labels $CL^1$ of $M_i$;
-    \STATE Trim $PosTree$ into $TrimTree1$ by $CL^1$;
-    \STATE Select the first seed $F_0$ from $M_i$;
-    \STATE Put $F_0$ into $CandidateList$;
-    \WHILE {$CandidateList$ is not empty}
-    	\STATE Pick a seed $F_S$;
-        \STATE Define group $G_S$, where $F_S\in G_S$;
-        \STATE Compute the common labels of $F_S$, denoted as $CL^2$;
-        \STATE Trim $TrimTree1$ into $TrimTree2$ according to $CL^2$;
-    	\STATE Put $F_S$ into $FloodFillQueue$;
-    	\WHILE {$FloodFillQueue$ is not empty}
-    		\STATE Get the next face $F_i$ from $FloodFillQueue$;
-    		\STATE Do set membership classification of $F_i$ based on $TrimTree2$;
-    		\FOR {each adjacent face $F_{Neighbor}$}
-    			\IF {$F_{Neighbor}$ belongs to $G_s$}
-    				\STATE Put $F_{Neighbor}$ into $FloodFillQueue$;
-    			\ELSE
-                    \STATE Put $F_{Neighbor}$ into $CandidateList$;
-    			\ENDIF
-    		\ENDFOR
-    	\ENDWHILE
-    \ENDWHILE
-    \ENDFOR
-    \end{algorithmic}
-\end{algorithm}
-
-\subsection{Trimming CSG Tree}
-\label{sec:trim}
-
-Trimming a CSG (binary) tree with the $In$ or $Out$ label is relatively simple.
-According to the first two lines of Equation \ref{eq:comb}, given a primitive $M$, if $L(M)$ is $In$ ($Out$), the label of $M$'s parent node is either $In$ ($Out$) or the value of its sibling.
-In either condition, the node representing $M$ can be trimmed from the tree.
-
-However, when trimming the original tree into the first trimmed tree for a specific inter-primitive group, a special label, $Same$, exists.
-This label means that the faces of the group are on the boundary of the primitive to which they belong, which is absolutely correct.
-This label is not easy to process because we cannot determine the label of its parent node unless we know the label of its sibling.
-Unfortunately, during tree trimming, the labels we have are incomplete.
-We may have to leave the $Same$ label unprocessed and wait for further information.
-This incurs considerable computation burden to check this special condition and makes the trimming algorithm inefficient.
-To solve the problems, we developed a new representation of the CSG tree, called CSGlist, to minimize the side effect of the special $Same$ label and enable early rejection of face groups that do not belong to the final model of the CSG.
-
-Given a face group from primitive $M$, we construct the CSGlist as follows.
-We cut the original CSG tree into a set of subtrees along the \emph{critical path}, which is the path from $M$ to the root (e.g., when $M=D$, the construction of CSGlist is shown in Fig.
-\ref{fig_trim}).
-Obviously, none of the subtrees contains the primitive $M$.
-Each subtree of CSGlist is associated with `desired' label values.
-That is, if the labels with respect to all subtrees meet their corresponding desired values respectively, the labels with respect to the original CSG tree is $Same$.
-On the contrary, if the labels with respect to any subtree are not desired, the labels with respect to the whole CSG tree is not $Same$; thus the related face group should be dropped.
-The desired value of a subtree is determined based on how the subtree connects to the critical path.
-According to the face selection rules (Equation \ref{eq:select}), if the subtree connects to a Union ($\cup$) node, then the desired value is $In$; otherwise, the desired value is $Out$.
-In addition, suppose the primitive $A$ in Equation \ref{eq:select} is the left child.
-Then if the subtree is in the left child of its parent node, $Same$ is also desired.
-
-Conversion to CSGlist is performed before the first trimming.
-After that, all the labels we use for CSG tree trimming are either $In$ or $Out$.
-Both the first and the second trimmed trees are represented by CSGlists.
-The subtrees of the CSGlist can be easily trimmed (since there is only $In$ and $Out$ labels) and their desired values are used to enable early rejection.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3.0in]{csgtree}
-\caption{Convert CSG tree into a CSGlist along the critical path (marked by the arrow) from primitive $D$ to the root.
-The CSGlist contain three subtrees.
-Each subtree has its desired label value.
-Subtree 1: $Out$ or $Same$.
-Subtree 2: $In$ or $Same$.
-Subtree 3: $Out$.}
-\label{fig_trim}
-\end{figure}
-
-\subsection{Classifying a Single Face}
-\label{section:setmemcls}
-
-If a face is non-intersected, the second trimmed tree will have single value, which can be used to determine whether the face is accepted.
-However, if it is an intersected face, further processing is needed.
-
-Intersected faces usually cannot be classified as a whole.
-They have to be tessellated into smaller non-intersected triangles, each of which is classified respectively.
-Robustness and efficiency are our main consideration.
-For these purposes, we nest the exact BSP structure \cite{bernstein2009fast, campen2010exact} into the intersected faces.
-We classify intersected face $F$ as follows.
-
-\vspace{0.5em}
-\noindent \textbf{Valid-IPs \& Pseudo-IPs}~~~~
-IPs of an intersected face are firstly divided into two types according to whether the IPs are in the second trimmed tree.
-The IP that is the primitive of the second trimmed tree is called the valid intersection primitive (valid-IP).
-Otherwise, it is called the pseudo-intersection primitive (pseudo-IP).
-Pseudo-IPs intersect the face; however, the labels with respect to pseudo-IPs do not affect the classification of $F$.
-In other words, the intersections of pseudo-IPs are not edges of the final models, as illustrated in Fig.
-\ref{fig:invalidcross}.
-Thus, we simply omit these pseudo-intersections during classification.
-This filtering stage saves computation time by avoiding unnecessary splitting of faces.
-An extreme instance is that there is no valid-IP.
-For this condition, the face is processed in the same way as a non-intersected face.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3.2in]{invalid-cross}
-\caption{2D illustration of pseudo-intersection. The vertices in red do not appear in the final model. They are so called pseudo-intersection vertices (line segments in the 3D case).}
-\label{fig:invalidcross}
-\end{figure}
-
-\vspace{0.5em}
-\noindent \textbf{Tessellation}~~~~
-In this step, $F$ is divided into a set of sub-triangles using the intersections recorded in Section \ref{section:isect}.
-Because constrained Delaunay triangulation (CDT) \cite{chew1989constrained} has good topology characteristics, we convert the tessellation into a problem of CDT.
-The zone of CDT is $F$, and the constraints are all the intersections by valid-IPs.
-The constraints ensure that no sub-triangles will cross these intersection lines.
-Because CDT in our method is a vertex-based 2D problem, the 3D coordinates computed by their plane-based representation are projected on a 2D space, which is the axis-aligned plane where the area of $F$ is maximized.
-
-It should be noted that intersections from different valid-IPs may intersect (Fig.
-\ref{fig:cdt}(c)).
-Omitting these intersection points may cause false results of CDT.
-To obtain the correct constraints, intersections from different valid-IPs are tested to determine whether they intersect.
-We implement this test again using plane-based geometry for robustness.
-As we know this kind of special intersection is actually the cross point of the three faces: $F$,  and the two associated intersected faces from the valid-IPs (Fig.
-\ref{fig:cdt}(d)).
-Therefore, such a point can be represented by the three supporting planes of the three faces.
-We determine whether the cross point exists by testing if the point is inside all three of these faces.
-By adopting the routine of the relative position of a point to a plane \cite{sugihara1990solid}, this test is robust and efficient.
-If the cross point of different intersection lines is detected, these lines are split by the cross point and the constrains of CDT are updated accordingly.
-Moreover, because the cross point is actually shared by the three faces, it is added to the point lists (Section \ref{sec:isecthandle}) of all three of these faces.
-
-\begin{figure}
-\centering
-\includegraphics[width=3.5in]{cdt}
-\caption{We classify the face $F$ from primitive $M$: (a) faces of $M_1$ (yellow) that intersect $F$.
-BSP of $M_1$ is constructed according to these.
-(b) Faces of $M_2$ (green) that intersect $F$.
-BSP of $M_2$ is constructed according to them.
-(c) If $M_1$ and $M_2$ are the only valid-IPs of $F$, then triangulation can be performed according to intersection lines recorded in the cross list.
-The red area shows a possible result of sub-triangle classification.
-Note that there are intersections between lines from different primitives (marked as red stars), which are (d) intersections of three faces each from different primitives.}
-\label{fig:cdt}
-\end{figure}
-
-\noindent \textbf{Classification of sub-triangles}~~~~
-An intersected face $F$ is divided by faces from each valid-IPs into $In$ cells, $Out$ cells and $On$ cells (Figs.
-\ref{fig:isect}(a) and (b)).
-The BSP tree \cite{naylor1990merging} is very suitable for describing such partitions.
-The labels of sub-triangles can be efficiently computed according to a BSP representation using the BSP-based point-in-polyhedra test \cite{gordon1991front, fuchs80visible, james1999binary}.
-Details are discussed as follows.
-
-Given a valid-IP, denoted as $M$, we firstly build a BSP tree nested within $F$ according to the intersections between $F$ and $M$.
-This is a 2D partition problem.
-Nevertheless, constructing BSP in 2D space of $F$ will introduce errors on account of the involved conversion from plane triples (plane-based representation) into 2D coordinates.
-Therefore, it is better to construct the BSP tree in 3D space.
-If we limit the space of the BSP construction zone within the face $F$ with tiny thickness, denoted as $P_F$, it is obvious that all faces from $M$ that intersect $P_F$ are recorded in the cross list and the coplanar list of $F$.
-These faces give the correct space partition on $P_F$.
-We construct the 3D BSP tree according to the intersected faces.
-The construction of the BSP tree is implemented using an exact plane-based algorithm proposed by Berstein and Fussell \cite{bernstein2009fast}.
-Now, given a sub-triangle $SF$, the label $L_{SF}(M)$ is then computed based on the classification results of the three corners of $SF$ according to the constructed BSP.
-If all three classification results are $On$, then $L_{SF}(M)$ is either $Same$ or $Oppo$.
-If any classification of the corners is not $On$, $L_{SF}(M)$  is the same as the non-$On$ classification .
-
-After all space labels of a sub-triangle are computed, we judge whether the sub-triangle belongs to the final model based on the second trimmed tree represented as CSGlist.
-The subtrees in CSGlist are evaluated using the combination rules of labels.
-The sub-triangle is accepted if and only if the evaluation results of all subtrees are desired.
-We might accelerate this step if the coplanar list of $F $is empty or the faces in the coplanar list are all from pseudo-IPs.
-In this case, the labels with respect to valid-IPs are either $In$ or $Out$, and each subtree of CSGlist can be efficiently evaluated using Blist, which was proposed by Hable and Rossignac \cite{hable2005blister}.
-For CSG models in which the coplanar cases are rare, this acceleration saves considerable computation time.
-
-\subsection{Secondary Seeds Generation}
-
-\begin{figure}
-  \centering
-  % Requires \usepackage{graphicx}
-  \includegraphics[width=2.0in]{sgen}\\
-  \caption{$F_x$ is the secondary seed, and $F_c$ is its associated face.
-The labels of $F_x$ with respect to primitives that intersect $F_c$ but do not intersect $F_x$ (e.g., the yellow intersection) can be computed using any point in $E_{x,c}$ as the sample.
-The labels of $F_x$ with respect to primitives that intersect neither $F_x$ nor $F_c$ are the same for both faces.
-Line segments of different colors are intersection lines by different primitives.}\label{fig:sgen}
-\end{figure}
-
-\label{sec:secondseed}
-
-As discussed in Section \ref{sec:framework}, during flood filling, faces belonging to the group of the current seed are classified according to the second trimmed tree of this group.
-The rest are added to a candidate list for generating secondary seeds when no more faces belong to the group of the current seed.
-The main task of secondary seed generation is to compute the space labels with respect to non-IPs of the new seeds.
-
-A straightforward scheme is to use the same approach as the first seed generation in Section \ref{sec:framework}.
-However, this scheme requires  recalculating all the space labels with respect to non-IPs using the time-consuming ray-shooting method.
-For complex CSG evaluation, in which secondary seed generation is frequently requested , we need a more efficient solution.
-Again, we use the information of neighboring faces to accelerate this process.
-When a face $F_x$ is added to the candidate list, we associate the following data with $F_x$: the face $F_c$ that is currently being visited (therefore $F_x$'s neighbor; see Fig.
-\ref{fig:sgen}) and the labels of $F_c$ with respect to $F_c$'s non-IPs.
-Note that the non-IP set of $F_x$, denoted as $C_x$, is different from that of $F_c$, denoted as $C_c$.
-
-Now, if $F_x$ is selected as a new secondary seed, we can compute the labels with respect to non-IPs of $F_x$ in two complementary ways: we can directly inherit from the labels of $F_c$, or represent $F_x$ with a point within $F_c$ and compute the label of this point using the BSP technique presented in Section \ref{section:setmemcls}.
-The former is used for the computation of the labels with respect to the primitives that are in $C_c\cap C_x$.
-The labels with respect to these primitives are the same for both $F_x$ and $F_c$.
-The latter is used for computing the labels with respect to the remaining of primitives (e.g., those in $C_c\setminus C_x$).
-According to Proposition 2, the sample point of $F_x$ can be chosen as any point in the common edge of $F_x$ and $F_c$, denoted as $E_{x,c}$.
-For robustness, we use one of the end points of $E_{x,c}$ as the sample point because we have its exact plane-based representation.
-
-\vspace{+1.0em}
-\noindent \textbf{Proposition 2.}~~~~Given two adjacent faces $F_c$ and $F_x$, the labels with respect to primitive $M$ for $F_x$ is the same as the classification result of any point on the common edge of $F_x$ and $F_c$ in the BSP tree of $M$ for $F_c$ (constructed in Section \ref{section:setmemcls}), if $M$ is in the IP-set of $F_c$ but not in the IP-set of $F_x$.
-\vspace{+0.5em}
-
-\noindent \textbf{Proof.}~~~~We know $M$ is not in the IP-set of $F_x$; therefore, it is obvious that all points on $F_x$ have the same labels with respect to $M$.
-Because the points on the common edge of $F_x$ and $F_c$ are in $F_x$, they have the same labels.
-\vspace{+1.0em}
-
-\section{Experiments and Discussion}
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3.2in]{raster}
-\caption{\emph{Cube} $\cup$ \emph{Sphere1} $\cap$ \emph{Sphere2}: our method resulted in simpler mesh connectivity than the method by Campen and Kobbelt \cite{campen2010exact}.}
-\label{fig:raster}
-\end{figure}
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=3.5in]{budda}
-\caption{Boolean operations on model \emph{Budda}: (a) two \emph{Buddas}, (b) results of \emph{Budda} $\cap$ \emph{Budda}, and (c) the incorrect result of \emph{Budda} $\cap$ \emph{Budda} generated by non-robust implementation of Feito et al.'s method \cite{feito2013fast}.}
-\label{fig:budda}
-\end{figure}
-
-\begin{figure*}[!t]
-\centering
-\includegraphics[width=7in]{models2}
-\caption{(a) Boolean operations between a \emph{Ring} and a set of \emph{Spheres}.
-$\langle 1\rangle$ after 200 operations.
-$\langle 2\rangle$ after 800 operations.
-(b) Union of \emph{Armadillo} and six \emph{Spoons}.
-(c) \emph{Head} - \emph{Cuboid} + \emph{LeftBrain} + \emph{RightBrain}.
-(d) Difference a \emph{BigCylinder} and 28 \emph{SmallCylinders}.
-(e) \emph{Man} $\cup$ \emph{Horse}.
-(f) \emph{Dragon} - \emph{Bunny}.
-(g) \emph{Palate} $\cup$ \emph{Mandible} $\cup$ (20 \emph{Teeth}).}
-\label{fig:models}
-\end{figure*}
-
-\begin{table*}[ht]
-\caption{Computation Time Statistics (Seconds)}
-\label{tab:performance}
-\centering
-\begin{tabular}{*{13}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
-\hline
-\multirow{2}{*}{No.} & \multirow{2}{*}{Figure} & \multicolumn{3}{c|}{Face Num.$^\nabla$} & \multirow{2}{*}{\tabincell{c}{Primitive\\Num.}} & \multirow{2}{*}{\tabincell{c}{CGAL \\ \cite{cgal:hk-bonp3-15a}}} & \multirow{2}{*}{\tabincell{c}{Maya \\ \cite{Maya2015}}} & \multirow{2}{*}{\tabincell{c}{Campen \\ \cite{campen2010exact}}} & \multirow{2}{*}{\tabincell{c}{Feito \\ \cite{feito2013fast}}}& \multicolumn{4}{c}{Our Approach}\\
-\cline{3-5} \cline{11-14}
- & & Total & Min & Max &&&&&& Total$^\circ$ & Step 1 & Step 2 & Step 3\\
-\hline \hline
-1 & \ref{fig:models}(a) & 37.6K & 180 & 1.6K & 201 & 1350 & 49.9 & TLE$^{\dag}$ & 15.9 & \textbf{3.13}  & 0.328 & 1.69 & 0.922 \\
-2 & \ref{fig:models}(a) & 146K & 180 & 1.6K & 801  & TLE & 1400 & TLE & Fail* & \textbf{12.8}  & 1.36 & 6.41 & 4.00 \\
-3 & \ref{fig:models}(b) & 377K & 2.56K & 346K & 7 & TLE & 224.5 & 45.7 & 11.7 & \textbf{1.44} & 0.438 & 0.062 & 0.563 \\
-4 & \ref{fig:models}(c) & 79.2K & 12 & 38.2K & 4  & 97.6 & Fail & 3.58 & 1.69 & \textbf{0.563}  & 0.187 & 0.141 & 0.172 \\
-5 & \ref{fig:models}(d) & 36K & 800 & 2.4K & 29 & 34.1 & 7.03 & 18.7 & 4.05 & \textbf{0.313} & 0.094 & 0.094 & 0.081 \\
-6 & \ref{fig:models}(e) & 597K & 96.9K & 500K & 2 & TLE & 38.3 & 26.4 & 5.63 & \textbf{2.13} & 0.563 & 0.031 & 0.984 \\
-7 & \ref{fig:models}(f) & 170K & 69.7K & 100K & 2  & 218 & 7.45 & 13.8 & 2.39 & \textbf{0.891} & 0.328 & 0.125 & 0.266 \\
-8 & \ref{fig:models}(g) & 362K & 6.91K & 276K & 22 & TLE & 344 & 256 & 19.2 & \textbf{1.80} & 0.766 & 0.172 & 0.593 \\
-9 & \ref{fig:budda} & 2.16M & 1.08M & 1.08M & 2 & Fail & Fail & MLE$^\bullet$ & Fail & \textbf{11.3} & 5.55 & 1.36 & 3.01 \\
-\hline
-\end{tabular}
-\begin{flushleft}
-$^{\nabla}$~~\emph{Min} (\emph{Max}) means the minimum (maximum) number of faces of a single primitive.
-
-$^{\circ}$~~The total computation time of our method includes the construction of half-edge structure and the three steps in Section \ref{sec:overview}.
-
-* ~~\emph{Fail} means nothing was returned, or we received the wrong evaluation results from the programs.
-
-$^{\dag}$~~\emph{TLE} means the processing time was more than  2,000 s.
-
-$^\bullet$~~\emph{MLE} denotes that the program was out of memory. The memory limit for our implementation of Campen et al.'s approach was around 1.2GB.
-
-\end{flushleft}
-\end{table*}
-
-\begin{table}
-\caption{Number of Primitives and Computation Time (Seconds)}
-\label{tab:linear}
-\centering
-\begin{tabular}{*{4}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
-\hline
-Number of Spheres & ~~100~~ & ~~200~~ & ~~300~~ & ~~400~~ \\
-\hline
-\hline
-Our Approach & \textbf{1.38} & \textbf{2.89} & \textbf{4.39 }& \textbf{5.97} \\
-Maya \cite{Maya2015} & 17.4 & 53.4 & 124 & 241 \\
-CGAL \cite{cgal:hk-bonp3-15a} & 439 & 1350 & - & -\\
-Feito \cite{feito2013fast} & 5.20 & 15.9 & 30.4 & -\\
-\hline
-\hline
-Number of Spheres  & 500 & 600 & 700 & 800 \\
-\hline
-\hline
-Our Approach & \textbf{7.90} & \textbf{9.49} & \textbf{11.0} & \textbf{12.8}\\
-Maya \cite{Maya2015} & 407 & 628 & 966 & 1400\\
-CGAL \cite{cgal:hk-bonp3-15a}& - & - & - & -\\
-Feito \cite{feito2013fast}& - & - & - & -\\
-\hline
-\end{tabular}
-\begin{flushleft}
-*~~This table was the computation time of the evaluation for Fig. \ref{fig:models} (a).
-\end{flushleft}
-\end{table}
-
-\iffalse
-\begin{table}
-\caption{Relations between Number of Operations and Computation Time (Millie Second)}
-\label{tab:subdivide}
-\centering
-\begin{tabular}{*{4}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
-\hline
-~~Face Number~~ & Step 1 & Step 2 & Step 3 & ~Total~ \\
-\hline
-\hline
-~~1.7K~~ & 6 & 12 & 15 & 37\\
-~~16K~~ & 50 & 37 & 51 & 153\\
-~~140K~~ & 302 & 121 & 249 & 790\\
-~~1300K~~ & 2006 & 372& 1508 & 4902\\
-\hline
-\end{tabular}
-\begin{flushleft}
-\end{flushleft}
-\end{table}
-\fi
-
-We implemented the proposed method in C++ and tested a series of examples with numerous primitives and/or faces on a consumer laptop with an Intel i5-4200D processor at 1.5GHz and with 8 GB of RAM.
-The OpenMesh library \cite{OpenMesh} is used for storing triangle meshes and supporting the query of neighboring faces.
-Tessellation of critical triangles is performed by constrained Delaunay triangulation using the Fade2D library \cite{Fade2D}.
-
-We compared four state-of-the-art Boolean evaluation techniques, including CGAL \cite{cgal:hk-bonp3-15a}, Maya 2015 \cite{Maya2015}, the method proposed by Campen and Kobbelt \cite{campen2010exact}, and the approach proposed by Feito et al.
-\cite{feito2013fast}.
-The latter two methods used localized schemes.
-Table \ref{tab:performance} shows the comparison in terms of computing time.
-It can be easily to seen that our approach was efficient in all these examples.
-Feito et al.'s method had performance relatively similar to ours for the examples with a  single Boolean operation (Examples 6, 7).
-This is because both the approaches use a face-based grouping scheme to accelerate face membership classification; thus have similar pipelines for single Boolean operations.
-However, when the number of primitives grows, the advantage of our non-incremental CSG evaluation approach becomes more obvious.
-In the examples of more than two primitives, our method is much faster than any other methods.
-In particular, our method worked out example 2 which consisted of 801 primitives, in 15 s, which was more than 100 times faster than the Boolean evaluation in Maya.
-
-Among the three main steps of our approach, the first step of the octree construction is a typical $O(n~log~n)$ algorithm, where $n$ is the total number of faces in the CSG.
-The second step of intersection computation is only performed within critical octree cells.
-The number of critical cells is often linear to the number of intersected faces $k$ (often an $O(\sqrt{n})$ number) in the CSG.
-Therefore, the computation complexity of the second step is almost $O(k)$.
-The condition of the third step of face membership classification is more complex.
-Although the flood filling algorithm used for intra-primitive grouping is $O(n)$ complex, classifying an intersected faces could consume much more time than classifying a non-intersected faces.
-Therefore, if we assume classifying an intersected faces spends $\theta$ times of computation time to classify a non-intersected face, we may generalize the time complexity of this step as $O(n+\theta\cdot k)$.
-When $k/n$ is constant, the third step is $O(n)$ complex.
-
-To further validate that our approach is efficient for non-incremental CSG evaluation, we analyzed how the computation time changes with respect to the number of primitives.
-Table \ref{tab:linear} shows the evaluation time for Fig.
-\ref{fig:models} (a), which was a CSG consisting of a ring and hundreds of identical spheres.
-We changed the number of spheres from 100 to 800 and recorded the evaluation times.
-In this condition, the $k/n$ was relatively constant, and as there are many intersected faces, the bottleneck lies in Step 2 and Step 3.
-The result shows that the computation time of our algorithm had a linear behavior, which conforms to our previous discussion.
-The computation time of other incremental approaches rapidly increased when the number of primitives increased, sometimes showing an $O(n^2)$ behavior.
-This is because for those approaches, as more spheres were added to or subtracted from the ring, the mesh of the ring became more complex, which made it more difficult to perform subsequent Boolean operations.
-
-One possible problem of a non-incremental CSG evaluation approach is memory inefficiency.
-Unlike incremental ones, non-incremental approaches (including ours) often require loading all the primitives into the memory before the evaluation.
-Fortunately, our approach does not significantly suffer from such a problem.
-Our implementation only constructs an octree, which needs typically an $O(n~log~n)$ size data structure, and some auxiliary information of intersected faces, which is usually $O(k)$ size.
-According to our experiment, our approach performed full evaluations in Table \ref{tab:performance} with less than 600MB.
-On the contrary, some incremental approaches can be very memory inefficient.
-For instance, in the evaluation of Example 6, CGAL consumed more than 6 GB of memory.
-Furthermore, in the evaluation of Example 2, which contained only 146 K faces, Maya 2015 used at least 5 GB of memory.
-
-Our method is robust and could correctly evaluate all the examples in Table \ref{tab:performance}.
-On the other hand, it is evident that the commercial software Maya could not even correctly evaluate Example 4, which contained only 38.6 k faces and four primitives.
-CGAL gave warnings when evaluating Example 9 and finally terminated without offering a result.
-Our implementation of Feito et al's method gave an incorrect result for Example 9 (Fig.
-\ref{fig:budda}(c)) and a result rife with small holes for Example 2.
-
-Topology simplicity is another significant characteristic of the quality of CSG evaluation.
-As shown in Fig.
-\ref{fig:raster}, our method led to less triangles to represent the final model than Campen et al.'s method without stages for surface merging.
-A simpler topology is preferred because it is easier to process.
-In fact, we found that it was owing to such inefficient tessellation that Campen et al.'s method took so long time to evaluate Examples 1 and 2.
-After hundreds of Boolean operations, the resulting surface became so fragmented that it could take tens of seconds to perform a single Boolean operation.
-
-\noindent \textbf{Limitations \& Future work}~~~~
-The major limitation of our method is that it is not unconditionally robust.
-Because the tessellation of intersected faces is performed using vertex-based representation, the computed vertex coordinates may shift from their real location, which may lead to incorrect tessellation in theory.
-From our tests, we have not found the visible failures caused by this problem, because that the coordinate errors in most cases are small without visible incorrect tessellation,  we will investigate to integrate plane-based geometry computation into intersected face tessellation in the future work.
-
-\section{Conclusion}
-In this paper, we proposed a novel method to evaluate CSG with triangular mesh primitives.
-It is able to efficiently perform non-incremental evaluation of large CSG with massive faces.
-The key idea of our approach is to use the local coherence of face space labels to accelerate face membership classification.
-A two-level grouping framework is developed to group neighboring faces together and thus space labels can be shared within each group.
-This scheme saves much time for space label computation, which is often very time-consuming for conventional Boolean evaluation algorithms.
-Additionally, in order to be robust, plane-based geometry computation is introduced into the intersection computation step of our approach.
-Experiments have verified the proposed approach is more efficient than the state-of-the-art techniques while retaining robustness and stability.
-We will further investigate the robust tessellation in future.
+\input{tex/intro}
+\input{tex/overview}
+\input{tex/inter}
+\input{tex/tess}
+\input{tex/class}
+\input{tex/exp}
 

### 2017-01-18 tex/intro.tex
before delete plane based implementation itemize

\IEEEtitleabstractindextext{
\begin{abstract}
  Constructive solid geometry (CSG) is widely used in computer aided design and manufacturing. However, boolean algorithms, which compute the boundary representations of CSG, have suffered from robustness and efficiency problems for more than three decades. We propose a fast and robust boolean operation method which is unconditionally robust for valid solids. Previously reported boolean methods using plane-based representations (P-reps) of polyhedrons are robust, but inefficient. Conversely, methods based on vertex-based representations (V-reps) are fast but not robust, unless exact arithmetic is applied. We choose to combine P-reps with V-reps, which allowed us to use the advantages of both. Our method uses V-reps for efficiency and uses P-reps to ensure robustness. Comparison experiments with the state-of-the-art show that our method is unconditionally robust, and similarly efficient to existing non-robust methods.
\end{abstract}

\begin{IEEEkeywords}
boolean operations, CSG evaluation, plane-based geometry
\end{IEEEkeywords}

}

\maketitle

\IEEEdisplaynontitleabstractindextext
\IEEEpeerreviewmaketitle

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{C}{onstructive} solid geometry (CSG) has long been a popular modeling tool for computer-aided design and computer-aided manufacturing (CAD / CAM). Complex models are constructed by combining primitives using regularized boolean operations \cite{requicha1977mathematical,tilove1980closure}: union, intersection, and difference. A CSG can be converted into the boundary representation (B-rep) through boolean algorithms. There are two major types of boolean algorithms, which vary according to how they deal with intersections between primitives. Approximate methods \cite{wang2011approximate,pavic2010hybrid,biermann2001approximate} rediscretize the intersection areas, fit vertices approximatively, and rearrange the topology. Conversely, exact methods \cite{ogayar2015deferred,douze2015quickcsg,zhou2016mesh} do not change vertex positions, and maintain as many input elements (such as faces, vertices, and topology) as possible. In many applications, exact methods are preferred for their accuracy. Additionally, the clear mapping between the surfaces of the input and output meshes in exact methods simplifies the inheritance of surface information, such as face colors and materials.

However, there is always a compromise between robustness and efficiency for exact boolean algorithms.
Robust methods often require exact arithmetics \cite{barki2015exact,zhou2016mesh}, which is significantly slower than normal floating point arithmetic.
Other methods only offer \textbf{quasi-robust} \cite{shewchuk1999lecture} implementations by using unreliable techniques, such as epsilon-tweaking \cite{laidlaw1986constructive,feito2013fast,segal1990using} and numerical pertubation on coordinates \cite{douze2015quickcsg}.
Recently, robust methods have been developed \cite{bernstein2009fast,campen2010exact} based on binary space partition (BSP) merging routines \cite{naylor1990merging,thibault1987set}.
The robustness of these methods are guaranteed by the theorem of Sugihara and Iri \cite{sugihara1990solid} that boolean operations can be performed without \textbf{constructions} \cite{shewchuk1999lecture} if polyhedrons are represented based on planes instead of vertices.
By only use \textbf{predicates}, implementations of boolean operations are easier to be robust.
These BSP-based methods are generally faster than other boolean algorithms using exact arithmetics. However, they still suffer from performance issues because of the complex conversions between vertex-based representations (V-reps) and plane-based representations (P-reps). In addition, the incoherence between V-reps and P-reps requires that extra steps to reconstruct connectivity, leading to complex implementations and worse performance.

Inspired by these previous studies, we have developed a robust boolean operation method, which is unconditionally robust given consistent input, and as fast as non-robust methods. In our method, we combine P-reps with V-reps, forming hybrid representations of meshes. To ensure robustness, we avoid constructions throughout our method, and only performing exact predicates. Numerical filters \cite{shewchuk1997adaptive} are applied to guarantee performance. Generally, the V-reps information is used for coarse tests and efficient neighboring face queries, while P-reps information is used for exact predicates.

Our method is different from the previous BSP-based methods \cite{bernstein2009fast,campen2010exact}.
While their methods are largely based on BSP theorem of \cite{naylor1990merging,thibault1987set}, our method is more like V-reps methods such as \cite{feito2013fast,zhou2016mesh} and is significantly faster. Our method is not a simple improvement of V-reps methods, but an efficient and systematical solution for robustness of boolean operations. During intersection computation, we encode the triangle intersections into sets of planes, and then use these planes to determine exact tessellations. Subsequently, we classify each face in the tessellated meshes using local binary space partition (BSP) trees, which also compliment the P-reps to guarantee exactness. In addition, while most existing boolean operations can only process two meshes, our method is varadic \cite{zhou2016mesh}, which can evaluate arbitrary inputs immediately. Thus, our method may reduces computation time in large cases by avoiding repetitive operations. Experiments have shown that our method is much faster than existing robust methods, and only around two times slower than non-robust exact methods.

%Because computations based on P-reps are slower, we develop a set of algorithms

\section{Related Work}

Boolean operations have been researched since their inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}. Existing methods can be put into two categories: exact methods and approximate methods. Exact methods retain vertex positions, and the topology of the inputs is preserved as much as possible. The coordinates of intersection points between input meshes are computed by input configurations. However, the coordinates cannot be represented exactly using fixed-precision floating point numbers, hence robustness is a significant problem. Conversely, approximate methods rediscretize the input mesh surfaces using techniques such as voxels, octrees, and Layered Depth Images (LDI). These methods generally have better performance and robustness than exact methods, but the loss of precision and geometry information is inevitable. In this section, we first introduce previous work of these two categories, and then discuss plane-based boolean algorithms, which have close relation with our method.

\subsection{Exact Methods}

Some exact methods \cite{ogayar2015deferred,douze2015quickcsg,zhou2016mesh,xu2013fast,feito2013fast}, are optimized for efficiency, but cannot guarantee robustness. They are implemented by fixed-precision floating point arithmetic, so numerical errors are inevitable, which often leads to incorrect results.
Douze et al. \cite{douze2015quickcsg} developed a very efficient method for handling very large meshes. In addition, their method is varadic, which means it can perform boolean operations with arbitrary number of inputs. However, this method makes general position assumption and cannot deal with coplanar situations. However, large CSGs are more complex, and thus more likely to contain degenerate cases, and more vulnerable to numerical errors.

Many researchers have attempted to solve the robustness issues using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}. However, these methods are too expensive in terms of computation time and memory. For example, CGAL's \cite{cgal:hk-bonp3-15a} exact-arithmetic implementation \cite{granados2003boolean} of Nef polyhedra \cite{bieri1988elementary} is more than 50 times slower than non-robust boolean operations \cite{bernstein2009fast}.

\subsection{Approximative Methods}

Because it is difficult to achieve efficiency, accuracy, and robustness simultaneously, some methods sacrifice accuracy for greater efficiency and robustness. Most such methods are based on volumetric representations of meshes. However, the quality of the resulting mesh depends on the resolution of the volume grid, and better quality require significantly higher resolutions.
To accelerate this process, some methods reduce the complexity of the output mesh \cite{varadhan2004topology}, whereas others preserve non-intersected areas of the input mesh to avoid redundant tessellation \cite{pavic2010hybrid,wang2011approximate,zhao2011parallel,hable2005blister,ogayar2006gpu}.
Moreover, with the development of general-purpose computing on graphics processing units (GPGPU), many of them utilize the computational power of graphics hardware for boolean operations. These methods have good performance, and are suitable for interactive applications. However, the fundamental problem of approximate methods arises from the grid-dependent nature of volumetric calculations; they inevitably suffer from geometric detail loss and unwieldy topological changes.

\subsection{Plane-Based Methods}
\label{sec:pbrelated}

The concept of plane-based representations (P-reps) of polyhedrons was first described by Sugihara and Iri \cite{sugihara1990solid}. By using P-reps, boolean operations can be performed with only predicates, which are much easier to implement accurately and robustly. Berstein and Fussell \cite{bernstein2009fast} combined P-reps with binary space partition (BSP) trees \cite{thibault1987set,naylor1990merging} to develop a boolean operation method which is unconditionally robust with consistent inputs. Unlike methods based on vertex-based representations, this method does not rely on exact arithmetic to be robust.
However, the merging of two BSP trees is has $O(mn)$ time complexity, where $m$ and $n$ are the size of the trees. This time complexity makes this method impractical for large meshes. Subsequently, Campen and Kobbelt \cite{campen2010exact} improved this method by localizing BSP operations using an octree. In this method, mesh refinements only take place locally, near intersections, which leads to better performance. However, their method splits the intersection regions and non-intersection regions, and requires extra stitching step to reconstruct topology. Also, the performance of localized BSP merging is still poor compared with vertex-based boolean methods.

### 2017-01-19 tex/intro.tex
谁来抄这篇论文？

@@
 \begin{abstract}
-  Constructive solid geometry (CSG) is widely used in computer aided design and manufacturing.
-However, boolean algorithms, which compute the boundary representations of CSG, have suffered from robustness and efficiency problems for more than three decades.
-We propose a fast and robust boolean operation method which is unconditionally robust for valid solids.
-Previously reported boolean methods using plane-based representations (P-reps) of polyhedrons are robust, but inefficient.
-Conversely, methods based on vertex-based representations (V-reps) are fast but not robust, unless exact arithmetic is applied.
-We choose to combine P-reps with V-reps, which allowed us to use the advantages of both.
-Our method uses V-reps for efficiency and uses P-reps to ensure robustness.
-Comparison experiments with the state-of-the-art show that our method is unconditionally robust, and similarly efficient to existing non-robust methods.
+  Constructive solid geometry (CSG) is a widely used modeling tool.
+It constructs complex models by combining primitive solids with boolean operations.
+However, boolean evaluation, which computes the final model of CSG, has suffered from robustness problem for more than three decades.
+Some methods are fast but not robust, while some methods are robust but rely on exact arithmetic which is slow.
+Recent works tried to implement fast and robust boolean evaluation methods using plane-based representations (P-reps) of polyhedrons instead of vertex-based representations (V-reps) of polyhedrons.
+While they have achieved remarkable improvements, they are still slow compared with non-robust methods.
+We propose a fast and robust boolean method.
+It uses hybrid representations of polyhedrons, which combines P-reps with V-reps.
+It allows us to take advantages of both the efficiency of V-reps and the exactness of P-reps.
+Comparison experiments with the state-of-the-art show that our method is unconditionally robust for solid inputs, and is similarly efficient to existing non-robust methods.
 \end{abstract}
@@
 Complex models are constructed by combining primitives using regularized boolean operations \cite{requicha1977mathematical,tilove1980closure}: union, intersection, and difference.
-A CSG can be converted into the boundary representation (B-rep) through boolean algorithms.
-There are two major types of boolean algorithms, which vary according to how they deal with intersections between primitives.
+A CSG can be converted into the boundary representation (B-rep) through boolean evaluation.
+There are two major types of boolean evaluation methods, which vary according to how they deal with intersections between primitives.
 Approximate methods \cite{wang2011approximate,pavic2010hybrid,biermann2001approximate} rediscretize the intersection areas, fit vertices approximatively, and rearrange the topology.
@@
 However, there is always a compromise between robustness and efficiency for exact boolean algorithms.
-Robust methods often require exact arithmetics \cite{barki2015exact,zhou2016mesh}, which is significantly slower than normal floating point arithmetic.
-Other methods only offer \textbf{quasi-robust} \cite{shewchuk1999lecture} implementations by using unreliable techniques, such as epsilon-tweaking \cite{laidlaw1986constructive,feito2013fast,segal1990using} and numerical pertubation on coordinates \cite{douze2015quickcsg}.
-Recently, robust methods have been developed \cite{bernstein2009fast,campen2010exact} based on binary space partition (BSP) merging routines \cite{naylor1990merging,thibault1987set}.
-The robustness of these methods are guaranteed by the theorem of Sugihara and Iri \cite{sugihara1990solid} that boolean operations can be performed without \textbf{constructions} \cite{shewchuk1999lecture} if polyhedrons are represented based on planes instead of vertices.
-By only use \textbf{predicates}, implementations of boolean operations are easier to be robust.
-These BSP-based methods are generally faster than other boolean algorithms using exact arithmetics.
-However, they still suffer from performance issues because of the complex conversions between vertex-based representations (V-reps) and plane-based representations (P-reps).
-In addition, the incoherence between V-reps and P-reps requires that extra steps to reconstruct connectivity, leading to complex implementations and worse performance.
+Robust methods often require exact arithmetic \cite{barki2015exact,zhou2016mesh}, which is significantly slower than normal floating-point arithmetic.
+Other methods only guarantee \textbf{quasi-robust} \cite{shewchuk1999lecture} by using unreliable techniques, such as epsilon-tweaking \cite{laidlaw1986constructive,feito2013fast,segal1990using} and numerical perturbation \cite{douze2015quickcsg}.
+Recently, robust plane-based methods have been developed \cite{bernstein2009fast,campen2010exact} based on binary space partition (BSP) merging algorithms \cite{naylor1990merging,thibault1987set}.
+The robustness of these methods is guaranteed by the theorem of Sugihara and Iri \cite{sugihara1990solid} that boolean evaluations can be performed without \textbf{constructions} \cite{shewchuk1999lecture} if polyhedrons are represented based on planes instead of vertices.
+By only use \textbf{predicates}, boolean methods are easier to be robust.
+These plane-based methods are generally faster than others which using exact arithmetic.
+However, they still suffer from performance issues because of the high computation complexity of BSP algorithms.
+In addition, the incoherence between BSP representations and B-reps of polyhedrons requires that extra steps for conversion and connectivity reconstruction, leading to worse performance.
 
-Inspired by these previous studies, we have developed a robust boolean operation method, which is unconditionally robust given consistent input, and as fast as non-robust methods.
-In our method, we combine P-reps with V-reps, forming hybrid representations of meshes.
-To ensure robustness, we avoid constructions throughout our method, and only performing exact predicates.
-Numerical filters \cite{shewchuk1997adaptive} are applied to guarantee performance.
+Inspired by these previous studies, we develop a robust boolean method, which is unconditionally robust given consistent solid inputs, and as fast as non-robust methods.
+In our method, we combine P-reps with V-reps, forming hybrid representations of solids.
 Generally, the V-reps information is used for coarse tests and efficient neighboring face queries, while P-reps information is used for exact predicates.
+To avoid using exact arithmetic and ensure efficiency, we avoid constructions throughout our method.
 
 Our method is different from the previous BSP-based methods \cite{bernstein2009fast,campen2010exact}.
-While their methods are largely based on BSP theorem of \cite{naylor1990merging,thibault1987set}, our method is more like V-reps methods such as \cite{feito2013fast,zhou2016mesh} and is significantly faster.
-Our method is not a simple improvement of V-reps methods, but an efficient and systematical solution for robustness of boolean operations.
+While their methods are largely based on BSP theorem of \cite{naylor1990merging,thibault1987set}, our method is more like vertex-based methods such as \cite{feito2013fast,zhou2016mesh} and is significantly faster than these BSP-based methods.
+Our method is not a simple improvement of vertex-based methods, but a systematical solution for robustness of boolean evaluations.
 During intersection computation, we encode the triangle intersections into sets of planes, and then use these planes to determine exact tessellations.
-Subsequently, we classify each face in the tessellated meshes using local binary space partition (BSP) trees, which also compliment the P-reps to guarantee exactness.
-In addition, while most existing boolean operations can only process two meshes, our method is varadic \cite{zhou2016mesh}, which can evaluate arbitrary inputs immediately.
-Thus, our method may reduces computation time in large cases by avoiding repetitive operations.
-Experiments have shown that our method is much faster than existing robust methods, and only around two times slower than non-robust exact methods.
-
-%Because computations based on P-reps are slower, we develop a set of algorithms
+Subsequently, we classify each face in the tessellated meshes using small local BSP trees, which also compliment the P-reps to guarantee exactness.
+In order to guarantee performance, we try to minimize the usage of plane-based exact predicates in these stages.
+In addition, while most existing boolean methods can only process two meshes, our method is \textbf{variadic} \cite{zhou2016mesh}, which can evaluate arbitrary inputs immediately.
+Thus, our method may reduce evaluation time of large CSGs by avoiding repetitive computation.
+Experiments have shown that our method is much faster than existing robust methods, and only around two times slower than non-robust methods.
 
@@
 
-Boolean operations have been researched since their inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}.
+Boolean methods have been researched since their inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}.
 Existing methods can be put into two categories: exact methods and approximate methods.
@@
 The coordinates of intersection points between input meshes are computed by input configurations.
-However, the coordinates cannot be represented exactly using fixed-precision floating point numbers, hence robustness is a significant problem.
+However, the coordinates cannot be represented exactly using fixed-precision floating point numbers, hence exact arithmetic is needed for robustness.
 Conversely, approximate methods rediscretize the input mesh surfaces using techniques such as voxels, octrees, and Layered Depth Images (LDI).
-These methods generally have better performance and robustness than exact methods, but the loss of precision and geometry information is inevitable.
-In this section, we first introduce previous work of these two categories, and then discuss plane-based boolean algorithms, which have close relation with our method.
+These methods generally have better performance and easier to be robust than exact methods, but the loss of precision and geometry information is inevitable.
+In this section, we first introduce previous work of these two categories, and then discuss plane-based boolean methods, which have close relation with our method.
 
@@
 
-Some exact methods \cite{ogayar2015deferred,douze2015quickcsg,zhou2016mesh,xu2013fast,feito2013fast}, are optimized for efficiency, but cannot guarantee robustness.
-They are implemented by fixed-precision floating point arithmetic, so numerical errors are inevitable, which often leads to incorrect results.
+Some exact methods \cite{ogayar2015deferred,douze2015quickcsg,xu2013fast,feito2013fast,updegrove2016boolean}, are optimized for efficiency, but cannot guarantee robustness.
+They are implemented by fixed-precision floating-point arithmetic, so numerical errors are inevitable, which often leads to inconsistent results.
 Douze et al.
-\cite{douze2015quickcsg} developed a very efficient method for handling very large meshes.
-In addition, their method is varadic, which means it can perform boolean operations with arbitrary number of inputs.
+\cite{douze2015quickcsg} developed a very efficient method for handling very large meshes and arbitrary input primitives.
 However, this method makes general position assumption and cannot deal with coplanar situations.
-However, large CSGs are more complex, and thus more likely to contain degenerate cases, and more vulnerable to numerical errors.
 
-Many researchers have attempted to solve the robustness issues using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}.
-However, these methods are too expensive in terms of computation time and memory.
+Many researchers have attempted to solve the robustness issues using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean, zhou2016mesh,barki2015exact} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}.
+However, these methods are too expensive in terms of computation time.
 For example, CGAL's \cite{cgal:hk-bonp3-15a} exact-arithmetic implementation \cite{granados2003boolean} of Nef polyhedra \cite{bieri1988elementary} is more than 50 times slower than non-robust boolean operations \cite{bernstein2009fast}.
@@
 Most such methods are based on volumetric representations of meshes.
-However, the quality of the resulting mesh depends on the resolution of the volume grid, and better quality require significantly higher resolutions.
-To accelerate this process, some methods reduce the complexity of the output mesh \cite{varadhan2004topology}, whereas others preserve non-intersected areas of the input mesh to avoid redundant tessellation \cite{pavic2010hybrid,wang2011approximate,zhao2011parallel,hable2005blister,ogayar2006gpu}.
-Moreover, with the development of general-purpose computing on graphics processing units (GPGPU), many of them utilize the computational power of graphics hardware for boolean operations.
+However, the quality of the resulting mesh depends on the resolution of the volume grid, and better quality requires significantly higher resolutions.
+To accelerate this process, some methods reduce the complexity of the output mesh \cite{varadhan2004topology}, whereas others preserve non-intersected areas of the input mesh to avoid redundant tessellation \cite{pavic2010hybrid,wang2011approximate,zhao2011parallel,hable2005blister,ogayar2006gpu,updegrove2016boolean}.
+Moreover, with the development of general-purpose computing on graphics processing units (GPGPU), many of them utilize the computational power of graphics hardware for boolean evaluations.
 These methods have good performance, and are suitable for interactive applications.
-However, the fundamental problem of approximate methods arises from the grid-dependent nature of volumetric calculations; they inevitably suffer from geometric detail loss and unwieldy topological changes.
+However, the fundamental problem of approximate methods arises from the grid-dependent nature of volumetric calculations.
+They inevitably suffer from geometric detail loss and unwieldy topological changes.
 
@@
 The concept of plane-based representations (P-reps) of polyhedrons was first described by Sugihara and Iri \cite{sugihara1990solid}.
-By using P-reps, boolean operations can be performed with only predicates, which are much easier to implement accurately and robustly.
-Berstein and Fussell \cite{bernstein2009fast} combined P-reps with binary space partition (BSP) trees \cite{thibault1987set,naylor1990merging} to develop a boolean operation method which is unconditionally robust with consistent inputs.
-Unlike methods based on vertex-based representations, this method does not rely on exact arithmetic to be robust.
+By using P-reps, boolean evaluations can be performed with only predicates, which are much easier to implement robustly.
+Berstein and Fussell \cite{bernstein2009fast} combined P-reps with BSP trees \cite{thibault1987set,naylor1990merging} to develop a boolean method which is unconditionally robust with consistent inputs.
+Unlike vertex-based methods, their method does not rely on exact arithmetic to be robust.
 However, the merging of two BSP trees is has $O(mn)$ time complexity, where $m$ and $n$ are the size of the trees.
-This time complexity makes this method impractical for large meshes.
+Such high time complexity makes this method impractical for large meshes.
 Subsequently, Campen and Kobbelt \cite{campen2010exact} improved this method by localizing BSP operations using an octree.
-In this method, mesh refinements only take place locally, near intersections, which leads to better performance.
+In this method, mesh refinements only take place locally near intersections, which leads to better performance.
 However, their method splits the intersection regions and non-intersection regions, and requires extra stitching step to reconstruct topology.
-Also, the performance of localized BSP merging is still poor compared with vertex-based boolean methods.
+Also, the performance of localized BSP merging is still poor compared with the vertex-based methods.

### 2017-01-19 tex/overview.tex
谁来抄这篇论文？

\section{Background and Overview}

\label{sec:overview}

Our method is designed for boolean evaluations on arbitrary number of inputs primitives \cite{requicha1985boolean}. Primitives are triangular solid meshes free of self-intersecting. Geometry connectivity is also required as inputs. Even if there are topological deficiencies, our method still try to give acceptable answer. Our method is not sensitive to topological deficiencies which are not near the regions where primitives intersect.

In the following, we first discuss the causes of non-robustness of boolean methods. Then we analyze the cause of inefficiency of previous plane-based methods and discuss how to avoid these problems. Finally, we give an overview of the proposed method.

\subsection{Robustness of Boolean Methods}
\label{sec:paradigm}

The boolean evaluations on mesh primitives are, in essence, a process of face selection. Namely, given a boolean expression, the operation collect those faces that satisfy the expression to generate the final mesh. Whether a certain face $\bm{s}$ belong to the final mesh is determined by its inclusion labels and the boolean expression $f$:
\begin{equation}
\lambda_f(\bm{s}) = f(\boldsymbol{\Lambda}(\bm{s})) = f(\lambda_1(\bm{s}), \lambda_2(\bm{s}), \cdots, \lambda_n(\bm{s})),
\end{equation}
where $\lambda_i(\bm{s})$ is the inclusion label with respect to primitive $M_i$. Each label has four conditions: completely inside (\emph{in}), completely outside (\emph{out}), on the boundary with consistent normal vector (\emph{same}) or with opposite normal vector (\emph{oppo}). To compute $\lambda_f(\bm{s})$, the labels with respect to all of the primitives (as $\boldsymbol{\Lambda}(\bm{s})$) must be known.
The evaluation of boolean expression with inclusion labels are discussed in \cite{douze2015quickcsg,feito2013fast}. If and only if $\lambda_f(\bm{s})=same$, $\bm{s}$ is on the surface of the final mesh.

Unfortunately, not all of the input faces can be classified collectively. For some faces near the intersections, only parts of them belong to the final mesh. Therefore, an extra step before face classification is required to detect intersections between meshes. Then input meshes are tessellated according to these intersections to ensure that every face is completely inside, outside, or on the boundary of other input meshes.

Most of the existing boolean methods follow such two-step paradigm---intersection computation and face classification, as does our method. Non-robustness comes from three stages of such boolean methods. 1) The intersection between faces may not be exactly computed. 2) Face tessellation produces inconsistent topology. 3) The computation of the inclusion labels is not consistent with the location of the faces (see Fig. \ref{fig:falseclass}). These problems all come from the numerical errors during geometric computation. Therefore, if these three stages can be performed in exact ways, boolean evaluations are robust.

\begin{figure}[t]
\centering
\includegraphics[width=2.2in]{boolean-01}
\caption{In this 2D view, face $\bm{s}$ (the red line segment) of mesh $M_2$ is on the surface of mesh $M_1$. However, because the face barycenter $\bm{v}_{c(\bm{s})}$ is used to compute the labels, the coordinates of which contain round-off errors, the point could be moved to $\bm{v'}_{c(\bm{s})}$. Thus, $\bm{s}$ may be falsely classified as being outside of $M_1$.}
\label{fig:falseclass}
\end{figure}

\subsection{Plane-based booleans}
Comparing with applying exact arithmetic, using plane-based geometry \cite{campen2010exact} is more promising to produce efficient exact computations. Therefore, in our method, we use P-reps as the key to avoid numerical errors.

\label{sec:substrates}
\subsubsection{Plane-based representation}

\begin{wrapfigure}{r}[0in]{0in}
\includegraphics[width=1.5 in]{p-reps}
\end{wrapfigure}

Using P-reps, each face $\bm{s}$ with $n$ edges is represented by a supporting plane $\bm{p}_{s,sp}$ on which the face lies, and a set bounding planes $\{\bm{p}_{s,b}^i \ \vert\  i = 0, 1,...,n-1\}$. Each edge line $\bm{e}_{\bm{s}}^i$ is represented by the intersection $\bm{p}_{s,sp} \cap \bm{p}_{s,b}^i$.
Vertex $\bm{v}_s^i$ is represented by the intersection of $\bm{p}_{s,sp}$ and two consecutive bounding planes. We use the method of Campen et al. \cite{campen2010exact} for the exact conversion of triangles to their P-reps. The exact plane-based predicates are sped up using numerical filtering techniques by Shewchuk \cite{shewchuk1997adaptive}.

Other commonly used notations in this paper are presented below. The normal of a plane $\bm{p}$ is denoted as $\bm{n}(\bm{p})$. A line $\bm{l}$ of P-reps can be represented by the intersection of two planes $(\bm{p}_l^0 \cap \bm{p}_l^1)$, hence, $\bm{l}\colon(\bm{p}_l^0 \cap \bm{p}_l^1)$. The positive direction of the line $\bm{l}$ is defined by $\bm{n}(\bm{p}_l^0) \times \bm{n}(\bm{p}_l^1)$.
A point $\bm{v}$ of P-reps can be represented by non-trivial plane triples $(\bm{p}_v^0 \cap \bm{p}_v^1 \cap \bm{p}_v^2)$, hence, $\bm{v}\colon(\bm{p}_v^0 \cap \bm{p}_v^1 \cap \bm{p}_v^2)$.

\subsubsection{Efficient embedding}

Under P-reps, vertex is represented with a much higher precision than under V-reps. A plane is represented by four parameters. Then a vertex takes twelve parameters under P-reps compared with only three parameters under V-reps. This makes geometric computations significantly slower under P-reps. Even though numerical filters can be applied to speed up, pure plane-based methods, such as \cite{sugihara1990solid,banerjee1996topologically}, cannot be as fast as vertex-based methods. On the other hand, a hybrid representation may bring both the efficiency of V-reps and the exactness of P-reps. And plane-based geometric computation should be avoided as much as possible to reduce computation cost.

BSP-based boolean algorithms are substantially based on planes, therefore are suitable to implement with P-reps \cite{bernstein2009fast,campen2010exact}. However, BSP merging is a pure plane-based algorithm. Also, BSP structure has additional two drawbacks which make it slow: a) BSP algorithms have high time complexity. b) BSP structure destroy geometry connectivity information, thus algorithms benefiting from connectivity require extra effort to reconstruct connectivity. Therefore, as an exact but not efficient representation, BSP should not substitute V-reps in total, but can serve as a compliment of V-reps to help plane-based geometric computation. Also, BSP structure has to be localized to minimize its size.

In our method, we use V-reps for coarse tests and fast connectivity queries and P-reps for exact predicates. The framework of our method is based on \cite{ogayar2015deferred}, which is a vertex-based method. Plane-based algorithms are embedded into the processing. This embedding is not a simple plane-based implementation of vertex-based algorithms. We develop three efficient algorithms which is optimized under P-reps: triangle-triangle intersection tests, triangle tessellation and polygon classification. These three algorithms are corresponding to the three sources of non-robustness discussed in \S\ref{sec:paradig}. The major difficulty is to avoid any computation under high precision, which means our method is designed to be implemented using only common double-precision floating-point arithmetic. Though BSP-based methods \cite{bernstein2009fast,campen2010exact} also do not use high precision arithmetic, this constrain is harder to satisfy under a vertex-based framework.

\subsubsection{Mapping to three diemensions}

Many vertex-based algorithms, such as 2D triangulation and face classification, is hard to implement under P-reps because they requires projection from three dimensions to planes or lines.  Projections are performed on vertex coordinates which are absent under P-reps. Since plane-based predicates \cite{bernstein2009fast,banerjee1996topologically} are usually performed under three dimensions, we have to find the equivalent three dimensional problem, whose projection to low dimension is the problem we want to compute. In the following, we discuss three such plane-based algorithms used in our method.

\vspace{0.5em}
\noindent \textbf{Point-line orientation}

\noindent Within the plane $\bm{p}_0$, the point-line orientation is computed by the line parameters and point coordinates under V-reps. Under P-reps, we map this problem to point-plane orientation by picking a plane $\bm{p_l}$ which satisfy three requirements: 1) the line is in $\bm{p_l}$. 2) $\bm{p_l}$ is not parallel with $\bm{p}_0$. 3) $\bm{n}(\bm{p}_0) \times \bm{n}(\bm{p_l})$ has the same orientation as the line.

\vspace{0.5em}
\noindent \textbf{Linear ordering of points}

\begin{figure}
  \centering
  \includegraphics[width=3.5in]{twopointoneline}\\
  \caption{Geometric configuration of the linear ordering of points. Points $\bm{v}_a$ and $\bm{v}_b$ are both on line $\bm{l}_{ab}$. We convert this problem into the plane ordering of $\bm{p}_a$ and $\bm{p}_b$ along $\bm{l}_{ab}$.}\label{fig:twopointoneline}
\end{figure}

\noindent Given a line $\bm{l}_{ab}$ with two points on it, $\bm{v}_a\colon(\bm{p}_a^0\cap\bm{p}_a^1\cap\bm{p}_a^2)$, and $\bm{v}_b\colon(\bm{p}_b^0\cap\bm{p}_b^1\cap\bm{p}_b^2)$, we need to determine the linear order of the two points along $\bm{l}_{ab}$ (see Fig. \ref{fig:twopointoneline}).
To solve this problem, we choose one plane that is not parallel with $\bm{l}_{ab}$ from the P-rep of each point, then convert this problem into one of determining the linear order of planes, which can be solved using the method of Banerjee et al. \cite{banerjee1996topologically}. The chosen planes should have the same orientation with respect to $\bm{l}_{ab}$ (the dot product between the plane normal and $\bm{l}_{ab}$ must be positive), and unqualified planes need to be flipped.

\begin{wrapfigure}{r}[0in]{0in}
\includegraphics[width=1.5 in]{boolean-02}
\end{wrapfigure}
\vspace{0.5em}
\noindent \textbf{Circular ordering of lines}~~~~

\noindent During face tessellation, we need to know which intersections are neighbors (see Fig. \ref{fig:circularorder}). This requires circular ordering of directed lines around a vertex. The Lines can be sorted in a divide-and-conquer way, based on the relative order of each pair of lines. Thus, this problem is converted to one where, given two lines $\bm{l}_a$ and $\bm{l}_b$ in a plane $\bm{p}_0$, circular order of the two lines needs to be computed.
We can compute the order by the sign of $\sin{\theta_{ab}}$, where $\theta_{ab}\in(-\pi,\pi)$ is the angle from $\bm{l}_a$ to $\bm{l}_b$ in the top-view of $\bm{p}_0$.

We know the sign of $\sin{\theta_{ab}}$ is the same as the sign of $\bm{n}(\bm{p}_0) \cdot (\bm{l}_a\times\bm{l}_b)$. However, directly computing this equation requires extra precision to explicitly compute $\bm{l}_a$ and $\bm{l}_b$. Fortunately, we found a efficient solution which only needs to compute the sign of a 3$\times$3 determinants, whose elements are all floating-point numbers.

\begin{theorem}
  \label{theorem1}
  Given two directed lines $\bm{l}_a\colon(\bm{p}_0\cap\bm{p}_a)$ and $\bm{l}_b\colon(\bm{p}_0\cap\bm{p}_b)$ within plane $\bm{p}_0$, the following relation always stands:
  \begin{equation}
    sign(\sin{\theta_{ab}})=  sign(\bm{n}(\bm{p}_0)\cdot(\bm{n}(\bm{p}_a) \times \bm{n}(\bm{p}_b)))
  \end{equation}
\end{theorem}

\begin{proof}
 First, $\bm{n}(\bm{p}_a)$ and $\bm{n}(\bm{p}_b)$ are orthogonally decomposed along $\bm{n}(\bm{p}_0)$:
 \begin{equation}
 \begin{split}
   &\bm{n}(\bm{p}_a)= \bm{n}^\parallel(\bm{p}_a) + \bm{n}^\perp(\bm{p}_a)\\
   &\bm{n}(\bm{p}_b)= \bm{n}^\parallel(\bm{p}_b) + \bm{n}^\perp(\bm{p}_b),
 \end{split}
 \end{equation}
 where the superscript $\parallel$ refers to the component parallel with $\bm{p}_0$ and $\perp$ means the component orthogonal to $\bm{p}_0$. Since $\bm{n}(\bm{p}_0)$ is orthogonal with $\bm{p}_0$, we get:
 \begin{equation}
   \label{eq:circ1}
   \bm{n}(\bm{p}_0) \cdot (\bm{n}(\bm{p}_a) \times \bm{n}(\bm{p}_b)) = \bm{n}(\bm{p}_0) \cdot (\bm{n}^\parallel(\bm{p}_a) \times \bm{n}^\parallel(\bm{p}_b)).
 \end{equation}
 On the other hand, the angle between $\bm{n}^\parallel(\bm{p}_a)$ and $\bm{n}^\parallel(\bm{p}_b)$ is exactly $\theta_{ab}$. Therefore,
 \begin{equation}
   \label{eq:circ2}
   sign(\sin{\theta_{ab}})=  sign(\bm{n}(\bm{p}_0) \cdot (\bm{n}^\parallel(\bm{p}_a) \times \bm{n}^\parallel(\bm{p}_b))).
 \end{equation}
 By (\ref{eq:circ1}) and (\ref{eq:circ2}), the theorem is proved.
\end{proof}

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{circularorder}
\caption{Geometric configuration of the circular ordering of lines. $\bm{l}_a\colon(\bm{p}_0 \cap \bm{p}_a)$ and $\bm{l}_b\colon(\bm{p}_0 \cap \bm{p}_b)$ are within plane $\bm{p}_0$.}
%Geometric configuration of the circular ordering of lines. la:
\label{fig:circularorder}
\end{figure}

\subsection{Method Overview}

%There are three steps to our method. The first step is to compute the intersections between each triangle face pair. In the second step, the input meshes are tessellated into intersection-free meshes according to these intersections. Lastly, each face is classified and the final mesh is generated.

Before going into details, we give an overview of our method. While the framework is similar to a V-rep based boolean method, we address the major differences in each stage and briefly explain why these differences are necessary.

\subsubsection{Intersection computation}

In this step, we compute the intersections between pairs of triangles. The triangle-triangle intersection algorithm is largely based on M\"{o}llers algorithm \cite{moller1997fast}. However, the conventional V-rep based implementation of M\"{o}ller's algorithm introduces numerical errors. Our P-rep based intersection algorithm implicitly represents intersections using planes to avoid errors. In addition, we carefully deal with degenerate cases, including point intersections, edge intersections, and coplanar intersections. Furthermore, octree is used to speed up the process. Details are provided in \S\ref{section:isect}.

\subsubsection{Deferred tessellation}

%Once all intersections between triangles are detected, we need to tessellate the input meshes and construct the intersection-free meshes. In many methods like \cite{ogayar2015deferred}, constraint Delaunay triangulation (CDT) is applied to perform tessellation. However, for a CSG with more than two meshes, intersections may overlap or intersect with each other, and cannot be used for constraints of CDT directly. In addition, as our intersections are represented by planes, implementation of CDT are complex and inefficient, as most CDT algorithms (e.g. \cite{chew1989constrained}, \cite{de1992line}) is not designed to handle planes and requires explicit coordinates. Therefore, we first perform intersection refinement to resolve intersecting intersections. After that, we construct a graph-like structure suitable for P-rep intersections, called \emph{tess-graph}, to guide the exact tessellation of each face. After all faces are tessellated, we get our intersection-free meshes. Details are shown in \S\ref{sec:tessellation}.

Once all of the intersections between triangles are determined, input meshes are subdivided, so that all intersections occurs on edges and vertices. In many existing methods (e.g., \cite{ogayar2015deferred,zhou2016mesh}), 2D constrained Delaunay triangulation (CDT) \cite{chew1989constrained}\cite{de1992line} is used to implement this stage. In our method, intersections are represented by planes. Therefore, projection is not allowed and the 2D CDT has to be mapped to an equivalent 3D problem. However, a 2D CDT needs to construct edges between arbitrary pair of vertices, whose equivalent 3D operation is to construct new planes which contains arbitrary two vertices. The newly constructed planes require extra precision to represent, and computations with them are slow.

Therefore, we choose to tessellate in a more conservative way that do not add any new edges. As a consequence, the subdivided faces are no more triangles. We first perform intersection refinement to resolve intersections between intersections to make them \emph{regularized}. We then construct a graph-like structure, called a \emph{tess-graph}, to guide the exact tessellation of each face. Details are given in \S\ref{sec:tessellation}.

\subsubsection{Face classification}

The purpose of this step is to collect faces that pass the CSG expression from the tessellated meshes to generate the final mesh. However, literally computing the inclusion label vector of each face is unacceptably slow for large CSGs. We utilize the connectivity information to propagate inclusion labels in a flood-filling manner. The seed labels used for flood-filling have to be computed beforehand. Typically, a seed face label is deduced by the label of point on that face. However, the point label can be incorrectly computed without exact arithmetic. We exactly computed face label by a local BSP constructed according to the faces of neighborhoods. Our algorithm does not requires exact arithmetic. Also, the constructed BSP is typically small, which resulting in good performance. Details are given in \S\ref{sec:classification}.

\begin{figure}[t]
\centering
\includegraphics[width=2.5in]{projection}
\caption{$Seg_1$ is the intersection between $\bm{p}_{t_2, sp}$ and $t_1$. $Seg_2$ is the intersection between $\bm{p}_{t_1, sp}$ and $t_2$. The intersection between $t_1$ and $t_2$ (yellow line segment) is the overlap of $Seg_1$ and $Seg_2$.}
%Seg1 is the intersection between pt2,sp and t1. Seg2 is the intersection between pt1,sp and t2. The intersection between t1 and t2 (yellow line segment) is the overlap of Seg1 and Seg2.
\label{fig_projection}
\end{figure}

### 2017-01-21 tex/inter.tex
before classification

\section{Intersection Computation}

\label{section:isect}

In this step, the intersections between faces are determined by triangle-triangle intersection tests. We use  M\"{o}ller's algorithm \cite{moller1997fast} because of its efficiency and simplicity. To ensure exact intersection computation, we integrate plane-based geometry into this algorithm. In the following, we first describe our space division algorithm, which reduces the number of intersection tests. Then our plane-based intersection algorithm is introduced. Lastly, we discuss how to deal with degenerate situations.

\subsection{Space Division}
\begin{wrapfigure}{r}[0in]{0in}
\includegraphics[width=1.2in]{octreediff}
\end{wrapfigure}

As intersection detection is performed between each pair of faces, space division is necessary to reduce the number of testing pairs. We use an adaptive octree for this purpose. Our implementation is akin to the implementation of Ogayar et al. \cite{ogayar2015deferred}. The intersections between triangle faces and octree nodes are efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}. Octree leaves are classified into two types. If all faces that intersect a leaf belong to the same mesh, we regard it as a \emph{normal cell}. Otherwise, it is regarded as a \emph{critical cell}, within which the triangle-triangle intersection tests are performed.

The difference between our octree and that of Ogayar et al. is that we do not subdivide any normal cell, no matter how many faces it contains. Subdividing normal cells is only beneficial for the point-in-polyhedron test \cite{frisken2002simple}, which is seldom used in our method. This simplification saves significant computing time, especially when intersections between primitives are sparse located in small regions.

\subsection{Plane-Based Intersection Test}

We first make a quick review of M\"{o}ller's vertex-based algorithm. Then we introduce our implicit representations of intersections using planes. After that, we discuss how to implement M\"{o}ller's algorithm using plane-based geometry.

\subsubsection{Review of M\"{o}ller's algorithm}

\begin{figure}[t]
\centering
\includegraphics[width=2.5in]{projection}
\caption{$Seg_1$ is the intersection between $\bm{p}_{t_2, sp}$ and $t_1$. $Seg_2$ is the intersection between $\bm{p}_{t_1, sp}$ and $t_2$. The intersection between $t_1$ and $t_2$ (yellow line segment) is the overlap of $Seg_1$ and $Seg_2$.}
%Seg1 is the intersection between pt2,sp and t1. Seg2 is the intersection between pt1,sp and t2. The intersection between t1 and t2 (yellow line segment) is the overlap of Seg1 and Seg2.
\label{fig_projection}
\end{figure}

M\"{o}ller's algorithm computes the intersection between two triangles $t_1$ and $t_2$ in three steps as shown in Fig. \ref{fig_projection}:
\begin{itemize}[leftmargin=0.45cm]
\item[1)] An early rejection is performed by testing whether $t_1$ intersects $\bm{p}_{t_2, sp}$, the supporting plane of $t_2$. The same test is also carried out between $t_2$ and $\bm{p}_{t_1, sp}$.
\item[2)]The intersection between $t_1$ and $\bm{p}_{t_2, sp}$, denoted as $Seg_1$, and the intersection between $t_2$ and $\bm{p}_{t_1, sp}$, denoted as $Seg_2$, are computed separately.
 \item[3)]The intersection between $t_1$ and $t_2$ is determined by computing the overlap between $Seg_1$ and $Seg_2$ .
\end{itemize}

The non-robustness of this algorithm stems from computing the coordinates of the intersection vertices (the end points of $Seg_1$ and $Seg_2$). Although implementation of this algorithm with arbitrary precision arithmetic produces exact coordinates, it is too costly for boolean evaluations with large CSGs.

\subsubsection{Plane-based intersection representation}
\label{sec:ir}

In our method, an intersection line segment  $\bm{\mathcal{I}}$ is stored as $\{T, \bm{P}_{ext}, \bm{P}_0, \bm{P}_1, \mathcal{N}\}$. This is the plane-based intersection representation (PBI-rep,  see Fig. \ref{fig:pbi}). The first component, $T$, indicates which triangle $\bm{\mathcal{I}}$ lies on.
$\bm{P}_{ext}$ indicates the plane that $\bm{\mathcal{I}}$ lies on. $T$ should not be in $\bm{P}_{ext}$. Thus the first two components indicate that  $\bm{\mathcal{I}}$ lies on the line $T \cap \bm{P}_{ext}$.
Then two end points of $\bm{\mathcal{I}}$ are $T \cap \bm{P}_{ext}\cap\bm{P}_0$ and $T \cap \bm{P}_{ext}\cap\bm{P}_1$.
The last component, $\mathcal{N}$, represents the neighborhood faces of $\bm{\mathcal{I}}$. $\mathcal{N}$ can be a single face, or a set faces from one or more input primitives.

\begin{figure}[t]
\centering
\includegraphics[width=3in]{pbirep2}
\caption{The geometry of planes in a PBI-rep. The yellow line segment is the intersection represented by $\bm{\mathcal{I}}$.}
\label{fig:pbi}
\end{figure}

For example, two triangle faces, $t_1$ and $t_2$, originating from meshes $M_i$ and $M_j$ respectively, intersect. Two intersections are generated, ${\bm{\mathcal{I}}}_{12}$ on $t_1$ and ${\bm{\mathcal{I}}}_{21}$ on $t_2$.
For ${\bm{\mathcal{I}}}_{12}$, $T = t_1$ and $\bm{P}_{ext}=\bm{p}_{t_2, sp}$. $\bm{P}_0$ and $\bm{P}_1$ are boundary planes of $t_2$, which will be discussed later.
The last component $\mathcal{N}=t_2$ in general situation. Sometimes, ${\bm{\mathcal{I}}}_{12}$ may lie on the edge of $t_2$ (see Fig. \ref{fig:twin}). This is called \emph{edge intersection}. In this situation, the $\mathcal{N}$ is the set of all the faces from $M_j$ adjacent to that edge. Edge intersection is discussed in \S\ref{sec:degenerate}.

\subsubsection{Plane-based implementation}

\label{sec:embed}
\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{sign}
\caption{We denote the signed distance from point $v_i$ to plane $\bm{p}_{t_2, sp}$ as $d_i$. The four conditions of intersection between $t_1$ and $\bm{p}_{t_2, sp}$ are:
(a) $d_0\cdot d_2<0$, $d_1\cdot d_2<0$;
(b) $d_0=0$, $d_1=0$, $d_2\neq 0$;
(c) $d_0=0$, $d_1\cdot d_2<0$;
(d) $d_0=0$, $d_1\cdot d_2>0$. End points of $Seg_1$ are the intersections between $\bm{p}_{t_2, sp}$ and the related edges of $t_1$ (bold red lines).}
\label{fig:isect}
\end{figure}

To implement M\"{o}ller's algorithm by plane-based geometry, we first convert each triangle to its P-reps: a supporting plane $\bm{p}_{t, sp}$  surrounded by three bounding planes $\{\bm{p}_{t, b}^i|\ i = 0,1,2\}$. The substrates of the intersection algorithms are point-plane orientation \cite{bernstein2009fast} and linear order of points (\S\ref{sec:substrates}), both of which can be implemented by plane-based geometry.

In the first step, the computation of signed distances involves only the vertices coordinates and the supporting planes of triangles. Therefore, if the early rejections occur, the bounding planes are not needed at all. In addition, according to the conversion method of Campen et al.\cite{campen2010exact}, the supporting plane is represented by four double-precision floating-point numbers. The precisions of the first three parameters and the last parameter are $L_a$ and $L_d$ respectively. They hold the relation $L_d = L_a + L + 1$, where $L$ is the precision of the coordinates of input vertices. This means we can compute the signed distance exactly within double-precision. With these two facts, our early rejection is as fast as the vertex-based implementation.

If $t_1$ and $t_2$ are not coplanar, $Seg_1$ and $Seg_2$ are computed. The end points are intersections between the supporting plane of one triangle and an edge of the other triangle. By computing the bounding planes, the end points can be implicitly represented by plane triples, $\bm{p}_{t_2, sp} \cap \bm{p}_{t_1, sp} \cap \bm{p}^i_{t_1, b}$, where $\bm{p}^i_{t_1, b}$ is the bounding plane of the related edge.
Fig. \ref{fig:isect} shows all of the possible intersection conditions between $t_1$ and $\bm{p}_{t_2, sp}$. The coplanar situation is discussed specifically in \S \ref{sec:degenerate}.

To avoid repetitive vertices in the final result, we perform vertex repetition elimination in this step. Because P-reps are used, the coincidence tests of the vertices are exact.

\subsection{Handling Degenerate Situations }
\label{sec:degenerate}

In most situations, intersections between triangles are line segments. However, they can also intersect on a point or a convex area. Even if the intersection is a line segment, the intersection can be on a primitive edge. These degenerate situations prevent us from performing robust boolean operations. In this section, we demonstrate our simple but effective ways of dealing with these degenerations, which conceals the complexity of intersections, and simplifies later processing.

\subsubsection{Point intersection}
\label{sec:ipoint}

If two triangles intersect at a single point (e.g., Fig. \ref{fig:isect}d) then the intersection cannot be represented using our PBI-rep. In this situation, we simply add the intersection point into the related triangles, guaranteeing correct tessellation. No intersection line segment is introduced.

\subsubsection{Edge intersection}

When a triangle intersects with the edge of other triangle, the generated intersection is referred as \emph{edge intersection}. The neighboring faces of the intersection is the set of all the faces that shared the edge rather than a single face. For example, in Fig. \ref{fig:twin}a, the neighboring faces of the intersection on $t_1$ are $t_2$ and $t^*_2$.

An edge intersection will be repeatedly detected. For example, in Fig. \ref{fig:twin}a, the same intersection on $t_1$ will be detected twice, because $t_1$ intersects both $t_2$ and $t_2^*$ at the same line segment. We solve this duplication in tessellation stage (see \S\ref{sec:tessellation}). We regard $t_2$ and $t_2^*$ as \emph{companion} triangles, because they are the neighboring faces of the same edge intersection. This concept will be referred to again in the discussion of coplanar cases.

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{edgeisect}
\caption{Different conditions of edge intersection. Triangle faces $t_1$ and $t_1^*$ are companion faces. Triangle faces $t_2$ and $t_2^*$ are companion faces. a) $t_2$ and $t_2^*$ are on different sides of $t_1$. b) $t_2$ and $t_2^*$ are on the same side of $t_1$. c) $t_2^*$ is coplanar with $t_1$. d) Both $t_1$ and $t_2$ have companion faces: the intersection is an edge intersection for both $t_1$ and $t_2$ (instead of only for $t_2$ is the previous three conditions). }
%Different conditions of edge intersection.
\label{fig:twin}
\end{figure}

\subsubsection{Copalnar}

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{boolean-03}
\caption{a) Coplanar situation. $t_1$ and $t_2$ intersect in 2D, dividing each other into a convex overlapping area and a exclusive area. b) Possible configurations of the companion faces. The blue triangles originate from the same mesh. For the yellow segment, it is not necessary in the final mesh, and it will not be detected. For the red segments, the companion triangles are not coplanar with $t_1$, so they can be detected during intersection tests between $t_1$ and the companion triangles ($t_a$ and $t_b$).}
\label{fig:coplanar}
\end{figure}

Consider two triangle faces, $t_1$ and $t_2$, which intersect within a common plane. Both $t_1$ and $t_2$ divide each other into two areas--a convex overlapping area and a exclusive area (see Fig. \ref{fig:coplanar}a). If we tessellate both $t_1$ and $t_2$ according to the boundary of the overlapping area, we can guarantee correct topology. This strategy is adopted by many previous methods \cite{feito2013fast,zhou2016mesh}. Conversely, in our method, we treat coplanar situations as if they do not intersect at all. We do not need any 2D intersection test. In this way, we avoid the processing of complex situations of 2D intersections, while having no side effect on the topological correctness.

We find that $t_1$ is actually clipped by edges of $t_2$ (see \ref{fig:coplanar}b). That means that we can view 2D intersections as special cases of edge intersections. There can be up to three edge intersections in one 2D intersection (red and yellow line segments). As discussed, edge intersections will be detected for multiple times by the companion triangles. Hence, we can rely on them to detect the intersections.

However, if all the companion triangles are coplanar, none of them will detect the intersection (the yellow segment). Fortunately, the intersection is not necessary in this situation. The neighboring faces of the intersection are all within the same plane. If such intersection is on the surface of the final mesh, the surface in the neighborhood of this intersection must be a plane. Therefore, the intersection is not necessary to be an edge in the final model and we can omit it.

Because we do not process coplanar intersections, the coplanar areas (the stripe areas) may have different tessellations in different primitives. It seems that inconsistent topology can occur in the final mesh. In fact, we do not need to worry about that, because faces from a certain primitive in such coplanar area are collected or abandoned together. The coplanar area, if on the surface of the final mesh, will inherit only one of the tessellations.

### 2017-01-21 tex/overview.tex
before classification

@@
 We develop three efficient algorithms which is optimized under P-reps: triangle-triangle intersection tests, triangle tessellation and polygon classification.
-These three algorithms are corresponding to the three sources of non-robustness discussed in \S\ref{sec:paradig}.
-The major difficulty is to avoid any computation under high precision, which means our method is designed to be implemented using only common double-precision floating-point arithmetic.
-Though BSP-based methods \cite{bernstein2009fast,campen2010exact} also do not use high precision arithmetic, this constrain is harder to satisfy under a vertex-based framework.
+These three algorithms are corresponding to the three sources of non-robustness discussed in \S\ref{sec:paradigm}.
+The major difficulty is to guarantee the efficiency and exactness simultaneously.
+For this purpose, we avoid any computation under high precision, which means our method is designed to be implemented using only common double-precision floating-point arithmetic.
 
@@
 \noindent Within the plane $\bm{p}_0$, the point-line orientation is computed by the line parameters and point coordinates under V-reps.
-Under P-reps, we map this problem to point-plane orientation by picking a plane $\bm{p_l}$ which satisfy three requirements: 1) the line is in $\bm{p_l}$.
-2) $\bm{p_l}$ is not parallel with $\bm{p}_0$.
-3) $\bm{n}(\bm{p}_0) \times \bm{n}(\bm{p_l})$ has the same orientation as the line.
+Under P-reps, we map this problem to point-plane orientation by picking a plane $\bm{p_l}$ which satisfy three requirements: 1) the line is in $\bm{p_l}$; 2) $\bm{p_l}$ is not parallel with $\bm{p}_0$; 3) $\bm{n}(\bm{p}_0) \times \bm{n}(\bm{p_l})$ has the same orientation as the line.
 
@@
 
-%There are three steps to our method.
-The first step is to compute the intersections between each triangle face pair.
-In the second step, the input meshes are tessellated into intersection-free meshes according to these intersections.
-Lastly, each face is classified and the final mesh is generated.
-
 Before going into details, we give an overview of our method.
-While the framework is similar to a V-rep based boolean method, we address the major differences in each stage and briefly explain why these differences are necessary.
+While the framework is similar to vertex-based boolean method, we address the major differences in each stage and briefly explain why these differences are necessary.
 
@@
 
-In this step, we compute the intersections between pairs of triangles.
-The triangle-triangle intersection algorithm is largely based on M\"{o}llers algorithm \cite{moller1997fast}.
-However, the conventional V-rep based implementation of M\"{o}ller's algorithm introduces numerical errors.
-Our P-rep based intersection algorithm implicitly represents intersections using planes to avoid errors.
-In addition, we carefully deal with degenerate cases, including point intersections, edge intersections, and coplanar intersections.
+We compute the intersections between pairs of triangles.
+The triangle-triangle intersection algorithm is largely based on M\"{o}ller's algorithm \cite{moller1997fast}.
+However, the conventional vertex-based implementation of M\"{o}ller's algorithm introduces numerical errors.
+Our plane-based intersection algorithm implicitly represents intersections using planes to avoid errors.
+In addition, we carefully deal with all of the degenerate situations, including point intersections, edge intersections, and coplanar intersections.
 Furthermore, octree is used to speed up the process.
@@
 
-%Once all intersections between triangles are detected, we need to tessellate the input meshes and construct the intersection-free meshes.
-In many methods like \cite{ogayar2015deferred}, constraint Delaunay triangulation (CDT) is applied to perform tessellation.
-However, for a CSG with more than two meshes, intersections may overlap or intersect with each other, and cannot be used for constraints of CDT directly.
-In addition, as our intersections are represented by planes, implementation of CDT are complex and inefficient, as most CDT algorithms (e.g.
-\cite{chew1989constrained}, \cite{de1992line}) is not designed to handle planes and requires explicit coordinates.
-Therefore, we first perform intersection refinement to resolve intersecting intersections.
-After that, we construct a graph-like structure suitable for P-rep intersections, called \emph{tess-graph}, to guide the exact tessellation of each face.
-After all faces are tessellated, we get our intersection-free meshes.
-Details are shown in \S\ref{sec:tessellation}.
-
 Once all of the intersections between triangles are determined, input meshes are subdivided, so that all intersections occurs on edges and vertices.
-In many existing methods (e.g., \cite{ogayar2015deferred,zhou2016mesh}), 2D constrained Delaunay triangulation (CDT) \cite{chew1989constrained}\cite{de1992line} is used to implement this stage.
+In many existing methods (e.g., \cite{ogayar2015deferred,zhou2016mesh}), 2D constrained Delaunay triangulation (CDT) \cite{chew1989constrained,de1992line} is used to implement this stage.
 In our method, intersections are represented by planes.
 Therefore, projection is not allowed and the 2D CDT has to be mapped to an equivalent 3D problem.
-However, a 2D CDT needs to construct edges between arbitrary pair of vertices, whose equivalent 3D operation is to construct new planes which contains arbitrary two vertices.
-The newly constructed planes require extra precision to represent, and computations with them are slow.
+However, a 2D CDT needs to construct edges between arbitrary pair of vertices, whose equivalent 3D operation is to construct new planes.
+The newly constructed planes have to contain arbitrary pair of vertices, thus require extra precision to represent.
 
-Therefore, we choose to tessellate in a more conservative way that do not add any new edges.
-As a consequence, the subdivided faces are no more triangles.
-We first perform intersection refinement to resolve intersections between intersections to make them \emph{regularized}.
-We then construct a graph-like structure, called a \emph{tess-graph}, to guide the exact tessellation of each face.
+To avoid this problem, we choose to tessellate in a more conservative way that do not add any new edges.
+As a consequence, the subdivided faces are no more triangles but polygons.
+We first perform intersection refinement to resolve intersections between intersections.
+We then construct a graph-like structure, called \emph{tess-graph}, to guide the exact tessellation of each face.
 Details are given in \S\ref{sec:tessellation}.
@@
 
-The purpose of this step is to collect faces that pass the CSG expression from the tessellated meshes to generate the final mesh.
+The purpose of this step is to collect faces that pass the boolean expression from the tessellated meshes to generate the final mesh.
 However, literally computing the inclusion label vector of each face is unacceptably slow for large CSGs.
 We utilize the connectivity information to propagate inclusion labels in a flood-filling manner.
-The seed labels used for flood-filling have to be computed beforehand.
-Typically, a seed face label is deduced by the label of point on that face.
-However, the point label can be incorrectly computed without exact arithmetic.
+Typically, the seed face label is deduced by the label of a point on that face.
+However, the computation of point label can be incorrect without exact arithmetic.
 We exactly computed face label by a local BSP constructed according to the faces of neighborhoods.
@@
 Details are given in \S\ref{sec:classification}.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=2.5in]{projection}
-\caption{$Seg_1$ is the intersection between $\bm{p}_{t_2, sp}$ and $t_1$.
-$Seg_2$ is the intersection between $\bm{p}_{t_1, sp}$ and $t_2$.
-The intersection between $t_1$ and $t_2$ (yellow line segment) is the overlap of $Seg_1$ and $Seg_2$.}
-%Seg1 is the intersection between pt2,sp and t1. Seg2 is the intersection between pt1,sp and t2. The intersection between t1 and t2 (yellow line segment) is the overlap of Seg1 and Seg2.
-\label{fig_projection}
-\end{figure}

### 2017-01-21 tex/tess.tex
before classification

\section{Deferred Tessellation}

\label{sec:tessellation}

Tessellation is performed on each intersecting triangle. This stage is referred as deferred tessellation, because the tessellation happens after all of the intersections between triangles are computed, instead of clipping triangles incrementally at each intersection.

Many methods use CDT to perform tessellation on triangles. They treated triangle faces as convex triangulation zones, and intersections as constraints. However, CDT algorithms \cite{chew1989constrained,preparata2012computational} are performed in 2D. Even after mapping to three dimensions, implementing a plane-based CDT requires introduction of new planes. These new planes are used to guarantee that each subface is a triangle (see Fig. \ref{fig:iisect}d). We find double-precision is not enough to store the coefficients of these planes. Therefore, we choose not to add any new edges, performing minimal tessellation on each triangle. In this way, the subdivided faces are no more triangles, but general polygons.

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{boolean-04}
\caption{a) Different colors indicate that the intersections originate from different meshes. The yellow and red intersections intersect at a point. The yellow intersection overlaps with the green intersection. b) After refinement, we introduce a new vertex $\bm{v}_a$, and merge overlapping intersections into a single edge $\bm{e}_b$. c) Our tessellation method does not guarantee that all of the faces are triangular. d) If triangulation is performed, new edges (red lines) are introduced and double-precision is not enough to hold the plane coefficients of their P-reps.}
\label{fig:iisect}
\end{figure}

In our method we first perform intersection refinement to ensure that intersections intersect each other only on end points. After that, we perform our minimal tessellation based on \emph{tess-graph}, a graph-like description of the intersections on a given face.

\subsection{Intersection Refinement}

\label{sec:refine}

Intersection vertices can be introduced by the intersection of three triangles, in addition to intersections between an edge and a triangle. Triangle-triangle intersection tests only compute the latter. Thus, it is necessary to refine these triangle-triangle intersections before the final tessellation.

Intersection refinement is performed on the scope of each intersecting triangle. For triangle face $t$, we collect all of the intersections on $t$ as a set $\bm{\Gamma}(t)$ and refine them together. We also include the three edges of $t$ in $\bm{\Gamma}(t)$, because the edges are also involved in the step of subfaces extraction. In $\bm{\Gamma}(t)$, the three edges are represented by PBI-reps. The neighboring faces $\mathcal{N}$ are set as $N/A$ because they do not have a neighboring face. Other PBI-rep components can be determined by the P-reps of the edges. The refinement of $\bm{\Gamma}(t)$ is done using only plane-based geometric predicates, in the following three steps.

\vspace{0.5em}
\noindent \textbf{Coincidence elimination}~~~~
We merge coincidence intersections that have the same end points. Intersections are undirected, so intersections with inverse end points are also coincident. The PBI-rep of the merged intersection is inherited from either of the original intersections, except for the neighboring faces $\mathcal{N}$. The neighboring faces of the merge intersection is the union of all the neighboring faces of original ones. It means from now on, an intersection may have neighboring faces from different primitives.

\vspace{0.5em}
%Intersection refinement is performed locally
\begin{wrapfigure}{r}[0in]{0in}
\includegraphics[width=1.6 in]{resolve}
%\caption{Plane-based representation of triangle}
\end{wrapfigure}
\noindent\textbf{Intersection resolving}~~~~
Each pair of intersections is tested if they intersect in any location other than end points. The test intersections should be from different primitives, since primitive inputs are free of self-intersecting. When two intersections intersect, at least one of them is split. New vertices may be introduced, whose P-reps are intersections between the common plane and the two $\bm{P}_ext$ of the PBI-reps. Because one intersection may be in contact with more than one other intersection, this splitting is deferred until all of the splitting points are found. The PBI-reps of the split segments inherit that of their father's, except for $\bm{P}_0, \bm{P}_1$, since the split segments have different end points.

\vspace{0.5em}
\noindent \textbf{Coincidence elimination (revisited)}~~~~
If two intersections are collinear, resolving their overlap may produce new coincident intersections. Therefore, the first step of the process is repeated here.

\subsection{Tessellation by Tess-Graph}
\label{sec:tess}

To perform tessellation and extract subfaces, we use tess-graph, which is the graph description of the tessellated face topology. For each intersecting triangle face, we construct a tess-graph according to the refined set of intersections. Nodes of the tess-graph represent the end points of intersections, and connections between nodes represent intersections. The construction of a tess-graph is straightforward, and readers should be able to determine the details.

After the tess-graph is constructed, we extract subfaces by   valid loops. A valid loop is a loop in tess-graph which satisfy two criteria: 1) the direction of the loop should correspond with the face normal, and 2) consecutive connections on the loop should be adjacent by circular order. Each valid loop corresponds to an intersection-free face. After all of the valid loops are determined from the tess-graph, the corresponding face is tessellated (see Fig. \ref{fig:cadj}). To facilitate face classification, we also store neighboring faces in the edges of the new faces. Because the edges have one-to-one correspondence to the connections in tess-graph , and the connections have one-to-one correspondence to the PBI-reps, the neighboring faces of edges is determined from the corresponding PBI-reps.

\begin{figure}[t]
\centering
\includegraphics[width=3in]{boolean-05}
\caption{a) To tessellate a triangle, we find all of the valid loops on a tess-graph. The direction of the loops must be coherent with the triangle normal (assuming here that the normal points to the outside of the paper). b) Each circular adjacent edge pair is an angle of the tessellated polygon.}
\label{fig:cadj}
\end{figure}

### 2017-01-21 tex/class.tex
hello

\section{Face Classification}

\label{sec:classification}

We traverse each face of the primitives, and determine which belong to the final mesh. The faces are classified by evaluating their inclusion label vector. Our classification method utilizes the space coherence of the label vectors, and shares the classification results among neighboring faces. Because we store the neighboring faces in the edges where intersections occur, the difference of labels between adjacent faces are computed according to the BSP constructed with these neighboring faces. For arbitrary adjacent faces $\bm{s}_1$ and $\bm{s}_2$, the label vectors $\bm{\Lambda}(\bm{s}_1)$ and $\bm{\Lambda}(\bm{s}_2)$ differ if their shared edge $\bm{e}_{12}$ lies on the surface of any other primitive.
In that cases, some neighboring faces should be stored on $\bm{e}_{12}$. The owner primitives of these neighboring faces indicate which labels differ. If there are neighboring faces from mesh $M_x$, the labels $\lambda_x(\bm{s}_1)$ and $\lambda_x(\bm{s}_2)$ differ. We outline our classification method in Algorithm \ref{code:floodfill}.

\begin{algorithm}[ht]
\caption{Fast Face Classification}
\label{code:floodfill}
\textbf{Input: } Tessellated primitives and boolean expression $f$

\textbf{Output: } Classification $f(\bm{\Lambda}(\bm{s}_i))$ of each face $\bm{s}_i$

\begin{algorithmic}[1]
\State Select a proper seed face $\bm{s}_0$
\State Compute the seed label vector $\boldsymbol{\Lambda}(\bm{s}_0)$
\State \Call{propagate} { $\bm{s}_0$ , $\boldsymbol{\Lambda}(\bm{s}_0)$}
\State
\Function{propagate}{ $\bm{s}$ , $\boldsymbol{\Lambda}(\bm{s})$}
    \State Compute $f(\boldsymbol{\Lambda}(\bm{s}))$
    \For {each neighboring face $\bm{s}_{s, i}$}
        \If {$\bm{s}_i$ has been classified}
            \State continue
        \EndIf
        \If {there are PBI-reps ${\bm{\mathcal{I}}}_k$ on $\bm{e}(\bm{s}_{s, i}, s)$}
            \State compute $\boldsymbol{\Lambda}(\bm{s}_{s, i})$ by $\boldsymbol{\Lambda}(\bm{s})$ and ${\bm{\mathcal{I}}}_k$
            \State \Call{propagate} { $\bm{s}_{s, i}$ , $\boldsymbol{\Lambda}(\bm{s}_{s, i})$}
        \Else
            \State \Call{propagate} { $\bm{s}_{s, i}$ , $\boldsymbol{\Lambda}(\bm{s})$}
        \EndIf
    \EndFor
\EndFunction
\end{algorithmic}
\end{algorithm}

\subsection{Label Computation}
\label{sec:propagation}

In methods like \cite{feito2013fast,ogayar2015deferred}, the face barycenter is used to compute the inclusion label of the face. This is because the face can be classified as a whole, and all inner points of the face has the same label vector. In methods like \cite{zhou2016mesh}, points inside the cell is used for label computation, and the face labels are decided by the labels of the two sides of the face. However, all these methods require to construct new vertices, whose coordinates require rational numbers to store, or round-off errors may be introduced. Incorrect label computation may occur because of such errors. To avoid this, we use the vertices instead, the exact coordinates of which are known.

\begin{wrapfigure}{r}[0in]{0in}
\includegraphics[width=1.3 in]{propagate}
\end{wrapfigure}

However, there are two discrepancies between the face labels and vertex labels. First, the vertex label is not always equal to the face label. Second, the face label has two subclasses in the $on$ case, $same$ and $oppo$, because the face has an orientation.

To deal with these discrepancies, we start from a seed vertex $\bm{v}_0$, which is one of the end point of an edge $\bm{e}_0$ of a face $\bm{s}_0$. We assume that the label vector $\bm{\Lambda}(\bm{v}_0)$ is known.
Then we use $\bm{\Lambda}(\bm{v}_0)$ to compute $\bm{\Lambda}(\bm{e}_0)$, and then $\bm{\Lambda}(\bm{s}_0)$. The trace of label propagation is:
\begin{equation}
\bm{v}_0\to \bm{e}_0\to \bm{s}_0\to \bm{s}_1\to \bm{s}_2\to ...~~~,
\end{equation}
There are three basic operations: $\bm{v}_{\bm{e}}\to \bm{e}$, $\bm{e}_{\bm{s}}\to \bm{s}$ and $\bm{s}_i\to \bm{s}_j$, where $\bm{v}_{\bm{e}}$ is the end point of $\bm{e}$,
$\bm{s}_{\bm{s}}$ is the edge of $\bm{s}$,
and $\bm{s}_i$ is adjacent to $\bm{s}_j$.

\begin{theorem}
  \label{thm:porder}
  Given the partial orders $on \succ in$ and $on \succ out$, the following relationship is true for labels within the tessellated primitives:
  \begin{equation}
    \lambda_k(\bm{v}_{\bm{e}_{\bm{s}}}) \succeq \lambda_k(\bm{e}_{\bm{s}}) \succeq \lambda_k(\bm{s}),
  \end{equation}
  where $\lambda_k(x)$ is the label of $x$ for a certain primitive $M_k$.
\end{theorem}

\begin{proof}
We prove this theorem by contradiction. When $\lambda_k(\bm{v}_{\bm{e}_{\bm{s}}}) \succeq \lambda_k(\bm{e}_{\bm{s}})$ is not satisfied, it means for a certain label $\lambda_k$, $\lambda_k(\bm{v}_{\bm{e}_{\bm{s}}})$ is $in$ or $out$, but $\lambda_k(\bm{e}_{\bm{s}}) \neq \lambda_k(\bm{v}_{\bm{e}_{\bm{s}}})$.
Let us assume that $\lambda_k(\bm{v}_{\bm{e}_{\bm{s}}})=in$ and $\lambda_k(\bm{e}_{\bm{s}})=on$ or $out$.

Because $\bm{v}_{\bm{e}_{\bm{s}}}$ is inside of closed regular set (solid) $M_k$, according to the continuity of space, any point in $U(\bm{v}_{\bm{e}_{\bm{s}}})$, which is the neighborhood of $\bm{v}_{\bm{e}_{\bm{s}}}$, should be inside of $M_k$.
And because $\bm{e}_{\bm{s}}^{\circ}\cap U(\bm{v}_{\bm{e}_{\bm{s}}})$ is not empty (superscript $\circ$ means interior), $\bm{e}_{\bm{s}}$ should be inside of $M_k$, which contradict our assumption.
\end{proof}

It indicates that when we perform $\bm{v}_{\bm{e}}\to \bm{e}$ and $\bm{e}_{\bm{s}}\to \bm{s}$, from a low-dimension to a high-dimension, we decide whether the $on$ label changes to $in$ or $out$, or remains $on$.
In addition, when considering the orientation of the face, we also need to determine whether the $on$ labels change to $same$ or $oppo$ during the $\bm{e}_{\bm{s}}\to \bm{s}$ operation.

\begin{figure}[t]
\centering
\includegraphics[width=3in]{bsps}
\caption{a) Because the inner sample point includes geometric constructions, we choose the face vertex (orange) instead to compute the face label. b-d) Different types of classification. The simple structure of the neighborhood BSP guarantees the same classification result for all of the points on $\bm{p}_{\bm{s}, sp}^+$. In d), the classification result is $on$ so it is necessary to determine the orientation from the normal of the BSP splitting plane $q$ and the face normal $p$. In this cases, the label should be $oppo$ because $p$ and $q$ are opposite.}
\label{fig:bsps}
\end{figure}

\vspace{0.5em}
\noindent\textbf{$\bm{\bm{e}_{\bm{s}}\to \bm{s}}$: } From theorem \ref{thm:porder}, we know that if $\lambda_k(\bm{e}_{\bm{s}}) \neq on$, then $\lambda_k(\bm{e}_{\bm{s}})=\lambda_k(\bm{s})$.
Conversely, when $\lambda_k(\bm{e}_{\bm{s}}) = on$, we can build a trivial BSP \cite{thibault1987set} using these the neighboring faces which belongs to $M_k$ stored in $\bm{e}_{\bm{s}}$.
The BSP can be used to compute inclusion state $\lambda_k(\bm{s})$ if a point can be sampled from $\bm{s}^{\circ} \cap \bm{U}(\bm{e}_{\bm{s}})$, where $\bm{U}(\bm{e}_{\bm{s}})$ is the neighborhood space of $\bm{e}_{\bm{s}}$. However, we cannot guarantee that such a point can be found with exact representation of double-precision.

\begin{theorem}
  \label{thm:bsp}
  The BSP is constructed by the neighboring faces around a certain edge $\bm{e}$. Then the inclusion states of all the points on interior of the half plane $\bm{h}$ are the same, if 1) $\bm{e}$ is within $\bm{h}$, and 2) $\bm{e}$ is the boundary of $\bm{h}$.
\end{theorem}
\begin{proof}
  The correctness of the theorem is obvious because the supporting planes of the neighboring faces always cross the edge $\bm{e}$ and extend to infinity.
\end{proof}

Let $\bm{h}_{\bm{s}}^+$ be the half of the supporting plane of $\bm{s}$ which lies on the interior side of $\bm{e}_{\bm{s}}$ (see Fig. \ref{fig:bsps}). By theorem \ref{thm:bsp}, the label of points on the half plane $\bm{h}_{\bm{s}}^+$ are identical.
Since $\bm{h}_{\bm{s}}^+ \cap \bm{s} \neq \varnothing$, we can compute $\lambda_k(\bm{s})$ by determining $\lambda_k(\bm{v}_x)$, where the vertex $\bm{v}_x \in \bm{h}_{\bm{s}}^+$. For polygons, we can always find at least one such vertex, which is represented exactly (by planes or vertex coordinates). In addition, we assign each BSP splitting plane a normal vector by the normal of the triangle it contains, from which we can decide the orientation ($same$ or $oppo$) when $\lambda_k(\bm{s})=on$.

\vspace{0.5em}
\begin{wrapfigure}{r}[0in]{0in}
 \includegraphics[width=1.3 in]{vneighbor}
\end{wrapfigure}
\noindent\textbf{$\bm{\bm{v}_{\bm{e}}\to e}$: }If $\lambda_k(\bm{v}_{\bm{e}})=on$, we first check whether $\lambda_k(\bm{e}) = on$, by checking whether there is neighboring faces from $M_k$ on $\bm{e}$. If not, we need to find where $\bm{v}_{\bm{e}}$ lies on $M_k$.
Because our tessellated meshes contain connectivity information, we can easily find all neighboring faces of $\bm{v}_{\bm{e}}$.
After that, the similar BSP-based classification method (as in ${\bm{e}_{\bm{s}}\to \bm{s}}$) can be used to determine the high dimension label $\lambda_k(\bm{e})$. We use the other end point $\bm{v}'_{\bm{e}}$ as the sample point for the BSP classification.

\vspace{0.5em}
\noindent\textbf{$\bm{s}_i\to \bm{s}_j$: } We need to determine which labels change if shared edge contains neighboring faces from other primitives. We can know which labels differ by the owner primitives of these neighboring faces. And the recomputation of these labels is exactly the same as in $\bm{\bm{e}_{\bm{s}}\to \bm{s}}$.

\subsection{Acceleration by Caching}
\label{sec:acc}

If the CSG tree is large, with hundreds of primitive nodes, evaluations of boolean expression by inclusion label vectors of each face can be costly. However, using label space coherence, we can reduce the computation time by caching the evaluation results.

The basic caching strategy is to cache the final evaluation results. Faces which share the same label vector can be classified together. We can also perform an intermediate results cache. The boolean expression can be simplified if some components of label vector are known. For example, assume we have a boolean expression $f = M_1\cup (M_2\cap M_3-M_4)$. Given the values of two labels $\lambda_1(\bm{s}_i)=out$, $\lambda_2(\bm{s}_i)=in$, the expression can be rewritten as $f(\lambda_1=out, \lambda_2=in)=out\cup (in\cap M_3-M_4)$. Using the combination rules, we can simplify the expression to $f(\lambda_1=out, \lambda_2=in)=M_3-M_4$.
In a large CSG, a certain primitive often intersects with only a few other primitives $\Theta= \{M_{n_1}, M_{n_2}, \cdots, M_{n_x}\}$. All of the faces in this primitive have the same labels with respect to primitives not in $\Theta$. Therefore, if we can determine these fixed labels and simplify the boolean function, then we compute the final label in this primitive based on the simplified expression.

\iffalse
\subsection{Tessellating on Classification}
We find for a CSG with many meshes, a large percentage of intersections are invalid (see \S\ref{sec:degenerate} for 'invalid'). Tessellation according to these invalid intersections is not necessary. To avoid unnecessary tessellation, we can give an early prediction of which intersections are invalid by intersections information of faces, but have to embed the tessellation stage into the classification stage, which we call it 'tessellating on classification'.

In most situations, a certain faces $\bm{s}$ only intersect with a few other meshes $\Theta(\bm{s})$. We can use the same cache strategy in \S\ref{sec:acc} to shrink the original CSG into a smaller one by the common labels of $\{P_i\}\backslash\Theta(\bm{s})$, where $\{P_i\}$ means all the primitive meshes. After the shrinking, the primitive meshes of the CSG must be from $\Theta(\bm{s})$. If any mesh in $\Theta(\bm{s})$ does not appear in the shrinked CSG, it means the label of that mesh does not change the classification result, which in another word, intersections on $\bm{s}$ from that mesh are invalid and do not affect the classification of any subfaces of $\bm{s}$. If the shrinked CSG is trivial which does not contain any primitives, it means $\bm{s}$ does not need tessellation. In this way, we save the computation time, and simplify the topology of the final result mesh. Because we can only shrink the CSG for $\bm{s}$ when we classify it---before that the labels of meshes from $\{P_i\}\backslash\Theta(\bm{s})$ are not known---we do not perform tessellation until we do the classification.
\fi

### 2017-01-21 tex/inter.tex
hello

@@
 \ref{fig:twin}a, the neighboring faces of the intersection on $t_1$ are $t_2$ and $t^*_2$.
-
-An edge intersection will be repeatedly detected.
-For example, in Fig.
-\ref{fig:twin}a, the same intersection on $t_1$ will be detected twice, because $t_1$ intersects both $t_2$ and $t_2^*$ at the same line segment.
+The same intersection on $t_1$ will be detected twice, because $t_1$ intersects both $t_2$ and $t_2^*$ at the same line segment.
+In fact, edge intersections are often detected for multiple times.
 We solve this duplication in tessellation stage (see \S\ref{sec:tessellation}).

### 2017-01-21 tex/overview.tex
hello

@@
 2) Face tessellation produces inconsistent topology.
-3) The computation of the inclusion labels is not consistent with the location of the faces (see Fig.
-\ref{fig:falseclass}).
+3) The computation of the inclusion labels is not consistent with the location of the faces.
 These problems all come from the numerical errors during geometric computation.
@@
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=2.2in]{boolean-01}
-\caption{In this 2D view, face $\bm{s}$ (the red line segment) of mesh $M_2$ is on the surface of mesh $M_1$.
+% \begin{figure}[t]
+% \centering
+% \includegraphics[width=2.2in]{boolean-01}
+% \caption{In this 2D view, face $\bm{s}$ (the red line segment) of mesh $M_2$ is on the surface of mesh $M_1$.
 However, because the face barycenter $\bm{v}_{c(\bm{s})}$ is used to compute the labels, the coordinates of which contain round-off errors, the point could be moved to $\bm{v'}_{c(\bm{s})}$.
 Thus, $\bm{s}$ may be falsely classified as being outside of $M_1$.}
-\label{fig:falseclass}
-\end{figure}
+% \label{fig:falseclass}
+% \end{figure}
 

### 2017-03-06 intro-hong.tex
before merge with hongbo

\IEEEtitleabstractindextext{
\begin{abstract}
	\ca{
  Constructive solid geometry (CSG) has been widely used for 3D modeling by combining primitive solids with boolean operations. 
  Striking a good balance between efficiency and robustness for boolean evaluation is not an easy task.} Some existing methods are fast but not robust, while some other are robust but slow due to their reliance on exact arithmetic. Recent works attempted to achieve both fast and robust boolean evaluation methods using plane-based representations (P-reps) of polyhedrons instead of vertex-based representations (V-reps) of polyhedrons \hongbo{too abrupt, since you have never talked about vertex-based representations earlier}. While they have achieved remarkable improvements, they are still slow compared with non-robust methods \hongbo{are they based on V-reps?}. We propose a fast and robust boolean method \hongbo{Better make your argument exact. Faster than? More robust than what? As fast as what?}. Our key idea is to use hybrid representations of polyhedrons, which combine P-reps with V-reps. The P-rep information is used for exact predicates computation and the V-rep information is for coarse tests and fast topology query, allowing us to take advantages of both the efficiency of V-reps and the exactness of P-reps. Comparisons with the state-of-the-art techniques show that our method is unconditionally robust for solid inputs, and is similarly efficient to existing non-robust methods. \hongbo{you should have at least one sentence to explain what ``N-Mesh'' is}
\end{abstract}

\begin{IEEEkeywords}
boolean operations, CSG evaluation, plane-based geometry
\end{IEEEkeywords}

}

\maketitle

\IEEEdisplaynontitleabstractindextext
\IEEEpeerreviewmaketitle

\begin{figure*}
	\centering
	\includegraphics[width=7in]{overview}
	\caption{The illustration of our framework for boolean evaluation using hybrid representations. Vertex-based computation has its advantage of efficiency, and plane-based is necessary to guarantee exact geometry predicates. }\label{fig:hybrid}
\end{figure*}

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{C}{onstructive} solid geometry (CSG) has long been a popular modeling tool for computer-aided design (CAD) and computer-aided manufacturing (CAM). Complex models are constructed by combining primitives using regularized boolean operations \cite{requicha1977mathematical,tilove1980closure}, namely, union, intersection, and difference. A CSG can be converted into the boundary representation (B-rep) through boolean evaluation. There are two major types of boolean evaluation methods, which vary according to how they deal with intersections between primitives.
Approximate methods \cite{wang2011approximate,pavic2010hybrid,biermann2001approximate} rediscretize \hongbo{why re-?} intersection areas, fit vertices approximatively, and rearrange the topology.
In constrast, exact methods \cite{ogayar2015deferred,douze2015quickcsg,zhou2016mesh} do not change vertex positions, and maintain as many input elements (such as faces, vertices, and topology) as possible. In many applications, exact methods are preferred for their accuracy. Additionally, the clear mapping between the surfaces of the input and output meshes in exact methods simplifies the inheritance of surface information, such as face colors and materials.

However, there is always a compromise between robustness and efficiency for exact boolean algorithms.
Robust methods often require exact arithmetic \cite{barki2015exact,zhou2016mesh}, which is significantly slower than normal floating-point arithmetic to evaluate.
Other methods only guarantee \textbf{quasi-robust} \hongbo{why boldface?} \cite{shewchuk1999lecture} by using unreliable techniques, such as epsilon-tweaking \cite{laidlaw1986constructive,feito2013fast,segal1990using} and numerical perturbation \cite{douze2015quickcsg}.
Recently, robust plane-based methods have been developed \cite{bernstein2009fast,campen2010exact} based on binary space partition (BSP) merging algorithms \cite{naylor1990merging,thibault1987set}.
The robustness of these methods is guaranteed by the theorem of Sugihara and Iri \cite{sugihara1990solid} that boolean evaluations can be performed without \textbf{constructions} \cite{shewchuk1999lecture} if polyhedrons are represented based on planes instead of vertices.
By using only \textbf{predicates}, it is easier to robust boolean methods.
These plane-based methods are generally faster than others which use exact arithmetic. However, they still suffer from performance issues because of the high computation complexity of BSP algorithms. In addition, the incoherence between BSP representations and B-reps of polyhedrons requires extra steps for conversion and connectivity reconstruction, leading to worse performance.

Inspired by these previous studies, we develop a robust boolean evaluation method, which is unconditionally robust given consistent solid inputs, and whose efficiency is comparable to non-robust methods. Our method combines P-reps with V-reps \hongbo{you should introduce P-rep and V-rep in the introduction again and make their advantages/disadvantages clear}, forming hybrid representations of solids, as illustrated in Figure~\ref{fig:hybrid}. Generally, the V-rep information is used for coarse tests and efficient neighboring face queries, while the P-rep information is used for exact predicates. To avoid using exact arithmetic and ensure efficiency, we avoid constructions throughout our method.
%
%\ca{making our method significantly faster than the previous BSP-based methods .}

%Our method is different from the previous BSP-based methods .
%While their methods are largely based on BSP theorem of \cite{naylor1990merging,thibault1987set}, our method is more like  and is .

\ca{Our method is more like vertex-based methods such as \cite{feito2013fast,zhou2016mesh} \hongbo{you didn't introduce vertex-based methods before} than BSP-based methods \cite{bernstein2009fast,campen2010exact}. However, we provide a systematical solution for robust boolean evaluations, instead of a simple improvement of vertex-based methods}. \hongbo{what is the purpose of the following text? More about the methodology itself or the difference from vertex-based approaches?} During intersection computation, we encode triangle intersections into sets of planes, and then use these planes to determine exact tessellations. \hongbo{Are the discussions here related to Fig. 1? If yes, please refer to different parts of the figure here} Subsequently, we classify each face in the tessellated meshes using small local BSP trees, which also compliment the P-reps to guarantee exactness. In order to achieve fast performance, we minimize the usage of plane-based exact predicates in these stages. In addition, while most existing boolean methods can only process two meshes in each time, our method is \textbf{variadic} \cite{zhou2016mesh} \hongbo{you haven't explained the N-Mesh appeared in the title}, and thus can evaluate boolean expression with multiple input meshes immediately \hongbo{simultaneously?}, reducing the evaluation time of large CSGs by avoiding repetitive computation. Experiments have shown that our method is much faster than the existing robust methods \hongbo{REF}, and only around two times slower than non-robust methods \hongbo{REF}.

\section{Related Work}
\hongbo{Since the main contribution is about the hybrid representation, you'd better clearly and explicitly introduce the vertex-based and plane-based methods. In addition, if we have any contribution using ``N-Mesh'' boolean evaluation, you'd also discuss the relevant existing works as well.}

Boolean methods have been researched since their inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}. Existing methods can be mainly divided into two categories: exact methods and approximate methods. Exact methods retain vertex positions, and the topology of the inputs is preserved as much as possible. The coordinates of intersection points between input meshes are computed by input configurations. However, the coordinates cannot be represented exactly using fixed-precision floating point numbers. Hence exact arithmetic is needed for robustness. In contrast, approximate methods rediscretize the input mesh surfaces using techniques like voxels, octrees, and Layered Depth Images (LDI). These methods generally have better performance and are often more robust than exact methods, but at the cost of relatively low precision and losing geometry information. 
\hongbo{It's expected you will comment whether the proposed technique is an exact or approximate method.}
In this section, we first introduce previous works of these two categories, and then discuss plane-based boolean methods, which have a close relation with our method.

\textbf{Exact Methods.}
Some exact methods (e.g., \cite{ogayar2015deferred,douze2015quickcsg,xu2013fast,feito2013fast,updegrove2016boolean}) are optimized for efficiency, but cannot guarantee robustness. Since they are implemented by fixed-precision floating-point arithmetic, numerical errors are inevitable and often lead to inconsistent results.
Douze et al. \cite{douze2015quickcsg} developed a very efficient method for handling very large meshes and arbitrary input primitives. However, their method makes a general position assumption and cannot deal with coplanar situations\hongbo{it's not clear why a general position assumption doesn't allow coplanar cases. in addition, you'd better comment if your method can handle coplanar cases}.

Some other methods focus more on achieving robustness. For example, the state-of-art method \cite{zhou2016mesh} tries to handle a large range of topology deficiencies and guarantees solid outputs, with the cost of many extra computations such as self-intersecting tests and vertex-rounding iterations.
Since the robustness problem is often due to numerical errors, many researchers have attempted use arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean, zhou2016mesh,barki2015exact} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}. However, exact arithmetic is computationally very expensive. For example, CGAL's \cite{cgal:hk-bonp3-15a} exact-arithmetic implementation \cite{granados2003boolean} of Nef polyhedra \cite{bieri1988elementary} is more than 50 times slower than non-robust boolean operations \cite{bernstein2009fast} \hongbo{why cite this work here? It is a robust plane-based approach?}. We aim to balance the performance and robustness, which guarantees solid outputs under valid inputs but without the use of exact arithmetic.

\textbf{Approximative Methods.}
Since it is difficult to achieve efficiency, accuracy, and robustness at the same time, some methods \hongbo{REF} sacrifice accuracy for greater efficiency and robustness. Most of such methods are based on volumetric representations of meshes. However, the quality of their results highly depends on the resolution of the volume grids, and better quality requires significantly higher resolutions.
To accelerate this process, some methods reduce the complexity of output meshes \cite{varadhan2004topology}, whereas others preserve non-intersected areas of input meshes to avoid redundant tessellation \cite{pavic2010hybrid,wang2011approximate,zhao2011parallel,hable2005blister,ogayar2006gpu,updegrove2016boolean}.
Moreover, with the development of general-purpose computing on graphics processing units (GPGPU), many of them utilize the computational power of graphics hardware for accelerating boolean evaluations. These methods achieve good performance, and thus are suitable for interactive applications. However, the fundamental problem of approximate methods arises from the grid-dependent nature of volumetric calculations. They inevitably suffer from geometric detail loss and unwieldy topological changes.
\hongbo{one sentence about our method}

\textbf{Plane-Based Methods.}
\label{sec:pbrelated}
The concept of plane-based representations (P-reps) of polyhedrons was first introduced by Sugihara and Iri \cite{sugihara1990solid}. By using the P-reps, boolean evaluations can be performed with only predicates, which are much easier to implement robustly \hongbo{than what?}. Berstein and Fussell \cite{bernstein2009fast} combined the P-reps with BSP trees \cite{thibault1987set,naylor1990merging} to develop a boolean evaluation method which is unconditionally robust with consistent inputs. Unlike vertex-based methods \hongbo{REF; again, no previous discussion on vertex-based methods yet}, their method \ca{is robust but without relying on exact arithmetic\hongbo{correct?}}
However, the merging of two BSP trees has $O(mn)$ time complexity, where $m$ and $n$ are the sizes of the trees. Such high time complexity\hongbo{only $O(m^2)$, not that computationally expensive?} makes this method impractical for large meshes. Subsequently, Campen and Kobbelt \cite{campen2010exact} improved this method by localizing BSP operations using an octree. In their method, mesh refinements only take place locally near intersections, leading to better performance. However, their method splits the intersection regions and non-intersection regions, and requires an extra stitching step to reconstruct topology. Also, the performance of localized BSP merging is still poor compared with the vertex-based methods. Our method uses plane-based geometry to guarantee no error introduced during boolean evaluation, while reducing the performance cost for plane-based computation with the V-rep information, which is much cheaper to use.

### 2017-03-06 paper.tex
before delete plane based implementation itemize
before merge with hongbo

@@
-\documentclass[10pt,journal,compsoc]{IEEEtran}
+\documentclass[10pt,final,compsoc]{IEEEtran}
 
@@
 
+\usepackage{amsthm}
+
 \usepackage{amssymb}% http://ctan.org/pkg/amssymb
@@
 \newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}
-
 \floatname{algorithm}{Algorithm}
+%\usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
+\newtheorem{theorem}{Theorem}
 
 \begin{document}
-\title{Efficient and Robust Plane-Based Boolean Operations on N Meshes}
-\author{%Rui~Wang,~
-        %Xudong~Jiang,~
-        %Hongbo~Fu,~
-        %Ping~Li,~
-        %Bin~Sheng~and
-        %Enhua~Wu
+\title{Efficient and Robust N-Mesh Boolean Operations Using Hybrid Representations}
+\author{
+        Rui~Wang,~
+        Bin~Sheng~
+        Hongbo~Fu,~
+        Ping~Li,~and~
+        Enhua~Wu
 \IEEEcompsocitemizethanks{
@@
 
-\IEEEcompsocthanksitem X. Jiang is with Autodesk China Research \& Development Center. Email: xudong.jiang@autodesk.com
+%\IEEEcompsocthanksitem X. Jiang is with Autodesk China Research \& Development Center. Email: xudong.jiang@autodesk.com
 
@@
 
-\IEEEcompsocthanksitem P. Li is with the Department of Mathematics and Information Technology, The Hong Kong Institute of Education. Email: pli@ied.edu.hk
+\IEEEcompsocthanksitem P. Li is with the Department of Mathematics and Information Technology, The Hong Kong Institute of Education. Email: pli@eduhk.hk
 
@@
 % if you will not have a photo at all:
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{xudong}}]{Xudong Jiang}
-received his Master degree in Computer Science from Shanghai Jiao Tong University in 2014.
+% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{xudong}}]{Xudong Jiang}
+% received his Master degree in Computer Science from Shanghai Jiao Tong University in 2014.
 He is currently working in Autodesk China Research \& Development Center.
 His research interest includes computer-aided geometric design and solid modeling.
+% \end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{sheng}}]{Bin Sheng}
+received his BS degree in computer science from Huazhong University of Science and Technology in 2004, MS degree in software engineering from University of Macau in 2007, and PhD Degree in computer science from The Chinese University of Hong Kong in 2011.
+He is currently an associate professor in the Department of Computer Science and Engineering at Shanghai Jiao Tong University.
+His research interests include virtual reality, computer graphics, and image-based techniques.
 \end{IEEEbiography}
@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{sheng}}]{Bin Sheng}
-received his BS degree in computer science from Huazhong University of Science and Technology in 2004, MS degree in software engineering from University of Macau in 2007, and PhD Degree in computer science from The Chinese University of Hong Kong in 2011.
-He is currently an associate professor in the Department of Computer Science and Engineering at Shanghai Jiao Tong University.
-His research interests include virtual reality, computer graphics, and image-based techniques.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{liping}}]{Li Ping}
+ received his Ph.D.
+from The Chinese University of Hong Kong.
+He is currently a Lecturer at The Education University of Hong Kong.
+His research interests include image/video stylization, learning analytics, big data visualization, and creative media.
 \end{IEEEbiography}

### 2017-03-06 tex/exp.tex
before merge with hongbo

\section{Results and Discussion}

\iffalse
\begin{figure}[t]
\centering
\includegraphics[width=3in]{perturb}
\caption{After perturbation, the self-union of \emph{Bunny} with QuickCSG still suffers from topology problem. The green boundary faces indicate topological deficiencies.}
%
\label{fig:boundaryedge}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3in]{buddalion}
\caption{ Results from $Budda\cup Lion$: a) incorrect result using CGAL, b) incorrect result using Cork, and c) correct result using our method. }
%.
\label{fig:buddalion}
\end{figure}
\fi
%We implemented the proposed method in C++ and tested a series of models on a laptop with Intel Core i5 1.5GHz CPU and 8GB RAM. To prove  both the efficiency and robustness, we perform boolean evaluation on various CSGs with different complexity. We also compared our method with several previous works with available implementations, including CGAL \cite{cgal:hk-bonp3-15a}, Maya \cite{Maya2015,barki2015exact},"Cork" \cite{Cork}, "QuickCSG" \cite{douze2015quickcsg}, "Carve" \cite{Carve}, and online service of Campen and Kobbelt's plane-based method \cite{campen2010exact,WebBSP}.

We implemented our proposed method in C++, and tested a series of models on a PC with an Intel Core i5 CPU and 8 GB of RAM. We compared our method with several existing methods, including CGAL \cite{cgal:hk-bonp3-15a}, Cork  \cite{Cork}, QuickCSG \cite{douze2015quickcsg}, Carve \cite{Carve}, and online service of Campen and Kobbelt's plane-based method \cite{campen2010exact,WebBSP}. Among them, CGAL and Carve use exact arithmetic. To ensure fairness, we turn off any features of multi-thread computation during the comparison.
%Also, the self-intersection tests of meshes are performed using an open-source library VCG \cite{VCG}.

\subsection{Self-Union on Thingi10K Dataset}

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{total3}
\caption{The performance of test on Thingi10k (top) and Barki et al.'s dataset (bottom). We outline the median of processing time for each method. The different histogram areas result from the different success rate.}
\label{fig:total}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{cleanness}
\caption{The result meshes of our method for the self-union of Thingi10k are cleaner than state-of-art methods. The Cork and QuickCSG assume general position and cannot handle self-union at all, so they failed to produce solids in most of the cases.}
\label{fig:cleanness}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{profile3}
\caption{Performance profile of tests on Thingi10k (top) and Barki et al.'s dataset (bottom). The red, yellow, green, blue areas represent the time percentage of octree construction, intersection computation, tessellation and classification, respectively. Each one-pixel column represents a test. All the tests are sorted by total processing time.}
\label{fig:profile}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3in]{scatter}
\caption{For the self-union tests on Thingi10k, the linear relation between processing time and triangle number is apparent.}
\label{fig:scatter}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3.2in]{comp}
\caption{\emph{First row}: the results of self-union of \emph{components}. QuickCSG (adding perturbation of 1e-12) and Cork cannot produce valid results. CGAL and Carve simple crashed and do not give a result. \emph{Second row}: In our self-union tests, QuickCSG tends to produce results with many boundary edges (green lines), and Cork tends to produce many self-intersecting faces (red faces).}
\label{fig:perturb}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3.0in]{boolean-11}
\caption{After coordinates approximation, the 'thin' triangle in the middle intersect adjacent faces and results in self-intersection on the mesh (red triangles).}
\label{fig:roundoff}
\end{figure}

We reproduce the experiments of \cite{zhou2016mesh} on the Thingi10K dataset on website thingiverse.com. The dataset currently contains 9956 .stl models, which are heavily biased towards 3D printing modeling by amateurs or semi-professionals. Since .stl models are triangle streams rather than meshes, we merge the exact coincident vertices to reconstruct connectivity. After that, we check the cleanness of all of the models. Among the 9956 meshes, 4509 meet the requirements of solid. The face numbers of these meshes generally follows a log-normal distribution with the average of 17k. We limit our comparison to these solid meshes.

The comparison results are available for CGAL, Cork, Carve and QuickCSG. Web service of Campen et al. \cite{campen2010exact,WebBSP} does not support batch processing. Therefore, we made a few tests manually, and roughly a half of them failed. The implementation of recent works \cite{zhou2016mesh,barki2015exact} are not available. Both methods are based on exact arithmetic. The performance of method in \cite{zhou2016mesh} is claimed to be close to Carve (with parallel computation) by the results on the same dataset Thingi10k in their paper.

The computation time of our method outperform most of other methods (see Fig. \ref{fig:total} \emph{top}). Even compared with the fastest QuickCSG, which is not exact, our method takes only about two times of the processing time. We profile each stage of our method, and the results indicate the bottleneck is the intersection computation (see Fig. \ref{fig:profile} \emph{top}). Also, from Fig. \ref{fig:scatter}, the linear relation between triangle number and processing time implies the ability of our method to handle large boolean evaluations.

Our method produces results in 98.8\% of the tests. The cleanness of resulting meshes are tested by checking self-intersecting (we use VCG \cite{VCG}) and the total signed incidence of every edge \cite{zhou2016mesh}. If the total signed incidence of every edge of a mesh is zero, then the mesh is a piecewise-constant
integer \emph{generalized winding number} (PWN) \cite{zhou2016mesh} mesh. These two requirements are sufficient conditions of solid. According to Fig. \ref{fig:cleanness}, over 80\% of our results are solids, which outperform all other methods. We also notice very low rates of success for Cork and QuickCSG. This is because both methods assume general position, which is not the case for self-union. Even after perturbation, they can hardly produce solid results (see Fig. \ref{fig:perturb}).

The failure cases and unclean results of our method do not impair the robustness of our algorithms. The reasons lie on the degenerate faces and close-to-degenerate faces from the inputs. The normal vectors of degenerate faces cannot be defined so face classification may fail when encounter such faces. Also, close-to-degenerate faces can become degenerate faces or lead to self-intersecting (see Fig. \ref{fig:roundoff}) after conversion to their P-reps. This is because the conversion method \cite{campen2010exact} requires coordinates rounding-off. In our implementation, the IEEE-754 single-precision floating-point coordinates (precision=24) are rounded to the precision of 18$\scriptsize{\sim}$20.

\subsection{Binary Boolean Operations}

\iffalse

\begin{table*}[ht]
\caption{Computation time statistics of binary boolean operations (seconds)}
\label{tab:performance}
\centering
\begin{tabular}{*{9}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
\hline
{No.} & {Model} & {Face Num. 1} & {Face Num. 2} &
CGAL & Maya & Cork & Carve & QuickCSG & Our Method
\\
\hline\hline
1 & Budda $\cup$ Lion & 1.08M & 400k & - & - & - & - & 3.44 & 4.30\\
2 & Dragon $\cup$ Bunny & 100k & 70k & - & - & - & - & 0.613 &1.12 \\
3 & Armadillo $\cup$ Armadillo2 & 150k & 150k & 487 & 15.4 & 7.00 & 189 & 0.746 & 1.33\\
4 & Horse $\cup$ Corpse & 145k & 499k & - & 38.6 & 12.6 & 1.52k & 0.630 & 0.980 \\
5 & Budda $\cup$ Budda2 & 1.08M & 1.08M & - & - & - & - & 4.84 & 7.73\\
\hline
\end{tabular}
\begin{flushleft}

\end{flushleft}
\end{table*}

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{total2}
\caption{a) There is ambiguity as to the orientation of the loop in this tess-graph. b) When there is more than one connected component in a tess-graph, auxiliary intersections (yellow line) are used to connect the components.}
\label{fig:profile2}
\end{figure}

\fi

The most common situations of boolean evaluations in CAD are binary evaluations. It is because people are used to incrementally refine their models by adding or subtracting one shape each time. Although our method is variadic, we perform comparisons of binary boolean evaluations. We reproduce the experiments in \cite{zhou2016mesh} on the dataset of Barki et al. \cite{barki2015exact}. The dataset of Barki et al. contains 26 triangle meshes. All of them are closed and manifold, and 10 of them contain local self-intersecting. We exhaustively perform union, intersection, and both asymmetric differences for all pairs, producing $26\times(26-1)/2 \times 4=1300$ results.

The configuration of such tests satisfy the general position assumption, so Cork and QuickCSG can produce correct result in more cases than during self-union tests. But we address that such tests are performed only for completeness and coplanar faces are important situations in CSG modeling. The results (see Fig. \ref{fig:total} \emph{bottom}) shows that our method is slightly slower than QuickCSG, and much faster than other exact methods. We notice the bottleneck shifts from intersection computation to octree construction in this time (see Fig. \ref{fig:profile} \emph{bottom}). This is because compared with self-union tests, the binary boolean evaluations generally process fewer intersections. We also find that Carve has shows much worse performance in these cases than in self-union tests, which indicates that Carve does not localize the boolean evaluations within intersection areas.

\subsection{Variadic Boolean Operations}

\begin{table*}[ht]
\caption{Computation time statistics of the evaluations of large CSGs (seconds)}
\label{tab:performance2}
\centering
\begin{tabular}{*{12}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
\hline
\multirow{2}{*}{No.} & \multirow{2}{*}{Model} & \multirow{2}{*}{\tabincell{c}{Face \\ Num.}} & \multirow{2}{*}{\tabincell{c}{Mesh \\ Num.}} & \multirow{2}{*}{\tabincell{c}{CGAL \\ \cite{cgal:hk-bonp3-15a}}}
& \multirow{2}{*}{\tabincell{c}{Cork \\ \cite{Cork}}} & \multirow{2}{*}{\tabincell{c}{Carve \\ \cite{Carve}}} & \multirow{2}{*}{\tabincell{c}{QuickCSG \\ \cite{douze2015quickcsg}}}&
\multicolumn{5}{c}{Our Approach$^\dag$}\\
 \cline{9-13}
 &&&&&&&& Total & Step 1 & Step 2 & Step 3 & Step 4\\
 \hline\hline
 1 & Organic & 219k & 6 & - & 14.3 & 63.1 & 0.580 & 2.75 & 0.892 & 1.32 & 0.397 & 0.118\\
 2 & T1 & 80k & 50 & 1.00k & 18.5 & 10.4 & 0.388 & 14.4 & 0.691 & 2.71  & 8.11 & 2.87\\
 3 & T2 & 7k & 50 & 2.81k & - & 16.0 & 0.804 & 5.52 & 0.162 & 1.11 & 3.29 & 0.746\\
 4 & Sprocket & 11k & 52 & 211  & - & 4.26 & (0.132)* & 0.386 & 0.093 & 0.105 & 0.149 & 0.034\\
 5 & Ring \& Ball & 146k & 801 & -  & - & 187 & (1.10) & 20.0 & 1.04 & 3.55 & 8.61 & 6.68\\
 \hline
 \end{tabular}
 \begin{flushleft}
   $^\dag$ ~~The \emph{step 1, 2, 3, 4} are octree constrcution, intersection computation, tessellation and classification respectively.

 * ~~The bracket indicates that although QuickCSG gives the answer, the result meshes are full of topology deficiencies that contain thousands of boundary edges.
 \end{flushleft}
 \end{table*}

\begin{figure*}[t]
\centering
\includegraphics[width=7in]{multi}
\caption{The result meshes of our method for variadic boolean evaluations. From the left to the right is Organic, T1, T2, Sprocket and Ring \& Ball respectively. The performance of our method is better on cases with loosely distributed primitives (T2, Sprocket, Ring \& Ball).}
\label{fig:multi}
\end{figure*}

To identify the ability of the methods to evaluate large CSGs, we reproduce the experiments of Douze et al. \cite{douze2015quickcsg}. Some of variadic test cases are not presented because of the 8GB memory limitation. Since only QuickCSG and our method are variadic, comparisons with the other methods are performed by decomposing CSG into binary boolean operations. We also add an extreme CSG with 801 primitives to prove the effect of label caching (\S\ref{sec:acc}).

The performance of our method  (see Table \ref{tab:performance2}) is not that good in these cases, because our method exhaustively compute all intersections between primitives, which is not necessary. The QuickCSG is much faster than our method, but generally produces results with worse qualities. Except QuickCSG, our performance is better than other methods in most time. The evaluation time of \emph{Ring} \& \emph{Ball} is 38.1s in our first try. We find that each primitive usually intersects with less than 10 other primitives. Therefore, we applied the label caching, and the total computation time drops to only half of the original.

\subsection{Implementation}
\label{sec:esubroutine}

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{boolean-06}
\caption{a) We construct an auxiliary connection to connect each inner component with outer component (the red line segment). By checking the intersections on the auxiliary connection, we find that the orange loops are identical.  b) We construct the P-rep of the auxiliary connection by $\bm{v}_o$ and the exact coordinates of the end points of $\bm{e}$. }
\label{fig:dual}
\end{figure}

\vspace{0.5em}
\noindent\textbf{Tess-graph with multiple components. }
There is no guarantee that the tess-graph will be a connected graph. If a tess-graph contains more than one connected component, we need to merge identical valid loops, which allows us to generate polygons with non-zero genus. To find identical loops, we construct an auxiliary connection $C_{ext}$ for each inner component, which connects a vertex $\bm{v}_o$ on the outer component and a vertex $\bm{v}_i$ on the current inner component (see Fig. \ref{fig:dual}a). After that, we search all the connections belongs to the current inner component that intersection $C_{ext}$, and find the one (as $C_1$) which is the nearest to $\bm{v}_o$. Then we search all the connections not belongs to the current inner component that intersection $C_{ext}$, and find the one (as $C_2$) which is the nearest to $C_1$. Finally, by figuring out in which valid loops $C_1$ and $C_2$ are, we find the identical pair of loops.

To guarantee that $C_{ext}$ has an exact P-rep within double-precision, the vertex of triangle is chosen as the $\bm{v}_o$. On the other hand, $\bm{v}_i$ must be the vertex generated by the intersection between an triangle and an edge (as $\bm{e}$). All intersection points introduced by triangle-triangle intersections are of this type. In this way, we obtain three vertices with exact coordinates ($\bm{v}_o$ and the two end points of $\bm{e}$). Therefore, we can construct the plane on which $C_{ext}$ lies by the same method of generating supporting planes of triangle faces (see Fig. \ref{fig:dual}b).

\vspace{0.5em}
\noindent\textbf{Seed label generation. }
The label vector of the seed vertex can be generated by a point-in-polyhedron test \cite{ogayar2005point}, using the octree as an acceleration structure \cite{frisken2002simple}. However, a simpler strategy can be adopted which chooses a vertex with known labels as the seed. The inclusion labels of vertex with the maximum $x$-coordinate are either $out$ ($in$, if the complement is applied on the mesh) or $on$. The $on$ labels can be determined by connectivity. Exceptions can occur because of our ignorance of coplanar situations---vertices may not be added to the primitive, even if they are on surface of it. Fortunately, if seed vertex is chosen whose neighboring faces are not all coplanar, exceptions can be avoided.

Label vectors can propagate within a certain mesh, and between different meshes across shared edges. Therefore, in most cases, only a single seed vertex is needed for classification. However, if there are more than two connected components among the tessellated meshes, extra seeds are required. The labels of these additional seeds have to be computed by point-in-polyhedron tests.

\vspace{0.5em}
\noindent\textbf{Exporting to float-point number. }
The vertices of the final mesh are represented as either planes or vertex coordinates. The vertices originating from the input meshes have exact coordinates, and the vertices newly introduced by the intersection between meshes have only P-reps, and require round-off when computing their coordinates. Although our method guarantees the correct topology in the final mesh, round-off errors can still cause topological deficiencies. This is called \textbf{vertex rounding} problem. We can adopt the method of Zhou et al. \cite{zhou2016mesh} to solve this problem iteratively. For the consideration of efficiency, we do not include this step during our comparison experiments.

\subsection{Limitations and Future Work}

We found that performance of our method was poor for CSGs that contained a lot of meshes within a small area (Table. \ref{tab:performance2}, \emph{T1}). In these cases, our method computes many intersections that will not appear as edges in the final mesh, leading to unnecessary tessellation. Optimization may be explored to alleviate this problem.

The inputs of our method are limited to solids. However, recent work \cite{zhou2016mesh} have proposed that the piecewise-constant integer \emph{generalized winding number} (PWN) is a more powerful method to identify the insides and outsides of meshes. The input requirements of our method may be extended to PWN meshes, that allow self-intersection. We believe that this would be an interesting and valuable extension of our work.

\section{Summary}

In this paper, we propose a novel boolean method. Our method can efficiently perform variadic boolean operations, and is robust with solid inputs. The novel component of our approach is to combine P-reps with V-reps. P-reps allow us to strictly follow the principle of no geometry construction to avoid numerical errors ,and the V-reps enables coarse tests and fast neighborhood queries to reduce the need of slow plane-based computation. The experimental results show that the performance of our method is competitive with state-of-the-art non-robust methods, while guaranteeing robustness under consistent inputs.

### 2017-03-06 tex/inter.tex
before merge with hongbo

@@
 \begin{wrapfigure}{r}[0in]{0in}
-\includegraphics[width=1.2in]{octreediff}
+\includegraphics[width=1.2in]{boolean-10}
 \end{wrapfigure}
@@
 \centering
-\includegraphics[width=2.5in]{projection}
+\includegraphics[width=3.5in]{boolean-12}
 \caption{$Seg_1$ is the intersection between $\bm{p}_{t_2, sp}$ and $t_1$.
 $Seg_2$ is the intersection between $\bm{p}_{t_1, sp}$ and $t_2$.
-The intersection between $t_1$ and $t_2$ (yellow line segment) is the overlap of $Seg_1$ and $Seg_2$.}
+The intersection between $t_1$ and $t_2$ (red line segment) is the overlap of $Seg_1$ and $Seg_2$.}
 %Seg1 is the intersection between pt2,sp and t1. Seg2 is the intersection between pt1,sp and t2. The intersection between t1 and t2 (yellow line segment) is the overlap of Seg1 and Seg2.
@@
 \centering
-\includegraphics[width=3in]{pbirep2}
-\caption{The geometry of planes in a PBI-rep. The yellow line segment is the intersection represented by $\bm{\mathcal{I}}$.}
+\includegraphics[width=3in]{boolean-13}
+\caption{The geometry of planes in a PBI-rep. The red line segment ($\bm{\mathcal{I}}$) is the intersection represented by $\bm{\mathcal{I}}$.}
 \label{fig:pbi}
@@
 This means we can compute the signed distance exactly within double-precision.
-With these two facts, our early rejection is as fast as the vertex-based implementation.
+With these two facts, our early rejection does not involve plane-based computation, thus is very efficient.
 
-If $t_1$ and $t_2$ are not coplanar, $Seg_1$ and $Seg_2$ are computed.
+If early rejection is not triggered and $t_1$ and $t_2$ are not coplanar, $Seg_1$ and $Seg_2$ are computed.
 The end points are intersections between the supporting plane of one triangle and an edge of the other triangle.

### 2017-03-06 tex/intro.tex
before merge with hongbo

@@
 It uses hybrid representations of polyhedrons, which combines P-reps with V-reps.
-It allows us to take advantages of both the efficiency of V-reps and the exactness of P-reps.
+The P-rep information is used for exact predicates computation and the V-rep information is used for coarse tests and fast topology query, which allows us to take advantages of both the efficiency of V-reps and the exactness of P-reps.
 Comparison experiments with the state-of-the-art show that our method is unconditionally robust for solid inputs, and is similarly efficient to existing non-robust methods.
@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=7in]{overview}
+  \caption{The illustration of our framework for boolean evaluation using hybrid representations.
+Vertex-based computation has its advantage of efficiency, and plane-based is necessary to guarantee exact geometry predicates.
+}\label{fig:hybrid}
+\end{figure*}
+
 However, there is always a compromise between robustness and efficiency for exact boolean algorithms.
@@
 
-Inspired by these previous studies, we develop a robust boolean method, which is unconditionally robust given consistent solid inputs, and as fast as non-robust methods.
+Inspired by these previous studies, we develop a robust boolean method, which is unconditionally robust given consistent solid inputs, and is comparable efficient as non-robust methods.
 In our method, we combine P-reps with V-reps, forming hybrid representations of solids.
-Generally, the V-reps information is used for coarse tests and efficient neighboring face queries, while P-reps information is used for exact predicates.
+Generally, the V-reps information is used for coarse tests and efficient neighboring face queries, while P-reps information is used for exact predicates (see Fig.
+\ref{fig:hybrid}).
 To avoid using exact arithmetic and ensure efficiency, we avoid constructions throughout our method.
@@
 In order to guarantee performance, we try to minimize the usage of plane-based exact predicates in these stages.
-In addition, while most existing boolean methods can only process two meshes, our method is \textbf{variadic} \cite{zhou2016mesh}, which can evaluate arbitrary inputs immediately.
-Thus, our method may reduce evaluation time of large CSGs by avoiding repetitive computation.
+In addition, while most existing boolean methods can only process two meshes in each time, our method is \textbf{variadic} \cite{zhou2016mesh}, which can evaluate boolean expression with multiple input meshes immediately.
+Thus, our method reduce evaluation time of large CSGs by avoiding repetitive computation.
 Experiments have shown that our method is much faster than existing robust methods, and only around two times slower than non-robust methods.
@@
 
-Many researchers have attempted to solve the robustness issues using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean, zhou2016mesh,barki2015exact} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}.
-However, these methods are too expensive in terms of computation time.
+On the other hand, some methods focus on robustness.
+The state-of-art method \cite{zhou2016mesh} try to handle a large range of topology deficiencies and guarantee to give solid outputs, with the cost of many extra computations such as self-intersecting test and vertex-rounding iterations.
+As robustness problem results from numerical errors, many researchers have attempted use arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean, zhou2016mesh,barki2015exact} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}.
+However, exact arithmetic are too expensive in terms of computation time.
 For example, CGAL's \cite{cgal:hk-bonp3-15a} exact-arithmetic implementation \cite{granados2003boolean} of Nef polyhedra \cite{bieri1988elementary} is more than 50 times slower than non-robust boolean operations \cite{bernstein2009fast}.
+Our method try to balance the performance and robustness, which guarantees the solid outputs under valid inputs without the use of exact arithmetic.
 
@@
 Also, the performance of localized BSP merging is still poor compared with the vertex-based methods.
+Our method uses plane-based geometry to guarantee no error introduced during boolean evaluation, while reduces the performance impact from plane-based computation with V-reps information, which is much cheaper to use.

### 2017-03-06 tex/overview.tex
before merge with hongbo

@@
 \begin{wrapfigure}{r}[0in]{0in}
-\includegraphics[width=1.5 in]{p-reps}
+\includegraphics[width=1.5 in]{boolean-07}
 \end{wrapfigure}
@@
 This makes geometric computations significantly slower under P-reps.
-Even though numerical filters can be applied to speed up, pure plane-based methods, such as \cite{sugihara1990solid,banerjee1996topologically}, cannot be as fast as vertex-based methods.
-On the other hand, a hybrid representation may bring both the efficiency of V-reps and the exactness of P-reps.
+Even though numerical filters can be applied to speed up, pure plane-based methods, such as \cite{sugihara1990solid,banerjee1996topologically}, are significant slower than vertex-based methods.
+On the other hand, a hybrid representation can bring both the efficiency of V-reps and the exactness of P-reps.
 And plane-based geometric computation should be avoided as much as possible to reduce computation cost.
@@
   \centering
-  \includegraphics[width=3.5in]{twopointoneline}\\
+  \includegraphics[width=3.5in]{boolean-09}\\
   \caption{Geometric configuration of the linear ordering of points.
@@
 
-\noindent Given a line $\bm{l}_{ab}$ with two points on it, $\bm{v}_a\colon(\bm{p}_a^0\cap\bm{p}_a^1\cap\bm{p}_a^2)$, and $\bm{v}_b\colon(\bm{p}_b^0\cap\bm{p}_b^1\cap\bm{p}_b^2)$, we need to determine the linear order of the two points along $\bm{l}_{ab}$ (see Fig.
+\noindent Given a line $\bm{l}$ with two points on it, $\bm{v}_a\colon(\bm{p}_a^0\cap\bm{p}_a^1\cap\bm{p}_a^2)$, and $\bm{v}_b\colon(\bm{p}_b^0\cap\bm{p}_b^1\cap\bm{p}_b^2)$, we need to determine the linear order of the two points along $\bm{l}$ (see Fig.
 \ref{fig:twopointoneline}).
-To solve this problem, we choose one plane that is not parallel with $\bm{l}_{ab}$ from the P-rep of each point, then convert this problem into one of determining the linear order of planes, which can be solved using the method of Banerjee et al.
+To solve this problem, we choose one plane that is not parallel with $\bm{l}$ from the P-rep of each point, then convert this problem into one of determining the linear order of planes, which can be solved using the method of Banerjee et al.
 \cite{banerjee1996topologically}.
-The chosen planes should have the same orientation with respect to $\bm{l}_{ab}$ (the dot product between the plane normal and $\bm{l}_{ab}$ must be positive), and unqualified planes need to be flipped.
+The chosen planes should have the same orientation with respect to $\bm{l}$ (the dot product between the plane normal and $\bm{l}$ must be positive), and unqualified planes need to be flipped.
 
@@
 \centering
-\includegraphics[width=3.5in]{circularorder}
+\includegraphics[width=3.5in]{boolean-08}
 \caption{Geometric configuration of the circular ordering of lines. $\bm{l}_a\colon(\bm{p}_0 \cap \bm{p}_a)$ and $\bm{l}_b\colon(\bm{p}_0 \cap \bm{p}_b)$ are within plane $\bm{p}_0$.}

### 2017-03-06 tex/tess.tex
before merge with hongbo

@@
 \begin{wrapfigure}{r}[0in]{0in}
-\includegraphics[width=1.6 in]{resolve}
+\includegraphics[width=1.5 in]{resolve}
 %\caption{Plane-based representation of triangle}
@@
 Each pair of intersections is tested if they intersect in any location other than end points.
-The test intersections should be from different primitives, since primitive inputs are free of self-intersecting.
+The tested intersections should be from different primitives, since primitive inputs are free of self-intersecting.
+The three conditions of intersections are illustrated on the right.
 When two intersections intersect, at least one of them is split.
-New vertices may be introduced, whose P-reps are intersections between the common plane and the two $\bm{P}_ext$ of the PBI-reps.
+New vertices may be introduced, whose P-reps are intersections between the common plane and the two $\bm{P}_{ext}$ of the PBI-reps of the two intersections.
 Because one intersection may be in contact with more than one other intersection, this splitting is deferred until all of the splitting points are found.
